### 2019-05-15 ManuscriptSample.tex
template and tex files for QSS

%% Documentclass:
%% Network Neuroscience
%\documentclass[finalfonts,NETN]{stjour}
%\documentclass[NETN]{stjour}

%% or 
%\documentclass[finalfonts,NETN]{stjour}

%% or 
%% Manuscript, for double spaced, larger fonts
\documentclass[manuscript,NETN]{stjour}
%% Only needed if you use `manuscript' option
 \journalname{Network Neuroscience}

%%%%%%%%%%% Article Set-Up %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Article Type:
%% Default is Research.

%% Or, choose one of these options:
%% Research, Methods, Data, Review, and Perspective

\articletype{Perspective}

%%%%%%%%%%% Please supply information %%%%%%%%%%%%%%%%%%%%%%%%%

\supportinginfo{dx.doi.org/10.7910/DVN/PQ6ILM}

%% if no conflicts, this command doesn't need to be used
%% \conflictsofinterest{}

%%%%%%%%%%% to be supplied by MIT Press, only %%%%%%%%%%%%%%%%%
\citation{Betzel, R. F., Fukushima, M.,
He, Ye,
Zuo, Xi-Nian,
Sporns, O. (2016)\\
Dynamic fluctuations coincide with periods of high and low modularity
in resting-state functional brain  networks\\
Network Neuroscience, 1
}

\received{20 October 2016}
\accepted{7 November 2016}
\published{26 January 2016}
\setdoi{10.1162/NETN-00001} %% ???

\handlingeditor{Xi-Nian Zuo}

%%%%%%%% End MIT Press commands %%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% author definitions should be placed here:

%% example definition
\def\taupav{\tau_{\mathrm{Pav}}}

\begin{document}
\title[Shortened Version of Title]{Title of Article}
\subtitle{Subtitle Here}

%% If shortened title for running head is needed so that the article title can fit
%%   in the running head, use [] argument, ie,
%%
%%   \title[Shortened Title for Running Head]{Title of Article}
%%   \subtitle{Subtitle Here}

%% Since we use \affil{} in the argument of the \author command, we
%% need to supply another version of the author names, without \affil{}
%% to be used for running heads:

\author[Author Names]
{Author Names with affiliations\affil{1},
Another Name\affil{2}, Still another Name\affil{2},\\
\and Final Name\affil{1}}

\affiliation{1}{Department, Institution, City, Country}

%ie.
%\affiliation{1}{Gatsby Computational Neuroscience Unit, University
%College London, London, United Kingdom}

\affiliation{2}{Another Department, Institution, City, Country}

%ie
%\affiliation{2}{Center for Studies in
%Behavioral Neurobiology, Concordia University, Montreal, Quebec,
%Canada}

\correspondingauthor{Author Name}{Corresponding author email address}

% ie,
%\correspondingauthor{Ritwik K. Niyogi}{ritwik.niyogi@gatsby.ucl.ac.uk}

\keywords{(a series of uncapitalized words, separated with commas)}

%ie
%\keywords{work, leisure, normative, microscopic,  reinforcement learning, economics}

\begin{abstract}
Abstract text here.
\end{abstract}

\begin{authorsummary}
Author summary here. 
\end{authorsummary}

\section{Sample Section}
Text here. Text here. Text here. Text here.
Text here. Text here. Text here. Text here.
Text here. Text here. Text here. Text here.
Text here. Text here. Text here. Text here.

\subsection{Sample Subsection}
Text here. Text here. Text here. Text here.
Text here. Text here. Text here. Text here.
Text here. Text here. Text here. Text here.
Text here. Text here. Text here. Text here.

\subsubsection{Sample Subsubsection}
Text here. Text here. Text here. Text here.
Text here. Text here. Text here. Text here.
Text here. Text here. Text here. Text here.
Text here. Text here. Text here. Text here.

\newpage
\section{Sample equations}
\begin{equation}
\label{eq:rhoCHT}
\rho^{\pi}= \frac{RI + \mathbb{E}_{\pi([L,\tau_L]|\textrm{post})}
\left[C_L(\taupav+\tau_L) \right]   +
\displaystyle{\int_{0}^{P}}{dw~ \mathbb{E}_{\pi_{w_L}}}
\Biggl[\/\sum_{n_{L|[\textrm{pre},w]}}C_L(\tau_L)
\Biggr]            }      {P +
\mathbb{E}_{\pi([L,\tau_L] |\textrm{post})}[\tau_{L}] +\taupav +
\displaystyle{ \int_{0}^{P}}{dw~ \mathbb{E}_{\pi_{w_L}}}   
\Biggl[\sum_{n_{L|[\textrm{pre},w]}}\tau_L\Biggr]  
}
\end{equation}
As long as
$RI - K_LP > 
\frac{1}{\beta}$
\begin{equation}
%\def\theequation{5.1}
\left.\begin{array}{lrcl}
&\rho^{\pi} &=&  \displaystyle\frac{\beta ( RI + K_L \taupav )-1} {\beta
(P+\taupav )}    \\[12pt]
\hbox{and}\hbox to .25in{\hfill}&\mathbb{E}[\tau_L | \text{post}] &=&\displaystyle \frac{P+\taupav}{\beta ( RI -
K_LP)-1}  
\label{eq:analytical_linear}
\end{array}\right\}\hbox to 1.25in{\hfill}
\end{equation} 
Text finishing first page.
Text finishing first page.
Text finishing first page.
Text finishing first page.
Text finishing first page.
Text finishing first page.
Text finishing first page.

\begin{boxedtext}{Comparative Analysis of Different Classes of Networks} 
Going beyond the examination of shared topological features across
nervous systems, the generalized mathematical language of graph theory
also offers tools for the comparison of the organization of brain
networks to other classes of network studied
by different scientific
disciplines.

Many real-world systems operate as some sort of
interaction or communication network, including, for example, social
networks, gene regulatory networks, computer networks, and
transportation networks. Similar to brain networks, many of these
real-world networks display an efficient small-world organization, a
pronounced community structure with densely connected modules, as well
as the formation of hubs and rich clubs. Going beyond the
comparison of networks within the class of nervous systems, the field
of `comparative network analysis' examines commonalities and
differences across a range of network classes.

\begin{figure}
\includegraphics[width=\hsize]{Fig1}
\caption{Here is the caption.}
\end{figure}
\end{boxedtext}

\begin{boxedtext}{Comparative Analysis of Different Classes of Networks} 
Going beyond the examination of shared topological features across
nervous systems, the generalized mathematical language of graph theory
also offers tools for the comparison of the organization of brain
networks to other classes of network studied by different scientific
disciplines. Many real-world systems operate as some sort of
interaction or communication network, including, for example, social
networks, gene regulatory networks, computer networks, and
transportation networks. Similar to brain networks, many of these
real-world networks display an efficient small-world organization, a
pronounced community structure with densely connected modules, as well
as the formation of hubs and rich clubs. Going beyond the
comparison of networks within the class of nervous systems, the field
of `comparative network analysis' examines commonalities and
differences across a range of network classes.

\begin{table}[ht]
\caption{Here is the caption.}

\centerline{\begin{tabular}{|c|c|c|}
\hline
one&two&three\\
\hline
four&five&six\\
\hline
\end{tabular}}
\end{table}
\end{boxedtext}

\subsection{Jargon Samples in margin}
One common decision is between working (performing an employer-defined
task) and engaging in leisure (activities pursued for oneself). Working
leads to external rewards such as food and money; whereas leisure is
supposed to be intrinsically beneficial \jargon[2in]{Intrinsically beneficial}{The characteristic of
leisure that we enjoy most.} (otherwise one would not want to
engage in it).
%% \jargon has optional argument in square brackets where you can specify
%% the amount of extra space below where it would normally appear when 
%% two \jargon entries are in the same paragraph:
$\beta \in [0,\infty)$\jargon[24pt]{$\beta \in [0,\infty)$}{inverse temperature or degree of
stochasticity-determinism parameter.} is often used to indicate an
important parameter, the stochasticity-determinism parameter.

\subsection{Simple code sample}

\begin{code}
\begin{verbatim}
procedure bubbleSort( A : list of sortable items )
    n = length(A)
    repeat
       newn = 0
       for i = 1 to n-1 inclusive do
          if A[i-1] > A[i] then
             swap(A[i-1], A[i])
             newn = i
          end if
       end for
       n = newn
    until n = 0
end procedure
\end{verbatim}
\end{code}

\subsection{Algorithm environment}
%% \begin{algorithm} takes option [p][b][t][h],  or some combination, like \begin{figure}
%% See documentation for algorithmic.sty for more information on formatting algorithms.

\begin{algorithm}[h]
\caption{A sample in an algorithm environment.}
\begin{algorithmic}
\If {$i\geq maxval$}
    \State $i\gets 0$
\Else
    \If {$i+k\leq maxval$}
        \State $i\gets i+k$
    \EndIf
\EndIf
\end{algorithmic}
\end{algorithm}

\section{Itemized Lists}

\subsection{Roman list:}

\begin{enumerate}
\item[(i)] at high 
payoffs, subjects work almost continuously.
\item[(ii)] at low payoffs, they 
engage in leisure all at once, in long bouts after working.
\item[(iii)] subjects work continuously for the entire price duration, as long as
the price is not very long;
\item[(iv)] the duration of leisure bouts is variable.
\end{enumerate}

\subsection{Numbered list:}

\begin{enumerate}
\item at high 
payoffs, subjects work almost continuously, engaging in little leisure
inbetween work bouts; 
\item at low payoffs, they 
engage in leisure all at once, in long bouts after working, rather
than distributing the same amount of leisure time into multiple short
leisure bouts; 
\item subjects work continuously for the entire price duration, as long as
the price is not very long (as shown by an analysis conducted by
Y-AB, to be published separately);  
\item the duration of leisure bouts is variable.
\end{enumerate}

\subsection{Bulleted list:}

\begin{itemize}
\item at high 
payoffs, subjects work almost continuously, engaging in little leisure
inbetween work bouts; 
\item at low payoffs, they 
engage in leisure all at once, in long bouts after working, rather
than distributing the same amount of leisure time into multiple short
leisure bouts; 
\item subjects work continuously for the entire price duration, as long as
the price is not very long (as shown by an analysis conducted by
Y-AB, to be published separately);  
\item the duration of leisure bouts is variable.
\end{itemize}

\subsection{Description list:}
\begin{description}
\item[High payoffs:] at high 
payoffs, subjects work almost continuously, engaging in little leisure
inbetween work bouts; 
\item[Low payoffs:] at low payoffs, they 
engage in leisure all at once, in long bouts after working, rather
than distributing the same amount of leisure time into multiple short
leisure bouts; 
\item[Continuous work:] subjects work continuously for the entire price duration, as long as
the price is not very long (as shown by an analysis conducted by Y-AB, to be published separately); 
\item[Duration:] the duration of leisure bouts is variable.
\end{description}

\newpage
\section{Sample citations}
For general information on the correct form for citations using
the APA 6 format, see the following sites:
\href{https://owl.english.purdue.edu/owl/resource/560/02/}
{APA 6, In-text citations, The Basics} and
\href{https://owl.english.purdue.edu/owl/resource/560/03/}
{APA 6, In-text citations}

\section{Natbib citation mark up}

\subsection{Single citations}
\noindent
\begin{tabular}{ll}
\bf Type&\bf Results\\
\hline
\verb+\citet{jon90}+&\dogray Jones et al. (1990)\\
\verb+\citet[chap. 2]{jon90}+&\dogray Jones et al. (1990, chap. 2)\\
    \verb+\citep{jon90}+	    &\dogray   	(Jones et al., 1990)\\
    \verb+\citep[chap. 2]{jon90}+ 	&\dogray    	(Jones et al., 1990, chap. 2)\\
    \verb+\citep[see][]{jon90}+ 	 &\dogray    	(see Jones et al., 1990)\\
    \verb+\citep[see][chap. 2]{jon90}+ 	&\dogray    	(see Jones et al., 1990, chap. 2)\\
    \verb+\citet*{jon90}+ 	    &\dogray    	Jones, Baker, and Williams (1990)\\
    \verb+\citep*{jon90}+	    & \dogray   	(Jones, Baker, and Williams,
    1990) \\
\end{tabular}

For example, some citations from the NETNbibsamp.bib database:

citet: \citet{bullmore2009complex}, citep: \citep{gomez2009analysis}, and
citep*: \citep*{de2012cortical}

\subsection{Multiple citations}
Multiple citations may be made by including more than one citation
key in the \verb+\cite+ command argument.

\noindent
\begin{tabular}{ll}
\bf Type&\bf Results\\
\hline
\verb+\citet{jon90,jam91}+&\dogray Jones et al. (1990); James et al. (1991)\\
\verb+\citep{jon90,jam91}+&\dogray (Jones et al., 1990; James et al. 1991)\\
\verb+\citep{jon90,jon91}+&\dogray (Jones et al., 1990, 1991)\\
\verb+\citep{jon90a,jon90b}+&\dogray (Jones et al., 1990a,b)\\
\end{tabular}

For example, multiple citations from the bibsamp.bib database:
citet: \citet{nooner2012nki,hutchison2013resting},
 citep:
\citep{tagliazucchi2012dynamic, de2012cortical}

As you see, the citations are automatically hyperlinked to their
reference in the bibliography.

\newpage

\section{Sample figures}

\begin{figure}[h] 
\centerline{\includegraphics[width=\textwidth]{Fig1.pdf}}
\caption{(Colour online) \textbf{Task and key features of the
 data.} \\
 A) Cumulative handling time (CHT) task. Grey bars denote work
(depressing a lever), white gaps show leisure. The subject must
accumulate work up to a total period of time called the
\emph{price} ($P$) in order to obtain a single reward (black dot) of subjective reward
intensity $RI$. The trial duration is $25\times \mathrm{price}$ (plus
$2$s each time the price is attained, during which the lever is retracted so it cannot
work; not shown).}
\label{fig:task_data}
\end{figure}
%% this command ends a page but does not fill the bottom with white space:
\eject

\begin{figure}[ht] 
\widefigure{\fullpagewidth}{Fig1.pdf}
\caption{(Colour online) \textbf{Task and key features of the
 data.} \\
 A) Cumulative handling time (CHT) task. Grey bars denote work
(depressing a lever), white gaps show leisure. The subject must
accumulate work up to a total period of time called the
\emph{price} ($P$) in order to obtain a single reward (black dot) of subjective reward
intensity $RI$. The trial duration is $25\times \mathrm{price}$ (plus
$2$s each time the price is attained, during which the lever is retracted so it cannot
work; not shown).}
\label{fig:task_data2}
\end{figure}

\newpage
\section{Sample tables}

\begin{table}[!ht]
\caption{Time of the Transition Between Phase 1 and Phase 2$^{a}$}
\label{tab:label}
\centering
\begin{tabular}{lc}
\hline
 Run  & Time (min)  \\
\hline
  $l1$  & 260   \\
  $l2$  & 300   \\
  $l3$  & 340   \\
  $h1$  & 270   \\
  $h2$  & 250   \\
  $h3$  & 380   \\
  $r1$  & 370   \\
  $r2$  & 390   \\
\hline
\multicolumn{2}{l}{$^{a}$Table note text here.}
\end{tabular}
\end{table}

\begin{table}[ht]
\widecaption{Sample table taken from [treu03]\label{tbl-1}}
\begin{widetable}
\advance\tabcolsep-1pt
\small
\begin{tabular}{ccrrccccccccc}
\hline
\bf 
POS &\bf  chip &\multicolumn1c{\bf ID} &\multicolumn1c{\bf X}
&\multicolumn1c{\bf Y} &\bf
RA &\bf DEC &\bf IAU$\pm$ $\delta$ IAU &\bf
IAP1$\pm$ $\delta$ IAP1 &\bf IAP2 $\pm$ $\delta$
IAP2 &\bf star &\bf E &\bf Comment\\
\hline
0 & 2 & 1 & 1370.99 & 57.35\rlap{$^a$}    &   6.651120 &  17.131149 &
21.344$\pm$0.006\rlap{$^b$}  & 2 4.385$\pm$0.016 & 23.528$\pm$0.013 & 0.0 & 9 & -    \\
0 & 2 & 2 & 1476.62 & 8.03     &   6.651480 &  17.129572 & 21.641$\pm$0.005  & 2 3.141$\pm$0.007 & 22.007$\pm$0.004 & 0.0 & 9 & -    \\
0 & 2 & 3 & 1079.62 & 28.92    &   6.652430 &  17.135000 & 23.953$\pm$0.030  & 2 4.890$\pm$0.023 & 24.240$\pm$0.023 & 0.0 & - & -    \\
0 & 2 & 4 & 114.58  & 21.22    &   6.655560 &  17.148020 & 23.801$\pm$0.025  & 2 5.039$\pm$0.026 & 24.112$\pm$0.021 & 0.0 & - & -    \\
0 & 2 & 5 & 46.78   & 19.46    &   6.655800 &  17.148932 & 23.012$\pm$0.012  & 2 3.924$\pm$0.012 & 23.282$\pm$0.011 & 0.0 & - & -    \\
0 & 2 & 6 & 1441.84 & 16.16    &   6.651480 &  17.130072 & 24.393$\pm$0.045  & 2 6.099$\pm$0.062 & 25.119$\pm$0.049 & 0.0 & - & -    \\
0 & 2 & 7 & 205.43  & 3.96     &   6.655520 &  17.146742 & 24.424$\pm$0.032  & 2 5.028$\pm$0.025 & 24.597$\pm$0.027 & 0.0 & - & -    \\
0 & 2 & 8 & 1321.63 & 9.76     &   6.651950 &  17.131672 &
22.189$\pm$0.011  & 2 4.743$\pm$0.021 & 23.298$\pm$0.011 & 0.0 & 4 &
edge \\
\hline\\[-6pt]
\multicolumn{13}{l}{%
Table 2 is published in its entirety in the electronic
edition of the {\it Astrophysical Journal}.}\\[3pt]
\multicolumn{13}{l}{%
$^a$ Sample footnote for table 2.}\\[3pt]
\multicolumn{13}{l}{%
$^b$ Another sample footnote for table 2.}
\end{tabular}
\end{widetable}
\end{table}

\begin{table}[p]
\rotatebox{90}{\vbox{\hsize=\textheight
\caption{Here is a caption for a table that is found in landscape
mode.}
\begin{tabular}{ccrrccccccccc}
\hline
\bf 
POS &\bf  chip &\multicolumn1c{\bf ID} &\multicolumn1c{\bf X}
&\multicolumn1c{\bf Y} &\bf
RA &\bf DEC &\bf IAU$\pm$ $\delta$ IAU &\bf
IAP1$\pm$ $\delta$ IAP1 &\bf IAP2 $\pm$ $\delta$
IAP2 &\bf star &\bf E &\bf Comment\\
\hline
0 & 2 & 1 & 1370.99 & 57.35\rlap{$^a$}    &   6.651120 &  17.131149 &
21.344$\pm$0.006\rlap{$^b$}  & 2 4.385$\pm$0.016 & 23.528$\pm$0.013 & 0.0 & 9 & -    \\
0 & 2 & 2 & 1476.62 & 8.03     &   6.651480 &  17.129572 & 21.641$\pm$0.005  & 2 3.141$\pm$0.007 & 22.007$\pm$0.004 & 0.0 & 9 & -    \\
0 & 2 & 3 & 1079.62 & 28.92    &   6.652430 &  17.135000 & 23.953$\pm$0.030  & 2 4.890$\pm$0.023 & 24.240$\pm$0.023 & 0.0 & - & -    \\
0 & 2 & 4 & 114.58  & 21.22    &   6.655560 &  17.148020 & 23.801$\pm$0.025  & 2 5.039$\pm$0.026 & 24.112$\pm$0.021 & 0.0 & - & -    \\
0 & 2 & 5 & 46.78   & 19.46    &   6.655800 &  17.148932 & 23.012$\pm$0.012  & 2 3.924$\pm$0.012 & 23.282$\pm$0.011 & 0.0 & - & -    \\
0 & 2 & 6 & 1441.84 & 16.16    &   6.651480 &  17.130072 & 24.393$\pm$0.045  & 2 6.099$\pm$0.062 & 25.119$\pm$0.049 & 0.0 & - & -    \\
0 & 2 & 7 & 205.43  & 3.96     &   6.655520 &  17.146742 & 24.424$\pm$0.032  & 2 5.028$\pm$0.025 & 24.597$\pm$0.027 & 0.0 & - & -    \\
0 & 2 & 8 & 1321.63 & 9.76     &   6.651950 &  17.131672 &
22.189$\pm$0.011  & 2 4.743$\pm$0.021 & 23.298$\pm$0.011 & 0.0 & 4 &
edge \\
\hline\\[-6pt]
\multicolumn{13}{l}{%
Table 2 is published in its entirety in the electronic
edition of the {\it Astrophysical Journal}.}\\[3pt]
\multicolumn{13}{l}{%
$^a$ Sample footnote for table 2.}\\[3pt]
\multicolumn{13}{l}{%
$^b$ Another sample footnote for table 2.}
\end{tabular}
}}
\end{table}
\clearpage
\begin{boxedtext}{Tools for comparison of networks} 
Going beyond the examination of shared topological features across
nervous systems, the generalized mathematical language of graph theory
also offers tools for the comparison of the organization of brain
networks to other classes of network studied by different scientific
disciplines.

From $\mathcal{W}$, we can estimate the variability in the fluctuations of the functional connection between nodes $i$ and $j$ over time as:
\begin{equation}
s_{ij}=\sqrt{\frac{1}{T-L}\sum_{t=1}^{T-L+1}(W_{ij}(t) - m_{ij})}
\end{equation}
where $m_{ij}=\frac{1}{T-L+1}\sum_{t=1}^{T-L+1}W_{ij}(t)$ is the mean
dynamic functional connectivity over time.

Many real-world systems operate as some sort of
interaction or communication network, including, for example, social
networks, gene regulatory networks, computer networks, and
transportation networks. Similar to brain networks, many of these
real-world networks display an efficient small-world organization, a
pronounced community structure with densely connected modules, as well
as the formation of hubs and rich clubs. Going beyond the
comparison of networks within the class of nervous systems, the field
of `comparative network analysis' examines commonalities and
differences across a range of network classes.
\end{boxedtext}

Example of table continuing over pages:

\begin{center}
\begin{longtable}{ccc@{}}
\caption{ApJ costs from 1991 to 2013
\label{tab:table}} \\[2pt]
\hline
\bf Year & \bf Subscription & \bf Publication \\
 & \bf cost &\bf charges\\
 & \bf(\$) & \bf (\$/page)\\
\hline
\endfirsthead

\multicolumn3c{Table \thetable, \it continued from previous page.}\\[6pt]
\multicolumn3c{ApJ costs from 1991 to 2013}\\[2pt]
\hline
\bf Year & \bf Subscription & \bf Publication \\
 & \bf cost &\bf charges\\
 & \bf(\$) & \bf (\$/page)\\
\hline
\endhead
\\\hline
\\[-8pt]
\multicolumn{3}{r}{\it Table continued on next page}\\ 
\endfoot

\hline
\endlastfoot

1991 & 600 & 100 \\
1992 & 650 & 105 \\
1993 & 550 & 103 \\
1994 & 450 & 110 \\
1995 & 410 & 112 \\
1996 & 400 & 114 \\
1997 & 525 & 115 \\
1998 & 590 & 116 \\
1999 & 575 & 115 \\
2000 & 450 & 103 \\
2001 & 490 &  90 \\
2002 & 500 &  88 \\
2003 & 450 &  90 \\
2004 & 460 &  88 \\
2005 & 440 &  79 \\
2006 & 350 &  77 \\
2007 & 325 &  70 \\
2008 & 320 &  65 \\
2009 & 190 &  68 \\
2010 & 280 &  70 \\
2011 & 275 &  68 \\
2012 & 150 &  56 \\
2013 & 140 &  55 \\
\end{longtable}
\end{center}

\section{Supportive Information}
Here you enter further sources of information, if desired.

%% A possible entry might be:
% No supportive information is available at this time.

\acknowledgments
Enter your acknowledgments here.

%% ie.,

% The authors thank Laurence Aitchison for fruitful discussions.  RKN
% and PD received funding from the Gatsby Charitable Foundation. Y-AB,
% RBS, KC and PS received funding from Canadian Institutes of Health
% Research grant $MOP74577$,
% Fond de recherche Qu\'{e}bec - Sant\'{e} (Group grant to the Groupe 
% de recherche en neurobiologie comportementale, Shimon Amir, P.I.), and
% Concordia University Research Chair (Tier I).

\authorcontributions 
Who helped formulate the project, who supplied data, analyses and
experiments, etc.

%% ie.
%% Project was formulated by RKN, PD, PS,
%% based on substantial data, analyses and experiments of Y-AB, KC, RS,
%% PS. RKN, PD formalised the model, RKN implemented and ran the model;
%% RKN analysed the molecular ethogram data; Y-AB formalised and
%% implemented a CTMC model. All authors wrote the manuscript.

\section{Making Your Bibliography for a Network Neuroscience Article}
{\it Network Neuroscience} uses the APA author-date  bibliography style,
apacite.bst. For more
information on apacite, for examples in how to make your .bib file and more, see:\\
\href{http://mirror.jmu.edu/pub/CTAN/biblio/bibtex/contrib/apacite/apacite.pdf}
{http://mirror.jmu.edu/pub/CTAN/biblio/bibtex/contrib/apacite/apacite.pdf}

\noindent
(In spite of the mention of apacite cite commands, please use only
Natbib commands for in text citations, as shown above.)

\subsection{BibTeX}
You will need to use BibTeX to form your bibliography; typing in the
references would be
a huge and unpleasant task. Look at the NETNSample.bbl file and you'll see why
typing in the bibitems would be difficult.

For a good basic introduction to using BibTeX, see\\
\href{https://www.economics.utoronto.ca/osborne/latex/BIBTEX.HTM}
{https://www.economics.utoronto.ca/osborne/latex/BIBTEX.HTM}

When you use BibTeX, the form of the bibliography will be correct. You
don't need to supply a bibliography style, since that is built into
the stjour.cls file when the NETN option is used
(\verb+\documentclass[NETN]{stjour}+).

\subsection{Sample citations}

Here are some samples using \verb+\citep{}+:\\
\citep{bullmore2009complex,
gomez2009analysis,
rubinov2011weight,
power2014methods,
sporns2015modular,
scheeringa2012eeg,
fortunato2007resolution,
reichardt2006statistical,
smith2009correspondence,
sporns2011networks,
liegeois2014cerebral}

And more using \verb+\citet{}+\\
\citet{allen2012tracking,
calhoun2014chronnectome,
liu2013time,
fisher1915frequency,
gonzalez2014spatial,
damaraju2014dynamic,
hutchison2013resting,
de2012cortical,
tagliazucchi2012dynamic,
nooner2012nki}

\newpage
%%%%%%%%%%%%%%%%%%%%%%%
%% The bibliography

\bibliography{NETNbibsamp}

%% No appendices allowed in Network Neuroscience style
%\appendix

\end{document}

### 2019-05-15 NETNSample.tex
template and tex files for QSS

--- 2019-05-15 ManuscriptSample.tex
@@
 %\documentclass[finalfonts,NETN]{stjour}
-%\documentclass[NETN]{stjour}
+\documentclass[NETN]{stjour}
 
 %% or
-%\documentclass[finalfonts,NETN]{stjour}
 
-%% or 
 %% Manuscript, for double spaced, larger fonts
-\documentclass[manuscript,NETN]{stjour}
+%\documentclass[manuscript]{stjour}
 %% Only needed if you use `manuscript' option
- \journalname{Network Neuroscience}
+% \journalname{Network Neuroscience}
 
@@
 
-\newpage
 \section{Sample equations}
@@
 
+\newpage
 \begin{boxedtext}{Comparative Analysis of Different Classes of Networks} 
@@
 leads to external rewards such as food and money; whereas leisure is
-supposed to be intrinsically beneficial \jargon[2in]{Intrinsically beneficial}{The characteristic of
+supposed to be intrinsically beneficial \jargon{Intrinsically beneficial}{The characteristic of
 leisure that we enjoy most.} (otherwise one would not want to
@@
 
+\newpage
 \subsection{Sample citations}

### 2019-05-15 NETNTemplate.tex
template and tex files for QSS

--- 2019-05-15 NETNSample.tex
@@
+%% NETN Template file
+
 %% Documentclass:
-%% Network Neuroscience
-%\documentclass[finalfonts,NETN]{stjour}
 \documentclass[NETN]{stjour}
 
-%% or
-
+%% Or,
 %% Manuscript, for double spaced, larger fonts
-%\documentclass[manuscript]{stjour}
+% \documentclass[manuscript]{stjour}
 %% Only needed if you use `manuscript' option
@@
 
+%% Or,
+%% For production only, need .otf fonts, and
+%% need to use lualatex:
+%% \documentclass[finalfonts,NETN]{stjour}
+
 %%%%%%%%%%% Article Set-Up %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %% Article Type:
-%% Default is Research.
 
-%% Or, choose one of these options:
-%% Research, Methods, Data, Review, and Perspective
+%% Choose one of these options, (Default is Research).
+%% Research
+%% Methods 
+%% Data
+%% Review
+%% Perspectives
 
-\articletype{Perspective}
+\articletype{Research}
 
@@
 
-\supportinginfo{dx.doi.org/10.7910/DVN/PQ6ILM}
+%% For Computational Psychiatry, Supporting Info
+\supportinginfo{http://dx.doi.org/10.7910/DVN/PQ6ILM}
 
-%% if no conflicts, this command doesn't need to be used
+%% If no conflicts, this command doesn't need to be used
 %% \conflictsofinterest{}
@@
 %%%%%%%%%%% to be supplied by MIT Press, only %%%%%%%%%%%%%%%%%
-\citation{Betzel, R. F., Fukushima, M.,
-He, Ye,
-Zuo, Xi-Nian,
-Sporns, O. (2016)\\
-Dynamic fluctuations coincide with periods of high and low modularity
-in resting-state functional brain  networks\\
-Network Neuroscience, 1
-}
 
-\received{20 October 2016}
-\accepted{7 November 2016}
-\published{26 January 2016}
-\setdoi{10.1162/NETN-00001} %% ???
+\citation{Niyogi, R. K., Breton, Y.-A., Solomon,
+R. B., Conover, K.,\\ Shizgal, P., Dayan, P. (2015).\\ 
+Optimal indolence: a normative microscopic approach to work and
+leisure. Network Neuroscience 1(1):
+1−12.}
 
-\handlingeditor{Xi-Nian Zuo}
+\received{20 October 2013}
+\accepted{7 November 2013}
+\published{26 January 2014}
+\handlingeditor{Editor Name}
+
+%% DOI address:
+\setdoi{10.1098/rsif.2013.0969}
 
@@
 \def\taupav{\tau_{\mathrm{Pav}}}
+\begin{document}
 
-\begin{document}
-\title[Shortened Version of Title]{Title of Article}
-\subtitle{Subtitle Here}
+\title{<Title of Article>}
+\subtitle{<Subtitle Here>} %% Optional subtitle
 
@@
 
+%%% Author/Affil
 %% Since we use \affil{} in the argument of the \author command, we
@@
 
-\author[Author Names]
-{Author Names with affiliations\affil{1},
+\author[Author Names]% shortened version for running head, optional
+{Author Names with affiliations\thanks{<for footnote for further info>}\affil{1},
 Another Name\affil{2}, Still another Name\affil{2},\\
@@
 
-\keywords{(a series of uncapitalized words, separated with commas)}
+\keywords{<a series of uncapitalized words, separated with commas>}
 
@@
 \begin{authorsummary}
-Author summary here. 
+Author Summary Here, required for Computational Psychiatry
 \end{authorsummary}
+
+<body of article>
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%% End of Article
+%%% Each of these elements should be used, with the exception of 
+%%% Appendix which is optional.
+
+%%% \section{Supportive Information}
+% \acknowledgments
+% \authorcontributions 
+% \bibliography{<name of .bib file>}
+%  (\appendix  not allowed!!)
+
+\section{Supportive Information}
+Here you enter further sources of information, if desired.
+
+%% A possible entry might be:
+% No supportive information is available at this time.
+
+\acknowledgments
+Enter your acknowledgments here.
+
+%% ie.,
+
+% The authors thank Laurence Aitchison for fruitful discussions.  RKN
+% and PD received funding from the Gatsby Charitable Foundation. Y-AB,
+% RBS, KC and PS received funding from Canadian Institutes of Health
+% Research grant $MOP74577$,
+% Fond de recherche Qu\'{e}bec - Sant\'{e} (Group grant to the Groupe 
+% de recherche en neurobiologie comportementale, Shimon Amir, P.I.), and
+% Concordia University Research Chair (Tier I).
+
+\authorcontributions 
+Who helped formulate the project, who supplied data, analyses and
+experiments, etc.
+
+%% ie.
+%% Project was formulated by RKN, PD, PS,
+%% based on substantial data, analyses and experiments of Y-AB, KC, RS,
+%% PS. RKN, PD formalised the model, RKN implemented and ran the model;
+%% RKN analysed the molecular ethogram data; Y-AB formalised and
+%% implemented a CTMC model. All authors wrote the manuscript.
+
+%%%%%%%%%%%%%%%%%%%%%%%
+%% The bibliography
+
+%% The bibliography is made using only the entries that you cite using 
+%% \cite{}, or one of the Natbib citation entries, like \citep{}, \citet{} etc.
+
+\bibliography{<your .bib file>}
+
+%ie.,
+%\bibliography{bibsamp}
+
+\end{document}
+
+The examples below may be helpful when you are looking
+for a quick example. They are taken from NETNsample.tex
+so you can see their results in NETNSample.pdf
+
+\begin{boxedtext}{box title}
+Text
+\end{boxedtext}
+
+or, put figure in boxed text:
+\begin{boxedtext}{box title}
+Text
+\begin{figure}
+illustration
+\caption{caption here}
+\end{figure}
+\end{boxedtext}
+
+or, put table in boxed text:
+\begin{boxedtext}{box title}
+Text
+\begin{table
+\caption{caption here}
+tabular...
+\end{table}
+\end{boxedtext}
+
+or, put anything in whitebox within boxed text:
+\begin{boxedtext}{Showing the use of whitebox} 
+Going beyond the examination of shared topological features across..
+
+\whitebox{
+From $\mathcal{W}$, we can estimate the variability in the fluctuations of the functional connection between nodes $i$ and $j$ over time as:
+\begin{equation}
+s_{ij}=\sqrt{\frac{1}{T-L}\sum_{t=1}^{T-L+1}(W_{ij}(t) - m_{ij})}
+\end{equation}
+where $m_{ij}=\frac{1}{T-L+1}\sum_{t=1}^{T-L+1}W_{ij}(t)$ is the mean
+dynamic functional connectivity over time. 
+}
+...differences across a range of network classes.
+\end{boxedtext}
+
+%% NO Appendices in the Network Neuroscience style
+
+==================
+More samples:
 
@@
 \end{equation}
-Text finishing first page.
-Text finishing first page.
-Text finishing first page.
-Text finishing first page.
-Text finishing first page.
-Text finishing first page.
-Text finishing first page.
-
-\begin{boxedtext}{Comparative Analysis of Different Classes of Networks} 
-Going beyond the examination of shared topological features across
-nervous systems, the generalized mathematical language of graph theory
-also offers tools for the comparison of the organization of brain
-networks to other classes of network studied
-by different scientific
-disciplines.
-
-Many real-world systems operate as some sort of
-interaction or communication network, including, for example, social
-networks, gene regulatory networks, computer networks, and
-transportation networks. Similar to brain networks, many of these
-real-world networks display an efficient small-world organization, a
-pronounced community structure with densely connected modules, as well
-as the formation of hubs and rich clubs. Going beyond the
-comparison of networks within the class of nervous systems, the field
-of `comparative network analysis' examines commonalities and
-differences across a range of network classes.
-
-\begin{figure}
-\includegraphics[width=\hsize]{Fig1}
-\caption{Here is the caption.}
-\end{figure}
-\end{boxedtext}
-
-\newpage
-\begin{boxedtext}{Comparative Analysis of Different Classes of Networks} 
-Going beyond the examination of shared topological features across
-nervous systems, the generalized mathematical language of graph theory
-also offers tools for the comparison of the organization of brain
-networks to other classes of network studied by different scientific
-disciplines. Many real-world systems operate as some sort of
-interaction or communication network, including, for example, social
-networks, gene regulatory networks, computer networks, and
-transportation networks. Similar to brain networks, many of these
-real-world networks display an efficient small-world organization, a
-pronounced community structure with densely connected modules, as well
-as the formation of hubs and rich clubs. Going beyond the
-comparison of networks within the class of nervous systems, the field
-of `comparative network analysis' examines commonalities and
-differences across a range of network classes.
-
-\begin{table}[ht]
-\caption{Here is the caption.}
-
-\centerline{\begin{tabular}{|c|c|c|}
-\hline
-one&two&three\\
-\hline
-four&five&six\\
-\hline
-\end{tabular}}
-\end{table}
-\end{boxedtext}
-
-\subsection{Jargon Samples in margin}
-One common decision is between working (performing an employer-defined
-task) and engaging in leisure (activities pursued for oneself). Working
-leads to external rewards such as food and money; whereas leisure is
-supposed to be intrinsically beneficial \jargon{Intrinsically beneficial}{The characteristic of
-leisure that we enjoy most.} (otherwise one would not want to
-engage in it).
-%% \jargon has optional argument in square brackets where you can specify
-%% the amount of extra space below where it would normally appear when 
-%% two \jargon entries are in the same paragraph:
-$\beta \in [0,\infty)$\jargon[24pt]{$\beta \in [0,\infty)$}{inverse temperature or degree of
-stochasticity-determinism parameter.} is often used to indicate an
-important parameter, the stochasticity-determinism parameter.
 
@@
 \subsection{Algorithm environment}
+
 %% \begin{algorithm} takes option [p][b][t][h],  or some combination, like \begin{figure}
@@
 
+\section{Jargon Samples in margin}
+One common decision is between working (performing an employer-defined
+task) and engaging in leisure (activities pursued for oneself). Working
+leads to external rewards such as food and money; whereas leisure is
+supposed to be intrinsically beneficial \jargon{Intrinsically beneficial}{The characteristic of
+leisure that we enjoy most.} (otherwise one would not want to
+engage in it).
+%% \jargon has optional argument in square brackets where you can specify
+%% the amount of extra space below where it would normally appear when 
+%% two \jargon entries are in the same paragraph:
+$\beta \in [0,\infty)$\jargon[24pt]{$\beta \in [0,\infty)$}{inverse temperature or degree of
+stochasticity-determinism parameter.} is often used to indicate an
+important parameter, the stochasticity-determinism parameter.
+
 \section{Itemized Lists}
@@
 \item[(i)] at high 
-payoffs, subjects work almost continuously.
+payoffs, subjects work almost continuously, engaging in little leisure
+in between work bouts; 
 \item[(ii)] at low payoffs, they 
-engage in leisure all at once, in long bouts after working.
+engage in leisure all at once, in long bouts after working, rather
+than distributing the same amount of leisure time into multiple short
+leisure bouts; 
 \item[(iii)] subjects work continuously for the entire price duration, as long as
-the price is not very long;
+the price is not very long (as shown by an analysis conducted by Y-AB, to be published separately); %(\textbf{Figure \ref{fig:task_data}D}).
 \item[(iv)] the duration of leisure bouts is variable.
@@
 \item subjects work continuously for the entire price duration, as long as
-the price is not very long (as shown by an analysis conducted by
-Y-AB, to be published separately);  
+the price is not very long (as shown by an analysis conducted by Y-AB, to be published separately); %(\textbf{Figure \ref{fig:task_data}D}).
 \item the duration of leisure bouts is variable.
@@
 \item subjects work continuously for the entire price duration, as long as
-the price is not very long (as shown by an analysis conducted by
-Y-AB, to be published separately);  
+the price is not very long (as shown by an analysis conducted by Y-AB, to be published separately); %(\textbf{Figure \ref{fig:task_data}D}).
 \item the duration of leisure bouts is variable.
 \end{itemize}
-
-\subsection{Description list:}
-\begin{description}
-\item[High payoffs:] at high 
-payoffs, subjects work almost continuously, engaging in little leisure
-inbetween work bouts; 
-\item[Low payoffs:] at low payoffs, they 
-engage in leisure all at once, in long bouts after working, rather
-than distributing the same amount of leisure time into multiple short
-leisure bouts; 
-\item[Continuous work:] subjects work continuously for the entire price duration, as long as
-the price is not very long (as shown by an analysis conducted by Y-AB, to be published separately); 
-\item[Duration:] the duration of leisure bouts is variable.
-\end{description}
-
-\newpage
-\section{Sample citations}
-For general information on the correct form for citations using
-the APA 6 format, see the following sites:
-\href{https://owl.english.purdue.edu/owl/resource/560/02/}
-{APA 6, In-text citations, The Basics} and
-\href{https://owl.english.purdue.edu/owl/resource/560/03/}
-{APA 6, In-text citations}
 
@@
 \hline
-\verb+\citet{jon90}+&\dogray Jones et al. (1990)\\
-\verb+\citet[chap. 2]{jon90}+&\dogray Jones et al. (1990, chap. 2)\\
-    \verb+\citep{jon90}+	    &\dogray   	(Jones et al., 1990)\\
-    \verb+\citep[chap. 2]{jon90}+ 	&\dogray    	(Jones et al., 1990, chap. 2)\\
-    \verb+\citep[see][]{jon90}+ 	 &\dogray    	(see Jones et al., 1990)\\
-    \verb+\citep[see][chap. 2]{jon90}+ 	&\dogray    	(see Jones et al., 1990, chap. 2)\\
-    \verb+\citet*{jon90}+ 	    &\dogray    	Jones, Baker, and Williams (1990)\\
-    \verb+\citep*{jon90}+	    & \dogray   	(Jones, Baker, and Williams,
+\verb+\citet{jon90}+&Jones et al. (1990)\\
+\verb+\citet[chap. 2]{jon90}+&Jones et al. (1990, chap. 2)\\
+    \verb+\citep{jon90}+	    &   	(Jones et al., 1990)\\
+    \verb+\citep[chap. 2]{jon90}+ 	&    	(Jones et al., 1990, chap. 2)\\
+    \verb+\citep[see][]{jon90}+ 	 &    	(see Jones et al., 1990)\\
+    \verb+\citep[see][chap. 2]{jon90}+ 	&    	(see Jones et al., 1990, chap. 2)\\
+    \verb+\citet*{jon90}+ 	    &    	Jones, Baker, and Williams (1990)\\
+    \verb+\citep*{jon90}+	    &    	(Jones, Baker, and Williams,
     1990) \\
@@
 
-For example, some citations from the NETNbibsamp.bib database:
-
-citet: \citet{bullmore2009complex}, citep: \citep{gomez2009analysis}, and
-citep*: \citep*{de2012cortical}
+For example, some citations from the CompPsychSample bibliography:
+citet:\citet{anderson}, citep:\citep{antibayes}, and
+cite*: \citet*{anderson}.
 
@@
 \hline
-\verb+\citet{jon90,jam91}+&\dogray Jones et al. (1990); James et al. (1991)\\
-\verb+\citep{jon90,jam91}+&\dogray (Jones et al., 1990; James et al. 1991)\\
-\verb+\citep{jon90,jon91}+&\dogray (Jones et al., 1990, 1991)\\
-\verb+\citep{jon90a,jon90b}+&\dogray (Jones et al., 1990a,b)\\
+\verb+\citet{jon90,jam91}+&Jones et al. (1990); James et al. (1991)\\
+\verb+\citep{jon90,jam91}+&(Jones et al., 1990; James et al. 1991)\\
+\verb+\citep{jon90,jon91}+&(Jones et al., 1990, 1991)\\
+\verb+\citep{jon90a,jon90b}+&(Jones et al., 1990a,b)\\
 \end{tabular}
 
-For example, multiple citations from the bibsamp.bib database:
-citet: \citet{nooner2012nki,hutchison2013resting},
- citep:
-\citep{tagliazucchi2012dynamic, de2012cortical}
-
+For example, multiple citations from the CompPsychSample bibliography:
+citet:\citet{anderson,antibayes}, citep:\citep{anderson,antibayes}.
 As you see, the citations are automatically hyperlinked to their
@@
 \begin{figure}[h] 
-\centerline{\includegraphics[width=\textwidth]{Fig1.pdf}}
+\centerline{\includegraphics[width=\textwidth]{Fig1}}
 \caption{(Colour online) \textbf{Task and key features of the
@@
 $2$s each time the price is attained, during which the lever is retracted so it cannot
-work; not shown).}
+work; not shown).
+}
 \label{fig:task_data}
 \end{figure}
-%% this command ends a page but does not fill the bottom with white space:
-\eject
 
 \begin{figure}[ht] 
-\widefigure{\fullpagewidth}{Fig1.pdf}
+\widefigure{\fullpagewidth}{Fig1}
 \caption{(Colour online) \textbf{Task and key features of the
@@
 $2$s each time the price is attained, during which the lever is retracted so it cannot
-work; not shown).}
-\label{fig:task_data2}
+work; not shown).
+}
+\label{newfig:task_data}
 \end{figure}
 
-\newpage
+\clearpage
 \section{Sample tables}
@@
 edge \\
-\hline\\[-6pt]
+\hline
 \multicolumn{13}{l}{%
@@
 \clearpage
-\begin{boxedtext}{Tools for comparison of networks} 
-Going beyond the examination of shared topological features across
-nervous systems, the generalized mathematical language of graph theory
-also offers tools for the comparison of the organization of brain
-networks to other classes of network studied by different scientific
-disciplines.
 
-From $\mathcal{W}$, we can estimate the variability in the fluctuations of the functional connection between nodes $i$ and $j$ over time as:
-\begin{equation}
-s_{ij}=\sqrt{\frac{1}{T-L}\sum_{t=1}^{T-L+1}(W_{ij}(t) - m_{ij})}
-\end{equation}
-where $m_{ij}=\frac{1}{T-L+1}\sum_{t=1}^{T-L+1}W_{ij}(t)$ is the mean
-dynamic functional connectivity over time.
-
-Many real-world systems operate as some sort of
-interaction or communication network, including, for example, social
-networks, gene regulatory networks, computer networks, and
-transportation networks. Similar to brain networks, many of these
-real-world networks display an efficient small-world organization, a
-pronounced community structure with densely connected modules, as well
-as the formation of hubs and rich clubs. Going beyond the
-comparison of networks within the class of nervous systems, the field
-of `comparative network analysis' examines commonalities and
-differences across a range of network classes.
-\end{boxedtext}
-
+\vglue 3in
 Example of table continuing over pages:
@@
 
-\section{Making Your Bibliography for a Network Neuroscience Article}
-{\it Network Neuroscience} uses the APA author-date  bibliography style,
-apacite.bst. For more
-information on apacite, for examples in how to make your .bib file and more, see:\\
-\href{http://mirror.jmu.edu/pub/CTAN/biblio/bibtex/contrib/apacite/apacite.pdf}
-{http://mirror.jmu.edu/pub/CTAN/biblio/bibtex/contrib/apacite/apacite.pdf}
-
-\noindent
-(In spite of the mention of apacite cite commands, please use only
-Natbib commands for in text citations, as shown above.)
-
-\subsection{BibTeX}
-You will need to use BibTeX to form your bibliography; typing in the
-references would be
-a huge and unpleasant task. Look at the NETNSample.bbl file and you'll see why
-typing in the bibitems would be difficult.
-
-For a good basic introduction to using BibTeX, see\\
-\href{https://www.economics.utoronto.ca/osborne/latex/BIBTEX.HTM}
-{https://www.economics.utoronto.ca/osborne/latex/BIBTEX.HTM}
-
-When you use BibTeX, the form of the bibliography will be correct. You
-don't need to supply a bibliography style, since that is built into
-the stjour.cls file when the NETN option is used
-(\verb+\documentclass[NETN]{stjour}+).
-
-\newpage
-\subsection{Sample citations}
-
-Here are some samples using \verb+\citep{}+:\\
-\citep{bullmore2009complex,
-gomez2009analysis,
-rubinov2011weight,
-power2014methods,
-sporns2015modular,
-scheeringa2012eeg,
-fortunato2007resolution,
-reichardt2006statistical,
-smith2009correspondence,
-sporns2011networks,
-liegeois2014cerebral}
-
-And more using \verb+\citet{}+\\
-\citet{allen2012tracking,
-calhoun2014chronnectome,
-liu2013time,
-fisher1915frequency,
-gonzalez2014spatial,
-damaraju2014dynamic,
-hutchison2013resting,
-de2012cortical,
-tagliazucchi2012dynamic,
-nooner2012nki}
-
-\newpage
 %%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\bibliography{NETNbibsamp}
+%% The bibliography is made using only
+%% the entries that you cite using \cite{}, or one of the Natbib citation
+%% entries, like \citep{}, \citet{} etc.
 
-%% No appendices allowed in Network Neuroscience style
-%\appendix
+\bibliography{bibsamp}
 
-\end{document}
+NO APPENDICES allowed in the Network Neuroscience Style

### 2019-05-15 cocit_r.tex
template and tex files for QSS

--- 2019-05-15 NETNSample.tex
@@
 
-\articletype{Perspective}
+\articletype{Research Article}
 
@@
 \begin{document}
-\title[Shortened Version of Title]{Title of Article}
-\subtitle{Subtitle Here}
+\title[Co-citations in context]{Co-citations in context}
+\subtitle{Disciplinary heterogeneity is relevant}
 
@@
 \author[Author Names]
-{Author Names with affiliations\affil{1},
-Another Name\affil{2}, Still another Name\affil{2},\\
-\and Final Name\affil{1}}
+{James Bradley\affil{1},
+Sitaram Devarakonda\affil{2}, Avon Davey\affil{2}, Dmitriy Korobskiy\affil{2}, Siyu Liu\affil{2}, Tandy Warnow\affil{3}
+\and George Chacko\affil{2}}
 
-\affiliation{1}{Department, Institution, City, Country}
+\affiliation{1}{Raymond A. Mason School of Business, College of William and Mary, Williamsburg, VA, USA}
+\affiliation{2}{Netelabs, NET ESolutions Corporation, McLean, VA 22102, USA}
+\affiliation{3}{Department of Computer Science, University of Illinois Urbana-Champaign, Champaign, IL 61820, USA}
 
@@
 
-\affiliation{2}{Another Department, Institution, City, Country}
+%\affiliation{2}{Another Department, Institution, City, Country}
 
@@
 
-\correspondingauthor{Author Name}{Corresponding author email address}
+\correspondingauthor{George Chacko}{netelabs@nete.com}
 
@@
 
-\keywords{(a series of uncapitalized words, separated with commas)}
+\keywords{(bibliometrics, co-citation analysis, random graphs )}
 
@@
 \begin{abstract}
-Abstract text here.
+Citation analysis of the scientific literature has been used to study and define disciplinary boundaries, to trace the dissemination of knowledge, and to estimate impact.
+Co-citation, the frequency with which pairs of publications are cited, provides insight into how documents relate to each other and across fields.
+Co-citation analysis has been used to characterize combinations of prior work as conventional or innovative and to derive features of highly cited publications.
+Given the organization of science into disciplines, a key question is the sensitivity of such analyses to frame of reference.
+Our study examines this question using  semantically-themed citation networks.
+We observe that trends reported to be true across the scientific literature do not hold for focused citation networks, and conclude that co-citation analysis requires a contextual perspective.
 \end{abstract}
 
-\begin{authorsummary}
-Author summary here. 
-\end{authorsummary}
+% \begin{authorsummary} 
+% \end{authorsummary}
 
-\section{Sample Section}
-Text here. Text here. Text here. Text here.
-Text here. Text here. Text here. Text here.
-Text here. Text here. Text here. Text here.
-Text here. Text here. Text here. Text here.
+\section{Introduction}
+Citation and network analysis of  scientific literature reveals information on semantic relationships between publications, collaboration between scientists, and the practice of citation itself~\cite{de_solla_price_networks_1965,newman_structure_2001}.
+Co-citation, the frequency with which two documents are cited together in other documents~\cite{small_co-citation_1973,marshakova-shaikevich_co-citation_1973}, provides additional insights, including the identification of semantically related documents and fields.
+Uzzi et al.
+applied co-citation analysis to 17.9 million publications from the Web of Science (WoS) to identify novel combinations of prior research and to characterize highly cited papers.
+They analyzed co-citations of references (and journals) within publications, and computed a `z-score' for each journal pair using Monte Carlo simulations based on a random graph model.
+The set of journal-pair z-scores for each publication was  used to assess  conventionality and novelty, resulting in four categories: high or low conventionality (HC or LC) and high or low novelty (HN or LN), and all four combinations are possible.
+The authors concluded that highly cited publications across the research literature (and within most subfields) are more likely to be characterized as HC and HN than less highly cited publications.
+Key to Uzzi is their random graph model, where  a reference cited in a publication is randomly replaced by another article from the same year as the cited reference, thus producing a random assignment of references to each paper.
+The model treats potential substitutions as equi-probable, irrespective of disciplinary origin.
+Accordingly, we hypothesize that analyzing semantically related sets of documents (and limiting substitutions to the citations in the local network) will reduce model misspecification and better simulate citation practice, leading to different and more relevant conclusions.
+We developed a highly efficient algorithm to simulate under a refined random graph model.
+Our study on three semantically-themed citation networks reveals significantly different patterns of conventionality and novelty between  citation networks and disciplines.
 
@@
 
-\bibliography{NETNbibsamp}
+\bibliography{cocit_r}
 

### 2019-05-16 cocit_r.tex
revision of Intro_gc

@@
 \section{Introduction}
-Citation and network analysis of  scientific literature reveals information on semantic relationships between publications, collaboration between scientists, and the practice of citation itself~\cite{de_solla_price_networks_1965,newman_structure_2001}.
-Co-citation, the frequency with which two documents are cited together in other documents~\cite{small_co-citation_1973,marshakova-shaikevich_co-citation_1973}, provides additional insights, including the identification of semantically related documents and fields.
-Uzzi et al.
-applied co-citation analysis to 17.9 million publications from the Web of Science (WoS) to identify novel combinations of prior research and to characterize highly cited papers.
-They analyzed co-citations of references (and journals) within publications, and computed a `z-score' for each journal pair using Monte Carlo simulations based on a random graph model.
-The set of journal-pair z-scores for each publication was  used to assess  conventionality and novelty, resulting in four categories: high or low conventionality (HC or LC) and high or low novelty (HN or LN), and all four combinations are possible.
-The authors concluded that highly cited publications across the research literature (and within most subfields) are more likely to be characterized as HC and HN than less highly cited publications.
-Key to Uzzi is their random graph model, where  a reference cited in a publication is randomly replaced by another article from the same year as the cited reference, thus producing a random assignment of references to each paper.
-The model treats potential substitutions as equi-probable, irrespective of disciplinary origin.
-Accordingly, we hypothesize that analyzing semantically related sets of documents (and limiting substitutions to the citations in the local network) will reduce model misspecification and better simulate citation practice, leading to different and more relevant conclusions.
-We developed a highly efficient algorithm to simulate under a refined random graph model.
-Our study on three semantically-themed citation networks reveals significantly different patterns of conventionality and novelty between  citation networks and disciplines.
+Citation and network analysis of  scientific literature reveals information on semantic relationships between publications, collaboration between scientists, and the practice of citation itself~\citep{de_solla_price_networks_1965,newman_structure_2001,Shi:2010:CHI:1816123.1816131,patience_pmid28560354}.
+Co-citation, the frequency with which two documents are cited together in other documents~\citep{small_co-citation_1973,marshakova-shaikevich_co-citation_1973}, provides additional insights, including the identification of semantically related documents and fields.
+Co-citations, bibliographic coupling and direct citation have been compared for XX.
+
+In an intriguing study, co-citation analysis of 17.9 million articles and their cited references from the Web of Science (WoS) was used to document novel combinations of prior research and to characterize highly cited papers~\citep{uzzi_atypical_2013}.
+In this study, $nC2$ combinations of the references in each article were generated and then the reference identifiers were replaced with journal identifiers to generate a journal-pair.
+Observed frequencies of journal pairs across the dataset were then normalized to expected values generated by a random graph model using a \emph{z-score} (Materials and Methods).
+Thus, every article was associated with multiple z-scores.
+For each article, positional statistics of these z-scores were calculated to describe conventionality (high conventionality (HC) if the median z-score for an article was greater than the median z-score of all articles and low conventionality for the inverse (LC).) Similarly with novelty (high novelty (HN) if the tenth percentile of z-scores for an article was less than zero and low novelty (LN) for the inverse).
+Accordingly, each article was labeled with respect to conventionality and novelty, e.g, HCLN, with all four combinations being possible.
+The finding of interest was that HCHN articles were twice as likely to be found in highly cited papers (defined as the top 10\% of all papers published in a given year considering the count of citations accumulated in the first 8 years since publication).
+
+Key to the study is the random graph approach, where every reference is randomly replaced by another article published in the same year as the cited reference to generate a null model for comparison.
+However, the approach inadequately accounts for observed citation behavior~\citep{wallace_lariviere_gingras_2012,moed_measuring_2010,klavans_research_2017} since (i) it treats potential substitutions as equi-probable, irrespective of disciplinary origin (ii) does not consider the frequency with which references are cited in the dataset.
+In illustration, a reference from musicology can replace one in quantum physics during the simulation process.
+Similarly, a reference cited over 100 times in a given year is selected with the same probability as a reference cited only once.
+Accordingly, the expected value calculations used in normalizing observed journal-pair-frequencies can be reasonably questioned on grounds of model mis-specification.
+
+A follow-up study using a smaller dataset of 12 million articles, also suggests that Uzzi and colleagues do not fully account for disciplinary and journal effects~\citep{boyack_vs_uzzi_2014}.
+While the two studies are conceptually similar, the authors of the latter study used Scopus data and the K50 measurement, a derivative of the $\chi^2$ method, for normalizing observed to expected journal-pair frequencies.
+Boyack and Klavans note that 'only 64.4\%  of  243  WoS  subject  categories` in the Uzzi study met the criterion of having the highest probability of hit papers in the HCHN category.
+Further they observed that journals vary widely in terms of size and influence and that 20 journals accounted for nearly 15\% of co-citations in their measurements.
+Lastly, that three multidisciplinary journals accounted for 9.4\% of all atypical combinations.
+suggesting strong effects from both disciplines and journals.
+
+Despite different methods used to generate expected values, both Uzzi and Boyack measured observed and expected journal-pair frequencies across disciplines and then examined subsets of publications for disciplinary effects.
+Since disciplinary origin was not considered when generating expected values in their studies, we hypothesized that analyzing semantically related sets of documents instead of all publications in a literature database would create disciplinary networks.
+From these, expected values could be calculated, with the effect of reducing model misspecification and better simulating citation practice, in turn leading to different and more relevant conclusions.
+We also developed an efficient algorithm that enabled us to conduct a greater number of simulations in a reasonable time.
+Thus, while Uzzi et al.
+averaged the results of 10 simulations for each year in their dataset, we performed 1,000 simulations to ensure greater coverage of observed journal pairs.
+Our study on three semantically-themed citation networks reveals significantly different patterns of conventionality and novelty between  citation networks and disciplines that challenges the conclusion that HCHN articles have a greater probability of being represented in highly cited publications.
 

### 2019-05-16 cocit_r.tex
trimmed off extraneous LaTeX

@@
 \section{Introduction}
-Citation and network analysis of  scientific literature reveals information on semantic relationships between publications, collaboration between scientists, and the practice of citation itself~\citep{de_solla_price_networks_1965,newman_structure_2001,Shi:2010:CHI:1816123.1816131,patience_pmid28560354}.
+Citation and network analysis of  scientific literature reveals information on semantic relationships between publications, collaboration between scientists, and the practice of citation itself~\citep{garfield_citation_1955,de_solla_price_networks_1965,newman_structure_2001,Shi:2010:CHI:1816123.1816131,patience_pmid28560354}.
 Co-citation, the frequency with which two documents are cited together in other documents~\citep{small_co-citation_1973,marshakova-shaikevich_co-citation_1973}, provides additional insights, including the identification of semantically related documents and fields.
@@
 In an intriguing study, co-citation analysis of 17.9 million articles and their cited references from the Web of Science (WoS) was used to document novel combinations of prior research and to characterize highly cited papers~\citep{uzzi_atypical_2013}.
-In this study, $nC2$ combinations of the references in each article were generated and then the reference identifiers were replaced with journal identifiers to generate a journal-pair.
-Observed frequencies of journal pairs across the dataset were then normalized to expected values generated by a random graph model using a \emph{z-score} (Materials and Methods).
+In this study, pairwise combinations of the references in each article were generated to create a multi-set of journal-pairs.
+Observed frequencies of these journal pairs across the dataset were computed and normalized to expected values generated by Monte Carlo simulations from a random graph model.
+Normalized, journal pair frequencies were termed \emph{z-scores} (Materials and Methods).
 Thus, every article was associated with multiple z-scores.
-For each article, positional statistics of these z-scores were calculated to describe conventionality (high conventionality (HC) if the median z-score for an article was greater than the median z-score of all articles and low conventionality for the inverse (LC).) Similarly with novelty (high novelty (HN) if the tenth percentile of z-scores for an article was less than zero and low novelty (LN) for the inverse).
+For each article, positional statistics of these z-scores were calculated to describe conventionality (high conventionality (HC) if the median z-score for an article was greater than the median of median z-scores of all articles and low conventionality for the inverse (LC).) Similarly with novelty (high novelty (HN)- if the tenth percentile of z-scores for an article was less than zero and low novelty (LN) for the inverse).
 Accordingly, each article was labeled with respect to conventionality and novelty, e.g, HCLN, with all four combinations being possible.
-The finding of interest was that HCHN articles were twice as likely to be found in highly cited papers (defined as the top 10\% of all papers published in a given year considering the count of citations accumulated in the first 8 years since publication).
+The finding of considerable interest was that HCHN articles were twice as likely to be found in highly cited papers (defined as the top 10\% of all papers published in a given year considering the count of citations accumulated in the first 8 years since publication).
 
-Key to the study is the random graph approach, where every reference is randomly replaced by another article published in the same year as the cited reference to generate a null model for comparison.
+Key to the Uzzi study, however, is the random graph approach, where every reference is randomly replaced by another article published in the same year as the reference to generate a null model for comparison.
 However, the approach inadequately accounts for observed citation behavior~\citep{wallace_lariviere_gingras_2012,moed_measuring_2010,klavans_research_2017} since (i) it treats potential substitutions as equi-probable, irrespective of disciplinary origin (ii) does not consider the frequency with which references are cited in the dataset.
@@
 A follow-up study using a smaller dataset of 12 million articles, also suggests that Uzzi and colleagues do not fully account for disciplinary and journal effects~\citep{boyack_vs_uzzi_2014}.
-While the two studies are conceptually similar, the authors of the latter study used Scopus data and the K50 measurement, a derivative of the $\chi^2$ method, for normalizing observed to expected journal-pair frequencies.
-Boyack and Klavans note that 'only 64.4\%  of  243  WoS  subject  categories` in the Uzzi study met the criterion of having the highest probability of hit papers in the HCHN category.
-Further they observed that journals vary widely in terms of size and influence and that 20 journals accounted for nearly 15\% of co-citations in their measurements.
-Lastly, that three multidisciplinary journals accounted for 9.4\% of all atypical combinations.
-suggesting strong effects from both disciplines and journals.
+While the two studies are conceptually similar, the authors of the latter study used Scopus data and the K50 measurement, a derivative of the $\chi^2$ method, rather than Monte Carlo simulations for normalizing observed to expected journal-pair frequencies.
+Boyack and Klavans note that `only 64.4\%  of  243  WoS  subject  categories' in the Uzzi study met the criterion of having the highest probability of hit papers in the HCHN category.
+Further, they observed that journals vary widely in terms of size and influence and that 20 journals accounted for nearly 15\% of co-citations in their measurements.
+Lastly, that three multidisciplinary journals accounted for 9.4\% of all atypical combinations, suggesting strong effects from both disciplines and journals.
 
 Despite different methods used to generate expected values, both Uzzi and Boyack measured observed and expected journal-pair frequencies across disciplines and then examined subsets of publications for disciplinary effects.
-Since disciplinary origin was not considered when generating expected values in their studies, we hypothesized that analyzing semantically related sets of documents instead of all publications in a literature database would create disciplinary networks.
-From these, expected values could be calculated, with the effect of reducing model misspecification and better simulating citation practice, in turn leading to different and more relevant conclusions.
-We also developed an efficient algorithm that enabled us to conduct a greater number of simulations in a reasonable time.
+Since disciplinary origin was not considered when generating expected values in their studies, we chose instead to analyze semantically related sets of documents (disciplinary networks) instead of all publications in a bibliographic database.
+We used keyword searches of the scientific literature to create three citation networks themed around broad search terms.
+For each of these, we calculated expected values using a refined random graph model that accounted for existing citation frequencies in these networks and an efficient simulation algorithm that randomly permuted references grouped by year of publication.
 Thus, while Uzzi et al.
-averaged the results of 10 simulations for each year in their dataset, we performed 1,000 simulations to ensure greater coverage of observed journal pairs.
-Our study on three semantically-themed citation networks reveals significantly different patterns of conventionality and novelty between  citation networks and disciplines that challenges the conclusion that HCHN articles have a greater probability of being represented in highly cited publications.
+averaged the results of 10 simulations for each year in their dataset, we averaged 1,000 simulations to ensure greater coverage of rarely observed journal pairs We hypothesized that our approach would  reduce model misspecification and better simulate citation practice, in turn leading to different and more relevant conclusions.
+Our study on these semantically-themed citation networks reveals significantly different patterns of conventionality and novelty between  citation networks and disciplines that challenges the conclusion of universality in HCHN articles have a greater probability of being represented in highly cited publications.
+
+\section{Materials and Methods}
+\section{Results}
+\section{Discussion}
 
@@
 \end{description}
-
-\newpage
-\section{Sample citations}
-For general information on the correct form for citations using
-the APA 6 format, see the following sites:
-\href{https://owl.english.purdue.edu/owl/resource/560/02/}
-{APA 6, In-text citations, The Basics} and
-\href{https://owl.english.purdue.edu/owl/resource/560/03/}
-{APA 6, In-text citations}
-
-\section{Natbib citation mark up}
-
-\subsection{Single citations}
-\noindent
-\begin{tabular}{ll}
-\bf Type&\bf Results\\
-\hline
-\verb+\citet{jon90}+&\dogray Jones et al. (1990)\\
-\verb+\citet[chap. 2]{jon90}+&\dogray Jones et al. (1990, chap. 2)\\
-    \verb+\citep{jon90}+	    &\dogray   	(Jones et al., 1990)\\
-    \verb+\citep[chap. 2]{jon90}+ 	&\dogray    	(Jones et al., 1990, chap. 2)\\
-    \verb+\citep[see][]{jon90}+ 	 &\dogray    	(see Jones et al., 1990)\\
-    \verb+\citep[see][chap. 2]{jon90}+ 	&\dogray    	(see Jones et al., 1990, chap. 2)\\
-    \verb+\citet*{jon90}+ 	    &\dogray    	Jones, Baker, and Williams (1990)\\
-    \verb+\citep*{jon90}+	    & \dogray   	(Jones, Baker, and Williams,
-    1990) \\
-\end{tabular}
-
-For example, some citations from the NETNbibsamp.bib database:
-
-citet: \citet{bullmore2009complex}, citep: \citep{gomez2009analysis}, and
-citep*: \citep*{de2012cortical}
-
-\subsection{Multiple citations}
-Multiple citations may be made by including more than one citation
-key in the \verb+\cite+ command argument.
-
-\noindent
-\begin{tabular}{ll}
-\bf Type&\bf Results\\
-\hline
-\verb+\citet{jon90,jam91}+&\dogray Jones et al. (1990); James et al. (1991)\\
-\verb+\citep{jon90,jam91}+&\dogray (Jones et al., 1990; James et al. 1991)\\
-\verb+\citep{jon90,jon91}+&\dogray (Jones et al., 1990, 1991)\\
-\verb+\citep{jon90a,jon90b}+&\dogray (Jones et al., 1990a,b)\\
-\end{tabular}
-
-For example, multiple citations from the bibsamp.bib database:
-citet: \citet{nooner2012nki,hutchison2013resting},
- citep:
-\citep{tagliazucchi2012dynamic, de2012cortical}
-
-As you see, the citations are automatically hyperlinked to their
-reference in the bibliography.
-
-\newpage
 
@@
 \acknowledgments
-Enter your acknowledgments here.
-
-%% ie.,
-
-% The authors thank Laurence Aitchison for fruitful discussions.  RKN
-% and PD received funding from the Gatsby Charitable Foundation. Y-AB,
-% RBS, KC and PS received funding from Canadian Institutes of Health
-% Research grant $MOP74577$,
-% Fond de recherche Qu\'{e}bec - Sant\'{e} (Group grant to the Groupe 
-% de recherche en neurobiologie comportementale, Shimon Amir, P.I.), and
-% Concordia University Research Chair (Tier I).
+We deeply thank Kevin Boyack and Dick Klavans for critically constructive discussions.
+We thank the authors of Uzzi et al.
+(2013) for sharing their Python simulation code.
+Research and development reported in this publication was partially supported by Federal funds from the National Institute on Drug Abuse, National Institutes of Health, US Department of Health and Human Services, under Contract Nos.
+HHSN271201700053C (N43DA-17-1216) and HHSN271201800040C (N44DA-18-1216).
+The content of this publication is solely the responsibility of the authors and does not necessarily represent the official views of the National Institutes of Health.
+TW receives funding from the Grainger Foundation.
+All the code used in this study is freely available from a Github site.
+Access to bibliographic data requires a license from Clarivate Analytics, which had no role in
+funding, experimental design, review of results, and conclusions presented.
 
 \authorcontributions 
-Who helped formulate the project, who supplied data, analyses and
-experiments, etc.
-
-%% ie.
-%% Project was formulated by RKN, PD, PS,
-%% based on substantial data, analyses and experiments of Y-AB, KC, RS,
-%% PS. RKN, PD formalised the model, RKN implemented and ran the model;
-%% RKN analysed the molecular ethogram data; Y-AB formalised and
-%% implemented a CTMC model. All authors wrote the manuscript.
-
-\section{Making Your Bibliography for a Network Neuroscience Article}
-{\it Network Neuroscience} uses the APA author-date  bibliography style,
-apacite.bst. For more
-information on apacite, for examples in how to make your .bib file and more, see:\\
-\href{http://mirror.jmu.edu/pub/CTAN/biblio/bibtex/contrib/apacite/apacite.pdf}
-{http://mirror.jmu.edu/pub/CTAN/biblio/bibtex/contrib/apacite/apacite.pdf}
-
-\noindent
-(In spite of the mention of apacite cite commands, please use only
-Natbib commands for in text citations, as shown above.)
-
-\subsection{BibTeX}
-You will need to use BibTeX to form your bibliography; typing in the
-references would be
-a huge and unpleasant task. Look at the NETNSample.bbl file and you'll see why
-typing in the bibitems would be difficult.
-
-For a good basic introduction to using BibTeX, see\\
-\href{https://www.economics.utoronto.ca/osborne/latex/BIBTEX.HTM}
-{https://www.economics.utoronto.ca/osborne/latex/BIBTEX.HTM}
-
-When you use BibTeX, the form of the bibliography will be correct. You
-don't need to supply a bibliography style, since that is built into
-the stjour.cls file when the NETN option is used
-(\verb+\documentclass[NETN]{stjour}+).
-
-\newpage
-\subsection{Sample citations}
-
-Here are some samples using \verb+\citep{}+:\\
-\citep{bullmore2009complex,
-gomez2009analysis,
-rubinov2011weight,
-power2014methods,
-sporns2015modular,
-scheeringa2012eeg,
-fortunato2007resolution,
-reichardt2006statistical,
-smith2009correspondence,
-sporns2011networks,
-liegeois2014cerebral}
-
-And more using \verb+\citet{}+\\
-\citet{allen2012tracking,
-calhoun2014chronnectome,
-liu2013time,
-fisher1915frequency,
-gonzalez2014spatial,
-damaraju2014dynamic,
-hutchison2013resting,
-de2012cortical,
-tagliazucchi2012dynamic,
-nooner2012nki}
+This study was designed by GD, JB, SD, and TW.
+Simulations and analysis were performed by AD, GC, JB, and SD.
+Infrastructure, and workflows used to generate data used in this study were developed by AD, DK, SL, SD, and GC.
+All authors reviewed and commented on the manuscript, which was written by GC, JB, and TW.
 

### 2019-05-17 cocit_r.tex
update

@@
 Citation and network analysis of  scientific literature reveals information on semantic relationships between publications, collaboration between scientists, and the practice of citation itself~\citep{garfield_citation_1955,de_solla_price_networks_1965,newman_structure_2001,Shi:2010:CHI:1816123.1816131,patience_pmid28560354}.
-Co-citation, the frequency with which two documents are cited together in other documents~\citep{small_co-citation_1973,marshakova-shaikevich_co-citation_1973}, provides additional insights, including the identification of semantically related documents and fields.
-Co-citations, bibliographic coupling and direct citation have been compared for XX.
+Co-citation, the frequency with which two documents are cited together in other documents provides additional insights, including the identification of semantically related documents, fields, idea, and specialization in science~\citep{small_co-citation_1973,marshakova-shaikevich_co-citation_1973}.
 
 In an intriguing study, co-citation analysis of 17.9 million articles and their cited references from the Web of Science (WoS) was used to document novel combinations of prior research and to characterize highly cited papers~\citep{uzzi_atypical_2013}.
-In this study, pairwise combinations of the references in each article were generated to create a multi-set of journal-pairs.
-Observed frequencies of these journal pairs across the dataset were computed and normalized to expected values generated by Monte Carlo simulations from a random graph model.
-Normalized, journal pair frequencies were termed \emph{z-scores} (Materials and Methods).
+In this study, pairwise combinations of the references in each article were generated to create a multiset of journal-pairs.
+Observed frequencies of these journal pairs across the dataset were computed and normalized to expected values generated by Monte Carlo simulations that shuffled cited references in the context of a random graph model.
+The resultant normalized, journal pair frequencies were termed \emph{z-scores} (Materials and Methods).
 Thus, every article was associated with multiple z-scores.
-For each article, positional statistics of these z-scores were calculated to describe conventionality (high conventionality (HC) if the median z-score for an article was greater than the median of median z-scores of all articles and low conventionality for the inverse (LC).) Similarly with novelty (high novelty (HN)- if the tenth percentile of z-scores for an article was less than zero and low novelty (LN) for the inverse).
+For each article, positional statistics of these z-scores were calculated to describe conventionality;(high conventionality (HC) if the median z-score for an article was greater than the median of median z-scores of all articles and low conventionality for the inverse (LC).
+Similarly with novelty;  high novelty (HN) if the tenth percentile of z-scores for an article was less than zero and low novelty (LN) for the inverse.
 Accordingly, each article was labeled with respect to conventionality and novelty, e.g, HCLN, with all four combinations being possible.
-The finding of considerable interest was that HCHN articles were twice as likely to be found in highly cited papers (defined as the top 10\% of all papers published in a given year considering the count of citations accumulated in the first 8 years since publication).
+The finding of considerable interest was that HCHN articles were twice as likely to be found in highly cited papers~\citep{uzzi_atypical_2013} suggesting that novel ideas flavoring a base of conventional thought were a recipe for impact.
+The authors examined subsets of publications grouped by disciplined and asserted universality of this feature.
 
-Key to the Uzzi study, however, is the random graph approach, where every reference is randomly replaced by another article published in the same year as the reference to generate a null model for comparison.
-However, the approach inadequately accounts for observed citation behavior~\citep{wallace_lariviere_gingras_2012,moed_measuring_2010,klavans_research_2017} since (i) it treats potential substitutions as equi-probable, irrespective of disciplinary origin (ii) does not consider the frequency with which references are cited in the dataset.
-In illustration, a reference from musicology can replace one in quantum physics during the simulation process.
+Key to the Uzzi study, however, is the random graph approach and the mechanism of citation shuffling employed.
+Random substitutions are made under conditions that preserve the number of publications in each year of the dataset as well as the number of references cited by each of these publications.
+However, the approach inadequately accounts for observed citation behavior~\citep{wallace_lariviere_gingras_2012,moed_measuring_2010,klavans_research_2017,garfield_1979} since (i) random substitutions are selected with equal probability irrespective of disciplinary origin (ii) replacements are drawn from the set of eligible references rather than the multi-set that accounts for the frequency with which a reference is cited.
+In illustration, a musicology reference from can replace a quantum physics reference during the simulation process.
 Similarly, a reference cited over 100 times in a given year is selected with the same probability as a reference cited only once.
-Accordingly, the expected value calculations used in normalizing observed journal-pair-frequencies can be reasonably questioned on grounds of model mis-specification.
+Accordingly, the expected value calculations generated by simulations and used in normalizing observed journal-pair-frequencies can be reasonably questioned on grounds of model mis-specification.
 
@@
 While the two studies are conceptually similar, the authors of the latter study used Scopus data and the K50 measurement, a derivative of the $\chi^2$ method, rather than Monte Carlo simulations for normalizing observed to expected journal-pair frequencies.
-Boyack and Klavans note that `only 64.4\%  of  243  WoS  subject  categories' in the Uzzi study met the criterion of having the highest probability of hit papers in the HCHN category.
+Boyack and Klavans note that ``only 64.4\%  of  243  WoS  subject  categories'' in the Uzzi study met the criterion of having the highest probability of hit papers in the HCHN category.
 Further, they observed that journals vary widely in terms of size and influence and that 20 journals accounted for nearly 15\% of co-citations in their measurements.
@@
 
-Despite different methods used to generate expected values, both Uzzi and Boyack measured observed and expected journal-pair frequencies across disciplines and then examined subsets of publications for disciplinary effects.
-Since disciplinary origin was not considered when generating expected values in their studies, we chose instead to analyze semantically related sets of documents (disciplinary networks) instead of all publications in a bibliographic database.
-We used keyword searches of the scientific literature to create three citation networks themed around broad search terms.
-For each of these, we calculated expected values using a refined random graph model that accounted for existing citation frequencies in these networks and an efficient simulation algorithm that randomly permuted references grouped by year of publication.
-Thus, while Uzzi et al.
-averaged the results of 10 simulations for each year in their dataset, we averaged 1,000 simulations to ensure greater coverage of rarely observed journal pairs We hypothesized that our approach would  reduce model misspecification and better simulate citation practice, in turn leading to different and more relevant conclusions.
+Despite different methods used to generate expected values, expected journal-pair frequencies were generated without disciplinary constraints in both these prior studies~\citep{uzzi_atypical_2013,boyack_vs_uzzi_2014}, after which subsets of publications were examined for disciplinary effects.
+To avoid the problem of discipline-insensitive substitutions, we chose instead to first construct semantically related sets of documents (disciplinary networks) and then measure observed and expected frequencies within these networks.
+Accordingly, we used keyword searches of the scientific literature to create three citation networks themed around broad search terms.
+For each of these, we calculated expected values using an efficient simulation algorithm that randomly permuted references grouped by year of publication in a random graph model that accounted for existing citation frequencies in these networks.
+We hypothesized that our approach would  reduce model misspecification and better simulate citation practice, in turn leading to different and more relevant conclusions.
+Additionally,while Uzzi et al.
+averaged the results of 10 simulations for each year in their dataset, we averaged the results of 1,000 simulations per dataset to ensure greater coverage of rarely observed journal pairs (Materials and Methods).
 Our study on these semantically-themed citation networks reveals significantly different patterns of conventionality and novelty between  citation networks and disciplines that challenges the conclusion of universality in HCHN articles have a greater probability of being represented in highly cited publications.
+Instead, we conclude that conventional thought as commonly defined in our study, Uzzi, and Boyack is more likely to drive higher citations..
+\emph{these are just filler conclusions that must be carefully rewritten and added to}.
 
 \section{Materials and Methods}
+
+\subsection{Bibliographic data} We have previously developed ERNIE, infrastructure to parse the Web of Science (WoS) Core Collection into a relational database that supports analytical studies~\cite{Keserci371955}.
+WoS data stored in ERNIE spans the period 1900-2019 and consists of over 72 million publications.
+For this study, we generated an analytical dataset from years 1985 to 2005.
+The total number of publications in this dataset was just over 25 million publications (25,134,073).
+For each of these years, we further restricted analysis to those of type Article.
+Since WoS data also contains incomplete references or references that point at other indexes,  we also considered only those references for which there were complete records (Table 1).
+Given consistent trends in the data, we analyzed flanking years and the mid-point (1985, 1995, and 2005).
+For example, WoS data for year 2005 contained 1,753,174 publications, which after restricting to type Article and considering only those references described above resulted in 916,573 publications, 6,095,594 unique references (set of references), and 17,167,347 total references (multiset of references).
+
+% latex table generated in R 3.5.3 by xtable 1.8-4 package
+% Fri May 17 14:28:31 2019
+\begin{table}[ht]
+\caption{Summary of WoS Analytical Dataset.
+UP: unique publications, UR: unique references, TR: total references.
+The number of publications, unique references, total references and the ratio of total references to unique references increases monotonically with each year indicating that both the number of documents and citation activity increase over time.
+Data for reference years is flanked by horizontal lines and shown in boldface.
+Only publications of type Article and references with complete WoS records are included in these counts.}
+\centering
+\begin{tabular}{|rrrrr|}
+  \hline
+Year & UP & UR & TR & TR/UR \\ 
+  \hline
+\textbf{1985} & \textbf{418495} & \textbf{2281297} & \textbf{5615496} & \textbf{2.46} \\ 
+\hline
+1986 & 402309 & 2316451 & 5708796 & 2.46 \\ 
+1987 & 412936 & 2427347 & 5998513 & 2.47 \\ 
+1988 & 426001 & 2545647 & 6354917 & 2.50 \\ 
+1989 & 443144 & 2673092 & 6749319 & 2.52 \\ 
+1990 & 458768 & 2827517 & 7209413 & 2.55 \\ 
+1991 & 477712 & 2977784 & 7729776 & 2.60 \\ 
+1992 & 492181 & 3134109 & 8188940 & 2.61 \\ 
+1993 & 504488 & 3278102 & 8676583 & 2.65 \\ 
+1994 & 523660 & 3458072 & 9255748 & 2.68 \\ 
+ \hline
+\textbf{1995} & \textbf{559685} & \textbf{3692575} & \textbf{9897946} & \textbf{2.68} \\ 
+\hline
+1996 & 663110 & 4144581 & 11641286 & 2.81 \\ 
+1997 & 677077 & 4340733 & 12135104 & 2.80 \\ 
+1998 & 693531 & 4573584 & 12728629 & 2.78 \\ 
+1999 & 709827 & 4784024 & 13280828 & 2.78 \\ 
+ 2000 & 721926 & 5008842 & 13810746 & 2.76 \\ 
+ 2001 & 727816 & 5203078 & 14261189 & 2.74 \\ 
+ 2002 & 747287 & 5464045 & 15001390 & 2.75 \\ 
+ 2003 & 786284 & 5773756 & 16024652 & 2.78 \\ 
+ 2004 & 826834 & 6095594 & 17167347 & 2.82 \\ 
+ \hline
+\textbf{2005} & \textbf{916573} & \textbf{6629595} & \textbf{19066249} & \textbf{2.88} \\ 
+ \hline
+\end{tabular}
+\end{table}
+
+\subsection{Disciplinary datasets}
+
 \section{Results}
+
+(i) disciplinary networks are different
+(ii) background makes a difference
+(iii) 
+(iv)
+
 \section{Discussion}

### 2019-05-17 cocit_r.tex
updates

@@
 We hypothesized that our approach would  reduce model misspecification and better simulate citation practice, in turn leading to different and more relevant conclusions.
-Additionally,while Uzzi et al.
-averaged the results of 10 simulations for each year in their dataset, we averaged the results of 1,000 simulations per dataset to ensure greater coverage of rarely observed journal pairs (Materials and Methods).
 Our study on these semantically-themed citation networks reveals significantly different patterns of conventionality and novelty between  citation networks and disciplines that challenges the conclusion of universality in HCHN articles have a greater probability of being represented in highly cited publications.
@@
 \section{Materials and Methods}
-
-\subsection{Bibliographic data} We have previously developed ERNIE, infrastructure to parse the Web of Science (WoS) Core Collection into a relational database that supports analytical studies~\cite{Keserci371955}.
+\emph{Bibliographic data} We have previously developed ERNIE, an open source knowledge platform into which we parse the Web of Science (WoS) Core Collection~\cite{Keserci371955}.
 WoS data stored in ERNIE spans the period 1900-2019 and consists of over 72 million publications.
@@
 Since WoS data also contains incomplete references or references that point at other indexes,  we also considered only those references for which there were complete records (Table 1).
-Given consistent trends in the data, we analyzed flanking years and the mid-point (1985, 1995, and 2005).
 For example, WoS data for year 2005 contained 1,753,174 publications, which after restricting to type Article and considering only those references described above resulted in 916,573 publications, 6,095,594 unique references (set of references), and 17,167,347 total references (multiset of references).
+Given consistent trends in the data, we analyzed the two boundary years (1985 and 2005) and the mid-point (1995).
+\\
+\emph{Disciplinary datasets} We constructed three disciplinary datasets based on keyword searches.
+(i) immunology (ii) metabolism (iii) applied physics.
+For the first two, rooted in biomedical research, we searched Pubmed for the term `immunology' or `metabolism' in the years 1985, 1995, and 2005.
+Pubmed IDs (pmids) returned were converted to WoS IDs (wos\_ids).
+For the applied physics dataset, we directly searched article level labels in WoS for `applied physics'.
+\\
+\emph{Normalization of observed and expected values} We analyzed Building upon the work of Uzzi and colleagues, $nC2$ reference pairs were generated for each publication where $n$ is the number of cited references in the publication.
+These reference pairs were then mapped to the journals they were published in using ISSN numbers creating journal pairs.
+Where multiple ISSN numbers exist for a journal, the most frequently used one in the WoS was assigned to the journal.
+In addition, publications containing less than two references were discarded.
+Journal pair frequencies were summed up across the dataset to create observed frequencies$(F_{obs})$.
+In contrast to the preceding study~\citep{uzzi_atypical_2013}, we we generated 1,000 rather than 10 null models for each dataset by randomly shuffling references while preserving the number of publications, the number of references in each publication, and the frequency with which these references were cited within the year of interest.
+Expected values $(F_{exp})$ were generated by averaging the result of 1,000 simulations.
+z-scores were calculated for each journal-pair using the formula $(F_{obs} - F_{exp})/\sigma$ where $\sigma$
+ is the standard deviation of the frequencies generated by simulation.
+As a result of these calculations, each publication becomes associated with a set of z-scores corresponding to the journal pairs derived from pairwise combinations of its cited references and positional statistics (quantiles) of z-scores were calculated for each publication.
+Publications were also labeled according to conventionality and novelty.
+(i) HC if the median z-score exceeded the median of median z-scores for all publications.
+LC if the median z-score was equal to or less than the median of median z-scores for all publications (ii) HN if the tenth percentile of z-scores for a publication was less than zero.
+LN if the tenth percentile of z-scores for a publication was greater than zero.
 
@@
 Only publications of type Article and references with complete WoS records are included in these counts.}
+\label{tab:label}
 \centering
@@
 
-\subsection{Disciplinary datasets}
+\begin{table}[ht]
+\caption{Disciplinary Datasets.
+PubMed and WoS were searched for articles using search terms, `immunology', `metabolism', and `applied physics'.
+Counts of retrieved publications are shown for each of the three years analyzed.}
+\label{tab:label}
+\centering
+\begin{tabular}{|r r r r|}
+  \hline
+Year & Immunology & Metabolism & Applied Physics \\ 
+  \hline
+1985 & 21,606 & 78,998 & 10,298 \\ 
+1995 & 29,320 & 121,247 & 21,012  \\ 
+2005 & 37,296 & 200,052 & 35,600  \\ 
+ \hline
+\end{tabular}
+\end{table}
 
@@
 \section{Discussion}
+
+\acknowledgments
+We deeply thank Kevin Boyack and Dick Klavans for critically constructive discussions.
+We thank the authors of Uzzi et al.
+(2013) for sharing their Python simulation code.
+Research and development reported in this publication was partially supported by Federal funds from the National Institute on Drug Abuse, National Institutes of Health, US Department of Health and Human Services, under Contract Nos.
+HHSN271201700053C (N43DA-17-1216) and HHSN271201800040C (N44DA-18-1216).
+The content of this publication is solely the responsibility of the authors and does not necessarily represent the official views of the National Institutes of Health.
+TW receives funding from the Grainger Foundation.
+All the code used in this study is freely available from a Github site.
+Access to bibliographic data requires a license from Clarivate Analytics, which had no role in
+funding, experimental design, review of results, and conclusions presented.
+
+\authorcontributions 
+This study was designed by GD, JB, SD, and TW.
+Simulations and analysis were performed by AD, GC, JB, and SD.
+Infrastructure, and workflows used to generate data used in this study were developed by AD, DK, SL, SD, and GC.
+All authors reviewed and commented on the manuscript, which was written by GC, JB, and TW.
+
+\newpage
+%%%%%%%%%%%%%%%%%%%%%%%
+%% The bibliography
+
+\bibliography{cocit_r}
+
+%% No appendices allowed in Network Neuroscience style
+%\appendix
+
+\end{document}
 
@@
 % No supportive information is available at this time.
-
-\acknowledgments
-We deeply thank Kevin Boyack and Dick Klavans for critically constructive discussions.
-We thank the authors of Uzzi et al.
-(2013) for sharing their Python simulation code.
-Research and development reported in this publication was partially supported by Federal funds from the National Institute on Drug Abuse, National Institutes of Health, US Department of Health and Human Services, under Contract Nos.
-HHSN271201700053C (N43DA-17-1216) and HHSN271201800040C (N44DA-18-1216).
-The content of this publication is solely the responsibility of the authors and does not necessarily represent the official views of the National Institutes of Health.
-TW receives funding from the Grainger Foundation.
-All the code used in this study is freely available from a Github site.
-Access to bibliographic data requires a license from Clarivate Analytics, which had no role in
-funding, experimental design, review of results, and conclusions presented.
-
-\authorcontributions 
-This study was designed by GD, JB, SD, and TW.
-Simulations and analysis were performed by AD, GC, JB, and SD.
-Infrastructure, and workflows used to generate data used in this study were developed by AD, DK, SL, SD, and GC.
-All authors reviewed and commented on the manuscript, which was written by GC, JB, and TW.
-
-\newpage
-%%%%%%%%%%%%%%%%%%%%%%%
-%% The bibliography
-
-\bibliography{cocit_r}
-
-%% No appendices allowed in Network Neuroscience style
-%\appendix
-
-\end{document}

### 2019-05-20 cocit-r.tex
renamed the file back to original

--- 2019-05-17 cocit_r.tex
@@
 \affiliation{2}{Netelabs, NET ESolutions Corporation, McLean, VA 22102, USA}
-\affiliation{3}{Department of Computer Science, University of Illinois Urbana-Champaign, Champaign, IL 61820, USA}
+\affiliation{3}{Department of Computer Science, University of Illinois at Urbana-Champaign, Champaign, IL 61820, USA}
 
@@
 Co-citation, the frequency with which pairs of publications are cited, provides insight into how documents relate to each other and across fields.
-Co-citation analysis has been used to characterize combinations of prior work as conventional or innovative and to derive features of highly cited publications.
+Co-citation analysis has been used to characterize combinations of prior work as conventional or innovative and to deriveå features of highly cited publications.
 Given the organization of science into disciplines, a key question is the sensitivity of such analyses to frame of reference.
@@
 
-In an intriguing study, co-citation analysis of 17.9 million articles and their cited references from the Web of Science (WoS) was used to document novel combinations of prior research and to characterize highly cited papers~\citep{uzzi_atypical_2013}.
-In this study, pairwise combinations of the references in each article were generated to create a multiset of journal-pairs.
-Observed frequencies of these journal pairs across the dataset were computed and normalized to expected values generated by Monte Carlo simulations that shuffled cited references in the context of a random graph model.
-The resultant normalized, journal pair frequencies were termed \emph{z-scores} (Materials and Methods).
+\cite{uzzi_atypical_2013} used a novel approach for co-citation analysis of 17.9 million articles and their cited references from the Web of Science (WoS)  to characterize the highly cited papers according to both novel and conventional combinations of prior research.
+%~\citep{uzzi_atypical_2013}.
+%In this study, pairwise combinations of the references in each article were generated to create a multiset of journal-pairs. 
+%They explored the use of a random graph model, in which 
+Observed frequencies of these journal pairs across the dataset were computed and compared to expected values generated by Monte Carlo simulations that shuffled cited references in the context of a random graph model, allowing substitutions of references by any other reference published in the same year and appearing in WoS.
+By normalizing the differences in these frequencies, journal pairs were assigned \emph{z-scores} (Materials and Methods). 
 Thus, every article was associated with multiple z-scores. 
-For each article, positional statistics of these z-scores were calculated to describe conventionality;(high conventionality (HC) if the median z-score for an article was greater than the median of median z-scores of all articles and low conventionality for the inverse (LC).
-Similarly with novelty;  high novelty (HN) if the tenth percentile of z-scores for an article was less than zero and low novelty (LN) for the inverse.
-Accordingly, each article was labeled with respect to conventionality and novelty, e.g, HCLN, with all four combinations being possible.
+For each article, positional statistics of these z-scores were calculated to describe conventionality: high conventionality (HC) if the median z-score for an article was greater than the median of median z-scores of all articles and low conventionality for the inverse (LC).
+Similarly,  an article was deemed to have high novelty (HN) if the tenth percentile of its z-scores  was negative and low novelty (LN) for the inverse.
+Accordingly, each article was labeled with respect to conventionality and novelty, e.g, HCLN (denoting that the article has high conventionality and low novelty), with all four combinations being possible.
 The finding of considerable interest was that HCHN articles were twice as likely to be found in highly cited papers~\citep{uzzi_atypical_2013} suggesting that novel ideas flavoring a base of conventional thought were a recipe for impact.
@@
 
-Key to the Uzzi study, however, is the random graph approach and the mechanism of citation shuffling employed.
-Random substitutions are made under conditions that preserve the number of publications in each year of the dataset as well as the number of references cited by each of these publications.
-However, the approach inadequately accounts for observed citation behavior~\citep{wallace_lariviere_gingras_2012,moed_measuring_2010,klavans_research_2017,garfield_1979} since (i) random substitutions are selected with equal probability irrespective of disciplinary origin (ii) replacements are drawn from the set of eligible references rather than the multi-set that accounts for the frequency with which a reference is cited.
+Key to the Uzzi {\em et al.} study, however, is the random graph approach and the mechanism of citation shuffling employed. 
+Their random graph model produces
+ substitutions of references by other references   that preserve the number of publications in each year of the dataset as well as the number of references cited by each of these publications. 
+ However, the approach also assumes that all substitutions are equiprobable (i.e., a substitution of a reference in physics by a reference in musicology has the same probability under their model as a substitution of the physics reference by another physics reference).
+ This assumption does not account %to replace a reference from the same year, with equal probability inadequately accounts 
+ for observed citation behavior~\citep{wallace_lariviere_gingras_2012,moed_measuring_2010,klavans_research_2017,garfield_1979}, and clearly is inconsistent with author behavior (i.e., in practice, an author of a paper in evolutionary biology is more likely to cite a biology paper than a paper in art history).
+% Furthermore, the citation frequency of the reference does not impact the probability of selecting the
+% reference, which also is inconsistent with author behavior. 
+  %since (i) random substitutions are selected with equal probability irrespective of disciplinary origin (ii) replacements are drawn from the set of eligible references rather than the multi-set that accounts for the frequency with which a reference is cited.
 In illustration, a musicology reference from can replace a quantum physics reference during the simulation process.
-Similarly, a reference cited over 100 times in a given year is selected with the same probability as a reference cited only once.
+ In addition, under the Uzzi {\em et al.} random model,  a reference cited over 100 times in a given year is selected with the same probability as a reference cited only once. 
  Accordingly, the expected value calculations generated by simulations and used in normalizing observed journal-pair-frequencies can be reasonably questioned on grounds of model mis-specification.
@@
 Lastly, that three multidisciplinary journals accounted for 9.4\% of all atypical combinations, suggesting strong effects from both disciplines and journals.
+Despite different methods used to generate expected values, both studies generated expected journal-pair frequencies without disciplinary considerations~\citep{uzzi_atypical_2013,boyack_vs_uzzi_2014}, and only after this were subsets of publications  examined for disciplinary effects.
 
-Despite different methods used to generate expected values, expected journal-pair frequencies were generated without disciplinary constraints in both these prior studies~\citep{uzzi_atypical_2013,boyack_vs_uzzi_2014}, after which subsets of publications were examined for disciplinary effects.
 To avoid the problem of discipline-insensitive substitutions, we chose instead to first construct semantically related sets of documents (disciplinary networks) and then measure observed and expected frequencies within these networks.

### 2019-05-21 cocit_r.tex
University of Illinois name updated
updated latex and bibtex

@@
 
-In an intriguing study, co-citation analysis of 17.9 million articles and their cited references from the Web of Science (WoS) was used to document novel combinations of prior research and to characterize highly cited papers~\citep{uzzi_atypical_2013}.
-In this study, pairwise combinations of the references in each article were generated to create a multiset of journal-pairs.
-Observed frequencies of these journal pairs across the dataset were computed and normalized to expected values generated by Monte Carlo simulations that shuffled cited references in the context of a random graph model.
-The resultant normalized, journal pair frequencies were termed \emph{z-scores} (Materials and Methods).
+\cite{uzzi_atypical_2013} used a novel approach for co-citation analysis of 17.9 million articles and their cited references from the Web of Science (WoS)  to characterize the highly cited papers according to both novel and conventional combinations of prior research.
+%~\citep{uzzi_atypical_2013}.
+%In this study, pairwise combinations of the references in each article were generated to create a multiset of journal-pairs. 
+%They explored the use of a random graph model, in which 
+Observed frequencies of these journal pairs across the dataset were computed and normalized, with respect to   expected values generated by Monte Carlo simulations  that shuffled cited references in the context of a random graph model, allowing substitutions of references by any other reference published in the same year and appearing in WoS.
+By normalizing the observed frequencies based on their random graph model, journal pairs were assigned \emph{z-scores} (Materials and Methods). 
 Thus, every article was associated with multiple z-scores. 
-For each article, positional statistics of these z-scores were calculated to describe conventionality;(high conventionality (HC) if the median z-score for an article was greater than the median of median z-scores of all articles and low conventionality for the inverse (LC).
-Similarly with novelty;  high novelty (HN) if the tenth percentile of z-scores for an article was less than zero and low novelty (LN) for the inverse.
-Accordingly, each article was labeled with respect to conventionality and novelty, e.g, HCLN, with all four combinations being possible.
-The finding of considerable interest was that HCHN articles were twice as likely to be found in highly cited papers~\citep{uzzi_atypical_2013} suggesting that novel ideas flavoring a base of conventional thought were a recipe for impact.
-The authors examined subsets of publications grouped by disciplined and asserted universality of this feature.
+For each article, positional statistics of these z-scores were calculated to describe conventionality: high conventionality (HC) if the median z-score for an article was greater than the median of median z-scores of all articles and low conventionality for the inverse (LC).
+Similarly,  an article was deemed to have high novelty (HN) if the tenth percentile of its z-scores  was negative and low novelty (LN) for the inverse.
+Accordingly, each article was labeled with respect to conventionality and novelty, e.g, HCLN (denoting that the article has high conventionality and low novelty), with all four combinations being possible.
+\cite{uzzi_atypical_2013} observed that HCHN articles were twice as likely to be found in highly cited papers, suggesting that novel ideas flavoring a base of conventional thought were a recipe for impact.
+Further,\cite{uzzi_atypical_2013} examined subsets of publications grouped by discipline and asserted universality of this feature; this claim of universality was made despite the fact that only about 60\% of the disciplines they examined displayed this bias to HCHN for the highly cited papers.
 
-Key to the Uzzi study, however, is the random graph approach and the mechanism of citation shuffling employed.
-Random substitutions are made under conditions that preserve the number of publications in each year of the dataset as well as the number of references cited by each of these publications.
-However, the approach inadequately accounts for observed citation behavior~\citep{wallace_lariviere_gingras_2012,moed_measuring_2010,klavans_research_2017,garfield_1979} since (i) random substitutions are selected with equal probability irrespective of disciplinary origin (ii) replacements are drawn from the set of eligible references rather than the multi-set that accounts for the frequency with which a reference is cited.
+Key to the Uzzi {\em et al.} study, however, is the random graph model, since it drives the definition of conventionality and novelty.
+A careful examination of the model (as defined by the Monte Carlo simulation) reveals that all substitutions of 
+references are equiprobable, which means that references can be substituted by any other reference in the same year, irrespective of subject matter and citation count.
+%These 
+% substitutions of references by other references   that preserve the number of publications in each year of the dataset as well as the number of references cited by each of these publications. 
+Both aspects of the model violate citation behavior.
+For example, the assumption that all substitutions are equiprobable has the consequence that a substitution of a reference in physics by a reference in musicology has the same probability under their model as a substitution of the physics reference by another physics reference)
+ This assumption does not account %to replace a reference from the same year, with equal probability inadequately accounts 
+ for observed citation behavior~\citep{wallace_lariviere_gingras_2012,moed_measuring_2010,klavans_research_2017,garfield_1979}, and clearly is inconsistent with author behavior (i.e., in practice, an author of a paper in evolutionary biology is more likely to cite a biology paper than a paper in art history).
+% Furthermore, the citation frequency of the reference does not impact the probability of selecting the
+% reference, which also is inconsistent with author behavior. 
+  %since (i) random substitutions are selected with equal probability irrespective of disciplinary origin (ii) replacements are drawn from the set of eligible references rather than the multi-set that accounts for the frequency with which a reference is cited.
 In illustration, a musicology reference from can replace a quantum physics reference during the simulation process.
-Similarly, a reference cited over 100 times in a given year is selected with the same probability as a reference cited only once.
-Accordingly, the expected value calculations generated by simulations and used in normalizing observed journal-pair-frequencies can be reasonably questioned on grounds of model mis-specification.
+ In addition, under the Uzzi {\em et al.} random model,  a reference cited over 100 times in a given year is selected with the same probability as a reference cited only once; this is also
+ a model assumption that violates author behavior, and is inconsistent with the observation of
+ a power law in citation frequencies. 
+ Accordingly, the expected value calculations generated by the \cite{uzzi_atypical_2013} simulations and used in characterizing journal pairs in terms of conventionality and novelty %normalizing observed journal-pair frequencies
+ can be reasonably questioned on grounds of model mis-specification.
 
-A follow-up study using a smaller dataset of 12 million articles, also suggests that Uzzi and colleagues do not fully account for disciplinary and journal effects~\citep{boyack_vs_uzzi_2014}.
-While the two studies are conceptually similar, the authors of the latter study used Scopus data and the K50 measurement, a derivative of the $\chi^2$ method, rather than Monte Carlo simulations for normalizing observed to expected journal-pair frequencies.
-Boyack and Klavans note that ``only 64.4\%  of  243  WoS  subject  categories'' in the Uzzi study met the criterion of having the highest probability of hit papers in the HCHN category.
+A follow-up study by \cite{boyack_vs_uzzi_2014} %using a smaller dataset of 12 million articles, 
+explored the impact of discipline and journal effects on the definition of conventionality and novelty.
+Their study had some methodological differences from \cite{uzzi_atypical_2013} (i.e., they used Scopus data and the K50 measurement to define z-scores) and revealed that Uzzi {\em et al.}~do not fully account for disciplinary and journal effects.
+%While the two studies are conceptually similar, 
+%the authors of the latter study used Scopus data and the K50 measurement, a derivative of the $\chi^2$ method, rather than Monte Carlo simulations for normalizing observed to expected journal-pair frequencies.
+Boyack and Klavans find the same basic trend that HCHN dominates the highly cited papers, but note that ``only 64.4\%  of  243  WoS  subject  categories'' in the Uzzi {\em et al.} study met the criterion of having the highest probability of hit papers in the HCHN category.
 Further, they observed that journals vary widely in terms of size and influence and that 20 journals accounted for nearly 15\% of co-citations in their measurements. 
-Lastly, that three multidisciplinary journals accounted for 9.4\% of all atypical combinations, suggesting strong effects from both disciplines and journals.
+Lastly, they noted that three multidisciplinary journals accounted for 9.4\% of all atypical combinations, suggesting strong effects from both disciplines and journals. 
+Despite different methods used to generate expected values, both \cite{uzzi_atypical_2013} and \cite{boyack_vs_uzzi_2014}  generated expected journal-pair frequencies without disciplinary considerations (i.e., the references used for a paper are selected with equal probability, irrespective of subject matter), and hence both studies explored co-citation analysis under models that do not reflect author behavior.
+%and the impact of disciplinary   only after this were subsets of publications  examined for disciplinary effects.
 
-Despite different methods used to generate expected values, expected journal-pair frequencies were generated without disciplinary constraints in both these prior studies~\citep{uzzi_atypical_2013,boyack_vs_uzzi_2014}, after which subsets of publications were examined for disciplinary effects.
 To avoid the problem of discipline-insensitive substitutions, we chose instead to first construct semantically related sets of documents (disciplinary networks) and then measure observed and expected frequencies within these networks.
@@
 We hypothesized that our approach would  reduce model misspecification and better simulate citation practice, in turn leading to different and more relevant conclusions.
-Our study on these semantically-themed citation networks reveals significantly different patterns of conventionality and novelty between  citation networks and disciplines that challenges the conclusion of universality in HCHN articles have a greater probability of being represented in highly cited publications.
-Instead, we conclude that conventional thought as commonly defined in our study, Uzzi, and Boyack is more likely to drive higher citations..
+Our study on these semantically-themed citation networks reveals significantly different patterns of conventionality and novelty between  citation networks and disciplines that challenges the conclusions
+of \cite{uzzi_atypical_2013} that  universality
+ in HCHN articles have a greater probability of being represented in highly cited publications. 
+Instead, we conclude that conventional thought as commonly defined in our study, 
+in \cite{uzzi_atypical_2013}, and  \cite{boyack_vs_uzzi_2014}, is more likely to drive higher citations..
  \emph{these are just filler conclusions that must be carefully rewritten and added to}.
@@
 \section{Materials and Methods}
-\emph{Bibliographic data} We have previously developed ERNIE, an open source knowledge platform into which we parse the Web of Science (WoS) Core Collection~\cite{Keserci371955}.
+\emph{Bibliographic data} We have previously developed ERNIE, an open source knowledge platform into which we parse the Web of Science (WoS) Core Collection~\citep{Keserci371955}.
 WoS data stored in ERNIE spans the period 1900-2019 and consists of over 72 million publications.
@@
 \\
-\emph{Normalization of observed and expected values} We analyzed Building upon the work of Uzzi and colleagues, $nC2$ reference pairs were generated for each publication where $n$ is the number of cited references in the publication.
-These reference pairs were then mapped to the journals they were published in using ISSN numbers creating journal pairs.
+\emph{Normalization of observed and expected values} Building upon the work of Uzzi {\em et al.}, all ${n \choose 2}$ reference pairs were generated for each publication, where $n$ is the number of cited references in the publication.
+These reference pairs were then mapped to the journals they were published in using ISSN numbers,  creating journal pairs.
 Where multiple ISSN numbers exist for a journal, the most frequently used one in the WoS was assigned to the journal.
 In addition, publications containing less than two references were discarded.
-Journal pair frequencies were summed up across the dataset to create observed frequencies$(F_{obs})$.
-In contrast to the preceding study~\citep{uzzi_atypical_2013}, we we generated 1,000 rather than 10 null models for each dataset by randomly shuffling references while preserving the number of publications, the number of references in each publication, and the frequency with which these references were cited within the year of interest.
+Journal pair frequencies were summed up across the dataset to create observed frequencies $(F_{obs})$.
+In contrast to the preceding study~\citep{uzzi_atypical_2013}, we generated 1,000 rather than 10 null models for each dataset by randomly shuffling references while preserving the number of publications, the number of references in each publication, and the frequency with which these references were cited within the year of interest.
 Expected values $(F_{exp})$ were generated by averaging the result of 1,000 simulations.

### 2019-05-21 cocit_r.tex
fleshed out the Intro some more

@@
 
-\cite{uzzi_atypical_2013} used a novel approach for co-citation analysis of 17.9 million articles and their cited references from the Web of Science (WoS)  to characterize the highly cited papers according to both novel and conventional combinations of prior research.
-%~\citep{uzzi_atypical_2013}.
-%In this study, pairwise combinations of the references in each article were generated to create a multiset of journal-pairs. 
-%They explored the use of a random graph model, in which 
-Observed frequencies of these journal pairs across the dataset were computed and normalized, with respect to   expected values generated by Monte Carlo simulations  that shuffled cited references in the context of a random graph model, allowing substitutions of references by any other reference published in the same year and appearing in WoS.
-By normalizing the observed frequencies based on their random graph model, journal pairs were assigned \emph{z-scores} (Materials and Methods). 
+\cite{uzzi_atypical_2013} used a novel approach for co-citation analysis of 17.9 million articles and their cited references from the Web of Science (WoS)  to characterize a subset of highly cited articles with respect to both novel and conventional combinations of prior research.
+Observed co-citation frequencies, mapped to journals, were computed across the dataset and normalized (shifted and scaled) to expected values generated by Monte Carlo simulations under a random graph model.
+These normalized journal pair frequencies were termed \emph{z-scores} (Materials and Methods).
 Thus, every article was associated with multiple z-scores.
@@
 Similarly,  an article was deemed to have high novelty (HN) if the tenth percentile of its z-scores  was negative and low novelty (LN) for the inverse.
-Accordingly, each article was labeled with respect to conventionality and novelty, e.g, HCLN (denoting that the article has high conventionality and low novelty), with all four combinations being possible.
-\cite{uzzi_atypical_2013} observed that HCHN articles were twice as likely to be found in highly cited papers, suggesting that novel ideas flavoring a base of conventional thought were a recipe for impact.
-Further,\cite{uzzi_atypical_2013} examined subsets of publications grouped by discipline and asserted universality of this feature; this claim of universality was made despite the fact that only about 60\% of the disciplines they examined displayed this bias to HCHN for the highly cited papers.
+Accordingly, each article was labeled with respect to conventionality and novelty, e.g, HCHN (denoting that the article exhibits high conventionality and high novelty), with all four combinations being possible.
+\cite{uzzi_atypical_2013} observed that HCHN articles were twice as likely to be found in highly cited papers, suggesting that novel combinations of ideas flavoring a body of conventional thought were a recipe for impact across the scientific literature.
 
-Key to the Uzzi {\em et al.} study, however, is the random graph model, since it drives the definition of conventionality and novelty.
-A careful examination of the model (as defined by the Monte Carlo simulation) reveals that all substitutions of 
-references are equiprobable, which means that references can be substituted by any other reference in the same year, irrespective of subject matter and citation count.
-%These 
-% substitutions of references by other references   that preserve the number of publications in each year of the dataset as well as the number of references cited by each of these publications. 
-Both aspects of the model violate citation behavior.
-For example, the assumption that all substitutions are equiprobable has the consequence that a substitution of a reference in physics by a reference in musicology has the same probability under their model as a substitution of the physics reference by another physics reference)
- This assumption does not account %to replace a reference from the same year, with equal probability inadequately accounts 
- for observed citation behavior~\citep{wallace_lariviere_gingras_2012,moed_measuring_2010,klavans_research_2017,garfield_1979}, and clearly is inconsistent with author behavior (i.e., in practice, an author of a paper in evolutionary biology is more likely to cite a biology paper than a paper in art history).
-% Furthermore, the citation frequency of the reference does not impact the probability of selecting the
-% reference, which also is inconsistent with author behavior. 
-  %since (i) random substitutions are selected with equal probability irrespective of disciplinary origin (ii) replacements are drawn from the set of eligible references rather than the multi-set that accounts for the frequency with which a reference is cited.
-In illustration, a musicology reference from can replace a quantum physics reference during the simulation process.
- In addition, under the Uzzi {\em et al.} random model,  a reference cited over 100 times in a given year is selected with the same probability as a reference cited only once; this is also
- a model assumption that violates author behavior, and is inconsistent with the observation of
- a power law in citation frequencies. 
- Accordingly, the expected value calculations generated by the \cite{uzzi_atypical_2013} simulations and used in characterizing journal pairs in terms of conventionality and novelty %normalizing observed journal-pair frequencies
- can be reasonably questioned on grounds of model mis-specification.
+Key to Uzzi {\em et al.}, however, is their random graph model and its underlying assumptions.
+A careful examination of the model (as defined by the Monte Carlo simulation) reveals that all substitutions of references are equiprobable, which means that a reference in an article can be substituted by any other reference randomly chosen from those published in the same year, irrespective of subject matter and citation count.
+For example, the model permits substitution of a reference in quantum physics with equal probability by a reference in classical literature, evolutionary biology, or anthropology.
+Such substitutions poorly model documented citation behavior~\citep{wallace_lariviere_gingras_2012,moed_measuring_2010,klavans_research_2017,garfield_1979}.
+In addition, under this random model,  a reference cited over 100 times in a given year is selected with the same probability as a reference cited only once, which is also inconsistent with the citation frequency distribution (Stringer, Perline).
+Accordingly, the expected value calculations generated by the \cite{uzzi_atypical_2013} simulations and used in characterizing journal pairs in terms of conventionality and novelty  can be reasonably questioned on grounds of model mis-specification.
 
-A follow-up study by \cite{boyack_vs_uzzi_2014} %using a smaller dataset of 12 million articles, 
-explored the impact of discipline and journal effects on the definition of conventionality and novelty.
-Their study had some methodological differences from \cite{uzzi_atypical_2013} (i.e., they used Scopus data and the K50 measurement to define z-scores) and revealed that Uzzi {\em et al.}~do not fully account for disciplinary and journal effects.
-%While the two studies are conceptually similar, 
-%the authors of the latter study used Scopus data and the K50 measurement, a derivative of the $\chi^2$ method, rather than Monte Carlo simulations for normalizing observed to expected journal-pair frequencies.
-Boyack and Klavans find the same basic trend that HCHN dominates the highly cited papers, but note that ``only 64.4\%  of  243  WoS  subject  categories'' in the Uzzi {\em et al.} study met the criterion of having the highest probability of hit papers in the HCHN category.
+A follow-up study by \cite{boyack_vs_uzzi_2014}  explored the impact of discipline and journal effects on the definition of conventionality and novelty.
+While their study had some methodological differences from \cite{uzzi_atypical_2013} in the use of Scopus data and a $\chi^2$ calculation for expected values, Boyack and Klavans find the same basic trend that HCHN is more probably in highly cited papers.
+However, they note that ``only 64.4\%  of  243  WoS  subject  categories'' in the Uzzi {\em et al.} study met the criterion of having the highest probability of hit papers in the HCHN category.
 Further, they observed that journals vary widely in terms of size and influence and that 20 journals accounted for nearly 15\% of co-citations in their measurements.
-Lastly, they noted that three multidisciplinary journals accounted for 9.4\% of all atypical combinations, suggesting strong effects from both disciplines and journals. 
-Despite different methods used to generate expected values, both \cite{uzzi_atypical_2013} and \cite{boyack_vs_uzzi_2014}  generated expected journal-pair frequencies without disciplinary considerations (i.e., the references used for a paper are selected with equal probability, irrespective of subject matter), and hence both studies explored co-citation analysis under models that do not reflect author behavior.
-%and the impact of disciplinary   only after this were subsets of publications  examined for disciplinary effects.
+Lastly, they noted that three multidisciplinary journals accounted for 9.4\% of all atypical combinations, suggesting strong effects from both disciplines and journals that were not reported by Uzzi et al.
 
-To avoid the problem of discipline-insensitive substitutions, we chose instead to first construct semantically related sets of documents (disciplinary networks) and then measure observed and expected frequencies within these networks.
+Despite different methods used to generate expected values, both \cite{uzzi_atypical_2013} and \cite{boyack_vs_uzzi_2014}  measured observed frequencies across the scientific literature and used these pan-literature z-scores to examine disciplinary subsets.
+In contrast, we chose instead to first construct semantically related sets of documents (disciplinary networks) and measure observed and expected frequencies within these networks.
+
 Accordingly, we used keyword searches of the scientific literature to create three citation networks themed around broad search terms.
-For each of these, we calculated expected values using an efficient simulation algorithm that randomly permuted references grouped by year of publication in a random graph model that accounted for existing citation frequencies in these networks.
+Within these disciplinary frameworks, we calculated expected values using a random graph model that accounted for existing citation frequencies and an efficient simulation algorithm that permitted a substantially greater number of simulations compared to Uzzi.
 We hypothesized that our approach would  reduce model misspecification and better simulate citation practice, in turn leading to different and more relevant conclusions.
-Our study on these semantically-themed citation networks reveals significantly different patterns of conventionality and novelty between  citation networks and disciplines that challenges the conclusions
-of \cite{uzzi_atypical_2013} that  universality
- in HCHN articles have a greater probability of being represented in highly cited publications. 
+Our study on these semantically-themed citation networks reveals significantly different patterns of conventionality and novelty between  citation networks and disciplines that challenges the conclusion that HCHN articles have a greater probability of being represented in highly cited publications.
 Instead, we conclude that conventional thought as commonly defined in our study, 
@@
 For example, WoS data for year 2005 contained 1,753,174 publications, which after restricting to type Article and considering only those references described above resulted in 916,573 publications, 6,095,594 unique references (set of references), and 17,167,347 total references (multiset of references).
-Given consistent trends in the data, we analyzed the two boundary years (1985 and 2005) and the mid-point (1995).
+Given consistent trends in the data, we analyzed the two boundary years (1985 and 2005) and the mid-point (1995) performing 1,000 simulations for each dataset.
 \\

### 2019-05-22 cocit_r.tex
more tweaks and Chacko subsection

@@
 Citation and network analysis of  scientific literature reveals information on semantic relationships between publications, collaboration between scientists, and the practice of citation itself~\citep{garfield_citation_1955,de_solla_price_networks_1965,newman_structure_2001,Shi:2010:CHI:1816123.1816131,patience_pmid28560354}.
-Co-citation, the frequency with which two documents are cited together in other documents provides additional insights, including the identification of semantically related documents, fields, idea, and specialization in science~\citep{small_co-citation_1973,marshakova-shaikevich_co-citation_1973}.
+Co-citation, the frequency with which two documents are cited together in other documents provides additional insights, including the identification of semantically related documents, fields, idea, and specialization in science~\citep{small_co-citation_1973,marshakova-shaikevich_co-citation_1973,boyack_co-citation_2010}.
 
-\cite{uzzi_atypical_2013} used a novel approach for co-citation analysis of 17.9 million articles and their cited references from the Web of Science (WoS)  to characterize a subset of highly cited articles with respect to both novel and conventional combinations of prior research.
+\citep{uzzi_atypical_2013} used a novel approach for co-citation analysis of 17.9 million articles and their cited references from the Web of Science (WoS)  to characterize a subset of highly cited articles with respect to both novel and conventional combinations of prior research.
 Observed co-citation frequencies, mapped to journals, were computed across the dataset and normalized (shifted and scaled) to expected values generated by Monte Carlo simulations under a random graph model.
@@
 Accordingly, each article was labeled with respect to conventionality and novelty, e.g, HCHN (denoting that the article exhibits high conventionality and high novelty), with all four combinations being possible.
-\cite{uzzi_atypical_2013} observed that HCHN articles were twice as likely to be found in highly cited papers, suggesting that novel combinations of ideas flavoring a body of conventional thought were a recipe for impact across the scientific literature.
+\citep{uzzi_atypical_2013} observed that HCHN articles were twice as likely to be found in highly cited papers, suggesting that novel combinations of ideas flavoring a body of conventional thought were a recipe for impact across the scientific literature.
 
@@
 Such substitutions poorly model documented citation behavior~\citep{wallace_lariviere_gingras_2012,moed_measuring_2010,klavans_research_2017,garfield_1979}.
-In addition, under this random model,  a reference cited over 100 times in a given year is selected with the same probability as a reference cited only once, which is also inconsistent with the citation frequency distribution (Stringer, Perline).
-Accordingly, the expected value calculations generated by the \cite{uzzi_atypical_2013} simulations and used in characterizing journal pairs in terms of conventionality and novelty  can be reasonably questioned on grounds of model mis-specification.
+In addition, under this random model,  a reference cited over 100 times in a given year is selected with the same probability as a reference cited only once, which is inconsistent with the frequency distribution of citations characterized as power law or lognormal~\citep{stringer_statistical_2010,perline_strong_2005}.
+Accordingly, the expected value calculations generated by the \citep{uzzi_atypical_2013} simulations and used in characterizing journal pairs in terms of conventionality and novelty  can be reasonably questioned on grounds of model mis-specification.
 
-A follow-up study by \cite{boyack_vs_uzzi_2014}  explored the impact of discipline and journal effects on the definition of conventionality and novelty.
-While their study had some methodological differences from \cite{uzzi_atypical_2013} in the use of Scopus data and a $\chi^2$ calculation for expected values, Boyack and Klavans find the same basic trend that HCHN is more probably in highly cited papers.
+A follow-up study by \citep{boyack_vs_uzzi_2014}  explored the impact of discipline and journal effects on the definition of conventionality and novelty.
+While their study had some methodological differences from \citep{uzzi_atypical_2013} in the use of Scopus data and a $\chi^2$ calculation for expected values, Boyack and Klavans find the same basic trend that HCHN is more probably in highly cited papers.
 However, they note that ``only 64.4\%  of  243  WoS  subject  categories'' in the Uzzi {\em et al.} study met the criterion of having the highest probability of hit papers in the HCHN category.
@@
 
-Despite different methods used to generate expected values, both \cite{uzzi_atypical_2013} and \cite{boyack_vs_uzzi_2014}  measured observed frequencies across the scientific literature and used these pan-literature z-scores to examine disciplinary subsets.
-In contrast, we chose instead to first construct semantically related sets of documents (disciplinary networks) and measure observed and expected frequencies within these networks.
+Despite different methods used to generate expected values, both \citep{uzzi_atypical_2013} and \citep{boyack_vs_uzzi_2014}  measured observed frequencies across the scientific literature without disciplinary constraints and subsequently used normalized frequencies to examine disciplinary subsets.
+In contrast, we chose instead to first construct semantically related sets of documents (disciplinary networks) to and measure observed and expected frequencies within these networks.
 
 Accordingly, we used keyword searches of the scientific literature to create three citation networks themed around broad search terms.
-Within these disciplinary frameworks, we calculated expected values using a random graph model that accounted for existing citation frequencies and an efficient simulation algorithm that permitted a substantially greater number of simulations compared to Uzzi.
+Within these disciplinary frameworks, we calculated expected values using a random graph model that accounted for existing citation frequencies and an efficient Monte Carlo simulation algorithm that permitted a substantially greater number of simulations.
 We hypothesized that our approach would  reduce model misspecification and better simulate citation practice, in turn leading to different and more relevant conclusions.
@@
 Instead, we conclude that conventional thought as commonly defined in our study, 
-in \cite{uzzi_atypical_2013}, and  \cite{boyack_vs_uzzi_2014}, is more likely to drive higher citations..
- \emph{these are just filler conclusions that must be carefully rewritten and added to}.
+in \citep{uzzi_atypical_2013}, and  \citep{boyack_vs_uzzi_2014}, is more likely to drive higher citations..
+ \emph{these are just filler conclusions that must be carefully rewritten and added to- need Jim's conclusions to be stated here.}.
 
@@
 For the first two, rooted in biomedical research, we searched Pubmed for the term `immunology' or `metabolism' in the years 1985, 1995, and 2005.
-Pubmed IDs (pmids) returned were converted to WoS IDs (wos\_ids).
+Pubmed IDs (pmids) returned were matched to WoS IDs (wos\_ids) and used to retrieve relevant articles.
 For the applied physics dataset, we directly searched article level labels in WoS for `applied physics'.
 \\
-\emph{Normalization of observed and expected values} Building upon the work of Uzzi {\em et al.}, all ${n \choose 2}$ reference pairs were generated for each publication, where $n$ is the number of cited references in the publication.
+\emph{Normalization of observed and expected values} Building upon prior work~\cite{uzzi_atypical_2013}, all ${n \choose 2}$ reference pairs were generated for each publication, where $n$ is the number of cited references in the publication.
 These reference pairs were then mapped to the journals they were published in using ISSN numbers,  creating journal pairs.
@@
 \section{Results}
-
+\subsection{Chacko}
 (i) disciplinary networks are different
@@
 \acknowledgments
-We deeply thank Kevin Boyack and Dick Klavans for critically constructive discussions.
+We are grateful to Kevin Boyack and Dick Klavans for critically constructive discussions.
 We thank the authors of Uzzi et al.
@@
 All the code used in this study is freely available from a Github site.
-Access to bibliographic data requires a license from Clarivate Analytics, which had no role in
-funding, experimental design, review of results, and conclusions presented.
+Access to the bibliographic data analyzed in this study requires a license from Clarivate Analytics, which had no role in funding, experimental design, review of results, and conclusions presented.
 

### 2019-05-24 cocit_r.tex
update Section Chacko

@@
 \title[Co-citations in context]{Co-citations in context}
-\subtitle{Disciplinary heterogeneity is relevant}
+\subtitle{disciplinary heterogeneity is relevant}
 
@@
 \section{Results}
-\subsection{Chacko}
-(i) disciplinary networks are different
-(ii) background makes a difference
-(iii) 
-(iv)
+\subsection{Chacko} In our study, we also use a Monte Carlo approach to simulate under a random graph model.
+A  principal consideration, however, was to restrict model misspecification arising from disciplinarily irrelevant references.
+We addressed this consideration by restricting random substitutions to only those references in the disciplinary network being studied.
+We estimated model misspecification by measuring the Kullback-Leibler (K-L) Divergence~\citep{kullback_information_1951} between observed and simulated frequencies for the set of journals common to both a disciplinary network and the WoS superset (Table 3).
+The results indicate that simulations under our model consistently have a lower K-L divergence compared to simulations that draw from the WoS superset and its attendant substitutions that are ectopic with respect to field and discipline (Introduction).
+
+\begin{table}[ht]
+\caption{Measuring Model Misspecification. For the set of journal pairs in common between a disciplinary network and the full WoS dataset, Kullback-Leibler (K-L) divergences
+between empirical and simulated journal pair frequencies were computed for the years 1985, 1995, and 2005 for the three disciplinary datasets (applied\_physics, immunology, and metabolism) using either the disciplinary network as background or the WoS superset (all\_wos) to generate the null model (Background).
+K-L divergence was calculated using the R seewave package with a base (logarithm) of 2.
+The ratio between the K-L divergence for disciplinary networks versus the full WoS ranges from 1.96 to 2.77 and is greater than 2.0 for eight out of nine cases, strongly suggesting that simulations that constrain substitutions to the given disciplinary network better model the observed data.}
+\label{tab:label}
+\centering
+\begin{tabular}{|r lrlr r|}
+  \hline
+ & Disciplinary Network & Year & Background & K-L Divergence & Ratio \\ 
+  \hline
+1 & appl\_physics & 1985 & appl\_physics & 1.21 &  \\ 
+  2 &  & 1985 & all\_wos & 2.37 & 1.96 \\ 
+  3 &  & 1995 & appl\_physics & 0.86 &  \\ 
+  4 &  & 1995 & all\_wos & 2.37 & 2.77 \\ 
+  5 &  & 2005 & appl\_physics & 0.95 &  \\ 
+  6 &  & 2005 & all\_wos & 2.35 & 2.47 \\ 
+    \hline
+  7 & immunology & 1985 & immunology & 0.75 &  \\ 
+  8 &  & 1985 & all\_wos & 1.68 & 2.24 \\ 
+  9 &  & 1995 & immunology & 0.78 &  \\ 
+  10 &  & 1995 & all\_wos & 1.70 & 2.19 \\ 
+  11 &  & 2005 & immunology & 0.73 &  \\ 
+  12 &  & 2005 & all\_wos & 1.92 & 2.63 \\ 
+    \hline
+  13 & metabolism & 1985 & metabolism & 1.11 &  \\ 
+  14 &  & 1985 & all\_wos & 2.24 & 2.02 \\ 
+  15 &  & 1995 & metabolism & 1.07 &  \\ 
+  16 &  & 1995 & all\_wos & 2.33 & 2.17 \\ 
+  17 &  & 2005 & metabolism & 1.19 &  \\ 
+  18 &  & 2005 & all\_wos & 2.60 & 2.18 \\ 
+   \hline
+\end{tabular}
+\end{table}
+
+\begin{figure}
+\includegraphics[width=\hsize]{Fig1}
+\caption{Fraction of publications with high conventionality (HC) and high novelty (HN) signatures relative to citation count.}
+\end{figure}
 
@@
 \acknowledgments
-We are grateful to Kevin Boyack and Dick Klavans for critically constructive discussions.
+We are grateful to Kevin Boyack and Dick Klavans for constructively critical discussions.
 We thank the authors of Uzzi et al.

### 2019-05-24 cocit_r.tex
My updates

--- 2019-05-22 cocit_r.tex
@@
 Co-citation, the frequency with which pairs of publications are cited, provides insight into how documents relate to each other and across fields.
-Co-citation analysis has been used to characterize combinations of prior work as conventional or innovative and to deriveå features of highly cited publications.
+Co-citation analysis has been used to characterize combinations of prior work as conventional or innovative and to derive features of highly cited publications.
 Given the organization of science into disciplines, a key question is the sensitivity of such analyses to frame of reference.
 Our study examines this question using  semantically-themed citation networks.
-We observe that trends reported to be true across the scientific literature do not hold for focused citation networks, and conclude that co-citation analysis requires a contextual perspective.
+We observe that trends reported to be true across the scientific literature do not hold for focused citation networks, and we conclude that co-citation analysis requires a contextual perspective.
 \end{abstract}
@@
 Citation and network analysis of  scientific literature reveals information on semantic relationships between publications, collaboration between scientists, and the practice of citation itself~\citep{garfield_citation_1955,de_solla_price_networks_1965,newman_structure_2001,Shi:2010:CHI:1816123.1816131,patience_pmid28560354}.
-Co-citation, the frequency with which two documents are cited together in other documents provides additional insights, including the identification of semantically related documents, fields, idea, and specialization in science~\citep{small_co-citation_1973,marshakova-shaikevich_co-citation_1973,boyack_co-citation_2010}.
+Co-citation, the frequency with which two documents are cited together in other documents provides additional insights, including the identification of semantically related documents, fields, ideas, and specializations in science~\citep{small_co-citation_1973,marshakova-shaikevich_co-citation_1973,boyack_co-citation_2010}.
 
@@
 These normalized journal pair frequencies were termed \emph{z-scores} (Materials and Methods).
-Thus, every article was associated with multiple z-scores.
-For each article, positional statistics of these z-scores were calculated to describe conventionality: high conventionality (HC) if the median z-score for an article was greater than the median of median z-scores of all articles and low conventionality for the inverse (LC).
-Similarly,  an article was deemed to have high novelty (HN) if the tenth percentile of its z-scores  was negative and low novelty (LN) for the inverse.
+Thus, every article was associated with multiple z-scores corresponding with the journal pairs represented by its citations.
+For each article, positional statistics of these z-scores were calculated to describe conventionality: high conventionality (HC) if the median z-score for an article was greater than the median of median z-scores of all articles and low conventionality for the converse (LC).
+Similarly,  an article was deemed to have high novelty (HN) if the tenth percentile of its z-scores  was negative and low novelty (LN) for the converse.
 Accordingly, each article was labeled with respect to conventionality and novelty, e.g, HCHN (denoting that the article exhibits high conventionality and high novelty), with all four combinations being possible.
-\citep{uzzi_atypical_2013} observed that HCHN articles were twice as likely to be found in highly cited papers, suggesting that novel combinations of ideas flavoring a body of conventional thought were a recipe for impact across the scientific literature.
+\citep{uzzi_atypical_2013} observed that HCHN articles were twice as likely to be highly cited, suggesting that novel combinations of ideas flavoring a body of conventional thought were a recipe for impact across the scientific literature.
 
@@
 Such substitutions poorly model documented citation behavior~\citep{wallace_lariviere_gingras_2012,moed_measuring_2010,klavans_research_2017,garfield_1979}.
-In addition, under this random model,  a reference cited over 100 times in a given year is selected with the same probability as a reference cited only once, which is inconsistent with the frequency distribution of citations characterized as power law or lognormal~\citep{stringer_statistical_2010,perline_strong_2005}.
+(Possibly insert reference to Sitaram's investigation here.) In addition, under this random model,  a reference cited over 100 times in a given year is selected with the same probability as a reference cited only once, which is inconsistent with the actual frequency of citation and also the power law or lognormal distributions observed in citations ~\citep{stringer_statistical_2010,perline_strong_2005}.
 Accordingly, the expected value calculations generated by the \citep{uzzi_atypical_2013} simulations and used in characterizing journal pairs in terms of conventionality and novelty  can be reasonably questioned on grounds of model mis-specification.
@@
 A follow-up study by \citep{boyack_vs_uzzi_2014} explored the impact of discipline and journal effects on the definition of conventionality and novelty.
-While their study had some methodological differences from \citep{uzzi_atypical_2013} in the use of Scopus data and a $\chi^2$ calculation for expected values, Boyack and Klavans find the same basic trend that HCHN is more probably in highly cited papers.
+While their study had some methodological differences from \citep{uzzi_atypical_2013} in the use of Scopus data and a $\chi^2$ calculation for the expected number of journal pair citations, Boyack and Klavans find the same basic trend that HCHN is more probably in highly cited papers.
 However, they note that ``only 64.4\%  of  243  WoS  subject  categories'' in the Uzzi {\em et al.} study met the criterion of having the highest probability of hit papers in the HCHN category.
@@
 Despite different methods used to generate expected values, both \citep{uzzi_atypical_2013} and \citep{boyack_vs_uzzi_2014}  measured observed frequencies across the scientific literature without disciplinary constraints and subsequently used normalized frequencies to examine disciplinary subsets.
-In contrast, we chose instead to first construct semantically related sets of documents (disciplinary networks) to and measure observed and expected frequencies within these networks.
+In contrast, we chose instead to first construct semantically related sets of documents (disciplinary networks) and to measure observed and expected frequencies within these networks.
+(or cite Sitaram's statistics here so as to add specificity to this sentence, which could have this appended to it: ``consistent with researchers' patterns of citing predominantly work from their own field.
+This doesn't preclude citations from outside of the discipline of focus, but constrains the random substitutions to more plausibly related literature.'')
 
@@
 Instead, we conclude that conventional thought as commonly defined in our study, 
-in \citep{uzzi_atypical_2013}, and  \citep{boyack_vs_uzzi_2014}, is more likely to drive higher citations..
+in \citep{uzzi_atypical_2013}, and  \citep{boyack_vs_uzzi_2014}, is more likely to drive higher citations (in the disciplinary networks we studied).
  \emph{these are just filler conclusions that must be carefully rewritten and added to- need Jim's conclusions to be stated here.}.
@@
 WoS data stored in ERNIE spans the period 1900-2019 and consists of over 72 million publications.
-For this study, we generated an analytical dataset from years 1985 to 2005.
+For this study, we generated an analytical dataset from years 1985 to 2005 from ERNIE.
 The total number of publications in this dataset was just over 25 million publications (25,134,073).
@@
 Where multiple ISSN numbers exist for a journal, the most frequently used one in the WoS was assigned to the journal.
-In addition, publications containing less than two references were discarded.
+In addition, publications containing fewer than two references were discarded.
 Journal pair frequencies were summed up across the dataset to create observed frequencies $(F_{obs})$.
@@
  is the standard deviation of the frequencies generated by simulation.
-As a result of these calculations, each publication becomes associated with a set of z-scores corresponding to the journal pairs derived from pairwise combinations of its cited references and positional statistics (quantiles) of z-scores were calculated for each publication.
+(Do we need a comment here that while we are using the term z-score, we do not imply that these are related to a normal distribution.
+Rather, we are using the terminology from Uzzi et al.) As a result of these calculations, each publication becomes associated with a set of z-scores corresponding to the journal pairs derived from pairwise combinations of its cited references and positional statistics (quantiles) of z-scores were calculated for each publication.
 Publications were also labeled according to conventionality and novelty.
@@
 LN if the tenth percentile of z-scores for a publication was greater than zero.
+
+We investigated multiple definitions of hit articles, as did Uzzi et al., with hits defined as the 1\%, 2\%, 5\%, and 10\% top-cited articles.
+Do we want to report on the percentile being used for novelty at both the 1 and 10th percentile, or just focus on the 10th percentile?
 
@@
 
+\subsection{Bradley}
+Figure \ref{fig:scatter} shows that the z-scores for the same journal pair can be positive (negative) when computed with respect to one data set but be negative (positive) for another data set.
+The journal-pair z-scores in Figure \ref{fig:scatter} have consistent signs for both Immunology and WoS data sets in 71.4\% of the instances and different signs for 28.6\% of the journal pairs.
+A negative journal pair z-score in one context increases the likelihood that articles citing it will be deemed to be novel while articles citing it in another context, where the journal pair z-score is positive, are less likely to be classified as novel and possibly more likely to be classified as conventional.
+Figure \ref{fig:scatter} reflects that the WoS data set has approximately 44,000 fewer negative z-scores than does the immunology data set, which contributes to its significantly lower percentage of high-novelty articles as shown in Figure \ref{fig:scatter}.
+
+\begin{figure}%[tbhp]
+\centering
+\includegraphics[width=3in]{fig2_scatter_z_scores_flattened.pdf}     %width=.8\linewidth
+\caption{Journal pair z-scores vary with reference dataset.
+Scatter plot points (319,005) indicate journal pair z-scores for the 1995 Immunology dataset along the x-axis and the 1995 Web of Science dataset on the y-axis.
+Black indicates journal pairs whose z-scores have the same sign when computed for both reference datasets while red points indicate the 28.6\% of journal pairs whose z-scores change sign across datasets.
+Regions with deeper hues indicate higher point densities and the histograms show the marginal distributions for each dataset separately.}
+\label{fig:scatter}
+\end{figure}
+
+%\begin{figure*}
+%\begin{tabular}{ccc}
+%\includegraphics[width=2.1in]{SIDoc/figs/scatter_z_scores_metab85_WoS_ZoomIn.pdf} & \includegraphics[width=2.1in]{Fig2H01N10.pdf} & \includegraphics[width=2.1in]{Fig2H05N10.pdf} \\
+%(a) & (b) & (c) \\
+%\end{tabular}
+%\caption{Scatter plot points show journal pair z-scores with respect to the Immunology data set for 1995 on the x-axis and the broad Web of Science on the y-axis.
+Black indicates journal pairs whose z-scores have the same sign when computed for both data sets while red points indicate journal pairs whose z-scores change sign across data sets.
+Regions with deeper hues indicate higher point density.
+The histograms show the marginal distributions of the z-scores for each of the data sets separately.}
+%\label{fig:Fig2}
+%\end{figure*}
+
+\begin{figure*}
+\centering
+\begin{tabular}{ccc}
+\includegraphics[width=1.5in]{Fig2H01N10.pdf} & \includegraphics[width=1.5in]{Fig2H10N10.pdf} \\
+(a) & (b) \\
+\end{tabular}
+\caption{Effect of Context on Journal-Pair z-scores and Categorical Hit Rates: Immunology, Applied Physics, and WoS for 1995.
+Panels (a) and (b) show hit rates for the LNLC, LNHC, HNLC, and HNHC categories for the immunology, applied physics, and WoS datasets when hit articles are defined as the top 1\% and top 10\% of articles, respectively.
+Novelty in both panels is defined at the 10th percentile of articles' z-score distributions.
+The number of data points in the immunology, applied physics, and WoS data sets are 21,917, 18,305, and 476,288, respectively.
+The results for the WoS data set mirrored previous results from Uzzi et al.
+~\cite{uzzi_atypical_2013} where the highest hit rate was for the HNHC category.
+The highest hit rates for the immunology dataset, in contrast, are in the LNHC category.
+The LNHC category often had the highest hit rate for the immunology dataset for various parameter settings with the HCHN category having the highest hit rate in other cases: metabolism results are similar.
+The applied physics dataset shows further contrast as the hit rate for it was highest in the HNLC category.
+The HNLC category demonstrated the highest hit rate often for applied physics: otherwise the highest hit rate was for HNHC articles.}
+\label{fig:Fig2}
+\end{figure*}
+
+\begin{table}%[tbhp]
+\centering
+\caption[Hit Rates]{Hit Rates by Category. The last four columns indicate the proportion of publications that are hits for each respective category.} \label{Tab:HitRate}
+\begin{tabular}{crrrrrrr}
+& \multicolumn{1}{c}{Hits as \%} & \multicolumn{1}{c}{Novelty}  &  &  &  &  \\ Data Set & \multicolumn{1}{c}{of Articles} & \multicolumn{1}{c}{Percentile} & \multicolumn{1}{c}{LNLC} & \multicolumn{1}{c}{LNHC} & \multicolumn{1}{c}{HNLC} & \multicolumn{1}{c}{HNHC} \\ \hline
+
+Imm95&1\%&10\%& 0.000& 0.019& 0.005& 0.014 \\ 
+Imm95&10\%&10\%& 0.017& 0.128& 0.076& 0.129 \\ 
+Metab95&1\%&10\%& 0.001& 0.017& 0.006& 0.014 \\ 
+Metab95&10\%&10\%& 0.019& 0.130& 0.074& 0.133 \\ 
+AP95&1\%&10\%& 0.002& 0.007& 0.012& 0.010 \\ 
+AP95&10\%&10\%& 0.047& 0.079& 0.123& 0.109 \\ 
+WoS95&1\%&10\%& 0.004& 0.013& 0.009& 0.017 \\ 
+WoS95&10\%&10\%& 0.056& 0.115& 0.104& 0.156 \\ \hline
+
+\end{tabular}
+\end{table}
+
+Figure \ref{fig:Fig2}, Panels (a) and (b), compares hit rates for the four categories among the Immunology, Applied Physics, and WoS datasets for 1995: the hit rate is defined as the number of hit articles in each category divided by the number of articles in the category.
+We evaluated the statistical significance of the categorical hit rates using multiple methods, some of which we describe here.
+Our first test was based on the null hypotheses that hits were distributed randomly among the four categories with uniform probability in proportion to the number of articles in each category.
+Using a Chi-Square Goodness of Fit test, rejecting the null hypothesis in favor of the alternate hypothesis supports a non-uniform dispersion of hits: that is, some of the four categories are individually associated with higher than expected, or lower than expected hit rates.
+The null hypothesis was rejected at a $p<0.001$ in all cases in  Figure \ref{fig:Fig2}, with the exception of the immunology and applied datasets where hit articles are designated as the top 1\% of articles: valid tests were not possible in those instances due to too few expected hits.
+The null hypothesis was rejected with $p<0.001$ for all valid tests for all parameter settings, all datasets, and all years: hypotheses tests were valid in 73 of 96 instances.
+We conclude that it is likely that the distribution of hits among categories is not uniform but, rather, hit rates vary among the categories in all datasets.
+(Should we insert a table with all statistical results?)
+
+We computed hit rates for the WoS dataset, which mirrored Uzzi et al.'s results whereby the largest hit rates were for the HNHC category, despite our methodological improvement of sampling citations in proportion to their frequency.
+We found contrary results in the 1995 immunology dataset where articles in the LNHC category often had the greatest hit rates, as reflected in Table \ref{Tab:HitRate} and Figure \ref{fig:Fig2}.
+Across all year's data, all datasets, and all parameter settings, the highest hit rates in the immunology datasets were sometimes in the LNHC category and sometimes in the HNHC category.
+The metabolism hit rates reflected this same pattern.
+The greatest hit rates for the applied physics data were often in the HNLC category as reflected in Table \ref{Tab:HitRate} and Figure \ref{fig:Fig2}, and otherwise in the HNHC category.
+We conclude that Uzzi et al.'s finding of high hit rates in the HNHC category does not hold generally for disciplinary-based datasets and that novel citation patterns are not always indicative of impactful research, as was the case with immunology.
+Furthermore, the categories displaying the greatest hit rate vary with parameter settings and with the year.
+The lack of stable results across parameter settings suggests that parameters must be selected judiciously.
+
+We also tested the explanatory power of each framework dimension by classifying articles as Low Novelty (LN) or High Novelty (HN) and, separately, as having Low Conventionality (LC) or High Conventionality (HC).
+We tested the null hypothesis that hits are distributed between LN and HN (LC and HC) in proportion to the total number of articles assigned to those categories.
+That null hypothesis was rejected for the WoS data along both dimensions.
+Consistent with previous analysis, hit articles were overrepresented in the HC category in every instance of WoS data at a $p<0.001$ and hit articles were overrepresented in the HN category at a $p<0.001$ in all but two cases.
+The p-values, in those cases, were 0.002 and 0.007.
+Hits in the immunology and metabolism data were overrepresented in the HC category with the same statistical significance as for WoS.
+The relationship of novelty with hits in the immunology and metabolism data differed dramatically from the WoS, however, with statistically significant findings of hit articles being sometimes overrepresented in the LN category, and sometimes being underrepresented.
+Of the 12 tests for applied physics, the statistical significance supporting a positive relationship between hit articles and HN were all $p<0.10$, and 10 of 12 were $p<0.05$.
+These tests also indicated strong support for the relationship between LN and hit articles in applied physics in a limited number of tests, with $p<0.10$ in 5 of 12 instances and $p < 0.05$ in 3 of 12 instances.
+These results suggest that (1) both conventionality and novelty are strongly related to hits in the WoS, (2) the conventionality dimension is strongly related with hits in immunology and metabolism and novelty is not, (3) novelty is more strongly related with hits in applied physics than is conventionality.
+More generally, we find that the dimensions most strongly related with hit articles vary across disciplines and between disciplinary and broad data sets.
+
 \section{Discussion}
+
+We conclude that Uzzi et al.'s finding of high hit rates in the HNHC category does not hold generally for all datasets and that novel citation patterns are not always indicative of impactful research.
+
+The z-scores that change sign across datasets is either contradictory or an acceptable variation due to the difference in reference sets.
+We contend that it is the former because the inappropriate substitution of citations with those from disciplines that are implausible and because the observed citation frequencies are ignored.
+That fewer z-scores are negative in the WoS dataset relative to the immunology dataset may be directly due to the uniform sampling of references whereby many resulting journal pairs are never observed in the literature and so that the expected frequencies of those observed pairs have lower expected values, thus biasing their z-scores upward.
+In addition, treating citation as a set versus a multiset means that a random model will sample popular citations downward, thus further increasing their z-scores.
+
+Contrary to Uzzi et al.
+we found the category displaying the highest hit rate to be sensitive to the experimental parameter settings, which included the percentage of articles deemed to be hits and the percentile of articles' z-score distributions that delineated between articles of low novelty and high novelty.
+Thus, with this lack of robustness, studies are faced with the necessity of defining which parameters are the best parameters to classify articles.
 

### 2019-05-26 cocit_r.tex
more edits

--- 2019-05-24 cocit_r.tex
@@
 Citation and network analysis of  scientific literature reveals information on semantic relationships between publications, collaboration between scientists, and the practice of citation itself~\citep{garfield_citation_1955,de_solla_price_networks_1965,newman_structure_2001,Shi:2010:CHI:1816123.1816131,patience_pmid28560354}.
-Co-citation, the frequency with which two documents are cited together in other documents provides additional insights, including the identification of semantically related documents, fields, idea, and specialization in science~\citep{small_co-citation_1973,marshakova-shaikevich_co-citation_1973,boyack_co-citation_2010}.
+Co-citation, the frequency with which two documents are cited together in other documents provides additional insights, including the identification of semantically related documents, fields, idea, and specialization in science~\citep{small_co-citation_1973,marshakova-shaikevich_co-citation_1973,boyack_co-citation_2010, 10.3389/frma.2018.00020}.
 
-\citep{uzzi_atypical_2013} used a novel approach for co-citation analysis of 17.9 million articles and their cited references from the Web of Science (WoS)  to characterize a subset of highly cited articles with respect to both novel and conventional combinations of prior research.
+\cite{uzzi_atypical_2013} used a novel approach for co-citation analysis of 17.9 million articles and their cited references from the Web of Science (WoS)  to characterize a subset of highly cited articles with respect to both novel and conventional combinations of prior research.
 Observed co-citation frequencies, mapped to journals, were computed across the dataset and normalized (shifted and scaled) to expected values generated by Monte Carlo simulations under a random graph model.
@@
 Similarly,  an article was deemed to have high novelty (HN) if the tenth percentile of its z-scores  was negative and low novelty (LN) for the inverse.
-Accordingly, each article was labeled with respect to conventionality and novelty, e.g, HCHN (denoting that the article exhibits high conventionality and high novelty), with all four combinations being possible.
+Accordingly, each article was labeled with respect to conventionality and novelty, e.g, HCHN (denoting that the article exhibits both high conventionality and high novelty), with all four combinations being possible.
 \citep{uzzi_atypical_2013} observed that HCHN articles were twice as likely to be found in highly cited papers, suggesting that novel combinations of ideas flavoring a body of conventional thought were a recipe for impact across the scientific literature.
@@
 Key to Uzzi {\em et al.}, however, is their random graph model and its underlying assumptions.
-A careful examination of the model (as defined by the Monte Carlo simulation) reveals that all substitutions of references are equiprobable, which means that a reference in an article can be substituted by any other reference randomly chosen from those published in the same year, irrespective of subject matter and citation count.
+A careful examination of the model (as defined by the Monte Carlo simulation) reveals that random substitutions of references used to generate expected values are equiprobable, which means that a reference in an article can be substituted by any other reference randomly chosen from those published in the same year, irrespective of disciplinary focus and citation count.
 For example, the model permits substitution of a reference in quantum physics with equal probability by a reference in classical literature, evolutionary biology, or anthropology.
@@
 In addition, under this random model,  a reference cited over 100 times in a given year is selected with the same probability as a reference cited only once, which is inconsistent with the frequency distribution of citations characterized as power law or lognormal~\citep{stringer_statistical_2010,perline_strong_2005}.
+Lastly, while the citation switching algorithm used in Uzzi preserves the number of publications and the number of references in each publication, it does not preserve the disciplinary proportions of cited references within the network.
 Accordingly, the expected value calculations generated by the \citep{uzzi_atypical_2013} simulations and used in characterizing journal pairs in terms of conventionality and novelty  can be reasonably questioned on grounds of model mis-specification.
@@
 Despite different methods used to generate expected values, both \citep{uzzi_atypical_2013} and \citep{boyack_vs_uzzi_2014}  measured observed frequencies across the scientific literature without disciplinary constraints and subsequently used normalized frequencies to examine disciplinary subsets.
-In contrast, we chose instead to first construct semantically related sets of documents (disciplinary networks) to and measure observed and expected frequencies within these networks.
+In contrast, we chose to consider disciplinary organization in science by first constructing semantically related sets of documents (disciplinary networks) and then measuring observed and expected frequencies within these networks.
 
 Accordingly, we used keyword searches of the scientific literature to create three citation networks themed around broad search terms.
-Within these disciplinary frameworks, we calculated expected values using a random graph model that accounted for existing citation frequencies and an efficient Monte Carlo simulation algorithm that permitted a substantially greater number of simulations.
+Within these disciplinary frameworks, we calculated expected values using a random graph model that accounted for existing citation frequencies and an efficient Monte Carlo simulation algorithm that permitted a substantially greater number of simulations while preserving the number of publications, references, and disciplinary proportions in the network.
 We hypothesized that our approach would  reduce model misspecification and better simulate citation practice, in turn leading to different and more relevant conclusions.
@@
 Pubmed IDs (pmids) returned were matched to WoS IDs (wos\_ids) and used to retrieve relevant articles.
-For the applied physics dataset, we directly searched article level labels in WoS for `applied physics'.
+For the applied physics dataset, we directly searched subject labels in WoS for `applied physics'.
 \\
 \emph{Normalization of observed and expected values} Building upon prior work~\cite{uzzi_atypical_2013}, all ${n \choose 2}$ reference pairs were generated for each publication, where $n$ is the number of cited references in the publication.
-These reference pairs were then mapped to the journals they were published in using ISSN numbers,  creating journal pairs.
+These reference pairs were then mapped to the journals they were published in using ISSN numbers, to create journal pairs.
 Where multiple ISSN numbers exist for a journal, the most frequently used one in the WoS was assigned to the journal.
@@
 Journal pair frequencies were summed up across the dataset to create observed frequencies $(F_{obs})$.
-In contrast to the preceding study~\citep{uzzi_atypical_2013}, we generated 1,000 rather than 10 null models for each dataset by randomly shuffling references while preserving the number of publications, the number of references in each publication, and the frequency with which these references were cited within the year of interest.
-Expected values $(F_{exp})$ were generated by averaging the result of 1,000 simulations.
+Null models were created by randomly shuffling references while preserving the number of publications, the number of references in each publication, and the frequency with which these references were cited within the year of interest.
+In contrast to the preceding study~\citep{uzzi_atypical_2013}, we generated 1,000 rather than 10 null models for each dataset.
+Expected values $(F_{exp})$ for journal pairs were generated by averaging the result of 1,000 simulations.
 z-scores were calculated for each journal-pair using the formula $(F_{obs} - F_{exp})/\sigma$ where $\sigma$

### 2019-05-27 cocit_r.tex
edited author contributions

@@
 \authorcontributions 
-This study was designed by GD, JB, SD, and TW.
+This study was designed by GC, JB, SD, and TW.
 Simulations and analysis were performed by AD, GC, JB, and SD.
-Infrastructure, and workflows used to generate data used in this study were developed by AD, DK, SL, SD, and GC.
+Infrastructure and workflows used to generate data used in this study were developed by AD, DK, SL, SD, and GC.
 All authors reviewed and commented on the manuscript, which was written by GC, JB, and TW.

### 2019-05-28 cocit_r.tex
edited introduction -- most changes were to correct citep{} to cite{}.

@@
 Accordingly, each article was labeled with respect to conventionality and novelty, e.g, HCHN (denoting that the article exhibits both high conventionality and high novelty), with all four combinations being possible.
-\citep{uzzi_atypical_2013} observed that HCHN articles were twice as likely to be found in highly cited papers, suggesting that novel combinations of ideas flavoring a body of conventional thought were a recipe for impact across the scientific literature.
+\cite{uzzi_atypical_2013} observed that HCHN articles were twice as likely to be found in highly cited papers, suggesting that novel combinations of ideas flavoring a body of conventional thought were a recipe for impact across the scientific literature.
 
@@
 A careful examination of the model (as defined by the Monte Carlo simulation) reveals that random substitutions of references used to generate expected values are equiprobable, which means that a reference in an article can be substituted by any other reference randomly chosen from those published in the same year, irrespective of disciplinary focus and citation count.
-For example, the model permits substitution of a reference in quantum physics with equal probability by a reference in classical literature, evolutionary biology, or anthropology.
+For example, the model permits substitution of a reference in quantum physics with equal probability by a reference in quantum biology (i.e., the same field) or in some entirely different field, such as classical literature, evolutionary biology, or anthropology.
 Such substitutions poorly model documented citation behavior~\citep{wallace_lariviere_gingras_2012,moed_measuring_2010,klavans_research_2017,garfield_1979}.
 In addition, under this random model,  a reference cited over 100 times in a given year is selected with the same probability as a reference cited only once, which is inconsistent with the frequency distribution of citations characterized as power law or lognormal~\citep{stringer_statistical_2010,perline_strong_2005}.
-Lastly, while the citation switching algorithm used in Uzzi preserves the number of publications and the number of references in each publication, it does not preserve the disciplinary proportions of cited references within the network.
-Accordingly, the expected value calculations generated by the \citep{uzzi_atypical_2013} simulations and used in characterizing journal pairs in terms of conventionality and novelty  can be reasonably questioned on grounds of model mis-specification.
+Lastly,  as we will show here, while the citation switching algorithm used in Uzzi  {\em et al.} preserves the number of publications and the number of references in each publication, it does not preserve the disciplinary proportions of cited references within the network.
+ Accordingly, the expected value calculations generated by the \cite{uzzi_atypical_2013} simulations and used in characterizing journal pairs in terms of conventionality and novelty  can be reasonably questioned on grounds of model mis-specification.
 
-A follow-up study by \citep{boyack_vs_uzzi_2014}  explored the impact of discipline and journal effects on the definition of conventionality and novelty.
-While their study had some methodological differences from \citep{uzzi_atypical_2013} in the use of Scopus data and a $\chi^2$ calculation for expected values, Boyack and Klavans find the same basic trend that HCHN is more probably in highly cited papers.
+A follow-up study by \cite{boyack_vs_uzzi_2014}  explored the impact of discipline and journal effects on the definition of conventionality and novelty.
+While their study had some methodological differences from \cite{uzzi_atypical_2013} in the use of Scopus data and a $\chi^2$ calculation for expected values, Boyack and Klavans find the same basic trend that HCHN is more probable in highly cited papers.
 However, they note that ``only 64.4\%  of  243  WoS  subject  categories'' in the Uzzi {\em et al.} study met the criterion of having the highest probability of hit papers in the HCHN category.
@@
 
-Despite different methods used to generate expected values, both \citep{uzzi_atypical_2013} and \citep{boyack_vs_uzzi_2014}  measured observed frequencies across the scientific literature without disciplinary constraints and subsequently used normalized frequencies to examine disciplinary subsets.
-In contrast, we chose to consider disciplinary organization in science by first constructing semantically related sets of documents (disciplinary networks) and then measuring observed and expected frequencies within these networks.
+Despite different methods used to generate expected values, both \cite{uzzi_atypical_2013} and \cite{boyack_vs_uzzi_2014}  measured observed co-citation frequencies across the scientific literature without disciplinary constraints and subsequently used normalized frequencies to examine disciplinary subsets.
+In contrast, we chose to consider disciplinary organization in science by first constructing semantically related sets of documents (disciplinary networks) and then measuring observed and expected co-citation frequencies within these networks.
 
@@
 Instead, we conclude that conventional thought as commonly defined in our study,
-in \citep{uzzi_atypical_2013}, and  \citep{boyack_vs_uzzi_2014}, is more likely to drive higher citations..
+in \cite{uzzi_atypical_2013}, and  \cite{boyack_vs_uzzi_2014}, is more likely to drive higher citations..
  \emph{these are just filler conclusions that must be carefully rewritten and added to- need Jim's conclusions to be stated here.}.

### 2019-05-28 cocit_r.tex
Update cocit_r.tex

--- 2019-05-26 cocit_r.tex
@@
 Citation and network analysis of  scientific literature reveals information on semantic relationships between publications, collaboration between scientists, and the practice of citation itself~\citep{garfield_citation_1955,de_solla_price_networks_1965,newman_structure_2001,Shi:2010:CHI:1816123.1816131,patience_pmid28560354}.
-Co-citation, the frequency with which two documents are cited together in other documents provides additional insights, including the identification of semantically related documents, fields, idea, and specialization in science~\citep{small_co-citation_1973,marshakova-shaikevich_co-citation_1973,boyack_co-citation_2010, 10.3389/frma.2018.00020}.
+Co-citation, the frequency with which two documents are cited together in other documents provides additional insights, including the identification of semantically related documents, fields, ideas, and specializations in science~\citep{small_co-citation_1973,marshakova-shaikevich_co-citation_1973,boyack_co-citation_2010}.
 
-\cite{uzzi_atypical_2013} used a novel approach for co-citation analysis of 17.9 million articles and their cited references from the Web of Science (WoS)  to characterize a subset of highly cited articles with respect to both novel and conventional combinations of prior research.
+\citep{uzzi_atypical_2013} used a novel approach for co-citation analysis of 17.9 million articles and their cited references from the Web of Science (WoS)  to characterize a subset of highly cited articles with respect to both novel and conventional combinations of prior research.
 Observed co-citation frequencies, mapped to journals, were computed across the dataset and normalized (shifted and scaled) to expected values generated by Monte Carlo simulations under a random graph model.
 These normalized journal pair frequencies were termed \emph{z-scores} (Materials and Methods).
-Thus, every article was associated with multiple z-scores.
-For each article, positional statistics of these z-scores were calculated to describe conventionality: high conventionality (HC) if the median z-score for an article was greater than the median of median z-scores of all articles and low conventionality for the inverse (LC).
-Similarly,  an article was deemed to have high novelty (HN) if the tenth percentile of its z-scores  was negative and low novelty (LN) for the inverse.
-Accordingly, each article was labeled with respect to conventionality and novelty, e.g, HCHN (denoting that the article exhibits both high conventionality and high novelty), with all four combinations being possible.
-\citep{uzzi_atypical_2013} observed that HCHN articles were twice as likely to be found in highly cited papers, suggesting that novel combinations of ideas flavoring a body of conventional thought were a recipe for impact across the scientific literature.
+Thus, every article was associated with multiple z-scores corresponding with the journal pairs represented by its citations.
+For each article, positional statistics of these z-scores were calculated to describe conventionality: high conventionality (HC) if the median z-score for an article was greater than the median of median z-scores of all articles and low conventionality for the converse (LC).
+Similarly,  an article was deemed to have high novelty (HN) if the tenth percentile of its z-scores  was negative and low novelty (LN) for the converse.
+Accordingly, each article was labeled with respect to conventionality and novelty, e.g, HCHN (denoting that the article exhibits high conventionality and high novelty), with all four combinations being possible.
+\citep{uzzi_atypical_2013} observed that HCHN articles were twice as likely to be highly cited, suggesting that novel combinations of ideas flavoring a body of conventional thought were a recipe for impact across the scientific literature.
 
 Key to Uzzi {\em et al.}, however, is their random graph model and its underlying assumptions.
-A careful examination of the model (as defined by the Monte Carlo simulation) reveals that random substitutions of references used to generate expected values are equiprobable, which means that a reference in an article can be substituted by any other reference randomly chosen from those published in the same year, irrespective of disciplinary focus and citation count.
+A careful examination of the model (as defined by the Monte Carlo simulation) reveals that all substitutions of references are equiprobable, which means that a reference in an article can be substituted by any other reference randomly chosen from those published in the same year, irrespective of subject matter and citation count.
 For example, the model permits substitution of a reference in quantum physics with equal probability by a reference in classical literature, evolutionary biology, or anthropology.
 Such substitutions poorly model documented citation behavior~\citep{wallace_lariviere_gingras_2012,moed_measuring_2010,klavans_research_2017,garfield_1979}.
-In addition, under this random model,  a reference cited over 100 times in a given year is selected with the same probability as a reference cited only once, which is inconsistent with the frequency distribution of citations characterized as power law or lognormal~\citep{stringer_statistical_2010,perline_strong_2005}.
-Lastly, while the citation switching algorithm used in Uzzi preserves the number of publications and the number of references in each publication, it does not preserve the disciplinary proportions of cited references within the network.
+(Possibly insert reference to Sitaram's investigation here.) In addition, under this random model,  a reference cited over 100 times in a given year is selected with the same probability as a reference cited only once, which is inconsistent with the actual frequency of citation and also the power law or lognormal distributions observed in citations ~\citep{stringer_statistical_2010,perline_strong_2005}.
 Accordingly, the expected value calculations generated by the \citep{uzzi_atypical_2013} simulations and used in characterizing journal pairs in terms of conventionality and novelty  can be reasonably questioned on grounds of model mis-specification.
@@
 Despite different methods used to generate expected values, both \citep{uzzi_atypical_2013} and \citep{boyack_vs_uzzi_2014}  measured observed frequencies across the scientific literature without disciplinary constraints and subsequently used normalized frequencies to examine disciplinary subsets.
-In contrast, we chose to consider disciplinary organization in science by first constructing semantically related sets of documents (disciplinary networks) and then measuring observed and expected frequencies within these networks.
+In contrast, we chose instead to first construct semantically related sets of documents (disciplinary networks) and to measure observed and expected frequencies within these networks.
+(or cite Sitaram's statistics here so as to add specificity to this sentence, which could have this appended to it: ``consistent with researchers' patterns of citing predominantly work from their own field.
+This doesn't preclude citations from outside of the discipline of focus, but constrains the random substitutions to more plausibly related literature.'')
 
 Accordingly, we used keyword searches of the scientific literature to create three citation networks themed around broad search terms.
-Within these disciplinary frameworks, we calculated expected values using a random graph model that accounted for existing citation frequencies and an efficient Monte Carlo simulation algorithm that permitted a substantially greater number of simulations while preserving the number of publications, references, and disciplinary proportions in the network.
+Within these disciplinary frameworks, we calculated expected values using a random graph model that accounted for existing citation frequencies and an efficient Monte Carlo simulation algorithm that permitted a substantially greater number of simulations.
 We hypothesized that our approach would  reduce model misspecification and better simulate citation practice, in turn leading to different and more relevant conclusions.
@@
 Pubmed IDs (pmids) returned were matched to WoS IDs (wos\_ids) and used to retrieve relevant articles.
-For the applied physics dataset, we directly searched subject labels in WoS for `applied physics'.
+For the applied physics dataset, we directly searched article level labels in WoS for `applied physics'.
 \\
 \emph{Normalization of observed and expected values} Building upon prior work~\cite{uzzi_atypical_2013}, all ${n \choose 2}$ reference pairs were generated for each publication, where $n$ is the number of cited references in the publication.
-These reference pairs were then mapped to the journals they were published in using ISSN numbers, to create journal pairs.
+These reference pairs were then mapped to the journals they were published in using ISSN numbers,  creating journal pairs.
 Where multiple ISSN numbers exist for a journal, the most frequently used one in the WoS was assigned to the journal.
-In addition, publications containing less than two references were discarded.
+In addition, publications containing fewer than two references were discarded.
 Journal pair frequencies were summed up across the dataset to create observed frequencies $(F_{obs})$.
-Null models were created by randomly shuffling references while preserving the number of publications, the number of references in each publication, and the frequency with which these references were cited within the year of interest.
-In contrast to the preceding study~\citep{uzzi_atypical_2013}, we generated 1,000 rather than 10 null models for each dataset.
-Expected values $(F_{exp})$ for journal pairs were generated by averaging the result of 1,000 simulations.
-z-scores were calculated for each journal-pair using the formula $(F_{obs} - F_{exp})/\sigma$ where $\sigma$
- is the standard deviation of the frequencies generated by simulation.
-As a result of these calculations, each publication becomes associated with a set of z-scores corresponding to the journal pairs derived from pairwise combinations of its cited references and positional statistics (quantiles) of z-scores were calculated for each publication.
+In contrast to the preceding study~\citep{uzzi_atypical_2013}, we generated 1,000 rather than 10 null models for each dataset by randomly shuffling references while preserving the number of publications, the number of references in each publication, and the frequency with which these references were cited within the year of interest.
+Expected values $(F_{exp})$ were generated by averaging the result of 1,000 simulations.
+z-scores were calculated for each journal-pair using the formula $(F_{obs} - F_{exp})/\sigma$ where $\sigma$  is the standard deviation of the frequencies generated by simulation.
+(Do we need a comment here that while we are using the term z-score, we do not imply that these are related to a normal distribution.
+Rather, we are using the terminology from Uzzi et al.) As a result of these calculations, each publication becomes associated with a set of z-scores corresponding to the journal pairs derived from pairwise combinations of its cited references and positional statistics (quantiles) of z-scores were calculated for each publication.
 Publications were also labeled according to conventionality and novelty.

### 2019-05-28 cocit_r.tex

@@
 \section{Introduction}
+
 Citation and network analysis of  scientific literature reveals information on semantic relationships between publications, collaboration between scientists, and the practice of citation itself~\citep{garfield_citation_1955,de_solla_price_networks_1965,newman_structure_2001,Shi:2010:CHI:1816123.1816131,patience_pmid28560354}.
-Co-citation, the frequency with which two documents are cited together in other documents provides additional insights, including the identification of semantically related documents, fields, ideas, and specializations in science~\citep{small_co-citation_1973,marshakova-shaikevich_co-citation_1973,boyack_co-citation_2010}.
+Co-citation, the frequency with which two documents are cited together in other documents provides additional insights, including the identification of semantically related documents, fields, ideas, and specializations in science~\citep{small_co-citation_1973,marshakova-shaikevich_co-citation_1973,boyack_co-citation_2010, 10.3389/frma.2018.00020}.
 
@@
 Key to Uzzi {\em et al.}, however, is their random graph model and its underlying assumptions.
-A careful examination of the model (as defined by the Monte Carlo simulation) reveals that all substitutions of references are equiprobable, which means that a reference in an article can be substituted by any other reference randomly chosen from those published in the same year, irrespective of subject matter and citation count.
-For example, the model permits substitution of a reference in quantum physics with equal probability by a reference in classical literature, evolutionary biology, or anthropology.
+A careful examination of the model (as defined by the Monte Carlo simulation) reveals that random substitutions of references used to generate expected values are equiprobable, which means that a reference in an article can be substituted by any other reference randomly chosen from those published in the same year, irrespective of subject matter, disciplinary focus and citation count.
+For example, the model permits substitution of a reference in quantum physics with equal probability by a reference in quantum biology (i.e., the same field) or in some entirely different field, such as classical literature, evolutionary biology, or anthropology.
 Such substitutions poorly model documented citation behavior~\citep{wallace_lariviere_gingras_2012,moed_measuring_2010,klavans_research_2017,garfield_1979}.
-(Possibly insert reference to Sitaram's investigation here.) In addition, under this random model,  a reference cited over 100 times in a given year is selected with the same probability as a reference cited only once, which is inconsistent with the actual frequency of citation and also the power law or lognormal distributions observed in citations ~\citep{stringer_statistical_2010,perline_strong_2005}.
-Accordingly, the expected value calculations generated by the \citep{uzzi_atypical_2013} simulations and used in characterizing journal pairs in terms of conventionality and novelty  can be reasonably questioned on grounds of model mis-specification.
+In addition, under this random model, a reference cited over 100 times in a given year is selected with the same probability as a reference cited only once, which is inconsistent with the actual frequency of citation and also with the frequency distribution of citations characterized as power law or lognormal~\citep{stringer_statistical_2010,perline_strong_2005}.
+Lastly,  as we will show here, while the citation switching algorithm used in Uzzi  {\em et al.} preserves the number of publications and the number of references in each publication, it does not preserve the disciplinary proportions of cited references within the network.
+ Accordingly, the expected value calculations generated by the \cite{uzzi_atypical_2013} simulations and used in characterizing journal pairs in terms of conventionality and novelty  can be reasonably questioned on grounds of model mis-specification.
 
@@
 
-Despite different methods used to generate expected values, both \citep{uzzi_atypical_2013} and \citep{boyack_vs_uzzi_2014}  measured observed frequencies across the scientific literature without disciplinary constraints and subsequently used normalized frequencies to examine disciplinary subsets.
-In contrast, we chose instead to first construct semantically related sets of documents (disciplinary networks) and to measure observed and expected frequencies within these networks.
-(or cite Sitaram's statistics here so as to add specificity to this sentence, which could have this appended to it: ``consistent with researchers' patterns of citing predominantly work from their own field.
-This doesn't preclude citations from outside of the discipline of focus, but constrains the random substitutions to more plausibly related literature.'')
+Despite different methods used to generate expected values, both \citep{uzzi_atypical_2013} and \citep{boyack_vs_uzzi_2014} measured observed co-citation frequencies across the scientific literature without disciplinary constraints and subsequently used normalized frequencies to examine disciplinary subsets.
+In contrast, we chose instead to first construct semantically related sets of documents (disciplinary networks) and to measure observed and expected frequencies within these networks, consistent with researchers' patterns of citing predominantly work from their own field.
 
@@
 Instead, we conclude that conventional thought as commonly defined in our study, 
-in \citep{uzzi_atypical_2013}, and  \citep{boyack_vs_uzzi_2014}, is more likely to drive higher citations (in the disciplinary networks we studied).
+in \citep{uzzi_atypical_2013}, and  \citep{boyack_vs_uzzi_2014}, is more likely to drive higher citations.
  \emph{these are just filler conclusions that must be carefully rewritten and added to- need Jim's conclusions to be stated here.}.
@@
 Pubmed IDs (pmids) returned were matched to WoS IDs (wos\_ids) and used to retrieve relevant articles.
+For the applied physics dataset, we directly searched subject labels in WoS for `applied physics'.
+\\
+%\emph{Disciplinary datasets} We constructed three disciplinary datasets based on keyword searches.
+(i) immunology (ii) metabolism (iii) applied physics.
+For the first two, rooted in biomedical research, we searched Pubmed for the term `immunology' or `metabolism' in the years 1985, 1995, and 2005.
+Pubmed IDs (pmids) returned were matched to WoS IDs (wos\_ids) and used to retrieve relevant articles.
 For the applied physics dataset, we directly searched article level labels in WoS for `applied physics'.
@@
 \emph{Normalization of observed and expected values} Building upon prior work~\cite{uzzi_atypical_2013}, all ${n \choose 2}$ reference pairs were generated for each publication, where $n$ is the number of cited references in the publication.
-These reference pairs were then mapped to the journals they were published in using ISSN numbers,  creating journal pairs.
+These reference pairs were then mapped to the journals they were published in using ISSN numbers to create journal pairs.
 Where multiple ISSN numbers exist for a journal, the most frequently used one in the WoS was assigned to the journal.
 In addition, publications containing fewer than two references were discarded.
-Journal pair frequencies were summed up across the dataset to create observed frequencies $(F_{obs})$.
+Journal pair frequencies were summed across the dataset to create observed frequencies $(F_{obs})$.
 In contrast to the preceding study~\citep{uzzi_atypical_2013}, we generated 1,000 rather than 10 null models for each dataset by randomly shuffling references while preserving the number of publications, the number of references in each publication, and the frequency with which these references were cited within the year of interest.
-Expected values $(F_{exp})$ were generated by averaging the result of 1,000 simulations.
-z-scores were calculated for each journal-pair using the formula $(F_{obs} - F_{exp})/\sigma$ where $\sigma$  is the standard deviation of the frequencies generated by simulation.
-(Do we need a comment here that while we are using the term z-score, we do not imply that these are related to a normal distribution.
-Rather, we are using the terminology from Uzzi et al.) As a result of these calculations, each publication becomes associated with a set of z-scores corresponding to the journal pairs derived from pairwise combinations of its cited references and positional statistics (quantiles) of z-scores were calculated for each publication.
+In contrast to the preceding study~\citep{uzzi_atypical_2013}, we generated 1,000 rather than 10 null models for each dataset.
+Expected values $(F_{exp})$ for journal pairs were generated by averaging the result of 1,000 simulations.
+z-scores were calculated for each journal-pair using the formula $(F_{obs} - F_{exp})/\sigma$ where $\sigma$
+ is the standard deviation of the frequencies generated by simulation.
+As a result of these calculations, each publication becomes associated with a set of z-scores corresponding to the journal pairs derived from pairwise combinations of its cited references and positional statistics (quantiles) of z-scores were calculated for each publication.
 Publications were also labeled according to conventionality and novelty.
@@
 LN if the tenth percentile of z-scores for a publication was greater than zero.
+(Do we need a comment here that while we are using the term z-score, we do not imply that these are related to a normal distribution.
+Rather, we are using the terminology from Uzzi et al.?)
 

### 2019-05-28 cocit_r.tex
Revised Introduction

@@
 \citep{uzzi_atypical_2013} used a novel approach for co-citation analysis of 17.9 million articles and their cited references from the Web of Science (WoS)  to characterize a subset of highly cited articles with respect to both novel and conventional combinations of prior research.
-Observed co-citation frequencies, mapped to journals, were computed across the dataset and normalized (shifted and scaled) to expected values generated by Monte Carlo simulations under a random graph model.
+Observed co-citation frequencies, mapped to journals, were computed across the dataset by Monte Carlo simulation under a random graph model and normalized (shifted and scaled) to expected values.
 These normalized journal pair frequencies were termed \emph{z-scores} (Materials and Methods).
-Thus, every article was associated with multiple z-scores corresponding with the journal pairs represented by its citations.
+Thus, every article was associated with multiple z-scores corresponding with the journal pairs represented in its citations.
 For each article, positional statistics of these z-scores were calculated to describe conventionality: high conventionality (HC) if the median z-score for an article was greater than the median of median z-scores of all articles and low conventionality for the converse (LC).
@@
 Key to Uzzi {\em et al.}, however, is their random graph model and its underlying assumptions.
-A careful examination of the model (as defined by the Monte Carlo simulation) reveals that random substitutions of references used to generate expected values are equiprobable, which means that a reference in an article can be substituted by any other reference randomly chosen from those published in the same year, irrespective of subject matter, disciplinary focus and citation count.
+A careful examination of their Monte Carlo simulation reveals that random substitutions of references used to generate expected journal pair frequencies are equiprobable, which means that a reference in an article can be substituted by any other reference randomly chosen from those published in the same year, irrespective of subject matter, disciplinary focus and citation count.
 For example, the model permits substitution of a reference in quantum physics with equal probability by a reference in quantum biology (i.e., the same field) or in some entirely different field, such as classical literature, evolutionary biology, or anthropology.
 Such substitutions poorly model documented citation behavior~\citep{wallace_lariviere_gingras_2012,moed_measuring_2010,klavans_research_2017,garfield_1979}.
-In addition, under this random model, a reference cited over 100 times in a given year is selected with the same probability as a reference cited only once, which is inconsistent with the actual frequency of citation and also with the frequency distribution of citations characterized as power law or lognormal~\citep{stringer_statistical_2010,perline_strong_2005}.
-Lastly,  as we will show here, while the citation switching algorithm used in Uzzi  {\em et al.} preserves the number of publications and the number of references in each publication, it does not preserve the disciplinary proportions of cited references within the network.
+In addition, under this random model, a reference cited over 100 times in a given year is selected with the same probability as a reference cited only once, which is inconsistent with the actual frequency of citation and also with the power law or lognormal citation distributions observed in the literature~\citep{stringer_statistical_2010,perline_strong_2005}.
+Lastly,  as we will show here, while the citation switching algorithm used in Uzzi  {\em et al.} preserves the number of publications and the number of references in each publication, it does not preserve the proportion of cited references from within the disciplinary network.
  Accordingly, the expected value calculations generated by the \cite{uzzi_atypical_2013} simulations and used in characterizing journal pairs in terms of conventionality and novelty  can be reasonably questioned on grounds of model mis-specification.
@@
 Despite different methods used to generate expected values, both \citep{uzzi_atypical_2013} and \citep{boyack_vs_uzzi_2014} measured observed co-citation frequencies across the scientific literature without disciplinary constraints and subsequently used normalized frequencies to examine disciplinary subsets.
-In contrast, we chose instead to first construct semantically related sets of documents (disciplinary networks) and to measure observed and expected frequencies within these networks, consistent with researchers' patterns of citing predominantly work from their own field.
+In contrast, we chose to first construct semantically related sets of documents (disciplinary networks) and to measure observed and expected frequencies within these networks in order to preserve the proportion of citations from a citing document's subject area under random sampling.
 
 Accordingly, we used keyword searches of the scientific literature to create three citation networks themed around broad search terms.
-Within these disciplinary frameworks, we calculated expected values using a random graph model that accounted for existing citation frequencies and an efficient Monte Carlo simulation algorithm that permitted a substantially greater number of simulations.
+Within these disciplinary frameworks, we calculated expected journal pair frequencies using a random graph model that accounted for existing citation frequencies and an efficient Monte Carlo simulation algorithm that permitted a substantially greater number of simulations.
 We hypothesized that our approach would  reduce model misspecification and better simulate citation practice, in turn leading to different and more relevant conclusions.
@@
 As a result of these calculations, each publication becomes associated with a set of z-scores corresponding to the journal pairs derived from pairwise combinations of its cited references and positional statistics (quantiles) of z-scores were calculated for each publication.
-Publications were also labeled according to conventionality and novelty.
-(i) HC if the median z-score exceeded the median of median z-scores for all publications.
-LC if the median z-score was equal to or less than the median of median z-scores for all publications (ii) HN if the tenth percentile of z-scores for a publication was less than zero.
-LN if the tenth percentile of z-scores for a publication was greater than zero.
-(Do we need a comment here that while we are using the term z-score, we do not imply that these are related to a normal distribution.
-Rather, we are using the terminology from Uzzi et al.?)
+Publications were subsequently labeled according to conventionality and novelty: (i) HC if the median z-score exceeded the median of median z-scores for all publications and LC if the median z-score was equal to or less than the median of median z-scores for all publications,
+and (ii) HN if the tenth percentile of z-scores for a publication was less than zero, and LN if the tenth percentile of z-scores for a publication was greater than zero.
+(Should we comment here that while we are using the term z-score, reusing it from Uzzi, we do not imply that these are related to a normal distribution?)
 
 We investigated multiple definitions of hit articles, as did Uzzi et al., with hits defined as the 1\%, 2\%, 5\%, and 10\% top-cited articles.
-Do we want to report on the percentile being used for novelty at both the 1 and 10th percentile, or just focus on the 10th percentile?
+Also, mention different thresholds, 1st and 10th, for novelty threshold.
 

### 2019-05-28 cocit_r.tex
Updated conclusions paragraph in Introduction

@@
 Within these disciplinary frameworks, we calculated expected journal pair frequencies using a random graph model that accounted for existing citation frequencies and an efficient Monte Carlo simulation algorithm that permitted a substantially greater number of simulations.
-We hypothesized that our approach would  reduce model misspecification and better simulate citation practice, in turn leading to different and more relevant conclusions.
-Our study on these semantically-themed citation networks reveals significantly different patterns of conventionality and novelty between  citation networks and disciplines that challenges the conclusion that HCHN articles have a greater probability of being represented in highly cited publications.
-Instead, we conclude that conventional thought as commonly defined in our study, 
-in \citep{uzzi_atypical_2013}, and  \citep{boyack_vs_uzzi_2014}, is more likely to drive higher citations.
- \emph{these are just filler conclusions that must be carefully rewritten and added to- need Jim's conclusions to be stated here.}.
+We hypothesized that our approach would reduce model mis-specification and better simulate citation practice, in turn leading to different and more relevant conclusions.
+We found our model did, in fact, preserve the citation patterns found in the literature within an allowance for statistical sampling whereas the approach of Uzzi et al.
+does not.
+Those differences, due to sampling from within a discipline and more broadly, is manifest in journal pair z-scores whose signs change depending on the background dataset: the presence of such journal pairs has a conflicting effect on an article's characterization vis-\'a-vis novelty and conventionality depending on the background dataset.
+Our analysis of these semantically-themed citation networks challenges the universality of articles in the HCHN category having the highest probability of being hits as found in \cite{uzzi_atypical_2013}.
+For example, while HC remains highly correlated with hit articles in immunology and metabolism research, HN is not.
+In addition, while HN is highly correlated with hit articles in applied physics, HC is not.
+Furthermore, we found that the categories demonstrating the highest percentage of hits is not robust with the parameters used to define hit articles and the threshold for highly novel citation patterns.
 

### 2019-05-28 cocit_r.tex
Updated conclusions paragraph in Introduction

@@
 In addition, while HN is highly correlated with hit articles in applied physics, HC is not.
-Furthermore, we found that the categories demonstrating the highest percentage of hits is not robust with the parameters used to define hit articles and the threshold for highly novel citation patterns.
+Furthermore, we found that the categories demonstrating the highest percentage of hits is not robust with respect to varying parameters that define hit articles and the threshold for highly novel citation patterns.
 

### 2019-05-28 cocit_r.tex
Updated conclusions paragraph in Introduction

@@
 
-Accordingly, we used keyword searches of the scientific literature to create three citation networks themed around broad search terms.
-Within these disciplinary frameworks, we calculated expected journal pair frequencies using a random graph model that accounted for existing citation frequencies and an efficient Monte Carlo simulation algorithm that permitted a substantially greater number of simulations.
-We hypothesized that our approach would reduce model mis-specification and better simulate citation practice, in turn leading to different and more relevant conclusions.
-We found our model did, in fact, preserve the citation patterns found in the literature within an allowance for statistical sampling whereas the approach of Uzzi et al.
+We hypothesized that assessing articles' novelty, conventionality, and impact on datasets focused in disciplinary areas would reduce model mis-specification and better simulate citation practice, in turn, leading to different and more relevant conclusions.
+Accordingly, we used keyword searches of the scientific literature to create three citation networks themed around academic disciplines.
+Within these disciplinary frameworks, we calculated expected journal pair frequencies using a random graph model that accounted for existing citation frequencies and an efficient Monte Carlo simulation algorithm that permitted a substantially greater number of simulations than do previous studies.
+We found our model did, in fact, preserve the citation patterns found in the literature whereas the approach of Uzzi et al.
 does not.
-Those differences, due to sampling from within a discipline and more broadly, is manifest in journal pair z-scores whose signs change depending on the background dataset: the presence of such journal pairs has a conflicting effect on an article's characterization vis-\'a-vis novelty and conventionality depending on the background dataset.
-Our analysis of these semantically-themed citation networks challenges the universality of articles in the HCHN category having the highest probability of being hits as found in \cite{uzzi_atypical_2013}.
+The varying citation patterns when sampling from a disciplinary-focused dataset versus a broader dataset due, was a cause of journal pair z-scores changing signs in 28.6\% of instances: the effect of any one of these journal pairs on an article's novelty or conventiality is contradictory between broad and, more narrow disciplinary datasets.
+We contend that the interpretation due to a disciplinary dataset, which preserved citation patterns, is more appropriate and an improvement on current methods.
+Furthermore, our analysis of these semantically-themed citation networks challenges the universality of articles in the HCHN category having the highest probability of being hits as found in \cite{uzzi_atypical_2013}.
 For example, while HC remains highly correlated with hit articles in immunology and metabolism research, HN is not.

### 2019-05-31 cocit_r.tex
revised intro

@@
 % \end{authorsummary}
-
 \section{Introduction}
@@
 Citation and network analysis of  scientific literature reveals information on semantic relationships between publications, collaboration between scientists, and the practice of citation itself~\citep{garfield_citation_1955,de_solla_price_networks_1965,newman_structure_2001,Shi:2010:CHI:1816123.1816131,patience_pmid28560354}.
-Co-citation, the frequency with which two documents are cited together in other documents provides additional insights, including the identification of semantically related documents, fields, ideas, and specializations in science~\citep{small_co-citation_1973,marshakova-shaikevich_co-citation_1973,boyack_co-citation_2010, 10.3389/frma.2018.00020}.
+Co-citation, the frequency with which two documents are cited together in other documents provides additional insights, including the identification of semantically related documents, fields, ideas, and specializations in science~\citep{small_co-citation_1973, marshakova-shaikevich_co-citation_1973,boyack_co-citation_2010, 10.3389/frma.2018.00020}.
 
-\citep{uzzi_atypical_2013} used a novel approach for co-citation analysis of 17.9 million articles and their cited references from the Web of Science (WoS)  to characterize a subset of highly cited articles with respect to both novel and conventional combinations of prior research.
-Observed co-citation frequencies, mapped to journals, were computed across the dataset by Monte Carlo simulation under a random graph model and normalized (shifted and scaled) to expected values.
+\citep{uzzi_atypical_2013} used a novel approach for co-citation analysis of 17.9 million articles stratified by year of publication, and their cited references, from the Web of Science (WoS)  to characterize a subset of highly cited articles with respect to both novel and conventional combinations of prior research.
+In this study, frequencies of cited references in articles published in the Web of Science were calculated and transformed to journal pairs (observed co-citation frequencies).
+Expected values of these journal pair co-citations were computed from Monte Carlo simulations under a random graph model.
+Observed frequencies were then normalized (shifted and scaled) to expected values.
 These normalized journal pair frequencies were termed \emph{z-scores} (Materials and Methods).
@@
 Key to Uzzi {\em et al.}, however, is their random graph model and its underlying assumptions.
-A careful examination of their Monte Carlo simulation reveals that random substitutions of references used to generate expected journal pair frequencies are equiprobable, which means that a reference in an article can be substituted by any other reference randomly chosen from those published in the same year, irrespective of subject matter, disciplinary focus and citation count.
-For example, the model permits substitution of a reference in quantum physics with equal probability by a reference in quantum biology (i.e., the same field) or in some entirely different field, such as classical literature, evolutionary biology, or anthropology.
+A careful examination of their Monte Carlo simulations reveals that random selection of the references used to generate a null model and expected values is equiprobable with respect to disciplinary origin and citation count.
+For example, the model permits substitution of a reference in quantum physics with equal probability by a reference in the related quantum chemistry field or in some entirely different field, such as classical literature, evolutionary biology, or anthropology.
 Such substitutions poorly model documented citation behavior~\citep{wallace_lariviere_gingras_2012,moed_measuring_2010,klavans_research_2017,garfield_1979}.
-In addition, under this random model, a reference cited over 100 times in a given year is selected with the same probability as a reference cited only once, which is inconsistent with the actual frequency of citation and also with the power law or lognormal citation distributions observed in the literature~\citep{stringer_statistical_2010,perline_strong_2005}.
-Lastly,  as we will show here, while the citation switching algorithm used in Uzzi  {\em et al.} preserves the number of publications and the number of references in each publication, it does not preserve the proportion of cited references from within the disciplinary network.
+In addition, under this random model, a reference cited over 100 times in a given year is selected with the same probability as a reference cited only once, which is inconsistent with citation behavior and inconsiderate of the power law or lognormal citation distributions described in the literature~\citep{stringer_statistical_2010,perline_strong_2005}.
+Lastly,  as we will show, while the citation switching algorithm used in Uzzi  {\em et al.} preserves the number of publications and the number of references in each publication, it is not designed to preserve disciplinary proportions of cited references within subsets of the Web of Science.
 Accordingly, the expected value calculations generated by the \cite{uzzi_atypical_2013} simulations and used in characterizing journal pairs in terms of conventionality and novelty  can be reasonably questioned on grounds of model mis-specification.
@@
 A follow-up study by \citep{boyack_vs_uzzi_2014} explored the impact of discipline and journal effects on the definition of conventionality and novelty.
-While their study had some methodological differences from \citep{uzzi_atypical_2013} in the use of Scopus data and a $\chi^2$ calculation for the expected number of journal pair citations, Boyack and Klavans find the same basic trend that HCHN is more probably in highly cited papers.
+While their study had some methodological differences from \citep{uzzi_atypical_2013} in the use of Scopus data and a $\chi^2$ calculation rather than Monte Carlo simulations to generate expected values of journal pair citations, Boyack and Klavans find the same basic trend that HCHN is more probably in highly cited papers.
 However, they note that ``only 64.4\%  of  243  WoS  subject  categories'' in the Uzzi {\em et al.} study met the criterion of having the highest probability of hit papers in the HCHN category.
@@
 Despite different methods used to generate expected values, both \citep{uzzi_atypical_2013} and \citep{boyack_vs_uzzi_2014} measured observed co-citation frequencies across the scientific literature without disciplinary constraints and subsequently used normalized frequencies to examine disciplinary subsets.
-In contrast, we chose to first construct semantically related sets of documents (disciplinary networks) and to measure observed and expected frequencies within these networks in order to preserve the proportion of citations from a citing document's subject area under random sampling.
+In extending this prior work, we hypothesized that analysis of datasets focused in disciplinary areas would reduce model mis-specification since the pool of citations would be relevant to those disciplinary areas rather than being drawn from all disciplines.
+Accordingly, we used keyword searches of the scientific literature to create three citation networks themed around academic disciplines.
+Within these disciplinary frameworks, we calculated observed and expected co-citation frequencies using a refined random graph model and an efficient Monte Carlo simulation algorithm.
+The null model generated by citation shuffling in our study preserves the number of publications, the number of references group by year within each publication and, importantly, the disciplinary proportions of cited references in each dataset.
 
-We hypothesized that assessing articles' novelty, conventionality, and impact on datasets focused in disciplinary areas would reduce model mis-specification and better simulate citation practice, in turn, leading to different and more relevant conclusions.
-Accordingly, we used keyword searches of the scientific literature to create three citation networks themed around academic disciplines.
-Within these disciplinary frameworks, we calculated expected journal pair frequencies using a random graph model that accounted for existing citation frequencies and an efficient Monte Carlo simulation algorithm that permitted a substantially greater number of simulations than do previous studies.
-We found our model did, in fact, preserve the citation patterns found in the literature whereas the approach of Uzzi et al.
-does not.
-The varying citation patterns when sampling from a disciplinary-focused dataset versus a broader dataset due, was a cause of journal pair z-scores changing signs in 28.6\% of instances: the effect of any one of these journal pairs on an article's novelty or conventiality is contradictory between broad and, more narrow disciplinary datasets.
+Our analysis of these semantically-themed citation networks challenges the concept of universal features of the scientific literature that can be described by co-citation patterns.
+Particularly that articles in the HCHN category have the highest probability of being hits as found in \cite{uzzi_atypical_2013}.
+We find, for example, while HC remains highly correlated with hit articles in the immunology and metabolism datasets we constructed, HN is not.
+In addition, while HN is highly correlated with hit articles in applied physics, HC is not.
+Furthermore, we found that the categories demonstrating the highest percentage of hits are not robust with respect to varying parameters that define hit articles and the threshold for highly novel citation patterns.
+
+\emph{these remaining sentences require some work}
+The varying citation patterns when sampling from a disciplinary-focused dataset versus a broader dataset due, was a cause of journal pair z-scores changing signs in 28.6\% of instances: the effect of any one of these journal pairs on an article's novelty or conventionality is contradictory between broad and, more narrow disciplinary datasets.
 We contend that the interpretation due to a disciplinary dataset, which preserved citation patterns, is more appropriate and an improvement on current methods.
-Furthermore, our analysis of these semantically-themed citation networks challenges the universality of articles in the HCHN category having the highest probability of being hits as found in \cite{uzzi_atypical_2013}.
-For example, while HC remains highly correlated with hit articles in immunology and metabolism research, HN is not.
-In addition, while HN is highly correlated with hit articles in applied physics, HC is not.
-Furthermore, we found that the categories demonstrating the highest percentage of hits is not robust with respect to varying parameters that define hit articles and the threshold for highly novel citation patterns.
 
@@
 The total number of publications in this dataset was just over 25 million publications (25,134,073).
-For each of these years, we further restricted analysis to those of type Article.
-Since WoS data also contains incomplete references or references that point at other indexes,  we also considered only those references for which there were complete records (Table 1).
+For each of these years, we further restricted analysis to publications of type Article.
+Since WoS data also contains incomplete references or references that point at other indexes, we also considered only those references for which there were complete records~(\ref{tab:summary_data}).
 For example, WoS data for year 2005 contained 1,753,174 publications, which after restricting to type Article and considering only those references described above resulted in 916,573 publications, 6,095,594 unique references (set of references), and 17,167,347 total references (multiset of references).
@@
 (i) immunology (ii) metabolism (iii) applied physics.
-For the first two, rooted in biomedical research, we searched Pubmed for the term `immunology' or `metabolism' in the years 1985, 1995, and 2005.
+For the first two, rooted in biomedical research, we searched Pubmed for the term `immunology' or `metabolism' in the years 1985, 1995, and 2005~(\ref{tab:disc-datasets}).
 Pubmed IDs (pmids) returned were matched to WoS IDs (wos\_ids) and used to retrieve relevant articles.
 For the applied physics dataset, we directly searched subject labels in WoS for `applied physics'.
-\\
-%\emph{Disciplinary datasets} We constructed three disciplinary datasets based on keyword searches.
-(i) immunology (ii) metabolism (iii) applied physics.
-For the first two, rooted in biomedical research, we searched Pubmed for the term `immunology' or `metabolism' in the years 1985, 1995, and 2005.
-Pubmed IDs (pmids) returned were matched to WoS IDs (wos\_ids) and used to retrieve relevant articles.
-For the applied physics dataset, we directly searched article level labels in WoS for `applied physics'.
-\\
+We also examined publications in the five major research areas in the Web of Science; life sciences \& biomedicine, physical sciences, technology, social sciences, arts \& humanities using the extended subcategory classification of 153 sub-groups to categorize disciplinary composition of cited references in the datasets we studied.
+
 \emph{Normalization of observed and expected values} Building upon prior work~\cite{uzzi_atypical_2013}, all ${n \choose 2}$ reference pairs were generated for each publication, where $n$ is the number of cited references in the publication.
@@
 Only publications of type Article and references with complete WoS records are included in these counts.}
-\label{tab:label}
+\label{tab:summary_data}
 \centering
@@
 Counts of retrieved publications are shown for each of the three years analyzed.}
-\label{tab:label}
+\label{tab:disc-datasets}
 \centering
@@
 A  principal consideration, however, was to restrict model misspecification arising from disciplinarily irrelevant references.
-We addressed this consideration by restricting random substitutions to only those references in the disciplinary network being studied.
-We estimated model misspecification by measuring the Kullback-Leibler (K-L) Divergence~\citep{kullback_information_1951} between observed and simulated frequencies for the set of journals common to both a disciplinary network and the WoS superset (Table 3).
-The results indicate that simulations under our model consistently have a lower K-L divergence compared to simulations that draw from the WoS superset and its attendant substitutions that are ectopic with respect to field and discipline (Introduction).
+We addressed this consideration by analyzing disciplinary subsets of the scientific literature, thereby restricting random selection of references to only those references in the disciplinary network being studied.
+We predicted that model misspecification as measured by the Kullback-Leibler (K-L) Divergence~\citep{kullback_information_1951} between observed and simulated frequencies in a disciplinary network would be less than the divergence for observed and simulated frequencies in the WoS superset.
+The results indicate that for the set of journals common to both a disciplinary network and the WoS superset~\ref{tab:KLD}, simulations under our model consistently have a lower K-L divergence compared to simulations that draw from the WoS superset (and its attendant substitutions that are ectopic with respect to field and discipline).
+
+\begin{figure}
+\includegraphics[width=0.5\hsize]{fold_effect.pdf}
+\caption{Intra-network citation shuffling preserves disciplinary composition.
+Publications of type Article belonging to the WoS research areas (i) Arts and Humanities (ii) Life Sciences and Biomedicine were subject to a single shuffle of all their cited references using either the cited references in these networks as a source of random substitutions (bg\_local) or references from all articles in WoS (bg\_allWoS).
+The disciplinary composition of cited reference before and after shuffling was measured for each of 151 sub-groups (from the extended subject classification in WoS) in these two research areas, expressed as fold difference between citation counts grouped by subject for original (o) and shuffled (s) references using the formula (fold\_difference = $ifelse(o > s, o/s, s/o)$) and rounded to the nearest integer.
+A fold difference of 1 indicates that citation shuffling did not alter disciplinary composition.
+Data are shown for articles published in 1985.
+All four boxplots are generated from 151 observations.
+Min \& Max values for fold differences were as follows.
+(i) Arts \& Humanities.
+bg\_local (1,2), bg\_allWoS (1, 488) (ii) Life Sciences \& Biomedicine.
+bg\_local(1,1), bg\_allWos (1, 352) Note y-axis: $log_2$ scale.}
+\end{figure}
 
@@
 The ratio between the K-L divergence for disciplinary networks versus the full WoS ranges from 1.96 to 2.77 and is greater than 2.0 for eight out of nine cases, strongly suggesting that simulations that constrain substitutions to the given disciplinary network better model the observed data.}
-\label{tab:label}
+\label{tab:kld}
 \centering

### 2019-06-03 cocit_r.tex
Update cocit_r.tex
Version prior to reorganization of Results section

@@
 The null model generated by citation shuffling in our study preserves the number of publications, the number of references group by year within each publication and, importantly, the disciplinary proportions of cited references in each dataset.
+Our analysis (see Results section) demonstrates the model misspecification prior studies and its resolution in our approach.
 
@@
 Given consistent trends in the data, we analyzed the two boundary years (1985 and 2005) and the mid-point (1995) performing 1,000 simulations for each dataset.
-\\
+
 \emph{Disciplinary datasets} We constructed three disciplinary datasets based on keyword searches.
@@
 
-We investigated multiple definitions of hit articles, as did Uzzi et al., with hits defined as the 1\%, 2\%, 5\%, and 10\% top-cited articles.
+\emph{This comment needs to be worked into the M\&M section in an appropriate place, with any other specifics about the experiment parameters} We investigated multiple definitions of hit articles, as did Uzzi et al., with hits defined as the 1\%, 2\%, 5\%, and 10\% top-cited articles.
 Also, mention different thresholds, 1st and 10th, for novelty threshold.
@@
 \section{Results}
+
+\subsection{Model Misspecification and the Attributes of Disciplinary Context}
+
+\subsection{Novelty and Conventionality as Determinants of Impact in Disciplinary Contexts}
+
 \subsection{Chacko} In our study, we also use a Monte Carlo approach to simulate under a random graph model.
@@
 \begin{figure}
+\centering
 \includegraphics[width=0.5\hsize]{fold_effect.pdf}
@@
 Thus, with this lack of robustness, studies are faced with the necessity of defining which parameters are the best parameters to classify articles.
+
+George's point from Slack conversation: ``A concern that surfaced on the drive are the definitions of conventionality and novelty.
+On the one hand we use them- on the other hand you've also pointed out that it isn't that simple.''
 

### 2019-06-04 cocit_r.tex
Start of material rearrangement

@@
 For each of these years, we further restricted analysis to publications of type Article.
-Since WoS data also contains incomplete references or references that point at other indexes, we also considered only those references for which there were complete records~(\ref{tab:summary_data}).
+Since WoS data also contains incomplete references or references that point at other indexes, we also considered only those references for which there were complete records~(Table \ref{tab:summary_data}).
 For example, WoS data for year 2005 contained 1,753,174 publications, which after restricting to type Article and considering only those references described above resulted in 916,573 publications, 6,095,594 unique references (set of references), and 17,167,347 total references (multiset of references).
 Given consistent trends in the data, we analyzed the two boundary years (1985 and 2005) and the mid-point (1995) performing 1,000 simulations for each dataset.
-
-\emph{Disciplinary datasets} We constructed three disciplinary datasets based on keyword searches.
-(i) immunology (ii) metabolism (iii) applied physics.
-For the first two, rooted in biomedical research, we searched Pubmed for the term `immunology' or `metabolism' in the years 1985, 1995, and 2005~(\ref{tab:disc-datasets}).
-Pubmed IDs (pmids) returned were matched to WoS IDs (wos\_ids) and used to retrieve relevant articles.
-For the applied physics dataset, we directly searched subject labels in WoS for `applied physics'.
-We also examined publications in the five major research areas in the Web of Science; life sciences \& biomedicine, physical sciences, technology, social sciences, arts \& humanities using the extended subcategory classification of 153 sub-groups to categorize disciplinary composition of cited references in the datasets we studied.
-
-\emph{Normalization of observed and expected values} Building upon prior work~\cite{uzzi_atypical_2013}, all ${n \choose 2}$ reference pairs were generated for each publication, where $n$ is the number of cited references in the publication.
-These reference pairs were then mapped to the journals they were published in using ISSN numbers to create journal pairs.
-Where multiple ISSN numbers exist for a journal, the most frequently used one in the WoS was assigned to the journal.
-In addition, publications containing fewer than two references were discarded.
-Journal pair frequencies were summed across the dataset to create observed frequencies $(F_{obs})$.
-In contrast to the preceding study~\citep{uzzi_atypical_2013}, we generated 1,000 rather than 10 null models for each dataset by randomly shuffling references while preserving the number of publications, the number of references in each publication, and the frequency with which these references were cited within the year of interest.
-In contrast to the preceding study~\citep{uzzi_atypical_2013}, we generated 1,000 rather than 10 null models for each dataset.
-Expected values $(F_{exp})$ for journal pairs were generated by averaging the result of 1,000 simulations.
-z-scores were calculated for each journal-pair using the formula $(F_{obs} - F_{exp})/\sigma$ where $\sigma$
- is the standard deviation of the frequencies generated by simulation.
-As a result of these calculations, each publication becomes associated with a set of z-scores corresponding to the journal pairs derived from pairwise combinations of its cited references and positional statistics (quantiles) of z-scores were calculated for each publication.
-Publications were subsequently labeled according to conventionality and novelty: (i) HC if the median z-score exceeded the median of median z-scores for all publications and LC if the median z-score was equal to or less than the median of median z-scores for all publications,
-and (ii) HN if the tenth percentile of z-scores for a publication was less than zero, and LN if the tenth percentile of z-scores for a publication was greater than zero.
-(Should we comment here that while we are using the term z-score, reusing it from Uzzi, we do not imply that these are related to a normal distribution?)
-
-\emph{This comment needs to be worked into the M\&M section in an appropriate place, with any other specifics about the experiment parameters} We investigated multiple definitions of hit articles, as did Uzzi et al., with hits defined as the 1\%, 2\%, 5\%, and 10\% top-cited articles.
-Also, mention different thresholds, 1st and 10th, for novelty threshold.
 
@@
 
+\emph{Disciplinary datasets} We constructed three disciplinary datasets based on keyword searches.
+(i) immunology (ii) metabolism (iii) applied physics.
+For the first two, rooted in biomedical research, we searched Pubmed for the term `immunology' or `metabolism' in the years 1985, 1995, and 2005~(Table \ref{tab:disc-datasets}).
+Pubmed IDs (pmids) returned were matched to WoS IDs (wos\_ids) and used to retrieve relevant articles.
+For the applied physics dataset, we directly searched subject labels in WoS for `applied physics'.
+We also examined publications in the five major research areas in the Web of Science; life sciences \& biomedicine, physical sciences, technology, social sciences, arts \& humanities using the extended subcategory classification of 153 sub-groups to categorize disciplinary composition of cited references in the datasets we studied.
+
 \begin{table}[ht]
@@
 
+\emph{Normalization of observed and expected values} Building upon prior work~\cite{uzzi_atypical_2013}, all ${n \choose 2}$ reference pairs were generated for each publication, where $n$ is the number of cited references in the publication.
+These reference pairs were then mapped to the journals they were published in using ISSN numbers to create journal pairs.
+Where multiple ISSN numbers exist for a journal, the most frequently used one in the WoS was assigned to the journal.
+In addition, publications containing fewer than two references were discarded.
+Journal pair frequencies were summed across the dataset to create observed frequencies $(F_{obs})$.
+In contrast to the preceding study~\citep{uzzi_atypical_2013}, we generated 1,000 rather than 10 null models for each dataset by randomly shuffling references while preserving the number of publications, the number of references in each publication, and the frequency with which these references were cited within the year of interest.
+In contrast to the preceding study~\citep{uzzi_atypical_2013}, we generated 1,000 rather than 10 null models for each dataset.
+Expected values $(F_{exp})$ for journal pairs were generated by averaging the result of 1,000 simulations.
+z-scores were calculated for each journal-pair using the formula $(F_{obs} - F_{exp})/\sigma$ where $\sigma$ is the standard deviation of the frequencies generated by simulation.
+As a result of these calculations, each publication becomes associated with a set of z-scores corresponding to the journal pairs derived from pairwise combinations of its cited references and positional statistics (quantiles) of z-scores were calculated for each publication.
+Publications were subsequently labeled according to conventionality and novelty: (i) HC if the median z-score exceeded the median of median z-scores for all publications and LC if the median z-score was equal to or less than the median of median z-scores for all publications,
+and (ii) HN if the tenth percentile of z-scores for a publication was less than zero, and LN if the tenth percentile of z-scores for a publication was greater than zero.
+(Should we comment here that while we are using the term z-score, reusing it from Uzzi, we do not imply that these are related to a normal distribution?)
+
+\emph{This comment needs to be worked into the M\&M section in an appropriate place, with any other specifics about the experiment parameters} We investigated multiple definitions of hit articles, as did Uzzi et al., with hits defined as the 1\%, 2\%, 5\%, and 10\% top-cited articles.
+Also, mention different thresholds, 1st and 10th, for novelty threshold.
+
 \section{Results}
@@
 
-\subsection{Novelty and Conventionality as Determinants of Impact in Disciplinary Contexts}
+\emph{This paragraph needs work, but I wanted to create a placeholder for the introduction to this subsection} A central theme of this article is the misspecification of the model in Uzzi et al.
+in terms of its sampling from a broad dataset without consideration of observed citation practices where papers cite a high percentage of papers from within the discipline related to the paper, frequency of citation, and xxx.
+For example we found (\emph{cite the statistics from Sitaram's study and other references about citation practices.}) We demonstrate the effects of model misspecification and effectiveness of using disciplinary datasets to resolve those issues.
 
-\subsection{Chacko} In our study, we also use a Monte Carlo approach to simulate under a random graph model.
+Figure \ref{fig:scatter} shows that the z-scores for the same journal pair can be positive (negative) when computed with respect to one data set but be negative (positive) for another data set.
+The journal-pair z-scores in Figure \ref{fig:scatter} have consistent signs for both Immunology and WoS data sets in 71.4\% of the instances and different signs for 28.6\% of the journal pairs.
+When a journal-pair z-score is negative with respect to one dataset and positive with respect to another dataset, articles citing that pair are more likely to be deemed novel in the first instance and less likely to be deemed novel in the second instance.
+It seems that any journal pair should either be indicative of novelty or not, but it should never have contradictory implications with a changing reference dataset.
+We view, therefore, these contradictions as symptomatic inappropriately sampling from a broad dataset and ignoring observed citation patterns.
+Figure \ref{fig:scatter} reflects that the WoS data set has approximately 44,000 fewer negative z-scores than does the immunology data set, which contributes to its significantly lower percentage of high-novelty articles.
+\emph{The plots I made of the cumulative z-score distributions for Immunology and WoS also could be used to demonstrate this phenomenon, although the scatter plot does this more clearly, and it is more striking.
+The scatter plot also encodes more data, that is, the matched z-scores for each journal pair.}
+
+Note also in Figure \ref{fig:scatter} that many z-scores change values significantly between the WoS and Immunology datasets, although the density of points near the origin in Figure \ref{fig:scatter} is significant where the z-scores may have different signs with respect to the two datasets, although their magnitudes are not significantly different.
+While no metric is without downside, this observation points to a weakness of measuring novelty based on the sign of the z-score where the implications of a small negative value and a large negative value are the same.
+
+\begin{figure}%[tbhp]
+\centering
+\includegraphics[width=3in]{fig2_scatter_z_scores_flattened.pdf}     %width=.8\linewidth
+\caption{Journal pair z-scores vary with reference dataset.
+Scatter plot points (319,005) indicate journal pair z-scores for the 1995 Immunology dataset along the x-axis and the 1995 Web of Science dataset on the y-axis.
+Black indicates journal pairs whose z-scores have the same sign when computed for both reference datasets while red points indicate the 28.6\% of journal pairs whose z-scores change sign across datasets.
+Regions with deeper hues indicate higher point densities and the histograms show the marginal distributions for each dataset separately.}
+\label{fig:scatter}
+\end{figure}
+
+%\begin{figure*}
+%\begin{tabular}{ccc}
+%\includegraphics[width=2.1in]{SIDoc/figs/scatter_z_scores_metab85_WoS_ZoomIn.pdf} & \includegraphics[width=2.1in]{Fig2H01N10.pdf} & \includegraphics[width=2.1in]{Fig2H05N10.pdf} \\
+%(a) & (b) & (c) \\
+%\end{tabular}
+%\caption{Scatter plot points show journal pair z-scores with respect to the Immunology data set for 1995 on the x-axis and the broad Web of Science on the y-axis.
+Black indicates journal pairs whose z-scores have the same sign when computed for both data sets while red points indicate journal pairs whose z-scores change sign across data sets.
+Regions with deeper hues indicate higher point density.
+The histograms show the marginal distributions of the z-scores for each of the data sets separately.}
+%\label{fig:Fig2}
+%\end{figure*}
+
+The variation in z-scores with respect to the reference datasets causes the percentages of articles denoted as highly conventional and highly novel to be significantly different, as demonstrated in Figure \ref{fig:Fig1}.
+\emph{Insert text about Figure \ref{fig:Fig1}.}
+
+\begin{figure}
+\includegraphics[width=\hsize]{Fig1}
+\caption{Fraction of publications with high conventionality (HC) and high novelty (HN) signatures relative to citation count.
+\emph{What follows is the caption from PNAS submission: is any of this useful?}  Effect of Research Discipline,  Background Network,  and Citation Count on Conventionality and Novelty.
+Data are shown for the applied physics (18,305), immunology (21,917), metabolism (97,405) and WoS (476,288) networks for 1995.
+The number of publications in each network is shown in parentheses.
+Citation counts shown are cumulative over the first 8 years since publication.
+X-axis: publications were classified into percentile groups based on citation counts (e.g., Top 1 indicates those publications in the top 1\%).
+Y axis: The percent of applications in each group that are high conventionality (HC) and high novelty (HN).
+The z-scores are computed for each disciplinary network based on the selected background network; thus, \emph{imm} denotes the immunology network with immunology z-scores and \emph{imm\_wos} denotes the immunology network with z-scores from WoS z-scores.
+The figure shows striking differences between the WOS network compared to the metabolism and immunology networks: across all networks, the percentage of high conventionality (HC) publications increases with citation counts, while the percentage of high novelty (HN) publications decreases with citation counts for the biological networks but not for WOS.
+\label{fig:Fig1}}
+\end{figure}
+
+Another possible symptom of model misspecification is to find that the citations associated with an article under random sampling do not match with the observed disciplinary makeup of citation in practice.
+\emph{More needed here}  Here is Sitaram's study:
+
+Adding to the point of papers citing papers belonging to the same discipline, I collected the subject areas for all the cited references from the 1985 Applied Physics dataset and searched for the keyword `Physics`.
+Then calculated the percentage of references related to Applied Physics for each paper References-related-to-physics/Total-references.
+Only papers with at-least 5 references were considered and the total publications were 6991.
+Results show a mean of 0.77 i.e. on an average papers cite 77\% of their references belonging to same discipline.
+
+\noindent count    6991.000000\\
+mean        0.774002
+
+We investigated the effect of sampling from disciplinary data sets versus more broadly from the WoS on the disciplinary make-up of the citations in articles under random sampling (\emph{sentence needs work but is an example of a transition.}) \emph{Insert text about Figure \ref{fold_effect}, specifically the right-hand side of Figure  \ref{fold_effect} where the fold statistics demonstrate the effect with Uzzi's approach.}
+
+Like Uzzi et al., we also used a Monte Carlo approach to simulate under a random graph model.
 A  principal consideration, however, was to restrict model misspecification arising from disciplinarily irrelevant references.
 We addressed this consideration by analyzing disciplinary subsets of the scientific literature, thereby restricting random selection of references to only those references in the disciplinary network being studied.
-We predicted that model misspecification as measured by the Kullback-Leibler (K-L) Divergence~\citep{kullback_information_1951} between observed and simulated frequencies in a disciplinary network would be less than the divergence for observed and simulated frequencies in the WoS superset.
-The results indicate that for the set of journals common to both a disciplinary network and the WoS superset~\ref{tab:KLD}, simulations under our model consistently have a lower K-L divergence compared to simulations that draw from the WoS superset (and its attendant substitutions that are ectopic with respect to field and discipline).
+\emph{Insert comment about the left-hand side of Figure \ref{fold_effect} where the disciplinary dataset has resolved the fold issue.}  We also predicted that model misspecification as measured by the Kullback-Leibler (K-L) Divergence~\citep{kullback_information_1951} between observed and simulated frequencies in a disciplinary network would be less than the divergence for observed and simulated frequencies in the WoS superset.
+The results in Table \ref{tab:KLD} indicate that for the set of journals common to both a disciplinary network and the WoS superset, simulations under our model consistently have a lower K-L divergence compared to simulations that draw from the WoS superset (and its attendant substitutions that are ectopic with respect to field and discipline).
 
 \begin{figure}
+\label{fold_effect}
 \centering
@@
 
-\begin{figure}
-\includegraphics[width=\hsize]{Fig1}
-\caption{Fraction of publications with high conventionality (HC) and high novelty (HN) signatures relative to citation count.}
-\end{figure}
-
-\subsection{Bradley}
-Figure \ref{fig:scatter} shows that the z-scores for the same journal pair can be positive (negative) when computed with respect to one data set but be negative (positive) for another data set.
-The journal-pair z-scores in Figure \ref{fig:scatter} have consistent signs for both Immunology and WoS data sets in 71.4\% of the instances and different signs for 28.6\% of the journal pairs.
-A negative journal pair z-score in one context increases the likelihood that articles citing it will be deemed to be novel while articles citing it in another context, where the journal pair z-score is positive, are less likely to be classified as novel and possibly more likely to be classified as conventional.
-Figure \ref{fig:scatter} reflects that the WoS data set has approximately 44,000 fewer negative z-scores than does the immunology data set, which contributes to its significantly lower percentage of high-novelty articles as shown in Figure \ref{fig:scatter}.
-
-\begin{figure}%[tbhp]
-\centering
-\includegraphics[width=3in]{fig2_scatter_z_scores_flattened.pdf}     %width=.8\linewidth
-\caption{Journal pair z-scores vary with reference dataset.
-Scatter plot points (319,005) indicate journal pair z-scores for the 1995 Immunology dataset along the x-axis and the 1995 Web of Science dataset on the y-axis.
-Black indicates journal pairs whose z-scores have the same sign when computed for both reference datasets while red points indicate the 28.6\% of journal pairs whose z-scores change sign across datasets.
-Regions with deeper hues indicate higher point densities and the histograms show the marginal distributions for each dataset separately.}
-\label{fig:scatter}
-\end{figure}
-
-%\begin{figure*}
-%\begin{tabular}{ccc}
-%\includegraphics[width=2.1in]{SIDoc/figs/scatter_z_scores_metab85_WoS_ZoomIn.pdf} & \includegraphics[width=2.1in]{Fig2H01N10.pdf} & \includegraphics[width=2.1in]{Fig2H05N10.pdf} \\
-%(a) & (b) & (c) \\
-%\end{tabular}
-%\caption{Scatter plot points show journal pair z-scores with respect to the Immunology data set for 1995 on the x-axis and the broad Web of Science on the y-axis.
-Black indicates journal pairs whose z-scores have the same sign when computed for both data sets while red points indicate journal pairs whose z-scores change sign across data sets.
-Regions with deeper hues indicate higher point density.
-The histograms show the marginal distributions of the z-scores for each of the data sets separately.}
-%\label{fig:Fig2}
-%\end{figure*}
+\subsection{Novelty and Conventionality as Determinants of Impact in Disciplinary Contexts}
 
@@
 
+Figure \ref{fig:Fig2}, Panels (a) and (b), compares hit rates for the four categories among the Immunology, Applied Physics, and WoS datasets for 1995: the hit rate is defined as the number of hit articles in each category divided by the number of articles in the category.
+We evaluated the statistical significance of the categorical hit rates using multiple methods, some of which we describe here.
+Our first test was based on the null hypotheses that hits were distributed randomly among the four categories with uniform probability in proportion to the number of articles in each category.
+Using a Chi-Square Goodness of Fit test, rejecting the null hypothesis in favor of the alternate hypothesis supports a non-uniform dispersion of hits: that is, some of the four categories are individually associated with higher than expected, or lower than expected hit rates.
+The null hypothesis was rejected at a $p<0.001$ in all cases in  Figure \ref{fig:Fig2}, with the exception of the immunology and applied datasets where hit articles are designated as the top 1\% of articles: valid tests were not possible in those instances due to too few expected hits.
+The null hypothesis was rejected with $p<0.001$ for all valid tests for all parameter settings, all datasets, and all years: hypotheses tests were valid in 73 of 96 instances.
+We conclude that it is likely that the distribution of hits among categories is not uniform but, rather, hit rates vary among the categories in all datasets.
+(Should we insert a table with all statistical results?)
+
 \begin{table}%[tbhp]
@@
 \end{table}
-
-Figure \ref{fig:Fig2}, Panels (a) and (b), compares hit rates for the four categories among the Immunology, Applied Physics, and WoS datasets for 1995: the hit rate is defined as the number of hit articles in each category divided by the number of articles in the category.
-We evaluated the statistical significance of the categorical hit rates using multiple methods, some of which we describe here.
-Our first test was based on the null hypotheses that hits were distributed randomly among the four categories with uniform probability in proportion to the number of articles in each category.
-Using a Chi-Square Goodness of Fit test, rejecting the null hypothesis in favor of the alternate hypothesis supports a non-uniform dispersion of hits: that is, some of the four categories are individually associated with higher than expected, or lower than expected hit rates.
-The null hypothesis was rejected at a $p<0.001$ in all cases in  Figure \ref{fig:Fig2}, with the exception of the immunology and applied datasets where hit articles are designated as the top 1\% of articles: valid tests were not possible in those instances due to too few expected hits.
-The null hypothesis was rejected with $p<0.001$ for all valid tests for all parameter settings, all datasets, and all years: hypotheses tests were valid in 73 of 96 instances.
-We conclude that it is likely that the distribution of hits among categories is not uniform but, rather, hit rates vary among the categories in all datasets.
-(Should we insert a table with all statistical results?)
 

### 2019-06-04 cocit_r.tex
Update cocit_r.tex

@@
 
-Another possible symptom of model misspecification is to find that the citations associated with an article under random sampling do not match with the observed disciplinary makeup of citation in practice.
+Another possible symptom of model misspecification is that random sampling of citations associated with an article do not match with the observed disciplinary makeup of citation in practice.
 \emph{More needed here}  Here is Sitaram's study:

### 2019-06-04 cocit_r.tex
More revision from 6/4

@@
 
+\emph{Text from George that may serve well with, or in place of the above as an introduction to this subsection.}  Like Uzzi et al., we also used a Monte Carlo approach to simulate under a random graph model.
+A  principal consideration, however, was to restrict model misspecification arising from disciplinarily irrelevant references.
+We addressed this consideration by analyzing disciplinary subsets of the scientific literature, thereby restricting random selection of references to only those references in the disciplinary network being studied.
+
 Figure \ref{fig:scatter} shows that the z-scores for the same journal pair can be positive (negative) when computed with respect to one data set but be negative (positive) for another data set.
@@
 
-Another possible symptom of model misspecification is that random sampling of citations associated with an article do not match with the observed disciplinary makeup of citation in practice.
-\emph{More needed here}  Here is Sitaram's study:
-
-Adding to the point of papers citing papers belonging to the same discipline, I collected the subject areas for all the cited references from the 1985 Applied Physics dataset and searched for the keyword `Physics`.
-Then calculated the percentage of references related to Applied Physics for each paper References-related-to-physics/Total-references.
-Only papers with at-least 5 references were considered and the total publications were 6991.
-Results show a mean of 0.77 i.e. on an average papers cite 77\% of their references belonging to same discipline.
-
-\noindent count    6991.000000\\
-mean        0.774002
+Another possible symptom of model misspecification is that random sampling of citations associated with an article do not match with the distribution of citations across the disciplines observed in articles from that discipline.
+\citep{wallace_lariviere_gingras_2012} found that, often, a majority of an article's citations are the specialty of the article, although the percentage of citations from the same disciplinary focus varied among disciplines in the eight specialties they investigated: from approximately 39\% to 89\% in 2006.
+\emph{More needed here}  Similarly, we found that 77.4\% of citation in applied physics articles in 1985 (replace with 1995 data?) were from applied physics.
+\emph{Add references to other datasets.} A random sampling of citations would ideally reflect the percentages from the discipline in question, as well as the percentages of articles from other discipline.
 
@@
 
-Like Uzzi et al., we also used a Monte Carlo approach to simulate under a random graph model.
-A  principal consideration, however, was to restrict model misspecification arising from disciplinarily irrelevant references.
-We addressed this consideration by analyzing disciplinary subsets of the scientific literature, thereby restricting random selection of references to only those references in the disciplinary network being studied.
 \emph{Insert comment about the left-hand side of Figure \ref{fold_effect} where the disciplinary dataset has resolved the fold issue.}  We also predicted that model misspecification as measured by the Kullback-Leibler (K-L) Divergence~\citep{kullback_information_1951} between observed and simulated frequencies in a disciplinary network would be less than the divergence for observed and simulated frequencies in the WoS superset.
@@
 we found the category displaying the highest hit rate to be sensitive to the experimental parameter settings, which included the percentage of articles deemed to be hits and the percentile of articles' z-score distributions that delineated between articles of low novelty and high novelty.
-Thus, with this lack of robustness, studies are faced with the necessity of defining which parameters are the best parameters to classify articles.
+Faced with this lack of robustness, we are confronted with the necessity of defining defendable parameters, if possible, that determine novelty and conventionalty.
+More significantly, we should question whether the simple approach of defining novelty and conventionality as is done this article and other research is sufficient or whether we should expect such variation in the factors associated with impact as we have observed.
 

### 2019-06-04 cocit_r.tex
More revisions on 6/3/19

@@
 
-\emph{This paragraph needs work, but I wanted to create a placeholder for the introduction to this subsection} A central theme of this article is the misspecification of the model in Uzzi et al.
-in terms of its sampling from a broad dataset without consideration of observed citation practices where papers cite a high percentage of papers from within the discipline related to the paper, frequency of citation, and xxx.
-For example we found (\emph{cite the statistics from Sitaram's study and other references about citation practices.}) We demonstrate the effects of model misspecification and effectiveness of using disciplinary datasets to resolve those issues.
-
-\emph{Text from George that may serve well with, or in place of the above as an introduction to this subsection.}  Like Uzzi et al., we also used a Monte Carlo approach to simulate under a random graph model.
-A  principal consideration, however, was to restrict model misspecification arising from disciplinarily irrelevant references.
+\emph{This paragraph needs work, but I wanted to create a placeholder for the introduction to this subsection.
+It uses some of the passages form the former chacko subsection.} We have conjectured that the approach of Uzzi et al.
+for generating journal-pair z-scores is misspecified in its sampling from a broad dataset and its disregard for the frequency with which journal pairs are cited.
+Like Uzzi et al., we also used a Monte Carlo approach to simulate under a random graph model, although our principal consideration was to restrict model misspecification arising from disciplinarily irrelevant references.
 We addressed this consideration by analyzing disciplinary subsets of the scientific literature, thereby restricting random selection of references to only those references in the disciplinary network being studied.
+In this subsection we demonstrate the effects of model misspecification or Uzzi et al.'s approach and the effectiveness of using disciplinary datasets in resolving the concomitant issues with the former.
 

### 2019-06-04 cocit_r.tex
More revisions on 6/3/19

@@
 \emph{This paragraph needs work, but I wanted to create a placeholder for the introduction to this subsection.
-It uses some of the passages form the former chacko subsection.} We have conjectured that the approach of Uzzi et al.
+It uses some of the passages form the former Chacko subsection.} We have conjectured that the approach of Uzzi et al.
 for generating journal-pair z-scores is misspecified in its sampling from a broad dataset and its disregard for the frequency with which journal pairs are cited.
@@
 When a journal-pair z-score is negative with respect to one dataset and positive with respect to another dataset, articles citing that pair are more likely to be deemed novel in the first instance and less likely to be deemed novel in the second instance.
-It seems that any journal pair should either be indicative of novelty or not, but it should never have contradictory implications with a changing reference dataset.
-We view, therefore, these contradictions as symptomatic inappropriately sampling from a broad dataset and ignoring observed citation patterns.
+It seems that any journal pair should either be indicative of novelty or not, but it should never have contradictory implications that depend on the reference dataset.
+We view, therefore, these contradictions as symptomatic of inappropriately sampling from a broad dataset and ignoring observed citation patterns.
 Figure \ref{fig:scatter} reflects that the WoS data set has approximately 44,000 fewer negative z-scores than does the immunology data set, which contributes to its significantly lower percentage of high-novelty articles.
@@
 
-Note also in Figure \ref{fig:scatter} that many z-scores change values significantly between the WoS and Immunology datasets, although the density of points near the origin in Figure \ref{fig:scatter} is significant where the z-scores may have different signs with respect to the two datasets, although their magnitudes are not significantly different.
-While no metric is without downside, this observation points to a weakness of measuring novelty based on the sign of the z-score where the implications of a small negative value and a large negative value are the same.
+Note also in Figure \ref{fig:scatter} that many z-scores values are significantly different between the WoS and Immunology datasets, although the density of points near the origin in Figure \ref{fig:scatter} indicates that some journal pairs change signs between the datasets while their magnitudes are not significantly different.
+While no metric is without downside, this observation points to a weakness of measuring novelty based simply on the sign of z-scores where no distinction is made between a small negative value and a large negative value, but a negative value of small magnitude is viewed as being significantly different than a small positive value.
 
@@
 
-Another possible symptom of model misspecification is that random sampling of citations associated with an article do not match with the distribution of citations across the disciplines observed in articles from that discipline.
-\citep{wallace_lariviere_gingras_2012} found that, often, a majority of an article's citations are the specialty of the article, although the percentage of citations from the same disciplinary focus varied among disciplines in the eight specialties they investigated: from approximately 39\% to 89\% in 2006.
-\emph{More needed here}  Similarly, we found that 77.4\% of citation in applied physics articles in 1985 (replace with 1995 data?) were from applied physics.
-\emph{Add references to other datasets.} A random sampling of citations would ideally reflect the percentages from the discipline in question, as well as the percentages of articles from other discipline.
+Another symptom of model misspecification is that random sampling of citations associated with an article do not match with the distribution of citations across the disciplines observed in articles from that discipline.
+\citep{wallace_lariviere_gingras_2012} found that, often, a majority of an article's citations are from the specialty of the article, although that percentage varied among disciplines in the eight specialties they investigated: from approximately 39\% to 89\% for 2006.
+\emph{More needed here.}  Similarly, we found that 77.4\% of citations in applied physics articles in 1985 (replace with 1995 data?) were from applied physics.
+\emph{Add references to other datasets.} A random sampling of citations would ideally reflect the percentages from the discipline in question, as well as the percentages of articles from other disciplines.
 
@@
 \emph{Insert comment about the left-hand side of Figure \ref{fold_effect} where the disciplinary dataset has resolved the fold issue.}  We also predicted that model misspecification as measured by the Kullback-Leibler (K-L) Divergence~\citep{kullback_information_1951} between observed and simulated frequencies in a disciplinary network would be less than the divergence for observed and simulated frequencies in the WoS superset.
-The results in Table \ref{tab:KLD} indicate that for the set of journals common to both a disciplinary network and the WoS superset, simulations under our model consistently have a lower K-L divergence compared to simulations that draw from the WoS superset (and its attendant substitutions that are ectopic with respect to field and discipline).
+The results in Table \ref{tab:kld} indicate that for the set of journals common to both a disciplinary network and the WoS superset, simulations under our model consistently have a lower K-L divergence compared to simulations that draw from the WoS superset (and its attendant substitutions that are ectopic with respect to field and discipline).
 
 \begin{figure}
-\label{fold_effect}
 \centering
 \includegraphics[width=0.5\hsize]{fold_effect.pdf}
-\caption{Intra-network citation shuffling preserves disciplinary composition.
+\caption{\label{fold_effect} Intra-network citation shuffling preserves disciplinary composition.
 Publications of type Article belonging to the WoS research areas (i) Arts and Humanities (ii) Life Sciences and Biomedicine were subject to a single shuffle of all their cited references using either the cited references in these networks as a source of random substitutions (bg\_local) or references from all articles in WoS (bg\_allWoS).

### 2019-06-06 cocit_r.tex
minor revisions

@@
 {James Bradley\affil{1},
-Sitaram Devarakonda\affil{2}, Avon Davey\affil{2}, Dmitriy Korobskiy\affil{2}, Siyu Liu\affil{2}, Tandy Warnow\affil{3}
+Sitaram Devarakonda\affil{2}, Avon Davey\affil{2}, Dmitriy Korobskiy\affil{2}, Siyu Liu\affil{2}, Djamil Lakhdar-Hamina\affil{2},Tandy Warnow\affil{3}
 \and George Chacko\affil{2}}
@@
 
-\keywords{(bibliometrics, co-citation analysis, random graphs )}
+\keywords{(co-citation analysis, bibliometrics, random graphs )}
 
@@
 Lastly,  as we will show, while the citation switching algorithm used in Uzzi  {\em et al.} preserves the number of publications and the number of references in each publication, it is not designed to preserve disciplinary proportions of cited references within subsets of the Web of Science.
-Accordingly, the expected value calculations generated by the \cite{uzzi_atypical_2013} simulations and used in characterizing journal pairs in terms of conventionality and novelty  can be reasonably questioned on grounds of model mis-specification.
+Accordingly, the expected value calculations generated by the \cite{uzzi_atypical_2013} simulations and used in characterizing journal pairs in terms of conventionality and novelty  can be reasonably questioned on grounds of model mis-specification when subsets of the WoS are studied.
 
@@
 
+\begin{figure}%[tbhp]
+\centering
+\includegraphics[width=0.8\linewidth]{background-effect}     
+\caption{\ Intra-network citation shuffling preserves the disciplinary composition of references.
+Publications of type Article belonging to the three disciplinary networks (i) Applied Physics (ii) Immunology (iii) Metabolism were subject to a single shuffle of all their cited references using either the cited references in these networks as a source of random substitutions (bg\_local) or references from all articles in WoS (bg\_allWoS).
+Citation shuffling was performed using either our algorithm (repcs) or that of Uzzi (umsj).
+The disciplinary composition of cited references before and after shuffling was measured as frequencies for each of 153 sub-disciplines (from the extended subject classification in WoS) and expressed as fold difference between citation counts grouped by subject for original (o) and shuffled (s) references using the formula (fold\_difference = $ifelse(o > s, o/s, s/o)$) and rounded to the nearest integer.
+Null values were set to 1.
+A fold difference of 1 indicates that citation shuffling did not alter disciplinary composition.
+Data are shown for articles published in 1985.
+All four boxplots are generated from 151 observations.
+Min \& Max values for fold differences were as follows.
+(i) Arts \& Humanities.
+bg\_local (1,2), bg\_allWoS (1, 488) (ii) Life Sciences \& Biomedicine.
+bg\_local(1,1), bg\_allWos (1, 352) Note y-axis: $log_2$ scale.}
+\label{be}
+\end{figure}
+
 Figure \ref{fig:scatter} shows that the z-scores for the same journal pair can be positive (negative) when computed with respect to one data set but be negative (positive) for another data set.
@@
 The results in Table \ref{tab:kld} indicate that for the set of journals common to both a disciplinary network and the WoS superset, simulations under our model consistently have a lower K-L divergence compared to simulations that draw from the WoS superset (and its attendant substitutions that are ectopic with respect to field and discipline).
-
-\begin{figure}
-\centering
-\includegraphics[width=0.5\hsize]{fold_effect.pdf}
-\caption{\label{fold_effect} Intra-network citation shuffling preserves disciplinary composition.
-Publications of type Article belonging to the WoS research areas (i) Arts and Humanities (ii) Life Sciences and Biomedicine were subject to a single shuffle of all their cited references using either the cited references in these networks as a source of random substitutions (bg\_local) or references from all articles in WoS (bg\_allWoS).
-The disciplinary composition of cited reference before and after shuffling was measured for each of 151 sub-groups (from the extended subject classification in WoS) in these two research areas, expressed as fold difference between citation counts grouped by subject for original (o) and shuffled (s) references using the formula (fold\_difference = $ifelse(o > s, o/s, s/o)$) and rounded to the nearest integer.
-A fold difference of 1 indicates that citation shuffling did not alter disciplinary composition.
-Data are shown for articles published in 1985.
-All four boxplots are generated from 151 observations.
-Min \& Max values for fold differences were as follows.
-(i) Arts \& Humanities.
-bg\_local (1,2), bg\_allWoS (1, 488) (ii) Life Sciences \& Biomedicine.
-bg\_local(1,1), bg\_allWos (1, 352) Note y-axis: $log_2$ scale.}
-\end{figure}
 

### 2019-06-06 cocit_r.tex
messy updates

@@
 Citation and network analysis of  scientific literature reveals information on semantic relationships between publications, collaboration between scientists, and the practice of citation itself~\citep{garfield_citation_1955,de_solla_price_networks_1965,newman_structure_2001,Shi:2010:CHI:1816123.1816131,patience_pmid28560354}.
-Co-citation, the frequency with which two documents are cited together in other documents provides additional insights, including the identification of semantically related documents, fields, ideas, and specializations in science~\citep{small_co-citation_1973, marshakova-shaikevich_co-citation_1973,boyack_co-citation_2010, 10.3389/frma.2018.00020}.
+Co-citation, the frequency with which two documents are cited together in other documents provides additional insights, including the identification of semantically related documents, fields, specializations, and new ideas in science~\citep{small_co-citation_1973, marshakova-shaikevich_co-citation_1973,boyack_co-citation_2010, 10.3389/frma.2018.00020}.
 
-\citep{uzzi_atypical_2013} used a novel approach for co-citation analysis of 17.9 million articles stratified by year of publication, and their cited references, from the Web of Science (WoS)  to characterize a subset of highly cited articles with respect to both novel and conventional combinations of prior research.
-In this study, frequencies of cited references in articles published in the Web of Science were calculated and transformed to journal pairs (observed co-citation frequencies).
-Expected values of these journal pair co-citations were computed from Monte Carlo simulations under a random graph model.
-Observed frequencies were then normalized (shifted and scaled) to expected values.
-These normalized journal pair frequencies were termed \emph{z-scores} (Materials and Methods).
-Thus, every article was associated with multiple z-scores corresponding with the journal pairs represented in its citations.
+\citep{uzzi_atypical_2013} used a novel approach for co-citation analysis using, as input, 17.9 million articles and their cited references, from the Web of Science (WoS)  to characterize a subset of highly cited articles with respect to both novel and conventional combinations of prior research.
+In this study, co-citation frequencies of references in were calculated and represented as journal pairs (observed co-citation frequencies).
+Expected values of these observed frequencies were then computed from Monte Carlo simulations under a random graph model.
+Observed frequencies were then normalized (shifted and scaled) to expected values and termed \emph{z-scores} (Materials and Methods).
+Thus, every article was associated with multiple z-scores corresponding co-cited journal pairs in its citations.
 For each article, positional statistics of these z-scores were calculated to describe conventionality: high conventionality (HC) if the median z-score for an article was greater than the median of median z-scores of all articles and low conventionality for the converse (LC).
-Similarly,  an article was deemed to have high novelty (HN) if the tenth percentile of its z-scores  was negative and low novelty (LN) for the converse.
-Accordingly, each article was labeled with respect to conventionality and novelty, e.g, HCHN (denoting that the article exhibits high conventionality and high novelty), with all four combinations being possible.
-\citep{uzzi_atypical_2013} observed that HCHN articles were twice as likely to be highly cited, suggesting that novel combinations of ideas flavoring a body of conventional thought were a recipe for impact across the scientific literature.
+Similarly,  an article was labeled high novelty (HN) if the tenth percentile of its z-scores  was negative and low novelty (LN) for the converse.
+Accordingly, each article was annotated with respect to conventionality and novelty, e.g, HCHN (denoting that the article exhibits high conventionality and high novelty), with all four combinations being possible.
+\cite{uzzi_atypical_2013} observed that HCHN articles were twice as likely to be highly cited, suggesting that novel combinations of ideas flavoring a body of conventional thought were `nearly universal' recipe for impact.
 
 Key to Uzzi {\em et al.}, however, is their random graph model and its underlying assumptions.
-A careful examination of their Monte Carlo simulations reveals that random selection of the references used to generate a null model and expected values is equiprobable with respect to disciplinary origin and citation count.
-For example, the model permits substitution of a reference in quantum physics with equal probability by a reference in the related quantum chemistry field or in some entirely different field, such as classical literature, evolutionary biology, or anthropology.
-Such substitutions poorly model documented citation behavior~\citep{wallace_lariviere_gingras_2012,moed_measuring_2010,klavans_research_2017,garfield_1979}.
-In addition, under this random model, a reference cited over 100 times in a given year is selected with the same probability as a reference cited only once, which is inconsistent with citation behavior and inconsiderate of the power law or lognormal citation distributions described in the literature~\citep{stringer_statistical_2010,perline_strong_2005}.
-Lastly,  as we will show, while the citation switching algorithm used in Uzzi  {\em et al.} preserves the number of publications and the number of references in each publication, it is not designed to preserve disciplinary proportions of cited references within subsets of the Web of Science.
-Accordingly, the expected value calculations generated by the \cite{uzzi_atypical_2013} simulations and used in characterizing journal pairs in terms of conventionality and novelty  can be reasonably questioned on grounds of model mis-specification when subsets of the WoS are studied.
+The citation switching algorithm used to generate a null model in Uzzi  {\em  et al.} elegantly preserves the number of publications, the number of references in each publication, the year of publication of both publications and references, and the disciplinary composition of the references cited in these publications.
+Random substitution of the references used to generate expected values is equiprobable with respect to disciplinary origin and citation count.
+The model would permit substitution of a reference in quantum physics with equal probability by a reference in the related quantum chemistry field or in some entirely different field, such as classical literature, evolutionary biology, or anthropology.
+Such substitutions poorly model documented the disciplinary nature of scientific endeavor and citation behavior~\citep{wallace_lariviere_gingras_2012,moed_measuring_2010,klavans_research_2017,garfield_1979}.
+In addition, under this random model, a reference cited over 100 times in a given year is selected with the same probability as a reference cited only once, which is also inconsistent with citation behavior and inconsiderate of the power law or lognormal citation distributions described in the literature~\citep{stringer_statistical_2010,perline_strong_2005}.
+Accordingly, the expected value calculations generated by the \cite{uzzi_atypical_2013} simulations and used in characterizing articles in terms of conventionality and novelty can be reasonably questioned on grounds of model mis-specification when subsets of the WoS are analyzed in the context of expected values generated across disciplines.
 
 A follow-up study by \citep{boyack_vs_uzzi_2014} explored the impact of discipline and journal effects on the definition of conventionality and novelty.
-While their study had some methodological differences from \citep{uzzi_atypical_2013} in the use of Scopus data and a $\chi^2$ calculation rather than Monte Carlo simulations to generate expected values of journal pair citations, Boyack and Klavans find the same basic trend that HCHN is more probably in highly cited papers.
+While their study had some methodological differences in the use of Scopus data rather than WoS data, a smaller dataset, and a $\chi^2$ calculation rather than Monte Carlo simulations to generate expected values of journal pairs, Boyack and Klavans also reported the trend that HCHN is more probable in highly cited papers.
 However, they note that ``only 64.4\%  of  243  WoS  subject  categories'' in the Uzzi {\em et al.} study met the criterion of having the highest probability of hit papers in the HCHN category.
@@
 Despite different methods used to generate expected values, both \citep{uzzi_atypical_2013} and \citep{boyack_vs_uzzi_2014} measured observed co-citation frequencies across the scientific literature without disciplinary constraints and subsequently used normalized frequencies to examine disciplinary subsets.
-In extending this prior work, we hypothesized that analysis of datasets focused in disciplinary areas would reduce model mis-specification since the pool of citations would be relevant to those disciplinary areas rather than being drawn from all disciplines.
+In extending their prior work, we hypothesized that analysis of datasets focused in disciplinary areas would reduce model mis-specification since the pool of citations would be relevant to those disciplinary areas rather than being drawn from all disciplines.
+
 Accordingly, we used keyword searches of the scientific literature to create three citation networks themed around academic disciplines.
 Within these disciplinary frameworks, we calculated observed and expected co-citation frequencies using a refined random graph model and an efficient Monte Carlo simulation algorithm.
-The null model generated by citation shuffling in our study preserves the number of publications, the number of references group by year within each publication and, importantly, the disciplinary proportions of cited references in each dataset.
-Our analysis (see Results section) demonstrates the model misspecification prior studies and its resolution in our approach.
-
-Our analysis of these semantically-themed citation networks challenges the concept of universal features of the scientific literature that can be described by co-citation patterns.
-Particularly that articles in the HCHN category have the highest probability of being hits as found in \cite{uzzi_atypical_2013}.
+Our analysis of these semantically-themed citation networks challenges the assertion of universality, particularly that articles in the HCHN category have the highest probability of being hits.
 We find, for example, while HC remains highly correlated with hit articles in the immunology and metabolism datasets we constructed, HN is not.
@@
 For this study, we generated an analytical dataset from years 1985 to 2005 from ERNIE.
-The total number of publications in this dataset was just over 25 million publications (25,134,073).
+The total number of publications in this dataset was just over 25 million publications (25,134,073), which were then stratified by year of publication.
 For each of these years, we further restricted analysis to publications of type Article.
@@
 Given consistent trends in the data, we analyzed the two boundary years (1985 and 2005) and the mid-point (1995) performing 1,000 simulations for each dataset.
+We also calculated the number of times each of these articles was cited in the first 8 years since publication.
 
@@
 \begin{table}[ht]
-\caption{Summary of WoS Analytical Dataset.
-UP: unique publications, UR: unique references, TR: total references.
-The number of publications, unique references, total references and the ratio of total references to unique references increases monotonically with each year indicating that both the number of documents and citation activity increase over time.
-Data for reference years is flanked by horizontal lines and shown in boldface.
-Only publications of type Article and references with complete WoS records are included in these counts.}
+\caption{Summary of WoS Analytical Dataset.The number of publications of type Article (UP), unique references (UR), total references (TR) and the ratio of total references to unique references increases monotonically with each year indicating that both the number of documents and citation activity increase over time.
+Data for reference years is shown in boldface.}
 \label{tab:summary_data}
@@
 
-\emph{Disciplinary datasets} We constructed three disciplinary datasets based on keyword searches.
+We constructed three disciplinary datasets based on keyword searches.
 (i) immunology (ii) metabolism (iii) applied physics.
@@
 
-\emph{Normalization of observed and expected values} Building upon prior work~\cite{uzzi_atypical_2013}, all ${n \choose 2}$ reference pairs were generated for each publication, where $n$ is the number of cited references in the publication.
+\emph{Monte Carlo simulations and normalization of observed frequencies}.
+Analysis was performed on publications from 1985, 1995, and 2005.
+Building upon prior work~\cite{uzzi_atypical_2013}, all ${n \choose 2}$ reference pairs were generated for each publication, where $n$ is the number of cited references in the publication.
 These reference pairs were then mapped to the journals they were published in using ISSN numbers to create journal pairs.
@@
 Journal pair frequencies were summed across the dataset to create observed frequencies $(F_{obs})$.
-In contrast to the preceding study~\citep{uzzi_atypical_2013}, we generated 1,000 rather than 10 null models for each dataset by randomly shuffling references while preserving the number of publications, the number of references in each publication, and the frequency with which these references were cited within the year of interest.
-In contrast to the preceding study~\citep{uzzi_atypical_2013}, we generated 1,000 rather than 10 null models for each dataset.
-Expected values $(F_{exp})$ for journal pairs were generated by averaging the result of 1,000 simulations.
-z-scores were calculated for each journal-pair using the formula $(F_{obs} - F_{exp})/\sigma$ where $\sigma$ is the standard deviation of the frequencies generated by simulation.
+We developed a performant citation switching algorithm, \emph{runtime enhanced permuting citation switcher (repcs)} that randomly permuted citations grouped by year of publication to switch citations while preserving the year of publication for both articles and references, the number of publications and the number of references in each dataset and the disciplinary composition of the references in each dataset.
+The code for the citation switching algorithm~\cite{uzzi_atypical_2013} kindly provided by the authors and referred to as \emph{umsj}~\cite{boyack_vs_uzzi_2014}, was used as a benchmark for the repcs algorithm.
+Comparative analysis showed that 10 rounds of citation switching in a dataset of 391,860 publications from 1985 completed in 2,186 hours using the umsj algorithm and in less than one hour using the repcs algorithm.
+In that test, using either the repcs or umsj algorithms resulted in generating simulated values for 75\% of the observed journal pair frequencies.
+Subsequent rounds of development and testing resulted in 99\% journal pair coverage with 1,000 simulations so we chose use the repcs algorithm in our study and generated 1,000 null models, in contrast to the 10 null models in the previous study, for each dataset we analyzed.
+
+Expected values $(F_{exp})$ for journal pairs were generated by averaging the result of 1,000 simulations and z-scores were then calculated for each journal-pair using the formula $(F_{obs} - F_{exp})/\sigma$ where $\sigma$ is the standard deviation of the frequencies generated by simulation.
 As a result of these calculations, each publication becomes associated with a set of z-scores corresponding to the journal pairs derived from pairwise combinations of its cited references and positional statistics (quantiles) of z-scores were calculated for each publication.
@@
 and (ii) HN if the tenth percentile of z-scores for a publication was less than zero, and LN if the tenth percentile of z-scores for a publication was greater than zero.
-(Should we comment here that while we are using the term z-score, reusing it from Uzzi, we do not imply that these are related to a normal distribution?)
-
-\emph{This comment needs to be worked into the M\&M section in an appropriate place, with any other specifics about the experiment parameters} We investigated multiple definitions of hit articles, as did Uzzi et al., with hits defined as the 1\%, 2\%, 5\%, and 10\% top-cited articles.
+We also investigated multiple definitions of hit articles with hits defined as the 1\%, 2\%, 5\%, and 10\% top-cited articles.
 Also, mention different thresholds, 1st and 10th, for novelty threshold.
@@
 
-\subsection{Model Misspecification and the Attributes of Disciplinary Context}
+\subsection{Model Misspecification and the Attributes of Disciplinary Context} We have invoked model mis-specification arising from disciplinarily irrelevant references as a concern.
+To address this issue, we analyzed the disciplinary composition of the references in our three test datasets, `applied physics', `immunology', and `metabolism' for the years 1985, 1995, and 2005 and observed that 8.4.2\% of the references in the applied physics dataset were classified as belonging to the WoS physical sciences research area.
+Similarly, 93.7\% and 92.1\% of the references in the immunology and metabolism datasets belonged to the life sciences and biomedicine research area, indicating strongly that references are more likely belong to the same research area as the publications that cite them.
+
+We  also analyzed the consequences of citation shuffling within a disciplinary set or all of the Web of Science.
+References in publications belonging to these three datasets were classified using the WoS Extended Subjects classification of 153 subject areas and summarized as a frequency distribution.
+A single shuffle of the references in these datasets or all the references in the corresponding WoS year slice was performed, using either the rpcs or umsj algorithms, and frequencies computed again.
+The fold change in subject frequencies of references before and after shuffling was calculated for all 153 Subject categories and summarized as boxplots in \ref{fig:be}.
+The data show consistently that disciplinary composition of references is preserved when citation shuffling is conducted within a disciplinary network.
+
+We then estimated model mis-specification by calculating the Kullback-Leibler (K-L) divergence between the simulated and observed journal pair frequencies for disciplinary datasets using again, either the references in the disciplinary datasets or those in all of WoS for the simulations~\ref{tab:kld} and observed that K-L divergences when using the WoS background was roughly double compared to the disciplinary network.
+
+We addressed this consideration by analyzing disciplinary subsets of the scientific literature, thereby restricting random selection of references to only those references in the disciplinary network being studied.
+What about z-scores? 
+We have conjectured that the approach of Uzzi et al.
+for generating journal-pair z-scores is misspecified in its sampling from a broad dataset and its disregard for the frequency with which journal pairs are citedOur principal consideration was to restrict model misspecification arising from disciplinarily irrelevant references.
+We addressed this consideration by analyzing disciplinary subsets of the scientific literature, thereby restricting random selection of references to only those references in the disciplinary network being studied.As observed in the Introduction, Monte Carlo simulations that use references from all publications do not account for observed citation practice (sentence needs to be made more eloquent)...
 
 \emph{This paragraph needs work, but I wanted to create a placeholder for the introduction to this subsection.
-It uses some of the passages form the former Chacko subsection.} We have conjectured that the approach of Uzzi et al.
-for generating journal-pair z-scores is misspecified in its sampling from a broad dataset and its disregard for the frequency with which journal pairs are cited.
+It uses some of the passages form the former Chacko subsection.} .
 Like Uzzi et al., we also used a Monte Carlo approach to simulate under a random graph model, although our principal consideration was to restrict model misspecification arising from disciplinarily irrelevant references.
@@
 bg\_local(1,1), bg\_allWos (1, 352) Note y-axis: $log_2$ scale.}
-\label{be}
+\label{fig:be}
 \end{figure}

### 2019-06-08 cocit_r.tex
revisions:

@@
 % ie,
-%\correspondingauthor{Ritwik K. Niyogi}{ritwik.niyogi@gatsby.ucl.ac.uk}
+\correspondingauthor{George Chacko}{netelabs@nete.com}
 
@@
 In this study, co-citation frequencies of references in were calculated and represented as journal pairs (observed co-citation frequencies).
-Expected values of these observed frequencies were then computed from Monte Carlo simulations under a random graph model.
-Observed frequencies were then normalized (shifted and scaled) to expected values and termed \emph{z-scores} (Materials and Methods).
-Thus, every article was associated with multiple z-scores corresponding co-cited journal pairs in its citations.
-For each article, positional statistics of these z-scores were calculated to describe conventionality: high conventionality (HC) if the median z-score for an article was greater than the median of median z-scores of all articles and low conventionality for the converse (LC).
-Similarly,  an article was labeled high novelty (HN) if the tenth percentile of its z-scores  was negative and low novelty (LN) for the converse.
-Accordingly, each article was annotated with respect to conventionality and novelty, e.g, HCHN (denoting that the article exhibits high conventionality and high novelty), with all four combinations being possible.
-\cite{uzzi_atypical_2013} observed that HCHN articles were twice as likely to be highly cited, suggesting that novel combinations of ideas flavoring a body of conventional thought were `nearly universal' recipe for impact.
+Expected values of these frequencies were generated from Monte Carlo simulations under a random graph model.
+Observed frequencies were then normalized (shifted and scaled) to averaged expected values from ten simulations and termed \emph{z-scores}, which were interpreted as suggesting conventional thought if positive and novel thought if negative.
+Consequently, every article was associated with multiple z-scores corresponding to co-cited journal pairs in its refernces.
+For each article, positional statistics of z-scores were calculated to set thresholds for a binary (high/low) classification of conventionality (C) using the median and novelty (N) using the tenth percentile of z-scores within an article.
+Thus, HCLN would denote high conventionality and low novelty with all four combinations being possible.
+\cite{uzzi_atypical_2013} observed that HCHN articles were twice as likely to be highly cited, suggesting that novel combinations of ideas flavoring a body of conventional thought were a 'nearly universal` recipe for impact.
 
-Key to Uzzi {\em et al.}, however, is their random graph model and its underlying assumptions.
-The citation switching algorithm used to generate a null model in Uzzi  {\em  et al.} elegantly preserves the number of publications, the number of references in each publication, the year of publication of both publications and references, and the disciplinary composition of the references cited in these publications.
-Random substitution of the references used to generate expected values is equiprobable with respect to disciplinary origin and citation count.
-The model would permit substitution of a reference in quantum physics with equal probability by a reference in the related quantum chemistry field or in some entirely different field, such as classical literature, evolutionary biology, or anthropology.
-Such substitutions poorly model documented the disciplinary nature of scientific endeavor and citation behavior~\citep{wallace_lariviere_gingras_2012,moed_measuring_2010,klavans_research_2017,garfield_1979}.
-In addition, under this random model, a reference cited over 100 times in a given year is selected with the same probability as a reference cited only once, which is also inconsistent with citation behavior and inconsiderate of the power law or lognormal citation distributions described in the literature~\citep{stringer_statistical_2010,perline_strong_2005}.
-Accordingly, the expected value calculations generated by the \cite{uzzi_atypical_2013} simulations and used in characterizing articles in terms of conventionality and novelty can be reasonably questioned on grounds of model mis-specification when subsets of the WoS are analyzed in the context of expected values generated across disciplines.
+Key to Uzzi {\em et al.}, is their random graph model and its underlying assumptions.
+The citation switching algorithm used to generate a null model elegantly preserves the number of publications, the number of references in each publication, the year of publication of both publications and references, and the disciplinary composition of the references cited in these publications.
+However, random substitution of the references used to generate expected values is equiprobable with respect to disciplinary origin and citation count.
+The model permits substitution of a reference in quantum physics with equal probability by a reference in the related quantum chemistry field or in some entirely different field, such as classical literature, evolutionary biology, or anthropology.
+Such substitutions poorly model the disciplinary nature of scientific endeavor and citation behavior~\citep{wallace_lariviere_gingras_2012,moed_measuring_2010,klavans_research_2017,garfield_1979}.
+In addition, under this random model, a reference cited over 100 times in a given year is selected with the same probability as a reference cited only once, which appears inconsistent with the power law or lognormal citation distributions described in the literature~\citep{stringer_statistical_2010,perline_strong_2005}.
+Accordingly, the expected value calculations used to characterize articles in terms of conventionality and novelty can be reasonably questioned on grounds of model mis-specification when disciplinary subsets of the WoS are analyzed in the context of expected values generated across all of WoS.
 
@@
 
-Despite different methods used to generate expected values, both \citep{uzzi_atypical_2013} and \citep{boyack_vs_uzzi_2014} measured observed co-citation frequencies across the scientific literature without disciplinary constraints and subsequently used normalized frequencies to examine disciplinary subsets.
-In extending their prior work, we hypothesized that analysis of datasets focused in disciplinary areas would reduce model mis-specification since the pool of citations would be relevant to those disciplinary areas rather than being drawn from all disciplines.
-
+Despite different methods used to generate expected values, both of these key preceding studies (vide supra) measured co-citation frequencies across the scientific literature without disciplinary constraints and subsequently analyzed disciplinary subsets.
+In extending their prior work, we hypothesized that normalization using expected values drawn from datasets focused in disciplinary areas, rather than all of WoS, would reduce model mis-specification.
 Accordingly, we used keyword searches of the scientific literature to create three citation networks themed around academic disciplines.
 Within these disciplinary frameworks, we calculated observed and expected co-citation frequencies using a refined random graph model and an efficient Monte Carlo simulation algorithm.
-Our analysis of these semantically-themed citation networks challenges the assertion of universality, particularly that articles in the HCHN category have the highest probability of being hits.
-We find, for example, while HC remains highly correlated with hit articles in the immunology and metabolism datasets we constructed, HN is not.
+Our analysis of these semantically-themed citation networks challenges the assertion of universality.
+Under our conditions of reduced model misspecification, we observe that while HC remains highly correlated with hit articles in the immunology and metabolism datasets, HN is not.
 In addition, while HN is highly correlated with hit articles in applied physics, HC is not.
-Furthermore, we found that the categories demonstrating the highest percentage of hits are not robust with respect to varying parameters that define hit articles and the threshold for highly novel citation patterns.
+Beyond variation across disciplines and the case for contextual analysis, we found that the categories demonstrating the highest percentage of hits are not robust with respect to varying parameters that define hit articles and the threshold for highly novel citation patterns.
 
@@
 For example, WoS data for year 2005 contained 1,753,174 publications, which after restricting to type Article and considering only those references described above resulted in 916,573 publications, 6,095,594 unique references (set of references), and 17,167,347 total references (multiset of references).
-Given consistent trends in the data, we analyzed the two boundary years (1985 and 2005) and the mid-point (1995) performing 1,000 simulations for each dataset.
+Given consistent trends in the data, Table \ref{tab:summary_data}, we analyzed the two boundary years (1985 and 2005) and the mid-point (1995) performing 1,000 simulations for each dataset.
 We also calculated the number of times each of these articles was cited in the first 8 years since publication.
@@
 \begin{table}[ht]
-\caption{Summary of WoS Analytical Dataset.The number of publications of type Article (UP), unique references (UR), total references (TR) and the ratio of total references to unique references increases monotonically with each year indicating that both the number of documents and citation activity increase over time.
-Data for reference years is shown in boldface.}
+\caption{Summary of base WoS Analytical Dataset.The number of publications of type Article (UP), unique references (UR), total references (TR) and the ratio of total references to unique references increases monotonically with each year indicating that both the number of documents and citation activity increase over time.
+Only publications of type Article with at least two references, and references with complete publication data were counted.}
 \label{tab:summary_data}
 \centering
-\begin{tabular}{|rrrrr|}
+\begin{tabular}{|r rrrr|}
   \hline
-Year & UP & UR & TR & TR/UR \\ 
+year & UP & UR & TR & TR/UR \\ 
   \hline
-\textbf{1985} & \textbf{418495} & \textbf{2281297} & \textbf{5615496} & \textbf{2.46} \\ 
+1985 & 391,860 & 2,266,584 & 5,588,861 & 2.47 \\ 
   \hline
-1986 & 402309 & 2316451 & 5708796 & 2.46 \\ 
-1987 & 412936 & 2427347 & 5998513 & 2.47 \\ 
-1988 & 426001 & 2545647 & 6354917 & 2.50 \\ 
-1989 & 443144 & 2673092 & 6749319 & 2.52 \\ 
-1990 & 458768 & 2827517 & 7209413 & 2.55 \\ 
-1991 & 477712 & 2977784 & 7729776 & 2.60 \\ 
-1992 & 492181 & 3134109 & 8188940 & 2.61 \\ 
-1993 & 504488 & 3278102 & 8676583 & 2.65 \\ 
-1994 & 523660 & 3458072 & 9255748 & 2.68 \\ 
+1986 & 402,309 & 2,316,451 & 5,708,796 & 2.46 \\ 
+1987 & 412,936 & 2,427,347 & 5,998,513 & 2.47 \\ 
+1988 & 426,001 & 2,545,647 & 6,354,917 & 2.50 \\ 
+1989 & 443,144 & 2,673,092 & 6,749,319 & 2.52 \\ 
+1990 & 458,768 & 2,827,517 & 7,209,413 & 2.55 \\ 
+1991 & 477,712 & 2,977,784 & 7,729,776 & 2.60 \\ 
+1992 & 492,181 & 3,134,109 & 8,188,940 & 2.61 \\ 
+1993 & 504,488 & 3,278,102 & 8,676,583 & 2.65 \\ 
+1994 & 523,660 & 3,458,072 & 9,255,748 & 2.68 \\ 
   \hline
-\textbf{1995} & \textbf{559685} & \textbf{3692575} & \textbf{9897946} & \textbf{2.68} \\ 
+1995 & 537,160 & 3,680,616 & 9,875,421 & 2.68 \\ 
   \hline
-1996 & 663110 & 4144581 & 11641286 & 2.81 \\ 
-1997 & 677077 & 4340733 & 12135104 & 2.80 \\ 
-1998 & 693531 & 4573584 & 12728629 & 2.78 \\ 
-1999 & 709827 & 4784024 & 13280828 & 2.78 \\ 
- 2000 & 721926 & 5008842 & 13810746 & 2.76 \\ 
- 2001 & 727816 & 5203078 & 14261189 & 2.74 \\ 
- 2002 & 747287 & 5464045 & 15001390 & 2.75 \\ 
- 2003 & 786284 & 5773756 & 16024652 & 2.78 \\ 
- 2004 & 826834 & 6095594 & 17167347 & 2.82 \\ 
+1996 & 663,110 & 4,144,581 & 11,641,286 & 2.81 \\ 
+1997 & 677,077 & 4,340,733 & 12,135,104 & 2.80 \\ 
+1998 & 693,531 & 4,573,584 & 12,728,629 & 2.78 \\ 
+1999 & 709,827 & 4,784,024 & 13,280,828 & 2.78 \\ 
+2000 & 721,926 & 5,008,842 & 13,810,746 & 2.76 \\ 
+2001 & 727,816 & 5,203,078 & 14,261,189 & 2.74 \\ 
+2002 & 747,287 & 5,464,045 & 15,001,390 & 2.75 \\ 
+2003 & 786,284 & 5,773,756 & 16,024,652 & 2.78 \\ 
+ 2004 & 826,834 & 6,095,594 & 17,167,347 & 2.82 \\ 
    \hline
-\textbf{2005} & \textbf{916573} & \textbf{6629595} & \textbf{19066249} & \textbf{2.88} \\ 
+ 2005 & 886,648 & 6,615,824 & 19,036,324 & 2.88 \\ 
  \hline
@@
 
-\emph{Monte Carlo simulations and normalization of observed frequencies}.
+\emph{Monte Carlo simulations, normalization of observed frequencies, annotations, and `hit' papers}.
 Analysis was performed on publications from 1985, 1995, and 2005.
 Building upon prior work~\cite{uzzi_atypical_2013}, all ${n \choose 2}$ reference pairs were generated for each publication, where $n$ is the number of cited references in the publication.
-These reference pairs were then mapped to the journals they were published in using ISSN numbers to create journal pairs.
+These reference pairs were then mapped to the journals they were published in using ISSN numbers as identifiers.
 Where multiple ISSN numbers exist for a journal, the most frequently used one in the WoS was assigned to the journal.
@@
 We developed a performant citation switching algorithm, \emph{runtime enhanced permuting citation switcher (repcs)} that randomly permuted citations grouped by year of publication to switch citations while preserving the year of publication for both articles and references, the number of publications and the number of references in each dataset and the disciplinary composition of the references in each dataset.
-The code for the citation switching algorithm~\cite{uzzi_atypical_2013} kindly provided by the authors and referred to as \emph{umsj}~\cite{boyack_vs_uzzi_2014}, was used as a benchmark for the repcs algorithm.
-Comparative analysis showed that 10 rounds of citation switching in a dataset of 391,860 publications from 1985 completed in 2,186 hours using the umsj algorithm and in less than one hour using the repcs algorithm.
-In that test, using either the repcs or umsj algorithms resulted in generating simulated values for 75\% of the observed journal pair frequencies.
-Subsequent rounds of development and testing resulted in 99\% journal pair coverage with 1,000 simulations so we chose use the repcs algorithm in our study and generated 1,000 null models, in contrast to the 10 null models in the previous study, for each dataset we analyzed.
+We used the citation switching algorithm of ~\cite{uzzi_atypical_2013} referred to as \emph{umsj}~\citep{boyack_vs_uzzi_2014}, as a benchmark for the repcs algorithm using code kindly provided by the authors.
+A comparative analysis showed that while 10 simulations of the WoS 1985 dataset (391,860 publications) completed in 2,186 hours using the umsj algorithm, it completed in less than one hour using the repcs algorithm implemented on a Spark cluster.
+Using either the repcs or umsj algorithms for 10 simulations resulted in expected value coverage of 75\% of the observed journal pair frequencies.
+Subsequent rounds of development and testing resulted in 99\% coverage of observed journal pairs when 1,000 simulations were conducted.
+The runtime advantage was significant enough that we chose to use the repcs algorithm in our study  and generated expected values averaged from 1,000 simulations for improved coverage for every dataset we analyzed.
 
-Expected values $(F_{exp})$ for journal pairs were generated by averaging the result of 1,000 simulations and z-scores were then calculated for each journal-pair using the formula $(F_{obs} - F_{exp})/\sigma$ where $\sigma$ is the standard deviation of the frequencies generated by simulation.
-As a result of these calculations, each publication becomes associated with a set of z-scores corresponding to the journal pairs derived from pairwise combinations of its cited references and positional statistics (quantiles) of z-scores were calculated for each publication.
-Publications were subsequently labeled according to conventionality and novelty: (i) HC if the median z-score exceeded the median of median z-scores for all publications and LC if the median z-score was equal to or less than the median of median z-scores for all publications,
-and (ii) HN if the tenth percentile of z-scores for a publication was less than zero, and LN if the tenth percentile of z-scores for a publication was greater than zero.
+Averaging the result of 1,000 simulations for each dataset studied, z-scores were then calculated for each journal-pair using the formula $(F_{obs} - F_{exp})/\sigma$ where $F_{obs}$ is the observed frequency, $F_{exp}$ is the averaged simulated frequency, and $\sigma$ is the standard deviation of the simulated frequencies.
+As a result of these calculations, each publication becomes associated with a set of z-scores corresponding to the journal pairs derived from pairwise combinations of its cited references.
+Positional statistics of z-scores were calculated for each publication, which was then labeled according to conventionality and novelty: (i) HC if the median z-score exceeded the median of median z-scores for all publications and LC if the median z-score was equal to or less than the median of median z-scores for all publications, and (ii) HN if the tenth percentile of z-scores for a publication was less than zero, and LN if the tenth percentile of z-scores for a publication was greater than zero.
+
+To consider the relationship between citation impact, conventionality, and novelty we calculated percentiles for the number of accumulated citations in the first 8 years since publication for each article we studied and stratified.
 We also investigated multiple definitions of hit articles with hits defined as the 1\%, 2\%, 5\%, and 10\% top-cited articles.
@@
 
-\subsection{Model Misspecification and the Attributes of Disciplinary Context} We have invoked model mis-specification arising from disciplinarily irrelevant references as a concern.
-To address this issue, we analyzed the disciplinary composition of the references in our three test datasets, `applied physics', `immunology', and `metabolism' for the years 1985, 1995, and 2005 and observed that 8.4.2\% of the references in the applied physics dataset were classified as belonging to the WoS physical sciences research area.
+\subsection{Model Misspecification and the Attributes of Disciplinary Context} We invoke model mis-specification arising from irrelevant references as a concern when disciplinary subsets are analyzed using a random graph model that generates expected co-citation frequencies from the full body of scientific literature.
+To address this issue, we first assembled three exemplar datasets using keyword searches for the terms `applied physics', `immunology', and `metabolism' (Materials and Methods).
+Using the WoS extended classificatation of 153 subject areas, we then analyzed the disciplinary composition of the references in these three datasets into the five research areas in the Web of Science (life sciences and biomedicine, physical sciences, social sciences, technology, and arts and humanities) for the years 1985, 1995, and 2005.
+We observed that 84.2\% of the references in the applied physics dataset were classified as belonging to the WoS physical sciences research area.
 Similarly, 93.7\% and 92.1\% of the references in the immunology and metabolism datasets belonged to the life sciences and biomedicine research area, indicating strongly that references are more likely belong to the same research area as the publications that cite them.
 
-We  also analyzed the consequences of citation shuffling within a disciplinary set or all of the Web of Science.
+We  next analyzed the consequences of citation shuffling within a disciplinary set or all of the Web of Science.
 References in publications belonging to these three datasets were classified using the WoS Extended Subjects classification of 153 subject areas and summarized as a frequency distribution.
-A single shuffle of the references in these datasets or all the references in the corresponding WoS year slice was performed, using either the rpcs or umsj algorithms, and frequencies computed again.
-The fold change in subject frequencies of references before and after shuffling was calculated for all 153 Subject categories and summarized as boxplots in \ref{fig:be}.
-The data show consistently that disciplinary composition of references is preserved when citation shuffling is conducted within a disciplinary network.
+A single shuffle of the references in these datasets or all the references in the corresponding WoS year slice was performed, using either the rpcs or umsj algorithms, after which subject frequencies were computed again.
+The fold change in subject frequencies of references before and after shuffling was calculated for these groups using all 153 Subject categories and are summarized as boxplots in Fig \ref{fig:be}.
+For example, the applied physics dataset contained 1 reference labeled Genetics and Heredity .
+This proportion was preserved in the intra-network shuffle but increased 1496 times when the WoS background was used as a source of substitution during Monte Carlo simulation with the repcs algorithm.
+Similarly, with the metabolism dataset.which contained one reference labeled Philosophy that was increased to 661 after a single repcs shuffle.
+The data show convincingly that the disciplinary composition of references is preserved when citation shuffling is conducted within a disciplinary network but is significantly altered when the full WoS network is used as a source of substitution.
+A second inference is that the choice of algorithm is not relevant beyond runtime advantage but that the background network used for the shuffle is critical.
 
-We then estimated model mis-specification by calculating the Kullback-Leibler (K-L) divergence between the simulated and observed journal pair frequencies for disciplinary datasets using again, either the references in the disciplinary datasets or those in all of WoS for the simulations~\ref{tab:kld} and observed that K-L divergences when using the WoS background was roughly double compared to the disciplinary network.
+We predicted that model misspecification as measured by the Kullback-Leibler (K-L) Divergence~\citep{kullback_information_1951} between observed and simulated frequencies in a disciplinary network would be less than the divergence for observed and simulated frequencies in the WoS superset.
+The results in Table \ref{tab:kld} indicate that for the set of journals common to both a disciplinary network and the WoS superset, simulations under our model consistently have a lower K-L divergence, roughly half, compared to simulations that draw from the WoS superset (and its attendant substitutions that are ectopic with respect to field and discipline).
+
+We used the criteria of Uzzi to calculate normalized journal pair frequencies (z-scores) and classify publications according to conventionality and novelty.
+We observe that z-score calculations are sensitive to the background network (disciplinary or WoS).
+Figure \ref{fig:scatter} shows that the z-scores for the same journal pair can be positive (negative) when computed with respect to one data set but be negative (positive) for another data set.
+The journal-pair z-scores in Figure \ref{fig:scatter} have consistent signs for both Immunology and WoS data sets in 71.4\% of the instances and different signs for 28.6\% of the journal pairs.
+When a journal-pair z-score is negative with respect to one dataset and positive with respect to another dataset, articles citing that pair are more likely to be deemed novel in the first instance and less likely to be deemed novel in the second instance.
+It seems that any journal pair should either be indicative of novelty or not, but it should never have contradictory implications that depend on the reference dataset.
+We view, therefore, these contradictions as symptomatic of inappropriately sampling from a broad dataset and ignoring observed citation patterns.
+Figure \ref{fig:scatter} reflects that the WoS data set has approximately 44,000 fewer negative z-scores than does the immunology data set, which contributes to its significantly lower percentage of high-novelty articles.
+\emph{The plots I made of the cumulative z-score distributions for Immunology and WoS also could be used to demonstrate this phenomenon, although the scatter plot does this more clearly, and it is more striking.
+The scatter plot also encodes more data, that is, the matched z-scores for each journal pair.}
+
+Further, we stratified publications in these datasets by percentiles using the number of citations accumulated in the first 8 years since publication and according to conventionality and novelty in a second dimension Fig \ref{fig:Fig1} and note that [INSERT WHATEVER WE NOTE].
 
 We addressed this consideration by analyzing disciplinary subsets of the scientific literature, thereby restricting random selection of references to only those references in the disciplinary network being studied.
-What about z-scores? 
+\emph{What about z-scores?} 
 We have conjectured that the approach of Uzzi et al.
@@
 The disciplinary composition of cited references before and after shuffling was measured as frequencies for each of 153 sub-disciplines (from the extended subject classification in WoS) and expressed as fold difference between citation counts grouped by subject for original (o) and shuffled (s) references using the formula (fold\_difference = $ifelse(o > s, o/s, s/o)$) and rounded to the nearest integer.
-Null values were set to 1.
 A fold difference of 1 indicates that citation shuffling did not alter disciplinary composition.
 Data are shown for articles published in 1985.
-All four boxplots are generated from 151 observations.
-Min \& Max values for fold differences were as follows.
-(i) Arts \& Humanities.
-bg\_local (1,2), bg\_allWoS (1, 488) (ii) Life Sciences \& Biomedicine.
-bg\_local(1,1), bg\_allWos (1, 352) Note y-axis: $log_2$ scale.}
+All eight boxplots are generated from 153 observations.
+Null values were set to 1.
+Note y-axis: $log_2$ scale.}
 \label{fig:be}
 \end{figure}
-
-Figure \ref{fig:scatter} shows that the z-scores for the same journal pair can be positive (negative) when computed with respect to one data set but be negative (positive) for another data set.
-The journal-pair z-scores in Figure \ref{fig:scatter} have consistent signs for both Immunology and WoS data sets in 71.4\% of the instances and different signs for 28.6\% of the journal pairs.
-When a journal-pair z-score is negative with respect to one dataset and positive with respect to another dataset, articles citing that pair are more likely to be deemed novel in the first instance and less likely to be deemed novel in the second instance.
-It seems that any journal pair should either be indicative of novelty or not, but it should never have contradictory implications that depend on the reference dataset.
-We view, therefore, these contradictions as symptomatic of inappropriately sampling from a broad dataset and ignoring observed citation patterns.
-Figure \ref{fig:scatter} reflects that the WoS data set has approximately 44,000 fewer negative z-scores than does the immunology data set, which contributes to its significantly lower percentage of high-novelty articles.
-\emph{The plots I made of the cumulative z-score distributions for Immunology and WoS also could be used to demonstrate this phenomenon, although the scatter plot does this more clearly, and it is more striking.
-The scatter plot also encodes more data, that is, the matched z-scores for each journal pair.}
 

### 2019-06-10 cocit_r.tex
fixed citep

@@
 
-\citep{uzzi_atypical_2013} used a novel approach for co-citation analysis using, as input, 17.9 million articles and their cited references, from the Web of Science (WoS)  to characterize a subset of highly cited articles with respect to both novel and conventional combinations of prior research.
+\cite{uzzi_atypical_2013} used a novel approach for co-citation analysis using, as input, 17.9 million articles and their cited references, from the Web of Science (WoS)  to characterize a subset of highly cited articles with respect to both novel and conventional combinations of prior research.
 In this study, co-citation frequencies of references in were calculated and represented as journal pairs (observed co-citation frequencies).

### 2019-06-10 cocit_r.tex

--- 2019-06-08 cocit_r.tex
@@
 %%%%%%%%%%% to be supplied by MIT Press, only %%%%%%%%%%%%%%%%%
-\citation{Betzel, R. F., Fukushima, M.,
+\citation{Betzel, R. F., Fukushima, M.,w
 He, Ye,
@@
 \citep{uzzi_atypical_2013} used a novel approach for co-citation analysis using, as input, 17.9 million articles and their cited references, from the Web of Science (WoS)  to characterize a subset of highly cited articles with respect to both novel and conventional combinations of prior research.
-In this study, co-citation frequencies of references in were calculated and represented as journal pairs (observed co-citation frequencies).
-Expected values of these frequencies were generated from Monte Carlo simulations under a random graph model.
-Observed frequencies were then normalized (shifted and scaled) to averaged expected values from ten simulations and termed \emph{z-scores}, which were interpreted as suggesting conventional thought if positive and novel thought if negative.
+In this study, the frequency with which references were calculated and reduced to journal pairs frequencies (observed co-citation frequencies).
+Expected values were generated from Monte Carlo simulations under a random graph model.
+Observed frequencies were then normalized (shifted and scaled) to averaged expected values from ten simulations and termed as \emph{z-scores}, which were interpreted as indicating conventional thought if positive and novel thought if negative.
 Consequently, every article was associated with multiple z-scores corresponding to co-cited journal pairs in its refernces.
@@
 Thus, HCLN would denote high conventionality and low novelty with all four combinations being possible.
-\cite{uzzi_atypical_2013} observed that HCHN articles were twice as likely to be highly cited, suggesting that novel combinations of ideas flavoring a body of conventional thought were a 'nearly universal` recipe for impact.
+\cite{uzzi_atypical_2013} observed that HCHN articles were twice as likely to be highly cited, suggesting that novel combinations of ideas flavoring a body of conventional thought were a 'nearly universal` feature for impact.
 
@@
 In addition, under this random model, a reference cited over 100 times in a given year is selected with the same probability as a reference cited only once, which appears inconsistent with the power law or lognormal citation distributions described in the literature~\citep{stringer_statistical_2010,perline_strong_2005}.
-Accordingly, the expected value calculations used to characterize articles in terms of conventionality and novelty can be reasonably questioned on grounds of model mis-specification when disciplinary subsets of the WoS are analyzed in the context of expected values generated across all of WoS.
+Accordingly, model mis-specification is likely to arise from the expected value calculations used to generate z-scores and characterize articles in terms of conventionality and novelty when disciplinary subsets of the WoS are analyzed in the context of expected values generated across all of WoS.
 
@@
 
-Despite different methods used to generate expected values, both of these key preceding studies (vide supra) measured co-citation frequencies across the scientific literature without disciplinary constraints and subsequently analyzed disciplinary subsets.
+Despite different methods used to generate expected values, both of these key preceding studies (\emph{vide supra}) measured co-citation frequencies across the scientific literature without disciplinary constraints and subsequently analyzed disciplinary subsets.
 In extending their prior work, we hypothesized that normalization using expected values drawn from datasets focused in disciplinary areas, rather than all of WoS, would reduce model mis-specification.
-Accordingly, we used keyword searches of the scientific literature to create three citation networks themed around academic disciplines.
+Consequently, we used keyword searches of the scientific literature to construct citation networks themed around academic disciplines: \emph{applied physics, immunology, and metabolism}.
 Within these disciplinary frameworks, we calculated observed and expected co-citation frequencies using a refined random graph model and an efficient Monte Carlo simulation algorithm.
+
 Our analysis of these semantically-themed citation networks challenges the assertion of universality.
-Under our conditions of reduced model misspecification, we observe that while HC remains highly correlated with hit articles in the immunology and metabolism datasets, HN is not.
+We demonstrate reduced model misspecification and observe that while HC remains highly correlated with hit articles in the immunology and metabolism datasets, HN is not.
 In addition, while HN is highly correlated with hit articles in applied physics, HC is not.
+Thus, disciplinary networks are different from each other and the full WoS network.
 Beyond variation across disciplines and the case for contextual analysis, we found that the categories demonstrating the highest percentage of hits are not robust with respect to varying parameters that define hit articles and the threshold for highly novel citation patterns.
@@
 PubMed and WoS were searched for articles using search terms, `immunology', `metabolism', and `applied physics'.
-Counts of retrieved publications are shown for each of the three years analyzed.}
+Counts of publications are shown for each of the three years analyzed.}
 \label{tab:disc-datasets}
@@
 Journal pair frequencies were summed across the dataset to create observed frequencies $(F_{obs})$.
+
 We developed a performant citation switching algorithm, \emph{runtime enhanced permuting citation switcher (repcs)} that randomly permuted citations grouped by year of publication to switch citations while preserving the year of publication for both articles and references, the number of publications and the number of references in each dataset and the disciplinary composition of the references in each dataset.
@@
 
-We  next analyzed the consequences of citation shuffling within a disciplinary set or all of the Web of Science.
+A symptom of model misspecification is that random sampling of citations associated with an article do not match with the distribution of citations across the disciplines observed in articles from that discipline.
+\cite{wallace_lariviere_gingras_2012} found that, often, a majority of an article's citations are from the specialty of the article, although that percentage varied among disciplines in the eight specialties they investigated: from approximately 39\% to 89\% for 2006.
+We also analyzed the consequences of citation shuffling within a disciplinary set or all of the Web of Science.
 References in publications belonging to these three datasets were classified using the WoS Extended Subjects classification of 153 subject areas and summarized as a frequency distribution.
@@
 Similarly, with the metabolism dataset.which contained one reference labeled Philosophy that was increased to 661 after a single repcs shuffle.
-The data show convincingly that the disciplinary composition of references is preserved when citation shuffling is conducted within a disciplinary network but is significantly altered when the full WoS network is used as a source of substitution.
+The data show convincingly that the disciplinary composition of references in a network is preserved when citation shuffling is conducted within it but is significantly altered when the full WoS network is used as a source of substitution.
 A second inference is that the choice of algorithm is not relevant beyond runtime advantage but that the background network used for the shuffle is critical.
@@
 \begin{figure}
-\includegraphics[width=\hsize]{Fig1}
-\caption{Fraction of publications with high conventionality (HC) and high novelty (HN) signatures relative to citation count.
-\emph{What follows is the caption from PNAS submission: is any of this useful?}  Effect of Research Discipline,  Background Network,  and Citation Count on Conventionality and Novelty.
+\includegraphics[width=\hsize]{pnas_fig1a}
+\caption{Effect of Research Discipline,  Background Network,  and Citation Count on Conventionality and Novelty.
 Data are shown for the applied physics (18,305), immunology (21,917), metabolism (97,405) and WoS (476,288) networks for 1995.
@@
 \end{figure}
-
-Another symptom of model misspecification is that random sampling of citations associated with an article do not match with the distribution of citations across the disciplines observed in articles from that discipline.
-\citep{wallace_lariviere_gingras_2012} found that, often, a majority of an article's citations are from the specialty of the article, although that percentage varied among disciplines in the eight specialties they investigated: from approximately 39\% to 89\% for 2006.
-\emph{More needed here.}  Similarly, we found that 77.4\% of citations in applied physics articles in 1985 (replace with 1995 data?) were from applied physics.
-\emph{Add references to other datasets.} A random sampling of citations would ideally reflect the percentages from the discipline in question, as well as the percentages of articles from other disciplines.
-
-We investigated the effect of sampling from disciplinary data sets versus more broadly from the WoS on the disciplinary make-up of the citations in articles under random sampling (\emph{sentence needs work but is an example of a transition.}) \emph{Insert text about Figure \ref{fold_effect}, specifically the right-hand side of Figure  \ref{fold_effect} where the fold statistics demonstrate the effect with Uzzi's approach.}
-
-\emph{Insert comment about the left-hand side of Figure \ref{fold_effect} where the disciplinary dataset has resolved the fold issue.}  We also predicted that model misspecification as measured by the Kullback-Leibler (K-L) Divergence~\citep{kullback_information_1951} between observed and simulated frequencies in a disciplinary network would be less than the divergence for observed and simulated frequencies in the WoS superset.
-The results in Table \ref{tab:kld} indicate that for the set of journals common to both a disciplinary network and the WoS superset, simulations under our model consistently have a lower K-L divergence compared to simulations that draw from the WoS superset (and its attendant substitutions that are ectopic with respect to field and discipline).
 
@@
 
-We conclude that Uzzi et al.'s finding of high hit rates in the HNHC category does not hold generally for all datasets and that novel citation patterns are not always indicative of impactful research.
-
+We conclude thathigh hit rates in the HNHC category does not hold generally for all datasets and that conventionality flavored with novelty is not always indicative of impactful research.
 The z-scores that change sign across datasets is either contradictory or an acceptable variation due to the difference in reference sets.
@@
 That fewer z-scores are negative in the WoS dataset relative to the immunology dataset may be directly due to the uniform sampling of references whereby many resulting journal pairs are never observed in the literature and so that the expected frequencies of those observed pairs have lower expected values, thus biasing their z-scores upward.
-In addition, treating citation as a set versus a multiset means that a random model will sample popular citations downward, thus further increasing their z-scores.
+In addition, treating citation as a set versus a multiset means that a random model will sample popular citations downward, thus further increasing their z-scores.\emph{need confirmation from Jim here}.
 
@@
 More significantly, we should question whether the simple approach of defining novelty and conventionality as is done this article and other research is sufficient or whether we should expect such variation in the factors associated with impact as we have observed.
-
-George's point from Slack conversation: ``A concern that surfaced on the drive are the definitions of conventionality and novelty.
-On the one hand we use them- on the other hand you've also pointed out that it isn't that simple.''
 

### 2019-06-10 cocit_r.tex
branch recovered1

@@
 
-Citation and network analysis of  scientific literature reveals information on semantic relationships between publications, collaboration between scientists, and the practice of citation itself~\citep{garfield_citation_1955,de_solla_price_networks_1965,newman_structure_2001,Shi:2010:CHI:1816123.1816131,patience_pmid28560354}.
+Citation and network analysis of  scientific literature reveals information on semantic relationships between publications, collaboration between scientists, and the practice of citation  and TESTING THE MERGE process itself~\citep{garfield_citation_1955,de_solla_price_networks_1965,newman_structure_2001,Shi:2010:CHI:1816123.1816131,patience_pmid28560354}.
 Co-citation, the frequency with which two documents are cited together in other documents provides additional insights, including the identification of semantically related documents, fields, specializations, and new ideas in science~\citep{small_co-citation_1973, marshakova-shaikevich_co-citation_1973,boyack_co-citation_2010, 10.3389/frma.2018.00020}.

### 2019-06-10 cocit_r.tex
rounding off merge

@@
 
-\citep{uzzi_atypical_2013} used a novel approach for co-citation analysis using, as input, 17.9 million articles and their cited references, from the Web of Science (WoS)  to characterize a subset of highly cited articles with respect to both novel and conventional combinations of prior research.
-In this study, the frequency with which references were calculated and reduced to journal pairs frequencies (observed co-citation frequencies).
+\citep{uzzi_atypical_2013} used a novel approach for co-citation analysis, using 17.9 million articles and their cited references from the Web of Science (WoS) as input, to characterize a subset of highly cited articles with respect to both novel and conventional combinations of prior research.
+The frequency with which references were co-cited was calculated and expressed as journal pair frequencies (observed co-citation frequencies).
 Expected values were generated from Monte Carlo simulations under a random graph model.
@@
 A follow-up study by \citep{boyack_vs_uzzi_2014} explored the impact of discipline and journal effects on the definition of conventionality and novelty.
-While their study had some methodological differences in the use of Scopus data rather than WoS data, a smaller dataset, and a $\chi^2$ calculation rather than Monte Carlo simulations to generate expected values of journal pairs, Boyack and Klavans also reported the trend that HCHN is more probable in highly cited papers.
-However, they note that ``only 64.4\%  of  243  WoS  subject  categories'' in the Uzzi {\em et al.} study met the criterion of having the highest probability of hit papers in the HCHN category.
+While their study had some methodological differences in the use of Scopus data rather than WoS data, a smaller dataset, and a $\chi^2$ calculation rather than Monte Carlo simulations to generate expected values of journal pairs, Boyack and Klavans noted strong effects from both disciplines and journals that were not reported by Uzzi et al.
+While they reported the trend that HCHN is more probable in highly cited papers, they observed that ``only 64.4\%  of  243  WoS  subject  categories'' in the Uzzi {\em et al.} study met the criterion of having the highest probability of hit papers in the HCHN category.
 Further, they observed that journals vary widely in terms of size and influence and that 20 journals accounted for nearly 15\% of co-citations in their measurements.
-Lastly, they noted that three multidisciplinary journals accounted for 9.4\% of all atypical combinations, suggesting strong effects from both disciplines and journals that were not reported by Uzzi et al.
+Lastly, they noted that three multidisciplinary journals accounted for 9.4\% of all atypical combinations.
 
-Despite different methods used to generate expected values, both of these key preceding studies (\emph{vide supra}) measured co-citation frequencies across the scientific literature without disciplinary constraints and subsequently analyzed disciplinary subsets.
-In extending their prior work, we hypothesized that normalization using expected values drawn from datasets focused in disciplinary areas, rather than all of WoS, would reduce model mis-specification.
+Despite different methods used to generate expected values, both of these key preceding studies (\emph{vide supra}) measured co-citation frequencies across the scientific literature and normalized them without disciplinary constraints before subsequently analyzing disciplinary subsets.
+We hypothesized that normalization using expected values drawn from datasets focused in disciplinary areas, rather than all of WoS, would reduce model mis-specification.
 Consequently, we used keyword searches of the scientific literature to construct citation networks themed around academic disciplines: \emph{applied physics, immunology, and metabolism}.
@@
 For example, WoS data for year 2005 contained 1,753,174 publications, which after restricting to type Article and considering only those references described above resulted in 916,573 publications, 6,095,594 unique references (set of references), and 17,167,347 total references (multiset of references).
-Given consistent trends in the data, Table \ref{tab:summary_data}, we analyzed the two boundary years (1985 and 2005) and the mid-point (1995) performing 1,000 simulations for each dataset.
-We also calculated the number of times each of these articles was cited in the first 8 years since publication.
+Given consistent trends in the data, Table \ref{tab:summary_data}, we analyzed the two boundary years (1985 and 2005) and the mid-point (1995).
+We also used the number of times each of these articles was cited in the first 8 years since publication as a measure of its impact.
 
@@
 \subsection{Model Misspecification and the Attributes of Disciplinary Context} We invoke model mis-specification arising from irrelevant references as a concern when disciplinary subsets are analyzed using a random graph model that generates expected co-citation frequencies from the full body of scientific literature.
+A symptom of model misspecification is that random sampling of citations associated with an article do not match with the distribution of citations across the disciplines observed in articles from that discipline.
+\cite{wallace_lariviere_gingras_2012} found that, often, a majority of an article's citations are from the specialty of the article, although that percentage varied among disciplines in the eight specialties they investigated: from approximately 39\% to 89\% for 2006.
 To address this issue, we first assembled three exemplar datasets using keyword searches for the terms `applied physics', `immunology', and `metabolism' (Materials and Methods).
@@
 
-A symptom of model misspecification is that random sampling of citations associated with an article do not match with the distribution of citations across the disciplines observed in articles from that discipline.
-\cite{wallace_lariviere_gingras_2012} found that, often, a majority of an article's citations are from the specialty of the article, although that percentage varied among disciplines in the eight specialties they investigated: from approximately 39\% to 89\% for 2006.
  We also analyzed the consequences of citation shuffling within a disciplinary set or all of the Web of Science.
@@
 The data show convincingly that the disciplinary composition of references in a network is preserved when citation shuffling is conducted within it but is significantly altered when the full WoS network is used as a source of substitution.
-A second inference is that the choice of algorithm is not relevant beyond runtime advantage but that the background network used for the shuffle is critical.
+A second inference is that the choice between these two algorithms is not relevant beyond runtime advantage but that the background network used for the shuffle is critical.
 

### 2019-06-11 cocit_r.tex
safety branch chacko:
continuing edits

@@
 \documentclass[NETN]{stjour}
+\usepackage{comment}
 
@@
 
+% CREATED A BRANCH FOR SAFETY %
 %%%%%%%%%%% Article Set-Up %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-Citation and network analysis of  scientific literature reveals information on semantic relationships between publications, collaboration between scientists, and the practice of citation  and TESTING THE MERGE process itself~\citep{garfield_citation_1955,de_solla_price_networks_1965,newman_structure_2001,Shi:2010:CHI:1816123.1816131,patience_pmid28560354}.
+Citation and network analysis of  scientific literature reveals information on semantic relationships between publications, collaboration between scientists, and the practice of citation itself~\citep{garfield_citation_1955,de_solla_price_networks_1965,newman_structure_2001,Shi:2010:CHI:1816123.1816131,patience_pmid28560354}.
 Co-citation, the frequency with which two documents are cited together in other documents provides additional insights, including the identification of semantically related documents, fields, specializations, and new ideas in science~\citep{small_co-citation_1973, marshakova-shaikevich_co-citation_1973,boyack_co-citation_2010, 10.3389/frma.2018.00020}.
 
-\citep{uzzi_atypical_2013} used a novel approach for co-citation analysis, using 17.9 million articles and their cited references from the Web of Science (WoS) as input, to characterize a subset of highly cited articles with respect to both novel and conventional combinations of prior research.
-The frequency with which references were co-cited was calculated and expressed as journal pair frequencies (observed co-citation frequencies).
-Expected values were generated from Monte Carlo simulations under a random graph model.
-Observed frequencies were then normalized (shifted and scaled) to averaged expected values from ten simulations and termed as \emph{z-scores}, which were interpreted as indicating conventional thought if positive and novel thought if negative.
-Consequently, every article was associated with multiple z-scores corresponding to co-cited journal pairs in its refernces.
-For each article, positional statistics of z-scores were calculated to set thresholds for a binary (high/low) classification of conventionality (C) using the median and novelty (N) using the tenth percentile of z-scores within an article.
+\cite{uzzi_atypical_2013} used a novel approach for co-citation analysis to characterize a subset of highly cited articles with respect to both novel and conventional combinations of prior research.
+The frequency with which references were co-cited  in 17.9 million articles and their cited references from the Web of Science (WoS) was calculated and expressed as journal pair frequencies (observed co-citation frequencies).
+Expected co-citation values were generated from Monte Carlo simulations under a random graph model.
+Observed frequencies were then normalized (shifted and scaled) to averaged expected values from ten simulations and termed as \emph{z-scores}.
+Consequently, every article was associated with multiple z-scores corresponding to co-cited journal pairs in its references.
+For each article, positional statistics of z-scores were calculated to set thresholds for a binary (high/low) classification of conventionality (C) using the median z-score of an article and novelty (N) using the tenth percentile of z-scores within an article.
 Thus, HCLN would denote high conventionality and low novelty with all four combinations being possible.
-\cite{uzzi_atypical_2013} observed that HCHN articles were twice as likely to be highly cited, suggesting that novel combinations of ideas flavoring a body of conventional thought were a 'nearly universal` feature for impact.
+The authors observed that HCHN articles were twice as likely to be highly cited, suggesting that novel combinations of ideas flavoring a body of conventional thought were a feature of impact and that `science follows a nearly universal pattern'.
 
 Key to Uzzi {\em et al.}, is their random graph model and its underlying assumptions.
-The citation switching algorithm used to generate a null model elegantly preserves the number of publications, the number of references in each publication, the year of publication of both publications and references, and the disciplinary composition of the references cited in these publications.
-However, random substitution of the references used to generate expected values is equiprobable with respect to disciplinary origin and citation count.
-The model permits substitution of a reference in quantum physics with equal probability by a reference in the related quantum chemistry field or in some entirely different field, such as classical literature, evolutionary biology, or anthropology.
+The citation switching algorithm used to generate expected values from random substitutions is designed to preserve the number of publications, the number of references in each publication, the year of publication of both publications and references, and the disciplinary composition of the references cited in these publications.
+However, substitutions are equiprobable with respect to disciplinary origin and citation count.
+The model permits substitution of a reference in quantum physics with equal probability by a reference in quantum physics, quantum chemistry, classical literature, entomology, or anthropology.
 Such substitutions poorly model the disciplinary nature of scientific endeavor and citation behavior~\citep{wallace_lariviere_gingras_2012,moed_measuring_2010,klavans_research_2017,garfield_1979}.
 In addition, under this random model, a reference cited over 100 times in a given year is selected with the same probability as a reference cited only once, which appears inconsistent with the power law or lognormal citation distributions described in the literature~\citep{stringer_statistical_2010,perline_strong_2005}.
-Accordingly, model mis-specification is likely to arise from the expected value calculations used to generate z-scores and characterize articles in terms of conventionality and novelty when disciplinary subsets of the WoS are analyzed in the context of expected values generated across all of WoS.
+Accordingly, model mis-specification is likely to arise on account of the simulated values not modeling the empirical data very well.
 
-A follow-up study by \citep{boyack_vs_uzzi_2014} explored the impact of discipline and journal effects on the definition of conventionality and novelty.
+A follow-up study by \cite{boyack_vs_uzzi_2014} explored the impact of discipline and journal effects on these definition of conventionality and novelty.
 While their study had some methodological differences in the use of Scopus data rather than WoS data, a smaller dataset, and a $\chi^2$ calculation rather than Monte Carlo simulations to generate expected values of journal pairs, Boyack and Klavans noted strong effects from both disciplines and journals that were not reported by Uzzi et al.
@@
 
-Despite different methods used to generate expected values, both of these key preceding studies (\emph{vide supra}) measured co-citation frequencies across the scientific literature and normalized them without disciplinary constraints before subsequently analyzing disciplinary subsets.
+Despite different methods used to generate expected values, both of these key preceding studies (\emph{vide supra}) measured co-citation frequencies across the scientific literature (the WoS superset) and normalized them without disciplinary constraints before subsequently analyzing disciplinary subsets.
 We hypothesized that normalization using expected values drawn from datasets focused in disciplinary areas, rather than all of WoS, would reduce model mis-specification.
-Consequently, we used keyword searches of the scientific literature to construct citation networks themed around academic disciplines: \emph{applied physics, immunology, and metabolism}.
+Consequently, we used keyword searches of the scientific literature to construct exemplar citation networks themed around academic disciplines: \emph{applied physics, immunology, and metabolism}.
 Within these disciplinary frameworks, we calculated observed and expected co-citation frequencies using a refined random graph model and an efficient Monte Carlo simulation algorithm.
@@
 WoS data stored in ERNIE spans the period 1900-2019 and consists of over 72 million publications.
-For this study, we generated an analytical dataset from years 1985 to 2005 from ERNIE.
+For this study, we generated an analytical dataset from years 1985 to 2005 using data in ERNIE.
 The total number of publications in this dataset was just over 25 million publications (25,134,073), which were then stratified by year of publication.
@@
 \caption{Summary of base WoS Analytical Dataset.The number of publications of type Article (UP), unique references (UR), total references (TR) and the ratio of total references to unique references increases monotonically with each year indicating that both the number of documents and citation activity increase over time.
-Only publications of type Article with at least two references, and references with complete publication data were counted.}
+Only publications of type Article with at least two references, and references with complete publication data were included.}
 \label{tab:summary_data}
@@
 Pubmed IDs (pmids) returned were matched to WoS IDs (wos\_ids) and used to retrieve relevant articles.
-For the applied physics dataset, we directly searched subject labels in WoS for `applied physics'.
+For the applied physics dataset, we directly searched traditional subject labels in WoS for `applied physics'.
 We also examined publications in the five major research areas in the Web of Science; life sciences \& biomedicine, physical sciences, technology, social sciences, arts \& humanities using the extended subcategory classification of 153 sub-groups to categorize disciplinary composition of cited references in the datasets we studied.
@@
 PubMed and WoS were searched for articles using search terms, `immunology', `metabolism', and `applied physics'.
-Counts of publications are shown for each of the three years analyzed.}
+Counts of publications are shown for each of the three years analyzed and expressed in parentheses as a percentage of the total number of publications in our analytical WoS dataset (Table \ref{tab:summary_data}) for that year.}
 \label{tab:disc-datasets}
@@
   \hline
-1985 & 21,606 & 78,998 & 10,298 \\ 
-1995 & 29,320 & 121,247 & 21,012  \\ 
-2005 & 37,296 & 200,052 & 35,600  \\ 
+1985 & 21,606 (5.5\%) & 78,998 (20.2\%) & 10,298 (2.7\%) \\ 
+1995 & 29,320 (5.5\%)  & 121,247 (22.6\%) & 21,012 (3.9\%)  \\ 
+2005 & 37,296 (4.2\%) & 200,052 (22.6\%) & 35,600 (4.0\%)  \\ 
  \hline
@@
 
-We developed a performant citation switching algorithm, \emph{runtime enhanced permuting citation switcher (repcs)} that randomly permuted citations grouped by year of publication to switch citations while preserving the year of publication for both articles and references, the number of publications and the number of references in each dataset and the disciplinary composition of the references in each dataset.
-We used the citation switching algorithm of ~\cite{uzzi_atypical_2013} referred to as \emph{umsj}~\citep{boyack_vs_uzzi_2014}, as a benchmark for the repcs algorithm using code kindly provided by the authors.
-A comparative analysis showed that while 10 simulations of the WoS 1985 dataset (391,860 publications) completed in 2,186 hours using the umsj algorithm, it completed in less than one hour using the repcs algorithm implemented on a Spark cluster.
+For citation shuffling, we developed a performant citation switching algorithm, \emph{runtime enhanced permuting citation switcher (repcs)} that randomly permuted citations grouped by year of publication to switch citations while preserving the year of publication for both articles and references, the number of publications and the number of references in each dataset and the disciplinary composition of the references in each dataset.
+In implementing this approach, our approach differs from umsj in the following ways (i) we sampled citations from a multiset rather than a set in order to reflect the observed frequency of citation (ii) we permitted a substitution to match the original reference in a publication when the random selection process dictated it rather than attempting to enforce that a different reference be substituted (iii) we introduced an error correction step to delete any publications that accumulated duplicate references during the substitution process.
+As a benchmark, we used the citation switching algorithm of ~\cite{uzzi_atypical_2013} referred to by others as \emph{umsj}~\citep{boyack_vs_uzzi_2014}, using code kindly provided by the authors.
+A single comparative analysis showed that while 10 simulations of the WoS 1985 dataset (391,860 publications) completed in 2,186 hours using the umsj algorithm, it completed in less than one hour using the our implementation of the repcs algorithm on a Spark cluster.
+We also tested repcs under comparable conditions to umsj and estimated a runtime advantage of at least two orders of magnitude.
 Using either the repcs or umsj algorithms for 10 simulations resulted in expected value coverage of 75\% of the observed journal pair frequencies.
 Subsequent rounds of development and testing resulted in 99\% coverage of observed journal pairs when 1,000 simulations were conducted.
-The runtime advantage was significant enough that we chose to use the repcs algorithm in our study  and generated expected values averaged from 1,000 simulations for improved coverage for every dataset we analyzed.
+The runtime advantage was significant enough that we chose to use the repcs algorithm in our study  and generated expected values averaged from 1,000 simulations for improved coverage of every dataset we analyzed.
 
-Averaging the result of 1,000 simulations for each dataset studied, z-scores were then calculated for each journal-pair using the formula $(F_{obs} - F_{exp})/\sigma$ where $F_{obs}$ is the observed frequency, $F_{exp}$ is the averaged simulated frequency, and $\sigma$ is the standard deviation of the simulated frequencies.
+Averaging the result of 1,000 simulations for each dataset studied, z-scores were then calculated for each journal-pair using the formula $(F_{obs} - F_{exp})/\sigma$ where $F_{obs}$ is the observed frequency, $F_{exp}$ is the averaged simulated frequency, and $\sigma$ is the standard deviation of the simulated frequencies for a journal pair.
 As a result of these calculations, each publication becomes associated with a set of z-scores corresponding to the journal pairs derived from pairwise combinations of its cited references.
@@
 
-\subsection{Model Misspecification and the Attributes of Disciplinary Context} We invoke model mis-specification arising from irrelevant references as a concern when disciplinary subsets are analyzed using a random graph model that generates expected co-citation frequencies from the full body of scientific literature.
+\subsection{Model Misspecification and the Attributes of Disciplinary Context} \emph{This is where we want to add the additional data about expected values ~2.5\% for AP as an example.} We invoke model mis-specification due to considering disciplinarily irrelevant references as a concern when disciplinary subsets are analyzed using a random graph model that generates expected co-citation frequencies from the WoS superset.
 A symptom of model misspecification is that random sampling of citations associated with an article do not match with the distribution of citations across the disciplines observed in articles from that discipline.
-\cite{wallace_lariviere_gingras_2012} found that, often, a majority of an article's citations are from the specialty of the article, although that percentage varied among disciplines in the eight specialties they investigated: from approximately 39\% to 89\% for 2006.
 To address this issue, we first assembled three exemplar datasets using keyword searches for the terms `applied physics', `immunology', and `metabolism' (Materials and Methods).
@@
 Similarly, 93.7\% and 92.1\% of the references in the immunology and metabolism datasets belonged to the life sciences and biomedicine research area, indicating strongly that references are more likely belong to the same research area as the publications that cite them.
+Our observations are in agreement with \cite{wallace_lariviere_gingras_2012} who found that, often, a majority of an article's citations are from the specialty of the article, although that percentage varied among disciplines in the eight specialties they investigated: from approximately 39\% to 89\% for 2006.
 
@@
 Similarly, with the metabolism dataset.which contained one reference labeled Philosophy that was increased to 661 after a single repcs shuffle.
-The data show convincingly that the disciplinary composition of references in a network is preserved when citation shuffling is conducted within it but is significantly altered when the full WoS network is used as a source of substitution.
+The data show convincingly that the disciplinary composition of references in a network is preserved when citation shuffling is conducted within it but is significantly distorted when the WoS superset is used as a source of substitution.
 A second inference is that the choice between these two algorithms is not relevant beyond runtime advantage but that the background network used for the shuffle is critical.
@@
 \centering
-\includegraphics[width=0.8\linewidth]{background-effect}     
+\includegraphics[width=0.6\linewidth]{background-effect}     
 \caption{\ Intra-network citation shuffling preserves the disciplinary composition of references.
@@
 Data are shown for articles published in 1985.
-All eight boxplots are generated from 153 observations.
+All eight boxplots are generated from 153 observations each.
 Null values were set to 1.
@@
 This study was designed by GC, JB, SD, and TW.
-Simulations and analysis were performed by AD, GC, JB, and SD.
+Simulations and analysis were performed by AD, DLH, GC, JB, and SD.
 Infrastructure and workflows used to generate data used in this study were developed by AD, DK, SL, SD, and GC.

### 2019-06-11 cocit_r.tex
bold restructure

@@
 
-% CREATED A BRANCH FOR SAFETY %
 %%%%%%%%%%% Article Set-Up %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 We demonstrate reduced model misspecification and observe that while HC remains highly correlated with hit articles in the immunology and metabolism datasets, HN is not.
+\emph{needs another sentence referencing Fig 2}.
 In addition, while HN is highly correlated with hit articles in applied physics, HC is not.
@@
 Beyond variation across disciplines and the case for contextual analysis, we found that the categories demonstrating the highest percentage of hits are not robust with respect to varying parameters that define hit articles and the threshold for highly novel citation patterns.
-
-\emph{these remaining sentences require some work}
-The varying citation patterns when sampling from a disciplinary-focused dataset versus a broader dataset due, was a cause of journal pair z-scores changing signs in 28.6\% of instances: the effect of any one of these journal pairs on an article's novelty or conventionality is contradictory between broad and, more narrow disciplinary datasets.
-We contend that the interpretation due to a disciplinary dataset, which preserved citation patterns, is more appropriate and an improvement on current methods.
 
@@
 Using the WoS extended classificatation of 153 subject areas, we then analyzed the disciplinary composition of the references in these three datasets into the five research areas in the Web of Science (life sciences and biomedicine, physical sciences, social sciences, technology, and arts and humanities) for the years 1985, 1995, and 2005.
-We observed that 84.2\% of the references in the applied physics dataset were classified as belonging to the WoS physical sciences research area.
-Similarly, 93.7\% and 92.1\% of the references in the immunology and metabolism datasets belonged to the life sciences and biomedicine research area, indicating strongly that references are more likely belong to the same research area as the publications that cite them.
+We observed that 84.2\% of the references in the applied physics dataset were classified as belonging to the WoS physical sciences research area, which is comparable to 79.5\% for the references in the physical sciences area.
+Similarly, 93.7\% and 92.1\% of the references in the immunology and metabolism datasets belonged to the life sciences and biomedicine research area, again comparable to 89.9\% for the references in the life sciences and biomedicine area.
+\emph{Add in Sitaram's new data}.
+These data indicate strongly that references are more likely belong to the same research area as the publications that cite them.
 Our observations are in agreement with \cite{wallace_lariviere_gingras_2012} who found that, often, a majority of an article's citations are from the specialty of the article, although that percentage varied among disciplines in the eight specialties they investigated: from approximately 39\% to 89\% for 2006.
-
-We also analyzed the consequences of citation shuffling within a disciplinary set or all of the Web of Science.
-References in publications belonging to these three datasets were classified using the WoS Extended Subjects classification of 153 subject areas and summarized as a frequency distribution.
-A single shuffle of the references in these datasets or all the references in the corresponding WoS year slice was performed, using either the rpcs or umsj algorithms, after which subject frequencies were computed again.
-The fold change in subject frequencies of references before and after shuffling was calculated for these groups using all 153 Subject categories and are summarized as boxplots in Fig \ref{fig:be}.
-For example, the applied physics dataset contained 1 reference labeled Genetics and Heredity .
-This proportion was preserved in the intra-network shuffle but increased 1496 times when the WoS background was used as a source of substitution during Monte Carlo simulation with the repcs algorithm.
-Similarly, with the metabolism dataset.which contained one reference labeled Philosophy that was increased to 661 after a single repcs shuffle.
-The data show convincingly that the disciplinary composition of references in a network is preserved when citation shuffling is conducted within it but is significantly distorted when the WoS superset is used as a source of substitution.
-A second inference is that the choice between these two algorithms is not relevant beyond runtime advantage but that the background network used for the shuffle is critical.
-
-We predicted that model misspecification as measured by the Kullback-Leibler (K-L) Divergence~\citep{kullback_information_1951} between observed and simulated frequencies in a disciplinary network would be less than the divergence for observed and simulated frequencies in the WoS superset.
-The results in Table \ref{tab:kld} indicate that for the set of journals common to both a disciplinary network and the WoS superset, simulations under our model consistently have a lower K-L divergence, roughly half, compared to simulations that draw from the WoS superset (and its attendant substitutions that are ectopic with respect to field and discipline).
-
-We used the criteria of Uzzi to calculate normalized journal pair frequencies (z-scores) and classify publications according to conventionality and novelty.
-We observe that z-score calculations are sensitive to the background network (disciplinary or WoS).
-Figure \ref{fig:scatter} shows that the z-scores for the same journal pair can be positive (negative) when computed with respect to one data set but be negative (positive) for another data set.
-The journal-pair z-scores in Figure \ref{fig:scatter} have consistent signs for both Immunology and WoS data sets in 71.4\% of the instances and different signs for 28.6\% of the journal pairs.
-When a journal-pair z-score is negative with respect to one dataset and positive with respect to another dataset, articles citing that pair are more likely to be deemed novel in the first instance and less likely to be deemed novel in the second instance.
-It seems that any journal pair should either be indicative of novelty or not, but it should never have contradictory implications that depend on the reference dataset.
-We view, therefore, these contradictions as symptomatic of inappropriately sampling from a broad dataset and ignoring observed citation patterns.
-Figure \ref{fig:scatter} reflects that the WoS data set has approximately 44,000 fewer negative z-scores than does the immunology data set, which contributes to its significantly lower percentage of high-novelty articles.
-\emph{The plots I made of the cumulative z-score distributions for Immunology and WoS also could be used to demonstrate this phenomenon, although the scatter plot does this more clearly, and it is more striking.
-The scatter plot also encodes more data, that is, the matched z-scores for each journal pair.}
-
-Further, we stratified publications in these datasets by percentiles using the number of citations accumulated in the first 8 years since publication and according to conventionality and novelty in a second dimension Fig \ref{fig:Fig1} and note that [INSERT WHATEVER WE NOTE].
-
-We addressed this consideration by analyzing disciplinary subsets of the scientific literature, thereby restricting random selection of references to only those references in the disciplinary network being studied.
-\emph{What about z-scores?} 
-We have conjectured that the approach of Uzzi et al.
-for generating journal-pair z-scores is misspecified in its sampling from a broad dataset and its disregard for the frequency with which journal pairs are citedOur principal consideration was to restrict model misspecification arising from disciplinarily irrelevant references.
-We addressed this consideration by analyzing disciplinary subsets of the scientific literature, thereby restricting random selection of references to only those references in the disciplinary network being studied.As observed in the Introduction, Monte Carlo simulations that use references from all publications do not account for observed citation practice (sentence needs to be made more eloquent)...
-
-\emph{This paragraph needs work, but I wanted to create a placeholder for the introduction to this subsection.
-It uses some of the passages form the former Chacko subsection.} .
-Like Uzzi et al., we also used a Monte Carlo approach to simulate under a random graph model, although our principal consideration was to restrict model misspecification arising from disciplinarily irrelevant references.
-We addressed this consideration by analyzing disciplinary subsets of the scientific literature, thereby restricting random selection of references to only those references in the disciplinary network being studied.
-In this subsection we demonstrate the effects of model misspecification or Uzzi et al.'s approach and the effectiveness of using disciplinary datasets in resolving the concomitant issues with the former.
 
@@
 
-Note also in Figure \ref{fig:scatter} that many z-scores values are significantly different between the WoS and Immunology datasets, although the density of points near the origin in Figure \ref{fig:scatter} indicates that some journal pairs change signs between the datasets while their magnitudes are not significantly different.
-While no metric is without downside, this observation points to a weakness of measuring novelty based simply on the sign of z-scores where no distinction is made between a small negative value and a large negative value, but a negative value of small magnitude is viewed as being significantly different than a small positive value.
-
-\begin{figure}%[tbhp]
-\centering
-\includegraphics[width=3in]{fig2_scatter_z_scores_flattened.pdf}     %width=.8\linewidth
-\caption{Journal pair z-scores vary with reference dataset.
-Scatter plot points (319,005) indicate journal pair z-scores for the 1995 Immunology dataset along the x-axis and the 1995 Web of Science dataset on the y-axis.
-Black indicates journal pairs whose z-scores have the same sign when computed for both reference datasets while red points indicate the 28.6\% of journal pairs whose z-scores change sign across datasets.
-Regions with deeper hues indicate higher point densities and the histograms show the marginal distributions for each dataset separately.}
-\label{fig:scatter}
-\end{figure}
-
-%\begin{figure*}
-%\begin{tabular}{ccc}
-%\includegraphics[width=2.1in]{SIDoc/figs/scatter_z_scores_metab85_WoS_ZoomIn.pdf} & \includegraphics[width=2.1in]{Fig2H01N10.pdf} & \includegraphics[width=2.1in]{Fig2H05N10.pdf} \\
-%(a) & (b) & (c) \\
-%\end{tabular}
-%\caption{Scatter plot points show journal pair z-scores with respect to the Immunology data set for 1995 on the x-axis and the broad Web of Science on the y-axis.
-Black indicates journal pairs whose z-scores have the same sign when computed for both data sets while red points indicate journal pairs whose z-scores change sign across data sets.
-Regions with deeper hues indicate higher point density.
-The histograms show the marginal distributions of the z-scores for each of the data sets separately.}
-%\label{fig:Fig2}
-%\end{figure*}
-
-The variation in z-scores with respect to the reference datasets causes the percentages of articles denoted as highly conventional and highly novel to be significantly different, as demonstrated in Figure \ref{fig:Fig1}.
-\emph{Insert text about Figure \ref{fig:Fig1}.}
-
-\begin{figure}
-\includegraphics[width=\hsize]{pnas_fig1a}
-\caption{Effect of Research Discipline,  Background Network,  and Citation Count on Conventionality and Novelty.
-Data are shown for the applied physics (18,305), immunology (21,917), metabolism (97,405) and WoS (476,288) networks for 1995.
-The number of publications in each network is shown in parentheses.
-Citation counts shown are cumulative over the first 8 years since publication.
-X-axis: publications were classified into percentile groups based on citation counts (e.g., Top 1 indicates those publications in the top 1\%).
-Y axis: The percent of applications in each group that are high conventionality (HC) and high novelty (HN).
-The z-scores are computed for each disciplinary network based on the selected background network; thus, \emph{imm} denotes the immunology network with immunology z-scores and \emph{imm\_wos} denotes the immunology network with z-scores from WoS z-scores.
-The figure shows striking differences between the WOS network compared to the metabolism and immunology networks: across all networks, the percentage of high conventionality (HC) publications increases with citation counts, while the percentage of high novelty (HN) publications decreases with citation counts for the biological networks but not for WOS.
-\label{fig:Fig1}}
-\end{figure}
+We also analyzed the consequences of citation shuffling within a disciplinary set or all of the Web of Science.
+References in publications belonging to these three datasets were classified using the WoS Extended Subjects classification of 153 subject areas and summarized as a frequency distribution.
+A single shuffle of the references in these datasets or all the references in the corresponding WoS year slice was performed, using either the rpcs or umsj algorithms, after which subject frequencies were computed again.
+The fold change in subject frequencies of references before and after shuffling was calculated for these groups using all 153 Subject categories and are summarized as boxplots in Fig \ref{fig:be}.
+For example, the applied physics dataset contained 1 reference labeled Genetics and Heredity .
+This proportion was preserved in the intra-network shuffle but increased 1496 times when the WoS background was used as a source of substitution during Monte Carlo simulation with the repcs algorithm.
+Similarly, with the metabolism dataset.which contained one reference labeled Philosophy that was increased to 661 after a single repcs shuffle.
+The data show convincingly that the disciplinary composition of references in a network is preserved when citation shuffling is conducted within it but is significantly distorted when the WoS superset is used as a source of substitution.
+A second inference is that the choice between these two algorithms is not relevant beyond runtime advantage but that the background network used for the shuffle is critical.
 
@@
 
+We predicted that model misspecification as measured by the Kullback-Leibler (K-L) Divergence~\citep{kullback_information_1951} between observed and simulated frequencies in a disciplinary network would be less than the divergence for observed and simulated frequencies in the WoS superset.
+The results in Table \ref{tab:kld} indicate that for the set of journals common to both a disciplinary network and the WoS superset, simulations under our model consistently have a lower K-L divergence, roughly half, compared to simulations that draw from the WoS superset (and its attendant substitutions that are ectopic with respect to field and discipline).
+
 \subsection{Novelty and Conventionality as Determinants of Impact in Disciplinary Contexts}
-
 \begin{figure*}
@@
 
-We conclude thathigh hit rates in the HNHC category does not hold generally for all datasets and that conventionality flavored with novelty is not always indicative of impactful research.
+\emph{needs to be expanded}
+We conclude that high hit rates in the HNHC category do not hold generally for all datasets and that conventionality flavored with novelty is not always indicative of impactful research.
 The z-scores that change sign across datasets is either contradictory or an acceptable variation due to the difference in reference sets.
@@
 \newpage
+
+\section{Residual}
+\emph{these remaining sentences require some work}
+The varying citation patterns when sampling from a disciplinary-focused dataset versus a broader dataset due, was a cause of journal pair z-scores changing signs in 28.6\% of instances: the effect of any one of these journal pairs on an article's novelty or conventionality is contradictory between broad and, more narrow disciplinary datasets.
+We contend that the interpretation due to a disciplinary dataset, which preserved citation patterns, is more appropriate and an improvement on current methods.
+
+\begin{figure}
+\includegraphics[width=\hsize]{pnas_fig1a}
+\caption{Effect of Research Discipline,  Background Network,  and Citation Count on Conventionality and Novelty.
+Data are shown for the applied physics (18,305), immunology (21,917), metabolism (97,405) and WoS (476,288) networks for 1995.
+The number of publications in each network is shown in parentheses.
+Citation counts shown are cumulative over the first 8 years since publication.
+X-axis: publications were classified into percentile groups based on citation counts (e.g., Top 1 indicates those publications in the top 1\%).
+Y axis: The percent of applications in each group that are high conventionality (HC) and high novelty (HN).
+The z-scores are computed for each disciplinary network based on the selected background network; thus, \emph{imm} denotes the immunology network with immunology z-scores and \emph{imm\_wos} denotes the immunology network with z-scores from WoS z-scores.
+The figure shows striking differences between the WOS network compared to the metabolism and immunology networks: across all networks, the percentage of high conventionality (HC) publications increases with citation counts, while the percentage of high novelty (HN) publications decreases with citation counts for the biological networks but not for WOS.
+\label{fig:Fig1}}
+\end{figure}
+
+We addressed this consideration by analyzing disciplinary subsets of the scientific literature, thereby restricting random selection of references to only those references in the disciplinary network being studied.
+\emph{What about z-scores?} 
+We have conjectured that the approach of Uzzi et al.
+for generating journal-pair z-scores is misspecified in its sampling from a broad dataset and its disregard for the frequency with which journal pairs are citedOur principal consideration was to restrict model misspecification arising from disciplinarily irrelevant references.
+We addressed this consideration by analyzing disciplinary subsets of the scientific literature, thereby restricting random selection of references to only those references in the disciplinary network being studied.As observed in the Introduction, Monte Carlo simulations that use references from all publications do not account for observed citation practice (sentence needs to be made more eloquent)...
+
+\emph{This paragraph needs work, but I wanted to create a placeholder for the introduction to this subsection.
+It uses some of the passages form the former Chacko subsection.} .
+Like Uzzi et al., we also used a Monte Carlo approach to simulate under a random graph model, although our principal consideration was to restrict model misspecification arising from disciplinarily irrelevant references.
+We addressed this consideration by analyzing disciplinary subsets of the scientific literature, thereby restricting random selection of references to only those references in the disciplinary network being studied.
+In this subsection we demonstrate the effects of model misspecification or Uzzi et al.'s approach and the effectiveness of using disciplinary datasets in resolving the concomitant issues with the former.
+
+Note also in Figure \ref{fig:scatter} that many z-scores values are significantly different between the WoS and Immunology datasets, although the density of points near the origin in Figure \ref{fig:scatter} indicates that some journal pairs change signs between the datasets while their magnitudes are not significantly different.
+While no metric is without downside, this observation points to a weakness of measuring novelty based simply on the sign of z-scores where no distinction is made between a small negative value and a large negative value, but a negative value of small magnitude is viewed as being significantly different than a small positive value.
+
+We used the criteria of Uzzi to calculate normalized journal pair frequencies (z-scores) and classify publications according to conventionality and novelty.
+We observe that z-score calculations are sensitive to the background network (disciplinary or WoS).
+Figure \ref{fig:scatter} shows that the z-scores for the same journal pair can be positive (negative) when computed with respect to one data set but be negative (positive) for another data set.
+The journal-pair z-scores in Figure \ref{fig:scatter} have consistent signs for both Immunology and WoS data sets in 71.4\% of the instances and different signs for 28.6\% of the journal pairs.
+When a journal-pair z-score is negative with respect to one dataset and positive with respect to another dataset, articles citing that pair are more likely to be deemed novel in the first instance and less likely to be deemed novel in the second instance.
+It seems that any journal pair should either be indicative of novelty or not, but it should never have contradictory implications that depend on the reference dataset.
+We view, therefore, these contradictions as symptomatic of inappropriately sampling from a broad dataset and ignoring observed citation patterns.
+Figure \ref{fig:scatter} reflects that the WoS data set has approximately 44,000 fewer negative z-scores than does the immunology data set, which contributes to its significantly lower percentage of high-novelty articles.
+\emph{The plots I made of the cumulative z-score distributions for Immunology and WoS also could be used to demonstrate this phenomenon, although the scatter plot does this more clearly, and it is more striking.
+The scatter plot also encodes more data, that is, the matched z-scores for each journal pair.}
+
+\begin{figure}%[tbhp]
+\centering
+\includegraphics[width=3in]{fig2_scatter_z_scores_flattened.pdf}     %width=.8\linewidth
+\caption{Journal pair z-scores vary with reference dataset.
+Scatter plot points (319,005) indicate journal pair z-scores for the 1995 Immunology dataset along the x-axis and the 1995 Web of Science dataset on the y-axis.
+Black indicates journal pairs whose z-scores have the same sign when computed for both reference datasets while red points indicate the 28.6\% of journal pairs whose z-scores change sign across datasets.
+Regions with deeper hues indicate higher point densities and the histograms show the marginal distributions for each dataset separately.}
+\label{fig:scatter}
+\end{figure}
+
+%\begin{figure*}
+%\begin{tabular}{ccc}
+%\includegraphics[width=2.1in]{SIDoc/figs/scatter_z_scores_metab85_WoS_ZoomIn.pdf} & \includegraphics[width=2.1in]{Fig2H01N10.pdf} & \includegraphics[width=2.1in]{Fig2H05N10.pdf} \\
+%(a) & (b) & (c) \\
+%\end{tabular}
+%\caption{Scatter plot points show journal pair z-scores with respect to the Immunology data set for 1995 on the x-axis and the broad Web of Science on the y-axis.
+Black indicates journal pairs whose z-scores have the same sign when computed for both data sets while red points indicate journal pairs whose z-scores change sign across data sets.
+Regions with deeper hues indicate higher point density.
+The histograms show the marginal distributions of the z-scores for each of the data sets separately.}
+%\label{fig:Fig2}
+%\end{figure*}
+
+The variation in z-scores with respect to the reference datasets causes the percentages of articles denoted as highly conventional and highly novel to be significantly different, as demonstrated in Figure \ref{fig:Fig1}.
+\emph{Insert text about Figure \ref{fig:Fig1}.}
+
 %%%%%%%%%%%%%%%%%%%%%%%

### 2019-06-11 cocit_r.tex
bold restructure
edited last paragraph of introduction

@@
 
-Our analysis of these semantically-themed citation networks challenges the assertion of universality.
-We demonstrate reduced model misspecification and observe that while HC remains highly correlated with hit articles in the immunology and metabolism datasets, HN is not.
-\emph{needs another sentence referencing Fig 2}.
-In addition, while HN is highly correlated with hit articles in applied physics, HC is not.
-Thus, disciplinary networks are different from each other and the full WoS network.
-Beyond variation across disciplines and the case for contextual analysis, we found that the categories demonstrating the highest percentage of hits are not robust with respect to varying parameters that define hit articles and the threshold for highly novel citation patterns.
+Our analyses, using three different techniques, provides substantial evidence that constraining the reference substitutions to the disciplinary subnetwork reduces model mis-specification compared to treating all substitutions within WoS as equiprobable (cite figures).
+Furthermore, re-analyses of the semantically-themed
+ citation networks under the improved model reveals strikingly different trends than those 
+ observed by Uzzi {\em et al.}.
+For example, while Uzzi et al.
+claimed that highly cited articles are more likely to be both HC and HN than expected, and that this trend held across all subdisciplines, we find that these trends vary with the subdiscipline so that no universal trends can be established.
+Specifically,
+ HC remains highly correlated with highly cited articles in the immunology and metabolism datasets but not with applied physics, and HN is highly correlated with highly cited articles in applied physics but not with immunology and metabolism.
+ Thus, disciplinary networks are different from each other, and trends that hold for the full WoS network do not hold for even large subnetworks (such as metabolism). 
+ Furthermore, we also found that the categories HC, HN, etc.,  demonstrating the highest percentage of highly cited articles are not robust with respect to varying thresholds for high citation counts or for highly novel citation patterns.
+ Overall, our study, although limited to three subnetworks, suggests that  co-citation analysis, while useful in many regards, cannot be used to provide universal features in scholarship, due to important differences between disciplines and between publications.
 
@@
 We also used the number of times each of these articles was cited in the first 8 years since publication as a measure of its impact.
-
+\vspace{-4mm}
 % latex table generated in R 3.5.3 by xtable 1.8-4 package
@@
 \centering
+\scalebox{0.7}{
 \begin{tabular}{|r rrrr|}
@@
  \hline
-\end{tabular}
+\end{tabular}}
+\vspace{-4mm}%Put here to reduce too much white space after your table 
 \end{table}
@@
 We also examined publications in the five major research areas in the Web of Science; life sciences \& biomedicine, physical sciences, technology, social sciences, arts \& humanities using the extended subcategory classification of 153 sub-groups to categorize disciplinary composition of cited references in the datasets we studied.
-
+\vspace{-2 mm}
 \begin{table}[ht]
@@
 \end{tabular}
+\vspace{-6mm}
 \end{table}

### 2019-06-12 cocit_r.tex
multiple edits across document

@@
 
-\keywords{(co-citation analysis, bibliometrics, random graphs )}
+\keywords{co-citation analysis, bibliometrics, random graphs }
 
@@
 Despite different methods used to generate expected values, both of these key preceding studies (\emph{vide supra}) measured co-citation frequencies across the scientific literature (the WoS superset) and normalized them without disciplinary constraints before subsequently analyzing disciplinary subsets.
-We hypothesized that normalization using expected values drawn from datasets focused in disciplinary areas, rather than all of WoS, would reduce model mis-specification.
+In other words, the concerns raised above about mis-specification resulting from treating
+all references as equiprobable, independent of discipline, apply to \cite{boyack_vs_uzzi_2014} as well.
+ We hypothesized that modifying the normalization to constrain references to be drawn only from the disciplinary citation network,   rather than all of WoS, would reduce model mis-specification.
 Consequently, we used keyword searches of the scientific literature to construct exemplar citation networks themed around academic disciplines: \emph{applied physics, immunology, and metabolism}.
@@
 
-Our analyses, using three different techniques, provides substantial evidence that constraining the reference substitutions to the disciplinary subnetwork reduces model mis-specification compared to treating all substitutions within WoS as equiprobable (cite figures).
-Furthermore, re-analyses of the semantically-themed
+Our analyses, using three different techniques, provides substantial evidence that constraining the reference substitutions to the disciplinary subnetwork reduces model mis-specification compared to treating all substitutions within WoS as equiprobable.
+Furthermore, re-analyses of these three semantically-themed
  citation networks  under the improved model reveals strikingly different trends than those 
- observed by Uzzi {\em et al.}.
-For example, while Uzzi et al.
-claimed that highly cited articles are more likely to be both HC and HN than expected, and that this trend held across all subdisciplines, we find that these trends vary with the subdiscipline so that no universal trends can be established.
+ observed by Uzzi {\em et al.} 
+ For example, while Uzzi {\em et al.}~claimed that highly cited articles are more likely to be both HC and HN than expected, and that this trend held across all subdisciplines, we find that these trends vary with the subdiscipline so that no universal trends can be established.
 Specifically,
@@
 For example, WoS data for year 2005 contained 1,753,174 publications, which after restricting to type Article and considering only those references described above resulted in 916,573 publications, 6,095,594 unique references (set of references), and 17,167,347 total references (multiset of references).
-Given consistent trends in the data, Table \ref{tab:summary_data}, we analyzed the two boundary years (1985 and 2005) and the mid-point (1995).
+Given consistent trends in the data (Table \ref{tab:summary_data}), we analyzed the two boundary years (1985 and 2005) and the mid-point (1995).
 We also used the number of times each of these articles was cited in the first 8 years since publication as a measure of its impact.
@@
 Analysis was performed on publications from 1985, 1995, and 2005.
-Building upon prior work~\cite{uzzi_atypical_2013}, all ${n \choose 2}$ reference pairs were generated for each publication, where $n$ is the number of cited references in the publication.
+Building upon prior work~\citep{uzzi_atypical_2013}, all ${n \choose 2}$ reference pairs were generated for each publication, where $n$ is the number of cited references in the publication.
 These reference pairs were then mapped to the journals they were published in using ISSN numbers as identifiers.
@@
 
-For citation shuffling, we developed a performant citation switching algorithm, \emph{runtime enhanced permuting citation switcher (repcs)} that randomly permuted citations grouped by year of publication to switch citations while preserving the year of publication for both articles and references, the number of publications and the number of references in each dataset and the disciplinary composition of the references in each dataset.
-In implementing this approach, our approach differs from umsj in the following ways (i) we sampled citations from a multiset rather than a set in order to reflect the observed frequency of citation (ii) we permitted a substitution to match the original reference in a publication when the random selection process dictated it rather than attempting to enforce that a different reference be substituted (iii) we introduced an error correction step to delete any publications that accumulated duplicate references during the substitution process.
-As a benchmark, we used the citation switching algorithm of ~\cite{uzzi_atypical_2013} referred to by others as \emph{umsj}~\citep{boyack_vs_uzzi_2014}, using code kindly provided by the authors.
-A single comparative analysis showed that while 10 simulations of the WoS 1985 dataset (391,860 publications) completed in 2,186 hours using the umsj algorithm, it completed in less than one hour using the our implementation of the repcs algorithm on a Spark cluster.
-We also tested repcs under comparable conditions to umsj and estimated a runtime advantage of at least two orders of magnitude.
-Using either the repcs or umsj algorithms for 10 simulations resulted in expected value coverage of 75\% of the observed journal pair frequencies.
+For citation shuffling, we developed a performant citation switching algorithm, \emph{runtime enhanced permuting citation switcher (repcs)}, that randomly permuted citations grouped by year of publication to switch citations while preserving the year of publication for both articles and references, the number of publications and the number of references in each dataset and the disciplinary composition of the references in each dataset.
+In implementing this approach, our approach differs from the approach in \cite{uzzi_atypical_2013}, in the following ways (i) we sampled citations proportional to their citation frequency (equivalently, from a multiset rather than a set) in order to better reflect citation practice,  (ii) we permitted a substitution to match the original reference in a publication when the random selection process dictated it rather than attempting to enforce that a different reference be substituted, and (iii) we introduced an error correction step to delete any publications that accumulated duplicate references during the substitution process.
+As a benchmark, we used the citation switching algorithm of ~\cite{uzzi_atypical_2013}, henceforth referred to  as \emph{umsj} (as also done in ~\citep{boyack_vs_uzzi_2014}), using code kindly provided by the authors.
+A single comparative analysis showed that while 10 simulations of the WoS 1985 dataset (391,860 publications) completed in 2,186 hours using the \emph{umsj} algorithm, it completed in less than one hour using the our implementation of the \emph{repcs}   algorithm on a Spark  cluster.
+We also tested \emph{repcs}  under comparable conditions to \emph{umsj} and estimated a runtime advantage of at least two orders of magnitude.
+Using either the \emph{repcs}   or \emph{umsj} algorithms for 10 simulations resulted in expected value coverage of 75\% of the observed journal pair frequencies.
 Subsequent rounds of development and testing resulted in 99\% coverage of observed journal pairs when 1,000 simulations were conducted.
-The runtime advantage was significant enough that we chose to use the repcs algorithm in our study  and generated expected values averaged from 1,000 simulations for improved coverage of every dataset we analyzed.
+The runtime advantage was significant enough that we chose to use the \emph{repcs}   algorithm in our study  and generated expected values averaged from 1,000 simulations for improved coverage of every dataset we analyzed.
 
@@
 
-\subsection{Model Misspecification and the Attributes of Disciplinary Context} \emph{This is where we want to add the additional data about expected values ~2.5\% for AP as an example.} We invoke model mis-specification due to considering disciplinarily irrelevant references as a concern when disciplinary subsets are analyzed using a random graph model that generates expected co-citation frequencies from the WoS superset.
+\subsection{Model Misspecification and the Attributes of Disciplinary Context} \textcolor{blue}{Tandy: I think this is where we can do a statistical test, and show that these numbers are highly unlikely under the random model.} \emph{This is where we want to add the additional data about expected values ~2.5\% for AP as an example.}
+
+We invoke model mis-specification due to considering disciplinarily irrelevant references as a concern when disciplinary subsets are analyzed using a random graph model that generates expected co-citation frequencies from the WoS superset.
 A symptom of model misspecification is that random sampling of citations associated with an article do not match with the distribution of citations across the disciplines observed in articles from that discipline.
 To address this issue, we first assembled three exemplar datasets using keyword searches for the terms `applied physics', `immunology', and `metabolism' (Materials and Methods).
-Using the WoS extended classificatation of 153 subject areas, we then analyzed the disciplinary composition of the references in these three datasets into the five research areas in the Web of Science (life sciences and biomedicine, physical sciences, social sciences, technology, and arts and humanities) for the years 1985, 1995, and 2005.
+Using the WoS extended classification of 153 subject areas, we then analyzed the disciplinary composition of the references in these three datasets into the five research areas in the Web of Science (life sciences and biomedicine, physical sciences, social sciences, technology, and arts and humanities) for the years 1985, 1995, and 2005.
 We observed that 84.2\% of the references in the applied physics dataset were classified as belonging to the WoS physical sciences research area, which is comparable to 79.5\% for the references in the physical sciences area.
@@
 \emph{Add in Sitaram's new data}.
-These data indicate strongly that references are more likely belong to the same research area as the publications that cite them.
+These data indicate strongly that references are likely to belong to the same research area as the publications that cite them.
 Our observations are in agreement with \cite{wallace_lariviere_gingras_2012} who found that, often, a majority of an article's citations are from the specialty of the article, although that percentage varied among disciplines in the eight specialties they investigated: from approximately 39\% to 89\% for 2006.
@@
 \caption{\ Intra-network citation shuffling preserves the disciplinary composition of references.
-Publications of type Article belonging to the three disciplinary networks (i) Applied Physics (ii) Immunology (iii) Metabolism were subject to a single shuffle of all their cited references using either the cited references in these networks as a source of random substitutions (bg\_local) or references from all articles in WoS (bg\_allWoS).
-Citation shuffling was performed using either our algorithm (repcs) or that of Uzzi (umsj).
-The disciplinary composition of cited references before and after shuffling was measured as frequencies for each of 153 sub-disciplines (from the extended subject classification in WoS) and expressed as fold difference between citation counts grouped by subject for original (o) and shuffled (s) references using the formula (fold\_difference = $ifelse(o > s, o/s, s/o)$) and rounded to the nearest integer.
-A fold difference of 1 indicates that citation shuffling did not alter disciplinary composition.
+Publications of type Article belonging to the three disciplinary networks (Applied Physics, Immunology, and  Metabolism) were subject to a single shuffle of all their cited references using either the cited references in these networks as a source of random substitutions (bg\_local) or references from all articles in WoS (bg\_allWoS).
+Citation shuffling was performed using either our algorithm (\emph{repcs})
+ or that of Uzzi et al.~(\emph{umsj}).
+The disciplinary composition of cited references before and after shuffling was measured as frequencies for each of 153 sub-disciplines (from the extended subject classification in WoS) and expressed as a fold difference between citation counts grouped by subject for original (o) and shuffled (s) references using the formula (fold\_difference = $ifelse(o > s, o/s, s/o)$) and rounded to the nearest integer.
+A fold difference of $1$ indicates that citation shuffling did not alter disciplinary composition.
 Data are shown for articles published in 1985.
 All eight boxplots are generated from 153 observations each.
-Null values were set to 1.
+Null values were set to $1$.
 Note y-axis: $log_2$ scale.}
@@
 References in publications belonging to these three datasets were classified using the WoS Extended Subjects classification of 153 subject areas and summarized as a frequency distribution.
-A single shuffle of the references in these datasets or all the references in the corresponding WoS year slice was performed, using either the rpcs or umsj algorithms, after which subject frequencies were computed again.
+A single shuffle of the references in these datasets or all the references in the corresponding WoS year slice was performed, using either the \emph{repcs}  or \emph{umsj} algorithms, after which subject frequencies were computed again.
 The fold change in subject frequencies of references before and after shuffling was calculated for these groups using all 153 Subject categories and are summarized as boxplots in Fig \ref{fig:be}.
 For example, the applied physics dataset contained 1 reference labeled Genetics and Heredity .
-This proportion was preserved in the intra-network shuffle but increased 1496 times when the WoS background was used as a source of substitution during Monte Carlo simulation with the repcs algorithm.
-Similarly, with the metabolism dataset.which contained one reference labeled Philosophy that was increased to 661 after a single repcs shuffle.
+This proportion was preserved in the intra-network shuffle but increased 1496 times when the WoS background was used as a source of substitution during Monte Carlo simulation with the \emph{repcs}   algorithm.
+Similarly, with the metabolism dataset.which contained one reference labeled Philosophy that was increased to 661 after a single \emph{repcs}  shuffle.
 The data show convincingly that the disciplinary composition of references in a network is preserved when citation shuffling is conducted within it but is significantly distorted when the WoS superset is used as a source of substitution.
@@
 \includegraphics[width=1.5in]{Fig2H01N10.pdf} & \includegraphics[width=1.5in]{Fig2H10N10.pdf} \\
-(a) & (b) \\
+(a) Top 1\% of cited articles & (b) Top 10\% of cited articles \\
 \end{tabular}
@@
 The results for the WoS data set mirrored previous results from Uzzi et al.
-~\cite{uzzi_atypical_2013} where the highest hit rate was for the HNHC category.
+~\citep{uzzi_atypical_2013} where the highest hit rate was for the HNHC category.
 The highest hit rates for the immunology dataset, in contrast, are in the LNHC category.
@@
 
-Contrary to Uzzi et al.
-we found the category displaying the highest hit rate to be sensitive to the experimental parameter settings, which included the percentage of articles deemed to be hits and the percentile of articles' z-score distributions that delineated between articles of low novelty and high novelty.
+Contrary to Uzzi et al., we found the category displaying the highest hit rate to be sensitive to the experimental parameter settings, which included the percentage of articles deemed to be hits and the percentile of articles' z-score distributions that delineated between articles of low novelty and high novelty.
 Faced with this lack of robustness, we are confronted with the necessity of defining defendable parameters, if possible, that determine novelty and conventionalty.
@@
 
+\bibliography{cocit_r}
+
 \newpage
-
 \section{Residual}
@@
 \includegraphics[width=3in]{fig2_scatter_z_scores_flattened.pdf}     %width=.8\linewidth
-\caption{Journal pair z-scores vary with reference dataset.
-Scatter plot points (319,005) indicate journal pair z-scores for the 1995 Immunology dataset along the x-axis and the 1995 Web of Science dataset on the y-axis.
-Black indicates journal pairs whose z-scores have the same sign when computed for both reference datasets while red points indicate the 28.6\% of journal pairs whose z-scores change sign across datasets.
-Regions with deeper hues indicate higher point densities and the histograms show the marginal distributions for each dataset separately.}
+\caption{Journal pair z-scores vary with background network. 
+Scatter plot points (319,005) indicate journal pair z-scores for the 1995 Immunology dataset with two different background networks: the x-axis is based on the local network (1995 Immunology) and the y-axis is based on the entire Web of Science network.
+Black indicates journal pairs whose z-scores have the same sign when computed for both background networks, while red points indicate the 28.6\% of journal pairs whose z-scores change sign across networks.
+Regions with deeper hues indicate higher point densities.
+} %and the histograms show the marginal distributions for each dataset separately.}
 \label{fig:scatter}
@@
 
-\bibliography{cocit_r}
+%\bibliography{cocit_r}
 

### 2019-06-12 cocit_r.tex
multiple edits

@@
 A single shuffle of the references in these datasets or all the references in the corresponding WoS year slice was performed, using either the \emph{repcs}  or \emph{umsj} algorithms, after which subject frequencies were computed again.
-The fold change in subject frequencies of references before and after shuffling was calculated for these groups using all 153 Subject categories and are summarized as boxplots in Fig \ref{fig:be}.
-For example, the applied physics dataset contained 1 reference labeled Genetics and Heredity .
-This proportion was preserved in the intra-network shuffle but increased 1496 times when the WoS background was used as a source of substitution during Monte Carlo simulation with the \emph{repcs}   algorithm.
-Similarly, with the metabolism dataset.which contained one reference labeled Philosophy that was increased to 661 after a single \emph{repcs}  shuffle.
-The data show convincingly that the disciplinary composition of references in a network is preserved when citation shuffling is conducted within it but is significantly distorted when the WoS superset is used as a source of substitution.
-A second inference is that the choice between these two algorithms is not relevant beyond runtime advantage but that the background network used for the shuffle is critical.
+The fold change in subject frequencies of references before and after shuffling was calculated for these groups using all 153 subject categories and are summarized as boxplots in Fig \ref{fig:be}.
+For example, the applied physics dataset contained one reference labeled Genetics and Heredity, but after the shuffle (using the WoS background), there were 1496 references labeled Genetics and Heredity.
+%This proportion was preserved in the intra-network shuffle but increased 1496 times when the WoS background was used as a source of substitution during the Monte Carlo simulation with the \emph{repcs}   algorithm.
+Similarly,  the metabolism dataset  contained one reference labeled Philosophy, but after a single shuffle (again using the WoS background), there were   661 occurrences with this label.
+%after a single \emph{repcs}  shuffle. 
+The data show convincingly that the disciplinary composition of references in a network is preserved when citation shuffling is constrained to the subnetwork, but is significantly distorted when the WoS superset is used as a source of substitution.
+A second inference is that the choice between these two algorithms is not relevant (except for running time considerations), and that the background network used for the shuffle is critical.
 
@@
 between empirical and simulated journal pair frequencies were computed for the years 1985, 1995, and 2005 for the three disciplinary datasets (applied\_physics, immunology, and metabolism) using either the disciplinary network as background or the WoS superset (all\_wos) to generate the null model (Background).
-K-L divergence was calculated using the R seewave package with a base (logarithm) of 2.
-The ratio between the K-L divergence for disciplinary networks versus the full WoS ranges from 1.96 to 2.77 and is greater than 2.0 for eight out of nine cases, strongly suggesting that simulations that constrain substitutions to the given disciplinary network better model the observed data.}
+K-L divergence was calculated using the R seewave package \citep{seewave2008} with a base (logarithm) of 2.
+}
 \label{tab:kld}
 \centering
-\begin{tabular}{|r lrlr r|}
+\begin{tabular}{ccccccc} 
   \hline
- & Disciplinary Network & Year & Background & K-L Divergence & Ratio \\ 
+ Disciplinary Network & Year & Background & K-L Divergence & Ratio \\ 
   \hline
-1 & appl\_physics & 1985 & appl\_physics & 1.21 &  \\ 
-  2 &  & 1985 & all\_wos & 2.37 & 1.96 \\ 
-  3 &  & 1995 & appl\_physics & 0.86 &  \\ 
-  4 &  & 1995 & all\_wos & 2.37 & 2.77 \\ 
-  5 &  & 2005 & appl\_physics & 0.95 &  \\ 
-  6 &  & 2005 & all\_wos & 2.35 & 2.47 \\ 
+ appl\_physics & 1985 & appl\_physics & 1.21 &  \\ 
+  & 1985 & all\_wos & 2.37 & 1.96 \\ 
+  & 1995 & appl\_physics & 0.86 &  \\ 
+  & 1995 & all\_wos & 2.37 & 2.77 \\ 
+  & 2005 & appl\_physics & 0.95 &  \\ 
+  & 2005 & all\_wos & 2.35 & 2.47 \\ 
     \hline
-  7 & immunology & 1985 & immunology & 0.75 &  \\ 
-  8 &  & 1985 & all\_wos & 1.68 & 2.24 \\ 
-  9 &  & 1995 & immunology & 0.78 &  \\ 
-  10 &  & 1995 & all\_wos & 1.70 & 2.19 \\ 
-  11 &  & 2005 & immunology & 0.73 &  \\ 
-  12 &  & 2005 & all\_wos & 1.92 & 2.63 \\ 
+  immunology & 1985 & immunology & 0.75 &  \\ 
+  & 1985 & all\_wos & 1.68 & 2.24 \\ 
+   & 1995 & immunology & 0.78 &  \\ 
+   & 1995 & all\_wos & 1.70 & 2.19 \\ 
+   & 2005 & immunology & 0.73 &  \\ 
+  & 2005 & all\_wos & 1.92 & 2.63 \\ 
     \hline
-  13 & metabolism & 1985 & metabolism & 1.11 &  \\ 
-  14 &  & 1985 & all\_wos & 2.24 & 2.02 \\ 
-  15 &  & 1995 & metabolism & 1.07 &  \\ 
-  16 &  & 1995 & all\_wos & 2.33 & 2.17 \\ 
-  17 &  & 2005 & metabolism & 1.19 &  \\ 
-  18 &  & 2005 & all\_wos & 2.60 & 2.18 \\ 
+ metabolism & 1985 & metabolism & 1.11 &  \\ 
+   & 1985 & all\_wos & 2.24 & 2.02 \\ 
+  & 1995 & metabolism & 1.07 &  \\ 
+  & 1995 & all\_wos & 2.33 & 2.17 \\ 
+     & 2005 & metabolism & 1.19 &  \\ 
+   & 2005 & all\_wos & 2.60 & 2.18 \\ 
    \hline
@@
 
-We predicted that model misspecification as measured by the Kullback-Leibler (K-L) Divergence~\citep{kullback_information_1951} between observed and simulated frequencies in a disciplinary network would be less than the divergence for observed and simulated frequencies in the WoS superset.
-The results in Table \ref{tab:kld} indicate that for the set of journals common to both a disciplinary network and the WoS superset, simulations under our model consistently have a lower K-L divergence, roughly half, compared to simulations that draw from the WoS superset (and its attendant substitutions that are ectopic with respect to field and discipline).
+We predicted that model misspecification, as measured by the Kullback-Leibler (K-L) Divergence~\citep{kullback_information_1951} between observed and simulated frequencies, constraining  reference substitutions to the disciplinary subnetwork would be less than the
+model misspecification when substitutions are drawn equiprobably from all of 
+the WoS superset. 
+The results in Table \ref{tab:kld} indicate that for the set of journals common to both a disciplinary network and the WoS superset,  confirm this prediction: simulations under our model (which constrains substitutions to the
+disciplinary subnetwork) consistently have a lower K-L divergence compared to simulations that draw from the WoS superset. 
+Furthermore, the K-L divergence for  the unconstrained model (where the references are equiprobable and allowed to be taken from all of WoS) is generally twice as large as the K-L divergence for the models where the references are constrained to  the disciplinary subnetworks (a ratio of 1.96 to 2.77,  and  greater than 2.0 for eight out of nine cases), demonstrating that simulations that constrain substitutions to the given disciplinary network better model the observed data.
 
@@
 The number of data points in the immunology, applied physics, and WoS data sets are 21,917, 18,305, and 476,288, respectively.
-The results for the WoS data set mirrored previous results from Uzzi et al.
-~\citep{uzzi_atypical_2013} where the highest hit rate was for the HNHC category.
+The results for the WoS data set mirrored previous results from \cite{uzzi_atypical_2013}, where the highest hit rate was for the HNHC category.
 The highest hit rates for the immunology dataset, in contrast, are in the LNHC category.
@@
 \centering
-\caption[Hit Rates]{Hit Rates by Category. The last four columns indicate the proportion of publications that are hits for each respective category.} \label{Tab:HitRate}
+\caption[Hit Rates]{Hit Rates by Category for the 1995 datasets. The last four columns indicate the proportion of publications that are hits for each respective category.} \label{Tab:HitRate}
 \begin{tabular}{crrrrrrr}
@@
 We conclude that high hit rates in the HNHC category do not hold generally for all datasets and that conventionality flavored with novelty is not always indicative of impactful research. 
-The z-scores that change sign across datasets is either contradictory or an acceptable variation due to the difference in reference sets.
+%The z-scores that change sign across datasets is either contradictory or an acceptable variation due to the difference in reference sets.
 We contend that it is the former because the inappropriate substitution of citations with those from disciplines that are implausible and because the observed citation frequencies are ignored.
-That fewer z-scores are negative in the WoS dataset relative to the immunology dataset may be directly due to the uniform sampling of references whereby many resulting journal pairs are never observed in the literature and so that the expected frequencies of those observed pairs have lower expected values, thus biasing their z-scores upward.
+That fewer z-scores are negative in the WoS dataset relative to the immunology dataset may be directly due to the uniform sampling of references, whereby many resulting journal pairs are never observed in the literature and so the expected frequencies of those observed pairs have lower expected values, thus biasing their z-scores upward.
 In addition, treating citation as a set versus a multiset means that a random model will sample popular citations downward, thus further increasing their z-scores.\emph{need confirmation from Jim here}.
@@
 Contrary to Uzzi et al., we found the category displaying the highest hit rate to be sensitive to the experimental parameter settings, which included the percentage of articles deemed to be hits and the percentile of articles' z-score distributions that delineated between articles of low novelty and high novelty.
-Faced with this lack of robustness, we are confronted with the necessity of defining defendable parameters, if possible, that determine novelty and conventionalty.
+Faced with this lack of robustness, we are confronted with the necessity of defining defendable parameters, if possible, that determine novelty and conventionality.
 More significantly, we should question whether the simple approach of defining novelty and conventionality as is done this article and other research is sufficient or whether we should expect such variation in the factors associated with impact as we have observed.
@@
 We are grateful to Kevin Boyack and Dick Klavans for constructively critical discussions.
-We thank the authors of Uzzi et al.
-(2013) for sharing their Python simulation code.
+We thank the authors of \cite{uzz_atypical_2013i} for sharing their Python simulation code.
 Research and development reported in this publication was partially supported by Federal funds from the National Institute on Drug Abuse, National Institutes of Health, US Department of Health and Human Services, under Contract Nos.

### 2019-06-12 cocit_r.tex
fixed typo in the acknowledgments in citing
fiddled with a few things, check tables

@@
 \begin{table}[ht]
-\caption{Summary of base WoS Analytical Dataset.The number of publications of type Article (UP), unique references (UR), total references (TR) and the ratio of total references to unique references increases monotonically with each year indicating that both the number of documents and citation activity increase over time.
-Only publications of type Article with at least two references, and references with complete publication data were included.}
+\caption{Summary of base WoS Analytical Dataset.
+The number of unique publications of type Article, unique references (UR), total references (TR), and the ratio of total references to unique references increases monotonically with each year indicating that both the number of documents and citation activity increase over time.
+Only publications of type Article with at least two references and references with complete publication data were included.}
 \label{tab:summary_data}
@@
 \scalebox{0.7}{
-\begin{tabular}{|r rrrr|}
+\begin{tabular}{|r  cccc |}
   \hline
-year & UP & UR & TR & TR/UR \\ 
+year & Unique Publications & Unique References (UR) & Total References (TR) & TR/UR \\ 
   \hline
@@
 In implementing this approach, our approach differs from the approach in \cite{uzzi_atypical_2013}, in the following ways (i) we sampled citations proportional to their citation frequency (equivalently, from a multiset rather than a set) in order to better reflect citation practice,  (ii) we permitted a substitution to match the original reference in a publication when the random selection process dictated it rather than attempting to enforce that a different reference be substituted, and (iii) we introduced an error correction step to delete any publications that accumulated duplicate references during the substitution process.
-As a benchmark, we used the citation switching algorithm of ~\cite{uzzi_atypical_2013}, henceforth referred to  as \emph{umsj} (as also done in ~\citep{boyack_vs_uzzi_2014}), using code kindly provided by the authors.
+As a benchmark, we used the citation switching algorithm of ~\cite{uzzi_atypical_2013}, henceforth referred to  as \emph{umsj} (as also done in ~\cite{boyack_vs_uzzi_2014}), using code kindly provided by the authors.
 A single comparative analysis showed that while 10 simulations of the WoS 1985 dataset (391,860 publications) completed in 2,186 hours using the \emph{umsj} algorithm, it completed in less than one hour using the our implementation of the \emph{repcs}   algorithm on a Spark  cluster.
@@
 \begin{table}[ht]
-\caption{Measuring Model Misspecification. For the set of journal pairs in common between a disciplinary network and the full WoS dataset, Kullback-Leibler (K-L) divergences
+\caption{Model misspecification is reduced by constraining substitutions to disciplinary subnetworks.
+For the set of journal pairs in common between a disciplinary network and the full WoS dataset, Kullback-Leibler (K-L) divergences
 between empirical and simulated journal pair frequencies were computed for the years 1985, 1995, and 2005 for the three disciplinary datasets (applied\_physics, immunology, and metabolism) using either the disciplinary network as background or the WoS superset (all\_wos) to generate the null model (Background).
 K-L divergence was calculated using the R seewave package \citep{seewave2008} with a base (logarithm) of 2.
+The reduction in K-L divergence between simulated and observed data  shows that model misspecification is reduced by  restricting the reference substitutions to the disciplinary subnetwork (our model), as compared to treating all substitutions within WoS as equiprobable (the Uzzi et al.
+model).
 }
@@
 \centering
-\begin{tabular}{ccccccc} 
+\begin{tabular}{| ccccc |} 
   \hline
@@
 \caption[Hit Rates]{Hit Rates by Category for the 1995 datasets. The last four columns indicate the proportion of publications that are hits for each respective category.} \label{Tab:HitRate}
-\begin{tabular}{crrrrrrr}
-& \multicolumn{1}{c}{Hits as \%} & \multicolumn{1}{c}{Novelty}  &  &  &  &  \\ Data Set & \multicolumn{1}{c}{of Articles} & \multicolumn{1}{c}{Percentile} & \multicolumn{1}{c}{LNLC} & \multicolumn{1}{c}{LNHC} & \multicolumn{1}{c}{HNLC} & \multicolumn{1}{c}{HNHC} \\ \hline
-
+\begin{tabular}{|crrrrrr|}
+\hline
+& \multicolumn{1}{c}{Hits as \%} & \multicolumn{1}{c}{Novelty}  &  &  &  &  \\ Data Set & \multicolumn{1}{c}{of Articles} & \multicolumn{1}{c}{Percentile} & \multicolumn{1}{c}{LNLC} & \multicolumn{1}{c}{LNHC} & \multicolumn{1}{c}{HNLC} & \multicolumn{1}{c}{HNHC} \\
+\hline  
 Imm95&1\%&10\%& 0.000& 0.019& 0.005& 0.014 \\ 
@@
 We are grateful to Kevin Boyack and Dick Klavans for constructively critical discussions.
-We thank the authors of \cite{uzz_atypical_2013i} for sharing their Python simulation code.
+We thank the authors of \cite{uzzi_atypical_2013} for sharing their Python simulation code.
 Research and development reported in this publication was partially supported by Federal funds from the National Institute on Drug Abuse, National Institutes of Health, US Department of Health and Human Services, under Contract Nos.

### 2019-06-12 cocit_r.tex
just a bunch of copyediting

@@
 For each article, positional statistics of z-scores were calculated to set thresholds for a binary (high/low) classification of conventionality (C) using the median z-score of an article and novelty (N) using the tenth percentile of z-scores within an article.
-Thus, HCLN would denote high conventionality and low novelty with all four combinations being possible.
+Thus, HCLN would denote high conventionality (HC) and low novelty (LN), with all four combinations being possible.
 The authors observed that HCHN articles were twice as likely to be highly cited, suggesting that novel combinations of ideas flavoring a body of conventional thought were a feature of impact and that `science follows a nearly universal pattern'.
@@
 The citation switching algorithm used to generate expected values from random substitutions is designed to preserve the number of publications, the number of references in each publication, the year of publication of both publications and references, and the disciplinary composition of the references cited in these publications.
-However, substitutions are equiprobable with respect to disciplinary origin and citation count.
-The model permits substitution of a reference in quantum physics with equal probability by a reference in quantum physics, quantum chemistry, classical literature, entomology, or anthropology.
+However, a critically important feature of the model is that all references published in the same year have equal probability of being cited by any given publication.
+Thus, in particular,  subject matter and  citation count do not impact the probability that the reference will be cited, so that  a reference in quantum physics can be substituted, with equal probability, by a reference in quantum physics, quantum chemistry, classical literature, entomology, or anthropology.
 Such substitutions poorly model the disciplinary nature of scientific endeavor and citation behavior~\citep{wallace_lariviere_gingras_2012,moed_measuring_2010,klavans_research_2017,garfield_1979}.
 In addition, under this random model, a reference cited over 100 times in a given year is selected with the same probability as a reference cited only once, which appears inconsistent with the power law or lognormal citation distributions described in the literature~\citep{stringer_statistical_2010,perline_strong_2005}.
-Accordingly, model mis-specification is likely to arise on account of the simulated values not modeling the empirical data very well.
+Accordingly, model misspecification is likely to arise on account of the simulated values not modeling the empirical data very well.
 
@@
 Despite different methods used to generate expected values, both of these key preceding studies (\emph{vide supra}) measured co-citation frequencies across the scientific literature (the WoS superset) and normalized them without disciplinary constraints before subsequently analyzing disciplinary subsets.
-In other words, the concerns raised above about mis-specification resulting from treating
+In other words, the concerns raised above about misspecification resulting from treating
 all references as equiprobable, independent of discipline, apply to \cite{boyack_vs_uzzi_2014} as well.
- We hypothesized that modifying the normalization to constrain references to be drawn only from the disciplinary citation network,   rather than all of WoS, would reduce model mis-specification.
+ We hypothesized that modifying the normalization to constrain references to be drawn only from the disciplinary citation subnetwork,   rather than all of WoS, would reduce model misspecification.
 Consequently, we used keyword searches of the scientific literature to construct exemplar citation networks themed around academic disciplines: \emph{applied physics, immunology, and metabolism}.
@@
 
-Our analyses, using three different techniques, provides substantial evidence that constraining the reference substitutions to the disciplinary subnetwork reduces model mis-specification compared to treating all substitutions within WoS as equiprobable.
+Our analyses, using multiple techniques, provides substantial evidence that constraining the reference substitutions to the disciplinary subnetwork reduces model misspecification compared to treating all substitutions within WoS as equiprobable.
 Furthermore, re-analyses of these three semantically-themed
@@
  Furthermore, we also found that the categories HC, HN, etc.,  demonstrating the highest percentage of highly cited articles are not robust with respect to varying thresholds for high citation counts or for highly novel citation patterns.
- Overall, our study, although limited to three subnetworks, suggests that  co-citation analysis, while useful in many regards, cannot be used to provide universal features in scholarship, due to important differences between disciplines and between publications.
+ Overall, our study, although limited to three disciplinary subnetworks, suggests that  co-citation analysis, while useful in many regards, cannot be used to provide universal features in scholarship, due to important differences between disciplines and between publications.
 
 \section{Materials and Methods}
-\emph{Bibliographic data} We have previously developed ERNIE, an open source knowledge platform into which we parse the Web of Science (WoS) Core Collection~\citep{Keserci371955}.
+
+\subsection{Bibliographic data} We have previously developed ERNIE, an open source knowledge platform into which we parse the Web of Science (WoS) Core Collection~\citep{Keserci371955}.
 WoS data stored in ERNIE spans the period 1900-2019 and consists of over 72 million publications.
@@
 \end{tabular}}
-\vspace{-4mm}%Put here to reduce too much white space after your table 
+\vspace{-1mm}%Put here to reduce too much white space after your table 
 \end{table}
 
-We constructed three disciplinary datasets based on keyword searches.
-(i) immunology (ii) metabolism (iii) applied physics.
+We constructed three disciplinary datasets based on keyword searches: immunology,   metabolism, and   applied physics.
 For the first two, rooted in biomedical research, we searched Pubmed for the term `immunology' or `metabolism' in the years 1985, 1995, and 2005~(Table \ref{tab:disc-datasets}).
@@
 For the applied physics dataset, we directly searched traditional subject labels in WoS for `applied physics'.
-We also examined publications in the five major research areas in the Web of Science; life sciences \& biomedicine, physical sciences, technology, social sciences, arts \& humanities using the extended subcategory classification of 153 sub-groups to categorize disciplinary composition of cited references in the datasets we studied.
+We also examined publications in the five major research areas in the Web of Science: life sciences \& biomedicine, physical sciences, technology, social sciences, and arts \& humanities,  using the extended subcategory classification of 153 sub-groups to categorize disciplinary composition of cited references in the datasets we studied.
 \vspace{-2 mm}
@@
 PubMed and WoS were searched for articles using search terms, `immunology', `metabolism', and `applied physics'.
-Counts of publications are shown for each of the three years analyzed and expressed in parentheses as a percentage of the total number of publications in our analytical WoS dataset (Table \ref{tab:summary_data}) for that year.}
+Counts of publications are shown for each of the three years analyzed and expressed in parentheses as a percentage of the total number of publications in our analytical WoS dataset (Table \ref{tab:summary_data}) for that year.
+Note that Applied Physics and Immunology each represent about 4\% of the publications in WoS, but Metabolism occupies nearly one-fourth of WoS.}
 \label{tab:disc-datasets}
@@
   \hline
-Year & Immunology & Metabolism & Applied Physics \\ 
+Year & Applied Physics & Immunology & Metabolism   \\ 
   \hline
-1985 & 21,606 (5.5\%) & 78,998 (20.2\%) & 10,298 (2.7\%) \\ 
-1995 & 29,320 (5.5\%)  & 121,247 (22.6\%) & 21,012 (3.9\%)  \\ 
-2005 & 37,296 (4.2\%) & 200,052 (22.6\%) & 35,600 (4.0\%)  \\ 
+1985 & 10,298 (2.7\%) & 21,606 (5.5\%) & 78,998 (20.2\%)  \\ 
+1995 & 21,012 (3.9\%)  & 29,320 (5.5\%)  & 121,247 (22.6\%)   \\ 
+2005 & 35,600 (4.0\%) & 37,296 (4.2\%) & 200,052 (22.6\%)    \\ 
  \hline
@@
 
-\emph{Monte Carlo simulations, normalization of observed frequencies, annotations, and `hit' papers}.
-Analysis was performed on publications from 1985, 1995, and 2005.
+\subsection{Monte Carlo simulations, normalization of observed frequencies, annotations, and `hit' papers}
+
+We performed analyses on publications from 1985, 1995, and 2005.
 Building upon prior work~\citep{uzzi_atypical_2013}, all ${n \choose 2}$ reference pairs were generated for each publication, where $n$ is the number of cited references in the publication.
@@
 
-We invoke model mis-specification due to considering disciplinarily irrelevant references as a concern when disciplinary subsets are analyzed using a random graph model that generates expected co-citation frequencies from the WoS superset.
-A symptom of model misspecification is that random sampling of citations associated with an article do not match with the distribution of citations across the disciplines observed in articles from that discipline.
-To address this issue, we first assembled three exemplar datasets using keyword searches for the terms `applied physics', `immunology', and `metabolism' (Materials and Methods).
+Recall our concern regarding model misspecification  in the Uzzi {\em et al.}~model arising from treating all references in a given year as equiprobable, thus allowing substitutions from WoS without consideration of subject matter (as reflected in the publication's discipline) or citation frequency.
+Under this model, the probability of replacing a reference by another reference in a given discipline is identical to the proportion of the articles in WoS that are in that particular discipline.
+Thus, if the model accurate reflects citation practice, the proportion of references within papers published in a given discipline $D$ would be the same as the proportion of articles in the discipline $D$, and--conversely--the degree to which the proportion deviates from the expected value reflects the degree of model misspecification.
+%due to considering disciplinarily irrelevant references as a concern when disciplinary subsets are analyzed using a random graph model that generates expected co-citation frequencies from the WoS superset.
+%A symptom of model misspecification is that random sampling of citations associated with an article do not match with the distribution of citations across the disciplines observed in articles from that discipline.
+We therefore  assembled three exemplar datasets using keyword searches for the terms `applied physics', `immunology', and `metabolism' (Materials and Methods). 
 Using the WoS extended classification of 153 subject areas, we then analyzed the disciplinary composition of the references in these three datasets into the five research areas in the Web of Science (life sciences and biomedicine, physical sciences, social sciences, technology, and arts and humanities) for the years 1985, 1995, and 2005.
-We observed that 84.2\% of the references in the applied physics dataset were classified as belonging to the WoS physical sciences research area, which is comparable to 79.5\% for the references in the physical sciences area.
-Similarly, 93.7\% and 92.1\% of the references in the immunology and metabolism datasets belonged to the life sciences and biomedicine research area, again comparable to 89.9\% for the references in the life sciences and biomedicine area.
+We observed that 84.2\% of the references in the applied physics dataset were classified as belonging to the WoS physical sciences research area, which is close to the value of 79.5\% for the references in the physical sciences area.
+Similarly, 93.7\% and 92.1\% of the references in the immunology and metabolism datasets belonged to the life sciences and biomedicine research area, again close to the value of 89.9\% for the references in the life sciences and biomedicine area.
 \emph{Add in Sitaram's new data}.
@@
 Our observations are in agreement with \cite{wallace_lariviere_gingras_2012} who found that, often, a majority of an article's citations are from the specialty of the article, although that percentage varied among disciplines in the eight specialties they investigated: from approximately 39\% to 89\% for 2006.
+\textcolor{blue}{Would be nice to know the proportion of publications in each of the five major subject areas.}
 
@@
 The results in Table \ref{tab:kld} indicate that for the set of journals common to both a disciplinary network and the WoS superset,  confirm this prediction: simulations under our model (which constrains substitutions to the
-disciplinary subnetwork) consistently have a lower K-L divergence compared to simulations that draw from the WoS superset. 
+disciplinary subnetwork) consistently have a lower K-L divergence compared to simulations that all replacements uniformly  from the WoS superset. 
 Furthermore, the K-L divergence for  the unconstrained model (where the references are equiprobable and allowed to be taken from all of WoS) is generally twice as large as the K-L divergence for the models where the references are constrained to  the disciplinary subnetworks (a ratio of 1.96 to 2.77,  and  greater than 2.0 for eight out of nine cases), demonstrating that simulations that constrain substitutions to the given disciplinary network better model the observed data.
@@
 
-Figure \ref{fig:Fig2}, Panels (a) and (b), compares hit rates for the four categories among the Immunology, Applied Physics, and WoS datasets for 1995: the hit rate is defined as the number of hit articles in each category divided by the number of articles in the category.
+Figure \ref{fig:Fig2}, Panels (a) and (b), compares hit rates for the four categories among the Immunology, Applied Physics, and WoS datasets for 1995, where the hit rate is defined as the number of hit articles in each category divided by the number of articles in the category.
 We evaluated the statistical significance of the categorical hit rates using multiple methods, some of which we describe here.
@@
 The null hypothesis was rejected with $p<0.001$ for all valid tests for all parameter settings, all datasets, and all years: hypotheses tests were valid in 73 of 96 instances.
-We conclude that it is likely that the distribution of hits among categories is not uniform but, rather, hit rates vary among the categories in all datasets.
-(Should we insert a table with all statistical results?)
-
-\begin{table}%[tbhp]
-\centering
-\caption[Hit Rates]{Hit Rates by Category for the 1995 datasets. The last four columns indicate the proportion of publications that are hits for each respective category.} \label{Tab:HitRate}
-\begin{tabular}{|crrrrrr|}
-\hline
-& \multicolumn{1}{c}{Hits as \%} & \multicolumn{1}{c}{Novelty}  &  &  &  &  \\ Data Set & \multicolumn{1}{c}{of Articles} & \multicolumn{1}{c}{Percentile} & \multicolumn{1}{c}{LNLC} & \multicolumn{1}{c}{LNHC} & \multicolumn{1}{c}{HNLC} & \multicolumn{1}{c}{HNHC} \\
-\hline  
-Imm95&1\%&10\%& 0.000& 0.019& 0.005& 0.014 \\ 
-Imm95&10\%&10\%& 0.017& 0.128& 0.076& 0.129 \\ 
-Metab95&1\%&10\%& 0.001& 0.017& 0.006& 0.014 \\ 
-Metab95&10\%&10\%& 0.019& 0.130& 0.074& 0.133 \\ 
-AP95&1\%&10\%& 0.002& 0.007& 0.012& 0.010 \\ 
-AP95&10\%&10\%& 0.047& 0.079& 0.123& 0.109 \\ 
-WoS95&1\%&10\%& 0.004& 0.013& 0.009& 0.017 \\ 
-WoS95&10\%&10\%& 0.056& 0.115& 0.104& 0.156 \\ \hline
-
-\end{tabular}
-\end{table}
+We conclude that it is likely that the distribution of hits among categories is not uniform and that instead hit rates vary among the categories in all datasets.
+%(Should we insert a table with all statistical results?)
 
 We computed hit rates for the WoS dataset, which mirrored Uzzi et al.'s results whereby the largest hit rates were for the HNHC category, despite our methodological improvement of sampling citations in proportion to their frequency.
-We found contrary results in the 1995 immunology dataset where articles in the LNHC category often had the greatest hit rates, as reflected in Table \ref{Tab:HitRate} and Figure \ref{fig:Fig2}.
-Across all year's data, all datasets, and all parameter settings, the highest hit rates in the immunology datasets were sometimes in the LNHC category and sometimes in the HNHC category.
-The metabolism hit rates reflected this same pattern.
-The greatest hit rates for the applied physics data were often in the HNLC category as reflected in Table \ref{Tab:HitRate} and Figure \ref{fig:Fig2}, and otherwise in the HNHC category.
+We found contrary results in the 1995 immunology dataset where articles in the LNHC category often had the greatest hit rates (Figure \ref{fig:Fig2}).
+Across all years and parameter settings, the highest hit rates in the immunology datasets were sometimes in the LNHC category and sometimes in the HNHC category, and the hit rates for the metabolism datasets reflected this same pattern  (Figure \ref{fig:Fig2}).
+The greatest hit rates for the applied physics data were often in the HNLC category and otherwise in the HNHC category (Figure \ref{fig:Fig2}).
 We conclude that Uzzi et al.'s finding of high hit rates in the HNHC category does not hold generally for disciplinary-based datasets and that novel citation patterns are not always indicative of impactful research, as was the case with immunology.
@@
 Consistent with previous analysis, hit articles were overrepresented in the HC category in every instance of WoS data at a $p<0.001$ and hit articles were overrepresented in the HN category at a $p<0.001$ in all but two cases.
-The p-values, in those cases, were 0.002 and 0.007.
+The p-values, in those cases, were $0.002$ and $0.007$.  
 Hits in the immunology and metabolism data were overrepresented in the HC category with the same statistical significance as for WoS.
@@
 \emph{needs to be expanded}
+
 We conclude that high hit rates in the HNHC category do not hold generally for all datasets and that conventionality flavored with novelty is not always indicative of impactful research. 
@@
 \emph{Insert text about Figure \ref{fig:Fig1}.}
+
+\begin{table}%[tbhp]
+\centering
+\caption[Hit Rates]{Hit Rates by Category for the 1995 datasets. The last four columns indicate the proportion of publications that are hits for each respective category.} \label{Tab:HitRate}
+\begin{tabular}{|crrrrrr|}
+\hline
+& \multicolumn{1}{c}{Hits as \%} & \multicolumn{1}{c}{Novelty}  &  &  &  &  \\ Data Set & \multicolumn{1}{c}{of Articles} & \multicolumn{1}{c}{Percentile} & \multicolumn{1}{c}{LNLC} & \multicolumn{1}{c}{LNHC} & \multicolumn{1}{c}{HNLC} & \multicolumn{1}{c}{HNHC} \\
+\hline  
+Imm95&1\%&10\%& 0.000& 0.019& 0.005& 0.014 \\ 
+Imm95&10\%&10\%& 0.017& 0.128& 0.076& 0.129 \\ 
+Metab95&1\%&10\%& 0.001& 0.017& 0.006& 0.014 \\ 
+Metab95&10\%&10\%& 0.019& 0.130& 0.074& 0.133 \\ 
+AP95&1\%&10\%& 0.002& 0.007& 0.012& 0.010 \\ 
+AP95&10\%&10\%& 0.047& 0.079& 0.123& 0.109 \\ 
+WoS95&1\%&10\%& 0.004& 0.013& 0.009& 0.017 \\ 
+WoS95&10\%&10\%& 0.056& 0.115& 0.104& 0.156 \\ \hline
+
+\end{tabular}
+\end{table}
 

### 2019-06-12 cocit_r.tex
edits all over

@@
 
-\subsection{Model Misspecification and the Attributes of Disciplinary Context} \textcolor{blue}{Tandy: I think this is where we can do a statistical test, and show that these numbers are highly unlikely under the random model.} \emph{This is where we want to add the additional data about expected values ~2.5\% for AP as an example.}
-
+\subsection{Model Misspecification and the Attributes of Disciplinary Context} 
 Recall our concern regarding model misspecification  in the Uzzi {\em et al.}~model arising from treating all references in a given year as equiprobable, thus allowing substitutions from WoS without consideration of subject matter (as reflected in the publication's discipline) or citation frequency.
@@
 Our observations are in agreement with \cite{wallace_lariviere_gingras_2012} who found that, often, a majority of an article's citations are from the specialty of the article, although that percentage varied among disciplines in the eight specialties they investigated: from approximately 39\% to 89\% for 2006.
-\textcolor{blue}{Would be nice to know the proportion of publications in each of the five major subject areas.}
+
+\textcolor{blue}{I don't think the paragraph above makes the point that the distribution that is observed is inconsistent with the Uzzi et al.
+model.
+But to make that point, it would be nice to know the proportion of publications in each of the five major subject areas.
+With that information,  I think this is where we can do a statistical test, and show that these numbers are highly unlikely under the random model.
+In other words, this is where we want to add the additional data about expected values ~2.5\% for AP as an example.}
 
@@
 
-We predicted that model misspecification, as measured by the Kullback-Leibler (K-L) Divergence~\citep{kullback_information_1951} between observed and simulated frequencies, constraining  reference substitutions to the disciplinary subnetwork would be less than the
-model misspecification when substitutions are drawn equiprobably from all of 
-the WoS superset. 
-The results in Table \ref{tab:kld} indicate that for the set of journals common to both a disciplinary network and the WoS superset,  confirm this prediction: simulations under our model (which constrains substitutions to the
-disciplinary subnetwork) consistently have a lower K-L divergence compared to simulations that all replacements uniformly  from the WoS superset. 
-Furthermore, the K-L divergence for  the unconstrained model (where the references are equiprobable and allowed to be taken from all of WoS) is generally twice as large as the K-L divergence for the models where the references are constrained to  the disciplinary subnetworks (a ratio of 1.96 to 2.77,  and  greater than 2.0 for eight out of nine cases), demonstrating that simulations that constrain substitutions to the given disciplinary network better model the observed data.
+Since our analyses show substantial model misspecification for the Uzzi {\em et al.} model, we then examined a modification to the model that we conjectured would better fit the observed data.
+Specifically,
+we conjectured that model misspecification would be reduced by constraining the substitutions to  disciplinary subnetworks,  and tested this by examining the Kullback-Leibler (K-L) Divergence~\citep{kullback_information_1951} between observed and predicted citation distributions,
+restricted to  the set of journals in a given disciplinary subnetwork.  
+The results (Table \ref{tab:kld}) confirm this prediction: simulations under the constrained model (which constrains substitutions to the
+disciplinary subnetwork) consistently have a lower K-L divergence compared to simulations under the unconstrained model of Uzzi {\em et al.},  where all references in WoS for a given year are equiprobable.
+Furthermore, the K-L divergence for  the unconstrained model is generally twice as large as the K-L divergence for the models where the references are constrained to  the disciplinary subnetworks (a ratio of 1.96 to 2.77,  and  greater than 2.0 for eight out of nine cases).
+These results clearly demonstrate that the modification to the Uzzi {\em et al.} model produced by  constraining reference substitutions to the given disciplinary network better models the observed data.
 
-\subsection{Novelty and Conventionality as Determinants of Impact in Disciplinary Contexts}
+\subsection{Calculation of Novelty and Conventionality using the constrained model}  
 \begin{figure*}
@@
 
+Since the constrained model better fits the observed data, we evaluated the distribution of 
+highly cited articles  (i.e., ``hit articles")
+ into the four categories (HCHN, LCHN, HCLN, LCLN), for different
+thresholds for hit articles.
 Figure \ref{fig:Fig2}, Panels (a) and (b), compares hit rates for the four categories among the Immunology, Applied Physics, and WoS datasets for 1995, where the hit rate is defined as the number of hit articles in each category divided by the number of articles in the category.
+The calculation for the hit rates for the WoS dataset (bottom row, Figure \ref{fig:Fig2})
+mirrors Uzzi et al.'s results, whereby the largest hit rates were for the HNHC category, despite our methodological improvement of sampling citations in proportion to their frequency. 
+However, results observed for the 1995 immunology and metabolism datasets show different
+trends, in that  articles in the LNHC category had the greatest hit rates for the top 1\% of cited articles and tied for the top 10\%.
+%Across all years and parameter settings, the highest hit rates in the immunology datasets were sometimes in the LNHC category and sometimes in the HNHC category, and the hit rates for the metabolism datasets reflected this same pattern  (Figure \ref{fig:Fig2}).
+On the other hand, the greatest hit rates for the applied physics data were   in the HNLC category for both the top 1\% and top 10\% of all cited articles.  
+Thus, the category exhibiting the highest hit rate (among highly cited papers) depends on the
+specific disciplinary network, and also to some extent on the threshold for being highly cited.
+ %was the case with immunology. 
+Furthermore, the categories displaying the greatest hit rate vary to some extent % with parameter settings and 
+with the year  \textcolor{blue}{(data not shown)}.
+%The lack of stable results across parameter settings suggests that parameters must be selected judiciously.
+
+\textcolor{blue}{I did not review the next two paragraphs}
+
 We evaluated the statistical significance of the categorical hit rates using multiple methods, some of which we describe here.
@@
 %(Should we insert a table with all statistical results?)
-
-We computed hit rates for the WoS dataset, which mirrored Uzzi et al.'s results whereby the largest hit rates were for the HNHC category, despite our methodological improvement of sampling citations in proportion to their frequency.
-We found contrary results in the 1995 immunology dataset where articles in the LNHC category often had the greatest hit rates (Figure \ref{fig:Fig2}).
-Across all years and parameter settings, the highest hit rates in the immunology datasets were sometimes in the LNHC category and sometimes in the HNHC category, and the hit rates for the metabolism datasets reflected this same pattern  (Figure \ref{fig:Fig2}).
-The greatest hit rates for the applied physics data were often in the HNLC category and otherwise in the HNHC category (Figure \ref{fig:Fig2}).
-We conclude that Uzzi et al.'s finding of high hit rates in the HNHC category does not hold generally for disciplinary-based datasets and that novel citation patterns are not always indicative of impactful research, as was the case with immunology.
-Furthermore, the categories displaying the greatest hit rate vary with parameter settings and with the year. 
-The lack of stable results across parameter settings suggests that parameters must be selected judiciously.
 
@@
 
+\textcolor{blue}{I think we should delete the next paragraph.}
+That fewer z-scores are negative in the WoS dataset relative to the immunology dataset may be directly due to the uniform sampling of references, whereby many resulting journal pairs are never observed in the literature and so the expected frequencies of those observed pairs have lower expected values, thus biasing their z-scores upward.
+In addition, treating citation as a set versus a multiset means that a random model will sample popular citations downward, thus further increasing their z-scores.\emph{need confirmation from Jim here}.
+
 \section{Discussion}
@@
 
-We conclude that high hit rates in the HNHC category do not hold generally for all datasets and that conventionality flavored with novelty is not always indicative of impactful research. 
+Our study shows strong evidence that a key assumption of the Uzzi {\em et al.} model that  
+substitutions of references  are not impacted by discipline deviates from citation practice, and that
+constraining the model to a disciplinary subnetwork reduces the model misspecification.
+Furthermore,  using the constrained model instead of the unconstrained model to redefine high (or low) novelty and conventionality produces different trends, depending on the subnetwork.
+In particular, while Uzzi {\em et al.} found that highly cited papers were most likely to be
+in the HNHC category, this observation does not hold when using the improved model.
+Instead, unlike Uzzi {\em et al.}, we find that conventionality flavored with novelty is {\em not} generally a feature of impactful research. 
+In particular,   high novelty (as defined by Uzzi {\em et al.}) is
+%We conclude that Uzzi et al.'s finding of high hit rates in the HNHC category does not hold generally for disciplinary-based datasets and that 
+%novel citation patterns are 
+not always indicative of impactful research (as reflected in citation counts), as shown by both Immunology and Metabolism having their highest hit rates for low novelty (Figure \ref{fig:Fig2}).
+More generally, these results show that the conclusions of Uzzi {\em et al.} of universal trends in highly cited papers
+may be the consequence of using a random model that has a poor fit to the observed data.
+
+Of equal concern, and also contrary to Uzzi et al., we found the category displaying the highest hit rate to be sensitive to the percentage of articles deemed to be hit articles (i.e., the definition of highly cited articles), as well as   and the percentile of articles' z-score distributions that delineated between articles of low novelty and high novelty \textcolor{blue}{(data not shown).}
+Faced with this lack of robustness, we are confronted with the necessity of defining defendable parameters, if possible, that determine novelty and conventionality. 
+More significantly, we should question whether the simple approach of defining novelty and conventionality, as is done in this article and other research, is sufficient or whether we should expect such variation in the factors associated with impact as we have observed.
+
 %The z-scores that change sign across datasets is either contradictory or an acceptable variation due to the difference in reference sets.
 We contend that it is the former because the inappropriate substitution of citations with those from disciplines that are implausible and because the observed citation frequencies are ignored.
-That fewer z-scores are negative in the WoS dataset relative to the immunology dataset may be directly due to the uniform sampling of references, whereby many resulting journal pairs are never observed in the literature and so the expected frequencies of those observed pairs have lower expected values, thus biasing their z-scores upward.
-In addition, treating citation as a set versus a multiset means that a random model will sample popular citations downward, thus further increasing their z-scores.\emph{need confirmation from Jim here}.
-
-Contrary to Uzzi et al., we found the category displaying the highest hit rate to be sensitive to the experimental parameter settings, which included the percentage of articles deemed to be hits and the percentile of articles' z-score distributions that delineated between articles of low novelty and high novelty.
-Faced with this lack of robustness, we are confronted with the necessity of defining defendable parameters, if possible, that determine novelty and conventionality.
-More significantly, we should question whether the simple approach of defining novelty and conventionality as is done this article and other research is sufficient or whether we should expect such variation in the factors associated with impact as we have observed.
 

### 2019-06-12 cocit_r.tex
small edits

@@
 \end{tabular}
-\caption{Effect of Context on Journal-Pair z-scores and Categorical Hit Rates: Immunology, Applied Physics, and WoS for 1995.
-Panels (a) and (b) show hit rates for the LNLC, LNHC, HNLC, and HNHC categories for the immunology, applied physics, and WoS datasets when hit articles are defined as the top 1\% and top 10\% of articles, respectively.
+\caption{Effect of using the improved model on  categorical hit rates for Immunology, Applied Physics, and WoS for 1995.
+Panels (a) and (b) show hit rates for the LNLC, LNHC, HNLC, and HNHC categories for the applied physics, immunology, metabolism, and WoS datasets when hit articles are defined as the top 1\% and top 10\% of articles, respectively.
 Novelty in both panels is defined at the 10th percentile of articles' z-score distributions.
+The results for the WoS data set mirror  results from \cite{uzzi_atypical_2013}, where the highest hit rate was for the HNHC category.
+Results for the three disciplinary subnetworks all differ from the overall WoS results: the highest hit rates for the immunology and metabolism datasets  are in the LNHC category and
+%The LNHC category often had the highest hit rate for the immunology dataset for various parameter settings with the HCHN category having the highest hit rate in other cases: metabolism results are similar.
+the highest hit rate for the applied physics datasets are in the HNLC category.  
+%The HNLC category demonstrated the highest hit rate often for applied physics: otherwise the highest hit rate was for HNHC articles.
+\textcolor{blue}{Need numbers for metabolism for the next sentence:}
 The number of data points in the immunology, applied physics, and WoS data sets are 21,917, 18,305, and 476,288, respectively.  
-The results for the WoS data set mirrored previous results from \cite{uzzi_atypical_2013}, where the highest hit rate was for the HNHC category.
-The highest hit rates for the immunology dataset, in contrast, are in the LNHC category.
-The LNHC category often had the highest hit rate for the immunology dataset for various parameter settings with the HCHN category having the highest hit rate in other cases: metabolism results are similar.
-The applied physics dataset shows further contrast as the hit rate for it was highest in the HNLC category.
-The HNLC category demonstrated the highest hit rate often for applied physics: otherwise the highest hit rate was for HNHC articles.}
+}
 \label{fig:Fig2}
@@
 thresholds for hit articles.
-Figure \ref{fig:Fig2}, Panels (a) and (b), compares hit rates for the four categories among the Immunology, Applied Physics, and WoS datasets for 1995, where the hit rate is defined as the number of hit articles in each category divided by the number of articles in the category.
+Figure \ref{fig:Fig2}, Panels (a) and (b), compares hit rates for the four categories among the Immunology, Metabolism, Applied Physics, and WoS datasets for 1995, where the hit rate is defined as the number of hit articles in each category divided by the number of articles in the category.
 The calculation for the hit rates for the WoS dataset (bottom row, Figure \ref{fig:Fig2})
 mirrors Uzzi et al.'s results, whereby the largest hit rates were for the HNHC category, despite our methodological improvement of sampling citations in proportion to their frequency. 
-However, results observed for the 1995 immunology and metabolism datasets show different
-trends, in that  articles in the LNHC category had the greatest hit rates for the top 1\% of cited articles and tied for the top 10\%.
+However, the trends  for all three  disciplinary subnetworks  are different from those for WoS.
+Specifically, the highest hit rates for the 1995 immunology and metabolism datasets are in the LNHC category for the top 1\% of cited articles (and tied between LNHC and HNHC for the top 10\%),
+and the highest hit rates for the 1995 applied physics datasets are in the 
+HNLC category for both the top 1\% and top 10\% of all cited articles.  
 %Across all years and parameter settings, the highest hit rates in the immunology datasets were sometimes in the LNHC category and sometimes in the HNHC category, and the hit rates for the metabolism datasets reflected this same pattern  (Figure \ref{fig:Fig2}).
-On the other hand, the greatest hit rates for the applied physics data were   in the HNLC category for both the top 1\% and top 10\% of all cited articles.  
  Thus, the category exhibiting the highest hit rate (among highly cited papers) depends on the
-specific disciplinary network, and also to some extent on the threshold for being highly cited.
+specific disciplinary network and to some extent on the threshold for being highly cited.
  %was the case with immunology. 
-Furthermore, the categories displaying the greatest hit rate vary to some extent % with parameter settings and 
+Furthermore, the categories displaying the greatest hit rate vary 
+to some extent % with parameter settings and 
 with the year  \textcolor{blue}{(data not shown)}.

### 2019-06-12 cocit_r.tex
edited terminal Introduction

@@
  Furthermore, we also found that the categories HC, HN, etc.,  demonstrating the highest percentage of highly cited articles are not robust with respect to varying thresholds for high citation counts or for highly novel citation patterns.
- Overall, our study, although limited to three disciplinary subnetworks, suggests that  co-citation analysis, while useful in many regards, cannot be used to provide universal features in scholarship, due to important differences between disciplines and between publications.
+ Overall, our study, although limited to three disciplinary subnetworks, suggests that  co-citation analysis, while useful in many regards, may not be very useful in detecting universal features of impactful publications, due to important differences between disciplines and between publications.
 

### 2019-06-12 cocit_r.tex
edited terminal Introduction

--- 2019-06-12 cocit_r.tex
@@
  Furthermore, we also found that the categories HC, HN, etc.,  demonstrating the highest percentage of highly cited articles are not robust with respect to varying thresholds for high citation counts or for highly novel citation patterns.
- Overall, our study, although limited to three disciplinary subnetworks, suggests that  co-citation analysis, while useful in many regards, cannot be used to provide universal features in scholarship, due to important differences between disciplines and between publications.
+Overall, our study, although limited to three disciplinary subnetworks, suggests that co-citation analysis that inadequately considers disciplinary differences, may not be very useful at detecting universal features of impactful publications.
 

### 2019-06-12 cocit_r.tex
note text in blue font

@@
 For the applied physics dataset, we directly searched traditional subject labels in WoS for `applied physics'.
+\textcolor{blue}{
+While immunology and applied physics represent somewhat small subnetworks (each occupying about 4\% of WoS), metabolism represents approximately 22\% of WoS, making them interesting and meaningful test cases.
+}
 We also examined publications in the five major research areas in the Web of Science: life sciences \& biomedicine, physical sciences, technology, social sciences, and arts \& humanities,  using the extended subcategory classification of 153 sub-groups to categorize disciplinary composition of cited references in the datasets we studied.
@@
 
-For citation shuffling, we developed a performant citation switching algorithm, \emph{runtime enhanced permuting citation switcher (repcs)}, that randomly permuted citations grouped by year of publication to switch citations while preserving the year of publication for both articles and references, the number of publications and the number of references in each dataset and the disciplinary composition of the references in each dataset.
+For citation shuffling, we developed a performant citation switching algorithm, \emph{runtime enhanced permuting citation switcher (repcs)} (\textcolor{blue}{available in github at XXX}), that randomly permuted citations grouped by year of publication to switch citations while preserving the year of publication for both articles and references, the number of publications and the number of references in each dataset and the disciplinary composition of the references in each dataset.
 In implementing this approach, our approach differs from the approach in \cite{uzzi_atypical_2013}, in the following ways (i) we sampled citations proportional to their citation frequency (equivalently, from a multiset rather than a set) in order to better reflect citation practice,  (ii) we permitted a substitution to match the original reference in a publication when the random selection process dictated it rather than attempting to enforce that a different reference be substituted, and (iii) we introduced an error correction step to delete any publications that accumulated duplicate references during the substitution process.
@@
 TW receives funding from the Grainger Foundation.
-All the code used in this study is freely available from a Github site.
+All the code used in this study is freely available from 
+\textcolor{blue}{a Github site}.
 Access to the bibliographic data analyzed in this study requires a license from Clarivate Analytics, which had no role in funding, experimental design, review of results, and conclusions presented.

### 2019-06-12 cocit_r.tex
fixed first para of Results section

@@
 
-\subsection{Model Misspecification and the Attributes of Disciplinary Context} 
-Recall our concern regarding model misspecification  in the Uzzi {\em et al.}~model arising from treating all references in a given year as equiprobable, thus allowing substitutions from WoS without consideration of subject matter (as reflected in the publication's discipline) or citation frequency.
-Under this model, the probability of replacing a reference by another reference in a given discipline is identical to the proportion of the articles in WoS that are in that particular discipline.
-Thus, if the model accurate reflects citation practice, the proportion of references within papers published in a given discipline $D$ would be the same as the proportion of articles in the discipline $D$, and--conversely--the degree to which the proportion deviates from the expected value reflects the degree of model misspecification.
-%due to considering disciplinarily irrelevant references as a concern when disciplinary subsets are analyzed using a random graph model that generates expected co-citation frequencies from the WoS superset.
-%A symptom of model misspecification is that random sampling of citations associated with an article do not match with the distribution of citations across the disciplines observed in articles from that discipline.
-We therefore  assembled three exemplar datasets using keyword searches for the terms `applied physics', `immunology', and `metabolism' (Materials and Methods). 
-Using the WoS extended classification of 153 subject areas, we then analyzed the disciplinary composition of the references in these three datasets into the five research areas in the Web of Science (life sciences and biomedicine, physical sciences, social sciences, technology, and arts and humanities) for the years 1985, 1995, and 2005.
-We observed that 84.2\% of the references in the applied physics dataset were classified as belonging to the WoS physical sciences research area, which is close to the value of 79.5\% for the references in the physical sciences area.
-Similarly, 93.7\% and 92.1\% of the references in the immunology and metabolism datasets belonged to the life sciences and biomedicine research area, again close to the value of 89.9\% for the references in the life sciences and biomedicine area.
-\emph{Add in Sitaram's new data}.
-These data indicate strongly that references are likely to belong to the same research area as the publications that cite them.
+\subsection{Model Misspecification and the Attributes of Disciplinary Context} A source of misspecification in the Uzzi {\em et al.}~model arises from not accounting for disciplinary heterogeneity by treating all references as equiprobable substituents.
+Under this model, the probability of replacing a reference in one discipline by another reference in a second discipline is identical to the proportion of the articles in WoS that from the second discipline.
+If the model approximated citation practice, the proportion of references within papers published in a given discipline $D$ would be expected to be equal to the proportion of articles in the discipline $D$, and--conversely--the degree to which the proportion deviates from the expected value would reflect the extent of model misspecification.
+
+We assembled three exemplar datasets using keyword searches for the terms `applied physics', `immunology', and `metabolism' (Materials and Methods).
+We used the the WoS extended classification of five major research areas comprising life sciences and biomedicine, physical sciences, social sciences, technology, and arts and humanities and matched our applied physics dataset to physical science, and our immunology and metabolism datasets to the life science and biomedicine research areas respectively.
+We analyzed the composition of the  references in our three datasets according to the five research areas in the Web of Science for the years 1985, 1995, and 2005.
+We observed that 84.2\% of the references in the applied physics dataset were classified as belonging to the WoS physical sciences research area and 93.7\% and 92.1\% of the references in the immunology and metabolism datasets respectively belonged to the life sciences and biomedicine research area,  However, corresponding reference content for the WoS superset was 33.4\% (physical sciences) and 52.9\% life sciences and biomedicine.
+These data suggest at a high level (i) misspecification (ii) strongly that references are likely to belong to the same research area as the publications that cite them rather than being drawn evenly from all five research areas.
 Our observations are in agreement with \cite{wallace_lariviere_gingras_2012} who found that, often, a majority of an article's citations are from the specialty of the article, although that percentage varied among disciplines in the eight specialties they investigated: from approximately 39\% to 89\% for 2006.
@@
 But to make that point, it would be nice to know the proportion of publications in each of the five major subject areas.
-With that information,  I think this is where we can do a statistical test, and show that these numbers are highly unlikely under the random model.
-In other words, this is where we want to add the additional data about expected values ~2.5\% for AP as an example.}
+With that information,  I think this is where we can do a statistical test, and show that these numbers are highly unlikely under the random model.}
 

### 2019-06-12 cocit_r.tex
fixed first para of Results section

@@
 We assembled three exemplar datasets using keyword searches for the terms `applied physics', `immunology', and `metabolism' (Materials and Methods).
-We used the the WoS extended classification of five major research areas comprising life sciences and biomedicine, physical sciences, social sciences, technology, and arts and humanities and matched our applied physics dataset to physical science, and our immunology and metabolism datasets to the life science and biomedicine research areas respectively.
-We analyzed the composition of the  references in our three datasets according to the five research areas in the Web of Science for the years 1985, 1995, and 2005.
-We observed that 84.2\% of the references in the applied physics dataset were classified as belonging to the WoS physical sciences research area and 93.7\% and 92.1\% of the references in the immunology and metabolism datasets respectively belonged to the life sciences and biomedicine research area,  However, corresponding reference content for the WoS superset was 33.4\% (physical sciences) and 52.9\% life sciences and biomedicine.
-These data suggest at a high level (i) misspecification (ii) strongly that references are likely to belong to the same research area as the publications that cite them rather than being drawn evenly from all five research areas.
+
+To study the disciplinary composition of references in our custom datasets, we used the the WoS extended classification consisting of 153 subjects aggregated into the five major research areas of life sciences and biomedicine, physical sciences, social sciences, technology, and arts and humanities.
+We measured the frequency with which these five major research areas occur in WoS for the years 1985, 1995, and 2005 and observed the following proportions: (i) life sciences and biomedicine (52.9\%), physical sciences (33.4\%), social sciences (7.2\%), technology (17.9\%), and arts and humanities (1\%).
+We then matched our applied physics dataset to physical science, and our immunology and metabolism datasets to the life science and biomedicine research areas respectively.
+We analyzed the composition of the references in our three datasets and observed that 84.2\% of the references in the applied physics dataset belonged to physical sciences, and 93.7\% and 92.1\% of the references in the immunology and metabolism datasets respectively belonged to the life sciences and biomedicine research area.
+These data suggest at a high level (i) that applying a discipline-indifferent model in Monte Carlo simulations would result in misspecification (ii) strongly that references are likely to belong to the same research area as the publications that cite them rather than being drawn evenly from all five research areas.
 Our observations are in agreement with \cite{wallace_lariviere_gingras_2012} who found that, often, a majority of an article's citations are from the specialty of the article, although that percentage varied among disciplines in the eight specialties they investigated: from approximately 39\% to 89\% for 2006.

### 2019-06-12 cocit_r.tex
fixed first para of Results section for the 4th time

@@
 To study the disciplinary composition of references in our custom datasets, we used the the WoS extended classification consisting of 153 subjects aggregated into the five major research areas of life sciences and biomedicine, physical sciences, social sciences, technology, and arts and humanities.
-We measured the frequency with which these five major research areas occur in WoS for the years 1985, 1995, and 2005 and observed the following proportions: (i) life sciences and biomedicine (52.9\%), physical sciences (33.4\%), social sciences (7.2\%), technology (17.9\%), and arts and humanities (1\%).
+We measured the frequency with which these five major research areas occur in WoS for the years 1985, 1995, and 2005 and observed the following proportions (some publications qualify for more than one label): (i) life sciences and biomedicine (52.9\%), physical sciences (33.4\%), social sciences (7.2\%), technology (17.9\%), and arts and humanities (1\%).
 We then matched our applied physics dataset to physical science, and our immunology and metabolism datasets to the life science and biomedicine research areas respectively.

### 2019-06-12 cocit_r.tex
edited first paragraph page 6

--- 2019-06-12 cocit_r.tex
@@
 Under this model, the probability of replacing a reference in one discipline by another reference in a second discipline is identical to the proportion of the articles in WoS that from the second discipline.
-If the model approximated citation practice, the proportion of references within papers published in a given discipline $D$ would be expected to be equal to the proportion of articles in the discipline $D$, and--conversely--the degree to which the proportion deviates from the expected value would reflect the extent of model misspecification.
-
-We assembled three exemplar datasets using keyword searches for the terms `applied physics', `immunology', and `metabolism' (Materials and Methods).
+If the Uzzi {\em et al.} model accurately reflects citation practice, the expected proportion of references within papers published in a given discipline $D$ would be equal to the proportion of references in  $D$, and--conversely--the degree to which the proportion deviates from the expected value would reflect the extent of model misspecification.
+
+%We assembled three exemplar datasets using keyword searches for the terms `applied physics', `immunology', and `metabolism' (Materials and Methods).
 
 To study the disciplinary composition of references in our custom datasets, we used the the WoS extended classification consisting of 153 subjects aggregated into the five major research areas of life sciences and biomedicine, physical sciences, social sciences, technology, and arts and humanities.
-We measured the frequency with which these five major research areas occur in WoS for the years 1985, 1995, and 2005 and observed the following proportions: (i) life sciences and biomedicine (52.9\%), physical sciences (33.4\%), social sciences (7.2\%), technology (17.9\%), and arts and humanities (1\%).
+%We measured the frequency with which these five major research areas occur in WoS for the years 1985, 1995, and 2005 and observed the following proportions (some publications qualify for more than one label): (i) life sciences and biomedicine (52.9\%), physical sciences (33.4\%), social sciences (7.2\%), technology (17.9\%), and arts and humanities (1\%).
 We then matched our applied physics dataset to physical science, and our immunology and metabolism datasets to the life science and biomedicine research areas respectively.
 We analyzed the composition of the references in our three datasets and observed that 84.2\% of the references in the applied physics dataset belonged to physical sciences, and 93.7\% and 92.1\% of the references in the immunology and metabolism datasets respectively belonged to the life sciences and biomedicine research area.
-These data suggest at a high level (i) that applying a discipline-indifferent model in Monte Carlo simulations would result in misspecification (ii) strongly that references are likely to belong to the same research area as the publications that cite them rather than being drawn evenly from all five research areas.
-Our observations are in agreement with \cite{wallace_lariviere_gingras_2012} who found that, often, a majority of an article's citations are from the specialty of the article, although that percentage varied among disciplines in the eight specialties they investigated: from approximately 39\% to 89\% for 2006.
-
-\textcolor{blue}{I don't think the paragraph above makes the point that the distribution that is observed is inconsistent with the Uzzi et al.
+The two largest of these research areas are physical sciences and life sciences and biomedicine,  which contribute on average approximately 35.1\% and 62.8\%, respectively, of the references in WoS over the three years of interest.
+%While there is some variability in different years, %approximately 35.1\% of the references in WoS are from the physical sciences and approximately 62.8\% of the references are from the life sciences and biomedicine.
+While there is some variability over the years, according to the Uzzi  {\em et al.} model, we would expect close to 35.1\% of the references cited by the publications in any large network  to be drawn from the physical sciences and roughly 62.8\% of the references to be drawn from the life sciences and biomedicine.
+Yet the empirical data present a very different  story: 79.6\% of the references cited in physical sciences publications are from the physical sciences and 89.9\% of the references cited in life sciences and biomedicine publications are from the life sciences and biomedicine.
+In other words, the empirical data shows a strong tendency of publications to cite papers that are in the same major research area rather than in some other research area.
+Thus, there is a strong bias towards citations that are {\em inside-the-network} rather than {\em outside-the-network}.
+This is inconsistent with the Uzzi {\em et al.} model, but makes sense, given what is well established about citation practice.
+%These data suggest at a high level (i) that applying a discipline-indifferent model in Monte Carlo simulations would result in misspecification (ii) strongly that references are likely to belong to the same research area as the publications that cite them rather than being drawn evenly from all five research areas.
+For example, our observations are in agreement with \cite{wallace_lariviere_gingras_2012} who found that, often, a majority of an article's citations are from the specialty of the article, even though that percentage varied among disciplines in the eight specialties they investigated (from approximately 39\% to 89\% for 2006).
+Furthermore, these findings strongly argue that Uzzi {\em et al.}'s model has substantial model misspecification (in deviating substantially from the empirical data), and supports our concern that
+definitions of  innovation and conventionality that are based on deviation from expected values under Uzzi's model may not be merited.
+
+%\textcolor{blue}{I don't think the paragraph above makes the point that the distribution that is observed is inconsistent with the Uzzi et al.
 model.

### 2019-06-13 cocit_r.tex
sanitized excessive reference to Uzzi

@@
 Under this model, the probability of replacing a reference in one discipline by another reference in a second discipline is identical to the proportion of the articles in WoS that from the second discipline.
-If the Uzzi {\em et al.} model accurately reflects citation practice, the expected proportion of references within papers published in a given discipline $D$ would be equal to the proportion of references in  $D$, and--conversely--the degree to which the proportion deviates from the expected value would reflect the extent of model misspecification.
+If the Uzzi {\em et al.} model accurately reflects citation practice, the expected proportion of references within papers published in a given discipline $D$ would be equal to the proportion of references in  $D$, and conversely, the degree to which the proportion deviates from the expected value would reflect the extent of model misspecification.
 
@@
 
-To study the disciplinary composition of references in our custom datasets, we used the the WoS extended classification consisting of 153 subjects aggregated into the five major research areas of life sciences and biomedicine, physical sciences, social sciences, technology, and arts and humanities.
-%We measured the frequency with which these five major research areas occur in WoS for the years 1985, 1995, and 2005 and observed the following proportions (some publications qualify for more than one label): (i) life sciences and biomedicine (52.9\%), physical sciences (33.4\%), social sciences (7.2\%), technology (17.9\%), and arts and humanities (1\%).
-We then matched our applied physics dataset to physical science, and our immunology and metabolism datasets to the life science and biomedicine research areas respectively.
-We analyzed the composition of the references in our three datasets and observed that 84.2\% of the references in the applied physics dataset belonged to physical sciences, and 93.7\% and 92.1\% of the references in the immunology and metabolism datasets respectively belonged to the life sciences and biomedicine research area.
+To study the disciplinary composition of references in our custom datasets, we first used the high level WoS classification of five major research areas: life sciences and biomedicine, physical sciences, social sciences, technology, and arts and humanities.
 The two largest of these research areas are physical sciences and life sciences and biomedicine, which contribute on average approximately 35.1\% and 62.8\%, respectively, of the references in WoS over the three years of interest.
-%While there is some variability in different years, %approximately 35.1\% of the references in WoS are from the physical sciences and approximately 62.8\% of the references are from the life sciences and biomedicine.
 While there is some variability over the years, according to the Uzzi  {\em et al.} model, we would expect close to 35.1\% of the references cited by the publications in any large network  to be drawn from the physical sciences and roughly 62.8\% of the references to be drawn from the life sciences and biomedicine.
@@
 In other words, the empirical data shows a strong tendency of publications to cite papers that are in the same major research area rather than in some other research area.
-Thus, there is a strong bias towards citations that are {\em inside-the-network} rather than {\em outside-the-network}.
-This is inconsistent with the Uzzi {\em et al.} model, but makes sense, given what is well established about citation practice.
-%These data suggest at a high level (i) that applying a discipline-indifferent model in Monte Carlo simulations would result in misspecification (ii) strongly that references are likely to belong to the same research area as the publications that cite them rather than being drawn evenly from all five research areas.
-For example, our observations are in agreement with \cite{wallace_lariviere_gingras_2012} who found that, often, a majority of an article's citations are from the specialty of the article, even though that percentage varied among disciplines in the eight specialties they investigated (from approximately 39\% to 89\% for 2006).
-Furthermore, these findings strongly argue that Uzzi {\em et al.}'s model has substantial model misspecification (in deviating substantially from the empirical data), and supports our concern that
-definitions of  innovation and conventionality that are based on deviation from expected values under Uzzi's model may not be merited.
-
-%\textcolor{blue}{I don't think the paragraph above makes the point that the distribution that is observed is inconsistent with the Uzzi et al.
-model.
-But to make that point, it would be nice to know the proportion of publications in each of the five major subject areas.
-With that information,  I think this is where we can do a statistical test, and show that these numbers are highly unlikely under the random model.}
+Thus, there is a strong bias towards citations that are {\em intra-network}.
+Our observations are in agreement with \cite{wallace_lariviere_gingras_2012} who found that, often, a majority of an article's citations are from the specialty of the article, even though that percentage varied among disciplines in the eight specialties they investigated (from approximately 39\% to 89\% for 2006).
+Furthermore, these findings argue that a discipline-indifferent random graph model would exhibit misspecification (in deviating substantially from the empirical data), and supports the  concern about definitions of  innovation and conventionality that are based on deviation from expected values.
 
@@
 
-We also analyzed the consequences of citation shuffling within a disciplinary set or all of the Web of Science.
-References in publications belonging to these three datasets were classified using the WoS Extended Subjects classification of 153 subject areas and summarized as a frequency distribution.
+We also analyzed disciplinary composition at a deeper level of the 153 Subjects in WoS extended classification and examining the consequences of  citation shuffling within a disciplinary set or all of the Web of Science.
+References in publications belonging to these three datasets were classified into 153 subject areas and summarized as a frequency distribution.
 A single shuffle of the references in these datasets or all the references in the corresponding WoS year slice was performed, using either the \emph{repcs}  or \emph{umsj} algorithms, after which subject frequencies were computed again.
@@
 For example, the applied physics dataset contained one reference labeled Genetics and Heredity, but after the shuffle (using the WoS background), there were 1496 references labeled Genetics and Heredity.
-%This proportion was preserved in the intra-network shuffle but increased 1496 times when the WoS background was used as a source of substitution during the Monte Carlo simulation with the \emph{repcs}   algorithm.
 Similarly,  the metabolism dataset  contained one reference labeled Philosophy, but after a single shuffle (again using the WoS background), there were   661 occurrences with this label.
-%after a single \emph{repcs}  shuffle. 
 The data show convincingly that the disciplinary composition of references in a network is preserved when citation shuffling is constrained to the subnetwork, but is significantly distorted when the WoS superset is used as a source of substitution.
-A second inference is that the choice between these two algorithms is not relevant (except for running time considerations), and that the background network used for the shuffle is critical.
+A second inference is that the two algorithms, except for running time considerations, have equivalent effects in this experiment.
 
@@
 between empirical and simulated journal pair frequencies were computed for the years 1985, 1995, and 2005 for the three disciplinary datasets (applied\_physics, immunology, and metabolism) using either the disciplinary network as background or the WoS superset (all\_wos) to generate the null model (Background).
-K-L divergence was calculated using the R seewave package \citep{seewave2008} with a base (logarithm) of 2.
-The reduction in K-L divergence between simulated and observed data  shows that model misspecification is reduced by  restricting the reference substitutions to the disciplinary subnetwork (our model), as compared to treating all substitutions within WoS as equiprobable (the Uzzi et al.
-model).
+K-L divergence was calculated using the R seewave package \citep{seewave2008}.
+The reduction in K-L divergence between simulated and observed data  shows that model misspecification is reduced by  restricting the reference substitutions to the disciplinary subnetwork (our model), as compared to treating all substitutions within WoS as equiprobable.
 }
@@
 
-Since our analyses show substantial model misspecification for the Uzzi {\em et al.} model, we then examined a modification to the model that we conjectured would better fit the observed data.
-Specifically,
-we conjectured that model misspecification would be reduced by constraining the substitutions to  disciplinary subnetworks,  and tested this by examining the Kullback-Leibler (K-L) Divergence~\citep{kullback_information_1951} between observed and predicted citation distributions,
-restricted to  the set of journals in a given disciplinary subnetwork.  
+ We tested the conjecture that model misspecification would be reduced by constraining the substitutions to  disciplinary subnetworks by examining the Kullback-Leibler (K-L) Divergence~\citep{kullback_information_1951} between observed and predicted citation distributions, restricted to  the set of journals in a given disciplinary subnetwork.
 The results (Table \ref{tab:kld}) confirm this prediction: simulations under the constrained model (which constrains substitutions to the
-disciplinary subnetwork) consistently have a lower K-L divergence compared to simulations under the unconstrained model of Uzzi {\em et al.},  where all references in WoS for a given year are equiprobable.
+disciplinary subnetwork) consistently have a lower K-L divergence compared to simulations under the unconstrained model,  where all references in WoS for a given year are equiprobable.
 Furthermore, the K-L divergence for  the unconstrained model is generally twice as large as the K-L divergence for the models where the references are constrained to  the disciplinary subnetworks (a ratio of 1.96 to 2.77,  and  greater than 2.0 for eight out of nine cases).
-These results clearly demonstrate that the modification to the Uzzi {\em et al.} model produced by  constraining reference substitutions to the given disciplinary network better models the observed data.
+These results clearly demonstrate that constraining reference substitutions to the given disciplinary network better models the observed data.
 
@@
 The calculation for the hit rates for the WoS dataset (bottom row, Figure \ref{fig:Fig2})
-mirrors Uzzi et al.'s results, whereby the largest hit rates were for the HNHC category, despite our methodological improvement of sampling citations in proportion to their frequency. 
+mirrors Uzzi et al.'s results, whereby the largest hit rates were for the HNHC category, despite our methodological changes in sampling citations in proportion to their frequency. 
 However, the trends  for all three  disciplinary subnetworks  are different from those for WoS.
@@
 We conclude that it is likely that the distribution of hits among categories is not uniform and that instead hit rates vary among the categories in all datasets.
-%(Should we insert a table with all statistical results?)
 
@@
 
-Our study shows strong evidence that a key assumption of the Uzzi {\em et al.} model that  
-substitutions of references  are not impacted by discipline deviates from citation practice, and that
-constraining the model to a disciplinary subnetwork reduces the model misspecification.
+Our study shows strong evidence that constraining the model to a disciplinary subnetwork reduces model misspecification.
 Furthermore,  using the constrained model instead of the unconstrained model to redefine high (or low) novelty and conventionality produces different trends, depending on the subnetwork.
 In particular, while Uzzi {\em et al.} found that highly cited papers were most likely to be
-in the HNHC category, this observation does not hold when using the improved model.
-Instead, unlike Uzzi {\em et al.}, we find that conventionality flavored with novelty is {\em not} generally a feature of impactful research. 
-In particular,   high novelty (as defined by Uzzi {\em et al.}) is
-%We conclude that Uzzi et al.'s finding of high hit rates in the HNHC category does not hold generally for disciplinary-based datasets and that 
-%novel citation patterns are 
-not always indicative of impactful research (as reflected in citation counts), as shown by both Immunology and Metabolism having their highest hit rates for low novelty (Figure \ref{fig:Fig2}).
-More generally, these results show that the conclusions of Uzzi {\em et al.} of universal trends in highly cited papers
-may be the consequence of using a random model that has a poor fit to the observed data.
+in the HNHC category, this observation does not consistently hold when using the improved model.
+Instead, we find that conventionality flavored with novelty is {\em not} generally a feature of impactful research.
+In particular,  high novelty (as defined by Uzzi {\em et al.}) is not always indicative of impactful research (as reflected in citation counts), as shown by both Immunology and Metabolism having their highest hit rates for low novelty (Figure \ref{fig:Fig2}).
+More generally, these results show that the conclusions of universal trends in highly cited papers may be the consequence of using a random model that has a poor fit to the observed data.
 
-Of equal concern, and also contrary to Uzzi et al., we found the category displaying the highest hit rate to be sensitive to the percentage of articles deemed to be hit articles (i.e., the definition of highly cited articles), as well as   and the percentile of articles' z-score distributions that delineated between articles of low novelty and high novelty \textcolor{blue}{(data not shown).}
-Faced with this lack of robustness, we are confronted with the necessity of defining defendable parameters, if possible, that determine novelty and conventionality. 
+Of relevance, we found the category displaying the highest hit rate to be sensitive to the percentage of articles deemed to be hit articles (i.e., the definition of highly cited articles), and the percentile of articles' z-score distributions that delineated between articles of low novelty and high novelty \textcolor{blue}{(data not shown).} Faced with this lack of robustness, we are confronted with the necessity of defining defendable parameters, if possible, that determine novelty and conventionality.
 More significantly, we should question whether the simple approach of defining novelty and conventionality, as is done in this article and other research, is sufficient or whether we should expect such variation in the factors associated with impact as we have observed.
-
-%The z-scores that change sign across datasets is either contradictory or an acceptable variation due to the difference in reference sets.
-We contend that it is the former because the inappropriate substitution of citations with those from disciplines that are implausible and because the observed citation frequencies are ignored.
 

### 2019-06-13 cocit_r.tex
cleaned up references

@@
 
-We constructed three disciplinary datasets based on keyword searches: immunology,   metabolism, and   applied physics. 
+We constructed three disciplinary datasets in areas of our interest based on the keyword searches: immunology,   metabolism, and   applied physics.
 For the first two, rooted in biomedical research, we searched Pubmed for the term `immunology' or `metabolism' in the years 1985, 1995, and 2005~(Table \ref{tab:disc-datasets}).
@@
 For the applied physics dataset, we directly searched traditional subject labels in WoS for `applied physics'.
-\textcolor{blue}{
-While immunology and applied physics represent somewhat small subnetworks (each occupying about 4\% of WoS), metabolism represents approximately 22\% of WoS, making them interesting and meaningful test cases.
-}
+While applied physics and immunology represent somewhat small subnetworks (roughly 2-6\% of WoS), metabolism represents approximately 22\% of WoS, making them interesting and meaningful test cases.
 We also examined publications in the five major research areas in the Web of Science: life sciences \& biomedicine, physical sciences, technology, social sciences, and arts \& humanities,  using the extended subcategory classification of 153 sub-groups to categorize disciplinary composition of cited references in the datasets we studied.
@@
 
-For citation shuffling, we developed a performant citation switching algorithm, \emph{runtime enhanced permuting citation switcher (repcs)} (\textcolor{blue}{available in github at XXX}), that randomly permuted citations grouped by year of publication to switch citations while preserving the year of publication for both articles and references, the number of publications and the number of references in each dataset and the disciplinary composition of the references in each dataset.
+For citation shuffling, we developed a performant citation switching algorithm, \emph{runtime enhanced permuting citation switcher (repcs)}~\citep{GithubERNIE2019}, that randomly permuted citations grouped by year of publication to switch citations while preserving the year of publication for both articles and references, the number of publications and the number of references in each dataset and the disciplinary composition of the references in each dataset.
 In implementing this approach, our approach differs from the approach in \cite{uzzi_atypical_2013}, in the following ways (i) we sampled citations proportional to their citation frequency (equivalently, from a multiset rather than a set) in order to better reflect citation practice,  (ii) we permitted a substitution to match the original reference in a publication when the random selection process dictated it rather than attempting to enforce that a different reference be substituted, and (iii) we introduced an error correction step to delete any publications that accumulated duplicate references during the substitution process.

### 2019-06-13 cocit_r.tex
cleaned up references

@@
 Consequently, every article was associated with multiple z-scores corresponding to co-cited journal pairs in its references.
-For each article, positional statistics of z-scores were calculated to set thresholds for a binary (high/low) classification of conventionality (C) using the median z-score of an article and novelty (N) using the tenth percentile of z-scores within an article.
+For each article, positional statistics of z-scores were calculated to set thresholds for a binary classification of conventionality using the median z-score of an article and novelty using the tenth percentile of z-scores within an article.
 Thus, HCLN would denote high conventionality (HC) and low novelty (LN), with all four combinations being possible.
@@
 We also investigated multiple definitions of hit articles with hits defined as the 1\%, 2\%, 5\%, and 10\% top-cited articles.
-Also, mention different thresholds, 1st and 10th, for novelty threshold.
+\textcolor{blue}{ Also, mention different thresholds, 1st and 10th, for novelty threshold.}
 
@@
 TW receives funding from the Grainger Foundation.
-All the code used in this study is freely available from 
-\textcolor{blue}{a Github site}.
+All the code used in this study is freely available from a Github site~\citep{GithubERNIE2019}.
 Access to the bibliographic data analyzed in this study requires a license from Clarivate Analytics, which had no role in funding, experimental design, review of results, and conclusions presented.

### 2019-06-13 cocit_r.tex
handing over to Jim

@@
 \acknowledgments
+ We thank the authors of \cite{uzzi_atypical_2013} for sharing their simulation code.
 We are grateful to Kevin Boyack and Dick Klavans for constructively critical discussions.
-We thank the authors of \cite{uzzi_atypical_2013} for sharing their Python simulation code.
 Research and development reported in this publication was partially supported by Federal funds from the National Institute on Drug Abuse, National Institutes of Health, US Department of Health and Human Services, under Contract Nos.

### 2019-06-13 cocit_r.tex
Minor revisions

@@
 Thus, HCLN would denote high conventionality (HC) and low novelty (LN), with all four combinations being possible.
-The authors observed that HCHN articles were twice as likely to be highly cited, suggesting that novel combinations of ideas flavoring a body of conventional thought were a feature of impact and that `science follows a nearly universal pattern'.
+The authors observed that HCHN articles were twice as likely to be highly cited, suggesting that novel combinations of ideas flavoring a body of conventional thought were a feature of impact and that `science follows a nearly universal pattern.'
 
 Key to Uzzi {\em et al.}, is their random graph model and its underlying assumptions.
-The citation switching algorithm used to generate expected values from random substitutions is designed to preserve the number of publications, the number of references in each publication, the year of publication of both publications and references, and the disciplinary composition of the references cited in these publications.
+The citation switching algorithm used to generate expected values from random substitutions is designed to preserve the number of publications, the number of references in each publication, the year of publication of both publications and references, and the \textcolor{blue}{disciplinary composition of the references cited in these publications}.
 However, a critically important feature of the model is that all references published in the same year have equal probability of being cited by any given publication.
@@
 Pubmed IDs (pmids) returned were matched to WoS IDs (wos\_ids) and used to retrieve relevant articles.
-For the applied physics dataset, we directly searched traditional subject labels in WoS for `applied physics'.
-While applied physics and immunology represent somewhat small subnetworks (roughly 2-6\% of WoS), metabolism represents approximately 22\% of WoS, making them interesting and meaningful test cases.
+For the applied physics dataset, we directly searched traditional subject labels in WoS for `applied physics.' While applied physics and immunology represent somewhat small subnetworks (roughly 2-6\% of WoS), metabolism represents approximately 22\% of WoS, making them interesting and meaningful test cases.
 We also examined publications in the five major research areas in the Web of Science: life sciences \& biomedicine, physical sciences, technology, social sciences, and arts \& humanities,  using the extended subcategory classification of 153 sub-groups to categorize disciplinary composition of cited references in the datasets we studied.
@@
 \caption{Disciplinary Datasets.
-PubMed and WoS were searched for articles using search terms, `immunology', `metabolism', and `applied physics'.
-Counts of publications are shown for each of the three years analyzed and expressed in parentheses as a percentage of the total number of publications in our analytical WoS dataset (Table \ref{tab:summary_data}) for that year.
+PubMed and WoS were searched for articles using search terms, `immunology', `metabolism', and `applied physics.' Counts of publications are shown for each of the three years analyzed and expressed in parentheses as a percentage of the total number of publications in our analytical WoS dataset (Table \ref{tab:summary_data}) for that year.
 Note that Applied Physics and Immunology each represent about 4\% of the publications in WoS, but Metabolism occupies nearly one-fourth of WoS.}

### 2019-06-13 cocit_r.tex
Minor revisions and noting future revisions in blue type

@@
 To study the disciplinary composition of references in our custom datasets, we first used the high level WoS classification of five major research areas: life sciences and biomedicine, physical sciences, social sciences, technology, and arts and humanities.
-The two largest of these research areas are physical sciences and life sciences and biomedicine, which contribute on average approximately 35.1\% and 62.8\%, respectively, of the references in WoS over the three years of interest.
-While there is some variability over the years, according to the Uzzi  {\em et al.} model, we would expect close to 35.1\% of the references cited by the publications in any large network  to be drawn from the physical sciences and roughly 62.8\% of the references to be drawn from the life sciences and biomedicine.
+The two largest of these research areas are \textcolor{blue}{physical sciences and life sciences and biomedicine}, which contribute on average approximately 35.1\% and 62.8\%, respectively, of the references in WoS over the three years of interest.
+\textcolor{blue}{While there is some variability over the years, according to the Uzzi  {\em et al.} model, we would expect close to 35.1\% of the references cited by the publications in any large network  to be drawn from the physical sciences and roughly 62.8\% of the references to be drawn from the life sciences and biomedicine.}
 Yet the empirical data present a very different  story: 79.6\% of the references cited in physical sciences publications are from the physical sciences and 89.9\% of the references cited in life sciences and biomedicine publications are from the life sciences and biomedicine.
@@
 \caption{\ Intra-network citation shuffling preserves the disciplinary composition of references.
-Publications of type Article belonging to the three disciplinary networks (Applied Physics, Immunology, and  Metabolism) were subject to a single shuffle of all their cited references using either the cited references in these networks as a source of random substitutions (bg\_local) or references from all articles in WoS (bg\_allWoS).
+Publications of type Article belonging to the three disciplinary networks (Applied Physics, Immunology, and  Metabolism) were subject to a single shuffle of all their cited references using either the cited references in these networks as a source of random substitutions (\textcolor{blue}{bg\_local}) or references from all articles in WoS (\textcolor{blue}{bg\_allWoS}).
 Citation shuffling was performed using either our algorithm (\emph{repcs})
@@
 For the set of journal pairs in common between a disciplinary network and the full WoS dataset, Kullback-Leibler (K-L) divergences
-between empirical and simulated journal pair frequencies were computed for the years 1985, 1995, and 2005 for the three disciplinary datasets (applied\_physics, immunology, and metabolism) using either the disciplinary network as background or the WoS superset (all\_wos) to generate the null model (Background).
+between empirical and simulated journal pair frequencies were computed for the years 1985, 1995, and 2005 for the three disciplinary datasets (\textcolor{blue}{applied\_physics}, immunology, and metabolism) using either the disciplinary network as background or the WoS superset (all\_wos) to generate the null model (Background).
 K-L divergence was calculated using the R seewave package \citep{seewave2008}.

### 2019-06-13 cocit_r.tex
Minor revisions

@@
  We tested the conjecture that model misspecification would be reduced by constraining the substitutions to  disciplinary subnetworks by examining the Kullback-Leibler (K-L) Divergence~\citep{kullback_information_1951} between observed and predicted citation distributions, restricted to  the set of journals in a given disciplinary subnetwork.
-The results (Table \ref{tab:kld}) confirm this prediction: simulations under the constrained model (which constrains substitutions to the
-disciplinary subnetwork) consistently have a lower K-L divergence compared to simulations under the unconstrained model,  where all references in WoS for a given year are equiprobable.
-Furthermore, the K-L divergence for  the unconstrained model is generally twice as large as the K-L divergence for the models where the references are constrained to  the disciplinary subnetworks (a ratio of 1.96 to 2.77,  and  greater than 2.0 for eight out of nine cases).
+The results (Table \ref{tab:kld}) confirm this prediction: simulations \textcolor{blue}{under the constrained model (which constrains substitutions to the
+disciplinary subnetwork)} consistently have a lower K-L divergence compared to simulations under the unconstrained model,  where all references in WoS for a given year are equiprobable.
+Furthermore, the K-L divergence for  the unconstrained model is generally twice as large as the K-L divergence for the models where the references are constrained to  the disciplinary subnetworks (ratios range from 1.96 to 2.77,  and are greater than 2.0 in eight out of nine cases).
 These results clearly demonstrate that constraining reference substitutions to the given disciplinary network better models the observed data.

### 2019-06-13 cocit_r.tex
Minor Revisions

@@
 highly cited articles  (i.e., ``hit articles")
- into the four categories (HCHN, LCHN, HCLN, LCLN), for different
+ in the four categories (HCHN, LCHN, HCLN, LCLN), for different
 thresholds for hit articles.

### 2019-06-13 cocit_r.tex
Minor revisions

@@
 %Across all years and parameter settings, the highest hit rates in the immunology datasets were sometimes in the LNHC category and sometimes in the HNHC category, and the hit rates for the metabolism datasets reflected this same pattern  (Figure \ref{fig:Fig2}).
- Thus, the category exhibiting the highest hit rate (among highly cited papers) depends on the
-specific disciplinary network and to some extent on the threshold for being highly cited.
+ Thus, the category exhibiting the highest hit rate \textcolor{blue}{(among highly cited papers)} depends on the
+specific disciplinary network and to some extent on the \textcolor{blue}{threshold for being highly cited}.
  %was the case with immunology. 

### 2019-06-13 cocit_r.tex
Minor revisions

@@
 
-We evaluated the statistical significance of the categorical hit rates using multiple methods, some of which we describe here.
+We evaluated the statistical significance of the categorical hit rates using multiple methods.
 Our first test was based on the null hypotheses that hits were distributed randomly among the four categories with uniform probability in proportion to the number of articles in each category.
-Using a Chi-Square Goodness of Fit test, rejecting the null hypothesis in favor of the alternate hypothesis supports a non-uniform dispersion of hits: that is, some of the four categories are individually associated with higher than expected, or lower than expected hit rates.
-The null hypothesis was rejected at a $p<0.001$ in all cases in  Figure \ref{fig:Fig2}, with the exception of the immunology and applied datasets where hit articles are designated as the top 1\% of articles: valid tests were not possible in those instances due to too few expected hits.
+Rejecting the null hypothesis, using a Chi-Square Goodness of Fit test, supports a non-uniform dispersion of hits with some of the four categories being associated with higher or lower than expected expected hit rates.
+The null hypothesis was rejected at a $p<0.001$ in all cases in  Figure \ref{fig:Fig2}, with the exception of the immunology and applied physics datasets where hit articles are designated as the top 1\% of articles: valid tests were not possible in those instances due to too few expected hits.
 The null hypothesis was rejected with $p<0.001$ for all valid tests for all parameter settings, all datasets, and all years: hypotheses tests were valid in 73 of 96 instances.
-We conclude that it is likely that the distribution of hits among categories is not uniform and that instead hit rates vary among the categories in all datasets.
+We conclude that it is likely that the distribution of hits among categories is not uniform and that, instead, hit rates vary among the categories in all datasets.
 

### 2019-06-13 cocit_r.tex
Minor revisions

@@
 
-We also tested the explanatory power of each framework dimension by classifying articles as Low Novelty (LN) or High Novelty (HN) and, separately, as having Low Conventionality (LC) or High Conventionality (HC).
+We also tested the explanatory power of each framework dimension by classifying articles as %Low Novelty (
+LN %)
+ or 
+% High Novelty (
+HN
+%)
+ and, separately, as 
+% having Low Conventionality (
+LC
+%) 
+or 
+%High Conventionality (
+HC
+%)
+.
 We tested the null hypothesis that hits are distributed between LN and HN (LC and HC) in proportion to the total number of articles assigned to those categories.
 That null hypothesis was rejected for the WoS data along both dimensions.
-Consistent with previous analysis, hit articles were overrepresented in the HC category in every instance of WoS data at a $p<0.001$ and hit articles were overrepresented in the HN category at a $p<0.001$ in all but two cases.
-The p-values, in those cases, were $0.002$ and $0.007$.  
+Consistent with the findings in~\cite{uzzi_atypical_2013}, hit articles were overrepresented in the HC category in every instance of WoS data at a $p<0.001$ and also overrepresented in the HN category at a $p<0.001$ in all but two cases: the p-values in those exceptions were $0.002$ and $0.007$.
 Hits in the immunology and metabolism data were overrepresented in the HC category with the same statistical significance as for WoS.

### 2019-06-13 cocit_r.tex
Minor revisions

@@
 
-\textcolor{blue}{I did not review the next two paragraphs}
+\textcolor{blue}{I did not review the next two paragraphs.  I did--JRB}
 
@@
 %High Conventionality (
-HC
+HC. 
 %)
-.
 We tested the null hypothesis that hits are distributed between LN and HN (LC and HC) in proportion to the total number of articles assigned to those categories.
@@
 Hits in the immunology and metabolism data were overrepresented in the HC category with the same statistical significance as for WoS.
-The relationship of novelty with hits in the immunology and metabolism data differed dramatically from the WoS, however, with statistically significant findings of hit articles being sometimes overrepresented in the LN category, and sometimes being underrepresented.
-Of the 12 tests for applied physics, the statistical significance supporting a positive relationship between hit articles and HN were all $p<0.10$, and 10 of 12 were $p<0.05$.
-These tests also indicated strong support for the relationship between LN and hit articles in applied physics in a limited number of tests, with $p<0.10$ in 5 of 12 instances and $p < 0.05$ in 3 of 12 instances.
+\textcolor{blue}{The relationship of novelty with hits in the immunology and metabolism data differed dramatically from the WoS, however, with statistically significant findings of hit articles being sometimes overrepresented in the LN category, and sometimes being underrepresented.}  In applied physics, hit articles were positively related with HN with a statistical significance of at least $p<0.10$ in all 12 parameter sets, and at $p<0.05$ in 10 of 12 cases.
+Furthermore, a strong positive relationship was found between LC and hit articles in applied physics in 5 of 12 instances with $p<0.10$.
 These results suggest that (1) both conventionality and novelty are strongly related to hits in the WoS, (2) the conventionality dimension is strongly related with hits in immunology and metabolism and novelty is not, (3) novelty is more strongly related with hits in applied physics than is conventionality.
-More generally, we find that the dimensions most strongly related with hit articles vary across disciplines and between disciplinary and broad data sets.
+More generally, we find that the dimensions most strongly related with hit articles vary between disciplinary and broad data sets, and also among disciplines.
 
-\textcolor{blue}{I think we should delete the next paragraph.}
-That fewer z-scores are negative in the WoS dataset relative to the immunology dataset may be directly due to the uniform sampling of references, whereby many resulting journal pairs are never observed in the literature and so the expected frequencies of those observed pairs have lower expected values, thus biasing their z-scores upward.
+%\textcolor{blue}{I think we should delete the next paragraph.}
+%That fewer z-scores are negative in the WoS dataset relative to the immunology dataset may be directly due to the uniform sampling of references, whereby many resulting journal pairs are never observed in the literature and so the expected frequencies of those observed pairs have lower expected values, thus biasing their z-scores upward.
 In addition, treating citation as a set versus a multiset means that a random model will sample popular citations downward, thus further increasing their z-scores.\emph{need confirmation from Jim here}.

### 2019-06-13 cocit_r.tex
Minor revisions

@@
 
-Of relevance, we found the category displaying the highest hit rate to be sensitive to the percentage of articles deemed to be hit articles (i.e., the definition of highly cited articles), and the percentile of articles' z-score distributions that delineated between articles of low novelty and high novelty \textcolor{blue}{(data not shown).} Faced with this lack of robustness, we are confronted with the necessity of defining defendable parameters, if possible, that determine novelty and conventionality.
+Of relevance, we found the category displaying the highest hit rate to be sensitive to the study parameters, which are the percentage of articles classified as hits and the z-score percentile threshold that delineates LN and HN.
+\textcolor{blue}{(data not shown).} Faced with this lack of robustness, we are confronted with the necessity of defining defendable parameters, if possible, that determine novelty and conventionality.
 More significantly, we should question whether the simple approach of defining novelty and conventionality, as is done in this article and other research, is sufficient or whether we should expect such variation in the factors associated with impact as we have observed.

### 2019-06-13 cocit_r.tex
Minor revisions

@@
 Of relevance, we found the category displaying the highest hit rate to be sensitive to the study parameters, which are the percentage of articles classified as hits and the z-score percentile threshold that delineates LN and HN.
-\textcolor{blue}{(data not shown).} Faced with this lack of robustness, we are confronted with the necessity of defining defendable parameters, if possible, that determine novelty and conventionality.
-More significantly, we should question whether the simple approach of defining novelty and conventionality, as is done in this article and other research, is sufficient or whether we should expect such variation in the factors associated with impact as we have observed.
+\textcolor{blue}{(data not shown).} This lack of robustness makes parameter selection of the utmost importance.
+However, the most appropriate definitions of novelty, conventionality, and hit articles in the framework that we have applied are not clear.
+More research might be done in that regard or, further, in investigating whether the current approach of defining novelty, conventionality, and impactful research sufficiently captures the complexity of the issue at hand.
 

### 2019-06-13 cocit_r.tex
Minor revisions and additions

@@
 More generally, these results show that the conclusions of universal trends in highly cited papers may be the consequence of using a random model that has a poor fit to the observed data.
+
+\textcolor{blue}{Placement and relevance to be determined.
+This paragraph is not yet well written...
+still working on it.} We described concerns with model misspecification at the outset in two general dimensions: the background dataset and sampling methodology for the random graph.
+The differences we found from prior research in which categories demonstrated the highest hit rates were caused both by differences in the background dataset and in our sampling methodology through differences in article z-score distributions.
+When z-scores are shifted downward, for example, using one algorithm versus another, then the former algorithm can result in an increased percentage of HN articles.
+We thought it important to identify which of our methodological approaches might account    Our sampling approach includes several enhancements to prior work, most notably sampling from a multiset so as to reflect the observed frequencies of individual citations as well as their associated journals and disciplines.
 

### 2019-06-13 cocit_r.tex
Minor revisions

@@
 The differences we found from prior research in which categories demonstrated the highest hit rates were caused both by differences in the background dataset and in our sampling methodology through differences in article z-score distributions.
-When z-scores are shifted downward, for example, using one algorithm versus another, then the former algorithm can result in an increased percentage of HN articles.
+When z-scores are shifted downward using one algorithm versus another, for example, then the former algorithm can result in an increased percentage of HN articles.
 We thought it important to identify which of our methodological approaches might account    Our sampling approach includes several enhancements to prior work, most notably sampling from a multiset so as to reflect the observed frequencies of individual citations as well as their associated journals and disciplines.

### 2019-06-13 cocit_r.tex
Minor revisions. Discussion paragraph added.

@@
 When z-scores are shifted downward using one algorithm versus another, for example, then the former algorithm can result in an increased percentage of HN articles.
-We thought it important to identify which of our methodological approaches might account    Our sampling approach includes several enhancements to prior work, most notably sampling from a multiset so as to reflect the observed frequencies of individual citations as well as their associated journals and disciplines.
+We thought it important to determine the extent to which each of our methodological differences contributed to our observations.
+We found that z-scores of 28.6\% of the journal pairs changed signs with our sampling algorithm, for example, when computed with respect to the WoS dataset versus the immunology dataset.
+In contrast, 2.8\% of z-scores changed signs in the WoS dataset depending on whether Uzzi st al.'s approach was used versus ours and x\% z-scores in the case of the immunology dataset.
+\textcolor{blue}{Need to insert data for the immunology dataset here also for an apples-to-apples comparison.} We conclude that the choice of background datasets is the source of a majority of differences we observed from prior research, although our sampling approach, most notably sampling from a multiset so as to reflect the observed frequencies of individual citations as well as their associated journals and disciplines, also can create material differences.
 

### 2019-06-13 cocit_r.tex
Minor revisions

--- 2019-06-13 cocit_r.tex
@@
 This paragraph is not yet well written...
-still working on it.} We described concerns with model misspecification at the outset in two general dimensions: the background dataset and sampling methodology for the random graph.
-The differences we found from prior research in which categories demonstrated the highest hit rates were caused both by differences in the background dataset and in our sampling methodology through differences in article z-score distributions.
+still working on it.} We described concerns with model misspecification at the outset along two general dimensions: the background dataset and sampling methodology for the random graph.
+The differences we found from prior research in terms of which categories demonstrated the highest hit rates were caused both by using disciplinary datasets and our sampling methodology through the article z-score distributions.
 When z-scores are shifted downward using one algorithm versus another, for example, then the former algorithm can result in an increased percentage of HN articles.
-We thought it important to identify which of our methodological approaches might account    Our sampling approach includes several enhancements to prior work, most notably sampling from a multiset so as to reflect the observed frequencies of individual citations as well as their associated journals and disciplines.
+We thought it important to determine the extent to which each of our methodological differences contributed to our observations.
+We found that z-scores of 28.6\% of the journal pairs changed signs with our sampling algorithm, for example, when computed with respect to the WoS dataset versus the immunology dataset.
+In contrast, 2.8\% of z-scores changed signs in the WoS dataset depending on whether Uzzi et al.'s or our random model was used and x\% z-scores changed signs in the case of the immunology dataset.
+\textcolor{blue}{Need to insert data for the immunology dataset here also for an apples-to-apples comparison.} We conclude that the choice of background datasets is the source of a majority of differences we observed the categories demonstrating the highest hit rates, although our sampling approach, most notably sampling from a multiset so as to reflect the observed frequencies of individual citations as well as their associated journals and disciplines, can also create material differences.
 

### 2019-06-13 cocit_r.tex
Minor revisions

@@
 For each article, positional statistics of z-scores were calculated to set thresholds for a binary classification of conventionality using the median z-score of an article and novelty using the tenth percentile of z-scores within an article.
-Thus, HCLN would denote high conventionality (HC) and low novelty (LN), with all four combinations being possible.
-The authors observed that HCHN articles were twice as likely to be highly cited, suggesting that novel combinations of ideas flavoring a body of conventional thought were a feature of impact and that `science follows a nearly universal pattern.'
+\textcolor{blue}{Note that Uzzi et al.
+reported on the 10th percentile in the paper, but investigated many other definitions of novelty in the supplemental paper.
+Should this be noted?
+Perhaps not for sake of brevity and we are citing just the main paper here.} Thus, HCLN would denote high conventionality (HC) and low novelty (LN), with all four combinations being possible.
+The authors observed that HCHN articles were twice as likely to be highly cited, suggesting that novel combinations of ideas flavoring a body of conventional thought were a feature of impact and that `science follows a nearly universal pattern.' \textcolor{blue}{Should we be more precise here in using 'twice?'  Uzzi et al.
+say twice the background rate whereas this might be construed as twice the rate of other categories which is a much different thing.}
 

### 2019-06-13 cocit_r.tex
Update cocit_r.tex

@@
 Key to Uzzi {\em et al.}, is their random graph model and its underlying assumptions.
-The citation switching algorithm used to generate expected values from random substitutions is designed to preserve the number of publications, the number of references in each publication, the year of publication of both publications and references, and the \textcolor{blue}{disciplinary composition of the references cited in these publications}.
+The citation switching algorithm used to generate expected values from random substitutions is designed to preserve the number of publications, the number of references in each publication, and the year of publication of both publications and references.
 However, a critically important feature of the model is that all references published in the same year have equal probability of being cited by any given publication.

### 2019-06-13 cocit_r.tex
lots of edits, look for blue text

--- 2019-06-13 cocit_r.tex
@@
 For each article, positional statistics of z-scores were calculated to set thresholds for a binary classification of conventionality using the median z-score of an article and novelty using the tenth percentile of z-scores within an article.
+%\textcolor{blue}{Note that Uzzi et al.
+reported on the 10th percentile in the paper, but investigated many other definitions of novelty in the supplemental paper.
+Should this be noted?
+Perhaps not for sake of brevity and we are citing just the main paper here.}
 Thus, HCLN would denote high conventionality (HC) and low novelty (LN), with all four combinations being possible.
-The authors observed that HCHN articles were twice as likely to be highly cited, suggesting that novel combinations of ideas flavoring a body of conventional thought were a feature of impact and that `science follows a nearly universal pattern.'
+The authors observed that HCHN articles were twice as likely to be highly cited \textcolor{blue}{compared to the background rate}, suggesting that novel combinations of ideas flavoring a body of conventional thought were a feature of impact and that `science follows a nearly universal pattern.'
+%\textcolor{blue}{Should we be more precise here in using 'twice?'  Uzzi et al.
+say twice the background rate whereas this might be construed as twice the rate of other categories which is a much different thing.}
 
 Key to Uzzi {\em et al.}, is their random graph model and its underlying assumptions.
-The citation switching algorithm used to generate expected values from random substitutions is designed to preserve the number of publications, the number of references in each publication, the year of publication of both publications and references, and the \textcolor{blue}{disciplinary composition of the references cited in these publications}.
+The citation switching algorithm used to generate expected values from random substitutions is designed to preserve the number of publications, the number of references in each publication, and the year of publication of both publications and references.
 However, a critically important feature of the model is that all references published in the same year have equal probability of being cited by any given publication.
@@
 all references as equiprobable, independent of discipline, apply to \cite{boyack_vs_uzzi_2014} as well.
- We hypothesized that modifying the normalization to constrain references to be drawn only from the disciplinary citation subnetwork,   rather than all of WoS, would reduce model misspecification.
+ We hypothesized that modifying the normalization to constrain references to be drawn only from the disciplinary citation subnetwork  \textcolor{blue}{(i.e., the ``local network")}  rather than all of WoS
+ \textcolor{blue}{ (the ``global network") } would reduce model misspecification.  
  Consequently, we used keyword searches of the scientific literature to construct exemplar citation networks themed around academic disciplines: \emph{applied physics, immunology, and metabolism}.
@@
 
-Our analyses, using multiple techniques, provides substantial evidence that constraining the reference substitutions to the disciplinary subnetwork reduces model misspecification compared to treating all substitutions within WoS as equiprobable.
+Our analyses, using multiple techniques, provides substantial evidence that constraining the reference substitutions to the \textcolor{blue}{local network}  reduces model misspecification compared to 
+the \textcolor{blue}{unconstrained model} that \textcolor{blue}{uses the global network, WoS, and treats all substitutions within WoS as equiprobable.} 
 Furthermore, re-analyses of these three semantically-themed
- citation networks  under the improved model reveals strikingly different trends than those 
- observed by Uzzi {\em et al.} 
- For example, while Uzzi {\em et al.}~claimed that highly cited articles are more likely to be both HC and HN than expected, and that this trend held across all subdisciplines, we find that these trends vary with the subdiscipline so that no universal trends can be established.
+ citation networks  under the improved model reveals strikingly different trends than
+ when using all of WoS. 
+ For example, while Uzzi {\em et al.}~claimed that highly cited articles are more likely to be both HC and HN than expected and that this trend held across all subdisciplines, we find that these trends vary with the subdiscipline so that no universal trends can be established.
  Specifically, 
@@
 To consider the relationship between citation impact, conventionality, and novelty we calculated percentiles for the number of accumulated citations in the first 8 years since publication for each article we studied and stratified.
-We also investigated multiple definitions of hit articles with hits defined as the 1\%, 2\%, 5\%, and 10\% top-cited articles.
-\textcolor{blue}{ Also, mention different thresholds, 1st and 10th, for novelty threshold.}
+We also investigated multiple definitions of hit articles, with hits defined as the 1\%, 2\%, 5\%, and 10\% top-cited articles, and \textcolor{blue}{ 1st and 10th percentiles as thresholds for high novelty}.
+% \textcolor{blue}%{ Also, mention different thresholds, 1st and 10th, for novelty threshold.}
 
@@
 
-\subsection{Model Misspecification and the Attributes of Disciplinary Context} A source of misspecification in the Uzzi {\em et al.}~model arises from not accounting for disciplinary heterogeneity by treating all references as equiprobable substituents.
+\subsection{Model Misspecification and the Attributes of Disciplinary Context} 
+A source of misspecification in the global model arises from not accounting for disciplinary heterogeneity by treating all references  \textcolor{blue}{within WoS} as equiprobable substituents.
 Under this model, the probability of replacing a reference in one discipline by another reference in a second discipline is identical to the proportion of the articles in WoS that from the second discipline.
-If the Uzzi {\em et al.} model accurately reflects citation practice, the expected proportion of references within papers published in a given discipline $D$ would be equal to the proportion of references in  $D$, and conversely, the degree to which the proportion deviates from the expected value would reflect the extent of model misspecification.
+If the global model accurately reflects citation practice, the expected proportion of references within papers published in a given discipline $D$ would be equal to the proportion of references in  $D$, and conversely, the degree to which the proportion deviates from the expected value would reflect the extent of model misspecification.
 
@@
 To study the disciplinary composition of references in our custom datasets, we first used the high level WoS classification of five major research areas: life sciences and biomedicine, physical sciences, social sciences, technology, and arts and humanities.
-The two largest of these research areas are \textcolor{blue}{physical sciences and life sciences and biomedicine}, which contribute on average approximately 35.1\% and 62.8\%, respectively, of the references in WoS over the three years of interest.
-\textcolor{blue}{While there is some variability over the years, according to the Uzzi  {\em et al.} model, we would expect close to 35.1\% of the references cited by the publications in any large network  to be drawn from the physical sciences and roughly 62.8\% of the references to be drawn from the life sciences and biomedicine.}
+The two largest of these research areas are physical sciences and life sciences \& biomedicine, which contribute on average approximately 35.1\% and 62.8\%, respectively, of the references in WoS over the three years of interest.
+\textcolor{blue}{While there is some variability over the years, under the unconstrained model, we would expect close to 35\% of the references cited by the publications in any large network  to be drawn from the physical sciences and close to 63\% of the references to be drawn from  life sciences and biomedicine.}
 Yet the empirical data present a very different  story: 79.6\% of the references cited in physical sciences publications are from the physical sciences and 89.9\% of the references cited in life sciences and biomedicine publications are from the life sciences and biomedicine.
@@
 \includegraphics[width=0.6\linewidth]{background-effect}     
-\caption{\ Intra-network citation shuffling preserves the disciplinary composition of references.
-Publications of type Article belonging to the three disciplinary networks (Applied Physics, Immunology, and  Metabolism) were subject to a single shuffle of all their cited references using either the cited references in these networks as a source of random substitutions (\textcolor{blue}{bg\_local}) or references from all articles in WoS (\textcolor{blue}{bg\_allWoS}).
-Citation shuffling was performed using either our algorithm (\emph{repcs})
- or that of Uzzi et al.~(\emph{umsj}).
+\caption{\textcolor{blue}{ Citation shuffling using the local network preserves the disciplinary composition of references within subnetworks, but using the global network does not.}   Publications of type Article belonging to the three disciplinary networks (ap=applied physics, imm=immunology, and  metab=metabolism) were subject to a single shuffle of all their cited references using either the local network (i.e., the cited references in these networks, denoted  bg\_local) or the global network (i.e., references from all articles in WoS, denoted bg\_WoS) as the source of allowed substitutions, where ``bg" indicates the disciplinary subnetwork.
+Citation shuffling was performed using either our algorithm (\emph{repcs}, top row)
+ or that of Uzzi et al.~(\emph{umsj}, bottom row).
  The disciplinary composition of cited references before and after shuffling was measured as frequencies for each of 153 sub-disciplines (from the extended subject classification in WoS) and expressed as a fold difference between citation counts grouped by subject for original (o) and shuffled (s) references using the formula (fold\_difference = $ifelse(o > s, o/s, s/o)$) and rounded to the nearest integer.
@@
 \begin{table}[ht]
-\caption{Model misspecification is reduced by constraining substitutions to disciplinary subnetworks.
+\caption{Model misspecification is reduced by constraining substitutions to the local  disciplinary subnetworks.
 For the set of journal pairs in common between a disciplinary network and the full WoS dataset, Kullback-Leibler (K-L) divergences
-between empirical and simulated journal pair frequencies were computed for the years 1985, 1995, and 2005 for the three disciplinary datasets (\textcolor{blue}{applied\_physics}, immunology, and metabolism) using either the disciplinary network as background or the WoS superset (all\_wos) to generate the null model (Background).
+between empirical and simulated journal pair frequencies were computed for the years 1985, 1995, and 2005 for the three disciplinary datasets (applied physics, immunology, and metabolism) using either the disciplinary network as background or the WoS superset (all\_wos) to generate the null model (Background).
 K-L divergence was calculated using the R seewave package \citep{seewave2008}.
@@
   \hline
- Disciplinary Network & Year & Background & K-L Divergence & Ratio \\ 
-  \hline
- appl\_physics & 1985 & appl\_physics & 1.21 &  \\ 
-  & 1985 & all\_wos & 2.37 & 1.96 \\ 
-  & 1995 & appl\_physics & 0.86 &  \\ 
-  & 1995 & all\_wos & 2.37 & 2.77 \\ 
-  & 2005 & appl\_physics & 0.95 &  \\ 
-  & 2005 & all\_wos & 2.35 & 2.47 \\ 
-    \hline
-  immunology & 1985 & immunology & 0.75 &  \\ 
-  & 1985 & all\_wos & 1.68 & 2.24 \\ 
-   & 1995 & immunology & 0.78 &  \\ 
-   & 1995 & all\_wos & 1.70 & 2.19 \\ 
-   & 2005 & immunology & 0.73 &  \\ 
-  & 2005 & all\_wos & 1.92 & 2.63 \\ 
-    \hline
- metabolism & 1985 & metabolism & 1.11 &  \\ 
-   & 1985 & all\_wos & 2.24 & 2.02 \\ 
-  & 1995 & metabolism & 1.07 &  \\ 
-  & 1995 & all\_wos & 2.33 & 2.17 \\ 
-     & 2005 & metabolism & 1.19 &  \\ 
-   & 2005 & all\_wos & 2.60 & 2.18 \\ 
+ Disciplinary Network & Year & Background Network & K-L Divergence & Ratio \\ 
+  \hline
+ appl\_physics & 1985 & local & 1.21 &  \\ 
+  & 1985 & global & 2.37 & 1.96 \\ 
+  & 1995 & local & 0.86 &  \\ 
+  & 1995 & global  & 2.37 & 2.77 \\ 
+  & 2005 & local & 0.95 &  \\ 
+  & 2005 & global  & 2.35 & 2.47 \\ 
+    \hline
+  immunology & 1985 & local & 0.75 &  \\ 
+  & 1985 & global  & 1.68 & 2.24 \\ 
+   & 1995 & local & 0.78 &  \\ 
+   & 1995 & global  & 1.70 & 2.19 \\ 
+   & 2005 & local & 0.73 &  \\ 
+  & 2005 & global  & 1.92 & 2.63 \\ 
+    \hline
+ metabolism & 1985 & local & 1.11 &  \\ 
+   & 1985 & global  & 2.24 & 2.02 \\ 
+  & 1995 & local & 1.07 &  \\ 
+  & 1995 & global  & 2.33 & 2.17 \\ 
+     & 2005 & local & 1.19 &  \\ 
+   & 2005 & global  & 2.60 & 2.18 \\ 
    \hline
@@
  We tested the conjecture that model misspecification would be reduced by constraining the substitutions to  disciplinary subnetworks by examining the Kullback-Leibler (K-L) Divergence~\citep{kullback_information_1951} between observed and predicted citation distributions, restricted to  the set of journals in a given disciplinary subnetwork.
-The results (Table \ref{tab:kld}) confirm this prediction: simulations \textcolor{blue}{under the constrained model (which constrains substitutions to the
-disciplinary subnetwork)} consistently have a lower K-L divergence compared to simulations under the unconstrained model,  where all references in WoS for a given year are equiprobable.
-Furthermore, the K-L divergence for  the unconstrained model is generally twice as large as the K-L divergence for the models where the references are constrained to  the disciplinary subnetworks (ratios range from 1.96 to 2.77,  and are greater than 2.0 in eight out of nine cases).
-These results clearly demonstrate that constraining reference substitutions to the given disciplinary network better models the observed data.
+ The results (Table \ref{tab:kld}) confirm this prediction: simulations 
+under the constrained model consistently have a lower K-L divergence compared to simulations under the unconstrained model,  where all references in WoS for a given year are equiprobable. 
+\textcolor{blue}{
+Furthermore, the K-L divergence for  the unconstrained model (background network all of WoS) is generally twice as large as the K-L divergence for the constrained models (where the background network is the local disciplinary subnetwork), with ratios that range from 1.96 to 2.77,  and are greater than 2.0 in eight out of nine cases.
+These results clearly demonstrate that constraining reference substitutions to the given local disciplinary network better fits the observed data, so that there is reduced model misspecification.}
 
@@
 %Across all years and parameter settings, the highest hit rates in the immunology datasets were sometimes in the LNHC category and sometimes in the HNHC category, and the hit rates for the metabolism datasets reflected this same pattern  (Figure \ref{fig:Fig2}).
- Thus, the category exhibiting the highest hit rate \textcolor{blue}{(among highly cited papers)} depends on the
-specific disciplinary network and to some extent on the \textcolor{blue}{threshold for being highly cited}.
+ Thus, the category exhibiting the highest hit rate among highly cited papers depends on the
+specific disciplinary network and to some extent on the threshold for being highly cited.
  %was the case with immunology. 
@@
 
-\textcolor{blue}{I did not review the next two paragraphs.  I did--JRB}
+%\textcolor{blue}{I did not review the next two paragraphs.  I did--JRB}
 
@@
 Hits in the immunology and metabolism data were overrepresented in the HC category with the same statistical significance as for WoS.
-\textcolor{blue}{The relationship of novelty with hits in the immunology and metabolism data differed dramatically from the WoS, however, with statistically significant findings of hit articles being sometimes overrepresented in the LN category, and sometimes being underrepresented.}  In applied physics, hit articles were positively related with HN with a statistical significance of at least $p<0.10$ in all 12 parameter sets, and at $p<0.05$ in 10 of 12 cases.
+\textcolor{blue}{The relationship of novelty with hits in the immunology and metabolism data differed dramatically from the WoS, however, with statistically significant findings of hit articles being sometimes overrepresented in the LN category, and sometimes being underrepresented.}
+In applied physics, hit articles were positively related with HN with a statistical significance of at least $p<0.10$ in all 12 parameter sets, and at $p<0.05$ in 10 of 12 cases.
 Furthermore, a strong positive relationship was found between LC and hit articles in applied physics in 5 of 12 instances with $p<0.10$.
-These results suggest that (1) both conventionality and novelty are strongly related to hits in the WoS, (2) the conventionality dimension is strongly related with hits in immunology and metabolism and novelty is not, (3) novelty is more strongly related with hits in applied physics than is conventionality.
+These results suggest that (1) both conventionality and novelty are strongly related to hits in the WoS, (2) the conventionality dimension is strongly related with hits in immunology and metabolism and novelty is not, and (3) novelty is more strongly related with hits in applied physics than is conventionality.
 More generally, we find that the dimensions most strongly related with hit articles vary between disciplinary and broad data sets, and also among disciplines.
 
-%\textcolor{blue}{I think we should delete the next paragraph.}
-%That fewer z-scores are negative in the WoS dataset relative to the immunology dataset may be directly due to the uniform sampling of references, whereby many resulting journal pairs are never observed in the literature and so the expected frequencies of those observed pairs have lower expected values, thus biasing their z-scores upward.
-In addition, treating citation as a set versus a multiset means that a random model will sample popular citations downward, thus further increasing their z-scores.\emph{need confirmation from Jim here}.
-
-\section{Discussion}
-
-\emph{needs to be expanded}
-
-Our study shows strong evidence that constraining the model to a disciplinary subnetwork reduces model misspecification.
-Furthermore,  using the constrained model instead of the unconstrained model to redefine high (or low) novelty and conventionality produces different trends, depending on the subnetwork.
-In particular, while Uzzi {\em et al.} found that highly cited papers were most likely to be
-in the HNHC category, this observation does not consistently hold when using the improved model.
-Instead, we find that conventionality flavored with novelty is {\em not} generally a feature of impactful research.
-In particular,  high novelty (as defined by Uzzi {\em et al.}) is not always indicative of impactful research (as reflected in citation counts), as shown by both Immunology and Metabolism having their highest hit rates for low novelty (Figure \ref{fig:Fig2}).
-More generally, these results show that the conclusions of universal trends in highly cited papers may be the consequence of using a random model that has a poor fit to the observed data.
-
-\textcolor{blue}{Placement and relevance to be determined.
-This paragraph is not yet well written...
-still working on it.} We described concerns with model misspecification at the outset along two general dimensions: the background dataset and sampling methodology for the random graph.
+We described concerns with model misspecification along two general dimensions: the background dataset and sampling methodology for the random graph.
 The differences we found from prior research in terms of which categories demonstrated the highest hit rates were caused both by using disciplinary datasets and our sampling methodology through the article z-score distributions.
@@
 We found that z-scores of 28.6\% of the journal pairs changed signs with our sampling algorithm, for example, when computed with respect to the WoS dataset versus the immunology dataset.
-In contrast, 2.8\% of z-scores changed signs in the WoS dataset depending on whether Uzzi et al.'s or our random model was used and x\% z-scores changed signs in the case of the immunology dataset.
-\textcolor{blue}{Need to insert data for the immunology dataset here also for an apples-to-apples comparison.} We conclude that the choice of background datasets is the source of a majority of differences we observed the categories demonstrating the highest hit rates, although our sampling approach, most notably sampling from a multiset so as to reflect the observed frequencies of individual citations as well as their associated journals and disciplines, can also create material differences.
-
+In contrast, 2.8\% of z-scores changed signs in the WoS dataset depending on whether Uzzi et al.'s or our random model was used.
+% and x\% z-scores changed signs in the case of the immunology dataset. \textcolor{blue}{Need to insert data for the immunology dataset here also for an apples-to-apples comparison.} 
+We conclude that the choice of background datasets is the source of a majority of differences we observed the categories demonstrating the highest hit rates, although our sampling approach, most notably sampling from a multiset so as to reflect the observed frequencies of individual citations as well as their associated journals and disciplines, can also create material differences.
+
+%\textcolor{blue}{I think we should delete the next paragraph.}
+%That fewer z-scores are negative in the WoS dataset relative to the immunology dataset may be directly due to the uniform sampling of references, whereby many resulting journal pairs are never observed in the literature and so the expected frequencies of those observed pairs have lower expected values, thus biasing their z-scores upward.
+In addition, treating citation as a set versus a multiset means that a random model will sample popular citations downward, thus further increasing their z-scores.\emph{need confirmation from Jim here}.
+
+\section{Discussion}
+
+%\emph{needs to be expanded}
+
+\textcolor{blue}{
+The fundamental difference between the Uzzi {\em et al.} model and ours is just one parameter--the set of references that can be used as substituents during the substitution process.
+We provided several lines of evidence that showed that changing this one parameter from all of WoS to the local disciplinary subnetwork
+%This study shows strong evidence that constraining the substitution model to the local disciplinary subnetwork 
+reduces model misspecification.
+Furthermore,  using the constrained model (which allows substitutions only within the local subnetwork)  instead of the unconstrained model (which allows substitutions in the entire WoS network) produces different trends in terms of conventionality and novelty, depending on the subnetwork.}
+ In particular, when using the unconstrained model, highly cited papers were most likely to be
+in the HNHC category but this trend does not consistently hold when using the constrained model.
+Instead, we find that conventionality flavored with novelty is {\em not} generally a feature of impactful research.
+In particular,  high ``novelty" is not always indicative of impactful research (as reflected in citation counts), as shown by both Immunology and Metabolism having their highest hit rates for low novelty (Figure \ref{fig:Fig2}).
+%\textcolor{blue}{Placement and relevance to be determined.  This paragraph is not yet well written... still working on it.} 
 Of relevance, we found the category displaying the highest hit rate to be sensitive to the study parameters, which are the percentage of articles classified as hits and the z-score percentile threshold that delineates LN and HN.
 \textcolor{blue}{(data not shown).} This lack of robustness makes parameter selection of the utmost importance.
-However, the most appropriate definitions of novelty, conventionality, and hit articles in the framework that we have applied are not clear.
-More research might be done in that regard or, further, in investigating whether the current approach of defining novelty, conventionality, and impactful research sufficiently captures the complexity of the issue at hand.
+%However, the most appropriate definitions of novelty, conventionality, and hit articles in the framework that we have applied are not clear.
+
+\textcolor{blue}{
+More generally, these results show that the conclusions of universal trends in highly cited papers may be the consequence of using a random model that has a poor fit to the observed data and that is not robust to changes in thresholds for defining high impart articles or high novelty.
+%More research might be done in that regard or, further, in investigating whether the current approach of defining novelty, conventionality, and impactful research sufficiently captures the complexity of the issue at hand.
+However, although  the constrained model reduces model misspecification compared to the unconstrained model,  this does not imply that the constrained model is reasonable nor that trends observed under the constrained model should be considered relevant to understanding scientific practice.
+Indeed, there are significant  challenges in using random models to understand human behavior, of which citation practice is one example.
+}
+
+\textcolor{blue}{
+However, this study does suggest some directions for future work...
+First, we do show that disciplinary behavior differs, so models based on individual disciplines
+}
 

### 2019-06-13 cocit_r.tex
George passes the token

@@
 The frequency with which references were co-cited  in 17.9 million articles and their cited references from the Web of Science (WoS) was calculated and expressed as journal pair frequencies (observed co-citation frequencies).
-Expected co-citation values were generated from Monte Carlo simulations under a random graph model.
-Observed frequencies were then normalized (shifted and scaled) to averaged expected values from ten simulations and termed as \emph{z-scores}.
+Expected co-citation values were generated from randomized networks using Monte Carlo simulations under a random graph model.
+Observed frequencies were then normalized (shifted and scaled) to averaged expected values from ten randomized networks and termed as \emph{z-scores}.
 Consequently, every article was associated with multiple z-scores corresponding to co-cited journal pairs in its references.
-For each article, positional statistics of z-scores were calculated to set thresholds for a binary classification of conventionality using the median z-score of an article and novelty using the tenth percentile of z-scores within an article.
-%\textcolor{blue}{Note that Uzzi et al.
-reported on the 10th percentile in the paper, but investigated many other definitions of novelty in the supplemental paper.
-Should this be noted?
-Perhaps not for sake of brevity and we are citing just the main paper here.}
+For each article, positional statistics of z-scores were calculated and evaluated to set thresholds for a binary classification of conventionality using the median z-score of an article and novelty using the tenth percentile of z-scores within an article.
+
 Thus, HCLN would denote high conventionality (HC) and low novelty (LN), with all four combinations being possible.
-The authors observed that HCHN articles were twice as likely to be highly cited \textcolor{blue}{compared to the background rate}, suggesting that novel combinations of ideas flavoring a body of conventional thought were a feature of impact and that `science follows a nearly universal pattern.'
-%\textcolor{blue}{Should we be more precise here in using 'twice?'  Uzzi et al.
-say twice the background rate whereas this might be construed as twice the rate of other categories which is a much different thing.}
+The authors observed that HCHN articles were twice as likely to be highly cited compared to the background rate, suggesting that novel combinations of ideas flavoring a body of conventional thought were a feature of impact.
 
 Key to Uzzi {\em et al.}, is their random graph model and its underlying assumptions.
-The citation switching algorithm used to generate expected values from random substitutions is designed to preserve the number of publications, the number of references in each publication, and the year of publication of both publications and references.
-However, a critically important feature of the model is that all references published in the same year have equal probability of being cited by any given publication.
-Thus, in particular,  subject matter and  citation count do not impact the probability that the reference will be cited, so that  a reference in quantum physics can be substituted, with equal probability, by a reference in quantum physics, quantum chemistry, classical literature, entomology, or anthropology.
+The citation switching algorithm used to generate expected values by random substitutions of references is designed to preserve the number of publications, the number of references in each publication, and the year of publication of both publications and references.
+Importantly, disciplinary origin does not affect the probability that a reference is selected to replace another one.
+For example, a reference in quantum physics can be substituted, with equal probability, by a reference in quantum physics, quantum chemistry, classical literature, entomology, or anthropology.
 Such substitutions poorly model the disciplinary nature of scientific endeavor and citation behavior~\citep{wallace_lariviere_gingras_2012,moed_measuring_2010,klavans_research_2017,garfield_1979}.
-In addition, under this random model, a reference cited over 100 times in a given year is selected with the same probability as a reference cited only once, which appears inconsistent with the power law or lognormal citation distributions described in the literature~\citep{stringer_statistical_2010,perline_strong_2005}.
+In addition, under this random model, a reference cited many times in a given year is selected with the same probability as a reference cited only once, which appears inconsistent with the power law or lognormal citation distributions described in the literature~\citep{stringer_statistical_2010,perline_strong_2005}.
 Accordingly, model misspecification is likely to arise on account of the simulated values not modeling the empirical data very well.
@@
 A follow-up study by \cite{boyack_vs_uzzi_2014} explored the impact of discipline and journal effects on these definition of conventionality and novelty.
-While their study had some methodological differences in the use of Scopus data rather than WoS data, a smaller dataset, and a $\chi^2$ calculation rather than Monte Carlo simulations to generate expected values of journal pairs, Boyack and Klavans noted strong effects from both disciplines and journals that were not reported by Uzzi et al.
-While they reported the trend that HCHN is more probable in highly cited papers, they observed that ``only 64.4\%  of  243  WoS  subject  categories'' in the Uzzi {\em et al.} study met the criterion of having the highest probability of hit papers in the HCHN category.
+While their study had some methodological differences in the use of Scopus data rather than WoS data, a smaller dataset, and a $\chi^2$ calculation rather than Monte Carlo simulations to generate expected values of journal pairs, Boyack and Klavans noted strong effects from both disciplines and journals.
+While they also reported the trend that HCHN is more probable in highly cited papers, they observed that ``only 64.4\%  of  243  WoS  subject  categories'' in the Uzzi {\em et al.} study met the criterion of having the highest probability of hit papers in the HCHN category.
 Further, they observed that journals vary widely in terms of size and influence and that 20 journals accounted for nearly 15\% of co-citations in their measurements.
@@
 
-Despite different methods used to generate expected values, both of these key preceding studies (\emph{vide supra}) measured co-citation frequencies across the scientific literature (the WoS superset) and normalized them without disciplinary constraints before subsequently analyzing disciplinary subsets.
-In other words, the concerns raised above about misspecification resulting from treating
-all references as equiprobable, independent of discipline, apply to \cite{boyack_vs_uzzi_2014} as well.
- We hypothesized that modifying the normalization to constrain references to be drawn only from the disciplinary citation subnetwork  \textcolor{blue}{(i.e., the ``local network")}  rather than all of WoS
- \textcolor{blue}{ (the ``global network") } would reduce model misspecification.  
- Consequently, we used keyword searches of the scientific literature to construct exemplar citation networks themed around academic disciplines: \emph{applied physics, immunology, and metabolism}.
+Despite different methods used to generate expected values, both of these key preceding studies measured co-citation frequencies across the scientific literature (the WoS or Scopus superset) and normalized them without disciplinary constraints before subsequently analyzing disciplinary subsets.
+We hypothesized instead that modifying the normalization to constrain substitution references to be drawn only from the citation network being studied (the ``local network") rather than all of WoS
+(the ``global network") would reduce model misspecification by limiting substitutions from disciplinarily ectopic references.
+Consequently, we used keyword searches of the scientific literature to construct exemplar citation networks themed around academic disciplines of interest: \emph{applied physics, immunology, and metabolism}.
 Within these disciplinary frameworks, we calculated observed and expected co-citation frequencies using a refined random graph model and an efficient Monte Carlo simulation algorithm.
 
-Our analyses, using multiple techniques, provides substantial evidence that constraining the reference substitutions to the \textcolor{blue}{local network}  reduces model misspecification compared to 
-the \textcolor{blue}{unconstrained model} that \textcolor{blue}{uses the global network, WoS, and treats all substitutions within WoS as equiprobable.} 
-Furthermore, re-analyses of these three semantically-themed
- citation networks  under the improved model reveals strikingly different trends than
- when using all of WoS. 
- For example, while Uzzi {\em et al.}~claimed that highly cited articles are more likely to be both HC and HN than expected and that this trend held across all subdisciplines, we find that these trends vary with the subdiscipline so that no universal trends can be established.
- Specifically, 
- HC remains highly correlated with highly cited articles in the immunology and metabolism datasets but not with applied physics, and HN is highly correlated with highly cited articles in applied physics but not with immunology and metabolism.
+Our analyses, using multiple techniques, provides substantial evidence that a constrained model where reference substitutions are limited to a local (disciplinary) network reduces model misspecification compared to the unconstrained model that uses the global network (WoS).
+Furthermore, re-analyses of these three semantically-themed citation networks  under the improved model reveals strikingly different trends.
+For example, while Uzzi {\em et al.} reported that highly cited articles are more likely to be both HC and HN than expected and that this trend largely held across all disciplines, we find that these trends vary with the discipline and that universal trends are not apparent.
+Specifically,  HC remains highly correlated with highly cited articles in the immunology and metabolism datasets but not with applied physics, and HN is highly correlated with highly cited articles in applied physics but not with immunology and metabolism.
 Thus, disciplinary networks are different from each other, and trends that hold for the full WoS network do not hold for even large subnetworks (such as metabolism).
@@
 \caption{Summary of base WoS Analytical Dataset.
-The number of unique publications of type Article, unique references (UR), total references (TR), and the ratio of total references to unique references increases monotonically with each year indicating that both the number of documents and citation activity increase over time.
-Only publications of type Article with at least two references and references with complete publication data were included.}
+Only publications of type Article with at least two references and references with complete publication data were selected for this data set.
+The number of unique publications of type Article, unique references (ur), total references (tr), and the ratio of total references to unique references increases monotonically with each year indicating that both the number of documents and citation activity increase over time.
+}
 \label{tab:summary_data}
@@
   \hline
-year & Unique Publications & Unique References (UR) & Total References (TR) & TR/UR \\ 
+year & Unique Publications & Unique References (ur) & Total References (tr) & tr/ur \\ 
   \hline
@@
 Pubmed IDs (pmids) returned were matched to WoS IDs (wos\_ids) and used to retrieve relevant articles.
-For the applied physics dataset, we directly searched traditional subject labels in WoS for `applied physics.' While applied physics and immunology represent somewhat small subnetworks (roughly 2-6\% of WoS), metabolism represents approximately 22\% of WoS, making them interesting and meaningful test cases.
+For the applied physics dataset, we directly searched traditional subject labels in WoS for `Physics, Applied' While applied physics and immunology represent somewhat small subnetworks (roughly 2-6\% of WoS), metabolism represents approximately 22\% of WoS, making them interesting and meaningful test cases.
 We also examined publications in the five major research areas in the Web of Science: life sciences \& biomedicine, physical sciences, technology, social sciences, and arts \& humanities,  using the extended subcategory classification of 153 sub-groups to categorize disciplinary composition of cited references in the datasets we studied.
@@
 For citation shuffling, we developed a performant citation switching algorithm, \emph{runtime enhanced permuting citation switcher (repcs)}~\citep{GithubERNIE2019}, that randomly permuted citations grouped by year of publication to switch citations while preserving the year of publication for both articles and references, the number of publications and the number of references in each dataset and the disciplinary composition of the references in each dataset.
-In implementing this approach, our approach differs from the approach in \cite{uzzi_atypical_2013}, in the following ways (i) we sampled citations proportional to their citation frequency (equivalently, from a multiset rather than a set) in order to better reflect citation practice,  (ii) we permitted a substitution to match the original reference in a publication when the random selection process dictated it rather than attempting to enforce that a different reference be substituted, and (iii) we introduced an error correction step to delete any publications that accumulated duplicate references during the substitution process.
+Our approach is different in the following ways (i) we sampled citations proportional to their citation frequency (equivalently from a multiset rather than a set) in order to better reflect citation practice (ii) we permitted a substitution to match the original reference in a publication when the random selection process dictated it rather than attempting to enforce that a different reference be substituted (iii) we introduced an error correction step to delete any publications that accumulated duplicate references during the substitution process.
 As a benchmark, we used the citation switching algorithm of ~\cite{uzzi_atypical_2013}, henceforth referred to  as \emph{umsj} (as also done in ~\cite{boyack_vs_uzzi_2014}), using code kindly provided by the authors.
@@
 We also investigated multiple definitions of hit articles, with hits defined as the 1\%, 2\%, 5\%, and 10\% top-cited articles, and \textcolor{blue}{ 1st and 10th percentiles as thresholds for high novelty}.
-% \textcolor{blue}%{ Also, mention different thresholds, 1st and 10th, for novelty threshold.}
 
@@
 \subsection{Model Misspecification and the Attributes of Disciplinary Context} 
-A source of misspecification in the global model arises from not accounting for disciplinary heterogeneity by treating all references  \textcolor{blue}{within WoS} as equiprobable substituents.
+A source of misspecification arises from not accounting for disciplinary heterogeneity by treating all eligible references within WoS as equiprobable substituents when studying a disciplinary network.
 Under this model, the probability of replacing a reference in one discipline by another reference in a second discipline is identical to the proportion of the articles in WoS that from the second discipline.
-If the global model accurately reflects citation practice, the expected proportion of references within papers published in a given discipline $D$ would be equal to the proportion of references in  $D$, and conversely, the degree to which the proportion deviates from the expected value would reflect the extent of model misspecification.
+If the global model accurately reflects citation practice, the expected proportion of references within papers published in a given discipline $D$ would be approximately equal to the proportion of references in  $D$, and conversely, the degree to which the proportion deviates from the expected value would reflect the extent of model misspecification.
 
-%We assembled three exemplar datasets using keyword searches for the terms `applied physics', `immunology', and `metabolism' (Materials and Methods).
-
-To study the disciplinary composition of references in our custom datasets, we first used the high level WoS classification of five major research areas: life sciences and biomedicine, physical sciences, social sciences, technology, and arts and humanities.
+To study the disciplinary composition of references in our custom datasets, we first used the high level WoS classification of five major research areas: life sciences \& biomedicine, physical sciences, social sciences, technology, and arts \& humanities.
 The two largest of these research areas are physical sciences and life sciences \& biomedicine, which contribute on average approximately 35.1\% and 62.8\%, respectively, of the references in WoS over the three years of interest.
-\textcolor{blue}{While there is some variability over the years, under the unconstrained model, we would expect close to 35\% of the references cited by the publications in any large network  to be drawn from the physical sciences and close to 63\% of the references to be drawn from  life sciences and biomedicine.}
-Yet the empirical data present a very different  story: 79.6\% of the references cited in physical sciences publications are from the physical sciences and 89.9\% of the references cited in life sciences and biomedicine publications are from the life sciences and biomedicine.
+Under the unconstrained model, we would expect close to 35\% of the references cited by the publications in any large network  to be drawn from the physical sciences and close to 63\% of the references to be drawn from  life sciences and biomedicine.
+Yet the empirical data present a very different  story: roughly 80\% of the references cited in physical sciences publications are from the physical sciences and 90\% of the references cited in life sciences \& biomedicine publications are from the life sciences \& biomedicine.
 In other words, the empirical data shows a strong tendency of publications to cite papers that are in the same major research area rather than in some other research area.
@@
 Our observations are in agreement with \cite{wallace_lariviere_gingras_2012} who found that, often, a majority of an article's citations are from the specialty of the article, even though that percentage varied among disciplines in the eight specialties they investigated (from approximately 39\% to 89\% for 2006).
-Furthermore, these findings argue that a discipline-indifferent random graph model would exhibit misspecification (in deviating substantially from the empirical data), and supports the  concern about definitions of  innovation and conventionality that are based on deviation from expected values.
+Furthermore, these findings argue that a discipline-indifferent random graph model would exhibit misspecification in deviating substantially from the empirical data, and supports the  concern about definitions of  innovation and conventionality that are based on deviation from expected values.
 
@@
 
-We also analyzed disciplinary composition at a deeper level of the 153 Subjects in WoS extended classification and examining the consequences of  citation shuffling within a disciplinary set or all of the Web of Science.
-References in publications belonging to these three datasets were classified into 153 subject areas and summarized as a frequency distribution.
+We also analyzed disciplinary composition at a deeper level using all 153 Subjects in the WoS extended classification and examining the consequences of  citation shuffling within a disciplinary set or all of the Web of Science.
+References in publications belonging to these three datasets were summarized as a frequency distribution 153 WoS Subjects as classes.
 A single shuffle of the references in these datasets or all the references in the corresponding WoS year slice was performed, using either the \emph{repcs}  or \emph{umsj} algorithms, after which subject frequencies were computed again.
 The fold change in subject frequencies of references before and after shuffling was calculated for these groups using all 153 subject categories and are summarized as boxplots in Fig \ref{fig:be}.
-For example, the applied physics dataset contained one reference labeled Genetics and Heredity, but after the shuffle (using the WoS background), there were 1496 references labeled Genetics and Heredity.
-Similarly,  the metabolism dataset  contained one reference labeled Philosophy, but after a single shuffle (again using the WoS background), there were   661 occurrences with this label.
+As an example, the applied physics dataset contained one reference labeled Genetics and Heredity, but after the shuffle (using the WoS background), acquired 1496 references labeled Genetics and Heredity.
+Similarly,  the metabolism dataset  contained one reference labeled Philosophy, but after a single shuffle (again using the WoS background), had 661 occurrences with this label.
 The data show convincingly that the disciplinary composition of references in a network is preserved when citation shuffling is constrained to the subnetwork, but is significantly distorted when the WoS superset is used as a source of substitution.
@@
 
- We tested the conjecture that model misspecification would be reduced by constraining the substitutions to  disciplinary subnetworks by examining the Kullback-Leibler (K-L) Divergence~\citep{kullback_information_1951} between observed and predicted citation distributions, restricted to  the set of journals in a given disciplinary subnetwork.
- The results (Table \ref{tab:kld}) confirm this prediction: simulations 
-under the constrained model consistently have a lower K-L divergence compared to simulations under the unconstrained model,  where all references in WoS for a given year are equiprobable. 
-\textcolor{blue}{
+ We then tested the conjecture that model misspecification would be reduced by constraining the substitutions to  disciplinary subnetworks by examining the Kullback-Leibler (K-L) Divergence~\citep{kullback_information_1951} between observed and predicted citation distributions, restricted to  the set of journals in a given disciplinary subnetwork.
+The results (Table \ref{tab:kld}) confirm this prediction: simulations under the constrained model consistently have a lower K-L divergence compared to simulations under the unconstrained model,  where all references in WoS for a given year are equiprobable.
 Furthermore, the K-L divergence for  the unconstrained model (background network all of WoS) is generally twice as large as the K-L divergence for the constrained models (where the background network is the local disciplinary subnetwork), with ratios that range from 1.96 to 2.77,  and are greater than 2.0 in eight out of nine cases.
-These results clearly demonstrate that constraining reference substitutions to the given local disciplinary network better fits the observed data, so that there is reduced model misspecification.}
+These results clearly demonstrate that constraining reference substitutions to the given local disciplinary network better fits the observed data, hence reduced model misspecification.
 
@@
 Novelty in both panels is defined at the 10th percentile of articles' z-score distributions.
-The results for the WoS data set mirror  results from \cite{uzzi_atypical_2013}, where the highest hit rate was for the HNHC category.
-Results for the three disciplinary subnetworks all differ from the overall WoS results: the highest hit rates for the immunology and metabolism datasets  are in the LNHC category and
-%The LNHC category often had the highest hit rate for the immunology dataset for various parameter settings with the HCHN category having the highest hit rate in other cases: metabolism results are similar.
-the highest hit rate for the applied physics datasets are in the HNLC category.  
-%The HNLC category demonstrated the highest hit rate often for applied physics: otherwise the highest hit rate was for HNHC articles.
-\textcolor{blue}{Need numbers for metabolism for the next sentence:}
-The number of data points in the immunology, applied physics, and WoS data sets are 21,917, 18,305, and 476,288, respectively.  
+The results for the WoS data set also show that the highest hit rate is for the HNHC category.
+Results for the three disciplinary subnetworks all differ from the overall WoS results: the highest hit rates for the immunology and metabolism datasets  are in the LNHC category and the highest hit rate for the applied physics datasets are in the HNLC category.
+\textcolor{blue}{Need numbers for metabolism for the next sentence:} The number of data points in the immunology, applied physics, and WoS data sets are 21,917, 18,305, and 476,288, respectively.  
 }
@@
 
-Since the constrained model better fits the observed data, we evaluated the distribution of 
-highly cited articles  (i.e., ``hit articles")
- in the four categories (HCHN, LCHN, HCLN, LCLN), for different
-thresholds for hit articles.
+Since the constrained model better fits the observed data, we evaluated the distribution of highly cited articles  (i.e., ``hit articles") in the four categories (HCHN, LCHN, HCLN, LCLN), for different thresholds for hit articles.
 Figure \ref{fig:Fig2}, Panels (a) and (b), compares hit rates for the four categories among the Immunology, Metabolism, Applied Physics, and WoS datasets for 1995, where the hit rate is defined as the number of hit articles in each category divided by the number of articles in the category.
-The calculation for the hit rates for the WoS dataset (bottom row, Figure \ref{fig:Fig2})
-mirrors Uzzi et al.'s results, whereby the largest hit rates were for the HNHC category, despite our methodological changes in sampling citations in proportion to their frequency. 
+The calculation for the hit rates for the WoS dataset (bottom row, Figure \ref{fig:Fig2}) mirrors Uzzi et al.'s results, whereby the largest hit rates were for the HNHC category, despite our methodological changes in sampling citations in proportion to their frequency.
 However, the trends  for all three  disciplinary subnetworks  are different from those for WoS.
-Specifically, the highest hit rates for the 1995 immunology and metabolism datasets are in the LNHC category for the top 1\% of cited articles (and tied between LNHC and HNHC for the top 10\%),
-and the highest hit rates for the 1995 applied physics datasets are in the 
-HNLC category for both the top 1\% and top 10\% of all cited articles.  
-%Across all years and parameter settings, the highest hit rates in the immunology datasets were sometimes in the LNHC category and sometimes in the HNHC category, and the hit rates for the metabolism datasets reflected this same pattern  (Figure \ref{fig:Fig2}).
- Thus, the category exhibiting the highest hit rate among highly cited papers depends on the
-specific disciplinary network and to some extent on the threshold for being highly cited.
- %was the case with immunology. 
-Furthermore, the categories displaying the greatest hit rate vary 
-to some extent % with parameter settings and 
-with the year \textcolor{blue}{(data not shown)}.
-%The lack of stable results across parameter settings suggests that parameters must be selected judiciously.
+Specifically, the highest hit rates for the 1995 immunology and metabolism datasets are in the LNHC category for the top 1\% of cited articles (and tied between LNHC and HNHC for the top 10\%),and the highest hit rates for the 1995 applied physics datasets are in the HNLC category for both the top 1\% and top 10\% of all cited articles.
+Thus, the category exhibiting the highest hit rate among highly cited papers depends on the specific disciplinary network and to some extent on the threshold for being highly cited.
 
-%\textcolor{blue}{I did not review the next two paragraphs.  I did--JRB}
+Furthermore, the categories displaying the greatest hit rate vary  to some extent with the year \textcolor{blue}{(data not shown)}.
 
@@
 
-We also tested the explanatory power of each framework dimension by classifying articles as %Low Novelty (
-LN %)
- or 
-% High Novelty (
-HN
-%)
- and, separately, as 
-% having Low Conventionality (
-LC
-%) 
-or 
-%High Conventionality (
-HC. 
-%)
+We also tested the explanatory power of each framework dimension by classifying articles as LN or HN and, separately, as LC or HC.
 We tested the null hypothesis that hits are distributed between LN and HN (LC and HC) in proportion to the total number of articles assigned to those categories.
 That null hypothesis was rejected for the WoS data along both dimensions.
-Consistent with the findings in~\cite{uzzi_atypical_2013}, hit articles were overrepresented in the HC category in every instance of WoS data at a $p<0.001$ and also overrepresented in the HN category at a $p<0.001$ in all but two cases: the p-values in those exceptions were $0.002$ and $0.007$.
+Consistent with prior findings, hit articles were overrepresented in the HC category in every instance of WoS data at a $p<0.001$ and also overrepresented in the HN category at a $p<0.001$ in all but two cases: the p-values in those exceptions were $0.002$ and $0.007$.
 Hits in the immunology and metabolism data were overrepresented in the HC category with the same statistical significance as for WoS.
-\textcolor{blue}{The relationship of novelty with hits in the immunology and metabolism data differed dramatically from the WoS, however, with statistically significant findings of hit articles being sometimes overrepresented in the LN category, and sometimes being underrepresented.}
-In applied physics, hit articles were positively related with HN with a statistical significance of at least $p<0.10$ in all 12 parameter sets, and at $p<0.05$ in 10 of 12 cases.
+\textcolor{blue}{The relationship of novelty with hits in the immunology and metabolism data differed dramatically from the WoS, however, with statistically significant findings of hit articles being sometimes overrepresented in the LN category, and sometimes being underrepresented.}  In applied physics, hit articles were positively related with HN with a statistical significance of at least $p<0.10$ in all 12 parameter sets, and at $p<0.05$ in 10 of 12 cases.
 Furthermore, a strong positive relationship was found between LC and hit articles in applied physics in 5 of 12 instances with $p<0.10$.
@@
 In contrast, 2.8\% of z-scores changed signs in the WoS dataset depending on whether Uzzi et al.'s or our random model was used.
-% and x\% z-scores changed signs in the case of the immunology dataset. \textcolor{blue}{Need to insert data for the immunology dataset here also for an apples-to-apples comparison.} 
+
 We conclude that the choice of background datasets is the source of a majority of differences we observed the categories demonstrating the highest hit rates, although our sampling approach, most notably sampling from a multiset so as to reflect the observed frequencies of individual citations as well as their associated journals and disciplines, can also create material differences.
-
-%\textcolor{blue}{I think we should delete the next paragraph.}
-%That fewer z-scores are negative in the WoS dataset relative to the immunology dataset may be directly due to the uniform sampling of references, whereby many resulting journal pairs are never observed in the literature and so the expected frequencies of those observed pairs have lower expected values, thus biasing their z-scores upward.
-In addition, treating citation as a set versus a multiset means that a random model will sample popular citations downward, thus further increasing their z-scores.\emph{need confirmation from Jim here}.
 
@@
 
-%\emph{needs to be expanded}
-
 \textcolor{blue}{
-The fundamental difference between the Uzzi {\em et al.} model and ours is just one parameter--the set of references that can be used as substituents during the substitution process.
-We provided several lines of evidence that showed that changing this one parameter from all of WoS to the local disciplinary subnetwork
-%This study shows strong evidence that constraining the substitution model to the local disciplinary subnetwork 
-reduces model misspecification.
-Furthermore,  using the constrained model (which allows substitutions only within the local subnetwork)  instead of the unconstrained model (which allows substitutions in the entire WoS network) produces different trends in terms of conventionality and novelty, depending on the subnetwork.}
+The principal difference between the two models is a single parameter--the set of references that can be used as substituents during the substitution process.
+We provided several lines of evidence that showed that changing this one parameter from to the local disciplinary subnetwork reduces model misspecification.
+Furthermore,  using the constrained model (which allows substitutions only within the local subnetwork)  instead of the unconstrained model (which allows substitutions in the entire WoS network) produces different trends in terms of conventionality and novelty, depending on the subnetwork.
 In particular, when using the unconstrained model, highly cited papers were most likely to be
@@
 Instead, we find that conventionality flavored with novelty is {\em not} generally a feature of impactful research.
-In particular,  high ``novelty" is not always indicative of impactful research (as reflected in citation counts), as shown by both Immunology and Metabolism having their highest hit rates for low novelty (Figure \ref{fig:Fig2}).
-%\textcolor{blue}{Placement and relevance to be determined.  This paragraph is not yet well written... still working on it.} 
+Further,  high ``novelty" is not always indicative of impactful research (as reflected in citation counts), as shown by both Immunology and Metabolism having their highest hit rates for low novelty (Figure \ref{fig:Fig2}).
 Of relevance, we found the category displaying the highest hit rate to be sensitive to the study parameters, which are the percentage of articles classified as hits and the z-score percentile threshold that delineates LN and HN.
 \textcolor{blue}{(data not shown).} This lack of robustness makes parameter selection of the utmost importance.
-%However, the most appropriate definitions of novelty, conventionality, and hit articles in the framework that we have applied are not clear.
-
-\textcolor{blue}{
-More generally, these results show that the conclusions of universal trends in highly cited papers may be the consequence of using a random model that has a poor fit to the observed data and that is not robust to changes in thresholds for defining high impart articles or high novelty.
-%More research might be done in that regard or, further, in investigating whether the current approach of defining novelty, conventionality, and impactful research sufficiently captures the complexity of the issue at hand.
-However, although  the constrained model reduces model misspecification compared to the unconstrained model,  this does not imply that the constrained model is reasonable nor that trends observed under the constrained model should be considered relevant to understanding scientific practice.
-Indeed, there are significant  challenges in using random models to understand human behavior, of which citation practice is one example.
 }
 
-\textcolor{blue}{
-However, this study does suggest some directions for future work...
-First, we do show that disciplinary behavior differs, so models based on individual disciplines
-}
+More generally, these results show that the trends approaching universality in highly cited papers may be the consequence of using a random model that has a poor fit to the observed data and that is not robust to changes in thresholds for defining high impact or high novelty articles.
+On the other hand, while  the constrained model reduces model misspecification compared to the unconstrained model, this does not imply that the constrained model is reasonable nor that trends observed under the constrained model convincingly explain scientific practice.
+Indeed, there are significant  challenges in using random models to understand human behavior, of which citation practice is one example.
 
@@
 \bibliography{cocit_r}
+
+\end{document}
 
@@
 %\appendix
-
-\end{document}
 

### 2019-06-13 cocit_r.tex
edited various, look for blue

@@
 
-Despite different methods used to generate expected values, both of these key preceding studies measured co-citation frequencies across the scientific literature (the WoS or Scopus superset) and normalized them without disciplinary constraints before subsequently analyzing disciplinary subsets.
+Despite different methods used to generate expected values, both of these key preceding studies measured co-citation frequencies across the scientific literature (using either WoS or Scopus) and normalized them without disciplinary constraints before subsequently analyzing disciplinary subsets.
 We hypothesized instead that modifying the normalization to constrain substitution references to be drawn only from the citation network being studied (the ``local network") rather than all of WoS
@@
 
-For citation shuffling, we developed a performant citation switching algorithm, \emph{runtime enhanced permuting citation switcher (repcs)}~\citep{GithubERNIE2019}, that randomly permuted citations grouped by year of publication to switch citations while preserving the year of publication for both articles and references, the number of publications and the number of references in each dataset and the disciplinary composition of the references in each dataset.
-Our approach is different in the following ways (i) we sampled citations proportional to their citation frequency (equivalently from a multiset rather than a set) in order to better reflect citation practice (ii) we permitted a substitution to match the original reference in a publication when the random selection process dictated it rather than attempting to enforce that a different reference be substituted (iii) we introduced an error correction step to delete any publications that accumulated duplicate references during the substitution process.
-As a benchmark, we used the citation switching algorithm of ~\cite{uzzi_atypical_2013}, henceforth referred to  as \emph{umsj} (as also done in ~\cite{boyack_vs_uzzi_2014}), using code kindly provided by the authors.
+For citation shuffling, we developed a performant citation switching algorithm, \emph{runtime enhanced permuting citation switcher (repcs)}~\citep{GithubERNIE2019}, that randomly permuted citations grouped by year of publication to switch citations while preserving the year of publication for both articles and references, the number of publications and the number of references in each dataset, and the disciplinary composition of the references in each dataset.
+\textcolor{blue}{
+Our approach is different} in the following ways: (i) we sampled citations proportional to their citation frequency (equivalently from a multiset rather than a set) in order to better reflect citation practice,
+(ii) we permitted a substitution to match the original reference in a publication when the random selection process dictated it rather than attempting to enforce that a different reference be substituted, and (iii) we introduced an error correction step to delete any publications that accumulated duplicate references during the substitution process.
+As a benchmark, we used the citation switching algorithm of ~\cite{uzzi_atypical_2013}, henceforth referred to  as \emph{umsj} (as also done in~\cite{boyack_vs_uzzi_2014}), using code kindly provided by the authors.
 A single comparative analysis showed that while 10 simulations of the WoS 1985 dataset (391,860 publications) completed in 2,186 hours using the \emph{umsj} algorithm, it completed in less than one hour using the our implementation of the \emph{repcs}   algorithm on a Spark  cluster.
@@
 \includegraphics[width=0.6\linewidth]{background-effect}     
-\caption{\textcolor{blue}{ Citation shuffling using the local network preserves the disciplinary composition of references within subnetworks, but using the global network does not.}   Publications of type Article belonging to the three disciplinary networks (ap=applied physics, imm=immunology, and  metab=metabolism) were subject to a single shuffle of all their cited references using either the local network (i.e., the cited references in these networks, denoted  bg\_local) or the global network (i.e., references from all articles in WoS, denoted bg\_WoS) as the source of allowed substitutions, where ``bg" indicates the disciplinary subnetwork.
+\caption{Citation shuffling using the local network preserves the disciplinary composition of references within subnetworks, but using the global network does not.
+Publications of type Article belonging to the three disciplinary networks (ap=applied physics, imm=immunology, and  metab=metabolism) were subject to a single shuffle of all their cited references using either the local network (i.e., the cited references in these networks, denoted  bg\_local) or the global network (i.e., references from all articles in WoS, denoted bg\_WoS) as the source of allowed substitutions, where ``bg" indicates the disciplinary subnetwork.
 Citation shuffling was performed using either our algorithm (\emph{repcs}, top row)
@@
 As an example, the applied physics dataset contained one reference labeled Genetics and Heredity, but after the shuffle (using the WoS background), acquired 1496 references labeled Genetics and Heredity.
-Similarly,  the metabolism dataset  contained one reference labeled Philosophy, but after a single shuffle (again using the WoS background), had 661 occurrences with this label.
+Similarly,  the metabolism dataset  contained one reference labeled Philosophy, but after a single shuffle (again using the WoS background) it had 661 occurrences with this label.
 The data show convincingly that the disciplinary composition of references in a network is preserved when citation shuffling is constrained to the subnetwork, but is significantly distorted when the WoS superset is used as a source of substitution.
-A second inference is that the two algorithms, except for running time considerations, have equivalent effects in this experiment.
+A second inference is that the two algorithms, \emph{repcs} and \emph{umsj}, have equivalent effects in this experiment (and so are only distinguishable for running time considerations).
 
@@
 \caption{Model misspecification is reduced by constraining substitutions to the local  disciplinary subnetworks. 
-For the set of journal pairs in common between a disciplinary network and the full WoS dataset, Kullback-Leibler (K-L) divergences
-between empirical and simulated journal pair frequencies were computed for the years 1985, 1995, and 2005 for the three disciplinary datasets (applied physics, immunology, and metabolism) using either the disciplinary network as background or the WoS superset (all\_wos) to generate the null model (Background).
+We computed 
+Kullback-Leibler (K-L) divergences
+between empirical and simulated journal pair frequencies using two different
+background networks (local versus global) for each disciplinary network  (applied physics, immunology, and metabolism)
+for the years 1985, 1995, and 2005.
+% for the three disciplinary datasets (applied physics, immunology, and metabolism) using either the disciplinary network as background or the WoS superset (all\_wos) to generate the null model (Background).
 K-L divergence was calculated using the R seewave package \citep{seewave2008}.  
-The reduction in K-L divergence between simulated and observed data  shows that model misspecification is reduced by  restricting the reference substitutions to the disciplinary subnetwork (our model), as compared to treating all substitutions within WoS as equiprobable.
+For every disciplinary network, there is a smaller K-L divergence between simulated and observed data
+when using the local network (i.e., the disciplinary network) as compared to the global network (all of WoS). 
+Put differently, 
+model misspecification is reduced in the constrained model compared to the unconstrained model.
+%by  restricting the reference substitutions to the disciplinary subnetwork  as compared to treating all substitutions within WoS as equiprobable.
 }
@@
  We then tested the conjecture that model misspecification would be reduced by constraining the substitutions to  disciplinary subnetworks by examining the Kullback-Leibler (K-L) Divergence~\citep{kullback_information_1951} between observed and predicted citation distributions, restricted to  the set of journals in a given disciplinary subnetwork.
-The results (Table \ref{tab:kld}) confirm this prediction: simulations under the constrained model consistently have a lower K-L divergence compared to simulations under the unconstrained model,  where all references in WoS for a given year are equiprobable.
-Furthermore, the K-L divergence for  the unconstrained model (background network all of WoS) is generally twice as large as the K-L divergence for the constrained models (where the background network is the local disciplinary subnetwork), with ratios that range from 1.96 to 2.77,  and are greater than 2.0 in eight out of nine cases.
-These results clearly demonstrate that constraining reference substitutions to the given local disciplinary network better fits the observed data, hence reduced model misspecification.
+The results (Table \ref{tab:kld}) confirm this prediction: simulations under the constrained model 
+(where the background network is the local disciplinary network) consistently have a lower K-L divergence compared to simulations under the unconstrained model  (where the background network is all of WoS).
+Furthermore, the K-L divergence for  the unconstrained model  is generally twice as large as the K-L divergence for the constrained models, with ratios that range from 1.96 to 2.77,  and are greater than 2.0 in eight out of nine cases.
+These results clearly demonstrate that constraining reference substitutions to the given local disciplinary network better fits the observed data, and hence reduces model misspecification.
 
@@
 We described concerns with model misspecification along two general dimensions: the background dataset and sampling methodology for the random graph.
-The differences we found from prior research in terms of which categories demonstrated the highest hit rates were caused both by using disciplinary datasets and our sampling methodology through the article z-score distributions.
+The differences we found from prior research in terms of which categories demonstrated the highest hit rates were caused both by using disciplinary datasets and our sampling methodology, \textit{repcs},  through the article z-score distributions.
 When z-scores are shifted downward using one algorithm versus another, for example, then the former algorithm can result in an increased percentage of HN articles.
-We thought it important to determine the extent to which each of our methodological differences contributed to our observations.
-We found that z-scores of 28.6\% of the journal pairs changed signs with our sampling algorithm, for example, when computed with respect to the WoS dataset versus the immunology dataset.
-In contrast, 2.8\% of z-scores changed signs in the WoS dataset depending on whether Uzzi et al.'s or our random model was used.
+We therefore examined  the extent to which each of our methodological differences contributed to our observations.  
+\textcolor{blue}{We found} 
+that z-scores changed sign more as a consequences  of choice of background network (local network or all of WoS) and much less as a consequence of choice of sampling algorithm
+ ({\textit{umsj} or \textit{repcs}). 
+For example,  on the immunology dataset, 28.6\% of the journal pairs changed signs with our sampling algorithm (\textit{repcs}) as the background network is changed from global (all of WoS) to local, and
+only 2.8\% of z-scores changed signs in the WoS dataset depending on whether 
+\textit{umsj} or \textit{repcs} was used.
 

### 2019-06-13 cocit_r.tex
handing over to JB

@@
 Specifically,  HC remains highly correlated with highly cited articles in the immunology and metabolism datasets but not with applied physics, and HN is highly correlated with highly cited articles in applied physics but not with immunology and metabolism.
-Thus, disciplinary networks are different from each other, and trends that hold for the full WoS network do not hold for even large subnetworks (such as metabolism).
+Thus, disciplinary networks are different from each other, and trends that hold for the full WoS network do not hold for even large networks (such as metabolism).
 Furthermore, we also found that the categories HC, HN, etc.,  demonstrating the highest percentage of highly cited articles are not robust with respect to varying thresholds for high citation counts or for highly novel citation patterns.
-Overall, our study, although limited to three disciplinary subnetworks, suggests that co-citation analysis that inadequately considers disciplinary differences, may not be very useful at detecting universal features of impactful publications.
+Overall, our study, although limited to three disciplinary networks, suggests that co-citation analysis that inadequately considers disciplinary differences, may not be very useful at detecting universal features of impactful publications.
 
@@
 Pubmed IDs (pmids) returned were matched to WoS IDs (wos\_ids) and used to retrieve relevant articles.
-For the applied physics dataset, we directly searched traditional subject labels in WoS for `Physics, Applied' While applied physics and immunology represent somewhat small subnetworks (roughly 2-6\% of WoS), metabolism represents approximately 22\% of WoS, making them interesting and meaningful test cases.
+For the applied physics dataset, we directly searched traditional subject labels in WoS for `Physics, Applied' While applied physics and immunology represent somewhat small networks (roughly 2-6\% of WoS), metabolism represents approximately 22\% of WoS, making them interesting and meaningful test cases.
 We also examined publications in the five major research areas in the Web of Science: life sciences \& biomedicine, physical sciences, technology, social sciences, and arts \& humanities,  using the extended subcategory classification of 153 sub-groups to categorize disciplinary composition of cited references in the datasets we studied.
@@
 \includegraphics[width=0.6\linewidth]{background-effect}     
-\caption{Citation shuffling using the local network preserves the disciplinary composition of references within subnetworks, but using the global network does not.
-Publications of type Article belonging to the three disciplinary networks (ap=applied physics, imm=immunology, and  metab=metabolism) were subject to a single shuffle of all their cited references using either the local network (i.e., the cited references in these networks, denoted  bg\_local) or the global network (i.e., references from all articles in WoS, denoted bg\_WoS) as the source of allowed substitutions, where ``bg" indicates the disciplinary subnetwork.
+\caption{Citation shuffling using the local network preserves the disciplinary composition of references within networks, but using the global network does not.
+Publications of type Article belonging to the three disciplinary networks (ap=applied physics, imm=immunology, and  metab=metabolism) were subject to a single shuffle of all their cited references using either the local network (i.e., the cited references in these networks, denoted  bg\_local) or the global network (i.e., references from all articles in WoS, denoted bg\_WoS) as the source of allowed substitutions, where ``bg" indicates the disciplinary network.
 Citation shuffling was performed using either our algorithm (\emph{repcs}, top row)
@@
 Similarly,  the metabolism dataset  contained one reference labeled Philosophy, but after a single shuffle (again using the WoS background) it had 661 occurrences with this label.
-The data show convincingly that the disciplinary composition of references in a network is preserved when citation shuffling is constrained to the subnetwork, but is significantly distorted when the WoS superset is used as a source of substitution.
+The data show convincingly that the disciplinary composition of references in a network is preserved when citation shuffling is constrained to the network, but is significantly distorted when the WoS superset is used as a source of substitution.
 A second inference is that the two algorithms, \emph{repcs} and \emph{umsj}, have equivalent effects in this experiment (and so are only distinguishable for running time considerations).
@@
 \begin{table}[ht]
-\caption{Model misspecification is reduced by constraining substitutions to the local  disciplinary subnetworks. 
+\caption{Model misspecification is reduced by constraining substitutions to the local  disciplinary networks. 
 We computed 
@@
 model misspecification is reduced in the constrained model compared to the unconstrained model.
-%by  restricting the reference substitutions to the disciplinary subnetwork  as compared to treating all substitutions within WoS as equiprobable.
+%by  restricting the reference substitutions to the disciplinary network  as compared to treating all substitutions within WoS as equiprobable.
 }
@@
   \hline
- appl\_physics & 1985 & local & 1.21 &  \\ 
+Applied Physics & 1985 & local & 1.21 &  \\ 
   & 1985 & global & 2.37 & 1.96 \\ 
@@
     \hline
-  immunology & 1985 & local & 0.75 &  \\ 
+Immunology & 1985 & local & 0.75 &  \\ 
   & 1985 & global  & 1.68 & 2.24 \\ 
@@
     \hline
- metabolism & 1985 & local & 1.11 &  \\ 
+Metabolism & 1985 & local & 1.11 &  \\ 
    & 1985 & global  & 2.24 & 2.02 \\ 
@@
 
- We then tested the conjecture that model misspecification would be reduced by constraining the substitutions to  disciplinary subnetworks by examining the Kullback-Leibler (K-L) Divergence~\citep{kullback_information_1951} between observed and predicted citation distributions, restricted to  the set of journals in a given disciplinary subnetwork.
+ We then tested the conjecture that model misspecification would be reduced by constraining the substitutions to  disciplinary networks by examining the Kullback-Leibler (K-L) Divergence~\citep{kullback_information_1951} between observed and predicted citation distributions, restricted to  the set of journals in a given disciplinary network.
 The results (Table \ref{tab:kld}) confirm this prediction: simulations under the constrained model 
@@
 The results for the WoS data set also show that the highest hit rate is for the HNHC category.
-Results for the three disciplinary subnetworks all differ from the overall WoS results: the highest hit rates for the immunology and metabolism datasets  are in the LNHC category and the highest hit rate for the applied physics datasets are in the HNLC category.
+Results for the three disciplinary networks all differ from the overall WoS results: the highest hit rates for the immunology and metabolism datasets  are in the LNHC category and the highest hit rate for the applied physics datasets are in the HNLC category.
 \textcolor{blue}{Need numbers for metabolism for the next sentence:} The number of data points in the immunology, applied physics, and WoS data sets are 21,917, 18,305, and 476,288, respectively.  
@@
 The calculation for the hit rates for the WoS dataset (bottom row, Figure \ref{fig:Fig2}) mirrors Uzzi et al.'s results, whereby the largest hit rates were for the HNHC category, despite our methodological changes in sampling citations in proportion to their frequency.
-However, the trends  for all three  disciplinary subnetworks  are different from those for WoS.
-Specifically, the highest hit rates for the 1995 immunology and metabolism datasets are in the LNHC category for the top 1\% of cited articles (and tied between LNHC and HNHC for the top 10\%),and the highest hit rates for the 1995 applied physics datasets are in the HNLC category for both the top 1\% and top 10\% of all cited articles.
+However, the trends  for all three  disciplinary networks  are different from those for WoS.Specifically, the highest hit rates for the 1995 immunology and metabolism datasets are in the LNHC category for the top 1\% of cited articles (and tied between LNHC and HNHC for the top 10\%),and the highest hit rates for the 1995 applied physics datasets are in the HNLC category for both the top 1\% and top 10\% of all cited articles.
 Thus, the category exhibiting the highest hit rate among highly cited papers depends on the specific disciplinary network and to some extent on the threshold for being highly cited.
@@
 We therefore examined  the extent to which each of our methodological differences contributed to our observations.  
-\textcolor{blue}{We found} 
-that z-scores changed sign more as a consequences  of choice of background network (local network or all of WoS) and much less as a consequence of choice of sampling algorithm
+We found that z-scores changed sign more as a consequence of background network (local network or all of WoS) and much less as a consequence of sampling algorithm
  ({\textit{umsj} or \textit{repcs}). 
@@
 
-\textcolor{blue}{
 The principal difference between the two models is a single parameter--the set of references that can be used as substituents during the substitution process.
-We provided several lines of evidence that showed that changing this one parameter from to the local disciplinary subnetwork reduces model misspecification.
-Furthermore,  using the constrained model (which allows substitutions only within the local subnetwork)  instead of the unconstrained model (which allows substitutions in the entire WoS network) produces different trends in terms of conventionality and novelty, depending on the subnetwork.
+We provided several lines of evidence that showed that changing this one parameter from to the local disciplinary network reduces model misspecification.
+Furthermore,  using the constrained model (which allows substitutions only within the local network)  instead of the unconstrained model (which allows substitutions in the entire WoS network) produces different trends in terms of conventionality and novelty, depending on the network.
 In particular, when using the unconstrained model, highly cited papers were most likely to be
@@
 Of relevance, we found the category displaying the highest hit rate to be sensitive to the study parameters, which are the percentage of articles classified as hits and the z-score percentile threshold that delineates LN and HN.
-\textcolor{blue}{(data not shown).} This lack of robustness makes parameter selection of the utmost importance.
-}
+\textcolor{blue}{(data not shown).}
 
-More generally, these results show that the trends approaching universality in highly cited papers may be the consequence of using a random model that has a poor fit to the observed data and that is not robust to changes in thresholds for defining high impact or high novelty articles.
+More generally, these results show that the trends approaching universality in highly cited papers are not robust to changes in thresholds for defining high impact or high novelty articles and may be the consequence of using a random model that has a poor fit to the observed data.
 On the other hand, while  the constrained model reduces model misspecification compared to the unconstrained model, this does not imply that the constrained model is reasonable nor that trends observed under the constrained model convincingly explain scientific practice.
 Indeed, there are significant  challenges in using random models to understand human behavior, of which citation practice is one example.
+
+In terms of further work, evaluation in context~\citep{hicks_bibliometrics:_2015} and increased consideration of the disciplinary nature of the scientific enterprise is likely to result in improved models that yield further insight.
 

### 2019-06-14 cocit_r.tex
Minor revisions

@@
 
-Thus, HCLN would denote high conventionality (HC) and low novelty (LN), with all four combinations being possible.
+Thus, HCLN would denote high conventionality (HC) and low novelty (LN), with all four combinations of LC and HC with LN and HN being possible.
 The authors observed that HCHN articles were twice as likely to be highly cited compared to the background rate, suggesting that novel combinations of ideas flavoring a body of conventional thought were a feature of impact.
@@
 In addition, under this random model, a reference cited many times in a given year is selected with the same probability as a reference cited only once, which appears inconsistent with the power law or lognormal citation distributions described in the literature~\citep{stringer_statistical_2010,perline_strong_2005}.
-Accordingly, model misspecification is likely to arise on account of the simulated values not modeling the empirical data very well.
+Accordingly, model misspecification is likely to arise on account of the simulated values not reflecting the empirical data very well.
 
-A follow-up study by \cite{boyack_vs_uzzi_2014} explored the impact of discipline and journal effects on these definition of conventionality and novelty.
+A follow-up study by \cite{boyack_vs_uzzi_2014} explored the impact of discipline and journal effects on these definitions of conventionality and novelty.
 While their study had some methodological differences in the use of Scopus data rather than WoS data, a smaller dataset, and a $\chi^2$ calculation rather than Monte Carlo simulations to generate expected values of journal pairs, Boyack and Klavans noted strong effects from both disciplines and journals.
@@
 Furthermore, re-analyses of these three semantically-themed citation networks  under the improved model reveals strikingly different trends.
-For example, while Uzzi {\em et al.} reported that highly cited articles are more likely to be both HC and HN than expected and that this trend largely held across all disciplines, we find that these trends vary with the discipline and that universal trends are not apparent.
+For example, while Uzzi {\em et al.} reported that highly cited articles are more likely than expected to be both HC and HN and that this trend largely held across all disciplines, we find that these trends vary with the discipline and that universal trends are not apparent.
 Specifically,  HC remains highly correlated with highly cited articles in the immunology and metabolism datasets but not with applied physics, and HN is highly correlated with highly cited articles in applied physics but not with immunology and metabolism.
@@
   \hline
-year & Unique Publications & Unique References (ur) & Total References (tr) & tr/ur \\ 
+Year & Unique Publications & Unique References (ur) & Total References (tr) & tr/ur \\ 
   \hline
@@
 For the applied physics dataset, we directly searched traditional subject labels in WoS for `Physics, Applied' While applied physics and immunology represent somewhat small networks (roughly 2-6\% of WoS), metabolism represents approximately 22\% of WoS, making them interesting and meaningful test cases.
-We also examined publications in the five major research areas in the Web of Science: life sciences \& biomedicine, physical sciences, technology, social sciences, and arts \& humanities,  using the extended subcategory classification of 153 sub-groups to categorize disciplinary composition of cited references in the datasets we studied.
+We also examined publications in the five major research areas in the WoS: life sciences \& biomedicine, physical sciences, technology, social sciences, and arts \& humanities,  using the extended subcategory classification of 153 sub-groups to categorize disciplinary composition of cited references in the datasets we studied.
 \vspace{-2 mm}
@@
 For citation shuffling, we developed a performant citation switching algorithm, \emph{runtime enhanced permuting citation switcher (repcs)}~\citep{GithubERNIE2019}, that randomly permuted citations grouped by year of publication to switch citations while preserving the year of publication for both articles and references, the number of publications and the number of references in each dataset, and the disciplinary composition of the references in each dataset.
-\textcolor{blue}{
-Our approach is different} in the following ways: (i) we sampled citations proportional to their citation frequency (equivalently from a multiset rather than a set) in order to better reflect citation practice,
+Our approach is different than previous studies in these ways: (i) we sampled citations in proportion to their citation frequency (equivalently from a multiset rather than a set) in order to better reflect citation practice,
 (ii) we permitted a substitution to match the original reference in a publication when the random selection process dictated it rather than attempting to enforce that a different reference be substituted, and (iii) we introduced an error correction step to delete any publications that accumulated duplicate references during the substitution process.
 As a benchmark, we used the citation switching algorithm of ~\cite{uzzi_atypical_2013}, henceforth referred to  as \emph{umsj} (as also done in~\cite{boyack_vs_uzzi_2014}), using code kindly provided by the authors.
-A single comparative analysis showed that while 10 simulations of the WoS 1985 dataset (391,860 publications) completed in 2,186 hours using the \emph{umsj} algorithm, it completed in less than one hour using the our implementation of the \emph{repcs}   algorithm on a Spark  cluster.
+A single comparative analysis showed that while 10 simulations of the WoS 1985 dataset (391,860 publications) completed in 2,186 hours using the \emph{umsj} algorithm, it completed in less than one hour using our implementation of the \emph{repcs}   algorithm on a Spark  cluster.
 We also tested \emph{repcs}  under comparable conditions to \emph{umsj} and estimated a runtime advantage of at least two orders of magnitude.

### 2019-06-14 cocit_r.tex
Minor revisions

@@
 As a result of these calculations, each publication becomes associated with a set of z-scores corresponding to the journal pairs derived from pairwise combinations of its cited references.
-Positional statistics of z-scores were calculated for each publication, which was then labeled according to conventionality and novelty: (i) HC if the median z-score exceeded the median of median z-scores for all publications and LC if the median z-score was equal to or less than the median of median z-scores for all publications, and (ii) HN if the tenth percentile of z-scores for a publication was less than zero, and LN if the tenth percentile of z-scores for a publication was greater than zero.
+Positional statistics of z-scores were calculated for each publication, which was then labeled according to conventionality and novelty: (i) HC if the median z-score exceeded the median of median z-scores for all publications and LC otherwise
+%if the median z-score was equal to or less than the median of median z-scores for all publications
+, and (ii) HN if the tenth percentile of z-scores for a publication was less than zero, and LN otherwise. 
+%if the tenth percentile of z-scores for a publication was greater than zero. 
+We also analyzed the effect of defining high novelty using the first percentile of z-scores.
 
 To consider the relationship between citation impact, conventionality, and novelty we calculated percentiles for the number of accumulated citations in the first 8 years since publication for each article we studied and stratified.
-We also investigated multiple definitions of hit articles, with hits defined as the 1\%, 2\%, 5\%, and 10\% top-cited articles, and \textcolor{blue}{ 1st and 10th percentiles as thresholds for high novelty}.
+We investigated multiple definitions of hit articles, with hits defined as the 1\%, 2\%, 5\%, and 10\% top-cited articles.
 

### 2019-06-14 cocit_r.tex
Minor revisions

@@
 A source of misspecification arises from not accounting for disciplinary heterogeneity by treating all eligible references within WoS as equiprobable substituents when studying a disciplinary network.
-Under this model, the probability of replacing a reference in one discipline by another reference in a second discipline is identical to the proportion of the articles in WoS that from the second discipline.
+Under this model, the probability of replacing a reference in one discipline by another reference in a second discipline is identical to the proportion of the articles in WoS from the second discipline.
 If the global model accurately reflects citation practice, the expected proportion of references within papers published in a given discipline $D$ would be approximately equal to the proportion of references in  $D$, and conversely, the degree to which the proportion deviates from the expected value would reflect the extent of model misspecification.

### 2019-06-14 cocit_r.tex
Minor revisions

@@
 \begin{tabular}{ccc}
-\includegraphics[width=1.5in]{Fig2H01N10.pdf} & \includegraphics[width=1.5in]{Fig2H10N10.pdf} \\
-(a) Top 1\% of cited articles & (b) Top 10\% of cited articles \\
+\includegraphics[width=1.5in]{Fig2H01N10.pdf} & \includegraphics[width=0.5in]{blank.pdf} & \includegraphics[width=1.5in]{Fig2H10N10.pdf} \\
+(a) Top 1\% of cited articles & & (b) Top 10\% of cited articles \\
 \end{tabular}
@@
 Further,  high ``novelty" is not always indicative of impactful research (as reflected in citation counts), as shown by both Immunology and Metabolism having their highest hit rates for low novelty (Figure \ref{fig:Fig2}).
-Of relevance, we found the category displaying the highest hit rate to be sensitive to the study parameters, which are the percentage of articles classified as hits and the z-score percentile threshold that delineates LN and HN.
+Of relevance, we found the category displaying the highest hit rate to be sensitive to the study parameters, which include the percentage of articles classified as hits, the z-score percentile threshold that delineates LN and HN, and the publication year.
 \textcolor{blue}{(data not shown).}

### 2019-06-14 cocit_r.tex
Minor revisions

@@
 A source of misspecification arises from not accounting for disciplinary heterogeneity by treating all eligible references within WoS as equiprobable substituents when studying a disciplinary network.
-Under this model, the probability of replacing a reference in one discipline by another reference in a second discipline is identical to the proportion of the articles in WoS from the second discipline.
+Under this model~\citep{Uzzi}, the probability of selecting a reference from a discipline is identical to the proportion of the articles in WoS in that discipline for a given year.
 If the global model accurately reflects citation practice, the expected proportion of references within papers published in a given discipline $D$ would be approximately equal to the proportion of references in  $D$, and conversely, the degree to which the proportion deviates from the expected value would reflect the extent of model misspecification.

### 2019-06-14 cocit_r.tex
Minor revisions

@@
 A source of misspecification arises from not accounting for disciplinary heterogeneity by treating all eligible references within WoS as equiprobable substituents when studying a disciplinary network.
-Under this model~\citep{Uzzi}, the probability of selecting a reference from a discipline is identical to the proportion of the articles in WoS in that discipline for a given year.
+Under this model~\citep{uzzi_atypical_2013}, the probability of selecting a reference from a discipline is identical to the proportion of the articles in WoS in that discipline for a given year.
 If the global model accurately reflects citation practice, the expected proportion of references within papers published in a given discipline $D$ would be approximately equal to the proportion of references in  $D$, and conversely, the degree to which the proportion deviates from the expected value would reflect the extent of model misspecification.

### 2019-06-14 cocit_r.tex
minor revisions

@@
 We also analyzed disciplinary composition at a deeper level using all 153 Subjects in the WoS extended classification and examining the consequences of  citation shuffling within a disciplinary set or all of the Web of Science.
-References in publications belonging to these three datasets were summarized as a frequency distribution 153 WoS Subjects as classes.
-A single shuffle of the references in these datasets or all the references in the corresponding WoS year slice was performed, using either the \emph{repcs}  or \emph{umsj} algorithms, after which subject frequencies were computed again.
-The fold change in subject frequencies of references before and after shuffling was calculated for these groups using all 153 subject categories and are summarized as boxplots in Fig \ref{fig:be}.
+References in publications belonging to these three datasets were summarized as a \textcolor{blue}{frequency distribution of 153 WoS Subjects as classes}.
+A single shuffle of the references in the disciplinary datasets and in the corresponding WoS year slice was performed, using either the \emph{repcs}  or \emph{umsj} algorithms, after which subject frequencies were computed again.
+The fold change in subject frequencies of references before and after shuffling was calculated for these groups using all 153 subject categories and summarized in the box plots in Fig \ref{fig:be}.
 As an example, the applied physics dataset contained one reference labeled Genetics and Heredity, but after the shuffle (using the WoS background), acquired 1496 references labeled Genetics and Heredity.
 Similarly,  the metabolism dataset  contained one reference labeled Philosophy, but after a single shuffle (again using the WoS background) it had 661 occurrences with this label.
-The data show convincingly that the disciplinary composition of references in a network is preserved when citation shuffling is constrained to the network, but is significantly distorted when the WoS superset is used as a source of substitution.
+The data show convincingly that a publication's disciplinary composition of references in a network is preserved when citation shuffling is constrained to the network, but is significantly distorted when the WoS superset is used as a source of substitution.
 A second inference is that the two algorithms, \emph{repcs} and \emph{umsj}, have equivalent effects in this experiment (and so are only distinguishable for running time considerations).

### 2019-06-14 cocit_r.tex
minor revisions

@@
 The calculation for the hit rates for the WoS dataset (bottom row, Figure \ref{fig:Fig2}) mirrors Uzzi et al.'s results, whereby the largest hit rates were for the HNHC category, despite our methodological changes in sampling citations in proportion to their frequency.
-However, the trends  for all three  disciplinary networks  are different from those for WoS.Specifically, the highest hit rates for the 1995 immunology and metabolism datasets are in the LNHC category for the top 1\% of cited articles (and tied between LNHC and HNHC for the top 10\%),and the highest hit rates for the 1995 applied physics datasets are in the HNLC category for both the top 1\% and top 10\% of all cited articles.
+However, the trends  for all three  disciplinary networks  are different from those for WoS.
+Specifically, the highest hit rates for the 1995 immunology and metabolism datasets are in the LNHC category for the top 1\% of cited articles (and tied between LNHC and HNHC for the top 10\%), and the highest hit rates for the 1995 applied physics datasets are in the HNLC category for both the top 1\% and top 10\% of all cited articles.
 Thus, the category exhibiting the highest hit rate among highly cited papers depends on the specific disciplinary network and to some extent on the threshold for being highly cited.
 
-Furthermore, the categories displaying the greatest hit rate vary  to some extent with the year \textcolor{blue}{(data not shown)}.
+Furthermore, the categories displaying the greatest hit rate vary to some extent with the year.
+For example, when the 1\% top-cited articles are deemed to be hits, the category with the highest hit rate in applied physics for 1985 and 1995 is HNLC, although the hit rate for HNHC is slightly greater than for HNLC in 2005 (1.3\% versus 1.1\%).
 
@@
 The null hypothesis was rejected with $p<0.001$ for all valid tests for all parameter settings, all datasets, and all years: hypotheses tests were valid in 73 of 96 instances.
-We conclude that it is likely that the distribution of hits among categories is not uniform and that, instead, hit rates vary among the categories in all datasets.
+We conclude that it is likely that the distribution of hits among categories is not uniform and that, instead, hit rates vary among the categories in all disciplinary datasets.
 

### 2019-06-14 cocit_r.tex
minor revisions

@@
 Furthermore, the categories displaying the greatest hit rate vary to some extent with the year.
-For example, when the 1\% top-cited articles are deemed to be hits, the category with the highest hit rate in applied physics for 1985 and 1995 is HNLC, although the hit rate for HNHC is slightly greater than for HNLC in 2005 (1.3\% versus 1.1\%).
+For example, when the 10\% top-cited articles are deemed to be hits and novelty is defined at the 10th percentile of z-scores, the category with the highest hit rate in applied physics for 1995 is in HNLC (12.3\% versus 10.9\% for HNHC), while the hit rate for HNHC is greater than for HNLC in 1985 and 2005 (13.2\% versus 10.9\%, and 11.4\% versus 10.7\%, respectively).
 
@@
 Hits in the immunology and metabolism data were overrepresented in the HC category with the same statistical significance as for WoS.
-\textcolor{blue}{The relationship of novelty with hits in the immunology and metabolism data differed dramatically from the WoS, however, with statistically significant findings of hit articles being sometimes overrepresented in the LN category, and sometimes being underrepresented.}  In applied physics, hit articles were positively related with HN with a statistical significance of at least $p<0.10$ in all 12 parameter sets, and at $p<0.05$ in 10 of 12 cases.
+\textcolor{blue}{The relationship of novelty with hits in the immunology and metabolism dataset differed dramatically from the WoS, however, with statistically significant findings of hit articles being sometimes overrepresented in the LN category, and sometimes being underrepresented.}  In applied physics, hit articles were positively related with HN with a statistical significance of at least $p<0.10$ in all 12 parameter sets, and at $p<0.05$ in 10 of 12 cases.
 Furthermore, a strong positive relationship was found between LC and hit articles in applied physics in 5 of 12 instances with $p<0.10$.

### 2019-06-14 cocit_r.tex
minor changes

@@
 
-Thus, HCLN would denote high conventionality (HC) and low novelty (LN), with all four combinations of LC and HC with LN and HN being possible.
-The authors observed that HCHN articles were twice as likely to be highly cited compared to the background rate, suggesting that novel combinations of ideas flavoring a body of conventional thought were a feature of impact.
+Thus, LNHC would denote low novelty (LN) and high conventionality (HC), with all four combinations of LN and HN with LC and HC being possible.
+The authors observed that HNHC articles were twice as likely to be highly cited compared to the background rate, suggesting that novel combinations of ideas flavoring a body of conventional thought were a feature of impact.
 
@@
 While their study had some methodological differences in the use of Scopus data rather than WoS data, a smaller dataset, and a $\chi^2$ calculation rather than Monte Carlo simulations to generate expected values of journal pairs, Boyack and Klavans noted strong effects from both disciplines and journals.
-While they also reported the trend that HCHN is more probable in highly cited papers, they observed that ``only 64.4\%  of  243  WoS  subject  categories'' in the Uzzi {\em et al.} study met the criterion of having the highest probability of hit papers in the HCHN category.
+While they also reported the trend that HNHC is more probable in highly cited papers, they observed that ``only 64.4\%  of  243  WoS  subject  categories'' in the Uzzi {\em et al.} study met the criterion of having the highest probability of hit papers in the HNHC category.
 Further, they observed that journals vary widely in terms of size and influence and that 20 journals accounted for nearly 15\% of co-citations in their measurements.
@@
 Hits in the immunology and metabolism data were overrepresented in the HC category with the same statistical significance as for WoS.
-\textcolor{blue}{The relationship of novelty with hits in the immunology and metabolism dataset differed dramatically from the WoS, however, with statistically significant findings of hit articles being sometimes overrepresented in the LN category, and sometimes being underrepresented.}  In applied physics, hit articles were positively related with HN with a statistical significance of at least $p<0.10$ in all 12 parameter sets, and at $p<0.05$ in 10 of 12 cases.
-Furthermore, a strong positive relationship was found between LC and hit articles in applied physics in 5 of 12 instances with $p<0.10$.
+The relationship of novelty with hits in the immunology and metabolism dataset differed dramatically from the WoS, however, with statistically significant findings of hit articles being sometimes overrepresented in the LN category, and sometimes being underrepresented.
+Consistent with the WoS, hit articles in applied physics were positively related with HN with a statistical significance of at least $p<0.10$ in all 12 parameter sets, and at $p<0.05$ in 10 of 12 cases.
+To the contrary, a strong positive relationship was found between LC and hit articles in applied physics in 5 of 12 instances with $p<0.10$.
 These results suggest that (1) both conventionality and novelty are strongly related to hits in the WoS, (2) the conventionality dimension is strongly related with hits in immunology and metabolism and novelty is not, and (3) novelty is more strongly related with hits in applied physics than is conventionality.
@@
 
-We conclude that the choice of background datasets is the source of a majority of differences we observed the categories demonstrating the highest hit rates, although our sampling approach, most notably sampling from a multiset so as to reflect the observed frequencies of individual citations as well as their associated journals and disciplines, can also create material differences.
+We conclude that the choice of background datasets is the source of a majority of differences we observed in the categories demonstrating the highest hit rates, although our sampling approach, most notably sampling from a multiset so as to reflect the observed frequencies of individual citations as well as their associated journals and disciplines, can also create material differences.
 

### 2019-06-14 cocit_r.tex
minor changes
Minor revisions and addition of new citation in bibtek file

@@
 We also analyzed disciplinary composition at a deeper level using all 153 Subjects in the WoS extended classification and examining the consequences of  citation shuffling within a disciplinary set or all of the Web of Science.
-References in publications belonging to these three datasets were summarized as a \textcolor{blue}{frequency distribution of 153 WoS Subjects as classes}.
+References in publications belonging to these three datasets were summarized as a frequency distribution of 153 WoS Subjects as classes.
 A single shuffle of the references in the disciplinary datasets and in the corresponding WoS year slice was performed, using either the \emph{repcs}  or \emph{umsj} algorithms, after which subject frequencies were computed again.
@@
 The principal difference between the two models is a single parameter--the set of references that can be used as substituents during the substitution process.
-We provided several lines of evidence that showed that changing this one parameter from to the local disciplinary network reduces model misspecification.
+We provided several lines of evidence that showed that changing this one parameter from \textcolor{blue}{a global network} to the local disciplinary network reduces model misspecification.
 Furthermore,  using the constrained model (which allows substitutions only within the local network)  instead of the unconstrained model (which allows substitutions in the entire WoS network) produces different trends in terms of conventionality and novelty, depending on the network.
@@
 Of relevance, we found the category displaying the highest hit rate to be sensitive to the study parameters, which include the percentage of articles classified as hits, the z-score percentile threshold that delineates LN and HN, and the publication year.
-\textcolor{blue}{(data not shown).}
 
@@
 Indeed, there are significant  challenges in using random models to understand human behavior, of which citation practice is one example.
+
+While our work has shown that the use of local networks defines a benchmark more consistent with research citation patterns, further work might explore how the alignment of benchmarks with practice might be further improved.
+These can be viewed, and possibly implemented as further constraints on the random assignment of citations to publications.
+For example, one might take into consideration the proximity of possible citations as defined in a co-author network~\citep{wallace_lariviere_gingras_2012} when defining probabilities for citation substitutions.
+Other foundations for benchmarks might include consideration of the possibility that citation patterns are partly due to communications within and between fields, as well a reflection of and exertion of intellectual influence~\citep{stigler_1994}.
 

### 2019-06-14 cocit_r.tex
minor

@@
 The principal difference between the two models is a single parameter--the set of references that can be used as substituents during the substitution process.
-We provided several lines of evidence that showed that changing this one parameter from \textcolor{blue}{a global network} to the local disciplinary network reduces model misspecification.
+We provided several lines of evidence that showed that changing this one parameter from a global network to the local disciplinary network reduces model misspecification.
 Furthermore,  using the constrained model (which allows substitutions only within the local network)  instead of the unconstrained model (which allows substitutions in the entire WoS network) produces different trends in terms of conventionality and novelty, depending on the network.

### 2019-06-14 cocit_r.tex
a very small number of edits, all minor

@@
 
-Key to Uzzi {\em et al.}, is their random graph model and its underlying assumptions.
+Key to Uzzi {\em et al.}~is their random graph model and its underlying assumptions.
 The citation switching algorithm used to generate expected values by random substitutions of references is designed to preserve the number of publications, the number of references in each publication, and the year of publication of both publications and references.
@@
 Furthermore, re-analyses of these three semantically-themed citation networks  under the improved model reveals strikingly different trends.
-For example, while Uzzi {\em et al.} reported that highly cited articles are more likely than expected to be both HC and HN and that this trend largely held across all disciplines, we find that these trends vary with the discipline and that universal trends are not apparent.
+For example, while Uzzi {\em et al.} reported that highly cited articles are more likely than expected to be both HC and HN and that this trend largely held across all disciplines, we find that these trends vary with the discipline so that universal trends are not apparent.
 Specifically,  HC remains highly correlated with highly cited articles in the immunology and metabolism datasets but not with applied physics, and HN is highly correlated with highly cited articles in applied physics but not with immunology and metabolism.
 Thus, disciplinary networks are different from each other, and trends that hold for the full WoS network do not hold for even large networks (such as metabolism).
-Furthermore, we also found that the categories HC, HN, etc.,  demonstrating the highest percentage of highly cited articles are not robust with respect to varying thresholds for high citation counts or for highly novel citation patterns.
-Overall, our study, although limited to three disciplinary networks, suggests that co-citation analysis that inadequately considers disciplinary differences, may not be very useful at detecting universal features of impactful publications.
+Furthermore, we also found that the categories  demonstrating the highest percentage of highly cited articles (e.g., HC, HN, etc.) are not robust with respect to varying thresholds for high citation counts or for highly novel citation patterns.
+Overall, our study, although limited to three disciplinary networks, suggests that co-citation analysis that inadequately considers disciplinary differences may not be very useful at detecting universal features of impactful publications.
 
@@
 Pubmed IDs (pmids) returned were matched to WoS IDs (wos\_ids) and used to retrieve relevant articles.
-For the applied physics dataset, we directly searched traditional subject labels in WoS for `Physics, Applied' While applied physics and immunology represent somewhat small networks (roughly 2-6\% of WoS), metabolism represents approximately 22\% of WoS, making them interesting and meaningful test cases.
+For the applied physics dataset, we directly searched traditional subject labels in WoS for `Physics, Applied'.
+ While applied physics and immunology represent somewhat small networks (roughly 2-6\% of WoS), metabolism represents approximately 22\% of WoS, making them interesting and meaningful test cases.
 We also examined publications in the five major research areas in the WoS: life sciences \& biomedicine, physical sciences, technology, social sciences, and arts \& humanities,  using the extended subcategory classification of 153 sub-groups to categorize disciplinary composition of cited references in the datasets we studied.
@@
 For citation shuffling, we developed a performant citation switching algorithm, \emph{runtime enhanced permuting citation switcher (repcs)}~\citep{GithubERNIE2019}, that randomly permuted citations grouped by year of publication to switch citations while preserving the year of publication for both articles and references, the number of publications and the number of references in each dataset, and the disciplinary composition of the references in each dataset.
-Our approach is different than previous studies in these ways: (i) we sampled citations in proportion to their citation frequency (equivalently from a multiset rather than a set) in order to better reflect citation practice,
+Our approach is different from previous studies in these ways: (i) we sampled citations in proportion to their citation frequency (equivalently from a multiset rather than a set) in order to better reflect citation practice,
 (ii) we permitted a substitution to match the original reference in a publication when the random selection process dictated it rather than attempting to enforce that a different reference be substituted, and (iii) we introduced an error correction step to delete any publications that accumulated duplicate references during the substitution process.
@@
 
-We conclude that the choice of background datasets is the source of a majority of differences we observed in the categories demonstrating the highest hit rates, although our sampling approach, most notably sampling from a multiset so as to reflect the observed frequencies of individual citations as well as their associated journals and disciplines, can also create material differences.
+We conclude that the choice of background datasets is the source of a majority of differences we observed in the categories demonstrating the highest hit rates, although our sampling approach, most notably sampling from a multiset so as to reflect the observed frequencies of individual citations as well as their associated journals and disciplines, can also create \textcolor{blue}{material differences.}
 

### 2019-06-14 cocit_r.tex
minor edit

@@
 
-We conclude that the choice of background datasets is the source of a majority of differences we observed in the categories demonstrating the highest hit rates, although our sampling approach, most notably sampling from a multiset so as to reflect the observed frequencies of individual citations as well as their associated journals and disciplines, can also create \textcolor{blue}{material differences.}
+We conclude that the choice of background datasets is the source of a majority of differences we observed in the categories demonstrating the highest hit rates, although our sampling approach, most notably sampling from a multiset so as to reflect the observed frequencies of individual citations as well as their associated journals and disciplines, can also create material differences.
 

### 2019-06-14 cocit_r.tex
penultimate para in Disc

@@
 
-Citation and network analysis of  scientific literature reveals information on semantic relationships between publications, collaboration between scientists, and the practice of citation itself~\citep{garfield_citation_1955,de_solla_price_networks_1965,newman_structure_2001,Shi:2010:CHI:1816123.1816131,patience_pmid28560354}.
+Citation and network analysis of  scientific literature reveals information on semantic relationships between publications, collaboration between scientists, and the practice of citation itself~\citep{garfield_citation_1955,de_solla_price_networks_1965,newman_structure_2001,Shi:2010:CHI:1816123.1816131,patience_pmid28560354,stigler_1994}.
 Co-citation, the frequency with which two documents are cited together in other documents provides additional insights, including the identification of semantically related documents, fields, specializations, and new ideas in science~\citep{small_co-citation_1973, marshakova-shaikevich_co-citation_1973,boyack_co-citation_2010, 10.3389/frma.2018.00020}.
@@
 A follow-up study by \cite{boyack_vs_uzzi_2014} explored the impact of discipline and journal effects on these definitions of conventionality and novelty.
-While their study had some methodological differences in the use of Scopus data rather than WoS data, a smaller dataset, and a $\chi^2$ calculation rather than Monte Carlo simulations to generate expected values of journal pairs, Boyack and Klavans noted strong effects from both disciplines and journals.
+While their study had some methodological differences in the use of Scopus data rather than WoS data, a smaller dataset, and a $\chi^2$ calculation rather than Monte Carlo simulations to generate expected values of journal pairs, Boyack and Klavans noted strong effects from disciplines and journals.
 While they also reported the trend that HNHC is more probable in highly cited papers, they observed that ``only 64.4\%  of  243  WoS  subject  categories'' in the Uzzi {\em et al.} study met the criterion of having the highest probability of hit papers in the HNHC category.
@@
 
-While our work has shown that the use of local networks defines a benchmark more consistent with research citation patterns, further work might explore how the alignment of benchmarks with practice might be further improved.
-These can be viewed, and possibly implemented as further constraints on the random assignment of citations to publications.
-For example, one might take into consideration the proximity of possible citations as defined in a co-author network~\citep{wallace_lariviere_gingras_2012} when defining probabilities for citation substitutions.
-Other foundations for benchmarks might include consideration of the possibility that citation patterns are partly due to communications within and between fields, as well a reflection of and exertion of intellectual influence~\citep{stigler_1994}.
-
-In terms of further work, evaluation in context~\citep{hicks_bibliometrics:_2015} and increased consideration of the disciplinary nature of the scientific enterprise is likely to result in improved models that yield further insight.
+\textcolor{blue}{Our work has shown that the use of local networks enables simulations that are more consistent with research citation patterns.
+Further work might explore additional constraints on random assignment of citations to publications.
+For example, the proximity of possible citations as defined in a co-author network~\citep{wallace_lariviere_gingras_2012} when defining probabilities for citation substitutions.
+Thus, evaluation in context~\citep{hicks_bibliometrics:_2015} and increased consideration of the disciplinary nature of the scientific enterprise is likely to result in improved models that yield further insight.}
 

### 2019-06-14 cocit_r.tex
Minor Revisions

@@
 
-\textcolor{blue}{Our work has shown that the use of local networks enables simulations that are more consistent with research citation patterns.
+Our work has shown that the use of local networks enables simulations that are more consistent with research citation patterns.
 Further work might explore additional constraints on random assignment of citations to publications.
 For example, the proximity of possible citations as defined in a co-author network~\citep{wallace_lariviere_gingras_2012} when defining probabilities for citation substitutions.
-Thus, evaluation in context~\citep{hicks_bibliometrics:_2015} and increased consideration of the disciplinary nature of the scientific enterprise is likely to result in improved models that yield further insight.}
+Thus, evaluation in context~\citep{hicks_bibliometrics:_2015} and increased consideration of the disciplinary nature of the scientific enterprise is likely to result in improved models that yield further insight.
 

### 2019-06-14 cocit_r.tex
minor revisions

@@
 Results for the three disciplinary networks all differ from the overall WoS results: the highest hit rates for the immunology and metabolism datasets  are in the LNHC category and the highest hit rate for the applied physics datasets are in the HNLC category.
-\textcolor{blue}{Need numbers for metabolism for the next sentence:} The number of data points in the immunology, applied physics, and WoS data sets are 21,917, 18,305, and 476,288, respectively.  
+The number of data points in the applied physics, immunology, metabolism, and WoS data sets are 18,305, 21,917, 97,405, and 476,288, respectively.
 }
@@
 
-Since the constrained model better fits the observed data, we evaluated the distribution of highly cited articles  (i.e., ``hit articles") in the four categories (HCHN, LCHN, HCLN, LCLN), for different thresholds for hit articles.
+Since the constrained model better fits the observed data, we evaluated the distribution of highly cited articles  (i.e., ``hit articles") in the four categories (HNHC, HNLC, LNHC, LNLC), for different thresholds for hit articles.
 Figure \ref{fig:Fig2}, Panels (a) and (b), compares hit rates for the four categories among the Immunology, Metabolism, Applied Physics, and WoS datasets for 1995, where the hit rate is defined as the number of hit articles in each category divided by the number of articles in the category.
@@
 We have conjectured that the approach of Uzzi et al.
-for generating journal-pair z-scores is misspecified in its sampling from a broad dataset and its disregard for the frequency with which journal pairs are citedOur principal consideration was to restrict model misspecification arising from disciplinarily irrelevant references.
+for generating journal-pair z-scores is misspecified in its sampling from a broad dataset and its disregard for the frequency with which journal pairs are cited.
+Our principal consideration was to restrict model misspecification arising from disciplinarily irrelevant references.
 We addressed this consideration by analyzing disciplinary subsets of the scientific literature, thereby restricting random selection of references to only those references in the disciplinary network being studied.As observed in the Introduction, Monte Carlo simulations that use references from all publications do not account for observed citation practice (sentence needs to be made more eloquent)...

### 2019-06-14 cocit_r.tex
minor changes

@@
 Since the constrained model better fits the observed data, we evaluated the distribution of highly cited articles  (i.e., ``hit articles") in the four categories (HNHC, HNLC, LNHC, LNLC), for different thresholds for hit articles.
-Figure \ref{fig:Fig2}, Panels (a) and (b), compares hit rates for the four categories among the Immunology, Metabolism, Applied Physics, and WoS datasets for 1995, where the hit rate is defined as the number of hit articles in each category divided by the number of articles in the category.
+Figure \ref{fig:Fig2}, Panels (a) and (b), compares hit rates for the four categories among the immunology, metabolism, applied physics, and WoS datasets for 1995, where the hit rate is defined as the number of hit articles in each category divided by the number of articles in the category.
 The calculation for the hit rates for the WoS dataset (bottom row, Figure \ref{fig:Fig2}) mirrors Uzzi et al.'s results, whereby the largest hit rates were for the HNHC category, despite our methodological changes in sampling citations in proportion to their frequency.

### 2019-06-14 cocit_r.tex
minor

@@
 Further,  high ``novelty" is not always indicative of impactful research (as reflected in citation counts), as shown by both Immunology and Metabolism having their highest hit rates for low novelty (Figure \ref{fig:Fig2}).
-Of relevance, we found the category displaying the highest hit rate to be sensitive to the study parameters, which include the percentage of articles classified as hits, the z-score percentile threshold that delineates LN and HN, and the publication year.
+%\textcolor{blue}{Of relevance, we found the category displaying the highest hit rate to be sensitive to the study parameters, which include the percentage of articles classified as hits, the z-score percentile threshold that delineates LN and HN, and the publication year.}
 
-More generally, these results show that the trends approaching universality in highly cited papers are not robust to changes in thresholds for defining high impact or high novelty articles and may be the consequence of using a random model that has a poor fit to the observed data.
+More generally, these results show that the trends approaching universality in highly cited papers are not robust to changes in thresholds for defining high impact or high novelty articles, or with time, and may be the consequence of using a random model that has a poor fit to the observed data.
 On the other hand, while  the constrained model reduces model misspecification compared to the unconstrained model, this does not imply that the constrained model is reasonable nor that trends observed under the constrained model convincingly explain scientific practice.
@@
 Our work has shown that the use of local networks enables simulations that are more consistent with research citation patterns.
-Further work might explore additional constraints on random assignment of citations to publications.
-For example, the proximity of possible citations as defined in a co-author network~\citep{wallace_lariviere_gingras_2012} when defining probabilities for citation substitutions.
+Further work might explore additional constraints on random assignment of citations to publications to better align benchmarks with citation practice.
+For example, the proximity of possible citations as defined in a co-author network~\citep{wallace_lariviere_gingras_2012} might be considered when defining probabilities for citation substitutions.
 Thus, evaluation in context~\citep{hicks_bibliometrics:_2015} and increased consideration of the disciplinary nature of the scientific enterprise is likely to result in improved models that yield further insight.

### 2019-06-14 cocit_r.tex
minor

@@
  While applied physics and immunology represent somewhat small networks (roughly 2-6\% of WoS), metabolism represents approximately 22\% of WoS, making them interesting and meaningful test cases.
-We also examined publications in the five major research areas in the WoS: life sciences \& biomedicine, physical sciences, technology, social sciences, and arts \& humanities,  using the extended subcategory classification of 153 sub-groups to categorize disciplinary composition of cited references in the datasets we studied.
+We also examined publications in the five major research areas in the WoS: life sciences \& biomedicine, physical sciences, technology, social sciences, and arts \& humanities,  using the extended WoS subcategory classification of 153 sub-groups to categorize disciplinary composition of cited references in the datasets we studied.
 \vspace{-2 mm}

### 2019-06-14 cocit_r.tex
very minor edits

@@
 As a result of these calculations, each publication becomes associated with a set of z-scores corresponding to the journal pairs derived from pairwise combinations of its cited references.
-Positional statistics of z-scores were calculated for each publication, which was then labeled according to conventionality and novelty: (i) HC if the median z-score exceeded the median of median z-scores for all publications and LC otherwise
-%if the median z-score was equal to or less than the median of median z-scores for all publications
-, and (ii) HN if the tenth percentile of z-scores for a publication was less than zero, and LN otherwise. 
+Positional statistics of z-scores were calculated for each publication, which was then labeled according to conventionality and novelty: (i) HC if the median z-score exceeded the median of median z-scores for all publications and LC otherwise and
+%if the median z-score was equal to or less than the median of median z-scores for all publications and
+(ii) HN if the tenth percentile of z-scores for a publication was less than zero and LN otherwise. 
 %if the tenth percentile of z-scores for a publication was greater than zero. 

### 2019-06-14 cocit_r.tex
closeout tweaks

--- 2019-06-14 cocit_r.tex
@@
 Citation and network analysis of  scientific literature reveals information on semantic relationships between publications, collaboration between scientists, and the practice of citation itself~\citep{garfield_citation_1955,de_solla_price_networks_1965,newman_structure_2001,Shi:2010:CHI:1816123.1816131,patience_pmid28560354,stigler_1994}.
-Co-citation, the frequency with which two documents are cited together in other documents provides additional insights, including the identification of semantically related documents, fields, specializations, and new ideas in science~\citep{small_co-citation_1973, marshakova-shaikevich_co-citation_1973,boyack_co-citation_2010, 10.3389/frma.2018.00020}.
+Co-citation, the frequency with which two documents are cited together in other documents, provides additional insights, including the identification of semantically related documents, fields, specializations, and new ideas in science~\citep{small_co-citation_1973, marshakova-shaikevich_co-citation_1973,boyack_co-citation_2010, 10.3389/frma.2018.00020}.
 
@@
 
-Key to Uzzi {\em et al.}~is their random graph model and its underlying assumptions.
+Key to the findings of Uzzi {\em et al.}~is their random graph model and its underlying assumptions.
 The citation switching algorithm used to generate expected values by random substitutions of references is designed to preserve the number of publications, the number of references in each publication, and the year of publication of both publications and references.
@@
 For example, a reference in quantum physics can be substituted, with equal probability, by a reference in quantum physics, quantum chemistry, classical literature, entomology, or anthropology.
-Such substitutions poorly model the disciplinary nature of scientific endeavor and citation behavior~\citep{wallace_lariviere_gingras_2012,moed_measuring_2010,klavans_research_2017,garfield_1979}.
+Such substitutions poorly model the disciplinary nature of scientific research and citation behavior~\citep{wallace_lariviere_gingras_2012,moed_measuring_2010,klavans_research_2017,garfield_1979}.
 In addition, under this random model, a reference cited many times in a given year is selected with the same probability as a reference cited only once, which appears inconsistent with the power law or lognormal citation distributions described in the literature~\citep{stringer_statistical_2010,perline_strong_2005}.
-Accordingly, model misspecification is likely to arise on account of the simulated values not reflecting the empirical data very well.
+Accordingly, model misspecification is likely to arise on account of the simulated values not corresponding to the empirical data very well.
 
 A follow-up study by \cite{boyack_vs_uzzi_2014} explored the impact of discipline and journal effects on these definitions of conventionality and novelty.
-While their study had some methodological differences in the use of Scopus data rather than WoS data, a smaller dataset, and a $\chi^2$ calculation rather than Monte Carlo simulations to generate expected values of journal pairs, Boyack and Klavans noted strong effects from disciplines and journals.
+While their study had some methodological differences in the use of Scopus data rather than WoS data, a smaller data set, and a $\chi^2$ calculation rather than Monte Carlo simulations to generate expected values of journal pairs, Boyack and Klavans noted strong effects from disciplines and journals.
 While they also reported the trend that HNHC is more probable in highly cited papers, they observed that ``only 64.4\%  of  243  WoS  subject  categories'' in the Uzzi {\em et al.} study met the criterion of having the highest probability of hit papers in the HNHC category.
@@
 For example, while Uzzi {\em et al.} reported that highly cited articles are more likely than expected to be both HC and HN and that this trend largely held across all disciplines, we find that these trends vary with the discipline so that universal trends are not apparent.
-Specifically,  HC remains highly correlated with highly cited articles in the immunology and metabolism datasets but not with applied physics, and HN is highly correlated with highly cited articles in applied physics but not with immunology and metabolism.
+Specifically,  HC remains highly correlated with highly cited articles in the immunology and metabolism data sets but not with applied physics, and HN is highly correlated with highly cited articles in applied physics but not with immunology and metabolism.
 Thus, disciplinary networks are different from each other, and trends that hold for the full WoS network do not hold for even large networks (such as metabolism).
@@
 WoS data stored in ERNIE spans the period 1900-2019 and consists of over 72 million publications.
-For this study, we generated an analytical dataset from years 1985 to 2005 using data in ERNIE.
-The total number of publications in this dataset was just over 25 million publications (25,134,073), which were then stratified by year of publication.
+For this study, we generated an analytical data set from years 1985 to 2005 using data in ERNIE.
+The total number of publications in this data set was just over 25 million publications (25,134,073), which were then stratified by year of publication.
 For each of these years, we further restricted analysis to publications of type Article.
@@
 \begin{table}[ht]
-\caption{Summary of base WoS Analytical Dataset.
+\caption{Summary of base WoS Analytical data set.
 Only publications of type Article with at least two references and references with complete publication data were selected for this data set.
@@
 
-We constructed three disciplinary datasets in areas of our interest based on the keyword searches: immunology,   metabolism, and   applied physics.
-For the first two, rooted in biomedical research, we searched Pubmed for the term `immunology' or `metabolism' in the years 1985, 1995, and 2005~(Table \ref{tab:disc-datasets}).
+We constructed three disciplinary data sets in areas of our interest based on the keyword searches: immunology,   metabolism, and   applied physics.
+For the first two, rooted in biomedical research, we searched Pubmed for the term `immunology' or `metabolism' in the years 1985, 1995, and 2005~(Table \ref{tab:disc-data sets}).
 Pubmed IDs (pmids) returned were matched to WoS IDs (wos\_ids) and used to retrieve relevant articles.
-For the applied physics dataset, we directly searched traditional subject labels in WoS for `Physics, Applied'.
+For the applied physics data set, we directly searched traditional subject labels in WoS for `Physics, Applied'.
 While applied physics and immunology represent somewhat small networks (roughly 2-6\% of WoS), metabolism represents approximately 22\% of WoS, making them interesting and meaningful test cases.
-We also examined publications in the five major research areas in the WoS: life sciences \& biomedicine, physical sciences, technology, social sciences, and arts \& humanities,  using the extended subcategory classification of 153 sub-groups to categorize disciplinary composition of cited references in the datasets we studied.
+We also examined publications in the five major research areas in WoS: life sciences \& biomedicine, physical sciences, technology, social sciences, and arts \& humanities,  using the extended WoS subcategory classification of 153 sub-groups to categorize disciplinary composition of cited references in the data sets we studied.
 \vspace{-2 mm}
 \begin{table}[ht]
-\caption{Disciplinary Datasets.
-PubMed and WoS were searched for articles using search terms, `immunology', `metabolism', and `applied physics.' Counts of publications are shown for each of the three years analyzed and expressed in parentheses as a percentage of the total number of publications in our analytical WoS dataset (Table \ref{tab:summary_data}) for that year.
+\caption{Disciplinary data sets.
+PubMed and WoS were searched for articles using search terms, `immunology', `metabolism', and `applied physics.' Counts of publications are shown for each of the three years analyzed and expressed in parentheses as a percentage of the total number of publications in our analytical WoS data set (Table \ref{tab:summary_data}) for that year.
 Note that Applied Physics and Immunology each represent about 4\% of the publications in WoS, but Metabolism occupies nearly one-fourth of WoS.}
-\label{tab:disc-datasets}
+\label{tab:disc-data sets}
 \centering
@@
 These reference pairs were then mapped to the journals they were published in using ISSN numbers as identifiers.
-Where multiple ISSN numbers exist for a journal, the most frequently used one in the WoS was assigned to the journal.
+Where multiple ISSN numbers exist for a journal, the most frequently used one in WoS was assigned to the journal.
 In addition, publications containing fewer than two references were discarded.
-Journal pair frequencies were summed across the dataset to create observed frequencies $(F_{obs})$.
+Journal pair frequencies were summed across the data set to create observed frequencies $(F_{obs})$.
 
-For citation shuffling, we developed a performant citation switching algorithm, \emph{runtime enhanced permuting citation switcher (repcs)}~\citep{GithubERNIE2019}, that randomly permuted citations grouped by year of publication to switch citations while preserving the year of publication for both articles and references, the number of publications and the number of references in each dataset, and the disciplinary composition of the references in each dataset.
+For citation shuffling, we developed a performant citation switching algorithm, \emph{runtime enhanced permuting citation switcher (repcs)}~\citep{GithubERNIE2019}, that randomly permuted citations grouped by year of publication to switch citations while preserving the year of publication for both articles and references, the number of publications and the number of references in each data set, and the disciplinary composition of the references in each data set.
 Our approach is different from previous studies in these ways: (i) we sampled citations in proportion to their citation frequency (equivalently from a multiset rather than a set) in order to better reflect citation practice,
@@
 As a benchmark, we used the citation switching algorithm of ~\cite{uzzi_atypical_2013}, henceforth referred to  as \emph{umsj} (as also done in~\cite{boyack_vs_uzzi_2014}), using code kindly provided by the authors.
-A single comparative analysis showed that while 10 simulations of the WoS 1985 dataset (391,860 publications) completed in 2,186 hours using the \emph{umsj} algorithm, it completed in less than one hour using our implementation of the \emph{repcs}   algorithm on a Spark  cluster.
-We also tested \emph{repcs}  under comparable conditions to \emph{umsj} and estimated a runtime advantage of at least two orders of magnitude.
+A single comparative analysis showed that while 10 simulations of the WoS 1985 data set (391,860 publications) completed in 2,186 hours using the \emph{umsj} algorithm, it completed in less than one hour using our implementation of the \emph{repcs}   algorithm on a Spark  cluster.
 Using either the \emph{repcs}   or \emph{umsj} algorithms for 10 simulations resulted in expected value coverage of 75\% of the observed journal pair frequencies.
 Subsequent rounds of development and testing resulted in 99\% coverage of observed journal pairs when 1,000 simulations were conducted.
-The runtime advantage was significant enough that we chose to use the \emph{repcs}   algorithm in our study  and generated expected values averaged from 1,000 simulations for improved coverage of every dataset we analyzed.
+We also tested \emph{repcs}  under comparable conditions to \emph{umsj} and estimated a runtime advantage of at least two orders of magnitude.
+This runtime advantage was significant enough that we chose to use the \emph{repcs}   algorithm in our study and generated expected values averaged from 1,000 simulations for improved coverage of every data set we analyzed.
 
-Averaging the result of 1,000 simulations for each dataset studied, z-scores were then calculated for each journal-pair using the formula $(F_{obs} - F_{exp})/\sigma$ where $F_{obs}$ is the observed frequency, $F_{exp}$ is the averaged simulated frequency, and $\sigma$ is the standard deviation of the simulated frequencies for a journal pair.
+Averaging the result of 1,000 simulations for each data set studied, z-scores were then calculated for each journal-pair using the formula $(F_{obs} - F_{exp})/\sigma$ where $F_{obs}$ is the observed frequency, $F_{exp}$ is the averaged simulated frequency, and $\sigma$ is the standard deviation of the simulated frequencies for a journal pair.
 As a result of these calculations, each publication becomes associated with a set of z-scores corresponding to the journal pairs derived from pairwise combinations of its cited references.
-Positional statistics of z-scores were calculated for each publication, which was then labeled according to conventionality and novelty: (i) HC if the median z-score exceeded the median of median z-scores for all publications and LC otherwise
-%if the median z-score was equal to or less than the median of median z-scores for all publications
-, and (ii) HN if the tenth percentile of z-scores for a publication was less than zero, and LN otherwise. 
-%if the tenth percentile of z-scores for a publication was greater than zero. 
+Positional statistics of z-scores were calculated for each publication, which was then labeled according to conventionality and novelty: (i) HC if the median z-score exceeded the median of median z-scores for all publications and LC otherwise and (ii) HN if the tenth percentile of z-scores for a publication was less than zero and LN otherwise.
 We also analyzed the effect of defining high novelty using the first percentile of z-scores.
@@
 
-To study the disciplinary composition of references in our custom datasets, we first used the high level WoS classification of five major research areas: life sciences \& biomedicine, physical sciences, social sciences, technology, and arts \& humanities.
+To study the disciplinary composition of references in our custom data sets, we first used the high level WoS classification of five major research areas: life sciences \& biomedicine, physical sciences, social sciences, technology, and arts \& humanities.
 The two largest of these research areas are physical sciences and life sciences \& biomedicine, which contribute on average approximately 35.1\% and 62.8\%, respectively, of the references in WoS over the three years of interest.
@@
 We also analyzed disciplinary composition at a deeper level using all 153 Subjects in the WoS extended classification and examining the consequences of  citation shuffling within a disciplinary set or all of the Web of Science.
-References in publications belonging to these three datasets were summarized as a frequency distribution of 153 WoS Subjects as classes.
-A single shuffle of the references in the disciplinary datasets and in the corresponding WoS year slice was performed, using either the \emph{repcs}  or \emph{umsj} algorithms, after which subject frequencies were computed again.
+References in publications belonging to these three data sets were summarized as a frequency distribution of 153 WoS Subjects as classes.
+A single shuffle of the references in the disciplinary data sets and in the corresponding WoS year slice was performed, using either the \emph{repcs}  or \emph{umsj} algorithms, after which subject frequencies were computed again.
 The fold change in subject frequencies of references before and after shuffling was calculated for these groups using all 153 subject categories and summarized in the box plots in Fig \ref{fig:be}.
-As an example, the applied physics dataset contained one reference labeled Genetics and Heredity, but after the shuffle (using the WoS background), acquired 1496 references labeled Genetics and Heredity.
-Similarly,  the metabolism dataset  contained one reference labeled Philosophy, but after a single shuffle (again using the WoS background) it had 661 occurrences with this label.
+As an example, the applied physics data set contained one reference labeled Genetics and Heredity, but after the shuffle (using the WoS background), acquired 1496 references labeled Genetics and Heredity.
+Similarly,  the metabolism data set  contained one reference labeled Philosophy, but after a single shuffle (again using the WoS background) it had 661 occurrences with this label.
 The data show convincingly that a publication's disciplinary composition of references in a network is preserved when citation shuffling is constrained to the network, but is significantly distorted when the WoS superset is used as a source of substitution.
@@
 \caption{Model misspecification is reduced by constraining substitutions to the local  disciplinary networks.
-We computed 
-Kullback-Leibler (K-L) divergences
-between empirical and simulated journal pair frequencies using two different
-background networks (local versus global) for each disciplinary network  (applied physics, immunology, and metabolism)
-for the years 1985, 1995, and 2005.
-% for the three disciplinary datasets (applied physics, immunology, and metabolism) using either the disciplinary network as background or the WoS superset (all\_wos) to generate the null model (Background).
+We computed Kullback-Leibler (K-L) divergencesbetween empirical and simulated journal pair frequencies using two different
+background networks (local versus global) for each disciplinary network  (applied physics, immunology, and metabolism) for the years 1985, 1995, and 2005.
 K-L divergence was calculated using the R seewave package \citep{seewave2008}.
-For every disciplinary network, there is a smaller K-L divergence between simulated and observed data
-when using the local network (i.e., the disciplinary network) as compared to the global network (all of WoS). 
-Put differently, 
-model misspecification is reduced in the constrained model compared to the unconstrained model.
-%by  restricting the reference substitutions to the disciplinary network  as compared to treating all substitutions within WoS as equiprobable.
-}
+For every disciplinary network, there is a smaller K-L divergence between simulated and observed data when using the local network (i.e., the disciplinary network) as compared to the global network (all of WoS).
+Put differently, model misspecification is reduced in the constrained model compared to the unconstrained model.}
 \label{tab:kld}
@@
 The results (Table \ref{tab:kld}) confirm this prediction: simulations under the constrained model 
-(where the background network is the local disciplinary network) consistently have a lower K-L divergence compared to simulations under the unconstrained model  (where the background network is all of WoS).
+(where the background network is the local disciplinary network) consistently have a lower K-L divergence compared to simulations under the unconstrained model  (where the background network is WoS).
 Furthermore, the K-L divergence for the unconstrained model is generally twice as large as the K-L divergence for the constrained models, with ratios that range from 1.96 to 2.77, and are greater than 2.0 in eight out of nine cases.
@@
 \caption{Effect of using the improved model on  categorical hit rates for Immunology, Applied Physics, and WoS for 1995.
-Panels (a) and (b) show hit rates for the LNLC, LNHC, HNLC, and HNHC categories for the applied physics, immunology, metabolism, and WoS datasets when hit articles are defined as the top 1\% and top 10\% of articles, respectively.
+Panels (a) and (b) show hit rates for the LNLC, LNHC, HNLC, and HNHC categories for the applied physics, immunology, metabolism, and WoS data sets when hit articles are defined as the top 1\% and top 10\% of articles, respectively.
 Novelty in both panels is defined at the 10th percentile of articles' z-score distributions.
 The results for the WoS data set also show that the highest hit rate is for the HNHC category.
-Results for the three disciplinary networks all differ from the overall WoS results: the highest hit rates for the immunology and metabolism datasets  are in the LNHC category and the highest hit rate for the applied physics datasets are in the HNLC category.
+Results for the three disciplinary networks all differ from the overall WoS results: the highest hit rates for the immunology and metabolism data sets  are in the LNHC category and the highest hit rate for the applied physics data sets are in the HNLC category.
 The number of data points in the applied physics, immunology, metabolism, and WoS data sets are 18,305, 21,917, 97,405, and 476,288, respectively.
@@
 Since the constrained model better fits the observed data, we evaluated the distribution of highly cited articles  (i.e., ``hit articles") in the four categories (HNHC, HNLC, LNHC, LNLC), for different thresholds for hit articles.
-Figure \ref{fig:Fig2}, Panels (a) and (b), compares hit rates for the four categories among the immunology, metabolism, applied physics, and WoS datasets for 1995, where the hit rate is defined as the number of hit articles in each category divided by the number of articles in the category.
-The calculation for the hit rates for the WoS dataset (bottom row, Figure \ref{fig:Fig2}) mirrors Uzzi et al.'s results, whereby the largest hit rates were for the HNHC category, despite our methodological changes in sampling citations in proportion to their frequency.
+Figure \ref{fig:Fig2}, Panels (a) and (b), compares hit rates for the four categories among the immunology, metabolism, applied physics, and WoS data sets for 1995, where the hit rate is defined as the number of hit articles in each category divided by the number of articles in the category.
+The calculation for the hit rates for the WoS data set (bottom row, Figure \ref{fig:Fig2}) mirrors Uzzi et al.'s results, whereby the largest hit rates were for the HNHC category, despite our methodological changes in sampling citations in proportion to their frequency.
 However, the trends  for all three  disciplinary networks  are different from those for WoS.
-Specifically, the highest hit rates for the 1995 immunology and metabolism datasets are in the LNHC category for the top 1\% of cited articles (and tied between LNHC and HNHC for the top 10\%), and the highest hit rates for the 1995 applied physics datasets are in the HNLC category for both the top 1\% and top 10\% of all cited articles.
+Specifically, the highest hit rates for the 1995 immunology and metabolism data sets are in the LNHC category for the top 1\% of cited articles (and tied between LNHC and HNHC for the top 10\%), and the highest hit rates for the 1995 applied physics data sets are in the HNLC category for both the top 1\% and top 10\% of all cited articles.
 Thus, the category exhibiting the highest hit rate among highly cited papers depends on the specific disciplinary network and to some extent on the threshold for being highly cited.
@@
 Rejecting the null hypothesis, using a Chi-Square Goodness of Fit test, supports a non-uniform dispersion of hits with some of the four categories being associated with higher or lower than expected expected hit rates.
-The null hypothesis was rejected at a $p<0.001$ in all cases in  Figure \ref{fig:Fig2}, with the exception of the immunology and applied physics datasets where hit articles are designated as the top 1\% of articles: valid tests were not possible in those instances due to too few expected hits.
-The null hypothesis was rejected with $p<0.001$ for all valid tests for all parameter settings, all datasets, and all years: hypotheses tests were valid in 73 of 96 instances.
-We conclude that it is likely that the distribution of hits among categories is not uniform and that, instead, hit rates vary among the categories in all disciplinary datasets.
+The null hypothesis was rejected at a $p<0.001$ in all cases in  Figure \ref{fig:Fig2}, with the exception of the immunology and applied physics data sets where hit articles are designated as the top 1\% of articles: valid tests were not possible in those instances due to too few expected hits.
+The null hypothesis was rejected with $p<0.001$ for all valid tests for all parameter settings, all data sets, and all years: hypotheses tests were valid in 73 of 96 instances.
+We conclude that it is likely that the distribution of hits among categories is not uniform and that, instead, hit rates vary among the categories in all disciplinary data sets.
 
@@
 Hits in the immunology and metabolism data were overrepresented in the HC category with the same statistical significance as for WoS.
-The relationship of novelty with hits in the immunology and metabolism dataset differed dramatically from the WoS, however, with statistically significant findings of hit articles being sometimes overrepresented in the LN category, and sometimes being underrepresented.
-Consistent with the WoS, hit articles in applied physics were positively related with HN with a statistical significance of at least $p<0.10$ in all 12 parameter sets, and at $p<0.05$ in 10 of 12 cases.
+The relationship of novelty with hits in the immunology and metabolism data set differed dramatically from WoS, however, with statistically significant findings of hit articles being sometimes overrepresented in the LN category, and sometimes being underrepresented.
+Consistent with WoS, hit articles in applied physics were positively related with HN with a statistical significance of at least $p<0.10$ in all 12 parameter sets, and at $p<0.05$ in 10 of 12 cases.
 To the contrary, a strong positive relationship was found between LC and hit articles in applied physics in 5 of 12 instances with $p<0.10$.
-These results suggest that (1) both conventionality and novelty are strongly related to hits in the WoS, (2) the conventionality dimension is strongly related with hits in immunology and metabolism and novelty is not, and (3) novelty is more strongly related with hits in applied physics than is conventionality.
+These results suggest that (1) both conventionality and novelty are strongly related to hits in WoS, (2) the conventionality dimension is strongly related with hits in immunology and metabolism and novelty is not, and (3) novelty is more strongly related with hits in applied physics than is conventionality.
 More generally, we find that the dimensions most strongly related with hit articles vary between disciplinary and broad data sets, and also among disciplines.
 
-We described concerns with model misspecification along two general dimensions: the background dataset and sampling methodology for the random graph.
-The differences we found from prior research in terms of which categories demonstrated the highest hit rates were caused both by using disciplinary datasets and our sampling methodology, \textit{repcs},  through the article z-score distributions.
+We described concerns with model misspecification along two general dimensions: the background data set and sampling methodology for the random graph.
+The differences we found from prior research in terms of which categories demonstrated the highest hit rates were caused both by using disciplinary data sets and our sampling methodology, \textit{repcs},  through the article z-score distributions.
 When z-scores are shifted downward using one algorithm versus another, for example, then the former algorithm can result in an increased percentage of HN articles.
 We therefore examined  the extent to which each of our methodological differences contributed to our observations.  
-We found that z-scores changed sign more as a consequence of background network (local network or all of WoS) and much less as a consequence of sampling algorithm
+We found that z-scores changed sign more as a consequence of background network (local network or WoS) and much less as a consequence of sampling algorithm
  ({\textit{umsj} or \textit{repcs}). 
-For example,  on the immunology dataset, 28.6\% of the journal pairs changed signs with our sampling algorithm (\textit{repcs}) as the background network is changed from global (all of WoS) to local, and
-only 2.8\% of z-scores changed signs in the WoS dataset depending on whether 
+For example,  on the immunology data set, 28.6\% of the journal pairs changed signs with our sampling algorithm (\textit{repcs}) as the background network is changed from global (WoS) to local, and 
+only 2.8\% of z-scores changed signs in the WoS data set depending on whether 
 \textit{umsj} or \textit{repcs} was used.
 
-We conclude that the choice of background datasets is the source of a majority of differences we observed in the categories demonstrating the highest hit rates, although our sampling approach, most notably sampling from a multiset so as to reflect the observed frequencies of individual citations as well as their associated journals and disciplines, can also create material differences.
+We conclude that the choice of background data sets is the source of a majority of differences we observed in the categories demonstrating the highest hit rates, although our sampling approach, most notably sampling from a multiset so as to reflect the observed frequencies of individual citations as well as their associated journals and disciplines, can also create material differences.
 
@@
 We provided several lines of evidence that showed that changing this one parameter from a global network to the local disciplinary network reduces model misspecification.
-Furthermore,  using the constrained model (which allows substitutions only within the local network)  instead of the unconstrained model (which allows substitutions in the entire WoS network) produces different trends in terms of conventionality and novelty, depending on the network.
+Furthermore,  using the constrained model (which allows substitutions only within the local network)  instead of the unconstrained model (which allows substitutions in the WoS network) produces different trends in terms of conventionality and novelty, depending on the network.
 In particular, when using the unconstrained model, highly cited papers were most likely to be
@@
 Further,  high ``novelty" is not always indicative of impactful research (as reflected in citation counts), as shown by both Immunology and Metabolism having their highest hit rates for low novelty (Figure \ref{fig:Fig2}).
-%\textcolor{blue}{Of relevance, we found the category displaying the highest hit rate to be sensitive to the study parameters, which include the percentage of articles classified as hits, the z-score percentile threshold that delineates LN and HN, and the publication year.}
 
@@
 Further work might explore additional constraints on random assignment of citations to publications to better align benchmarks with citation practice.
-For example, the proximity of possible citations as defined in a co-author network~\citep{wallace_lariviere_gingras_2012} might be considered when defining probabilities for citation substitutions.
+For example, proximity defined by co-author networks~\citep{wallace_lariviere_gingras_2012} might be considered when defining probabilities for citation substitutions.
 Thus, evaluation in context~\citep{hicks_bibliometrics:_2015} and increased consideration of the disciplinary nature of the scientific enterprise is likely to result in improved models that yield further insight.
@@
 \emph{these remaining sentences require some work}
-The varying citation patterns when sampling from a disciplinary-focused dataset versus a broader dataset due, was a cause of journal pair z-scores changing signs in 28.6\% of instances: the effect of any one of these journal pairs on an article's novelty or conventionality is contradictory between broad and, more narrow disciplinary datasets.
-We contend that the interpretation due to a disciplinary dataset, which preserved citation patterns, is more appropriate and an improvement on current methods.
+The varying citation patterns when sampling from a disciplinary-focused data set versus a broader data set due, was a cause of journal pair z-scores changing signs in 28.6\% of instances: the effect of any one of these journal pairs on an article's novelty or conventionality is contradictory between broad and, more narrow disciplinary data sets.
+We contend that the interpretation due to a disciplinary data set, which preserved citation patterns, is more appropriate and an improvement on current methods.
 
@@
 The z-scores are computed for each disciplinary network based on the selected background network; thus, \emph{imm} denotes the immunology network with immunology z-scores and \emph{imm\_wos} denotes the immunology network with z-scores from WoS z-scores.
-The figure shows striking differences between the WOS network compared to the metabolism and immunology networks: across all networks, the percentage of high conventionality (HC) publications increases with citation counts, while the percentage of high novelty (HN) publications decreases with citation counts for the biological networks but not for WOS.
+The figure shows striking differences between the WoS network compared to the metabolism and immunology networks: across all networks, the percentage of high conventionality (HC) publications increases with citation counts, while the percentage of high novelty (HN) publications decreases with citation counts for the biological networks but not for WoS.
 \label{fig:Fig1}}
@@
 We have conjectured that the approach of Uzzi et al.
-for generating journal-pair z-scores is misspecified in its sampling from a broad dataset and its disregard for the frequency with which journal pairs are cited.
+for generating journal-pair z-scores is misspecified in its sampling from a broad data set and its disregard for the frequency with which journal pairs are cited.
 Our principal consideration was to restrict model misspecification arising from disciplinarily irrelevant references.
@@
 We addressed this consideration by analyzing disciplinary subsets of the scientific literature, thereby restricting random selection of references to only those references in the disciplinary network being studied.
-In this subsection we demonstrate the effects of model misspecification or Uzzi et al.'s approach and the effectiveness of using disciplinary datasets in resolving the concomitant issues with the former.
+In this subsection we demonstrate the effects of model misspecification or Uzzi et al.'s approach and the effectiveness of using disciplinary data sets in resolving the concomitant issues with the former.
 
-Note also in Figure \ref{fig:scatter} that many z-scores values are significantly different between the WoS and Immunology datasets, although the density of points near the origin in Figure \ref{fig:scatter} indicates that some journal pairs change signs between the datasets while their magnitudes are not significantly different.
+Note also in Figure \ref{fig:scatter} that many z-scores values are significantly different between WoS and Immunology data sets, although the density of points near the origin in Figure \ref{fig:scatter} indicates that some journal pairs change signs between the data sets while their magnitudes are not significantly different.
 While no metric is without downside, this observation points to a weakness of measuring novelty based simply on the sign of z-scores where no distinction is made between a small negative value and a large negative value, but a negative value of small magnitude is viewed as being significantly different than a small positive value.
@@
 The journal-pair z-scores in Figure \ref{fig:scatter} have consistent signs for both Immunology and WoS data sets in 71.4\% of the instances and different signs for 28.6\% of the journal pairs.
-When a journal-pair z-score is negative with respect to one dataset and positive with respect to another dataset, articles citing that pair are more likely to be deemed novel in the first instance and less likely to be deemed novel in the second instance.
-It seems that any journal pair should either be indicative of novelty or not, but it should never have contradictory implications that depend on the reference dataset.
-We view, therefore, these contradictions as symptomatic of inappropriately sampling from a broad dataset and ignoring observed citation patterns.
+When a journal-pair z-score is negative with respect to one data set and positive with respect to another data set, articles citing that pair are more likely to be deemed novel in the first instance and less likely to be deemed novel in the second instance.
+It seems that any journal pair should either be indicative of novelty or not, but it should never have contradictory implications that depend on the reference data set.
+We view, therefore, these contradictions as symptomatic of inappropriately sampling from a broad data set and ignoring observed citation patterns.
 Figure \ref{fig:scatter} reflects that the WoS data set has approximately 44,000 fewer negative z-scores than does the immunology data set, which contributes to its significantly lower percentage of high-novelty articles.
@@
 \caption{Journal pair z-scores vary with background network. 
-Scatter plot points (319,005) indicate journal pair z-scores for the 1995 Immunology dataset with two different background networks: the x-axis is based on the local network (1995 Immunology) and the y-axis is based on the entire Web of Science network.
+Scatter plot points (319,005) indicate journal pair z-scores for the 1995 Immunology data set with two different background networks: the x-axis is based on the local network (1995 Immunology) and the y-axis is based on the entire Web of Science network.
 Black indicates journal pairs whose z-scores have the same sign when computed for both background networks, while red points indicate the 28.6\% of journal pairs whose z-scores change sign across networks.
 Regions with deeper hues indicate higher point densities.
-} %and the histograms show the marginal distributions for each dataset separately.}
+} %and the histograms show the marginal distributions for each data set separately.}
 \label{fig:scatter}
@@
 
-The variation in z-scores with respect to the reference datasets causes the percentages of articles denoted as highly conventional and highly novel to be significantly different, as demonstrated in Figure \ref{fig:Fig1}.
+The variation in z-scores with respect to the reference data sets causes the percentages of articles denoted as highly conventional and highly novel to be significantly different, as demonstrated in Figure \ref{fig:Fig1}.
 \emph{Insert text about Figure \ref{fig:Fig1}.}
@@
 \centering
-\caption[Hit Rates]{Hit Rates by Category for the 1995 datasets. The last four columns indicate the proportion of publications that are hits for each respective category.} \label{Tab:HitRate}
+\caption[Hit Rates]{Hit Rates by Category for the 1995 data sets. The last four columns indicate the proportion of publications that are hits for each respective category.} \label{Tab:HitRate}
 \begin{tabular}{|crrrrrr|}

### 2019-06-16 cocit_r.tex
closeout tweaks
changed fold change to fold difference in document

@@
 
-Key to the findings of Uzzi {\em et al.}~is their random graph model and its underlying assumptions.
+Key to the findings of Uzzi {\em et al.}~is the random graph model used, and its underlying assumptions.
 The citation switching algorithm used to generate expected values by random substitutions of references is designed to preserve the number of publications, the number of references in each publication, and the year of publication of both publications and references.
@@
 A single shuffle of the references in the disciplinary data sets and in the corresponding WoS year slice was performed, using either the \emph{repcs}  or \emph{umsj} algorithms, after which subject frequencies were computed again.
-The fold change in subject frequencies of references before and after shuffling was calculated for these groups using all 153 subject categories and summarized in the box plots in Fig \ref{fig:be}.
+The fold difference in subject frequencies of references before and after shuffling was calculated for these groups using all 153 subject categories and summarized in the box plots in Fig \ref{fig:be}.
 As an example, the applied physics data set contained one reference labeled Genetics and Heredity, but after the shuffle (using the WoS background), acquired 1496 references labeled Genetics and Heredity.

### 2019-07-14 rebuttal.tex
early draft of rebuttal

\documentclass[11pt, oneside]{article}   	% use "amsart" instead of "article" for AMSLaTeX format
\usepackage{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   		% ... or a4paper or a5paper or ... 
%\geometry{landscape}                		% Activate for rotated page geometry
%\usepackage[parfill]{parskip}    		% Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}				% Use pdf, png, jpg, or epsÂ§ with pdflatex; use eps in DVI mode
								% TeX will automatically convert eps --> pdf in pdflatex		
\usepackage{amssymb}

%SetFonts

%SetFonts

\title{Brief Article}
\author{The Author}
%\date{}							% Activate to display a given date or no date

\begin{document}
\maketitle

The Editor\\
Quantitative Science Studies\\

We thank the reviewers for their constructive critiques, which we have attempted to respond to in a systematic manner below and in a revision of the manuscript.

\section{Reviewer 1}

\emph{This study focuses specifically on a potential flaw in a study by Uzzi, Mukherjee, Stringer, \& Jones  (2013).  Uzzi et al. used articles from the WoS database. They developed an indicator of conventionality and innovativeness for each article by focusing on the pairs of references within each article- and the corresponding pairs of journals associated with those pairs of references.  Journals were assumed to represent areas of knowledge.  Articles that built upon journal-pairs that were commonly mentioned together represented conventionality.  Articles that built upon journals pairs that were rarely mentioned together represented innovativeness. They found that articles with high conventionality and high innovative (HC; HI) were more highly cited (a commonly used indicator that the paper has had a greater impact).  Uzzi et al. also went through a variety of sensitivity analyses to show that the results held across different disciplinary fields (they used standard definitions of disciplines).}

\emph{ This study doesn't question the database.  They don't question the assumption that conventionality and innovativeness can be detected by calculating within-article journal co-occurrences. Their point of departure is in the calculation of z-scores (the deviation of journal co-occurences from expected values). Uzzi et al. used a random reference substitution approach to determine z-scores. The authors in this article suggest that substitutions should not be random.  One doesn't substitute a reference to a physics journal with a reference to a social science journal.  Substitutions should be within the local field.  Using their alternative approach, they show that Uzzi et al's central finding (that high conventionality and high innovativeness results in higher impact across many disciplines) does not apply equally across the three broadly defined fields they focused on: applied physics, immunology and metabolism.   They found that It doesn't apply equally across WoS disciplinary categories. This is, in essence, a highly focused methodological critique of an article that was published over five years ago.  As such, the technical contribution of this article, while important, may be marginal. The authors seem to suggest that their new substation approach should be used. I'm not convinced.}

The reviewer is correct. We do not question the database- the Web of Science is sufficiently comprehensive to conduct such studies. We are puzzled by the comment about the technical contribution being marginal. It is true that Uzzi was published five years ago but, with the exception of Boyack and Klavans (2014), it seems to have been uncritically cited over 175 times since.

\emph{As such, I recommend that the authors resubmit the article after resolving the following issues.
1.  Focus on the issue at hand.  Much of the early text is totally off the point of the study.  This is not a study in semantics. Nor is it about co-citation analysis and disciplinary affects.   The title seems totally misleading.  The article is about a very narrow methodological issue: whether the construction of Z-scores using a random substitution model is inherently biased vis-à-vis construction of Z-scores using a local substitution model.  So if the authors choose to rewrite- please edit out all of the superfluous material. It's a huge distraction.}

We have revised the text to reflect these suggestions. We have not changed the title. The methodological concern only has relevance in the larger context of co-citaton analysis and differences between disciplinary citation practice.

\emph{2.  Realize that the proposed approach is also flawed.  On the surface- it would make sense- don't substitute an anthropology journal for a physics journal. But deeper down, it may not make sense because there is no agreed upon way to decide what is ?local' and what isn't.   Does one use word searches to define fields (as suggested by the authors)?   Subject categories?   And since there's so much latitude in what one could use- aren't you running the risk of getting a false negative because of misspecification of the discipline?  
Stated differently, the proposed approach may be equally flawed because most highly influential journals (such as Science and Nature) can't be assigned to fields or disciplines.   These highly influential journals were found to have an excessively strong effect on the indicator of conventionality and innovativeness in Uzzi's study (see Boyack \& Klavans, 2014)- so a change in how the Z-score is calculated for this group will have a disproportional effect on the results.   It's not clear how does this new approach address this issue.  Science and Nature (and the other high influence journals) can publish across all three of their fields (immunology, applied physics and metabolism)- who should their cohort group be?  If a very small set of journals can have such a huge influence on the outcome- will the local substitution approach really help or hurt?}

The reviewer makes very valid points. In citing Boyack and Klavans (2014), we also reiterate that there are journal effects that we do not investigate in this study. However, we would like to point out that a keyword search defines a set of articles without modifying the references cited in those publications. In out approach, the expected values for z-score calculations are calculated from those references cited by the authors of those articles instead of the indiscriminate substitutions of Uzzi. An argument for our approach is the K-L measurements showing less model misspecification in our approach compared to Uzzi's.

\emph{3. Provide more concrete evidence that one approach is better than the other.  For example- use Uzzi's approach and your new approach to nominate the ?high innovative' and ?high conventional' papers.   Then focus on differences in these sets- the papers that are HI-using the old method vs. HI using the new method; HC-old vs. HC-new method; LI new vs. LI old; LC new vs. LC old).  Rely on a third approach to make the judgment about which approach is better (such as the recent work by Henry Small that detects whether a paper is a discovery paper using citance analysis). I suspect that, if one is trying to identify innovative papers, citance analysis that focuses on discovery (as a surrogate for innovation) is a reasonable approach- and gives a more concrete way of assessing the merits of the two approaches. Since these sets of papers can (and should) be made public- others can also see (for themselves) which method really works best.}

Again, we thank the reviewer. We have revised the text of our manuscript to make more clear that we're not endorsing this approach. [Tandy please insert your points here..]. We're not trying to identify innovative papers- our point is more that the proxy measure for impact suggests that HC flavored with HI (as defined by Uzzi) is not a universal feature of highly cited papers. A mixed methods approach where qualitative judgment is brought to bear on the quantitative results as per (Ioannidis, Klavans, and Boyack) is an excellent suggestion but we think it's beyond the scope of this manuscript.

\section{Reviewer 2}

\emph{This paper builds on the Uzzi et al (2013) Science paper.  It argues that a local network approach (rather than Uzzi's global network approach) is appropriate for identifying unusual combinations.  It also shows that Uzzi's findings regarding the relationship between novelty X conventionality and citation impact does not hold when using the local network approach. I really enjoyed reading this paper and believe that it is an important contribution: the topic and findings are important, data analysis is thorough, and paper is well-written.}

Thank you.

\emph{However, one major concern is about whether a local network is indeed more appropriate than a global network.  The authors did give very convincing arguments.  However, it can be argued that most atypical combinations are cross-disciplinary.  By using a local network for reference swapping, these cross-disciplinary atypical combinations will not be identified as such.  At the fundamental level, what is the relationship between novelty and interdisciplinary?  Clearly they are not empirically independent of each other, but what about their conceptual relationship?  Should we consider novelty as something net of interdisciplinary, such that a local network is appropriate in order to clear out interdisciplinarity, or should we consider novelty as something that is related with interdisciplinarity, such that a global network is needed for not missing cross-disciplinary unusual combinations.  I would suggest the authors do develop a clear conceptualization of novelty before claiming that local network is appropriate.  In addition, it might be interesting to separate within-discipline and cross-discipline novelty and examine their effects on citation impact.}

This is a very important point that is also brought up by Reviewer 1 so we would like to reiterate that our approach does not alter the original references cited by the authors of the articles we assemble into datasets. We u

\emph{Figure 2 is informative, it shows that when using local network instead of global network, the Uzzi finding still holds for the whole WoS database but not for applied physics, immunology, or metabolism.  However, there are two possible explanations: (1) Uzzi's findings are not universal across fields, and (2) difference in using local vs. global networks.  It would be helpful to replicate the same plots using Uzzi's global network approach and single out which factor made the difference.}

\emph{On page 2, ?In addition, under this random model, a reference cited many times in a given year is selected with the same probability as a reference cited only once, which appears inconsistent with the power law or lognormal citation distributions described in the literature.?  I do not quite understand this.  In Uzzi's reference swapping, for each references, its total number of forward citations is preserved, so at the system level, a reference with fewer citations does have a smaller probability of being swapped.  So I do not exactly understand this criticism.}

Our apologies for not being clear. In examining the shuffling code of Uzzi (kindly shared by Satyam Mukkherjee and Ben Jones), we realized that the choice of substitutions was restricted to the set rather than the multi-set of eligible references. The reciprocal substitution approach ensures that the total number of references is still preserved after shuffling but selection is equiprobable. The points below may serve to illustrate our point.

a) Consider a toy dataset slice of 5 publications all published in the same year. Each of these publications cites 4 references, thus, 20 citations. Of these, one is cited in each of the publications (thus cited 5 times) and the remaining 15 are cited once in total. During citation shuffling (i)  in our approach. the probability of selecting x would be 5/20. In Uzzi it would be 1/20. Further Uzzi's code allows 20 successive substitution attempts if the original reference is selected. Thus, it favors creating diversity in the expected values.

b) In a local or a global network it does not make sense to treat a highly cited reference as equiprobable with a reference cited only once.

c) We should add a section on Jim's analysis showing 2.5\% of the references are affected- for a distribution in which the top 1-2\% qualify as highly cited then it becomes important.

\end{document}

### 2019-07-14 rebuttal.tex
please see everything in blue text

@@
 \documentclass[11pt, oneside]{article}   	% use "amsart" instead of "article" for AMSLaTeX format
-\usepackage{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
+\usepackage{geometry,color}                		% See geometry.pdf to learn the layout options. There are lots.
 \geometry{letterpaper}                   		% ... or a4paper or a5paper or ... 
@@
 
-\title{Brief Article}
-\author{The Author}
+%\title{Brief Article}
+%\author{The Author}
 %\date{}							% Activate to display a given date or no date
@@
 \begin{document}
-\maketitle
+%\maketitle
 
+\noindent
 The Editor\\
@@
 
+\textcolor{blue}{
+George - I think that it's not  true that we don't question the assumption that
+conventionality and innovativeness can be detected by calculating journal co-occurrences.
+I realize it's not the most important thing to discuss, but perhaps we should not leave that
+statement completely alone.}
+
 The reviewer is correct.
-We do not question the database- the Web of Science is sufficiently comprehensive to conduct such studies.
+We do not question the database--the Web of Science is sufficiently comprehensive to conduct such studies.
 We are puzzled by the comment about the technical contribution being marginal.
@@
 We have not changed the title.
-The methodological concern only has relevance in the larger context of co-citaton analysis and differences between disciplinary citation practice.
+The methodological concern only has relevance in the larger context of co-citation analysis and differences between disciplinary citation practice.
 
@@
 On the surface- it would make sense- don't substitute an anthropology journal for a physics journal.
-But deeper down, it may not make sense because there is no agreed upon way to decide what is ?local' and what isn't.
+But deeper down, it may not make sense because there is no agreed upon way to decide what is `local' and what isn't.
 Does one use word searches to define fields (as suggested by the authors)?
@@
 However, we would like to point out that a keyword search defines a set of articles without modifying the references cited in those publications.
-In out approach, the expected values for z-score calculations are calculated from those references cited by the authors of those articles instead of the indiscriminate substitutions of Uzzi.
+In our approach, the expected values for z-score calculations are calculated from those references cited by the authors of those articles instead of the indiscriminate substitutions of Uzzi.
 An argument for our approach is the K-L measurements showing less model misspecification in our approach compared to Uzzi's.
+
+\textcolor{blue}{George, I think it would be good to say that we do not assert that our model/method is unflawed -- in fact we acknowledge this explicitly, and will make that point even stronger.
+But we do note that we establish a reduction in model misspecification in using our model compared to Uzzi et al.'s model, and so even if our model is flawed (and it will be), it is less flawed than Uzzi's.
+}
 
@@
 Provide more concrete evidence that one approach is better than the other.
-For example- use Uzzi's approach and your new approach to nominate the ?high innovative' and ?high conventional' papers.
+For example- use Uzzi's approach and your new approach to nominate the `high innovative' and `high conventional' papers.
 Then focus on differences in these sets- the papers that are HI-using the old method vs.
@@
 
-Again, we thank the reviewer.
-We have revised the text of our manuscript to make more clear that we're not endorsing this approach.
-[Tandy please insert your points here..].
-We're not trying to identify innovative papers- our point is more that the proxy measure for impact suggests that HC flavored with HI (as defined by Uzzi) is not a universal feature of highly cited papers.
-A mixed methods approach where qualitative judgment is brought to bear on the quantitative results as per (Ioannidis, Klavans, and Boyack) is an excellent suggestion but we think it's beyond the scope of this manuscript.
+Again, we thank the reviewer. We have revised the text of our manuscript to make it more clear that we're not endorsing this approach. 
+\textcolor{blue}{An important point in our paper (which we clearly didn't make strongly
+enough)  is that we are not
+proposing that our model (which restricts the substitutions to a defined citation network) be used to
+define conventionality and innovativeness.
+Instead, our point is not to propose a new model, but rather to show that a small change in the model results in a reduction in model misspecification and presents very different trends.
+Hence, any conclusions based on Uzzi's model that are not
+also seen when analyzing the WoS using our model are likely to be the result of 
+model misspecification.
+[Tandy please insert your points here..].}  We're not trying to identify innovative papers--our point is more that the proxy measure for impact suggests that HC flavored with HI (as defined by Uzzi) is not a universal feature of highly cited papers.
+A mixed methods approach where qualitative judgment is brought to bear on the quantitative results as per (Ioannidis, Klavans, and Boyack) is an excellent suggestion, but we think it's beyond the scope of this manuscript.
 
@@
 
+\textcolor{blue}{George,  think it would good to re-iterate that we are not proposing a new model be used in subsequent studies.
+We are just showing a dramatic reduction in model misspecification by restricting to local networks, and that trends shown for our model (which by K-L divergences is superior to Uzzi's model) are very different from what were seen for Uzzi's model.
+}
+
 \emph{Figure 2 is informative, it shows that when using local network instead of global network, the Uzzi finding still holds for the whole WoS database but not for applied physics, immunology, or metabolism.
@@
 
-\emph{On page 2, ?In addition, under this random model, a reference cited many times in a given year is selected with the same probability as a reference cited only once, which appears inconsistent with the power law or lognormal citation distributions described in the literature.?
-I do not quite understand this.
+\emph{On page 2, `In addition, under this random model, a reference cited many times in a given year is selected with the same probability as a reference cited only once, which appears inconsistent with the power law or lognormal citation distributions described in the literature.'  I do not quite understand this.
 In Uzzi's reference swapping, for each references, its total number of forward citations is preserved, so at the system level, a reference with fewer citations does have a smaller probability of being swapped.
@@
 Each of these publications cites 4 references, thus, 20 citations.
-Of these, one is cited in each of the publications (thus cited 5 times) and the remaining 15 are cited once in total.
-During citation shuffling (i)  in our approach.
-the probability of selecting x would be 5/20.
+Of these, one (which we will call $x$) is cited in each of the publications (thus cited 5 times) and the remaining 15 are cited once in total.
+During citation shuffling (i)  in our approach, the probability of selecting $x$ would be 5/20.
 In Uzzi it would be 1/20.
-Further Uzzi's code allows 20 successive substitution attempts if the original reference is selected.
+Further, Uzzi's code allows 20 successive substitution attempts if the original reference is selected.
 Thus, it favors creating diversity in the expected values.

### 2019-07-15 rebuttal.tex
please see everything in blue text

@@
 \textcolor{blue}{
-George - I think that it's not  true that we don't question the assumption that
-conventionality and innovativeness can be detected by calculating journal co-occurrences.
-I realize it's not the most important thing to discuss, but perhaps we should not leave that
-statement completely alone.}
-
-The reviewer is correct.
-We do not question the database--the Web of Science is sufficiently comprehensive to conduct such studies.
-We are puzzled by the comment about the technical contribution being marginal.
-It is true that Uzzi was published five years ago but, with the exception of Boyack and Klavans (2014), it seems to have been uncritically cited over 175 times since.
+The reviewer is correct that we do not question the database--the Web of Science is sufficiently comprehensive to conduct such studies, and also correct about our statement that 
+random substitutions should not be made without consideration of  disciplinary context.
+However,  we certainly do not endorse  the assumption that  ``conventionality  and innovativeness can be detected by calculating journal co-occurrences", but instead we point out the 
+challenges in using co-citation analysis in assessing these properties.
+We agree that our study is a focused methodological critique.
+However,  we do not agree that the contribution is marginal.
+% we are puzzled by the comment about the technical contribution being marginal. 
+It is true that Uzzi was published five years ago,  but, with the exception of Boyack and Klavans (2014), it seems to have been uncritically cited over 175 times since its publication.}
 
@@
 
+\textcolor{blue}{
 We have revised the text to reflect these suggestions.
@@
 The methodological concern only has relevance in the larger context of co-citation analysis and differences between disciplinary citation practice.
+}
 
@@
 
-The reviewer makes very valid points.
-In citing Boyack and Klavans (2014), we also reiterate that there are journal effects that we do not investigate in this study.
+\textcolor{blue}{
+The reviewer makes two very valid points, the first being that we should acknowledge that the
+model we use is also flawed, and the second having to do with challenges in using co-citation analysis defined by journals in characterizing which publications are conventional and/or innovative.
+In response to the first point,
+we do not assert that our model/method is unflawed -- in fact we acknowledge this explicitly, and have
+revised the paper to make that point even stronger.
+But we do note that we establish a reduction in model misspecification in using our model compared to Uzzi et al.'s model (as indicated by the Kullback-Liebler divergence reducing), and so even though our model will also be flawed (and it will be), it is less flawed than Uzzi's.
+With respect to the second point, 
+in citing Boyack and Klavans (2014), we also reiterate that there are journal effects that we do not investigate in this study.
 However, we would like to point out that a keyword search defines a set of articles without modifying the references cited in those publications.
-In our approach, the expected values for z-score calculations are calculated from those references cited by the authors of those articles instead of the indiscriminate substitutions of Uzzi.
-An argument for our approach is the K-L measurements showing less model misspecification in our approach compared to Uzzi's.
-
-\textcolor{blue}{George, I think it would be good to say that we do not assert that our model/method is unflawed -- in fact we acknowledge this explicitly, and will make that point even stronger.
-But we do note that we establish a reduction in model misspecification in using our model compared to Uzzi et al.'s model, and so even if our model is flawed (and it will be), it is less flawed than Uzzi's.
-}
+In our approach, the expected values for z-score calculations are calculated from those references cited by the authors of those articles instead of the indiscriminate substitutions of Uzzi. }
+%An argument for our approach is the K-L measurements showing less model misspecification in our approach compared to Uzzi's.
 
@@
 
-Again, we thank the reviewer. We have revised the text of our manuscript to make it more clear that we're not endorsing this approach. 
-\textcolor{blue}{An important point in our paper (which we clearly didn't make strongly
-enough)  is that we are not
-proposing that our model (which restricts the substitutions to a defined citation network) be used to
-define conventionality and innovativeness.
-Instead, our point is not to propose a new model, but rather to show that a small change in the model results in a reduction in model misspecification and presents very different trends.
+\textcolor{blue}{
+Again, we thank the reviewer for this interesting suggestion. 
+%An important point in our paper (which we clearly didn't make strongly enough)  is that we are not proposing that our model (which restricts the substitutions to a defined citation network) be used to define conventionality and innovativeness.
+However, the objective of this study was not to propose a new model, but rather to show that a small change in the  Uzzi model results in a reduction in model misspecification and presents very different trends.
 Hence, any conclusions based on Uzzi's model that are not
-also seen when analyzing the WoS using our model are likely to be the result of 
+also seen  using our model are likely to be the result of 
 model misspecification.
-[Tandy please insert your points here..].}  We're not trying to identify innovative papers--our point is more that the proxy measure for impact suggests that HC flavored with HI (as defined by Uzzi) is not a universal feature of highly cited papers.
-A mixed methods approach where qualitative judgment is brought to bear on the quantitative results as per (Ioannidis, Klavans, and Boyack) is an excellent suggestion, but we think it's beyond the scope of this manuscript.
-
+(Equally importantly, because as this reviewer points out our model is also likely flawed, that does not
+mean that trends found using our model are valid!)
+Moreover, we are not trying to identify innovative papers--our point is more that the proxy measure for impact suggests that HC flavored with HI (as defined by Uzzi) is not a universal feature of highly cited papers.
+Finally, we would argue that
+a mixed methods approach where qualitative judgment is brought to bear on the quantitative results as per (Ioannidis, Klavans, and Boyack) is an excellent suggestion, but we think it's beyond the scope of this manuscript.
+ }
 \section{Reviewer 2}
@@
 
+\textcolor{blue}{
 Thank you. 
+}
 
-\emph{However, one major concern is about whether a local network is indeed more appropriate than a global network.
-The authors did give very convincing arguments.
+\emph{However, one major concern is about whether a local network is indeed more appropriate than a global network.  The authors did give very convincing arguments. }
+
+\textcolor{blue}{We agree that there are limitations to local networks as well as to global networks, but as our study shows that model misspecification is dramatically reduced by restricting substitutions to the local network, we feel that it is reasonable to claim that local networks are, overall, more appropriate
+than global networks.}
+
+\emph{
 However, it can be argued that most atypical combinations are cross-disciplinary.
@@
 
-This is a very important point that is also brought up by Reviewer 1 so we would like to reiterate that our approach does not alter the original references cited by the authors of the articles we assemble into datasets.
-We u
-
-\textcolor{blue}{George,  think it would good to re-iterate that we are not proposing a new model be used in subsequent studies.
-We are just showing a dramatic reduction in model misspecification by restricting to local networks, and that trends shown for our model (which by K-L divergences is superior to Uzzi's model) are very different from what were seen for Uzzi's model.
-}
+\textcolor{blue}{
+We thank the reviewer for these interesting and thought provoking points.
+To respond to this, we  wish to elaborate on how we define the local networks, and hence
+which substitutions are allowed.
+The way we defined the local network is that it contains all papers that are cited by
+any paper  recognized by the keyword search. 
+Thus, the local network explicitly includes papers that are from multiple disciplines,
+while still being restricted to those papers that are cited.
+(In contrast, if we had defined the local network to only be papers that were published in physics journals, this would have indeed prevented interdisciplinary citations, and most likely have produced a very different outcome.)
+In other words, 
+our approach does not alter the original references cited by the authors of the articles we assemble into datasets. We u...}
 
@@
 
+\textcolor{blue}{
 Our apologies for not being clear.
@@
 The reciprocal substitution approach ensures that the total number of references is still preserved after shuffling but selection is equiprobable.
-The points below may serve to illustrate our point.
+The points below may serve to illustrate our point.}
 
+\textcolor{blue}{
 a) Consider a toy dataset slice of 5 publications all published in the same year.
@@
 Thus, it favors creating diversity in the expected values.
+}
 
-b) In a local or a global network it does not make sense to treat a highly cited reference as equiprobable with a reference cited only once.
+\textcolor{blue}{
+b) In a local or a global network it does not make sense to treat a highly cited reference as equiprobable with a reference cited only once. }
 
+\textcolor{blue}{
 c) We should add a section on Jim's analysis showing 2.5\% of the references are affected- for a distribution in which the top 1-2\% qualify as highly cited then it becomes important.
-
+}
 \end{document}

### 2019-07-15 rebuttal.tex
next round of tweaks

--- 2019-07-14 rebuttal.tex
@@
 \usepackage{amssymb}
-
+\usepackage{parskip}
+%\setlength\parindent{0pt}
 %SetFonts
@@
 
-\noindent
-The Editor\\
-Quantitative Science Studies\\
+The Editor
+Quantitative Science Studies
 
-We thank the reviewers for their constructive critiques, which we have attempted to respond to in a systematic manner below and in a revision of the manuscript.
+We thank the reviewers for their constructive critiques as well as their time, effort, and professional courtesy in reviewing our manuscript.
+We have attempted to respond  in a systematic manner both below and in a revision of the manuscript.
 
@@
 also went through a variety of sensitivity analyses to show that the results held across different disciplinary fields (they used standard definitions of disciplines).}
+
+We largely agree but would add that since journal pairs are computed across a dataset, frequently occurring journal pairs can contain both frequently and rarely co-cited reference pairs.
+The sensitivity analyses of Uzzi are challenged in Boyack and Klavans, 2014.
 
@@
 
-\textcolor{blue}{
-George - I think that it's not  true that we don't question the assumption that
-conventionality and innovativeness can be detected by calculating journal co-occurrences.
-I realize it's not the most important thing to discuss, but perhaps we should not leave that
-statement completely alone.}
+The reviewer is correct that we do not question the database--the Web of Science is sufficiently comprehensive to conduct such studies, and is also correct about our statement that  random substitutions should not be made without consideration of  disciplinary context.
+However,  we certainly do not endorse  the assumption that  ``conventionality  and innovativeness can be detected by calculating journal co-occurrences".
+Instead, we point out the challenges in using co-citation analysis in assessing these properties.
 
-The reviewer is correct.
-We do not question the database--the Web of Science is sufficiently comprehensive to conduct such studies.
-We are puzzled by the comment about the technical contribution being marginal.
-It is true that Uzzi was published five years ago but, with the exception of Boyack and Klavans (2014), it seems to have been uncritically cited over 175 times since.
+We agree that our study is a focused methodological critique.
+However, we do not agree that its contribution is marginal merely because Uzzi was published five years ago.
+By that standard, a critical consideration or extension of Small and Marshakova could also be considered marginal, With the exception of a challenge by Boyack and Klavans (2014), Uzzi seems to have been cited rather uncritically over 175 times since its publication placing it in the top 1-2\% of papers and we think that our work has value in identifying a significant weakness inherent in its approach.
 
@@
 We have revised the text to reflect these suggestions.
-We have not changed the title.
-The methodological concern only has relevance in the larger context of co-citation analysis and differences between disciplinary citation practice.
+However, we would like to comment that the methodological issue we elucidate in the paper only has relevance in the larger context of co-citation analysis and differences in citation practice between disciplines.
+Thus, we are unwilling to discard mention of the larger context.
+We agree that this manuscript is not a study in semantics but the local networks we study are semantically themed.
+We respectfully disagree that the title is misleading.
 
@@
 
-The reviewer makes very valid points.
-In citing Boyack and Klavans (2014), we also reiterate that there are journal effects that we do not investigate in this study.
-However, we would like to point out that a keyword search defines a set of articles without modifying the references cited in those publications.
-In our approach, the expected values for z-score calculations are calculated from those references cited by the authors of those articles instead of the indiscriminate substitutions of Uzzi.
-An argument for our approach is the K-L measurements showing less model misspecification in our approach compared to Uzzi's.
+The reviewer makes two very valid points, the first being that we should acknowledge that the model we use is also flawed, and the second having to do with challenges in using co-citation analysis defined by journals in characterizing which publications are conventional and/or innovative.
+In response to the first point, we do not assert that our model/method is perfect -- in fact we acknowledge this explicitly, and have revised the paper to make that point even stronger.
+But we do note that we establish a reduction in model misspecification when using our model compared to Uzzi et al.'s model (as indicated by a reduction in the Kullback-Leibler divergence), and so even though our model will also be flawed (and it will be), it is less flawed than Uzzi's.
+With respect to the second point, we have reiterated (in citing Boyack and Klavans, 2014) that there are journal effects that we do not investigate in this study but these are offset slightly by the use of keyword searches to define a network.
 
-\textcolor{blue}{George, I think it would be good to say that we do not assert that our model/method is unflawed -- in fact we acknowledge this explicitly, and will make that point even stronger.
-But we do note that we establish a reduction in model misspecification in using our model compared to Uzzi et al.'s model, and so even if our model is flawed (and it will be), it is less flawed than Uzzi's.
-}
+A keyword search defines a set of articles without modifying the references cited in those publications.
+These references were selected by the authors of the articles and while they are typically dominated by the closest discipline, they can be drawn from any discipline (Fig 2 and we as we also cite in our manuscript: Garfield, 1979; Klavans \& Boyack, 2017; Moed, 2010; Wallace, Lariviere, \& Gingras, 2012).
+In our approach, the expected values for z-score calculations are calculated from those references cited by the authors of those articles in contrast to the indiscriminate substitutions of Uzzi.
 
@@
 
-Again, we thank the reviewer. We have revised the text of our manuscript to make it more clear that we're not endorsing this approach. 
-\textcolor{blue}{An important point in our paper (which we clearly didn't make strongly
-enough)  is that we are not
-proposing that our model (which restricts the substitutions to a defined citation network) be used to
-define conventionality and innovativeness.
-Instead, our point is not to propose a new model, but rather to show that a small change in the model results in a reduction in model misspecification and presents very different trends.
-Hence, any conclusions based on Uzzi's model that are not
-also seen when analyzing the WoS using our model are likely to be the result of 
-model misspecification.
-[Tandy please insert your points here..].}  We're not trying to identify innovative papers--our point is more that the proxy measure for impact suggests that HC flavored with HI (as defined by Uzzi) is not a universal feature of highly cited papers.
-A mixed methods approach where qualitative judgment is brought to bear on the quantitative results as per (Ioannidis, Klavans, and Boyack) is an excellent suggestion, but we think it's beyond the scope of this manuscript.
+Again, we thank the reviewer for this interesting suggestion.
+However, the objective of this study was to demonstrate that a small change in the  Uzzi model results in a reduction in model misspecification and presents very different trends.
+Hence, any conclusions based on Uzzi's model that are not also seen  using our model are likely to be the result of  model misspecification.
+(Equally importantly, since the reviewer points out our model is also likely flawed, it does not mean that trends found using our model are valid!) Moreover, we are not trying to identify innovative papers--our point is more that the proxy measure for impact suggests that HC flavored with HI (as defined by Uzzi) is not a universal feature of highly cited papers.
+Finally, we would argue that a mixed methods approach where qualitative judgment is brought to bear on quantitative results as per (Ioannidis, Klavans, and Boyack) is an excellent suggestion, but we think it's beyond the scope of this manuscript.
 
@@
 
-\emph{However, one major concern is about whether a local network is indeed more appropriate than a global network.
-The authors did give very convincing arguments.
-However, it can be argued that most atypical combinations are cross-disciplinary.
+\emph{However, one major concern is about whether a local network is indeed more appropriate than a global network.  The authors did give very convincing arguments. }
+
+We agree that there are limitations to local networks as well as to global networks, but as our study shows that model misspecification is dramatically reduced by restricting substitutions to the local network, we feel that it is reasonable to claim that local networks are, overall, more appropriate
+than global networks.
+
+\emph{However, it can be argued that most atypical combinations are cross-disciplinary.
 By using a local network for reference swapping, these cross-disciplinary atypical combinations will not be identified as such.
@@
 
-This is a very important point that is also brought up by Reviewer 1 so we would like to reiterate that our approach does not alter the original references cited by the authors of the articles we assemble into datasets.
-We u
-
-\textcolor{blue}{George,  think it would good to re-iterate that we are not proposing a new model be used in subsequent studies.
-We are just showing a dramatic reduction in model misspecification by restricting to local networks, and that trends shown for our model (which by K-L divergences is superior to Uzzi's model) are very different from what were seen for Uzzi's model.
-}
+We thank the reviewer for these interesting and thought provoking points.
+To respond to this, we  wish to elaborate on how we define the local networks, and hence which substitutions are allowed.
+The way we defined the local network is that it contains all papers that are cited by any paper recognized by the keyword search.
+Thus, \emph{the local network explicitly includes papers that are from multiple disciplines}, while still being restricted to those papers that are cited.
+In contrast, if we had defined the local network to papers that citing references from a single discipline, it would have indeed prevented interdisciplinary citations, and most likely have produced a very different outcome.
+In other words, our approach does not alter the original references cited by the authors of the articles we assemble into datasets (we raise this point in our response to Reviewer 1 as well).
 
@@
 
+The figure below was included in an earlier version of this manuscript submitted to another journal and was criticized for being confusing.
+It specifically addresses the reviewer's point.
+Thus, both factors are in play- there is a difference between local and global.
+Disciplines can be different from each other.
+
 \emph{On page 2, `In addition, under this random model, a reference cited many times in a given year is selected with the same probability as a reference cited only once, which appears inconsistent with the power law or lognormal citation distributions described in the literature.'  I do not quite understand this.
@@
 Our apologies for not being clear.
-In examining the shuffling code of Uzzi (kindly shared by Satyam Mukkherjee and Ben Jones), we realized that the choice of substitutions was restricted to the set rather than the multi-set of eligible references.
-The reciprocal substitution approach ensures that the total number of references is still preserved after shuffling but selection is equiprobable.
-The points below may serve to illustrate our point.
+In examining the citation shuffling code of Uzzi (kindly shared by Satyam Mukherjee and Ben Jones), we realized that the choice of substitutions was restricted to the set rather than the multi-set of eligible references.
+Their reciprocal substitution approach built-in to their code ensures that the total number of references is still preserved after shuffling but selection is equiprobable.
+In other words, Uzzi's algorithm systematically shuffles every reference but replacements are selected from the set, e.g., a,b,c,d...
+rather than the multi-set, e.g., aaaa, b, ccc, dd...
+of eligible references.
 
@@
 During citation shuffling (i)  in our approach, the probability of selecting $x$ would be 5/20.
-In Uzzi it would be 1/20.
-Further, Uzzi's code allows 20 successive substitution attempts if the original reference is selected.
-Thus, it favors creating diversity in the expected values.
+In Uzzi it would be 1/15.
+Further, Uzzi's code allows 20 successive substitution attempts if the original reference is selected as a substitute.
+Our code permits such a replacement.
 

### 2019-07-15 rebuttal.tex
tweaks

@@
 
-We largely agree but would add that since journal pairs are computed across a dataset, frequently occurring journal pairs can contain both frequently and rarely co-cited reference pairs.
-The sensitivity analyses of Uzzi are challenged in Boyack and Klavans, 2014.
+We largely concur but would like to add that since journal pairs are computed across the dataset being studied, frequently occurring journal pairs can be a composite of both frequently and rarely co-cited reference pairs.
+Secondly, the sensitivity analyses of Uzzi are challenged in Boyack and Klavans, 2014, to wit,``However, their detailed results showed that the N+C+ bin in the 2x2 matrix had the highest probability of containing a hit paper for only 64.4\% of 243 WoS subject categories.''
 
@@
 
-We agree that our study is a focused methodological critique.
+We agree that our study is centered around a focused methodological critique.
+One that has important implications for whether co-citation analysis can be used to infer novelty and conventionality.
 However, we do not agree that its contribution is marginal merely because Uzzi was published five years ago.
-By that standard, a critical consideration or extension of Small and Marshakova could also be considered marginal, With the exception of a challenge by Boyack and Klavans (2014), Uzzi seems to have been cited rather uncritically over 175 times since its publication placing it in the top 1-2\% of papers and we think that our work has value in identifying a significant weakness inherent in its approach.
+By this standard, a critical consideration or extension of Small and Marshakova who formulated the concept of co-citation could also be considered marginal, With the exception of a challenge by Boyack and Klavans (2014), Uzzi seems to have been cited (rather uncritically) over 175 times since its publication placing it in the top 1-2\% of papers and we think that our work has value in identifying a significant weakness inherent in its approach.
 
@@
 
-We have revised the text to reflect these suggestions.
+We have revised the text to be considerate of these suggestions, which we value.
 However, we would like to comment that the methodological issue we elucidate in the paper only has relevance in the larger context of co-citation analysis and differences in citation practice between disciplines.
-Thus, we are unwilling to discard mention of the larger context.
-We agree that this manuscript is not a study in semantics but the local networks we study are semantically themed.
+Thus, we are unwilling to discard placing the work in a larger context.
+We agree that this manuscript is not a study in semantics, indeed we do not make such an assertion.
+However, the local networks we study are semantically themed.
 We respectfully disagree that the title is misleading.
@@
 A keyword search defines a set of articles without modifying the references cited in those publications.
-These references were selected by the authors of the articles and while they are typically dominated by the closest discipline, they can be drawn from any discipline (Fig 2 and we as we also cite in our manuscript: Garfield, 1979; Klavans \& Boyack, 2017; Moed, 2010; Wallace, Lariviere, \& Gingras, 2012).
-In our approach, the expected values for z-score calculations are calculated from those references cited by the authors of those articles in contrast to the indiscriminate substitutions of Uzzi.
+These references were selected by the authors of the articles and while they are typically dominated by the closest discipline, they can be drawn from any discipline (as we also cite in our manuscript: Garfield, 1979; Klavans \& Boyack, 2017; Moed, 2010; Wallace, Lariviere, \& Gingras, 2012).
+In our approach, the expected values for z-score calculations are calculated from references cited by the authors of those articles in contrast to the indiscriminate substitutions of Uzzi.
+Thus, Science and Nature are accounted for without the baggage of the articles in them that are irrelevant to the network being studied.
 
@@
 Each of these publications cites 4 references, thus, 20 citations.
+For simplicity, we will assume that all of these references were published in the same year.
 Of these, one (which we will call $x$) is cited in each of the publications (thus cited 5 times) and the remaining 15 are cited once in total.
@@
 In Uzzi it would be 1/15.
-Further, Uzzi's code allows 20 successive substitution attempts if the original reference is selected as a substitute.
-Our code permits such a replacement.
+Further, Uzzi's code enforces 20 successive substitution attempts if the original reference is selected as a substitute.
+Our code allows such a replacement.
 

### 2019-07-15 rebuttal.tex
added fig and table

@@
 \usepackage{parskip}
+\usepackage{verbatim}
+\usepackage{graphicx}
 %\setlength\parindent{0pt}
@@
 
-The Editor
+The Editor\\
 Quantitative Science Studies
 
+Dear Dr. Waltman:
+
+Please find below, our response to critique.
 We thank the reviewers for their constructive critiques as well as their time, effort, and professional courtesy in reviewing our manuscript.
-We have attempted to respond  in a systematic manner both below and in a revision of the manuscript.
+We have attempted to respond  in a systematic manner both below and in a revision of the manuscript (attached).
+
+Sincerely
+
+George Chacko
 
@@
 We largely concur but would like to add that since journal pairs are computed across the dataset being studied, frequently occurring journal pairs can be a composite of both frequently and rarely co-cited reference pairs.
+This is also true for less frequently cited journal pairs.
+Thus, collapsing reference pairs into journal pairs imposes a cost on resolution but it reduces $\sim10^{14}$ possible reference pairs to ~$\sim10^7$ possible combinations, which are more easily analyzed.
 Secondly, the sensitivity analyses of Uzzi are challenged in Boyack and Klavans, 2014, to wit,``However, their detailed results showed that the N+C+ bin in the 2x2 matrix had the highest probability of containing a hit paper for only 64.4\% of 243 WoS subject categories.''
@@
 However,  we certainly do not endorse  the assumption that  ``conventionality  and innovativeness can be detected by calculating journal co-occurrences".
-Instead, we point out the challenges in using co-citation analysis in assessing these properties.
+Instead, we point out the challenges in using co-citation analysis to assess these properties.
 
@@
 However, we do not agree that its contribution is marginal merely because Uzzi was published five years ago.
-By this standard, a critical consideration or extension of Small and Marshakova who formulated the concept of co-citation could also be considered marginal, With the exception of a challenge by Boyack and Klavans (2014), Uzzi seems to have been cited (rather uncritically) over 175 times since its publication placing it in the top 1-2\% of papers and we think that our work has value in identifying a significant weakness inherent in its approach.
+By this standard, a critical consideration or extension of Small (1973) and Marshakova-Shaikevich (1973) who formulated the concept of co-citation could also be considered marginal, With the exception of a challenge by Boyack and Klavans (2014), Uzzi seems to have been cited rather uncritically over 175 times since its publication, which places it in the top 1-2\% of papers.
+We think that our work has value in identifying a significant weakness inherent in its approach.
 
@@
 
-We have revised the text to be considerate of these suggestions, which we value.
+We have revised the text to be considerate of these valuable suggestions.
 However, we would like to comment that the methodological issue we elucidate in the paper only has relevance in the larger context of co-citation analysis and differences in citation practice between disciplines.
-Thus, we are unwilling to discard placing the work in a larger context.
+Thus, we are unwilling to discard the discussion of context.
 We agree that this manuscript is not a study in semantics, indeed we do not make such an assertion.
@@
 In response to the first point, we do not assert that our model/method is perfect -- in fact we acknowledge this explicitly, and have revised the paper to make that point even stronger.
-But we do note that we establish a reduction in model misspecification when using our model compared to Uzzi et al.'s model (as indicated by a reduction in the Kullback-Leibler divergence), and so even though our model will also be flawed (and it will be), it is less flawed than Uzzi's.
+But we do note that we establish a reduction in model misspecification when using our model compared to Uzzi et al.'s model (as indicated by a reduction in the Kullback-Leibler divergence).
+All models are imperfect but our model is significantly less flawed than Uzzi's.
 With respect to the second point, we have reiterated (in citing Boyack and Klavans, 2014) that there are journal effects that we do not investigate in this study but these are offset slightly by the use of keyword searches to define a network.
 
-A keyword search defines a set of articles without modifying the references cited in those publications.
-These references were selected by the authors of the articles and while they are typically dominated by the closest discipline, they can be drawn from any discipline (as we also cite in our manuscript: Garfield, 1979; Klavans \& Boyack, 2017; Moed, 2010; Wallace, Lariviere, \& Gingras, 2012).
+A keyword search defines a set of articles that are semantically themed and that may cross conventional disciplinary boundaries.
+The references in these articles were selected by the authors and while they are typically dominated by the closest discipline, they can be drawn from any discipline (as we also cite in our manuscript: Garfield, 1979; Klavans \& Boyack, 2017; Moed, 2010; Wallace, Lariviere, \& Gingras, 2012).
 In our approach, the expected values for z-score calculations are calculated from references cited by the authors of those articles in contrast to the indiscriminate substitutions of Uzzi.
-Thus, Science and Nature are accounted for without the baggage of the articles in them that are irrelevant to the network being studied.
+Thus, Science and Nature are accounted for without the distraction of articles in these multidisciplinary journals that are irrelevant to the network being studied.
 
@@
 Hence, any conclusions based on Uzzi's model that are not also seen  using our model are likely to be the result of  model misspecification.
-(Equally importantly, since the reviewer points out our model is also likely flawed, it does not mean that trends found using our model are valid!) Moreover, we are not trying to identify innovative papers--our point is more that the proxy measure for impact suggests that HC flavored with HI (as defined by Uzzi) is not a universal feature of highly cited papers.
-Finally, we would argue that a mixed methods approach where qualitative judgment is brought to bear on quantitative results as per (Ioannidis, Klavans, and Boyack) is an excellent suggestion, but we think it's beyond the scope of this manuscript.
+Equally important, since the reviewer points out our model is also likely flawed, it does not mean that trends found using our model are valid.
+Moreover, we are not trying to identify innovative papers--our point is more that the proxy measure for impact suggests that HC flavored with HI (as defined by Uzzi) is not a universal feature of highly cited papers and in some cases (immunology), impact may be largely driven by conventional thought.
+Finally, we comment that a mixed methods approach where qualitative judgment is brought to bear on quantitative results (Ioannidis, Klavans, and Boyack, 2014, Nature 10.1038/514561a) would be very valuable, but we think it's well beyond the scope of this manuscript.
+Similarly with citance analysis, a potentially valuable method.
 
@@
 We thank the reviewer for these interesting and thought provoking points.
-To respond to this, we  wish to elaborate on how we define the local networks, and hence which substitutions are allowed.
-The way we defined the local network is that it contains all papers that are cited by any paper recognized by the keyword search.
-Thus, \emph{the local network explicitly includes papers that are from multiple disciplines}, while still being restricted to those papers that are cited.
-In contrast, if we had defined the local network to papers that citing references from a single discipline, it would have indeed prevented interdisciplinary citations, and most likely have produced a very different outcome.
+To respond to them, we  wish to elaborate on how we define the local networks, and hence which substitutions are allowed.
+The way we defined the local network is that it contains all papers defined by a semantic theme and the papers that are cited by them.
+Thus, \emph{the local network explicitly includes papers that are from multiple disciplines}.
 In other words, our approach does not alter the original references cited by the authors of the articles we assemble into datasets (we raise this point in our response to Reviewer 1 as well).
+Thus, the local network does not exclude interdisciplinary work.
+It is the indiscriminate nature of the Uzzi model that causes us alarm.
+The point about within-discipline and cross-discipline novelty is very pertinent- we have referred to it in the revised Discussion and will follow up in a subsequent study.
+After we submitted the paper, we also analyzed the disciplinary content of both publications and references in our three datasets using the Web of Science research area classification.
+The results are provided below in the table and make our point that while the publications in the datasets are tightly aligned with their cognate disciplines, the references are less so.
+\newpage
+
+% latex table generated in R 3.5.3 by xtable 1.8-4 package
+% Mon Jul 15 10:24:29 2019
+\begin{table}[ht!]
+\centering
+\scalebox{0.8}{
+\begin{tabular}{|r rllrrrrrrr r|}
+  \hline
+ & yr & disc & type & lsb & ps & tech & ss & ah & sum\_cat & total\_distinct & top\_frac\_pcnt \\
+  \hline
+1 & 1985 & ap & pubs &   0 & 10298 & 4526 &   0 &   0 & 14824 & 10298 & 100.00 \\
+  2 & 1985 & ap & refs & 938 & 63123 & 25534 &  67 &   2 & 89664 & 73333 & 86.10 \\
+  3 & 1995 & ap & pubs &   0 & 21012 & 11561 &   0 &   0 & 32573 & 21012 & 100.00 \\
+  4 & 1995 & ap & refs & 1875 & 123457 & 59198 & 157 &  14 & 184701 & 144162 & 85.60 \\
+  5 & 2005 & ap & pubs &  38 & 35600 & 20811 &   0 &   0 & 56449 & 35600 & 100.00 \\
+  6 & 2005 & ap & refs & 13026 & 243739 & 138171 & 361 &  55 & 395352 & 301826 & 80.80 \\
+  \hline
+  7 & 1985 & imm & pubs & 9201 &   0 &  53 &   0 &   0 & 9254 & 9201 & 100.00 \\
+  8 & 1985 & imm & refs & 84765 & 1723 & 5474 & 100 &  11 & 92073 & 90798 & 93.40 \\
+  9 & 1995 & imm & pubs & 22191 & 184 & 796 &  33 &   7 & 23211 & 22759 & 97.50 \\
+  10 & 1995 & imm & refs & 282128 & 4219 & 20038 & 795 &  48 & 307228 & 303072 & 93.10 \\
+  11 & 2005 & imm & pubs & 27905 & 470 & 876 &  52 &   0 & 29303 & 28536 & 97.80 \\
+  12 & 2005 & imm & refs & 456842 & 9545 & 25612 & 1738 & 156 & 493893 & 483605 & 94.50 \\
+  \hline
+  13 & 1985 & metab & pubs & 64592 & 1597 & 2667 & 390 &  55 & 69301 & 67330 & 95.90 \\
+  14 & 1985 & metab & refs & 575890 & 25866 & 32641 & 4926 & 247 & 639570 & 620324 & 92.80 \\
+  15 & 1995 & metab & pubs & 97123 & 2707 & 4117 & 397 &  27 & 104371 & 100350 & 96.80 \\
+  16 & 1995 & metab & refs & 1001822 & 43916 & 59390 & 7150 & 302 & 1112580 & 1078575 & 92.90 \\
+  17 & 2005 & metab & pubs & 152148 & 11818 & 8214 & 666 &   3 & 172849 & 159897 & 95.20 \\
+  18 & 2005 & metab & refs & 1900163 & 176902 & 128639 & 19484 & 726 & 2225914 & 2099942 & 90.50 \\
+   \hline
+\end{tabular}
+}
+\caption{The disciplinary compositions of the three analytical datasets in our manuscript ap: applied physics, imm: immunology, and metab: metabolism were analyzed for the years, 1985, 1995, and 2005 using the Web of Science research area categorizations of \emph{lsb: lifesciences and biology, ps:physical sciences, tech: technology, ss: social sciences, and ah: arts \& humanities}.
+Both publications (pubs) and cited references (refs) were analyzed.
+The data show that while publications closely track their most similar research area, references have a greater cross disciplinary content- especially in the applied physics dataset but also for the other two.
+}
+\end{table}
+
+\newpage
 
@@
 
-The figure below was included in an earlier version of this manuscript submitted to another journal and was criticized for being confusing.
+The figure shown below was included in an earlier version of this manuscript submitted to another journal and was criticized for being confusing so we left it out in this version.
 It specifically addresses the reviewer's point.
-Thus, both factors are in play- there is a difference between local and global.
-Disciplines can be different from each other.
+Thus, both factors are in play (i) there is a difference when local and global networks are used to generate expected values (ii)  disciplines can be different from each other.
+We could include it as supplementary material since we're already over the 10 page limit.
+\newpage
+
+\begin{figure}
+\begin{tabular}{cc}
+\includegraphics[width=3in]{fig1a.pdf} & \includegraphics[width=3in]{fig1b.pdf}
+\\
+(a) & (b)  \\
+\end{tabular}
+\caption{Effect of Research Discipline,  Background Network,  and Citation Count on Conventionality and Novelty.
+Data are shown for the applied physics (18,305), immunology (21,917), metabolism (97,405) and WoS (476,288) networks for 1995; numbers in parentheses are the count of publications in each network.
+Subfigures (a) and (b): the x-axis show publications classified into percentile groups based on citation counts (e.g., Top 1 indicates those publications in the top 1\%) and the y-axis shows the percent of publications in each set that are HC or HN.
+Based on the selected background network, z-scores are computed for each disciplinary network; thus, \emph{imm} denotes the immunology network with immunology z-scores and \emph{imm\_wos} denotes the immunology network with z-scores from WoS z-scores.
+}
+\label{fig:Fig1}
+\end{figure}
+\newpage
 
@@
 Our apologies for not being clear.
-In examining the citation shuffling code of Uzzi (kindly shared by Satyam Mukherjee and Ben Jones), we realized that the choice of substitutions was restricted to the set rather than the multi-set of eligible references.
-Their reciprocal substitution approach built-in to their code ensures that the total number of references is still preserved after shuffling but selection is equiprobable.
-In other words, Uzzi's algorithm systematically shuffles every reference but replacements are selected from the set, e.g., a,b,c,d...
-rather than the multi-set, e.g., aaaa, b, ccc, dd...
-of eligible references.
+In examining the citation shuffling code of Uzzi kindly shared by Satyam Mukherjee and Ben Jones, we realized that the choice of substitutions was restricted to the set rather than the multi-set of eligible references.
+While their reciprocal substitution approach  ensures that the total number of references is still preserved after shuffling, selection of a substituent is equiprobable.
+In other words, Uzzi's algorithm systematically shuffles every reference but replacements are selected from the set \{a,b,c,d,e\} rather than the multi-set \{aaaa,b,ccc,dd,e\} of eligible references.
+This flies in the face of what we know about preferential attachment and citation practice.
 
-a) Consider a toy dataset slice of 5 publications all published in the same year.
+Uzzi's citation shuffling code is available on our Github site with permission from the authors.
+https://bit.ly/2xRsCCM.
+The key snippet below shows that the references stored in the object below constitute a set, which is selected from during substitution.
+
+\begin{verbatim}
+class Dset(dict):
+    def __init__(self, default=None):
+        self.default = default
+
+    def __getitem__(self, key):
+#        if not self.has_key(key):
+        if key not in self:
+            self[key] = set()
+        return dict.__getitem__(self, key)
+\end{verbatim}
+
+In either a local or a global network, it does not make sense to treat a highly cited reference as equiprobable with a reference cited only once.
+Consider a toy Web of Science dataset consisting of 5 publications all published in the same year.
 Each of these publications cites 4 references, thus, 20 citations.
@@
 Of these, one (which we will call $x$) is cited in each of the publications (thus cited 5 times) and the remaining 15 are cited once in total.
-During citation shuffling (i)  in our approach, the probability of selecting $x$ would be 5/20.
-In Uzzi it would be 1/15.
+During citation shuffling (i)  in our approach, the probability of selecting $x$ would be 5/20 or 1/4.
+In Uzzi it would be 1/16.
+The remaining 15 references in Uzzi would have a probability of 1/16, whereas in our model they would have a probability of 1/20.
 Further, Uzzi's code enforces 20 successive substitution attempts if the original reference is selected as a substitute.
-Our code allows such a replacement.
+Our code allows such a replacement without attempting to artificially enforce substitution with a different reference.
+Uzzi's code does not check for duplicate references as a result of shuffling, whereas we do and suppress it.
 
-b) In a local or a global network it does not make sense to treat a highly cited reference as equiprobable with a reference cited only once.
-
-c) We should add a section on Jim's analysis showing 2.5\% of the references are affected- for a distribution in which the top 1-2\% qualify as highly cited then it becomes important.
+We should add a section on Jim's analysis showing 2.5\% of the references are affected- for a distribution in which the top 1-2\% qualify as highly cited then it becomes important.
 

### 2019-07-15 rebuttal.tex
Minor revision

@@
 %\usepackage[parfill]{parskip}    		% Activate to begin paragraphs with an empty line rather than an indent
-\usepackage{graphicx}				% Use pdf, png, jpg, or epsÂ§ with pdflatex; use eps in DVI mode
+\usepackage{graphicx}				% Use pdf, png, jpg, or eps§ with pdflatex; use eps in DVI mode
 								% TeX will automatically convert eps --> pdf in pdflatex		
@@
 The title seems totally misleading.
-The article is about a very narrow methodological issue: whether the construction of Z-scores using a random substitution model is inherently biased vis-à-vis construction of Z-scores using a local substitution model.
+The article is about a very narrow methodological issue: whether the construction of Z-scores using a random substitution model is inherently biased vis-\'a-vis construction of Z-scores using a local substitution model.
 So if the authors choose to rewrite- please edit out all of the superfluous material.
@@
 It is the indiscriminate nature of the Uzzi model that causes us alarm.
+Our approach still identifies those interdisciplinary combinations that are atypical while confining the combinations to those which are relevant within a field.
 The point about within-discipline and cross-discipline novelty is very pertinent- we have referred to it in the revised Discussion and will follow up in a subsequent study.

### 2019-07-15 rebuttal.tex
Added content on sampling technique

@@
 
-We should add a section on Jim's analysis showing 2.5\% of the references are affected- for a distribution in which the top 1-2\% qualify as highly cited then it becomes important.
+The deviation of our results from those of Uzzi et al.
+can be due to a choice of data (local vs.
+global) or in sampling techniques.
+We compared our sampling approach with Uzzi's to understand how much of the difference was due to  the background data set versus the sampling technique.
+The categorization along the dimension of novelty depends on the sign of z-scores, and so we compared z-scores of each journal-pair with our sampling method versus Uzzi's while keeping  the data set constant.
+For the WoS and Applied Physics data sets, we found that 2.8\% and 4.0\% of journal pair z-scores changed sign, respectively.
+While this may induce a material effect, it was apparent that most of the differences in z-scores were due to the background data set and so we did not comment further in the submission on the differences in sampling techniques.
 

### 2019-07-15 rebuttal.tex
Minor revision

@@
 can be due to a choice of data (local vs.
-global) or in sampling techniques.
-We compared our sampling approach with Uzzi's to understand how much of the difference was due to  the background data set versus the sampling technique.
+global) or sampling technique, and so we compared our sampling approach with Uzzi's to understand how much of the difference was due to the background data set versus the sampling technique.
 The categorization along the dimension of novelty depends on the sign of z-scores, and so we compared z-scores of each journal-pair with our sampling method versus Uzzi's while keeping  the data set constant.
 For the WoS and Applied Physics data sets, we found that 2.8\% and 4.0\% of journal pair z-scores changed sign, respectively.
-While this may induce a material effect, it was apparent that most of the differences in z-scores were due to the background data set and so we did not comment further in the submission on the differences in sampling techniques.
+While this may induce a material effect on whether an article is deemed to be novel, it was apparent that most of the differences in z-scores were due to the background data set and so we did not comment further in the submission on the differences in sampling techniques.
 

### 2019-07-15 rebuttal.tex
minor

@@
 The deviation of our results from those of Uzzi et al.
-can be due to a choice of data (local vs.
+can be due to a choice of data set (local vs.
 global) or sampling technique, and so we compared our sampling approach with Uzzi's to understand how much of the difference was due to the background data set versus the sampling technique.
-The categorization along the dimension of novelty depends on the sign of z-scores, and so we compared z-scores of each journal-pair with our sampling method versus Uzzi's while keeping  the data set constant.
+The categorization of articles along the dimension of novelty depends on the sign of z-scores, and so we compared z-scores of each journal-pair with our sampling method versus Uzzi's while keeping  the data set constant.
 For the WoS and Applied Physics data sets, we found that 2.8\% and 4.0\% of journal pair z-scores changed sign, respectively.

### 2019-07-15 rebuttal.tex
post JB by GC

@@
 We have attempted to respond  in a systematic manner both below and in a revision of the manuscript (attached).
+For ease in reading, we have broken up the comments from reviewers into blocks of italicized text.
 
@@
 This is also true for less frequently cited journal pairs.
-Thus, collapsing reference pairs into journal pairs imposes a cost on resolution but it reduces $\sim10^{14}$ possible reference pairs to ~$\sim10^7$ possible combinations, which are more easily analyzed.
+Thus, collapsing reference pairs into journal pairs imposes a cost on resolution but it also reduces $\sim10^{14}$ possible reference pairs to ~$\sim10^7$ possible combinations, which are more easily analyzed.
 Secondly, the sensitivity analyses of Uzzi are challenged in Boyack and Klavans, 2014, to wit,``However, their detailed results showed that the N+C+ bin in the 2x2 matrix had the highest probability of containing a hit paper for only 64.4\% of 243 WoS subject categories.''
@@
 
+A keyword search defines a set of articles that are semantically themed and that may cross conventional disciplinary boundaries.
+The references in these articles were selected by the authors and while they are typically dominated by the closest discipline, they can be drawn from any discipline (as we also cite in our manuscript: Garfield, 1979; Klavans \& Boyack, 2017; Moed, 2010; Wallace, Lariviere, \& Gingras, 2012).
+In our approach, the expected values for z-score calculations are calculated from references cited by the authors of those articles in contrast to the indiscriminate substitutions of Uzzi.
+Thus, Science and Nature are accounted for without the distraction of articles in these multidisciplinary journals that are irrelevant to the network being studied.
+
 The reviewer makes two very valid points, the first being that we should acknowledge that the model we use is also flawed, and the second having to do with challenges in using co-citation analysis defined by journals in characterizing which publications are conventional and/or innovative.
@@
 With respect to the second point, we have reiterated (in citing Boyack and Klavans, 2014) that there are journal effects that we do not investigate in this study but these are offset slightly by the use of keyword searches to define a network.
-
-A keyword search defines a set of articles that are semantically themed and that may cross conventional disciplinary boundaries.
-The references in these articles were selected by the authors and while they are typically dominated by the closest discipline, they can be drawn from any discipline (as we also cite in our manuscript: Garfield, 1979; Klavans \& Boyack, 2017; Moed, 2010; Wallace, Lariviere, \& Gingras, 2012).
-In our approach, the expected values for z-score calculations are calculated from references cited by the authors of those articles in contrast to the indiscriminate substitutions of Uzzi.
-Thus, Science and Nature are accounted for without the distraction of articles in these multidisciplinary journals that are irrelevant to the network being studied.
 
@@
 Equally important, since the reviewer points out our model is also likely flawed, it does not mean that trends found using our model are valid.
-Moreover, we are not trying to identify innovative papers--our point is more that the proxy measure for impact suggests that HC flavored with HI (as defined by Uzzi) is not a universal feature of highly cited papers and in some cases (immunology), impact may be largely driven by conventional thought.
+Moreover, we are not trying to identify innovative papers--our point is more that the proxy measure for impact suggests that HC flavored with HI (as defined by Uzzi) is not a universal feature of highly cited papers and in some cases, immunology for example, impact may be largely driven by conventional thought.
 Finally, we comment that a mixed methods approach where qualitative judgment is brought to bear on quantitative results (Ioannidis, Klavans, and Boyack, 2014, Nature 10.1038/514561a) would be very valuable, but we think it's well beyond the scope of this manuscript.
@@
 To respond to them, we  wish to elaborate on how we define the local networks, and hence which substitutions are allowed.
-The way we defined the local network is that it contains all papers defined by a semantic theme and the papers that are cited by them.
+The way we defined the local network is that it contains all articles discovered by a semantic definition and the references cited by these articles.
 Thus, \emph{the local network explicitly includes papers that are from multiple disciplines}.
-In other words, our approach does not alter the original references cited by the authors of the articles we assemble into datasets (we raise this point in our response to Reviewer 1 as well).
+Our approach does not alter the original references cited by the authors of the articles we assemble into datasets (we raise this point in our response to Reviewer 1 as well).
 Thus, the local network does not exclude interdisciplinary work.
@@
 }
-\caption{The disciplinary compositions of the three analytical datasets in our manuscript ap: applied physics, imm: immunology, and metab: metabolism were analyzed for the years, 1985, 1995, and 2005 using the Web of Science research area categorizations of \emph{lsb: lifesciences and biology, ps:physical sciences, tech: technology, ss: social sciences, and ah: arts \& humanities}.
+\caption{The disciplinary compositions of the three analytical datasets in our manuscript ap: applied physics, imm: immunology, and metab: metabolism were analyzed for the years, 1985, 1995, and 2005 using the Web of Science research area categorizations of \emph{lsb: life sciences and biology, ps:physical sciences, tech: technology, ss: social sciences, and ah: arts \& humanities}.
 Both publications (pubs) and cited references (refs) were analyzed.
@@
 
-The figure shown below was included in an earlier version of this manuscript submitted to another journal and was criticized for being confusing so we left it out in this version.
+The figure shown below was included in an earlier version of this manuscript submitted to another journal and was criticized for being confusing so we left it out in the submission to QSS.
 It specifically addresses the reviewer's point.

### 2019-07-15 cocit_r.tex
made tweaks to article to reflect critique

@@
 \documentclass[NETN]{stjour}
-\usepackage{comment}
 
@@
 
-%ie.
-%\affiliation{1}{Gatsby Computational Neuroscience Unit, University
-%College London, London, United Kingdom}
-
-%\affiliation{2}{Another Department, Institution, City, Country}
-
-%ie
-%\affiliation{2}{Center for Studies in
-%Behavioral Neurobiology, Concordia University, Montreal, Quebec,
-%Canada}
-
 \correspondingauthor{George Chacko}{netelabs@nete.com}
-
-% ie,
-\correspondingauthor{George Chacko}{netelabs@nete.com}
-
 \keywords{co-citation analysis, bibliometrics, random graphs }
-
-%ie
-%\keywords{work, leisure, normative, microscopic,  reinforcement learning, economics}
 
@@
 Our study examines this question using  semantically-themed citation networks.
-We observe that trends reported to be true across the scientific literature do not hold for focused citation networks, and we conclude that co-citation analysis requires a contextual perspective.
+\textcolor{blue}{We observe that trends reported to be true across the scientific literature do not hold for focused citation networks, and we conclude that inferring novelty through co-citation analysis requires disciplinary context.}
 \end{abstract}
@@
 
-\cite{uzzi_atypical_2013} used a novel approach for co-citation analysis to characterize a subset of highly cited articles with respect to both novel and conventional combinations of prior research.
-The frequency with which references were co-cited  in 17.9 million articles and their cited references from the Web of Science (WoS) was calculated and expressed as journal pair frequencies (observed co-citation frequencies).
+\textcolor{blue} {In a novel approach, \cite{uzzi_atypical_2013} used co-citation analysis to characterize a subset of highly cited articles with respect to both novel and conventional combinations of prior research.} The frequency with which references were co-cited  in 17.9 million articles and their cited references from the Web of Science (WoS) was calculated and expressed as journal pair frequencies (observed co-citation frequencies).
 Expected co-citation values were generated from randomized networks using Monte Carlo simulations under a random graph model.
@@
 
-Key to the findings of Uzzi {\em et al.}~is the random graph model used, and its underlying assumptions.
-The citation switching algorithm used to generate expected values by random substitutions of references is designed to preserve the number of publications, the number of references in each publication, and the year of publication of both publications and references.
+\textcolor{blue}{Key to the findings of Uzzi {\em et al.}~is the random graph model used, and its underlying assumptions.
+The citation switching algorithm used to generate expected values by substituting cited references with randomly selected references published in the same year is designed to preserve the number of publications, the number of references in each publication, and the year of publication of both publications and references.
 Importantly, disciplinary origin does not affect the probability that a reference is selected to replace another one.
@@
 Such substitutions poorly model the disciplinary nature of scientific research and citation behavior~\citep{wallace_lariviere_gingras_2012,moed_measuring_2010,klavans_research_2017,garfield_1979}.
-In addition, under this random model, a reference cited many times in a given year is selected with the same probability as a reference cited only once, which appears inconsistent with the power law or lognormal citation distributions described in the literature~\citep{stringer_statistical_2010,perline_strong_2005}.
-Accordingly, model misspecification is likely to arise on account of the simulated values not corresponding to the empirical data very well.
+In addition, under this random model, a reference cited many times in a given year is selected as a substituent with the same probability as a reference cited only once, which is inconsistent with the power law or lognormal citation distributions of citations described in the literature~\citep{stringer_statistical_2010,perline_strong_2005}.
+Accordingly, model misspecification is likely to arise on account of the simulated values not corresponding to the empirical data very well.}
 
@@
 While they also reported the trend that HNHC is more probable in highly cited papers, they observed that ``only 64.4\%  of  243  WoS  subject  categories'' in the Uzzi {\em et al.} study met the criterion of having the highest probability of hit papers in the HNHC category.
-Further, they observed that journals vary widely in terms of size and influence and that 20 journals accounted for nearly 15\% of co-citations in their measurements.
+Further, they observed that journals vary widely in terms of size and influence and that \textcolor{blue}{20 journals accounted for 15.9\% of co-citations in their measurements}.
 Lastly, they noted that three multidisciplinary journals accounted for 9.4\% of all atypical combinations.
@@
 We hypothesized instead that modifying the normalization to constrain substitution references to be drawn only from the citation network being studied (the ``local network") rather than all of WoS
-(the ``global network") would reduce model misspecification by limiting substitutions from disciplinarily ectopic references.
-Consequently, we used keyword searches of the scientific literature to construct exemplar citation networks themed around academic disciplines of interest: \emph{applied physics, immunology, and metabolism}.
-Within these disciplinary frameworks, we calculated observed and expected co-citation frequencies using a refined random graph model and an efficient Monte Carlo simulation algorithm.
+(the ``global network") would reduce model misspecification by \textcolor{blue}{limiting substitutions from references that were ectopic to these networks.} Consequently, we used keyword searches of the scientific literature to construct exemplar citation networks themed around academic disciplines of interest: \emph{applied physics, immunology, and metabolism}.
+\textcolor{blue}{The cited references in these networks while predominantly aligned with the parent discipline (physics or life sciences in this case), also included articles from other disciplines.} Within these disciplinary frameworks, we calculated observed and expected co-citation frequencies using a refined random graph model and an efficient Monte Carlo simulation algorithm.
 
-Our analyses, using multiple techniques, provides substantial evidence that a constrained model where reference substitutions are limited to a local (disciplinary) network reduces model misspecification compared to the unconstrained model that uses the global network (WoS).
+Our analyses, using multiple techniques, provide substantial evidence that a constrained model where reference substitutions are limited to a local (disciplinary) network reduces model misspecification compared to the unconstrained model that uses the global network (WoS).
 Furthermore, re-analyses of these three semantically-themed citation networks  under the improved model reveals strikingly different trends.
@@
 \vspace{-4mm}
-% latex table generated in R 3.5.3 by xtable 1.8-4 package
-% Fri May 17 14:28:31 2019
+
 \begin{table}[ht]
@@
 For citation shuffling, we developed a performant citation switching algorithm, \emph{runtime enhanced permuting citation switcher (repcs)}~\citep{GithubERNIE2019}, that randomly permuted citations grouped by year of publication to switch citations while preserving the year of publication for both articles and references, the number of publications and the number of references in each data set, and the disciplinary composition of the references in each data set.
-Our approach is different from previous studies in these ways: (i) we sampled citations in proportion to their citation frequency (equivalently from a multiset rather than a set) in order to better reflect citation practice,
+\textcolor{blue}{Our approach is different from previous studies in these ways: (i) we sampled citations in proportion to their citation frequency (equivalently from a multiset rather than a set) in order to better reflect citation practice,
 (ii) we permitted a substitution to match the original reference in a publication when the random selection process dictated it rather than attempting to enforce that a different reference be substituted, and (iii) we introduced an error correction step to delete any publications that accumulated duplicate references during the substitution process.
@@
 We also tested \emph{repcs}  under comparable conditions to \emph{umsj} and estimated a runtime advantage of at least two orders of magnitude.
-This runtime advantage was significant enough that we chose to use the \emph{repcs}   algorithm in our study and generated expected values averaged from 1,000 simulations for improved coverage of every data set we analyzed.
+This runtime advantage was significant enough that we chose to use the \emph{repcs}   algorithm in our study and generated expected values averaged from 1,000 simulations for improved coverage of every data set we analyzed.}
 
@@
 \caption{Model misspecification is reduced by constraining substitutions to the local  disciplinary networks.
-We computed Kullback-Leibler (K-L) divergencesbetween empirical and simulated journal pair frequencies using two different
+We computed Kullback-Leibler (K-L) divergences between empirical and simulated journal pair frequencies using two different
 background networks (local versus global) for each disciplinary network  (applied physics, immunology, and metabolism) for the years 1985, 1995, and 2005.
@@
 
-The principal difference between the two models is a single parameter--the set of references that can be used as substituents during the substitution process.
+The principal difference between the two models we discuss is a single parameter--the set of references that can be used as substituents during the substitution process.
+\textcolor{blue}{The keyword search we use also has the advantage of selecting only relevant articles from multidisciplinary journals.
+However, it is important to note that the local networks we evaluated are not monodisciplinary, the references cited within exhibit disciplinary diversity}.
 We provided several lines of evidence that showed that changing this one parameter from a global network to the local disciplinary network reduces model misspecification.
-Furthermore,  using the constrained model (which allows substitutions only within the local network)  instead of the unconstrained model (which allows substitutions in the WoS network) produces different trends in terms of conventionality and novelty, depending on the network.
-In particular, when using the unconstrained model, highly cited papers were most likely to be
-in the HNHC category but this trend does not consistently hold when using the constrained model.
+} Using the constrained model (which allows substitutions only within the local network)  instead of the unconstrained model (which allows substitutions in the WoS network) produces different trends in terms of conventionality and novelty, depending on the network \textcolor{blue}{and the parent discipline.} In particular, when using the unconstrained model, highly cited papers were most likely to be in the HNHC category but this trend does not consistently hold when using the constrained model.
 Instead, we find that conventionality flavored with novelty is {\em not} generally a feature of impactful research.
@@
 More generally, these results show that the trends approaching universality in highly cited papers are not robust to changes in thresholds for defining high impact or high novelty articles, or with time, and may be the consequence of using a random model that has a poor fit to the observed data.
-On the other hand, while  the constrained model reduces model misspecification compared to the unconstrained model, this does not imply that the constrained model is reasonable nor that trends observed under the constrained model convincingly explain scientific practice.
-Indeed, there are significant  challenges in using random models to understand human behavior, of which citation practice is one example.
+On the other hand, while  the constrained model reduces model misspecification compared to the unconstrained model, \textcolor{blue}{this does not imply that the constrained model is reasonable nor that trends observed under the constrained model convincingly explain scientific practice.
+Indeed, there are significant  challenges in using random models to understand human behavior, of which citation practice is one example.}
 
@@
 \end{document}
-
-\newpage
-\section{Residual}
-\emph{these remaining sentences require some work}
-The varying citation patterns when sampling from a disciplinary-focused data set versus a broader data set due, was a cause of journal pair z-scores changing signs in 28.6\% of instances: the effect of any one of these journal pairs on an article's novelty or conventionality is contradictory between broad and, more narrow disciplinary data sets.
-We contend that the interpretation due to a disciplinary data set, which preserved citation patterns, is more appropriate and an improvement on current methods.
-
-\begin{figure}
-\includegraphics[width=\hsize]{pnas_fig1a}
-\caption{Effect of Research Discipline,  Background Network,  and Citation Count on Conventionality and Novelty.
-Data are shown for the applied physics (18,305), immunology (21,917), metabolism (97,405) and WoS (476,288) networks for 1995.
-The number of publications in each network is shown in parentheses.
-Citation counts shown are cumulative over the first 8 years since publication.
-X-axis: publications were classified into percentile groups based on citation counts (e.g., Top 1 indicates those publications in the top 1\%).
-Y axis: The percent of applications in each group that are high conventionality (HC) and high novelty (HN).
-The z-scores are computed for each disciplinary network based on the selected background network; thus, \emph{imm} denotes the immunology network with immunology z-scores and \emph{imm\_wos} denotes the immunology network with z-scores from WoS z-scores.
-The figure shows striking differences between the WoS network compared to the metabolism and immunology networks: across all networks, the percentage of high conventionality (HC) publications increases with citation counts, while the percentage of high novelty (HN) publications decreases with citation counts for the biological networks but not for WoS.
-\label{fig:Fig1}}
-\end{figure}
-
-We addressed this consideration by analyzing disciplinary subsets of the scientific literature, thereby restricting random selection of references to only those references in the disciplinary network being studied.
-\emph{What about z-scores?} 
-We have conjectured that the approach of Uzzi et al.
-for generating journal-pair z-scores is misspecified in its sampling from a broad data set and its disregard for the frequency with which journal pairs are cited.
-Our principal consideration was to restrict model misspecification arising from disciplinarily irrelevant references.
-We addressed this consideration by analyzing disciplinary subsets of the scientific literature, thereby restricting random selection of references to only those references in the disciplinary network being studied.As observed in the Introduction, Monte Carlo simulations that use references from all publications do not account for observed citation practice (sentence needs to be made more eloquent)...
-
-\emph{This paragraph needs work, but I wanted to create a placeholder for the introduction to this subsection.
-It uses some of the passages form the former Chacko subsection.} .
-Like Uzzi et al., we also used a Monte Carlo approach to simulate under a random graph model, although our principal consideration was to restrict model misspecification arising from disciplinarily irrelevant references.
-We addressed this consideration by analyzing disciplinary subsets of the scientific literature, thereby restricting random selection of references to only those references in the disciplinary network being studied.
-In this subsection we demonstrate the effects of model misspecification or Uzzi et al.'s approach and the effectiveness of using disciplinary data sets in resolving the concomitant issues with the former.
-
-Note also in Figure \ref{fig:scatter} that many z-scores values are significantly different between WoS and Immunology data sets, although the density of points near the origin in Figure \ref{fig:scatter} indicates that some journal pairs change signs between the data sets while their magnitudes are not significantly different.
-While no metric is without downside, this observation points to a weakness of measuring novelty based simply on the sign of z-scores where no distinction is made between a small negative value and a large negative value, but a negative value of small magnitude is viewed as being significantly different than a small positive value.
-
-We used the criteria of Uzzi to calculate normalized journal pair frequencies (z-scores) and classify publications according to conventionality and novelty.
-We observe that z-score calculations are sensitive to the background network (disciplinary or WoS).
-Figure \ref{fig:scatter} shows that the z-scores for the same journal pair can be positive (negative) when computed with respect to one data set but be negative (positive) for another data set.
-The journal-pair z-scores in Figure \ref{fig:scatter} have consistent signs for both Immunology and WoS data sets in 71.4\% of the instances and different signs for 28.6\% of the journal pairs.
-When a journal-pair z-score is negative with respect to one data set and positive with respect to another data set, articles citing that pair are more likely to be deemed novel in the first instance and less likely to be deemed novel in the second instance.
-It seems that any journal pair should either be indicative of novelty or not, but it should never have contradictory implications that depend on the reference data set.
-We view, therefore, these contradictions as symptomatic of inappropriately sampling from a broad data set and ignoring observed citation patterns.
-Figure \ref{fig:scatter} reflects that the WoS data set has approximately 44,000 fewer negative z-scores than does the immunology data set, which contributes to its significantly lower percentage of high-novelty articles.
-\emph{The plots I made of the cumulative z-score distributions for Immunology and WoS also could be used to demonstrate this phenomenon, although the scatter plot does this more clearly, and it is more striking.
-The scatter plot also encodes more data, that is, the matched z-scores for each journal pair.}
-
-\begin{figure}%[tbhp]
-\centering
-\includegraphics[width=3in]{fig2_scatter_z_scores_flattened.pdf}     %width=.8\linewidth
-\caption{Journal pair z-scores vary with background network. 
-Scatter plot points (319,005) indicate journal pair z-scores for the 1995 Immunology data set with two different background networks: the x-axis is based on the local network (1995 Immunology) and the y-axis is based on the entire Web of Science network.
-Black indicates journal pairs whose z-scores have the same sign when computed for both background networks, while red points indicate the 28.6\% of journal pairs whose z-scores change sign across networks.
-Regions with deeper hues indicate higher point densities.
-} %and the histograms show the marginal distributions for each data set separately.}
-\label{fig:scatter}
-\end{figure}
-
-%\begin{figure*}
-%\begin{tabular}{ccc}
-%\includegraphics[width=2.1in]{SIDoc/figs/scatter_z_scores_metab85_WoS_ZoomIn.pdf} & \includegraphics[width=2.1in]{Fig2H01N10.pdf} & \includegraphics[width=2.1in]{Fig2H05N10.pdf} \\
-%(a) & (b) & (c) \\
-%\end{tabular}
-%\caption{Scatter plot points show journal pair z-scores with respect to the Immunology data set for 1995 on the x-axis and the broad Web of Science on the y-axis.
-Black indicates journal pairs whose z-scores have the same sign when computed for both data sets while red points indicate journal pairs whose z-scores change sign across data sets.
-Regions with deeper hues indicate higher point density.
-The histograms show the marginal distributions of the z-scores for each of the data sets separately.}
-%\label{fig:Fig2}
-%\end{figure*}
-
-The variation in z-scores with respect to the reference data sets causes the percentages of articles denoted as highly conventional and highly novel to be significantly different, as demonstrated in Figure \ref{fig:Fig1}.
-\emph{Insert text about Figure \ref{fig:Fig1}.}
-
-\begin{table}%[tbhp]
-\centering
-\caption[Hit Rates]{Hit Rates by Category for the 1995 data sets. The last four columns indicate the proportion of publications that are hits for each respective category.} \label{Tab:HitRate}
-\begin{tabular}{|crrrrrr|}
-\hline
-& \multicolumn{1}{c}{Hits as \%} & \multicolumn{1}{c}{Novelty}  &  &  &  &  \\ Data Set & \multicolumn{1}{c}{of Articles} & \multicolumn{1}{c}{Percentile} & \multicolumn{1}{c}{LNLC} & \multicolumn{1}{c}{LNHC} & \multicolumn{1}{c}{HNLC} & \multicolumn{1}{c}{HNHC} \\
-\hline  
-Imm95&1\%&10\%& 0.000& 0.019& 0.005& 0.014 \\ 
-Imm95&10\%&10\%& 0.017& 0.128& 0.076& 0.129 \\ 
-Metab95&1\%&10\%& 0.001& 0.017& 0.006& 0.014 \\ 
-Metab95&10\%&10\%& 0.019& 0.130& 0.074& 0.133 \\ 
-AP95&1\%&10\%& 0.002& 0.007& 0.012& 0.010 \\ 
-AP95&10\%&10\%& 0.047& 0.079& 0.123& 0.109 \\ 
-WoS95&1\%&10\%& 0.004& 0.013& 0.009& 0.017 \\ 
-WoS95&10\%&10\%& 0.056& 0.115& 0.104& 0.156 \\ \hline
-
-\end{tabular}
-\end{table}
-
-%%%%%%%%%%%%%%%%%%%%%%%
-%% The bibliography
-
-%\bibliography{cocit_r}
-
-%% No appendices allowed in Network Neuroscience style
-%\appendix
-
-\subsection{Sample Subsection}
-Text here. Text here. Text here. Text here.
-Text here. Text here. Text here. Text here.
-Text here. Text here. Text here. Text here.
-Text here. Text here. Text here. Text here.
-
-\subsubsection{Sample Subsubsection}
-Text here. Text here. Text here. Text here.
-Text here. Text here. Text here. Text here.
-Text here. Text here. Text here. Text here.
-Text here. Text here. Text here. Text here.
-
-\section{Sample equations}
-\begin{equation}
-\label{eq:rhoCHT}
-\rho^{\pi}= \frac{RI + \mathbb{E}_{\pi([L,\tau_L]|\textrm{post})}
-\left[C_L(\taupav+\tau_L) \right]   +
-\displaystyle{\int_{0}^{P}}{dw~ \mathbb{E}_{\pi_{w_L}}}
-\Biggl[\/\sum_{n_{L|[\textrm{pre},w]}}C_L(\tau_L)
-\Biggr]            }      {P +
-\mathbb{E}_{\pi([L,\tau_L] |\textrm{post})}[\tau_{L}] +\taupav +
-\displaystyle{ \int_{0}^{P}}{dw~ \mathbb{E}_{\pi_{w_L}}}   
-\Biggl[\sum_{n_{L|[\textrm{pre},w]}}\tau_L\Biggr]  
-}
-\end{equation}
-As long as
-$RI - K_LP > 
-\frac{1}{\beta}$
-\begin{equation}
-%\def\theequation{5.1}
-\left.\begin{array}{lrcl}
-&\rho^{\pi} &=&  \displaystyle\frac{\beta ( RI + K_L \taupav )-1} {\beta
-(P+\taupav )}    \\[12pt]
-\hbox{and}\hbox to .25in{\hfill}&\mathbb{E}[\tau_L | \text{post}] &=&\displaystyle \frac{P+\taupav}{\beta ( RI -
-K_LP)-1}  
-\label{eq:analytical_linear}
-\end{array}\right\}\hbox to 1.25in{\hfill}
-\end{equation} 
-Text finishing first page.
-Text finishing first page.
-Text finishing first page.
-Text finishing first page.
-Text finishing first page.
-Text finishing first page.
-Text finishing first page.
-
-\begin{boxedtext}{Comparative Analysis of Different Classes of Networks} 
-Going beyond the examination of shared topological features across
-nervous systems, the generalized mathematical language of graph theory
-also offers tools for the comparison of the organization of brain
-networks to other classes of network studied
-by different scientific
-disciplines.
-
-Many real-world systems operate as some sort of
-interaction or communication network, including, for example, social
-networks, gene regulatory networks, computer networks, and
-transportation networks. Similar to brain networks, many of these
-real-world networks display an efficient small-world organization, a
-pronounced community structure with densely connected modules, as well
-as the formation of hubs and rich clubs. Going beyond the
-comparison of networks within the class of nervous systems, the field
-of `comparative network analysis' examines commonalities and
-differences across a range of network classes.
-
-\begin{figure}
-\includegraphics[width=\hsize]{Fig1}
-\caption{Here is the caption.}
-\end{figure}
-\end{boxedtext}
-
-\newpage
-\begin{boxedtext}{Comparative Analysis of Different Classes of Networks} 
-Going beyond the examination of shared topological features across
-nervous systems, the generalized mathematical language of graph theory
-also offers tools for the comparison of the organization of brain
-networks to other classes of network studied by different scientific
-disciplines. Many real-world systems operate as some sort of
-interaction or communication network, including, for example, social
-networks, gene regulatory networks, computer networks, and
-transportation networks. Similar to brain networks, many of these
-real-world networks display an efficient small-world organization, a
-pronounced community structure with densely connected modules, as well
-as the formation of hubs and rich clubs. Going beyond the
-comparison of networks within the class of nervous systems, the field
-of `comparative network analysis' examines commonalities and
-differences across a range of network classes.
-
-\begin{table}[ht]
-\caption{Here is the caption.}
-
-\centerline{\begin{tabular}{|c|c|c|}
-\hline
-one&two&three\\
-\hline
-four&five&six\\
-\hline
-\end{tabular}}
-\end{table}
-\end{boxedtext}
-
-\subsection{Jargon Samples in margin}
-One common decision is between working (performing an employer-defined
-task) and engaging in leisure (activities pursued for oneself). Working
-leads to external rewards such as food and money; whereas leisure is
-supposed to be intrinsically beneficial \jargon{Intrinsically beneficial}{The characteristic of
-leisure that we enjoy most.} (otherwise one would not want to
-engage in it).
-%% \jargon has optional argument in square brackets where you can specify
-%% the amount of extra space below where it would normally appear when 
-%% two \jargon entries are in the same paragraph:
-$\beta \in [0,\infty)$\jargon[24pt]{$\beta \in [0,\infty)$}{inverse temperature or degree of
-stochasticity-determinism parameter.} is often used to indicate an
-important parameter, the stochasticity-determinism parameter.
-
-\subsection{Simple code sample}
-
-\begin{code}
-\begin{verbatim}
-procedure bubbleSort( A : list of sortable items )
-    n = length(A)
-    repeat
-       newn = 0
-       for i = 1 to n-1 inclusive do
-          if A[i-1] > A[i] then
-             swap(A[i-1], A[i])
-             newn = i
-          end if
-       end for
-       n = newn
-    until n = 0
-end procedure
-\end{verbatim}
-\end{code}
-
-\subsection{Algorithm environment}
-%% \begin{algorithm} takes option [p][b][t][h],  or some combination, like \begin{figure}
-%% See documentation for algorithmic.sty for more information on formatting algorithms.
-
-\begin{algorithm}[h]
-\caption{A sample in an algorithm environment.}
-\begin{algorithmic}
-\If {$i\geq maxval$}
-    \State $i\gets 0$
-\Else
-    \If {$i+k\leq maxval$}
-        \State $i\gets i+k$
-    \EndIf
-\EndIf
-\end{algorithmic}
-\end{algorithm}
-
-\section{Itemized Lists}
-
-\subsection{Roman list:}
-
-\begin{enumerate}
-\item[(i)] at high 
-payoffs, subjects work almost continuously.
-\item[(ii)] at low payoffs, they 
-engage in leisure all at once, in long bouts after working.
-\item[(iii)] subjects work continuously for the entire price duration, as long as
-the price is not very long;
-\item[(iv)] the duration of leisure bouts is variable.
-\end{enumerate}
-
-\subsection{Numbered list:}
-
-\begin{enumerate}
-\item at high 
-payoffs, subjects work almost continuously, engaging in little leisure
-inbetween work bouts; 
-\item at low payoffs, they 
-engage in leisure all at once, in long bouts after working, rather
-than distributing the same amount of leisure time into multiple short
-leisure bouts; 
-\item subjects work continuously for the entire price duration, as long as
-the price is not very long (as shown by an analysis conducted by
-Y-AB, to be published separately);  
-\item the duration of leisure bouts is variable.
-\end{enumerate}
-
-\subsection{Bulleted list:}
-
-\begin{itemize}
-\item at high 
-payoffs, subjects work almost continuously, engaging in little leisure
-inbetween work bouts; 
-\item at low payoffs, they 
-engage in leisure all at once, in long bouts after working, rather
-than distributing the same amount of leisure time into multiple short
-leisure bouts; 
-\item subjects work continuously for the entire price duration, as long as
-the price is not very long (as shown by an analysis conducted by
-Y-AB, to be published separately);  
-\item the duration of leisure bouts is variable.
-\end{itemize}
-
-\subsection{Description list:}
-\begin{description}
-\item[High payoffs:] at high 
-payoffs, subjects work almost continuously, engaging in little leisure
-inbetween work bouts; 
-\item[Low payoffs:] at low payoffs, they 
-engage in leisure all at once, in long bouts after working, rather
-than distributing the same amount of leisure time into multiple short
-leisure bouts; 
-\item[Continuous work:] subjects work continuously for the entire price duration, as long as
-the price is not very long (as shown by an analysis conducted by Y-AB, to be published separately); 
-\item[Duration:] the duration of leisure bouts is variable.
-\end{description}
-
-\section{Sample figures}
-
-\begin{figure}[h] 
-\centerline{\includegraphics[width=\textwidth]{Fig1.pdf}}
-\caption{(Colour online) \textbf{Task and key features of the
- data.} \\
- A) Cumulative handling time (CHT) task. Grey bars denote work
-(depressing a lever), white gaps show leisure. The subject must
-accumulate work up to a total period of time called the
-\emph{price} ($P$) in order to obtain a single reward (black dot) of subjective reward
-intensity $RI$. The trial duration is $25\times \mathrm{price}$ (plus
-$2$s each time the price is attained, during which the lever is retracted so it cannot
-work; not shown).}
-\label{fig:task_data}
-\end{figure}
-%% this command ends a page but does not fill the bottom with white space:
-\eject
-
-\begin{figure}[ht] 
-\widefigure{\fullpagewidth}{Fig1.pdf}
-\caption{(Colour online) \textbf{Task and key features of the
- data.} \\
- A) Cumulative handling time (CHT) task. Grey bars denote work
-(depressing a lever), white gaps show leisure. The subject must
-accumulate work up to a total period of time called the
-\emph{price} ($P$) in order to obtain a single reward (black dot) of subjective reward
-intensity $RI$. The trial duration is $25\times \mathrm{price}$ (plus
-$2$s each time the price is attained, during which the lever is retracted so it cannot
-work; not shown).}
-\label{fig:task_data2}
-\end{figure}
-
-\newpage
-\section{Sample tables}
-
-\begin{table}[!ht]
-\caption{Time of the Transition Between Phase 1 and Phase 2$^{a}$}
-\label{tab:label}
-\centering
-\begin{tabular}{lc}
-\hline
- Run  & Time (min)  \\
-\hline
-  $l1$  & 260   \\
-  $l2$  & 300   \\
-  $l3$  & 340   \\
-  $h1$  & 270   \\
-  $h2$  & 250   \\
-  $h3$  & 380   \\
-  $r1$  & 370   \\
-  $r2$  & 390   \\
-\hline
-\multicolumn{2}{l}{$^{a}$Table note text here.}
-\end{tabular}
-\end{table}
-
-\begin{table}[ht]
-\widecaption{Sample table taken from [treu03]\label{tbl-1}}
-\begin{widetable}
-\advance\tabcolsep-1pt
-\small
-\begin{tabular}{ccrrccccccccc}
-\hline
-\bf 
-POS &\bf  chip &\multicolumn1c{\bf ID} &\multicolumn1c{\bf X}
-&\multicolumn1c{\bf Y} &\bf
-RA &\bf DEC &\bf IAU$\pm$ $\delta$ IAU &\bf
-IAP1$\pm$ $\delta$ IAP1 &\bf IAP2 $\pm$ $\delta$
-IAP2 &\bf star &\bf E &\bf Comment\\
-\hline
-0 & 2 & 1 & 1370.99 & 57.35\rlap{$^a$}    &   6.651120 &  17.131149 &
-21.344$\pm$0.006\rlap{$^b$}  & 2 4.385$\pm$0.016 & 23.528$\pm$0.013 & 0.0 & 9 & -    \\
-0 & 2 & 2 & 1476.62 & 8.03     &   6.651480 &  17.129572 & 21.641$\pm$0.005  & 2 3.141$\pm$0.007 & 22.007$\pm$0.004 & 0.0 & 9 & -    \\
-0 & 2 & 3 & 1079.62 & 28.92    &   6.652430 &  17.135000 & 23.953$\pm$0.030  & 2 4.890$\pm$0.023 & 24.240$\pm$0.023 & 0.0 & - & -    \\
-0 & 2 & 4 & 114.58  & 21.22    &   6.655560 &  17.148020 & 23.801$\pm$0.025  & 2 5.039$\pm$0.026 & 24.112$\pm$0.021 & 0.0 & - & -    \\
-0 & 2 & 5 & 46.78   & 19.46    &   6.655800 &  17.148932 & 23.012$\pm$0.012  & 2 3.924$\pm$0.012 & 23.282$\pm$0.011 & 0.0 & - & -    \\
-0 & 2 & 6 & 1441.84 & 16.16    &   6.651480 &  17.130072 & 24.393$\pm$0.045  & 2 6.099$\pm$0.062 & 25.119$\pm$0.049 & 0.0 & - & -    \\
-0 & 2 & 7 & 205.43  & 3.96     &   6.655520 &  17.146742 & 24.424$\pm$0.032  & 2 5.028$\pm$0.025 & 24.597$\pm$0.027 & 0.0 & - & -    \\
-0 & 2 & 8 & 1321.63 & 9.76     &   6.651950 &  17.131672 &
-22.189$\pm$0.011  & 2 4.743$\pm$0.021 & 23.298$\pm$0.011 & 0.0 & 4 &
-edge \\
-\hline\\[-6pt]
-\multicolumn{13}{l}{%
-Table 2 is published in its entirety in the electronic
-edition of the {\it Astrophysical Journal}.}\\[3pt]
-\multicolumn{13}{l}{%
-$^a$ Sample footnote for table 2.}\\[3pt]
-\multicolumn{13}{l}{%
-$^b$ Another sample footnote for table 2.}
-\end{tabular}
-\end{widetable}
-\end{table}
-
-\begin{table}[p]
-\rotatebox{90}{\vbox{\hsize=\textheight
-\caption{Here is a caption for a table that is found in landscape
-mode.}
-\begin{tabular}{ccrrccccccccc}
-\hline
-\bf 
-POS &\bf  chip &\multicolumn1c{\bf ID} &\multicolumn1c{\bf X}
-&\multicolumn1c{\bf Y} &\bf
-RA &\bf DEC &\bf IAU$\pm$ $\delta$ IAU &\bf
-IAP1$\pm$ $\delta$ IAP1 &\bf IAP2 $\pm$ $\delta$
-IAP2 &\bf star &\bf E &\bf Comment\\
-\hline
-0 & 2 & 1 & 1370.99 & 57.35\rlap{$^a$}    &   6.651120 &  17.131149 &
-21.344$\pm$0.006\rlap{$^b$}  & 2 4.385$\pm$0.016 & 23.528$\pm$0.013 & 0.0 & 9 & -    \\
-0 & 2 & 2 & 1476.62 & 8.03     &   6.651480 &  17.129572 & 21.641$\pm$0.005  & 2 3.141$\pm$0.007 & 22.007$\pm$0.004 & 0.0 & 9 & -    \\
-0 & 2 & 3 & 1079.62 & 28.92    &   6.652430 &  17.135000 & 23.953$\pm$0.030  & 2 4.890$\pm$0.023 & 24.240$\pm$0.023 & 0.0 & - & -    \\
-0 & 2 & 4 & 114.58  & 21.22    &   6.655560 &  17.148020 & 23.801$\pm$0.025  & 2 5.039$\pm$0.026 & 24.112$\pm$0.021 & 0.0 & - & -    \\
-0 & 2 & 5 & 46.78   & 19.46    &   6.655800 &  17.148932 & 23.012$\pm$0.012  & 2 3.924$\pm$0.012 & 23.282$\pm$0.011 & 0.0 & - & -    \\
-0 & 2 & 6 & 1441.84 & 16.16    &   6.651480 &  17.130072 & 24.393$\pm$0.045  & 2 6.099$\pm$0.062 & 25.119$\pm$0.049 & 0.0 & - & -    \\
-0 & 2 & 7 & 205.43  & 3.96     &   6.655520 &  17.146742 & 24.424$\pm$0.032  & 2 5.028$\pm$0.025 & 24.597$\pm$0.027 & 0.0 & - & -    \\
-0 & 2 & 8 & 1321.63 & 9.76     &   6.651950 &  17.131672 &
-22.189$\pm$0.011  & 2 4.743$\pm$0.021 & 23.298$\pm$0.011 & 0.0 & 4 &
-edge \\
-\hline\\[-6pt]
-\multicolumn{13}{l}{%
-Table 2 is published in its entirety in the electronic
-edition of the {\it Astrophysical Journal}.}\\[3pt]
-\multicolumn{13}{l}{%
-$^a$ Sample footnote for table 2.}\\[3pt]
-\multicolumn{13}{l}{%
-$^b$ Another sample footnote for table 2.}
-\end{tabular}
-}}
-\end{table}
-\clearpage
-\begin{boxedtext}{Tools for comparison of networks} 
-Going beyond the examination of shared topological features across
-nervous systems, the generalized mathematical language of graph theory
-also offers tools for the comparison of the organization of brain
-networks to other classes of network studied by different scientific
-disciplines.
-
-From $\mathcal{W}$, we can estimate the variability in the fluctuations of the functional connection between nodes $i$ and $j$ over time as:
-\begin{equation}
-s_{ij}=\sqrt{\frac{1}{T-L}\sum_{t=1}^{T-L+1}(W_{ij}(t) - m_{ij})}
-\end{equation}
-where $m_{ij}=\frac{1}{T-L+1}\sum_{t=1}^{T-L+1}W_{ij}(t)$ is the mean
-dynamic functional connectivity over time.
-
-Many real-world systems operate as some sort of
-interaction or communication network, including, for example, social
-networks, gene regulatory networks, computer networks, and
-transportation networks. Similar to brain networks, many of these
-real-world networks display an efficient small-world organization, a
-pronounced community structure with densely connected modules, as well
-as the formation of hubs and rich clubs. Going beyond the
-comparison of networks within the class of nervous systems, the field
-of `comparative network analysis' examines commonalities and
-differences across a range of network classes.
-\end{boxedtext}
-
-Example of table continuing over pages:
-
-\begin{center}
-\begin{longtable}{ccc@{}}
-\caption{ApJ costs from 1991 to 2013
-\label{tab:table}} \\[2pt]
-\hline
-\bf Year & \bf Subscription & \bf Publication \\
- & \bf cost &\bf charges\\
- & \bf(\$) & \bf (\$/page)\\
-\hline
-\endfirsthead
-
-\multicolumn3c{Table \thetable, \it continued from previous page.}\\[6pt]
-\multicolumn3c{ApJ costs from 1991 to 2013}\\[2pt]
-\hline
-\bf Year & \bf Subscription & \bf Publication \\
- & \bf cost &\bf charges\\
- & \bf(\$) & \bf (\$/page)\\
-\hline
-\endhead
-\\\hline
-\\[-8pt]
-\multicolumn{3}{r}{\it Table continued on next page}\\ 
-\endfoot
-
-\hline
-\endlastfoot
-
-1991 & 600 & 100 \\
-1992 & 650 & 105 \\
-1993 & 550 & 103 \\
-1994 & 450 & 110 \\
-1995 & 410 & 112 \\
-1996 & 400 & 114 \\
-1997 & 525 & 115 \\
-1998 & 590 & 116 \\
-1999 & 575 & 115 \\
-2000 & 450 & 103 \\
-2001 & 490 &  90 \\
-2002 & 500 &  88 \\
-2003 & 450 &  90 \\
-2004 & 460 &  88 \\
-2005 & 440 &  79 \\
-2006 & 350 &  77 \\
-2007 & 325 &  70 \\
-2008 & 320 &  65 \\
-2009 & 190 &  68 \\
-2010 & 280 &  70 \\
-2011 & 275 &  68 \\
-2012 & 150 &  56 \\
-2013 & 140 &  55 \\
-\end{longtable}
-\end{center}
-
-\section{Supportive Information}
-Here you enter further sources of information, if desired.
-
-%% A possible entry might be:
-% No supportive information is available at this time.

### 2019-07-15 rebuttal.tex
george closing out

@@
 For ease in reading, we have broken up the comments from reviewers into blocks of italicized text.
+We have highlighted, in blue, changes in the text as as well as sections we wish to draw attention to.
 
@@
 Our apologies for not being clear.
+In the  revised manuscript, we have also highlighted a section of the Materials and Methods that is relevant.
 In examining the citation shuffling code of Uzzi kindly shared by Satyam Mukherjee and Ben Jones, we realized that the choice of substitutions was restricted to the set rather than the multi-set of eligible references.
-While their reciprocal substitution approach  ensures that the total number of references is still preserved after shuffling, selection of a substituent is equiprobable.
+While their reciprocal substitution approach  ensures that the total number of references stratified by year of publication is still preserved after shuffling, selection of a substituent is equiprobable.
 In other words, Uzzi's algorithm systematically shuffles every reference but replacements are selected from the set \{a,b,c,d,e\} rather than the multi-set \{aaaa,b,ccc,dd,e\} of eligible references.
@@
 Uzzi's code does not check for duplicate references as a result of shuffling, whereas we do and suppress it.
+The reason we did not emphasize this to a greater extent is because the number of highly cited references is relatively small in a lognormal distribution.
+Thus, expected values of journal pairs certainly differ between the two algorithmic approaches but our analysis was largely conducted at a high level.
+Further, the differences between performing 10 (Uzzi) versus 1,000 simulations with better coverage of observed journal pairs (this manuscript) and the effects of the local network seemed more important to focus on.
 

### 2019-07-15 rebuttal.tex
tweaked rebuttal
various changes, see blue stuff

@@
 \documentclass[11pt, oneside]{article}   	% use "amsart" instead of "article" for AMSLaTeX format
-\usepackage{geometry,color}                		% See geometry.pdf to learn the layout options. There are lots.
+\usepackage{geometry,color, url}                		% See geometry.pdf to learn the layout options. There are lots.
 \geometry{letterpaper}                   		% ... or a4paper or a5paper or ... 
@@
 
-Please find below, our response to critique.
-We thank the reviewers for their constructive critiques as well as their time, effort, and professional courtesy in reviewing our manuscript.
+We thank the reviewers for their constructive critiques as well as their time, effort, and professional courtesy in reviewing our manuscript, and for the opportunity to revise the manuscript in response to the reviews.
+
+Some of the comments from both reviewers reflect a lack of clarity in our manuscript, and our responses to these comments attempt to correct this.
+However, we also note two concerns from both reviewers that merit a deeper response.
+
+First,   both reviewers raise as a potential concern that our use of the keyword search in defining  our citation networks could lead to monodisciplinary networks.
+We have therefore explicitly addressed this issue by explaining that these citation networks are in fact quite multi-disciplinary: first, because keyword searches generate a set of publications that can span several different disciplines, and secondly the references cited within these publications can come from additional disparate disciplines.
+Thus, the citation networks we assemble contain both these publications and their cited references, and have a greater breadth of disciplinary scope than would be implied by just the keyword itself.
+
+Another  question that was raised was why we are confident that the restriction of substitutions to a ``local" network is better than the global network.
+The main response to this is that our study shows that the model misspecification is reduced by restricting substitutions to the local network, as evidenced by the reduction in the Kullback-Liebler divergence (a standard statistical test) between the model distribution and the empirical distribution.
+
+Finally, we wish to note that the objective of this paper was not to provide a new approach for co-citation analysis in order to better characterize novelty and conventionality; instead,  
+the objective of our study was to demonstrate that a small change in the  Uzzi model results in a reduction in model misspecification and presents very different trends.
+Hence, any conclusions based on Uzzi's model that are not also seen  using our model are likely to be the result of  model misspecification.
+Our study achieves this goal, and clarifies issues that need to be considered in developing robust models that are able to provide meaningful insights into characteristics of high impact
+papers via co-citation analysis.
+
 We have attempted to respond  in a systematic manner both below and in a revision of the manuscript (attached).
@@
 
-We agree that our study is centered around a focused methodological critique.
-One that has important implications for whether co-citation analysis can be used to infer novelty and conventionality.
+We agree that our study is centered around a focused methodological critique, and one that has important implications for whether co-citation analysis can be used to infer novelty and conventionality.
 However, we do not agree that its contribution is marginal merely because Uzzi was published five years ago.
-By this standard, a critical consideration or extension of Small (1973) and Marshakova-Shaikevich (1973) who formulated the concept of co-citation could also be considered marginal, With the exception of a challenge by Boyack and Klavans (2014), Uzzi seems to have been cited rather uncritically over 175 times since its publication, which places it in the top 1-2\% of papers.
+By this standard, a critical consideration or extension of Small (1973) and Marshakova-Shaikevich (1973) who formulated the concept of co-citation could also be considered marginal.
+ With the exception of a challenge by Boyack and Klavans (2014), Uzzi seems to have been cited rather uncritically over 175 times since its publication, which places it in the top 1-2\% of papers.
 We think that our work has value in identifying a significant weakness inherent in its approach.
@@
 
-A keyword search defines a set of articles that are semantically themed and that may cross conventional disciplinary boundaries.
-The references in these articles were selected by the authors and while they are typically dominated by the closest discipline, they can be drawn from any discipline (as we also cite in our manuscript: Garfield, 1979; Klavans \& Boyack, 2017; Moed, 2010; Wallace, Lariviere, \& Gingras, 2012).
-In our approach, the expected values for z-score calculations are calculated from references cited by the authors of those articles in contrast to the indiscriminate substitutions of Uzzi.
-Thus, Science and Nature are accounted for without the distraction of articles in these multidisciplinary journals that are irrelevant to the network being studied.
+The reviewer makes two very valid points, the first being that we should acknowledge that the model we use is also flawed, and the second having to do with challenges in using co-citation analysis defined by journals in characterizing which publications are conventional and/or innovative.
 
-The reviewer makes two very valid points, the first being that we should acknowledge that the model we use is also flawed, and the second having to do with challenges in using co-citation analysis defined by journals in characterizing which publications are conventional and/or innovative.
-In response to the first point, we do not assert that our model/method is perfect -- in fact we acknowledge this explicitly, and have revised the paper to make that point even stronger.
-But we do note that we establish a reduction in model misspecification when using our model compared to Uzzi et al.'s model (as indicated by a reduction in the Kullback-Leibler divergence).
-All models are imperfect but our model is significantly less flawed than Uzzi's.
+In response to the first point, we do not assert that our model/method is perfect--in fact we acknowledge this explicitly, and have revised the paper to make that point even stronger.
+But we do note that we establish a reduction in model misspecification when using our model compared to Uzzi et al.'s model (as indicated by a reduction in the Kullback-Leibler divergence): all models are imperfect but our model is significantly less flawed than Uzzi's.
+
 With respect to the second point, we have reiterated (in citing Boyack and Klavans, 2014) that there are journal effects that we do not investigate in this study but these are offset slightly by the use of keyword searches to define a network.
+Importantly, the keyword search approach  defines a set of articles that are semantically themed and that may cross conventional disciplinary boundaries. 
+Furthermore, the citation network based on the keyword search includes these articles and {\em also the references they cite}.
+This is noteworthy on two accounts: first, the inclusion of these references means that the disciplinary scope of the papers in the citation network can be quite large, and second, the references in these articles are not arbitrary references, but instead are those that were selected by the authors.
+Thus, although the cited references are typically dominated by the closest discipline, they can be drawn from any discipline (as we also cite in our manuscript: Garfield, 1979; Klavans \& Boyack, 2017; Moed, 2010; Wallace, Lariviere, \& Gingras, 2012).
+This may help explain why there is reduced model misspecification  in our model compared to Uzzi: in our approach, the expected values for z-score calculations are calculated from references cited by the authors of those articles in contrast to the indiscriminate substitutions of Uzzi.
+Note also that Science and Nature are accounted for without the distraction of articles in these multidisciplinary journals that are irrelevant to the network being studied.
 
@@
 Our approach still identifies those interdisciplinary combinations that are atypical while confining the combinations to those which are relevant within a field.
-The point about within-discipline and cross-discipline novelty is very pertinent- we have referred to it in the revised Discussion and will follow up in a subsequent study.
+
+The point about within-discipline and cross-discipline novelty is very pertinent--we have referred to it in the revised Discussion and will follow up in a subsequent study.
 After we submitted the paper, we also analyzed the disciplinary content of both publications and references in our three datasets using the Web of Science research area classification.
@@
 }
-\caption{The disciplinary compositions of the three analytical datasets in our manuscript ap: applied physics, imm: immunology, and metab: metabolism were analyzed for the years, 1985, 1995, and 2005 using the Web of Science research area categorizations of \emph{lsb: life sciences and biology, ps:physical sciences, tech: technology, ss: social sciences, and ah: arts \& humanities}.
+\caption{The disciplinary compositions of the three analytical datasets in our manuscript ap: applied physics, imm: immunology, and metab: metabolism were analyzed for the years, 1985, 1995, and 2005 using the Web of Science research area categorizations of \emph{lsb: life sciences and biology, ps: physical sciences, tech: technology, ss: social sciences, and ah: arts \& humanities}.
 Both publications (pubs) and cited references (refs) were analyzed.
-The data show that while publications closely track their most similar research area, references have a greater cross disciplinary content- especially in the applied physics dataset but also for the other two.
+The data show that while publications closely track their most similar research area, references have a greater cross disciplinary content--especially in the applied physics dataset but also for the other two.
 }
@@
 
-The figure shown below was included in an earlier version of this manuscript submitted to another journal and was criticized for being confusing so we left it out in the submission to QSS.
-It specifically addresses the reviewer's point.
-Thus, both factors are in play (i) there is a difference when local and global networks are used to generate expected values (ii)  disciplines can be different from each other.
-We could include it as supplementary material since we're already over the 10 page limit.
-\newpage
+Please see the figure included in this response (noted as Figure 1), which was not included in the submitted paper due to space limitations.
+%was included in an earlier version of this manuscript submitted to another journal and was criticized for being confusing so we left it out in the submission to QSS. It 
+The figure specifically addresses the reviewer's point, and shows that both factors are in play:  (i) there is a difference when local and global networks are used to generate expected values, and  (ii)  disciplines can be different from each other.
+If space is not an issue, we  could include this in the paper, or perhaps as supplementary material (since we're already over the 10 page limit). %\newpage
 
@@
 In examining the citation shuffling code of Uzzi kindly shared by Satyam Mukherjee and Ben Jones, we realized that the choice of substitutions was restricted to the set rather than the multi-set of eligible references.
-While their reciprocal substitution approach  ensures that the total number of references stratified by year of publication is still preserved after shuffling, selection of a substituent is equiprobable.
-In other words, Uzzi's algorithm systematically shuffles every reference but replacements are selected from the set \{a,b,c,d,e\} rather than the multi-set \{aaaa,b,ccc,dd,e\} of eligible references.
+While their reciprocal substitution approach  ensures that the total number of references stratified by year of publication is still preserved after shuffling,
+the selection of a substituent is equiprobable. In other words, 
+\textcolor{blue}{
+Uzzi's algorithm systematically shuffles every reference but replacements are selected from the set \{a,b,c,d,e\} rather than the multi-set \{aaaa,b,ccc,dd,e\} of eligible references. }
 This flies in the face of what we know about preferential attachment and citation practice.
 
-Uzzi's citation shuffling code is available on our Github site with permission from the authors.
-https://bit.ly/2xRsCCM.
-The key snippet below shows that the references stored in the object below constitute a set, which is selected from during substitution.
+Uzzi's citation shuffling code is available on our Github site with permission from the authors:
+\url{https://bit.ly/2xRsCCM}. The key snippet below shows that the references stored in the object below constitute a set, which is selected from during substitution.
 
@@
 
-The deviation of our results from those of Uzzi et al.
-can be due to a choice of data set (local vs.
+The deviation of our results from those of Uzzi et al.~can be due to a choice of data set (local vs.
 global) or sampling technique, and so we compared our sampling approach with Uzzi's to understand how much of the difference was due to the background data set versus the sampling technique.

### 2019-07-16 rebuttal.tex
post TW

@@
 
-We thank the reviewers for their constructive critiques as well as their time, effort, and professional courtesy in reviewing our manuscript, and for the opportunity to revise the manuscript in response to the reviews.
+We thank the reviewers for their constructive critiques as well as their time, effort, and professional courtesy in reviewing our manuscript. We thank you for the opportunity to revise our manuscript.
 
-Some of the comments from both reviewers reflect a lack of clarity in our manuscript, and our responses to these comments attempt to correct this.
+Some of the comments from both reviewers reflect a lack of clarity in our manuscript, and we have attempted to correct this in the attached revision.
 However, we also note two concerns from both reviewers that merit a deeper response.
 
-First,   both reviewers raise as a potential concern that our use of the keyword search in defining  our citation networks could lead to monodisciplinary networks.
-We have therefore explicitly addressed this issue by explaining that these citation networks are in fact quite multi-disciplinary: first, because keyword searches generate a set of publications that can span several different disciplines, and secondly the references cited within these publications can come from additional disparate disciplines.
-Thus, the citation networks we assemble contain both these publications and their cited references, and have a greater breadth of disciplinary scope than would be implied by just the keyword itself.
+First,   both reviewers raise as a potential concern that our use of keyword searches in defining  citation networks could lead to monodisciplinary networks.
+We have therefore explicitly addressed this issue by explaining that such citation networks are in fact multi-disciplinary: first, because keyword searches generate a set of publications that can span several different disciplines, but secondly because the references cited within these publications are drawn from multiple disciplines.
+Thus, the citation networks we assemble contain both these publications and their cited references, and have a greater breadth of disciplinary scope than would be implied by a keyword.
+Another  question that was raised was why we are confident that the restriction of substitutions to a ``local" network is better than the global network.
+The main response to this is that our study shows that the model misspecification is reduced by restricting substitutions to the local network, as evidenced by the reduction in the Kullback-Liebler divergence (a standard statistical measure) between the model distribution and the empirical distribution.
 
-Another  question that was raised was why we are confident that the restriction of substitutions to a ``local" network is better than the global network.
-The main response to this is that our study shows that the model misspecification is reduced by restricting substitutions to the local network, as evidenced by the reduction in the Kullback-Liebler divergence (a standard statistical test) between the model distribution and the empirical distribution.
-
-Finally, we wish to note that the objective of this paper was not to provide a new approach for co-citation analysis in order to better characterize novelty and conventionality; instead,  
-the objective of our study was to demonstrate that a small change in the  Uzzi model results in a reduction in model misspecification and presents very different trends.
+Finally, we wish to note that the objective of this paper was not to provide a new approach for co-citation analysis in order to better characterize novelty and conventionality; instead, to demonstrate that a small change in the  Uzzi model results in a reduction in model misspecification with very different trends.
 Hence, any conclusions based on Uzzi's model that are not also seen  using our model are likely to be the result of  model misspecification.
@@
 
-We have attempted to respond  in a systematic manner both below and in a revision of the manuscript (attached).
+We have attempted to respond  to critique systematically below.
 For ease in reading, we have broken up the comments from reviewers into blocks of italicized text.
@@
 By this standard, a critical consideration or extension of Small (1973) and Marshakova-Shaikevich (1973) who formulated the concept of co-citation could also be considered marginal.
- With the exception of a challenge by Boyack and Klavans (2014), Uzzi seems to have been cited rather uncritically over 175 times since its publication, which places it in the top 1-2\% of papers.
+With the exception of a challenge by Boyack and Klavans (2014), Uzzi seems to have been cited rather uncritically over 175 times since its publication, which likely places it in the top 2\% of papers.
 We think that our work has value in identifying a significant weakness inherent in its approach.
@@
 
-We have revised the text to be considerate of these valuable suggestions.
-However, we would like to comment that the methodological issue we elucidate in the paper only has relevance in the larger context of co-citation analysis and differences in citation practice between disciplines.
-Thus, we are unwilling to discard the discussion of context.
+We are unwilling to discard the single introductory paragraph that places this study in context.
+We respectfully disagree that the title is misleading.
+However, we have revised the text slightly to be considerate of these valuable suggestions.
+The methodological issue we elucidate in the paper only has relevance in the larger context of co-citation analysis and differences in citation practice between disciplines.
 We agree that this manuscript is not a study in semantics, indeed we do not make such an assertion.
 However, the local networks we study are semantically themed.
-We respectfully disagree that the title is misleading.
 
@@
 
-The reviewer makes two very valid points, the first being that we should acknowledge that the model we use is also flawed, and the second having to do with challenges in using co-citation analysis defined by journals in characterizing which publications are conventional and/or innovative.
+The reviewer makes two very valid points, the first being that we should acknowledge that the model we use also has weaknesses, and the second having to do with challenges in using co-citation analysis defined by journals in characterizing which publications are conventional and/or innovative.
 
@@
 Importantly, the keyword search approach  defines a set of articles that are semantically themed and that may cross conventional disciplinary boundaries.
+Note that they keyword search approach selects relevant articles from journals like Science and Nature without the distraction of articles in these multidisciplinary journals that are irrelevant to the network being studied.
+
 Furthermore, the citation network based on the keyword search includes these articles and {\em also the references they cite}.
@@
 This may help explain why there is reduced model misspecification  in our model compared to Uzzi: in our approach, the expected values for z-score calculations are calculated from references cited by the authors of those articles in contrast to the indiscriminate substitutions of Uzzi.
-Note also that Science and Nature are accounted for without the distraction of articles in these multidisciplinary journals that are irrelevant to the network being studied.
 
@@
 In examining the citation shuffling code of Uzzi kindly shared by Satyam Mukherjee and Ben Jones, we realized that the choice of substitutions was restricted to the set rather than the multi-set of eligible references.
-While their reciprocal substitution approach  ensures that the total number of references stratified by year of publication is still preserved after shuffling,
-the selection of a substituent is equiprobable. In other words, 
-\textcolor{blue}{
-Uzzi's algorithm systematically shuffles every reference but replacements are selected from the set \{a,b,c,d,e\} rather than the multi-set \{aaaa,b,ccc,dd,e\} of eligible references. }
+While their reciprocal substitution approach  ensures that the total number of references stratified by year of publication is still preserved after shuffling, the selection of a substituent is equiprobable.
+In either a local or a global network, it does not make sense to treat a highly cited reference as equiprobable with a reference cited only once.
 This flies in the face of what we know about preferential attachment and citation practice.
+
+Consider a toy Web of Science dataset consisting of 5 publications all published in the same year.
+Each of these publications cites 4 references, thus, 20 citations.
+For simplicity, we will assume that all of these references were published in the same year.
+Of these, one (which we will call $x$) is cited in each of the publications (thus cited 5 times) and the remaining 15 are cited once in total.
+During citation shuffling (i)  in our approach, the probability of selecting $x$ would be 5/20 or 1/4.
+In Uzzi it would be 1/16.
+The remaining 15 references in Uzzi would have a probability of 1/16, whereas in our model they would have a probability of 1/20.
+In other words
+Uzzi's algorithm seeks to systematically shuffles every reference in the network but replacements are selected from the set \{x,a,b,c,d,e...\} rather than the multi-set \{x,x,x,x,x,b,c,c,c,d,d,e...\} of eligible references.
+
+Further, Uzzi's code enforces 20 successive substitution attempts before the original reference is allowed as a substitute for itself.
+Our code allows such self replacements without attempting to artificially enforce substitution with a different reference.
+Uzzi's code does not check for duplicate references as a result of shuffling, whereas we do and suppress it.
+The reason we did not emphasize these points to a greater extent is because the number of highly cited references is relatively small in a lognormal distribution.
+Thus, expected values of journal pairs certainly differ between the two algorithmic approaches but our analysis was largely conducted on aggregate measures.
+Further, the differences between performing 10 (Uzzi) versus 1,000 simulations with better coverage of observed journal pairs (this manuscript) and the effects of the local network seemed more important to focus on.
 
@@
 
-In either a local or a global network, it does not make sense to treat a highly cited reference as equiprobable with a reference cited only once.
-Consider a toy Web of Science dataset consisting of 5 publications all published in the same year.
-Each of these publications cites 4 references, thus, 20 citations.
-For simplicity, we will assume that all of these references were published in the same year.
-Of these, one (which we will call $x$) is cited in each of the publications (thus cited 5 times) and the remaining 15 are cited once in total.
-During citation shuffling (i)  in our approach, the probability of selecting $x$ would be 5/20 or 1/4.
-In Uzzi it would be 1/16.
-The remaining 15 references in Uzzi would have a probability of 1/16, whereas in our model they would have a probability of 1/20.
-Further, Uzzi's code enforces 20 successive substitution attempts if the original reference is selected as a substitute.
-Our code allows such a replacement without attempting to artificially enforce substitution with a different reference.
-Uzzi's code does not check for duplicate references as a result of shuffling, whereas we do and suppress it.
-The reason we did not emphasize this to a greater extent is because the number of highly cited references is relatively small in a lognormal distribution.
-Thus, expected values of journal pairs certainly differ between the two algorithmic approaches but our analysis was largely conducted at a high level.
-Further, the differences between performing 10 (Uzzi) versus 1,000 simulations with better coverage of observed journal pairs (this manuscript) and the effects of the local network seemed more important to focus on.
-
 The deviation of our results from those of Uzzi et al.~can be due to a choice of data set (local vs.

### 2019-07-16 cocit_r.tex
post TW-GC

@@
 For example, proximity defined by co-author networks~\citep{wallace_lariviere_gingras_2012} might be considered when defining probabilities for citation substitutions.
-Thus, evaluation in context~\citep{hicks_bibliometrics:_2015} and increased consideration of the disciplinary nature of the scientific enterprise is likely to result in improved models that yield further insight.
+\textcolor{blue}{Another interesting but challenging direction would be to find ways to distinguish intra-disciplinary versus cross-disciplinary novelty.} Overall, evaluation in context~\citep{hicks_bibliometrics:_2015} and increased consideration of the disciplinary nature of the scientific enterprise is likely to result in improved models that yield further insight.
 
@@
 We are grateful to Kevin Boyack and Dick Klavans for constructively critical discussions.
+We thank two anonymous reviewers for their insightful comments.
 Research and development reported in this publication was partially supported by Federal funds from the National Institute on Drug Abuse, National Institutes of Health, US Department of Health and Human Services, under Contract Nos.

### 2019-07-16 rebuttal.tex
post TW-GC

@@
 In other words
-Uzzi's algorithm seeks to systematically shuffles every reference in the network but replacements are selected from the set \{x,a,b,c,d,e...\} rather than the multi-set \{x,x,x,x,x,b,c,c,c,d,d,e...\} of eligible references.
+Uzzi's algorithm seeks to systematically shuffles every reference in the network but replacements are selected from the set \{x,a,b,c,d,e...\} rather than the multi-set \{x,x,x,x,x,b,c,d,,e...\} of eligible references.
 

### 2019-07-16 rebuttal.tex
Minor revision

@@
 In other words
-Uzzi's algorithm seeks to systematically shuffles every reference in the network but replacements are selected from the set \{x,a,b,c,d,e...\} rather than the multi-set \{x,x,x,x,x,b,c,d,,e...\} of eligible references.
+Uzzi's algorithm seeks to systematically shuffle every reference in the network but replacements are selected from the set \{x,a,b,c,d,e...\} rather than the multi-set \{x,x,x,x,x,b,c,d,,e...\} of eligible references.
 

### 2019-07-16 rebuttal.tex
fixed typo on Liebler

@@
 Another  question that was raised was why we are confident that the restriction of substitutions to a ``local" network is better than the global network.
-The main response to this is that our study shows that the model misspecification is reduced by restricting substitutions to the local network, as evidenced by the reduction in the Kullback-Liebler divergence (a standard statistical measure) between the model distribution and the empirical distribution.
+The main response to this is that our study shows that the model misspecification is reduced by restricting substitutions to the local network, as evidenced by the reduction in the Kullback-Leibler divergence (a standard statistical measure) between the model distribution and the empirical distribution.
 

### 2019-07-16 cocit_r.tex
Minor revisions
final typo:

--- 2019-07-15 cocit_r.tex
@@
 Using either the \emph{repcs}   or \emph{umsj} algorithms for 10 simulations resulted in expected value coverage of 75\% of the observed journal pair frequencies.
-Subsequent rounds of development and testing resulted in 99\% coverage of observed journal pairs when 1,000 simulations were conducted.
+Subsequent development and testing of \emph{repcs} resulted in 99\% coverage of observed journal pairs when 1,000 simulations were conducted.
 We also tested \emph{repcs}  under comparable conditions to \emph{umsj} and estimated a runtime advantage of at least two orders of magnitude.
@@
 For example, proximity defined by co-author networks~\citep{wallace_lariviere_gingras_2012} might be considered when defining probabilities for citation substitutions.
-Thus, evaluation in context~\citep{hicks_bibliometrics:_2015} and increased consideration of the disciplinary nature of the scientific enterprise is likely to result in improved models that yield further insight.
+\textcolor{blue}{Another interesting but challenging direction would be to find ways to distinguish intra-disciplinary from cross-disciplinary novelty.} Overall, evaluation in context~\citep{hicks_bibliometrics:_2015} and increased consideration of the disciplinary nature of the scientific enterprise is likely to result in improved models that yield further insight.
 

### 2019-07-19 rebuttal.tex
tweak

@@
 Please see the figure included in this response (noted as Figure 1), which was not included in the submitted paper due to space limitations.
-%was included in an earlier version of this manuscript submitted to another journal and was criticized for being confusing so we left it out in the submission to QSS. It 
 The figure specifically addresses the reviewer's point, and shows that both factors are in play:  (i) there is a difference when local and global networks are used to generate expected values, and  (ii)  disciplines can be different from each other.
-If space is not an issue, we  could include this in the paper, or perhaps as supplementary material (since we're already over the 10 page limit). %\newpage
+While we do not think this figure needs to be included in the manuscript, we  could include if necessary or make it available as supplementary material through FigShare or some other site.
 

### 2019-07-28 rebuttal.tex
fixed rebuttal

@@
 The remaining 15 references in Uzzi would have a probability of 1/16, whereas in our model they would have a probability of 1/20.
-In other words
-Uzzi's algorithm seeks to systematically shuffle every reference in the network but replacements are selected from the set \{x,a,b,c,d,e...\} rather than the multi-set \{x,x,x,x,x,b,c,d,,e...\} of eligible references.
+In other words, Uzzi's algorithm seeks to systematically shuffle every reference in the network but replacements are selected from the set \{x,a,b,c,d,e...n\} rather than the multi-set \{x,x,x,x,x,a,b,c,d,e...n\} of eligible references.
 

### 2019-09-10 cocit_r_v2.tex
added Wang, Veugelers, and Stephan reference and early edits

--- 2019-07-16 cocit_r.tex
@@
 
+\textcolor{green}{A related study by \cite{wang_bias_2017} does...fill in the blanks}
+
 \textcolor{blue}{Key to the findings of Uzzi {\em et al.}~is the random graph model used, and its underlying assumptions.
@@
 Such substitutions poorly model the disciplinary nature of scientific research and citation behavior~\citep{wallace_lariviere_gingras_2012,moed_measuring_2010,klavans_research_2017,garfield_1979}.
-In addition, under this random model, a reference cited many times in a given year is selected as a substituent with the same probability as a reference cited only once, which is inconsistent with the power law or lognormal citation distributions of citations described in the literature~\citep{stringer_statistical_2010,perline_strong_2005}.
+\textcolor{green}{In addition, under this random model, a reference cited many times in a given year is selected as a substituent with the same probability as a reference cited only once}.
 Accordingly, model misspecification is likely to arise on account of the simulated values not corresponding to the empirical data very well.}

### 2019-09-10 cocit_r_v2.tex
added Wang, Veugelers, and Stephan reference and early edits

@@
 Our study examines this question using  semantically-themed citation networks.
-\textcolor{blue}{We observe that trends reported to be true across the scientific literature do not hold for focused citation networks, and we conclude that inferring novelty through co-citation analysis requires disciplinary context.}
+We observe that trends reported to be true across the scientific literature do not hold for focused citation networks, and we conclude that inferring novelty through co-citation analysis requires disciplinary context.
 \end{abstract}
@@
 
-\textcolor{blue} {In a novel approach, \cite{uzzi_atypical_2013} used co-citation analysis to characterize a subset of highly cited articles with respect to both novel and conventional combinations of prior research.} The frequency with which references were co-cited  in 17.9 million articles and their cited references from the Web of Science (WoS) was calculated and expressed as journal pair frequencies (observed co-citation frequencies).
+In a novel approach, \cite{uzzi_atypical_2013} used co-citation analysis to characterize a subset of highly cited articles with respect to both novel and conventional combinations of prior research.
+The frequency with which references were co-cited  in 17.9 million articles and their cited references from the Web of Science (WoS) was calculated and expressed as journal pair frequencies (observed co-citation frequencies).
 Expected co-citation values were generated from randomized networks using Monte Carlo simulations under a random graph model.
@@
 
-\textcolor{green}{A related study by \cite{wang_bias_2017} does...fill in the blanks}
+\textcolor{green}{A related study by \cite{wang_bias_2017} also uses journal pairings to study novelty in scientific publications but focuses on previously undetected journal pairs to generate a novelty index}
 
-\textcolor{blue}{Key to the findings of Uzzi {\em et al.}~is the random graph model used, and its underlying assumptions.
+Key to the findings of Uzzi {\em et al.}~is the random graph model used, and its underlying assumptions.
 The citation switching algorithm used to generate expected values by substituting cited references with randomly selected references published in the same year is designed to preserve the number of publications, the number of references in each publication, and the year of publication of both publications and references.
@@
 \textcolor{green}{In addition, under this random model, a reference cited many times in a given year is selected as a substituent with the same probability as a reference cited only once}.
-Accordingly, model misspecification is likely to arise on account of the simulated values not corresponding to the empirical data very well.}
+Accordingly, model misspecification is likely to arise on account of the simulated values not corresponding to the empirical data very well.
 
@@
 While they also reported the trend that HNHC is more probable in highly cited papers, they observed that ``only 64.4\%  of  243  WoS  subject  categories'' in the Uzzi {\em et al.} study met the criterion of having the highest probability of hit papers in the HNHC category.
-Further, they observed that journals vary widely in terms of size and influence and that \textcolor{blue}{20 journals accounted for 15.9\% of co-citations in their measurements}.
+Further, they observed that journals vary widely in terms of size and influence and that 20 journals accounted for 15.9\% of co-citations in their measurements.
 Lastly, they noted that three multidisciplinary journals accounted for 9.4\% of all atypical combinations.
@@
 We hypothesized instead that modifying the normalization to constrain substitution references to be drawn only from the citation network being studied (the ``local network") rather than all of WoS
-(the ``global network") would reduce model misspecification by \textcolor{blue}{limiting substitutions from references that were ectopic to these networks.} Consequently, we used keyword searches of the scientific literature to construct exemplar citation networks themed around academic disciplines of interest: \emph{applied physics, immunology, and metabolism}.
-\textcolor{blue}{The cited references in these networks while predominantly aligned with the parent discipline (physics or life sciences in this case), also included articles from other disciplines.} Within these disciplinary frameworks, we calculated observed and expected co-citation frequencies using a refined random graph model and an efficient Monte Carlo simulation algorithm.
+(the ``global network") would reduce model misspecification by limiting substitutions from references that were ectopic to these networks.
+Consequently, we used keyword searches of the scientific literature to construct exemplar citation networks themed around academic disciplines of interest: \emph{applied physics, immunology, and metabolism}.
+The cited references in these networks while predominantly aligned with the parent discipline (physics or life sciences in this case), also included articles from other disciplines.
+Within these disciplinary frameworks, we calculated observed and expected co-citation frequencies using a refined random graph model and an efficient Monte Carlo simulation algorithm.
 
@@
 For citation shuffling, we developed a performant citation switching algorithm, \emph{runtime enhanced permuting citation switcher (repcs)}~\citep{GithubERNIE2019}, that randomly permuted citations grouped by year of publication to switch citations while preserving the year of publication for both articles and references, the number of publications and the number of references in each data set, and the disciplinary composition of the references in each data set.
-\textcolor{blue}{Our approach is different from previous studies in these ways: (i) we sampled citations in proportion to their citation frequency (equivalently from a multiset rather than a set) in order to better reflect citation practice,
+Our approach is different from previous studies in these ways: (i) we sampled citations in proportion to their citation frequency (equivalently from a multiset rather than a set) in order to better reflect citation practice,
 (ii) we permitted a substitution to match the original reference in a publication when the random selection process dictated it rather than attempting to enforce that a different reference be substituted, and (iii) we introduced an error correction step to delete any publications that accumulated duplicate references during the substitution process.
@@
 We also tested \emph{repcs}  under comparable conditions to \emph{umsj} and estimated a runtime advantage of at least two orders of magnitude.
-This runtime advantage was significant enough that we chose to use the \emph{repcs}   algorithm in our study and generated expected values averaged from 1,000 simulations for improved coverage of every data set we analyzed.}
+This runtime advantage was significant enough that we chose to use the \emph{repcs}   algorithm in our study and generated expected values averaged from 1,000 simulations for improved coverage of every data set we analyzed.
 
@@
 The principal difference between the two models we discuss is a single parameter--the set of references that can be used as substituents during the substitution process.
-\textcolor{blue}{The keyword search we use also has the advantage of selecting only relevant articles from multidisciplinary journals.
-However, it is important to note that the local networks we evaluated are not monodisciplinary, the references cited within exhibit disciplinary diversity}.
+The keyword search we use also has the advantage of selecting only relevant articles from multidisciplinary journals.
+However, it is important to note that the local networks we evaluated are not monodisciplinary, the references cited within exhibit disciplinary diversity.
 We provided several lines of evidence that showed that changing this one parameter from a global network to the local disciplinary network reduces model misspecification.
-} Using the constrained model (which allows substitutions only within the local network)  instead of the unconstrained model (which allows substitutions in the WoS network) produces different trends in terms of conventionality and novelty, depending on the network \textcolor{blue}{and the parent discipline.} In particular, when using the unconstrained model, highly cited papers were most likely to be in the HNHC category but this trend does not consistently hold when using the constrained model.
+Using the constrained model (which allows substitutions only within the local network)  instead of the unconstrained model (which allows substitutions in the WoS network) produces different trends in terms of conventionality and novelty, depending on the network and the parent discipline.
+In particular, when using the unconstrained model, highly cited papers were most likely to be in the HNHC category but this trend does not consistently hold when using the constrained model.
 Instead, we find that conventionality flavored with novelty is {\em not} generally a feature of impactful research.
@@
 More generally, these results show that the trends approaching universality in highly cited papers are not robust to changes in thresholds for defining high impact or high novelty articles, or with time, and may be the consequence of using a random model that has a poor fit to the observed data.
-On the other hand, while  the constrained model reduces model misspecification compared to the unconstrained model, \textcolor{blue}{this does not imply that the constrained model is reasonable nor that trends observed under the constrained model convincingly explain scientific practice.
-Indeed, there are significant  challenges in using random models to understand human behavior, of which citation practice is one example.}
+On the other hand, while  the constrained model reduces model misspecification compared to the unconstrained model, this does not imply that the constrained model is reasonable nor that trends observed under the constrained model convincingly explain scientific practice.
+Indeed, there are significant  challenges in using random models to understand human behavior, of which citation practice is one example.
 
@@
 For example, proximity defined by co-author networks~\citep{wallace_lariviere_gingras_2012} might be considered when defining probabilities for citation substitutions.
-\textcolor{blue}{Another interesting but challenging direction would be to find ways to distinguish intra-disciplinary from cross-disciplinary novelty.} Overall, evaluation in context~\citep{hicks_bibliometrics:_2015} and increased consideration of the disciplinary nature of the scientific enterprise is likely to result in improved models that yield further insight.
+Another interesting but challenging direction would be to find ways to distinguish intra-disciplinary from cross-disciplinary novelty.
+\textcolor{green}{In this respect, the related work of \citep{wang_bias_2017} is particularly insightful with its use of empirical data and observations on novelty, quality, dispersion, and kinetics of accrued citations of articles classified as novel.
+We note that journals are used as grouping units for articles in the three studies we discuss \citep{wang_bias_2017, uzzi_atypical_2013, boyack_vs_uzzi_2014} as well as this one.
+Such grouping, while appealing in its relative simplicity, obscures measurements of novel pairings at the article level.
+Journals are also of limited use in representing individual fields and repeating some of these studies using article clusters may be more informative~\cite{traag_louvain_2019, klavans_which_2017}}.
+Overall, evaluation in context~\citep{hicks_bibliometrics:_2015} and increased consideration of the disciplinary nature of the scientific enterprise is likely to result in improved models that yield further insight.
 
@@
 We are grateful to Kevin Boyack and Dick Klavans for constructively critical discussions.
-We thank two anonymous reviewers for their insightful comments.
+We thank the editor and two anonymous reviewers for their insightful comments.
 Research and development reported in this publication was partially supported by Federal funds from the National Institute on Drug Abuse, National Institutes of Health, US Department of Health and Human Services, under Contract Nos.
@@
 TW receives funding from the Grainger Foundation.
-All the code used in this study is freely available from a Github site~\citep{GithubERNIE2019}.
+The code used in this study is freely available from a Github site~\citep{GithubERNIE2019}.
 Access to the bibliographic data analyzed in this study requires a license from Clarivate Analytics, which had no role in funding, experimental design, review of results, and conclusions presented.
@@
 Infrastructure and workflows used to generate data used in this study were developed by AD, DK, SL, SD, and GC.
-All authors reviewed and commented on the manuscript, which was written by GC, JB, and TW.
+All authors reviewed the manuscript, which was written by GC, JB, and TW.
 

### 2019-09-10 cocit_r_v2.tex
update

@@
 
-\handlingeditor{Xi-Nian Zuo}
+\handlingeditor{Ludo Waltman}
 
@@
 
-\textcolor{green}{A related study by \cite{wang_bias_2017} also uses journal pairings to study novelty in scientific publications but focuses on previously undetected journal pairs to generate a novelty index}
+\textcolor{blue}{A related study by \cite{wang_bias_2017} also uses journal pairings to study novelty in scientific publications but focuses on previously undetected journal pairs to generate a novelty index}
 
@@
 Such substitutions poorly model the disciplinary nature of scientific research and citation behavior~\citep{wallace_lariviere_gingras_2012,moed_measuring_2010,klavans_research_2017,garfield_1979}.
-\textcolor{green}{In addition, under this random model, a reference cited many times in a given year is selected as a substituent with the same probability as a reference cited only once}.
+\textcolor{blue}{In addition, under this random model, a reference cited many times in a given year is selected as a substituent with the same probability as a reference cited only once}.
 Accordingly, model misspecification is likely to arise on account of the simulated values not corresponding to the empirical data very well.
@@
 Another interesting but challenging direction would be to find ways to distinguish intra-disciplinary from cross-disciplinary novelty.
-\textcolor{green}{In this respect, the related work of \citep{wang_bias_2017} is particularly insightful with its use of empirical data and observations on novelty, quality, dispersion, and kinetics of accrued citations of articles classified as novel.
-We note that journals are used as grouping units for articles in the three studies we discuss \citep{wang_bias_2017, uzzi_atypical_2013, boyack_vs_uzzi_2014} as well as this one.
-Such grouping, while appealing in its relative simplicity, obscures measurements of novel pairings at the article level.
+\textcolor{blue}{In this respect, the related work of \citep{wang_bias_2017} is particularly insightful with its use of empirical data and the observations made on novelty, quality, as well as dispersion and kinetics of accrued citations of articles classified as novel.}
+
+\textcolor{blue}{We note that journals are used as grouping units for articles in the three studies we discuss \citep{wang_bias_2017, uzzi_atypical_2013, boyack_vs_uzzi_2014} as well as this one.
+Such grouping, while appealing on account of relative simplicity, obscures measurements of novel pairings at the article level.
 Journals are also of limited use in representing individual fields and repeating some of these studies using article clusters may be more informative~\cite{traag_louvain_2019, klavans_which_2017}}.

### 2019-09-11 cocit_r_v2.tex
resetting revisions

@@
 \end{abstract}
+
+\section{Reviews}
+\subsection{Reviewer 1}
+
+\emph{The revised manuscript is much improved, and the specific comments to both reviews were very helpful.
+Overall, the authors have addressed all of the issues I’ve raised satisfactorily.
+The paper is important as a critique to Uzzi.
+The paper does not claim to present an alternative (better) way to identify innovative papers.
+But I was hoping that it could- and agree with the editor that the additional requirement (of comparing evaluations from both approaches) is not needed.
+In my second reading, I did realize one additional flaw that I would like the authors to address- upon the editor’s discretion.
+It looks like the study had a low threshold (just two references) for including papers in their studies.
+And we know that citation impact is correlated with the number of references.
+Is it possible that the signals they (or Uzzi) get for ‘innovative’ or ‘conforming’ are dependent on the number of references?
+This can be easily checked (a simple table of \# of references and likelihood of a signal of conformity or innovativeness) should be done.
+I suspect you won’t get any signal for papers with fewer than 5 references (how can one really assess either concept with such a small number?).
+But with 10 or more references- I’m quite comfortable with conclusions about impact being based on conformity and innovativeness.
+They may also find, when applying a reference threshold (such as 10) that they get different results.}
+
+\begin{itemize}
+\item Conventionality and Innovativeness are part of the framework developed by Uzzi.
+We neither challenge nor embrace the framework but simply use it a read out.
+The reviewer is holding us responsible for Uzzi's construct.
+\item We provide quantitative data addressing the reference count issue.
+\end{itemize}
+
+\subsection{Reviewer 2}
+
+\emph{I would like to thank the authors for the revision.
+However, I am afraid the revision has not sufficiently addressed my concerns.
+First, thanks for clarifying the reference shuffling.
+Let’s say Pub A has a reference B, A is in discipline X and B in discipline Y.
+I initially thought the local network approach swaps B with another reference which is also in discipline Y.
+The authors actually did was to swap B with another reference from another paper which is in discipline X.
+Is that correct?
+The authors have clarified it in the paper, but I think it still needs to improved, maybe provide some illustrative examples.
+Although my initial comment was because of misunderstanding the method, the underlying argument still holds.
+It is still unclear whether global or discipline-specific novelty is more appropriate.
+For example, bibliometrics papers cite a lot of mathematics paper, so in the pool of references cited by bibliometrics, combinations between bibliometrics and mathematics are very common.
+However, mathematics do not cite bibliometrics so much, then combinations between bibliometrices and mathematics seems rather unusual when examining the mathematics.
+I can see arguments supporting both the global and local approaches.
+I do not think this paper can get away with it without clarifying the conceptualization.
+Second, the relationship between novelty/conventionality and citation impact itself does not seem to be a ground truth.
+Using statistics about misspecification is based on a huge assumption, which needs to be made explicit and supported by conceptualization and theories.}
+
+An irresponsible choice of words- `I do not think this paper can get away with it...' We are not trying to get away with anything!
+Perhaps the reviewer confuses her/his own clumsy sophistry with our presentation?
+If so, it is most regrettable and we will strive to  ensure a distinction.
+Secondly, the reviewer's critique suffers from being somewhat incoherent.
+Even so....
+\begin{itemize}
+\item An illustration has been provided
+\item Yes, a difference between bibliometrics and mathematics may be that bibliometrics papers cite mathematics papers more often than the other way around.
+The local model accounts for this but the global one does not
+\item The relationship between novelty and conventionality is not a ground truth, we have never claimed it is.
+This framework was developed by Uzzi et al.
+(2013) and we have used it to enable \emph{ceteris paribus} comparisons
+\end{itemize}
 

### 2019-09-11 cocit_r_v2.tex
resetting revisions

@@
 \begin{itemize}
-\item Conventionality and Innovativeness are part of the framework developed by Uzzi.
-We neither challenge nor embrace the framework but simply use it a read out.
-The reviewer is holding us responsible for Uzzi's construct.
-\item We provide quantitative data addressing the reference count issue.
+\item This is an interesting point. We reviewed the literature in which correlation between reference count and citations is asserted. 
+\item We provide quantitative data addressing the reference count issue and conclude that the relationship is not a strong one...
 \end{itemize}
@@
 
-An irresponsible choice of words- `I do not think this paper can get away with it...' We are not trying to get away with anything!
-Perhaps the reviewer confuses her/his own clumsy sophistry with our presentation?
-If so, it is most regrettable and we will strive to  ensure a distinction.
-Secondly, the reviewer's critique suffers from being somewhat incoherent.
-Even so....
 \begin{itemize}
@@
 (2013) and we have used it to enable \emph{ceteris paribus} comparisons
+\end{itemize}
+
+\subsection{Editor}
+\emph{I have one other suggestion.
+In addition to the work on novelty by Brian Uzzi and colleagues, there is also work on novelty by Reinhilde Veugelers and colleagues, who operationalize novelty in a different way.
+For completeness, you may consider providing a brief discussion of the work by Veugelers and colleagues in your manuscript.}
+\begin{itemize}
+\item We thank you for bringing this to our attention.
+Discussing this paper broadens the scope of our manuscript and we've referenced it in the Discussion.
+As one of our co-authors pointed out, the definition of novelty is a little restrictive to say the least but the rest of the paper is excellent.
 \end{itemize}

### 2019-09-12 cocit_r_v2.tex
Revert "small fixes to response to review"
This reverts commit 7daf4f076b8cc61436aff618ea79e6566058aa92.

@@
 Overall, the authors have addressed all of the issues I’ve raised satisfactorily.
-The paper is important as a critique to Uzzi.
-The paper does not claim to present an alternative (better) way to identify innovative papers.
+The paper is important as a critique to Uzzi.The paper does not claim to present an alternative (better) way to identify innovative papers.
 But I was hoping that it could- and agree with the editor that the additional requirement (of comparing evaluations from both approaches) is not needed.
@@
 \begin{itemize}
-\item This is an interesting point. We reviewed the literature in which correlation between reference count and citations is asserted. 
-\item We provide quantitative data addressing the reference count issue and conclude that the relationship is not a strong one...
+\item This is an interesting point although it is not quite clear what is meant by signal.
+We chose to set the threshold at 2 references since it is the smallest number that could yield a reference pair.
+It is perhaps useful to be reminded that these reference pairs are then mapped to journal pairs whose frequencies are summed across the dataset being studied, then normalized and returned to the parent article as z-scores.
+The reviewer argues that 10 references (45 z-scores) would be a reassuring number.
+This choice appears intuitive rather than reasoned but may reflect valuable insight.
+However, there is a penalty for arbitrarily excluding low-reference publications.
+For example, restricting the applied physics dataset from 1985 we analyze (ap\_1985) to those with 5 references or less results in a loss of 28\% of the publications.
+We are loath to do so.
+\\
+
+\vspace{1mm}
+We also reviewed the literature in which correlation between reference count and citations is claimed.
+In particular, we studied Vieira and Gomes (2010), and Peters and van Raan (1994) since other articles asserting a correlation between reference count and citations seem to eventually trail back to these two.
+\begin{enumerate}
+\item Peters and van Raan used a set of 226 articles drawn from the bibliographies of 18 internationally recognized chemical engineers for the years 1977-1986.
+They observed a possible bi-phasic distribution when 5-year impact was measured in a histogram with reference count intervals of 5 between groups ($<=9, 10-14, 15-19, 20-24, 35-29, 30-34, >=35$).
+They reported a Pearson's correlation coefficient of 0.52 and inferred a weak but positive correlation (Fig 1d and Table 1) consistent with the observations of Moed \emph{et al} 1985.
+This is not very convincing (or easily compared to our larger datasets from later years) but we do respect the finding.
+
+\item More interestingly, Vieira and Gomes examined 226,166 articles from 2004 classified into Biology \& Biochemistry, Chemistry, Mathematics, and Physics per the WOS ESI.
+Biology and Biochemistry consisted of 455 journals, 44248 articles; Chemistry (574j, 97177a); Mathematics (387j, 20127a); and Physics (338j, 64614a).
+As far as we can tell, these authors counted total citations accumulated in around 5 years (the paper was submitted and accepted in 2009).
+Fig 9 shows a positive relationship between the number of references and the citations that differs in slope and intercept between subjects when a linear fit is applied to the data.
+Our study differs in that we are looking at different subsets of the data and counting citations for the first 8 years.
+
+We evaluated the relationship between references and citation counts on all 12 datasets we analyzed in this paper using the approach of Vieira and Gomes.
+The results are very interesting.
+When plotting reference counts (independent variable on the x axis) against the mean of citation counts we see a linear relationship that gets noisy after about papers with 75 references or more.
+This is consistent with the observations of Vieira and Gomes and not unexpected since it could be accounted for by review articles.
+However, when plotting citation counts (independent variable on the x axis) against the mean of reference counts the results suggest that publications with a broad range of cited references can accrue similar citations over the first 8 years since publication (figures).
+We conclude that Fig 9 of their paper masks variance of citations by plotting the mean citation count as a dependent variable.
+Thus, the basis for arguing that reference counts correlate with citation counts is a little shaky although it may be true for a narrow range of references.
+\end{enumerate}
+\vspace{2mm}
+\item However, we also provide quantitative data addressing the reference count issue and conclude that the relationship is not a strong one...
 \end{itemize}
@@
 \begin{itemize}
-\item An illustration has been provided
+\item An illustration has been generated that will become part of supplementary material.
 \item Yes, a difference between bibliometrics and mathematics may be that bibliometrics papers cite mathematics papers more often than the other way around.
-The local model accounts for this but the global one does not
+The local model accounts for this but the global one does not.
+We argue consistently that local models reduce mis-specification.
 \item The relationship between novelty and conventionality is not a ground truth, we have never claimed it is.
 This framework was developed by Uzzi et al.
-(2013) and we have used it to enable \emph{ceteris paribus} comparisons
+(2013) and we have used it to enable \emph{ceteris paribus} comparisons.
+We cannot address the question of the huge unstated assumption- we don't think we make such an assumption.
 \end{itemize}
@@
 \item We thank you for bringing this to our attention.
+We really ought to have cited it but we perhaps myopically focused on the details of the random graph approach.
 Discussing this paper broadens the scope of our manuscript and we've referenced it in the Discussion.
-As one of our co-authors pointed out, the definition of novelty is a little restrictive to say the least but the rest of the paper is excellent.
+As one of our co-authors pointed out, the definition of novelty is a little restrictive to say the least but the paper is an excellent one.
 \end{itemize}
@@
 \textcolor{blue}{We note that journals are used as grouping units for articles in the three studies we discuss \citep{wang_bias_2017, uzzi_atypical_2013, boyack_vs_uzzi_2014} as well as this one.
+While we used keyword searches to identify sets of articles, we still relied on journal grouping to generate z-scores.
 Such grouping, while appealing on account of relative simplicity, obscures measurements of novel pairings at the article level.

### 2019-09-15 Revision2Letter.tex
update

\documentclass[11pt, oneside]{article}   	% use "amsart" instead of "article" for AMSLaTeX format
\usepackage{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   		% ... or a4paper or a5paper or ... 
%\geometry{landscape}                		% Activate for rotated page geometry
%\usepackage[parfill]{parskip}    		% Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}				% Use pdf, png, jpg, or eps§ with pdflatex; use eps in DVI mode
								% TeX will automatically convert eps --> pdf in pdflatex		
\usepackage{amssymb}

%SetFonts

%SetFonts

\title{QSS27: Revision II}
\author{George Chacko}
%\date{}							% Activate to display a given date or no date

\begin{document}
\maketitle
%\section{}
%\subsection{}

Dear Dr. Waltman:

\vspace{5mm}
\raggedright 
Thank you for the opportunity to submit a revision. Again, we thank the reviewers for their diligence and professional courtesy. We have considered the comments from both reviewers carefully and provide a response below. The response is also reflected in a revised manuscript with blue text indicating where changes have been made to the first revision. We have also responded to your suggestion that we include a discussion of the work of Wang, Veugelers, and Stephan.

\vspace{3mm}
Sincerely
\vspace{5mm}

George Chacko

\section{Reviews}
\subsection{Reviewer 1}

\emph{The revised manuscript is much improved, and the specific comments to both reviews were very helpful. Overall, the authors have addressed all of the issues I’ve raised satisfactorily. The paper is important as a critique to Uzzi.The paper does not claim to present an alternative (better) way to identify innovative papers.  But I was hoping that it could- and agree with the editor that the additional requirement (of comparing evaluations from both approaches) is not needed.
In my second reading, I did realize one additional flaw that I would like the authors to address- upon the editor’s discretion.  It looks like the study had a low threshold (just two references) for including papers in their studies. And we know that citation impact is correlated with the number of references. Is it possible that the signals they (or Uzzi) get for ‘innovative’ or ‘conforming’ are dependent on the number of references? This can be easily checked (a simple table of \# of references and likelihood of a signal of conformity or innovativeness) should be done. I suspect you won’t get any signal for papers with fewer than 5 references (how can one really assess either concept with such a small number?).  But with 10 or more references- I'm quite comfortable with conclusions about impact being based on conformity and innovativeness. They may also find, when applying a reference threshold (such as 10) that they get different results.}

\begin{itemize}
\item The reference count issue is interesting although it is not quite clear what is meant by signal. We chose to set the threshold at 2 references since it is the smallest number that yields a reference pair. It is perhaps useful to be reminded that these reference pairs are then mapped to journal pairs whose frequencies are summed across the dataset being studied, then normalized, and finally returned to the parent article as z-scores. The reviewer argues that 10 references (45 z-scores) would be a reassuring number. This choice appears intuitive rather than reasoned but likely reflects insight. However, there is a penalty for arbitrarily excluding low-reference publications. For example, restricting the applied physics dataset from 1985 we analyze (ap\_1985) to those with 5 references or less results in a loss of 28\% of the publications and their associated references. \\

\vspace{1mm}
We reviewed the literature in which correlation between reference count and citations is claimed. In particular, we studied Peters and van Raan (1994) and Vieira and Gomes (2010) since other articles reporting a correlation between reference count and citations seem to eventually trail back to these two. 
\begin{enumerate}
\item Peters and van Raan used a set of 226 articles drawn from the bibliographies of 18 internationally recognized chemical engineers for the years 1977-1986. They observed a possible bi-phasic distribution when 5-year impact was measured in a histogram with reference count intervals of 5 between groups ($<=9, 10-14, 15-19, 20-24, 35-29, 30-34, >=35$). They reported a Pearson's correlation coefficient of 0.52 and inferred a weak but positive correlation (Fig 1d and Table 1 of their paper) consistent with the observations of Moed \emph{et al} 1985. This is not very convincing (or easily compared to our larger datasets from later years) but we do respect the finding.

\item More interestingly, Vieira and Gomes examined 226,166 articles from 2004 classified into Biology \& Biochemistry, Chemistry, Mathematics, and Physics per the WOS ESI. Biology and Biochemistry consisted of 455 journals, 44248 articles; Chemistry (574j, 97177a); Mathematics (387j, 20127a); and Physics (338j, 64614a). Our study differs in that we are looking at different subsets of the data, larger amounts of data, and counting citations for the first 8 years.

As far as we can tell, these authors counted total citations accumulated in around 5 years (the paper was submitted and accepted in 2009).  Fig 9 of their paper shows a positive relationship between the number of references and the citations that differs in slope and intercept between subjects when a linear fit is applied to the data.  We evaluated the relationship between references and citation counts on all 9 local networks we analyzed in this paper using the approach of Vieira and Gomes. The results are very interesting. When plotting reference counts (independent variable on the x axis) against the mean of citation counts we see a linear relationship that gets noisy after about papers with 75 references or more (our Figure 1 below). This is consistent with the observations of Vieira and Gomes and not unexpected since the noisy part of the data could be accounted for by review articles. However, when plotting citation counts (independent variable on the x axis) against the mean of reference counts the results suggest that publications with a broad range of cited references can accrue similar citations over the first 8 years since publication (our Figures 2 \& 3). We conclude that Fig 9 of Vieira and Gomes masks the variance of citation counts when the mean citation count is plotted as a dependent variable. Thus, the basis for arguing that reference counts correlate with citation counts is a little shaky although it may be true for a narrow range and subset of articles (Figure 3, column 3 in particular). In other words, trying to focus the analysis on just a subset of the data based on number of references is not likely to provide much insight. Nor will studying this be simple as not only reference counts but a number of factors would seem to explain the variance (both Peters and van Raan \& Vieira and Gomes).

However, controlling for the number of references (as a proxy for the number of z-scores) in a publication appears reasonable so we provide some data below. Perhaps this is what the reviewer had in mind as well?
\end{enumerate}
\item INSERT Jim's data
\end{itemize}

\subsection{Reviewer 2}

\emph{I would like to thank the authors for the revision.  However, I am afraid the revision has not sufficiently addressed my concerns. First, thanks for clarifying the reference shuffling.  Let’s say Pub A has a reference B, A is in discipline X and B in discipline Y.  I initially thought the local network approach swaps B with another reference which is also in discipline Y.  The authors actually did was to swap B with another reference from another paper which is in discipline X.  Is that correct?  The authors have clarified it in the paper, but I think it still needs to improved, maybe provide some illustrative examples.  Although my initial comment was because of misunderstanding the method, the underlying argument still holds.  It is still unclear whether global or discipline-specific novelty is more appropriate.  For example, bibliometrics papers cite a lot of mathematics paper, so in the pool of references cited by bibliometrics, combinations between bibliometrics and mathematics are very common.  However, mathematics do not cite bibliometrics so much, then combinations between bibliometrices and mathematics seems rather unusual when examining the mathematics.  I can see arguments supporting both the global and local approaches.  I do not think this paper can get away with it without clarifying the conceptualization. Second, the relationship between novelty/conventionality and citation impact itself does not seem to be a ground truth. Using statistics about misspecification is based on a huge assumption, which needs to be made explicit and supported by conceptualization and theories.}

\begin{itemize}
\item An illustration has been generated that will be added to supplementary material that contains material from the first rebuttal.
\item Yes, the reviewers description of our citation swapping strategy is now correct. Further, a difference between bibliometrics and mathematics may be that bibliometrics papers cite mathematics papers more often than the other way around. The local model accounts for this but the global one does not. We argue consistently that local models reduce mis-specification and provide data to support the argument.
\item The relationship between novelty, conventionality, and citation counts is not a ground truth, we have never claimed it is. This framework was developed by Uzzi et al. (2013) and we have used it to enable \emph{ceteris paribus} comparisons. We cannot address the question of the `huge assumption', which is not actually stated by the reviewer- we don't think we make such an assumption.
\end{itemize}

\subsection{Editor}
\emph{I have one other suggestion. In addition to the work on novelty by Brian Uzzi and colleagues, there is also work on novelty by Reinhilde Veugelers and colleagues, who operationalize novelty in a different way. For completeness, you may consider providing a brief discussion of the work by Veugelers and colleagues in your manuscript.}
\begin{itemize}
\item We thank you for bringing this publication to our attention. We really ought to have cited it but we were guilty of, perhaps myopically, focusing on the details of the random graph approach. Discussing this paper broadens the context of our manuscript and we've now referenced it in the Discussion. As one of our co-authors observes, the definition of novelty is a little restrictive to say the least but the paper is an excellent one and we are happy to reference it.
\item We have also added a sentence about the limitations of grouping by journals and have suggested that analyzing article level clusters may be more insightful. This has come out of our more recent interest in clustering, which informs this new direction.
 \end{itemize}

 \newpage

\begin{figure}[tbhp]
\centering
\includegraphics[width=0.6\linewidth]{all_ref_cit_year_gp}     
\caption{Apparent linear relationship between reference count(x-axis) and citation count(y-axis). Data from 9 local networks analyzed in our paper are shown. These results are approximately consistent with the observations of Vieira and Gomes(2010)} 
\label{fig:refcit}
\end{figure}
\newpage

\begin{figure}[tbhp]
\centering
\includegraphics[width=0.6\linewidth]{all_cit_ref_year_gp}     
\caption{Inversion of axes unmasks variance in citation counts. In this case, the mean of reference counts is plotted as a dependent variable and citation counts are plotted as an independent variable. Data from 9 local networks analyzed in our paper are shown as in previous Figure. These results are not consistent with the observations  of Vieira and Gomes(2010)} 
\label{fig:citref}
\end{figure}
\newpage

\begin{figure}[tbhp]
\centering
\includegraphics[width=0.9\linewidth]{all_cit_ref_year_gp_zoom}     
\caption{Inversion of axes unmasks variance in citation counts. In this case, the mean of reference counts is plotted as a dependent variable and citation counts are plotted as an independent variable [ZOOMED from Figure 2]. Data from 9 local networks analyzed in our paper are shown. To enable better visualization, the citation counts from Fig 2 are restricted at the lower end to the 90th percentile or greater for the ap\_1985 dataset (the smallest of the 9 datasets) and to an upper limit of 2000 citations to exclude a single outlier value,. These results are not consistent with the observations  of Vieira and Gomes(2010)} 
\label{fig:refcit}
\end{figure}
\newpage

\end{document}

### 2019-09-15 cocit_r_v2.tex
update

--- 2019-09-11 cocit_r_v2.tex
@@
 \end{abstract}
-
-\section{Reviews}
-\subsection{Reviewer 1}
-
-\emph{The revised manuscript is much improved, and the specific comments to both reviews were very helpful.
-Overall, the authors have addressed all of the issues I’ve raised satisfactorily.
-The paper is important as a critique to Uzzi.
-The paper does not claim to present an alternative (better) way to identify innovative papers.
-But I was hoping that it could- and agree with the editor that the additional requirement (of comparing evaluations from both approaches) is not needed.
-In my second reading, I did realize one additional flaw that I would like the authors to address- upon the editor’s discretion.
-It looks like the study had a low threshold (just two references) for including papers in their studies.
-And we know that citation impact is correlated with the number of references.
-Is it possible that the signals they (or Uzzi) get for ‘innovative’ or ‘conforming’ are dependent on the number of references?
-This can be easily checked (a simple table of \# of references and likelihood of a signal of conformity or innovativeness) should be done.
-I suspect you won’t get any signal for papers with fewer than 5 references (how can one really assess either concept with such a small number?).
-But with 10 or more references- I’m quite comfortable with conclusions about impact being based on conformity and innovativeness.
-They may also find, when applying a reference threshold (such as 10) that they get different results.}
-
-\begin{itemize}
-\item Conventionality and Innovativeness are part of the framework developed by Uzzi.
-We neither challenge nor embrace the framework but simply use it a read out.
-The reviewer is holding us responsible for Uzzi's construct.
-\item We provide quantitative data addressing the reference count issue.
-\end{itemize}
-
-\subsection{Reviewer 2}
-
-\emph{I would like to thank the authors for the revision.
-However, I am afraid the revision has not sufficiently addressed my concerns.
-First, thanks for clarifying the reference shuffling.
-Let’s say Pub A has a reference B, A is in discipline X and B in discipline Y.
-I initially thought the local network approach swaps B with another reference which is also in discipline Y.
-The authors actually did was to swap B with another reference from another paper which is in discipline X.
-Is that correct?
-The authors have clarified it in the paper, but I think it still needs to improved, maybe provide some illustrative examples.
-Although my initial comment was because of misunderstanding the method, the underlying argument still holds.
-It is still unclear whether global or discipline-specific novelty is more appropriate.
-For example, bibliometrics papers cite a lot of mathematics paper, so in the pool of references cited by bibliometrics, combinations between bibliometrics and mathematics are very common.
-However, mathematics do not cite bibliometrics so much, then combinations between bibliometrices and mathematics seems rather unusual when examining the mathematics.
-I can see arguments supporting both the global and local approaches.
-I do not think this paper can get away with it without clarifying the conceptualization.
-Second, the relationship between novelty/conventionality and citation impact itself does not seem to be a ground truth.
-Using statistics about misspecification is based on a huge assumption, which needs to be made explicit and supported by conceptualization and theories.}
-
-An irresponsible choice of words- `I do not think this paper can get away with it...' We are not trying to get away with anything!
-Perhaps the reviewer confuses her/his own clumsy sophistry with our presentation?
-If so, it is most regrettable and we will strive to  ensure a distinction.
-Secondly, the reviewer's critique suffers from being somewhat incoherent.
-Even so....
-\begin{itemize}
-\item An illustration has been provided
-\item Yes, a difference between bibliometrics and mathematics may be that bibliometrics papers cite mathematics papers more often than the other way around.
-The local model accounts for this but the global one does not
-\item The relationship between novelty and conventionality is not a ground truth, we have never claimed it is.
-This framework was developed by Uzzi et al.
-(2013) and we have used it to enable \emph{ceteris paribus} comparisons
-\end{itemize}
 

### 2019-09-15 cocit_r_v2.tex
tweaks

@@
 Citation and network analysis of  scientific literature reveals information on semantic relationships between publications, collaboration between scientists, and the practice of citation itself~\citep{garfield_citation_1955,de_solla_price_networks_1965,newman_structure_2001,Shi:2010:CHI:1816123.1816131,patience_pmid28560354,stigler_1994}.
-Co-citation, the frequency with which two documents are cited together in other documents, provides additional insights, including the identification of semantically related documents, fields, specializations, and new ideas in science~\citep{small_co-citation_1973, marshakova-shaikevich_co-citation_1973,boyack_co-citation_2010, 10.3389/frma.2018.00020}.
+Co-citation, the frequency with which two documents are cited together in other documents, provides additional insights, including the identification of semantically related documents, fields, specializations, and new ideas in science~\citep{small_co-citation_1973, marshakova-shaikevich_co-citation_1973,boyack_co-citation_2010, 10.3389/frma.2018.00020,wang_bias_2017}.
 
-In a novel approach, \cite{uzzi_atypical_2013} used co-citation analysis to characterize a subset of highly cited articles with respect to both novel and conventional combinations of prior research.
+In a novel approach, \citep{uzzi_atypical_2013} used co-citation analysis to characterize a subset of highly cited articles with respect to both novel and conventional combinations of prior research.
 The frequency with which references were co-cited  in 17.9 million articles and their cited references from the Web of Science (WoS) was calculated and expressed as journal pair frequencies (observed co-citation frequencies).
-Expected co-citation values were generated from randomized networks using Monte Carlo simulations under a random graph model.
+Expected co-citation values were generated using Monte Carlo simulations under a random graph model.
 Observed frequencies were then normalized (shifted and scaled) to averaged expected values from ten randomized networks and termed as \emph{z-scores}.
@@
 
-\textcolor{blue}{A related study by \cite{wang_bias_2017} also uses journal pairings to study novelty in scientific publications but focuses on previously undetected journal pairs to generate a novelty index}
-
 Key to the findings of Uzzi {\em et al.}~is the random graph model used, and its underlying assumptions.
@@
 Importantly, disciplinary origin does not affect the probability that a reference is selected to replace another one.
-For example, a reference in quantum physics can be substituted, with equal probability, by a reference in quantum physics, quantum chemistry, classical literature, entomology, or anthropology.
-Such substitutions poorly model the disciplinary nature of scientific research and citation behavior~\citep{wallace_lariviere_gingras_2012,moed_measuring_2010,klavans_research_2017,garfield_1979}.
-\textcolor{blue}{In addition, under this random model, a reference cited many times in a given year is selected as a substituent with the same probability as a reference cited only once}.
+For example, a reference in quantum physics can be substituted, with equal probability, by a reference published in the same year but from the field of  quantum physics, quantum chemistry, classical literature, entomology, or anthropology.
+Such substitutions do not account for the disciplinary nature of scientific research and citation behavior~\citep{wallace_lariviere_gingras_2012,moed_measuring_2010,klavans_research_2017,garfield_1979} very well.
 Accordingly, model misspecification is likely to arise on account of the simulated values not corresponding to the empirical data very well.
 
-A follow-up study by \cite{boyack_vs_uzzi_2014} explored the impact of discipline and journal effects on these definitions of conventionality and novelty.
+A follow-up study by \citep{boyack_vs_uzzi_2014} explored the impact of discipline and journal effects on these definitions of conventionality and novelty.
 While their study had some methodological differences in the use of Scopus data rather than WoS data, a smaller data set, and a $\chi^2$ calculation rather than Monte Carlo simulations to generate expected values of journal pairs, Boyack and Klavans noted strong effects from disciplines and journals.
@@
 For citation shuffling, we developed a performant citation switching algorithm, \emph{runtime enhanced permuting citation switcher (repcs)}~\citep{GithubERNIE2019}, that randomly permuted citations grouped by year of publication to switch citations while preserving the year of publication for both articles and references, the number of publications and the number of references in each data set, and the disciplinary composition of the references in each data set.
-Our approach is different from previous studies in these ways: (i) we sampled citations in proportion to their citation frequency (equivalently from a multiset rather than a set) in order to better reflect citation practice,
-(ii) we permitted a substitution to match the original reference in a publication when the random selection process dictated it rather than attempting to enforce that a different reference be substituted, and (iii) we introduced an error correction step to delete any publications that accumulated duplicate references during the substitution process.
-As a benchmark, we used the citation switching algorithm of ~\cite{uzzi_atypical_2013}, henceforth referred to  as \emph{umsj} (as also done in~\cite{boyack_vs_uzzi_2014}), using code kindly provided by the authors.
-A single comparative analysis showed that while 10 simulations of the WoS 1985 data set (391,860 publications) completed in 2,186 hours using the \emph{umsj} algorithm, it completed in less than one hour using our implementation of the \emph{repcs}   algorithm on a Spark  cluster.
-Using either the \emph{repcs}   or \emph{umsj} algorithms for 10 simulations resulted in expected value coverage of 75\% of the observed journal pair frequencies.
-Subsequent development and testing of \emph{repcs} resulted in 99\% coverage of observed journal pairs when 1,000 simulations were conducted.
+\textcolor{blue}{Our approach is different from previous studies in these ways: (i) we sampled citations in proportion to their citation frequency (equivalently from a multiset rather than a set) in order to better reflect citation practice,
+(ii) we permitted a substitution to match the original reference in a publication when the random selection process dictated it rather than attempting to enforce that a different reference be substituted, and (iii) we introduced an error correction step to delete any publications that accumulated duplicate references during the substitution process.}  As a benchmark, we used the citation switching algorithm of ~\citep{uzzi_atypical_2013}, henceforth referred to  as \emph{umsj} (as also done in~\citep{boyack_vs_uzzi_2014}), using code kindly provided by the authors.
+A single comparative analysis showed that while 10 simulations of the WoS 1985 data set (391,860 selected articles) completed in 2,186 hours using the \emph{umsj} algorithm, it completed in less than one hour using our implementation of the \emph{repcs}   algorithm on a Spark  cluster.
 We also tested \emph{repcs}  under comparable conditions to \emph{umsj} and estimated a runtime advantage of at least two orders of magnitude.
@@
 Thus, there is a strong bias towards citations that are {\em intra-network}.
-Our observations are in agreement with \cite{wallace_lariviere_gingras_2012} who found that, often, a majority of an article's citations are from the specialty of the article, even though that percentage varied among disciplines in the eight specialties they investigated (from approximately 39\% to 89\% for 2006).
+Our observations are in agreement with \citep{wallace_lariviere_gingras_2012} who found that, often, a majority of an article's citations are from the specialty of the article, even though that percentage varied among disciplines in the eight specialties they investigated (from approximately 39\% to 89\% for 2006).
 Furthermore, these findings argue that a discipline-indifferent random graph model would exhibit misspecification in deviating substantially from the empirical data, and supports the  concern about definitions of  innovation and conventionality that are based on deviation from expected values.
@@
 Instead, we find that conventionality flavored with novelty is {\em not} generally a feature of impactful research.
-Further,  high ``novelty" is not always indicative of impactful research (as reflected in citation counts), as shown by both Immunology and Metabolism having their highest hit rates for low novelty (Figure \ref{fig:Fig2}).
+Further,  high ``novelty" is not always indicative of impactful research \textcolor{blue}{(as measured by citation counts, which should themselves be interpreted with caution)}, as shown by both Immunology and Metabolism having their highest hit rates for low novelty (Figure \ref{fig:Fig2}).
 
@@
 Indeed, there are significant  challenges in using random models to understand human behavior, of which citation practice is one example.
+\textcolor{blue}{As we note, \emph{vide supra}, under our conditions of analysis, the trends for all three disciplinary networks are different from those for WoS.}
 
@@
 Another interesting but challenging direction would be to find ways to distinguish intra-disciplinary from cross-disciplinary novelty.
-\textcolor{blue}{In this respect, the related work of \citep{wang_bias_2017} is particularly insightful with its use of empirical data and the observations made on novelty, quality, as well as dispersion and kinetics of accrued citations of articles classified as novel.}
+\textcolor{blue}{In this respect, the related work of \citep{wang_bias_2017} is insightful with its use of empirical data and the observations made on novelty, quality, as well as dispersion and kinetics of accrued citations of articles.}
 
@@
 While we used keyword searches to identify sets of articles, we still relied on journal grouping to generate z-scores.
-Such grouping, while appealing on account of relative simplicity, obscures measurements of novel pairings at the article level.
-Journals are also of limited use in representing individual fields and repeating some of these studies using article clusters may be more informative~\cite{traag_louvain_2019, klavans_which_2017}}.
-Overall, evaluation in context~\citep{hicks_bibliometrics:_2015} and increased consideration of the disciplinary nature of the scientific enterprise is likely to result in improved models that yield further insight.
+Such grouping, while appealing on account of its relative simplicity, obscures measurements of novel pairings at the article level.
+Journals are also of limited use in representing individual fields and repeating some of these studies using article clusters may be more informative~\citep{traag_louvain_2019, klavans_which_2017}}.
+Overall, evaluation in context~\citep{hicks_bibliometrics:_2015} and appropriate consideration of the disciplinary nature of the scientific enterprise is likely to result in improved models that yield further insight.
 
 \acknowledgments
- We thank the authors of \cite{uzzi_atypical_2013} for sharing their simulation code.
+ We thank the authors of \citep{uzzi_atypical_2013} for sharing their simulation code.
 We are grateful to Kevin Boyack and Dick Klavans for constructively critical discussions.
@@
 TW receives funding from the Grainger Foundation.
-The code used in this study is freely available from a Github site~\citep{GithubERNIE2019}.
+Code generated for this this study is freely available from a Github site~\citep{GithubERNIE2019}.
 Access to the bibliographic data analyzed in this study requires a license from Clarivate Analytics, which had no role in funding, experimental design, review of results, and conclusions presented.

### 2019-09-15 Revision2Letter.tex
tweaks

@@
 Again, we thank the reviewers for their diligence and professional courtesy.
-We have considered the comments from both reviewers carefully and provide a response below.
-The response is also reflected in a revised manuscript with blue text indicating where changes have been made to the first revision.
+We have considered their comments and provide a response below.
 We have also responded to your suggestion that we include a discussion of the work of Wang, Veugelers, and Stephan.
+Our response is reflected in a revised manuscript with blue text indicating where changes have been made to the first revision or where we have made minor edits to assist clarity.
 
@@
 Overall, the authors have addressed all of the issues I’ve raised satisfactorily.
-The paper is important as a critique to Uzzi.The paper does not claim to present an alternative (better) way to identify innovative papers.
+The paper is important as a critique to Uzzi.
+The paper does not claim to present an alternative (better) way to identify innovative papers.
 But I was hoping that it could- and agree with the editor that the additional requirement (of comparing evaluations from both approaches) is not needed.
@@
 \begin{itemize}
-\item The reference count issue is interesting although it is not quite clear what is meant by signal.
-We chose to set the threshold at 2 references since it is the smallest number that yields a reference pair.
-It is perhaps useful to be reminded that these reference pairs are then mapped to journal pairs whose frequencies are summed across the dataset being studied, then normalized, and finally returned to the parent article as z-scores.
-The reviewer argues that 10 references (45 z-scores) would be a reassuring number.
-This choice appears intuitive rather than reasoned but likely reflects insight.
-However, there is a penalty for arbitrarily excluding low-reference publications.
-For example, restricting the applied physics dataset from 1985 we analyze (ap\_1985) to those with 5 references or less results in a loss of 28\% of the publications and their associated references.
-\\
-
-\vspace{1mm}
-We reviewed the literature in which correlation between reference count and citations is claimed.
+\item We reviewed the literature in which correlation between reference count and citations is claimed.
 In particular, we studied Peters and van Raan (1994) and Vieira and Gomes (2010) since other articles reporting a correlation between reference count and citations seem to eventually trail back to these two.
@@
 They reported a Pearson's correlation coefficient of 0.52 and inferred a weak but positive correlation (Fig 1d and Table 1 of their paper) consistent with the observations of Moed \emph{et al} 1985.
-This is not very convincing (or easily compared to our larger datasets from later years) but we do respect the finding.
+This is not very convincing (or easily compared to our larger datasets from later years) but is pertinent.
 
@@
 Biology and Biochemistry consisted of 455 journals, 44248 articles; Chemistry (574j, 97177a); Mathematics (387j, 20127a); and Physics (338j, 64614a).
-Our study differs in that we are looking at different subsets of the data, larger amounts of data, and counting citations for the first 8 years.
-
 As far as we can tell, these authors counted total citations accumulated in around 5 years (the paper was submitted and accepted in 2009).
+Our study differs in that we look at different subsets of the data, larger amounts of data, and count citations for the first 8 years.
+\\
+\vspace{3mm}
 Fig 9 of their paper shows a positive relationship between the number of references and the citations that differs in slope and intercept between subjects when a linear fit is applied to the data.
@@
 The results are very interesting.
-When plotting reference counts (independent variable on the x axis) against the mean of citation counts we see a linear relationship that gets noisy after about papers with 75 references or more (our Figure 1 below).
+When plotting reference counts (independent variable on the x axis) against the mean of citation counts we see a linear relationship that gets noisy after about papers with 75 references or more (Figure 1 of this document below).
 This is consistent with the observations of Vieira and Gomes and not unexpected since the noisy part of the data could be accounted for by review articles.
@@
 We conclude that Fig 9 of Vieira and Gomes masks the variance of citation counts when the mean citation count is plotted as a dependent variable.
-Thus, the basis for arguing that reference counts correlate with citation counts is a little shaky although it may be true for a narrow range and subset of articles (Figure 3, column 3 in particular).
-In other words, trying to focus the analysis on just a subset of the data based on number of references is not likely to provide much insight.
-Nor will studying this be simple as not only reference counts but a number of factors would seem to explain the variance (both Peters and van Raan \& Vieira and Gomes).
 
-However, controlling for the number of references (as a proxy for the number of z-scores) in a publication appears reasonable so we provide some data below.
-Perhaps this is what the reviewer had in mind as well?
+Thus, the basis for arguing that reference counts generally correlates with citation counts seems a little shaky although it may be true for a narrow range and subset of articles (Figure 3, column 3 in particular).
+A number of factors help explain variance in citation counts (both Peters and van Raan \& Vieira and Gomes) and focusing on reference count alone is distracting to the purpose of our paper.
+
+\item Nevertheless, the reference count issue raised is interesting in itself (although it is not quite clear what is meant by signal) so we have added a sentence to the Discussion addressing it.
+The reviewer argues that 10 references (45 z-scores/article) would be a reassuring number.
+This choice appears intuitive rather than reasoned.
+We chose to set the threshold at 2 references since it is the smallest number that yields a reference pair.
+This threshold also supports comparison with Uzzi's data.
+It is perhaps useful to be reminded that these reference pairs are then mapped to journal pairs whose frequencies are summed across the dataset being studied, then normalized, and finally returned to the parent article as z-scores.
+Lastly, there is a penalty for arbitrarily excluding low-reference publications.
+For example, restricting the applied physics dataset from 1985 (ap\_1985) to publications with 5 references or less results in a loss of 28\% of the publications and associated references.
+
+\vspace{3mm} Even so, \emph{we INSERT Jim's new data here... }
+
+\begin{table}[ht]
+\begin{centering}
+\caption{Hit Rates By Category: Effect of Omitting Articles with 10 and Fewer References}
+\vspace{3mm}
+\begin{tabular}{|c crr rrr r|}
+ \hline
+ Dataset & Year & Hit Rate & Omitted  & LNLC & LNHC & HNLC & HNHC \\ 
+  \hline
+Metabolism & 2005&1\%&& 0.6& \bf{1.3}& 0.7& \bf{1.3} \\ 
+Metabolism & 2005&1\%& \checkmark & 0.7& \bf{1.4}& 0.7& \bf{1.2} \\ 
+\hline
+Metabolism & 2005&2\%&& 1.0& \bf{2.5}& 1.5& \bf{2.6} \\ 
+Metabolism & 2005&2\%& \checkmark & 1.2& \bf{2.7}& 1.5& \bf{2.5} \\ 
+\hline
+Metabolism & 2005&5\%&& 2.3& 6.0& 3.9& \bf{6.6} \\ 
+Metabolism & 2005&5\%& \checkmark & 2.7& \bf{6.3} & 3.8& \bf{6.4} \\ 
+\hline
+Metabolism & 2005&10\%&& 4.1& 11.4& 8.1& \bf{12.6} \\ 
+Metabolism & 2005&10\%& \checkmark & 5.3& \bf{12.0} & 8.1& \bf{12.5} \\ 
+\hline
+\end{tabular} \\
+\end{centering}
+\end{table} 
 \end{enumerate}
-\item INSERT Jim's data
 \end{itemize}
@@
 \begin{itemize}
-\item An illustration has been generated that will be added to supplementary material that contains material from the first rebuttal.
-\item Yes, the reviewers description of our citation swapping strategy is now correct.
+\item An illustration has been generated that will be added to supplementary material that contains figures from the first rebuttal.
+\item Yes, the reviewer's description of our citation swapping strategy is now correct.
 Further, a difference between bibliometrics and mathematics may be that bibliometrics papers cite mathematics papers more often than the other way around.
@@
 We argue consistently that local models reduce mis-specification and provide data to support the argument.
-\item The relationship between novelty, conventionality, and citation counts is not a ground truth, we have never claimed it is.
+\item We agree with the reviewer that Uzzi et al.
+make an assumption regarding this connection between novelty, conventionality, and citation counts.
+We have not portrayed this assumption as a ground truth in the manuscript.
 This framework was developed by Uzzi et al.
-(2013) and we have used it to enable \emph{ceteris paribus} comparisons.
-We cannot address the question of the `huge assumption', which is not actually stated by the reviewer- we don't think we make such an assumption.
+(2013) and we have used it to enable \emph{ceteris paribus} comparisons between our work and prior art.
+Furthermore, the analysis we provided using K-L divergence (between a generative model and the empirical data) establishes that there is a reduction in model misspecification by restricting to local networks and is independent of this assumption.
 \end{itemize}
@@
 \item We thank you for bringing this publication to our attention.
-We really ought to have cited it but we were guilty of, perhaps myopically, focusing on the details of the random graph approach.
-Discussing this paper broadens the context of our manuscript and we've now referenced it in the Discussion.
-As one of our co-authors observes, the definition of novelty is a little restrictive to say the least but the paper is an excellent one and we are happy to reference it.
-\item We have also added a sentence about the limitations of grouping by journals and have suggested that analyzing article level clusters may be more insightful.
-This has come out of our more recent interest in clustering, which informs this new direction.
+We really ought to have mentioned it but we were focused on the details of the random graph approach in local and global contexts.
+Discussing this paper broadens the context of our manuscript and we've now referenced it in both the Introduction and Discussion.
+The definition of novelty is a little restrictive in this paper but it makes a number of excellent points.
+\item We added a sentence about the limitations of grouping by journals and have suggested that analyzing article level clusters may be more insightful.
+We have also sounded a cautionary note (that ought to be superfluous) about the limitations of using citation counts as a readout for impact.
 \end{itemize}

### 2019-09-15 cocit_r_v2.tex
tweaks

--- 2019-09-15 cocit_r_v2.tex
@@
 We provided several lines of evidence that showed that changing this one parameter from a global network to the local disciplinary network reduces model misspecification.
-Using the constrained model (which allows substitutions only within the local network)  instead of the unconstrained model (which allows substitutions in the WoS network) produces different trends in terms of conventionality and novelty, depending on the network and the parent discipline.
+Using the constrained model (which allows substitutions only within the local network)  instead of the unconstrained model (which allows substitutions in the WoS network) produces different trends in terms of conventionality and novelty, depending on the network and the originating discipline.
 In particular, when using the unconstrained model, highly cited papers were most likely to be in the HNHC category but this trend does not consistently hold when using the constrained model.
@@
 Another interesting but challenging direction would be to find ways to distinguish intra-disciplinary from cross-disciplinary novelty.
-\textcolor{blue}{In this respect, the related work of \citep{wang_bias_2017} is particularly insightful with its use of empirical data and the observations made on novelty, quality, as well as dispersion and kinetics of accrued citations of articles classified as novel.}
+\textcolor{blue}{In this respect, the related work of \citep{wang_bias_2017} is insightful with its use of empirical data and observations made on novelty and quality, as well as dispersion and kinetics of accrued citations of articles classified as novel.}
 
@@
 Such grouping, while appealing on account of relative simplicity, obscures measurements of novel pairings at the article level.
-Journals are also of limited use in representing individual fields and repeating some of these studies using article clusters may be more informative~\cite{traag_louvain_2019, klavans_which_2017}}.
-Overall, evaluation in context~\citep{hicks_bibliometrics:_2015} and increased consideration of the disciplinary nature of the scientific enterprise is likely to result in improved models that yield further insight.
+Journals are also of limited use in representing individual fields and repeating some of these studies using article clusters may be more informative~\cite{traag_louvain_2019, klavans_which_2017}.
+We also acknowledge the limitations of using citation counts to identify impactful publications.
+Various factors contribute to citations \citep{peters_determinants_1994, vieira_citations_2010} and further study in the context of co-citation may be merited.
+Overall, evaluation in context~\citep{hicks_bibliometrics:_2015} and further consideration of the disciplinary nature of the scientific enterprise is likely to result in improved models that yield further insight.}
 

### 2019-09-15 cocit_r_v3.tex

--- 2019-09-15 cocit_r_v2.tex
@@
 Despite different methods used to generate expected values, both of these key preceding studies measured co-citation frequencies across the scientific literature (using either WoS or Scopus) and normalized them without disciplinary constraints before subsequently analyzing disciplinary subsets.
-We hypothesized instead that modifying the normalization to constrain substitution references to be drawn only from the citation network being studied (the ``local network") rather than all of WoS
-(the ``global network") would reduce model misspecification by limiting substitutions from references that were ectopic to these networks.
+We hypothesized instead that modifying the normalization to constrain substitution references to be drawn only from the citation network being studied (the ``local network'') rather than all of WoS
+(the ``global network'') would reduce model misspecification by limiting substitutions from references that were ectopic to these networks.
 Consequently, we used keyword searches of the scientific literature to construct exemplar citation networks themed around academic disciplines of interest: \emph{applied physics, immunology, and metabolism}.
@@
 \caption{Citation shuffling using the local network preserves the disciplinary composition of references within networks, but using the global network does not.
-Publications of type Article belonging to the three disciplinary networks (ap=applied physics, imm=immunology, and  metab=metabolism) were subject to a single shuffle of all their cited references using either the local network (i.e., the cited references in these networks, denoted  bg\_local) or the global network (i.e., references from all articles in WoS, denoted bg\_WoS) as the source of allowed substitutions, where ``bg" indicates the disciplinary network.
+Publications of type Article belonging to the three disciplinary networks (ap=applied physics, imm=immunology, and  metab=metabolism) were subject to a single shuffle of all their cited references using either the local network (i.e., the cited references in these networks, denoted  bg\_local) or the global network (i.e., references from all articles in WoS, denoted bg\_WoS) as the source of allowed substitutions, where ``bg'' indicates the disciplinary network.
 Citation shuffling was performed using either our algorithm (\emph{repcs}, top row)
@@
 
-Since the constrained model better fits the observed data, we evaluated the distribution of highly cited articles  (i.e., ``hit articles") in the four categories (HNHC, HNLC, LNHC, LNLC), for different thresholds for hit articles.
+Since the constrained model better fits the observed data, we evaluated the distribution of highly cited articles  (i.e., ``hit articles'') in the four categories (HNHC, HNLC, LNHC, LNLC), for different thresholds for hit articles.
 Figure \ref{fig:Fig2}, Panels (a) and (b), compares hit rates for the four categories among the immunology, metabolism, applied physics, and WoS data sets for 1995, where the hit rate is defined as the number of hit articles in each category divided by the number of articles in the category.
@@
 Instead, we find that conventionality flavored with novelty is {\em not} generally a feature of impactful research.
-Further,  high ``novelty" is not always indicative of impactful research \textcolor{blue}{(as measured by citation counts, which should themselves be interpreted with caution)}, as shown by both Immunology and Metabolism having their highest hit rates for low novelty (Figure \ref{fig:Fig2}).
+Further,  high ``novelty'' is not always indicative of impactful research \textcolor{blue}{(as measured by citation counts, which should themselves be interpreted with caution)}, as shown by both Immunology and Metabolism having their highest hit rates for low novelty (Figure \ref{fig:Fig2}).
 
@@
 \textcolor{blue}{As we note, \emph{vide supra}, under our conditions of analysis, the trends for all three disciplinary networks are different from those for WoS.}
+
+Our work has shown that the use of local networks enables simulations that are more consistent with research citation patterns.
+Further work might explore additional constraints on random assignment of citations to publications to better align benchmarks with citation practice.
+For example, proximity defined by co-author networks~\citep{wallace_lariviere_gingras_2012} might be considered when defining probabilities for citation substitutions.
+Another interesting but challenging direction would be to find ways to distinguish intra-disciplinary from cross-disciplinary novelty.
+\textcolor{blue}{In this respect, the related work of \citep{wang_bias_2017} is insightful with its use of empirical data and observations made on novelty and quality, as well as dispersion and kinetics of accrued citations of articles classified as novel.}
+
+\textcolor{blue}{We note that journals are used as grouping units for articles in the three studies we discuss \citep{wang_bias_2017, uzzi_atypical_2013, boyack_vs_uzzi_2014} as well as this one.
+While we used keyword searches to identify sets of articles, we still relied on journal grouping to generate z-scores.
+Such grouping, while appealing on account of relative simplicity, obscures measurements of novel pairings at the article level.
+Journals are also of limited use in representing individual fields and repeating some of these studies using article clusters may be more informative~\cite{traag_louvain_2019, klavans_which_2017}.
+We also acknowledge the limitations of using citation counts to identify impactful publications.
+Various factors contribute to citations \citep{peters_determinants_1994, vieira_citations_2010} and further study in the context of co-citation may be merited.
+Overall, evaluation in context~\citep{hicks_bibliometrics:_2015} and further consideration of the disciplinary nature of the scientific enterprise is likely to result in improved models that yield further insight.}
 

### 2019-09-15 v2_suppl.tex
added template for supplemental

--- 2019-09-15 Revision2Letter.tex
@@
 
-\title{QSS27: Revision II}
-\author{George Chacko}
+\title{v2 Supplemental}
+\author{To be added later...}
 %\date{}							% Activate to display a given date or no date
@@
 
-Dear Dr. Waltman:
-
-\vspace{5mm}
-\raggedright 
-Thank you for the opportunity to submit a revision.
-Again, we thank the reviewers for their diligence and professional courtesy.
-We have considered the comments from both reviewers carefully and provide a response below.
-The response is also reflected in a revised manuscript with blue text indicating where changes have been made to the first revision.
-We have also responded to your suggestion that we include a discussion of the work of Wang, Veugelers, and Stephan.
-
-\vspace{3mm}
-Sincerely
-\vspace{5mm}
-
-George Chacko
-
-\section{Reviews}
-\subsection{Reviewer 1}
-
-\emph{The revised manuscript is much improved, and the specific comments to both reviews were very helpful.
-Overall, the authors have addressed all of the issues I’ve raised satisfactorily.
-The paper is important as a critique to Uzzi.The paper does not claim to present an alternative (better) way to identify innovative papers.
-But I was hoping that it could- and agree with the editor that the additional requirement (of comparing evaluations from both approaches) is not needed.
-In my second reading, I did realize one additional flaw that I would like the authors to address- upon the editor’s discretion.
-It looks like the study had a low threshold (just two references) for including papers in their studies.
-And we know that citation impact is correlated with the number of references.
-Is it possible that the signals they (or Uzzi) get for ‘innovative’ or ‘conforming’ are dependent on the number of references?
-This can be easily checked (a simple table of \# of references and likelihood of a signal of conformity or innovativeness) should be done.
-I suspect you won’t get any signal for papers with fewer than 5 references (how can one really assess either concept with such a small number?).
-But with 10 or more references- I'm quite comfortable with conclusions about impact being based on conformity and innovativeness.
-They may also find, when applying a reference threshold (such as 10) that they get different results.}
-
-\begin{itemize}
-\item The reference count issue is interesting although it is not quite clear what is meant by signal.
-We chose to set the threshold at 2 references since it is the smallest number that yields a reference pair.
-It is perhaps useful to be reminded that these reference pairs are then mapped to journal pairs whose frequencies are summed across the dataset being studied, then normalized, and finally returned to the parent article as z-scores.
-The reviewer argues that 10 references (45 z-scores) would be a reassuring number.
-This choice appears intuitive rather than reasoned but likely reflects insight.
-However, there is a penalty for arbitrarily excluding low-reference publications.
-For example, restricting the applied physics dataset from 1985 we analyze (ap\_1985) to those with 5 references or less results in a loss of 28\% of the publications and their associated references.
-\\
-
-\vspace{1mm}
-We reviewed the literature in which correlation between reference count and citations is claimed.
-In particular, we studied Peters and van Raan (1994) and Vieira and Gomes (2010) since other articles reporting a correlation between reference count and citations seem to eventually trail back to these two.
-\begin{enumerate}
-\item Peters and van Raan used a set of 226 articles drawn from the bibliographies of 18 internationally recognized chemical engineers for the years 1977-1986.
-They observed a possible bi-phasic distribution when 5-year impact was measured in a histogram with reference count intervals of 5 between groups ($<=9, 10-14, 15-19, 20-24, 35-29, 30-34, >=35$).
-They reported a Pearson's correlation coefficient of 0.52 and inferred a weak but positive correlation (Fig 1d and Table 1 of their paper) consistent with the observations of Moed \emph{et al} 1985.
-This is not very convincing (or easily compared to our larger datasets from later years) but we do respect the finding.
-
-\item More interestingly, Vieira and Gomes examined 226,166 articles from 2004 classified into Biology \& Biochemistry, Chemistry, Mathematics, and Physics per the WOS ESI.
-Biology and Biochemistry consisted of 455 journals, 44248 articles; Chemistry (574j, 97177a); Mathematics (387j, 20127a); and Physics (338j, 64614a).
-Our study differs in that we are looking at different subsets of the data, larger amounts of data, and counting citations for the first 8 years.
-
-As far as we can tell, these authors counted total citations accumulated in around 5 years (the paper was submitted and accepted in 2009).
-Fig 9 of their paper shows a positive relationship between the number of references and the citations that differs in slope and intercept between subjects when a linear fit is applied to the data.
-We evaluated the relationship between references and citation counts on all 9 local networks we analyzed in this paper using the approach of Vieira and Gomes.
-The results are very interesting.
-When plotting reference counts (independent variable on the x axis) against the mean of citation counts we see a linear relationship that gets noisy after about papers with 75 references or more (our Figure 1 below).
-This is consistent with the observations of Vieira and Gomes and not unexpected since the noisy part of the data could be accounted for by review articles.
-However, when plotting citation counts (independent variable on the x axis) against the mean of reference counts the results suggest that publications with a broad range of cited references can accrue similar citations over the first 8 years since publication (our Figures 2 \& 3).
-We conclude that Fig 9 of Vieira and Gomes masks the variance of citation counts when the mean citation count is plotted as a dependent variable.
-Thus, the basis for arguing that reference counts correlate with citation counts is a little shaky although it may be true for a narrow range and subset of articles (Figure 3, column 3 in particular).
-In other words, trying to focus the analysis on just a subset of the data based on number of references is not likely to provide much insight.
-Nor will studying this be simple as not only reference counts but a number of factors would seem to explain the variance (both Peters and van Raan \& Vieira and Gomes).
-
-However, controlling for the number of references (as a proxy for the number of z-scores) in a publication appears reasonable so we provide some data below.
-Perhaps this is what the reviewer had in mind as well?
-\end{enumerate}
-\item INSERT Jim's data
-\end{itemize}
-
-\subsection{Reviewer 2}
-
-\emph{I would like to thank the authors for the revision.
-However, I am afraid the revision has not sufficiently addressed my concerns.
-First, thanks for clarifying the reference shuffling.
-Let’s say Pub A has a reference B, A is in discipline X and B in discipline Y.
-I initially thought the local network approach swaps B with another reference which is also in discipline Y.
-The authors actually did was to swap B with another reference from another paper which is in discipline X.
-Is that correct?
-The authors have clarified it in the paper, but I think it still needs to improved, maybe provide some illustrative examples.
-Although my initial comment was because of misunderstanding the method, the underlying argument still holds.
-It is still unclear whether global or discipline-specific novelty is more appropriate.
-For example, bibliometrics papers cite a lot of mathematics paper, so in the pool of references cited by bibliometrics, combinations between bibliometrics and mathematics are very common.
-However, mathematics do not cite bibliometrics so much, then combinations between bibliometrices and mathematics seems rather unusual when examining the mathematics.
-I can see arguments supporting both the global and local approaches.
-I do not think this paper can get away with it without clarifying the conceptualization.
-Second, the relationship between novelty/conventionality and citation impact itself does not seem to be a ground truth.
-Using statistics about misspecification is based on a huge assumption, which needs to be made explicit and supported by conceptualization and theories.}
-
-\begin{itemize}
-\item An illustration has been generated that will be added to supplementary material that contains material from the first rebuttal.
-\item Yes, the reviewers description of our citation swapping strategy is now correct.
-Further, a difference between bibliometrics and mathematics may be that bibliometrics papers cite mathematics papers more often than the other way around.
-The local model accounts for this but the global one does not.
-We argue consistently that local models reduce mis-specification and provide data to support the argument.
-\item The relationship between novelty, conventionality, and citation counts is not a ground truth, we have never claimed it is.
-This framework was developed by Uzzi et al.
-(2013) and we have used it to enable \emph{ceteris paribus} comparisons.
-We cannot address the question of the `huge assumption', which is not actually stated by the reviewer- we don't think we make such an assumption.
-\end{itemize}
-
-\subsection{Editor}
-\emph{I have one other suggestion.
-In addition to the work on novelty by Brian Uzzi and colleagues, there is also work on novelty by Reinhilde Veugelers and colleagues, who operationalize novelty in a different way.
-For completeness, you may consider providing a brief discussion of the work by Veugelers and colleagues in your manuscript.}
-\begin{itemize}
-\item We thank you for bringing this publication to our attention.
-We really ought to have cited it but we were guilty of, perhaps myopically, focusing on the details of the random graph approach.
-Discussing this paper broadens the context of our manuscript and we've now referenced it in the Discussion.
-As one of our co-authors observes, the definition of novelty is a little restrictive to say the least but the paper is an excellent one and we are happy to reference it.
-\item We have also added a sentence about the limitations of grouping by journals and have suggested that analyzing article level clusters may be more insightful.
-This has come out of our more recent interest in clustering, which informs this new direction.
- \end{itemize}
-
- \newpage
-
-\begin{figure}[tbhp]
-\centering
-\includegraphics[width=0.6\linewidth]{all_ref_cit_year_gp}     
-\caption{Apparent linear relationship between reference count(x-axis) and citation count(y-axis).
-Data from 9 local networks analyzed in our paper are shown.
-These results are approximately consistent with the observations of Vieira and Gomes(2010)}
-\label{fig:refcit}
-\end{figure}
-\newpage
-
-\begin{figure}[tbhp]
-\centering
-\includegraphics[width=0.6\linewidth]{all_cit_ref_year_gp}     
-\caption{Inversion of axes unmasks variance in citation counts.
-In this case, the mean of reference counts is plotted as a dependent variable and citation counts are plotted as an independent variable.
-Data from 9 local networks analyzed in our paper are shown as in previous Figure.
-These results are not consistent with the observations  of Vieira and Gomes(2010)}
-\label{fig:citref}
-\end{figure}
-\newpage
-
-\begin{figure}[tbhp]
-\centering
-\includegraphics[width=0.9\linewidth]{all_cit_ref_year_gp_zoom}     
-\caption{Inversion of axes unmasks variance in citation counts.
-In this case, the mean of reference counts is plotted as a dependent variable and citation counts are plotted as an independent variable [ZOOMED from Figure 2].
-Data from 9 local networks analyzed in our paper are shown.
-To enable better visualization, the citation counts from Fig 2 are restricted at the lower end to the 90th percentile or greater for the ap\_1985 dataset (the smallest of the 9 datasets) and to an upper limit of 2000 citations to exclude a single outlier value,.
-These results are not consistent with the observations  of Vieira and Gomes(2010)}
-\label{fig:refcit}
-\end{figure}
-\newpage
-
 \end{document}

### 2019-09-15 Revision2Letter.tex
tweak

@@
 We have also responded to your suggestion that we include a discussion of the work of Wang, Veugelers, and Stephan.
-Our response is reflected in a revised manuscript with blue text indicating where changes have been made to the first revision or where we have made minor edits to assist clarity.
+Our response is also reflected in a revised manuscript with blue text indicating where changes have been made to the first revision or where we have made minor edits to assist clarity.
 
@@
 Thus, the basis for arguing that reference counts generally correlates with citation counts seems a little shaky although it may be true for a narrow range and subset of articles (Figure 3, column 3 in particular).
-A number of factors help explain variance in citation counts (both Peters and van Raan \& Vieira and Gomes) and focusing on reference count alone is distracting to the purpose of our paper.
+A number of factors help explain variance in citation counts (both Peters and van Raan \& Vieira and Gomes), particularly impact of publishing journal and impact of cited references so focusing on reference count alone seems distracting to the purpose of our paper.
 

### 2019-09-15 cocit_r_v3.tex
tweak

@@
 Such grouping, while appealing on account of its relative simplicity, obscures measurements of novel pairings at the article level.
-Journals are also of limited use in representing individual fields and repeating some of these studies using article clusters may be more informative~\citep{traag_louvain_2019, klavans_which_2017}}.
-Overall, evaluation in context~\citep{hicks_bibliometrics:_2015} and appropriate consideration of the disciplinary nature of the scientific enterprise is likely to result in improved models that yield further insight.
+Journals are also of limited use in representing individual fields and repeating some of these studies using article clusters may be more informative~\citep{traag_louvain_2019, klavans_which_2017}.
+We acknowledge the limitations of using citation counts to measure impact, a number of factors contribute to these counts\citep{peters_determinants_1994,vieira_citations_2010} and studying them further in the context of this study may be of interest, Overall, evaluation in context~\citep{hicks_bibliometrics:_2015} and appropriate consideration of the disciplinary nature of the scientific enterprise is likely to result in improved models that yield further insight.}
 

### 2019-09-15 cocit_r_v3.tex
duplicate paras in Discu

--- 2019-09-15 cocit_r_v3.tex
@@
 We also acknowledge the limitations of using citation counts to identify impactful publications.
-Various factors contribute to citations \citep{peters_determinants_1994, vieira_citations_2010} and further study in the context of co-citation may be merited.
+Various factors contribute to citations \citep{peters_determinants_1994, vieira_citations_2010} and further study of these in the context of co-citation may be merited.
 Overall, evaluation in context~\citep{hicks_bibliometrics:_2015} and further consideration of the disciplinary nature of the scientific enterprise is likely to result in improved models that yield further insight.}
-
-Our work has shown that the use of local networks enables simulations that are more consistent with research citation patterns.
-Further work might explore additional constraints on random assignment of citations to publications to better align benchmarks with citation practice.
-For example, proximity defined by co-author networks~\citep{wallace_lariviere_gingras_2012} might be considered when defining probabilities for citation substitutions.
-Another interesting but challenging direction would be to find ways to distinguish intra-disciplinary from cross-disciplinary novelty.
-\textcolor{blue}{In this respect, the related work of \citep{wang_bias_2017} is insightful with its use of empirical data and the observations made on novelty, quality, as well as dispersion and kinetics of accrued citations of articles.}
-
-\textcolor{blue}{We note that journals are used as grouping units for articles in the three studies we discuss \citep{wang_bias_2017, uzzi_atypical_2013, boyack_vs_uzzi_2014} as well as this one.
-While we used keyword searches to identify sets of articles, we still relied on journal grouping to generate z-scores.
-Such grouping, while appealing on account of its relative simplicity, obscures measurements of novel pairings at the article level.
-Journals are also of limited use in representing individual fields and repeating some of these studies using article clusters may be more informative~\citep{traag_louvain_2019, klavans_which_2017}}.
-Overall, evaluation in context~\citep{hicks_bibliometrics:_2015} and appropriate consideration of the disciplinary nature of the scientific enterprise is likely to result in improved models that yield further insight.
 

### 2019-09-15 cocit_r_v3.tex
duplicate paras in Discu

@@
 Another interesting but challenging direction would be to find ways to distinguish intra-disciplinary from cross-disciplinary novelty.
-\textcolor{blue}{In this respect, the related work of \citep{wang_bias_2017} is insightful with its use of empirical data and observations made on novelty and quality, as well as dispersion and kinetics of accrued citations of articles classified as novel.}
+\textcolor{blue}{In this respect, the related work of \cite{wang_bias_2017} is insightful with its use of empirical data and observations made on novelty and quality, as well as dispersion and kinetics of accrued citations of articles classified as novel.}
 
@@
 While we used keyword searches to identify sets of articles, we still relied on journal grouping to generate z-scores. 
-Such grouping, while appealing on account of relative simplicity, obscures measurements of novel pairings at the article level.
-Journals are also of limited use in representing individual fields and repeating some of these studies using article clusters may be more informative~\cite{traag_louvain_2019, klavans_which_2017}.
+Such a grouping, while appealing on account of relative simplicity, obscures measurements of novel pairings at the article level.
+Journals are also of limited use in representing individual fields, and repeating some of these studies using article clusters may be more informative~\citep{traag_louvain_2019, klavans_which_2017}.
 We also acknowledge the limitations of using citation counts to identify impactful publications.

### 2019-09-15 cocit_r_v3.tex
Bradley's suggestion

@@
 Instead, we find that conventionality flavored with novelty is {\em not} generally a feature of impactful research.
-Further,  high ``novelty'' is not always indicative of impactful research \textcolor{blue}{(as measured by citation counts, which should themselves be interpreted with caution)}, as shown by both Immunology and Metabolism having their highest hit rates for low novelty (Figure \ref{fig:Fig2}).
+Further,  high ``novelty'' is not always indicative of impactful research \textcolor{blue}{, as we measure it in this study using citation counts.}
 
@@
 Journals are also of limited use in representing individual fields, and repeating some of these studies using article clusters may be more informative~\citep{traag_louvain_2019, klavans_which_2017}.
-We also acknowledge the limitations of using citation counts to identify impactful publications.
-Various factors contribute to citations \citep{peters_determinants_1994, vieira_citations_2010} and further study of these in the context of co-citation may be merited.
+We acknowledge the limitations of using citation counts to identify impactful publications.
+Various factors contribute to citation counts \citep{peters_determinants_1994, vieira_citations_2010} and further study of these in the context of co-citation analysis may be of interest.
 Overall, evaluation in context~\citep{hicks_bibliometrics:_2015} and further consideration of the disciplinary nature of the scientific enterprise is likely to result in improved models that yield further insight.}

### 2019-09-15 Revision2Letter.tex
Bradley's suggestion

@@
 
+In fact, what began as a simple experiment turned out to be quite complicated and out of scope for this article. We have modified the Discussion to make this point.
+
 \begin{itemize}
@@
 This choice appears intuitive rather than reasoned.
-We chose to set the threshold at 2 references since it is the smallest number that yields a reference pair.
+In our manuscript, we chose to set the threshold at 2 references since it is the smallest number that yields a reference pair.
 This threshold also supports comparison with Uzzi's data.
@@
 For example, restricting the applied physics dataset from 1985 (ap\_1985) to publications with 5 references or less results in a loss of 28\% of the publications and associated references.
+For the two biology-baed datasets recovery of between 92-95 \% of the publications we analyzed occurs when a cutoff of 10 references is applied.
+For the applied\_physics dataset, which has different citation and reference characteristics, we would recover between 45-69\% for the three years we studied.
+For the complete WoS set, recovery ranges between 63-77\%.
+This is not surprising, we expect disciplinary differences but a cutoff value of 10 references has different effects that need to be carefully studied along with the other variables that contribute to citation counts.
 

### 2019-09-15 Revision2Letter.tex
Bradley's suggestion

@@
 
-In fact, what began as a simple experiment turned out to be quite complicated and out of scope for this article. We have modified the Discussion to make this point.
+In fact, what began as a simple experiment turned out to be quite complicated and, in our assessment, out of scope for this article  We have modified the Discussion to make this point.
+In addition, we emphasize that innovation and conventionality are measured by legacy conventions that assist disciplined thought but should not be considered ground truth.
 
@@
 For example, restricting the applied physics dataset from 1985 (ap\_1985) to publications with 5 references or less results in a loss of 28\% of the publications and associated references.
-For the two biology-baed datasets recovery of between 92-95 \% of the publications we analyzed occurs when a cutoff of 10 references is applied.
+For the two biology-based datasets recovery of between 92-95 \% of the publications we analyzed occurs when a cutoff of 10 references is applied.
 For the applied\_physics dataset, which has different citation and reference characteristics, we would recover between 45-69\% for the three years we studied.
-For the complete WoS set, recovery ranges between 63-77\%.
+For the complete WoS set, recovery ranges between 63-77\% (again consistent with allWos being a mixture of disciplines).
 This is not surprising, we expect disciplinary differences but a cutoff value of 10 references has different effects that need to be carefully studied along with the other variables that contribute to citation counts.
@@
 \item We added a sentence about the limitations of grouping by journals and have suggested that analyzing article level clusters may be more insightful.
-We have also sounded a cautionary note (that ought to be superfluous) about the limitations of using citation counts as a readout for impact.
+We have also sounded a cautionary note (that is probably superfluous) about the limitations of using citation counts as a readout for impact.
 \end{itemize}

### 2019-09-16 Revision2Letter.tex
added Jim's text and tables

@@
 In fact, what began as a simple experiment turned out to be quite complicated and, in our assessment, out of scope for this article  We have modified the Discussion to make this point.
-In addition, we emphasize that innovation and conventionality are measured by legacy conventions that assist disciplined thought but should not be considered ground truth.
+In addition, we emphasize that innovation and conventionality are measured by legacy conventions (Uzzi) that assist disciplined thought but should not be considered ground truth.
+This point is also made in the manuscript.
 
@@
 This threshold also supports comparison with Uzzi's data.
-It is perhaps useful to be reminded that these reference pairs are then mapped to journal pairs whose frequencies are summed across the dataset being studied, then normalized, and finally returned to the parent article as z-scores.
+It is useful to be reminded that these reference pairs are then mapped to journal pairs whose frequencies are summed across the dataset being studied, then normalized, and finally returned to the parent article as z-scores.
 Lastly, there is a penalty for arbitrarily excluding low-reference publications.
@@
 
-\vspace{3mm} Even so, \emph{we INSERT Jim's new data here... }
-
-\begin{table}[ht]
-\begin{centering}
-\caption{Hit Rates By Category: Effect of Omitting Articles with 10 and Fewer References}
-\vspace{3mm}
-\begin{tabular}{|c crr rrr r|}
- \hline
- Dataset & Year & Hit Rate & Omitted  & LNLC & LNHC & HNLC & HNHC \\ 
-  \hline
-Metabolism & 2005&1\%&& 0.6& \bf{1.3}& 0.7& \bf{1.3} \\ 
-Metabolism & 2005&1\%& \checkmark & 0.7& \bf{1.4}& 0.7& \bf{1.2} \\ 
-\hline
-Metabolism & 2005&2\%&& 1.0& \bf{2.5}& 1.5& \bf{2.6} \\ 
-Metabolism & 2005&2\%& \checkmark & 1.2& \bf{2.7}& 1.5& \bf{2.5} \\ 
-\hline
-Metabolism & 2005&5\%&& 2.3& 6.0& 3.9& \bf{6.6} \\ 
-Metabolism & 2005&5\%& \checkmark & 2.7& \bf{6.3} & 3.8& \bf{6.4} \\ 
-\hline
-Metabolism & 2005&10\%&& 4.1& 11.4& 8.1& \bf{12.6} \\ 
-Metabolism & 2005&10\%& \checkmark & 5.3& \bf{12.0} & 8.1& \bf{12.5} \\ 
-\hline
-\end{tabular} \\
-\end{centering}
-\end{table} 
-\end{enumerate}
-\end{itemize}
+\vspace{3mm} Even so, we have followed up on the question.The hit rates for (i) our original data sets and (ii) the hit rates for those same data sets omitting articles having 10 or fewer references are shown in Tables 1 and 2, respectively.
+While omission of these articles poses difficulties with maintaining the feasibility of chi square hypothesis tests, these tables indicate that the hit rates do not change appreciably with the omission of these articles and, more importantly, the adjusted hit rates revisions still support the conclusions reached in the original version of our article.
+The dominant hit rates have been highlighted in boldface for easy comparison of the two tables."}
 
@@
 \item An illustration has been generated that will be added to supplementary material that contains figures from the first rebuttal.
-\item Yes, the reviewer's description of our citation swapping strategy is now correct.
+\item Yes, the reviewer's description of our citation swapping strategy is now approximately correct.
 Further, a difference between bibliometrics and mathematics may be that bibliometrics papers cite mathematics papers more often than the other way around.
@@
 
+\begin{table}
+\begin{centering}
+\caption{Hit Rates By Category: All Data}
+\vspace{3 mm}
+\scalebox{0.8}{
+\begin{tabular}{|c crrrr r|}
+ \hline
+Dataset & Year & Highly Cited  & LNLC & LNHC & HNLC & HNHC \\ 
+ \hline
+Applied Physics & 1985&1\%& 0.0& 0.5& \bf{1.2}& \bf{1.2} \\ 
+Applied Physics & 1985&2\%& 0.9& 0.9& \bf{2.5}& \bf{2.4} \\ 
+Applied Physics & 1985&5\%& 2.8& 3.0& 5.5& \bf{6.5} \\ 
+Applied Physics & 1985&10\%& 5.2& 6.7& 10.6& \bf{13.2} \\ 
+Applied Physics & 1995&1\%& 0.2& 0.7& \bf{1.2}& \bf{1.0} \\ 
+Applied Physics & 1995&2\%& 0.2& 1.3& \bf{2.5}& 2.1 \\ 
+Applied Physics & 1995&5\%& 0.9& 3.4& \bf{6.0}& 5.2 \\ 
+Applied Physics & 1995&10\%& 4.7& 7.9& \bf{12.3}& 10.9 \\ 
+Applied Physics & 2005&1\%& 0.8& 0.6& \bf{1.1}& \bf{1.3} \\ 
+Applied Physics & 2005&2\%& 1.1& 1.3& \bf{2.1}& \bf{2.3}\\ 
+Applied Physics & 2005&5\%& 1.6& 3.3& 5.4& \bf{5.9} \\ 
+Applied Physics & 2005&10\%& 3.9& 7.5& 10.7& \bf{11.4} \\
+\hline 
+Immunology & 1985&1\%& 0.0& \bf{1.5}& 0.6& \bf{1.4} \\ 
+Immunology & 1985&2\%& 0.0& \bf{3.0}& 1.2& \bf{2.8} \\ 
+Immunology & 1985&5\%& 1.5& 6.5& 3.2& \bf{7.1} \\ 
+Immunology & 1985&10\%& 3.0& 12.0& 7.1& \bf{14.0} \\ 
+Immunology & 1995&1\%& 0.0& \bf{1.9}& 0.5& 1.4 \\ 
+Immunology & 1995&2\%& 0.0& \bf{3.4}& 1.1& 2.8 \\ 
+Immunology & 1995&5\%& 0.6& \bf{7.2}& 3.2& 6.8 \\ 
+Immunology & 1995&10\%& 1.7& \bf{12.8}& 7.6& \bf{12.9} \\ 
+Immunology & 2005&1\%& 0.0& \bf{1.5}& 0.6& \bf{1.3} \\ 
+Immunology & 2005&2\%& 0.0& \bf{2.7}& 1.3& \bf{2.7} \\ 
+Immunology & 2005&5\%& 0.0& 6.0& 3.6& \bf{6.7} \\ 
+Immunology & 2005&10\%& 2.0& 10.8& 8.1& \bf{12.9} \\ 
+\hline
+Metabolism & 1985&1\%& 0.1& \bf{1.5}& 0.5& \bf{1.5} \\ 
+Metabolism & 1985&2\%& 0.3& \bf{2.7}& 1.3& \bf{2.9} \\ 
+Metabolism & 1985&5\%& 0.7& 6.6& 3.4& \bf{7.0} \\ 
+Metabolism & 1985&10\%& 2.3& 12.3& 7.2& \bf{13.8} \\ 
+Metabolism & 1995&1\%& 0.1& \bf{1.7}& 0.6& \bf{1.4} \\ 
+Metabolism & 1995&2\%& 0.3& \bf{3.1}& 1.2& \bf{2.8} \\ 
+Metabolism & 1995&5\%& 0.7& \bf{7.}0& 3.4& \bf{6.7} \\ 
+Metabolism & 1995&10\%& 1.9& \bf{13.0}& 7.4& \bf{13.3} \\ 
+Metabolism & 2005&1\%& 0.6& \bf{1.3}& 0.7& \bf{1.3} \\ 
+Metabolism & 2005&2\%& 1.0& \bf{2.5}& 1.5& \bf{2.6} \\ 
+Metabolism & 2005&5\%& 2.3& 6.0& 3.9& \bf{6.6} \\ 
+Metabolism & 2005&10\%& 4.1& 11.4& 8.1& \bf{12.6} \\ 
+\hline
+Web of Science & 1985&1\%& 0.4& 1.2& 1.0& \bf{1.6} \\ 
+Web of Science & 1985&2\%& 0.9& 2.4& 2.0& \bf{3.3} \\ 
+Web of Science & 1985&5\%& 2.6& 5.9& 5.1& \bf{8.4} \\ 
+Web of Science & 1985&10\%& 5.8& 11.4& 10.4& \bf{15.8} \\ 
+Web of Science & 1995&1\%& 0.4& 1.3& 0.9& \bf{1.7} \\ 
+Web of Science & 1995&2\%& 0.9& 2.4& 1.9& \bf{3.3} \\ 
+Web of Science & 1995&5\%& 2.5& 6.0& 5.0& \bf{8.0} \\ 
+Web of Science & 1995&10\%& 5.6& 11.5& 10.4& \bf{15.6} \\ 
+Web of Science & 2005&1\%& 0.4& 1.2& 1.0& \bf{1.7} \\ 
+Web of Science & 2005&2\%& 0.9& 2.3& 2.0& \bf{3.4} \\ 
+Web of Science & 2005&5\%& 2.5& 5.7& 5.3& \bf{8.1} \\ 
+Web of Science & 2005&10\%& 5.6& 11.2& 10.8& \bf{15.0} \\
+\hline
+%\multicolumn{7}{l}{\multirow{5}{*}{\parbox{12cm}{The hit rate is the percentage of publications in the referenced category that are in the top $1\%$, $2\%$, $5\%$, or $10\%$ of papers according to citation count  (see column 3) for novel articles defined as those with the 10th percentile z-score being negative.
+The z-scores are computed using the local network.
+The category with the highest percentile is boldfaced (the second highest is also boldfaced if within 0.3\% and greater than the overall percentage of articles considered to be hits).
+We also evaluated novelty defined as the 1st percentile of z-scores being negative.
+We report here on novelty defined at the most stringent parameter setting, while the remaining results are reported at \textcolor{blue}{https://bit.ly/2CFMOuf}.}}}
+\end{tabular}} \\
+\end{centering}
+%\addtabletext{}
+\end{table}
+​
+
+\begin{table}
+\begin{centering}
+\caption{Hit Rates By Category: Data Omits Articles with 10 or Fewer References}
+\vspace{3mm}
+\scalebox{0.8}{
+\begin{tabular}{|c crrrr r|}
+ \hline
+ Dataset  & Year& Highly Cited & LNLC & LNHC & HNLC & HNHC \\ 
+  \hline
+Applied Physics & 1985&1\%& 0.0& 0.3& \bf{1.3}& \bf{1.0} \\ 
+Applied Physics & 1985&2\%& 0.0& 1.2& \bf{2.8}& 1.6 \\ 
+Applied Physics & 1985&5\%& 0.0& 2.9& \bf{6.4}& 4.6 \\ 
+Applied Physics & 1985&10\%& 8.3& 5.6& \bf{11.7}& 10.2 \\ 
+Applied Physics & 1995&1\%& 0.0& 0.8& \bf{1.2}& 0.8 \\ 
+Applied Physics & 1995&2\%& 0.0& 1.8& \bf{2.4}& 1.7 \\ 
+Applied Physics & 1995&5\%& 0.0& 4.2& \bf{5.8}& 4.2 \\ 
+Applied Physics & 1995&10\%& 3.0& 8.3& \bf{12.}2& 9.4 \\ 
+Applied Physics & 2005&1\%& \bf{1.2}& 0.8& \bf{1.0}& \bf{1.1} \\ 
+Applied Physics & 2005&2\%& 1.2& 1.7& \bf{1.9}&\bf{ 2.2} \\ 
+Applied Physics & 2005&5\%& 3.6& 4.5& 4.7& \bf{5.7} \\ 
+Applied Physics & 2005&10\%& 6.0& 9.6& 9.8& \bf{11.1} \\ 
+\hline
+Immunology & 1985&1\%& 0.0& \bf{1.6}& 0.6& \bf{1.4} \\ 
+Immunology & 1985&2\%& 0.0& \bf{2.7}& 1.1& 3.1 \\ 
+Immunology & 1985&5\%& 9.1& 5.6& 3.3& \bf{7.2} \\ 
+Immunology & 1985&10\%& 9.1& 11.4& 7.5& \bf{13.1} \\ 
+Immunology & 1995&1\%& 0.0& \bf{2.1}& 0.5& 1.4 \\ 
+Immunology & 1995&2\%& 0.0& \bf{3.6}& 1.1& 2.7 \\ 
+Immunology & 1995&5\%& 1.6& \bf{7.8}& 3.1& 6.7 \\ 
+Immunology & 1995&10\%& 4.7& \bf{14.2}& 7.5& 12.2 \\ 
+Immunology & 2005&1\%& 0.0& \bf{1.6}& 0.6& \bf{1.3} \\ 
+Immunology & 2005&2\%& 0.0& \bf{3.1}& 1.3& 2.7 \\ 
+Immunology & 2005&5\%& 0.0& \bf{6.8}& 3.5& \bf{6.5} \\ 
+Immunology & 2005&10\%& 4.0& 12.1& 7.8& \bf{12.5} \\ 
+\hline
+Metabolism & 1985&1\%& 0.1& \bf{1.6}& 0.5& \bf{1.4} \\ 
+Metabolism & 1985&2\%& 0.4& \bf{3.0}& 1.2& \bf{2.7} \\ 
+Metabolism & 1985&5\%& 1.4& \bf{7.0} & 3.4& 6.6 \\ 
+Metabolism & 1985&10\%& 3.3& \bf{13.4} & 7.4& \bf{13.2} \\ 
+Metabolism & 1995&1\%& 0.1& \bf{1.7} & 0.5& 1.3 \\ 
+Metabolism & 1995&2\%& 0.3& \bf{3.3}& 1.1& 2.7 \\ 
+Metabolism & 1995&5\%& 0.9& \bf{7.4} & 3.3& 6.5 \\ 
+Metabolism & 1995&10\%& 2.8& \bf{13.9}& 7.3& 12.8 \\ 
+Metabolism & 2005&1\%& 0.7& \bf{1.4}& 0.7& \bf{1.2} \\ 
+Metabolism & 2005&2\%& 1.2& \bf{2.7}& 1.5& \bf{2.5} \\ 
+Metabolism & 2005&5\%& 2.7& \bf{6.3} & 3.8& \bf{6.4} \\ 
+Metabolism & 2005&10\%& 5.3& 12.0& 8.1& \bf{12.5} \\ 
+\hline
+Web of Science & 1985&1\%& 0.5& \bf{1.3}& 0.8& \bf{1.3} \\ 
+Web of Science & 1985&2\%& 1.2& \bf{2.5}& 1.7& \bf{2.6} \\ 
+Web of Science & 1985&5\%& 3.0& 6.0& 4.4& \bf{6.4} \\ 
+Web of Science & 1985&10\%& 7.0& 12.0& 9.2& \bf{12.7} \\ 
+Web of Science & 1995&1\%& 0.4& \bf{1.3}& 0.8& \bf{1.4} \\ 
+Web of Science & 1995&2\%& 1.0& \bf{2.5}& 1.7& \bf{2.8} \\ 
+Web of Science & 1995&5\%& 2.9& 6.0& 4.5& \bf{6.6} \\ 
+Web of Science & 1995&10\%& 6.4& 11.6& 9.3& \bf{12.9} \\ 
+Web of Science & 2005&1\%& 0.5& 1.1& 1.0& \bf{1.5} \\ 
+Web of Science & 2005&2\%& 1.2& 2.3& 1.9& \bf{2.9} \\ 
+Web of Science & 2005&5\%& 3.2& 5.6& 5.1& \bf{6.9} \\ 
+Web of Science & 2005&10\%& 6.9& 10.9& 10.1& \bf{12.9} \\ 
+\hline
+%\multicolumn{7}{l}{The hit rate is the percentage of publications in the referenced category that are in the top $1\%$, $2\%$, $5\%$, or $10\%$ of papers according to citation count  (see column 3) for novel articles defined as those with the 10th percentile z-score being negative.
+The z-scores are computed using the local network.
+The category with the highest percentile is boldfaced (the second highest is also boldfaced if within 0.3\% and greater than the overall percentage of articles considered to be hits).
+We also evaluated novelty defined as the 1st percentile of z-scores being negative.
+We report here on novelty defined at the most stringent parameter setting, while the remaining results are reported at \textcolor{blue}{https://bit.ly/2CFMOuf}.}
+\end{tabular}} \\
+\end{centering}
+%\addtabletext{}
+\end{table}
+
 \end{document}

### 2019-09-16 cocit_r_v3.tex
Update cocit_r_v3.tex
Changed description of switching algorithm.

@@
 
-For citation shuffling, we developed a performant citation switching algorithm, \emph{runtime enhanced permuting citation switcher (repcs)}~\citep{GithubERNIE2019}, that randomly permuted citations grouped by year of publication to switch citations while preserving the year of publication for both articles and references, the number of publications and the number of references in each data set, and the disciplinary composition of the references in each data set.
+For citation shuffling, we developed a performant citation switching algorithm, \emph{runtime enhanced permuting citation switcher (repcs)}~\citep{GithubERNIE2019}, that randomly permuted citations \textcolor{blue}{within each disciplinary data set and within each }
+%grouped by
+year of publication: \textcolor{blue}{each citation within each article was switched within its permutation group in order to preserve the number of references from each publication year within each article}.
+%to switch citations while preserving the year of publication for both articles and references, 
+In do doing, the number of publications, the number of references in each data set, and the disciplinary composition of the references in each data set were preserved.
 \textcolor{blue}{Our approach is different from previous studies in these ways: (i) we sampled citations in proportion to their citation frequency (equivalently from a multiset rather than a set) in order to better reflect citation practice,

### 2019-09-16 Revision2Letter.tex
final tweaks

@@
 We have also responded to your suggestion that we include a discussion of the work of Wang, Veugelers, and Stephan.
-Our response is also reflected in a revised manuscript with blue text indicating where changes have been made to the first revision or where we have made minor edits to assist clarity.
+Our response is also reflected in a revised manuscript with blue text indicating where changes have been made to the first revision or where we have made edits to assist clarity.
+We have not highlighted minor edits amounting to punctuation or correction of typographic errors.
 
@@
 A number of factors help explain variance in citation counts (both Peters and van Raan \& Vieira and Gomes), particularly impact of publishing journal and impact of cited references so focusing on reference count alone seems distracting to the purpose of our paper.
-
+\end{enumerate}
 \item Nevertheless, the reference count issue raised is interesting in itself (although it is not quite clear what is meant by signal) so we have added a sentence to the Discussion addressing it.
@@
 \vspace{3mm} Even so, we have followed up on the question.The hit rates for (i) our original data sets and (ii) the hit rates for those same data sets omitting articles having 10 or fewer references are shown in Tables 1 and 2, respectively.
-While omission of these articles poses difficulties with maintaining the feasibility of chi square hypothesis tests, these tables indicate that the hit rates do not change appreciably with the omission of these articles and, more importantly, the adjusted hit rates revisions still support the conclusions reached in the original version of our article.
-The dominant hit rates have been highlighted in boldface for easy comparison of the two tables."}
-
+While omission of these articles poses difficulties with maintaining the feasibility of chi square hypothesis tests, these tables indica
+te that the hit rates do not change appreciably with the omission of these articles and, more importantly, the adjusted hit rates revisions still support the conclusions reached in the original version of our article.
+The dominant hit rates have been highlighted in boldface for easy comparison of the two tables."
+\end{itemize}
 \subsection{Reviewer 2}
@@
 \item Yes, the reviewer's description of our citation swapping strategy is now approximately correct.
+We have modified our description of the swapping algorithm in an attempt to make it more clear.
 Further, a difference between bibliometrics and mathematics may be that bibliometrics papers cite mathematics papers more often than the other way around.
@@
 In this case, the mean of reference counts is plotted as a dependent variable and citation counts are plotted as an independent variable.
-Data from 9 local networks analyzed in our paper are shown as in previous Figure.
+Data from 9 local networks analyzed in our paper are shown as in Figure 1(previous figure in this document).
 These results are not consistent with the observations  of Vieira and Gomes(2010)}
@@
 These results are not consistent with the observations  of Vieira and Gomes(2010)}
-\label{fig:refcit}
+\label{fig:citref2}
 \end{figure}
@@
 \hline
-%\multicolumn{7}{l}{\multirow{5}{*}{\parbox{12cm}{The hit rate is the percentage of publications in the referenced category that are in the top $1\%$, $2\%$, $5\%$, or $10\%$ of papers according to citation count  (see column 3) for novel articles defined as those with the 10th percentile z-score being negative.
-The z-scores are computed using the local network.
-The category with the highest percentile is boldfaced (the second highest is also boldfaced if within 0.3\% and greater than the overall percentage of articles considered to be hits).
-We also evaluated novelty defined as the 1st percentile of z-scores being negative.
-We report here on novelty defined at the most stringent parameter setting, while the remaining results are reported at \textcolor{blue}{https://bit.ly/2CFMOuf}.}}}
-\end{tabular}} \\
+\end{tabular}} 
 \end{centering}
-%\addtabletext{}
 \end{table}

### 2019-09-16 cocit_r_v3.tex
final tweaks

--- 2019-09-15 cocit_r_v3.tex
@@
 Our study examines this question using  semantically-themed citation networks.
-We observe that trends reported to be true across the scientific literature do not hold for focused citation networks, and we conclude that inferring novelty through co-citation analysis requires disciplinary context.
+\textcolor{blue}{We observe that trends reported to be true across the scientific literature do not hold for focused citation networks, and we conclude that inferring novelty using co-citation analysis and random graph models benefits from disciplinary context.}
 \end{abstract}
@@
 Consequently, every article was associated with multiple z-scores corresponding to co-cited journal pairs in its references.
-For each article, positional statistics of z-scores were calculated and evaluated to set thresholds for a binary classification of conventionality using the median z-score of an article and novelty using the tenth percentile of z-scores within an article.
+For each article, positional statistics of z-scores were calculated and evaluated to set thresholds for a binary classification of conventionality using the median z-score of an article, and novelty using the tenth percentile of z-scores within an article.
 
@@
 For the applied physics data set, we directly searched traditional subject labels in WoS for `Physics, Applied'.
-While applied physics and immunology represent somewhat small networks (roughly 2-6\% of WoS), metabolism represents approximately 22\% of WoS, making them interesting and meaningful test cases.
+While applied physics and immunology represent somewhat small networks (roughly 3-6\% of analytical WoS dataset), metabolism represents approximately 20-23\%, making them interesting and meaningful test cases.
 We also examined publications in the five major research areas in WoS: life sciences \& biomedicine, physical sciences, technology, social sciences, and arts \& humanities,  using the extended WoS subcategory classification of 153 sub-groups to categorize disciplinary composition of cited references in the data sets we studied.
@@
 PubMed and WoS were searched for articles using search terms, `immunology', `metabolism', and `applied physics.' Counts of publications are shown for each of the three years analyzed and expressed in parentheses as a percentage of the total number of publications in our analytical WoS data set (Table \ref{tab:summary_data}) for that year.
-Note that Applied Physics and Immunology each represent about 4\% of the publications in WoS, but Metabolism occupies nearly one-fourth of WoS.}
+Note that Applied Physics and Immunology represent about 3-6\% of the publications in our analytical WoS datasets, but Metabolism occupies nearly a fourth.}
 \label{tab:disc-data sets}
@@
 
-For citation shuffling, we developed a performant citation switching algorithm, \emph{runtime enhanced permuting citation switcher (repcs)}~\citep{GithubERNIE2019}, that randomly permuted citations grouped by year of publication to switch citations while preserving the year of publication for both articles and references, the number of publications and the number of references in each data set, and the disciplinary composition of the references in each data set.
-\textcolor{blue}{Our approach is different from previous studies in these ways: (i) we sampled citations in proportion to their citation frequency (equivalently from a multiset rather than a set) in order to better reflect citation practice,
-(ii) we permitted a substitution to match the original reference in a publication when the random selection process dictated it rather than attempting to enforce that a different reference be substituted, and (iii) we introduced an error correction step to delete any publications that accumulated duplicate references during the substitution process.}  As a benchmark, we used the citation switching algorithm of ~\citep{uzzi_atypical_2013}, henceforth referred to  as \emph{umsj} (as also done in~\citep{boyack_vs_uzzi_2014}), using code kindly provided by the authors.
+For citation shuffling, we developed a performant citation switching algorithm, \emph{runtime enhanced permuting citation switcher (repcs)}~\citep{GithubERNIE2019}, that randomly permuted citations within each disciplinary data set and within each year of publication: \textcolor{blue}{each citation within each article was switched within its permutation group in order to preserve the number of references from each publication year within each article.
+In do doing, the number of publications, the number of references in each data set, and the disciplinary composition of the references in each data set were preserved}.
+\textcolor{blue}{Our approach is different from previous studies in these ways: (i) we sampled citations in proportion to their citation frequency (equivalently from a multiset rather than a set) in order to better reflect citation practice, (ii) we permitted a substitution to match the original reference in a publication when the random selection process dictated it rather than attempting to enforce that a different reference be substituted, and (iii) we introduced an error correction step to delete any publications that accumulated duplicate references during the substitution process.}  As a benchmark, we used the citation switching algorithm of ~\citep{uzzi_atypical_2013}, henceforth referred to  as \emph{umsj} (as also done in~\citep{boyack_vs_uzzi_2014}), using code kindly provided by the authors.
 A single comparative analysis showed that while 10 simulations of the WoS 1985 data set (391,860 selected articles) completed in 2,186 hours using the \emph{umsj} algorithm, it completed in less than one hour using our implementation of the \emph{repcs}   algorithm on a Spark  cluster.
@@
 
-Averaging the result of 1,000 simulations for each data set studied, z-scores were then calculated for each journal-pair using the formula $(F_{obs} - F_{exp})/\sigma$ where $F_{obs}$ is the observed frequency, $F_{exp}$ is the averaged simulated frequency, and $\sigma$ is the standard deviation of the simulated frequencies for a journal pair.
+Averaging the result of 1,000 simulations for each data set studied, z-scores were then calculated for each journal-pair using the formula $(F_{obs} - F_{exp})/\sigma$ where $F_{obs}$ is the observed frequency, $F_{exp}$ is the averaged simulated frequency, and $\sigma$ is the standard deviation of the simulated frequencies for a journal pair\citep{uzzi_atypical_2013}.
 As a result of these calculations, each publication becomes associated with a set of z-scores corresponding to the journal pairs derived from pairwise combinations of its cited references.
@@
 Null values were set to $1$.
-Note y-axis: $log_2$ scale.}
+Note y-axis values: $log_2$}
 \label{fig:be}
@@
 Instead, we find that conventionality flavored with novelty is {\em not} generally a feature of impactful research.
-Further,  high ``novelty'' is not always indicative of impactful research \textcolor{blue}{, as we measure it in this study using citation counts.}
+Further,  high ``novelty'' is not always indicative of impactful research.
 
@@
 Journals are also of limited use in representing individual fields, and repeating some of these studies using article clusters may be more informative~\citep{traag_louvain_2019, klavans_which_2017}.
-We acknowledge the limitations of using citation counts to identify impactful publications.
 Various factors contribute to citation counts \citep{peters_determinants_1994, vieira_citations_2010} and further study of these in the context of co-citation analysis may be of interest.
+We also acknowledge the limitations of using citation counts to identify impactful publications.
 Overall, evaluation in context~\citep{hicks_bibliometrics:_2015} and further consideration of the disciplinary nature of the scientific enterprise is likely to result in improved models that yield further insight.}

### 2019-09-16 cocit_r_v3.tex
Bradley's suggestion

@@
 TW receives funding from the Grainger Foundation.
-Code generated for this this study is freely available from a Github site~\citep{GithubERNIE2019}.
+Code generated for this study is freely available from our Github site~\citep{GithubERNIE2019}.
+Avon Davey's present affiliation is GlaxoSmithKline, Research Triangle Park, NC, USA.
+His contributions to this manuscript were made when he was a full time employee of NET ESolutions Corporation.
  Access to the bibliographic data analyzed in this study requires a license from Clarivate Analytics, which had no role in funding, experimental design, review of results, and conclusions presented. 
-
 \authorcontributions 

### 2019-09-16 Revision2Letter.tex
superminor tweaks

@@
 Thank you for the opportunity to submit a revision.
-Again, we thank the reviewers for their diligence and professional courtesy.
-We have considered their comments and provide a response below.
+Again, we thank the reviewers for their diligence and professional courtesy in evaluating our manuscript.
+We have considered their comments carefully and provide a response below.
 We have also responded to your suggestion that we include a discussion of the work of Wang, Veugelers, and Stephan.
@@
 But with 10 or more references- I'm quite comfortable with conclusions about impact being based on conformity and innovativeness.
-They may also find, when applying a reference threshold (such as 10) that they get different results.}
-
-In fact, what began as a simple experiment turned out to be quite complicated and, in our assessment, out of scope for this article  We have modified the Discussion to make this point.
+They may also find, when applying a reference threshold (such as 10) that they get different results.}\\
+\vspace{3mm}
+In fact, what began as a simple experiment turned out to be quite complicated and, in our assessment, out of scope for this article  We have modified the Discussion to address this point though.
 In addition, we emphasize that innovation and conventionality are measured by legacy conventions (Uzzi) that assist disciplined thought but should not be considered ground truth.
@@
 Lastly, there is a penalty for arbitrarily excluding low-reference publications.
-For example, restricting the applied physics dataset from 1985 (ap\_1985) to publications with 5 references or less results in a loss of 28\% of the publications and associated references.
-For the two biology-based datasets recovery of between 92-95 \% of the publications we analyzed occurs when a cutoff of 10 references is applied.
+For the two biology-based datasets recovery of between 92-95\% of the publications we analyzed occurs when a cutoff of 10 references is applied.
 For the applied\_physics dataset, which has different citation and reference characteristics, we would recover between 45-69\% for the three years we studied.
 For the complete WoS set, recovery ranges between 63-77\% (again consistent with allWos being a mixture of disciplines).
-This is not surprising, we expect disciplinary differences but a cutoff value of 10 references has different effects that need to be carefully studied along with the other variables that contribute to citation counts.
+This is not surprising, we expect disciplinary differences but we are alerted that a cutoff value of 10 references has varying effects that need to be carefully studied along with the other variables that contribute to citation counts.
 
 \vspace{3mm} Even so, we have followed up on the question.The hit rates for (i) our original data sets and (ii) the hit rates for those same data sets omitting articles having 10 or fewer references are shown in Tables 1 and 2, respectively.
-While omission of these articles poses difficulties with maintaining the feasibility of chi square hypothesis tests, these tables indica
-te that the hit rates do not change appreciably with the omission of these articles and, more importantly, the adjusted hit rates revisions still support the conclusions reached in the original version of our article.
-The dominant hit rates have been highlighted in boldface for easy comparison of the two tables."
+While omission of these articles poses difficulties with maintaining the feasibility of chi square hypothesis tests, these tables indicate that the hit rates do not change appreciably with the omission of these articles and, more importantly, the adjusted hit rates still support the conclusions reached in the original version of our article.
+The dominant hit rates have been highlighted in boldface for easy comparison of the two tables.
 \end{itemize}
@@
 \begin{itemize}
-\item An illustration has been generated that will be added to supplementary material that contains figures from the first rebuttal.
+
 \item Yes, the reviewer's description of our citation swapping strategy is now approximately correct.
@@
 We really ought to have mentioned it but we were focused on the details of the random graph approach in local and global contexts.
+The definition of novelty is a little restrictive in this paper but it makes a number of excellent points.
 Discussing this paper broadens the context of our manuscript and we've now referenced it in both the Introduction and Discussion.
-The definition of novelty is a little restrictive in this paper but it makes a number of excellent points.
-\item We added a sentence about the limitations of grouping by journals and have suggested that analyzing article level clusters may be more insightful.
-We have also sounded a cautionary note (that is probably superfluous) about the limitations of using citation counts as a readout for impact.
+\item We also added a sentence about the limitations of grouping by journals and have suggested that analyzing article level clusters may be more insightful.
+We have sounded a cautionary note (that is probably superfluous) about the limitations of using citation counts as a readout for impact.
 \end{itemize}

### 2019-09-17 cocit_r_final.tex
proof copy

--- 2019-09-16 cocit_r_v3.tex
@@
 
-In a novel approach, \citep{uzzi_atypical_2013} used co-citation analysis to characterize a subset of highly cited articles with respect to both novel and conventional combinations of prior research.
+In a novel approach, \cite{uzzi_atypical_2013} used co-citation analysis to characterize a subset of highly cited articles with respect to both novel and conventional combinations of prior research.
 The frequency with which references were co-cited  in 17.9 million articles and their cited references from the Web of Science (WoS) was calculated and expressed as journal pair frequencies (observed co-citation frequencies).
@@
 
-A follow-up study by \citep{boyack_vs_uzzi_2014} explored the impact of discipline and journal effects on these definitions of conventionality and novelty.
+A follow-up study by \cite{boyack_vs_uzzi_2014} explored the impact of discipline and journal effects on these definitions of conventionality and novelty.
 While their study had some methodological differences in the use of Scopus data rather than WoS data, a smaller data set, and a $\chi^2$ calculation rather than Monte Carlo simulations to generate expected values of journal pairs, Boyack and Klavans noted strong effects from disciplines and journals.
@@
 In do doing, the number of publications, the number of references in each data set, and the disciplinary composition of the references in each data set were preserved}.
-\textcolor{blue}{Our approach is different from previous studies in these ways: (i) we sampled citations in proportion to their citation frequency (equivalently from a multiset rather than a set) in order to better reflect citation practice, (ii) we permitted a substitution to match the original reference in a publication when the random selection process dictated it rather than attempting to enforce that a different reference be substituted, and (iii) we introduced an error correction step to delete any publications that accumulated duplicate references during the substitution process.}  As a benchmark, we used the citation switching algorithm of ~\citep{uzzi_atypical_2013}, henceforth referred to  as \emph{umsj} (as also done in~\citep{boyack_vs_uzzi_2014}), using code kindly provided by the authors.
+\textcolor{blue}{Our approach is different from previous studies in these ways: (i) we sampled citations in proportion to their citation frequency (equivalently from a multiset rather than a set) in order to better reflect citation practice, (ii) we permitted a substitution to match the original reference in a publication when the random selection process dictated it rather than attempting to enforce that a different reference be substituted, and (iii) we introduced an error correction step to delete any publications that accumulated duplicate references during the substitution process.}  As a benchmark, we used the citation switching algorithm of ~\citep{uzzi_atypical_2013}, henceforth referred to  as \emph{umsj} as also done in~\cite{boyack_vs_uzzi_2014}, using code kindly provided by the authors.
 A single comparative analysis showed that while 10 simulations of the WoS 1985 data set (391,860 selected articles) completed in 2,186 hours using the \emph{umsj} algorithm, it completed in less than one hour using our implementation of the \emph{repcs}   algorithm on a Spark  cluster.

### 2019-09-17 cocit_r_final.tex
proof copy

@@
 \documentclass[NETN]{stjour}
-
-%% or
-
-%% Manuscript, for double spaced, larger fonts
-%\documentclass[manuscript]{stjour}
-%% Only needed if you use `manuscript' option
-% \journalname{Network Neuroscience}
-
-%%%%%%%%%%% Article Set-Up %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Article Type:
-%% Default is Research.
-
-%% Or, choose one of these options:
-%% Research, Methods, Data, Review, and Perspective
-
 \articletype{Research Article}
@@
 
-\supportinginfo{dx.doi.org/10.7910/DVN/PQ6ILM}
-
-%% if no conflicts, this command doesn't need to be used
-%% \conflictsofinterest{}
+\supportinginfo{dx.doi.org/XXX?}
 
@@
 %% example definition
-\def\taupav{\tau_{\mathrm{Pav}}}
+%\def\taupav{\tau_{\mathrm{Pav}}}
 
@@
 Our study examines this question using  semantically-themed citation networks.
-\textcolor{blue}{We observe that trends reported to be true across the scientific literature do not hold for focused citation networks, and we conclude that inferring novelty using co-citation analysis and random graph models benefits from disciplinary context.}
+We observe that trends reported to be true across the scientific literature do not hold for focused citation networks, and we conclude that inferring novelty using co-citation analysis and random graph models benefits from disciplinary context.
 \end{abstract}
@@
 % \end{authorsummary}
+
 \section{Introduction}
@@
 
-For citation shuffling, we developed a performant citation switching algorithm, \emph{runtime enhanced permuting citation switcher (repcs)}~\citep{GithubERNIE2019}, that randomly permuted citations within each disciplinary data set and within each year of publication: \textcolor{blue}{each citation within each article was switched within its permutation group in order to preserve the number of references from each publication year within each article.
-In do doing, the number of publications, the number of references in each data set, and the disciplinary composition of the references in each data set were preserved}.
-\textcolor{blue}{Our approach is different from previous studies in these ways: (i) we sampled citations in proportion to their citation frequency (equivalently from a multiset rather than a set) in order to better reflect citation practice, (ii) we permitted a substitution to match the original reference in a publication when the random selection process dictated it rather than attempting to enforce that a different reference be substituted, and (iii) we introduced an error correction step to delete any publications that accumulated duplicate references during the substitution process.}  As a benchmark, we used the citation switching algorithm of ~\citep{uzzi_atypical_2013}, henceforth referred to  as \emph{umsj} as also done in~\cite{boyack_vs_uzzi_2014}, using code kindly provided by the authors.
+For citation shuffling, we developed a performant citation switching algorithm, \emph{runtime enhanced permuting citation switcher (repcs)}~\citep{GithubERNIE2019}, that randomly permuted citations within each disciplinary data set and within each year of publication: each citation within each article was switched within its permutation group in order to preserve the number of references from each publication year within each article.
+In do doing, the number of publications, the number of references in each data set, and the disciplinary composition of the references in each data set were preserved.
+Our approach is different from previous studies in these ways: (i) we sampled citations in proportion to their citation frequency (equivalently from a multiset rather than a set) in order to better reflect citation practice, (ii) we permitted a substitution to match the original reference in a publication when the random selection process dictated it rather than attempting to enforce that a different reference be substituted, and (iii) we introduced an error correction step to delete any publications that accumulated duplicate references during the substitution process.
+As a benchmark, we used the citation switching algorithm of ~\citep{uzzi_atypical_2013}, henceforth referred to  as \emph{umsj} as also done in~\cite{boyack_vs_uzzi_2014}, using code kindly provided by the authors.
 A single comparative analysis showed that while 10 simulations of the WoS 1985 data set (391,860 selected articles) completed in 2,186 hours using the \emph{umsj} algorithm, it completed in less than one hour using our implementation of the \emph{repcs}   algorithm on a Spark  cluster.
@@
 Indeed, there are significant  challenges in using random models to understand human behavior, of which citation practice is one example.
-\textcolor{blue}{As we note, \emph{vide supra}, under our conditions of analysis, the trends for all three disciplinary networks are different from those for WoS.}
+As we note, \emph{vide supra}, under our conditions of analysis, the trends for all three disciplinary networks are different from those for WoS.
 
@@
 Another interesting but challenging direction would be to find ways to distinguish intra-disciplinary from cross-disciplinary novelty.
-\textcolor{blue}{In this respect, the related work of \cite{wang_bias_2017} is insightful with its use of empirical data and observations made on novelty and quality, as well as dispersion and kinetics of accrued citations of articles classified as novel.}
+In this respect, the related work of \cite{wang_bias_2017} is insightful with its use of empirical data and observations made on novelty and quality, as well as dispersion and kinetics of accrued citations of articles classified as novel.
 
-\textcolor{blue}{We note that journals are used as grouping units for articles in the three studies we discuss \citep{wang_bias_2017, uzzi_atypical_2013, boyack_vs_uzzi_2014} as well as this one. 
+We note that journals are used as grouping units for articles in the three studies we discuss \citep{wang_bias_2017, uzzi_atypical_2013, boyack_vs_uzzi_2014} as well as this one.
 While we used keyword searches to identify sets of articles, we still relied on journal grouping to generate z-scores.
@@
 We also acknowledge the limitations of using citation counts to identify impactful publications.
-Overall, evaluation in context~\citep{hicks_bibliometrics:_2015} and further consideration of the disciplinary nature of the scientific enterprise is likely to result in improved models that yield further insight.}
+Overall, evaluation in context~\citep{hicks_bibliometrics:_2015} and further consideration of the disciplinary nature of the scientific enterprise is likely to result in improved models that yield further knowledge.
 
@@
 Code generated for this study is freely available from our Github site~\citep{GithubERNIE2019}.
-Avon Davey's present affiliation is GlaxoSmithKline, Research Triangle Park, NC, USA.
 His contributions to this manuscript were made when he was a full time employee of NET ESolutions Corporation.
@@
 All authors reviewed the manuscript, which was written by GC, JB, and TW.
+Avon Davey's present affiliation is GlaxoSmithKline, Research Triangle Park, NC, USA.
 

### 2019-09-17 cocit_r_final.tex
per QSS checklist

@@
 \keywords{co-citation analysis, bibliometrics, random graphs }
+
+% ORCID_ids
+% James Bradley: 0000-0001-8766-6830
+% Sitaram Devarakonda: 0000-0001-7722-756X
+% Avon Davey: 0000-0002-1221-9283
+% Dmitriy Korobskiy: 0000-0002-7909-0218
+% Siyu Liu: 0000-0003-4051-2476
+% Djamil Lakhdar-Hamina: 0000-0002-8209-093X
+% Tandy Warnow: 0000-0001-7717-3514
+% George Chacko: 0000-0002-2127-1892
 
@@
 \centering
-\includegraphics[width=0.6\linewidth]{background-effect}     
+\includegraphics[width=0.6\linewidth]{background-effect_final}     
 \caption{Citation shuffling using the local network preserves the disciplinary composition of references within networks, but using the global network does not.
@@
 TW receives funding from the Grainger Foundation.
+Avon Davey's present affiliation is GlaxoSmithKline, Research Triangle Park, NC, USA.
+His contributions to this manuscript were made when he was a full time employee of NET ESolutions Corporation.
+The authors do not declare any competing interests.
+Access to the bibliographic data analyzed in this study requires a license from Clarivate Analytics, which had no role in funding, experimental design, review of results, and conclusions presented.
 Code generated for this study is freely available from our Github site~\citep{GithubERNIE2019}.
-His contributions to this manuscript were made when he was a full time employee of NET ESolutions Corporation.
- Access to the bibliographic data analyzed in this study requires a license from Clarivate Analytics, which had no role in funding, experimental design, review of results, and conclusions presented. 
+
 \authorcontributions 
-This study was designed by GC, JB, SD, and TW.
-Simulations and analysis were performed by AD, DLH, GC, JB, and SD.
-Infrastructure and workflows used to generate data used in this study were developed by AD, DK, SL, SD, and GC.
-All authors reviewed the manuscript, which was written by GC, JB, and TW.
-Avon Davey's present affiliation is GlaxoSmithKline, Research Triangle Park, NC, USA.
+Conceptualization, GC, JB, SD, and TW; Methodology, AD, DK, GC, JB, SD, SL, and TW; Investigation, DL-H, GC, JB, and SD; Writing -Original Draft, GC, JB, TW; Writing- Review and Editing, AD, DK, DL-H, GC, JB, SD, SL, and  TW;
+Funding Acquisition, GC; Resources, DK and GC; Supervision, GC. Authors are listed in alphabetic order.
 

### 2019-09-17 cocit_r_final.tex
compliance

@@
 \acknowledgments
+We thank the editor and two anonymous reviewers for their helpful comments.
 We thank the authors of \citep{uzzi_atypical_2013} for sharing their simulation code.
 We are grateful to Kevin Boyack and Dick Klavans for constructively critical discussions.
-We thank the editor and two anonymous reviewers for their insightful comments.
+We also thank Stephen Gallo and Scott Glisson for helpful suggestions.
+The authors do not declare any competing interests.
 Research and development reported in this publication was partially supported by Federal funds from the National Institute on Drug Abuse, National Institutes of Health, US Department of Health and Human Services, under Contract Nos.
@@
 TW receives funding from the Grainger Foundation.
-Avon Davey's present affiliation is GlaxoSmithKline, Research Triangle Park, NC, USA.
-His contributions to this manuscript were made when he was a full time employee of NET ESolutions Corporation.
-The authors do not declare any competing interests.
+Avon Davey's present affiliation is GlaxoSmithKline, Research Triangle Park, NC, USA but his contributions to this manuscript were made while he was a full time employee of NET ESolutions Corporation.
 Access to the bibliographic data analyzed in this study requires a license from Clarivate Analytics, which had no role in funding, experimental design, review of results, and conclusions presented.

### 2019-09-18 cocit_r_final.tex
final-final

@@
 For the applied physics data set, we directly searched traditional subject labels in WoS for `Physics, Applied'.
-While applied physics and immunology represent somewhat small networks (roughly 3-6\% of analytical WoS dataset), metabolism represents approximately 20-23\%, making them interesting and meaningful test cases.
+While applied physics and immunology represent somewhat small networks (roughly 3-6\% of our analytical WoS datasets) over the three years examined, metabolism represents approximately 20-23\%, making them interesting and meaningful test cases.
 We also examined publications in the five major research areas in WoS: life sciences \& biomedicine, physical sciences, technology, social sciences, and arts \& humanities,  using the extended WoS subcategory classification of 153 sub-groups to categorize disciplinary composition of cited references in the data sets we studied.
@@
 For citation shuffling, we developed a performant citation switching algorithm, \emph{runtime enhanced permuting citation switcher (repcs)}~\citep{GithubERNIE2019}, that randomly permuted citations within each disciplinary data set and within each year of publication: each citation within each article was switched within its permutation group in order to preserve the number of references from each publication year within each article.
-In do doing, the number of publications, the number of references in each data set, and the disciplinary composition of the references in each data set were preserved.
+In so doing, the number of publications, the number of references in each data set, and the disciplinary composition of the references in each data set were preserved.
 Our approach is different from previous studies in these ways: (i) we sampled citations in proportion to their citation frequency (equivalently from a multiset rather than a set) in order to better reflect citation practice, (ii) we permitted a substitution to match the original reference in a publication when the random selection process dictated it rather than attempting to enforce that a different reference be substituted, and (iii) we introduced an error correction step to delete any publications that accumulated duplicate references during the substitution process.
@@
 We also tested \emph{repcs}  under comparable conditions to \emph{umsj} and estimated a runtime advantage of at least two orders of magnitude.
-This runtime advantage was significant enough that we chose to use the \emph{repcs}   algorithm in our study and generated expected values averaged from 1,000 simulations for improved coverage of every data set we analyzed.
+This runtime advantage was significant enough that we chose to use the \emph{repcs}   algorithm in our study and generated expected values averaged over 1,000 simulations for improved coverage of every data set we analyzed.
 
-Averaging the result of 1,000 simulations for each data set studied, z-scores were then calculated for each journal-pair using the formula $(F_{obs} - F_{exp})/\sigma$ where $F_{obs}$ is the observed frequency, $F_{exp}$ is the averaged simulated frequency, and $\sigma$ is the standard deviation of the simulated frequencies for a journal pair\citep{uzzi_atypical_2013}.
+Using averaged results from 1,000 simulations for each data set studied, z-scores were calculated for each journal-pair using the formula $(F_{obs} - F_{exp})/\sigma$ where $F_{obs}$ is the observed frequency, $F_{exp}$ is the averaged simulated frequency, and $\sigma$ is the standard deviation of the simulated frequencies for a journal pair\citep{uzzi_atypical_2013}.
 As a result of these calculations, each publication becomes associated with a set of z-scores corresponding to the journal pairs derived from pairwise combinations of its cited references.
@@
 We thank the editor and two anonymous reviewers for their helpful comments.
-We thank the authors of \citep{uzzi_atypical_2013} for sharing their simulation code.
+We thank the authors of \citep{uzzi_atypical_2013} for sharing their Python code for citation swapping.
 We are grateful to Kevin Boyack and Dick Klavans for constructively critical discussions.
 We also thank Stephen Gallo and Scott Glisson for helpful suggestions.
-The authors do not declare any competing interests.
 Research and development reported in this publication was partially supported by Federal funds from the National Institute on Drug Abuse, National Institutes of Health, US Department of Health and Human Services, under Contract Nos.
@@
 TW receives funding from the Grainger Foundation.
-Avon Davey's present affiliation is GlaxoSmithKline, Research Triangle Park, NC, USA but his contributions to this manuscript were made while he was a full time employee of NET ESolutions Corporation.
-Access to the bibliographic data analyzed in this study requires a license from Clarivate Analytics, which had no role in funding, experimental design, review of results, and conclusions presented.
+
+\section{Competing Interests}The authors have no competing interests.
+Web of Science data leased from Clarivate Analytics was used in this study.
+Clarivate Analytics, had no role in conceptualization, experimental design, review of results, conclusions presented, and funding.
+Avon Davey's present affiliation is GlaxoSmithKline, Research Triangle Park, NC, USA.
+His contributions to this article were made while he was a full time employee of NET ESolutions Corporation.
+
+\section{Data Availability} Access to the bibliographic data analyzed in this study requires a license from Clarivate Analytics.
+We have made supplementary data available on Mendeley Data at \\DOI: 10.17632/4n8ns8vzvz.
 Code generated for this study is freely available from our Github site~\citep{GithubERNIE2019}.

### 2019-09-19 supplementary-cocit.tex
prepped supplementary documents

\documentclass{article}
\usepackage{changepage}
\usepackage{graphicx}

\begin{document}
\centerline{Supplementary Information for ``Co-citations in context: disciplinary heterogeneity is relevant''}
\centerline{James Bradley, Sitaram Devarakonda, Avon Davey, Siyu Liu, Dmitriy Korobskiy, Tandy Warnow, George Chacko}

\section{Discussion of algorithmic approach in Uzzi et al (2013)}
The MCMC algorithmic approach in Uzzi et al (2013), DOI: 10.1126/science.1240474 for citation switching involves building three dicts 
containing publications, references, and year of publication information, and using them as lookup tables for  various operations. In plain language, an iteration process selects each publication in turn. Then each reference in 
the selected publication is replaced by a random selection from the *set* of eligible references published in the same year.  If the potential replacement candidate is not the same as the reference to be replaced then a replacement is made. If it is the same, then up to 20 tries are made to find a non-self replacement. This process occurs for all the references in the set of publications being analyzed. Thus, reference a in three publications A,B,C could be replaced by references [b,c,d] or [b,b,d] but not [a,b,c]. Secondly, a reciprocal switch is made with a publication that cites the replacement. Thus, if publication A cites reference a published in year X then a is substituted with reference b also published in year X and and a randomly selected publication, say publication B that cites b, will have b replaced with a. See 'satyam\_mukherjee\_mcmc.py' kindly provided by the authors of this paper DOI: 10.1126/science.1240474.

Our approach is roughly similar. References are first grouped by year of publication and then the sample function in R is used on the *multi-set* of potential replacements to permute all references in a single step. A check is then run to see if the permutation process has created any duplicate references within each publication. Those publications with duplicate references are then deleted (typically $<= 0.2\%$). See `permute\_script.R'.  A key difference is that the pool of replacement candidates is the *set* in one case and the *multi-set* in the 
other. Every substitution in the first approach is independent for instances of the same reference. Using the *multi-set* accounts for existing citation frequency when selecting possible replacements. Thus a publication in year X that has accumulated 10,000 citations is more likely to be selected than a publication that is cited only once. Reference a in publications A,B,C could be replaced by references [a,b,c]. This process is very fast in comparison and we have scaled it up even further by porting it to the Spark environment. In a recent comparison of publications in WoS in year 1985 (39,1860 pubs and 5,588,861 total references), ten simulations using the `satyam\_mukherjee\_mcmc.py' took roughly 22 hours per simulation on a 32 Gb CentOS VM. Run times using our approach on comparable hardware amounted to roughly 30 seconds per shuffle plus an overhead of 3-4 hours to consolidate the data. We, also performed 1,000 simulations in 60 hrs using a small Spark cluster for the much large 2005 data set (886,648 publications and 19,036,324 total references)

For input data we selected all publications of type `Article' in WoS for a given year. Articles are then filtered to those that have at least two references in them. Further, only those references that have complete records in the Web of Science Core Collection are considered. This eliminates those that have cryptic references to other data sources or are just placeholders. Publications and references are mapped to their respective journals using ISSNs as identifiers. Where a reference has more than one ISSN, the most popular one is assigned to ensure that each reference is associated only with one journal.

For n $<= 1000$ simulations on disciplinary networks (immunology, metabolism, applied physics) permute\_script.R is 
used to generate n files each with shuffled references. Typically, run times are less than 2 min per simulation on a 32 Gb CentOS box with 8 vCPUs in MS Azure. The permutation\_testing\_script.sh shell script is then run, which calls four Python scripts in turn.

\begin{enumerate}
\item observed\_frequency.py: generates journal pair frequencies for the year slice of the WoS or disciplinary data set being analyzed.
\item background\_frequency.py: generates journal pair frequencies for the background model implemented using permute\_script.R
\item journal\_count.py: joins all permuted files generated by background\_frequency and calculates mean, sd, and z-scores
\item Table\_generator.py: final output file which contains all publications, reference pairs along with observed frequency and z-scores
\end{enumerate}

Thus, the workflow is (i) generate year slice (input data) (ii) generate background models by shuffling references (iii) calculate journal pair frequencies (iv) consolidate observed and simulated frequencies into a single table and calculate z-scores.

This process tends to slow down with large data set such as WoS in 2005 with ~886,000 publications and 5.8 million
journal pairs. Consequently, the entire process has been ported to Spark and provisioning a cluster, copying source data from the ERNIE PostgreSQL database over to Spark, conducting in-memory calculations, and copying a final table back to PostgreSQL has been automated (see Spark folder).\clearpage

\begin{table}
\begin{adjustwidth}{-2cm}{}
\caption{Comparison of Citation Switching Algorithms. The citation switching algorithm of Uzzi et al. (2013) \emph{umsj} has been implemented in Python. Ten simulations of the WoS 1985 data set were executed on a 32 Gb, 8 vCPU CentOS 7.4 virtual machine to generate the data in Col 2. Each simulation took roughly 22 hours to complete. Scaling up the experiment, 10 or 1000 simulations of our modifications of this algorithm \emph{repcs}were executed on a 4-node Apache Spark cluster for the Wos 1985 data set. 1000 simulations completed in less than 50 hours (roughly 3 minute/simulation).}
\vspace{3mm}
\begin{centering}
\scalebox{0.9}{
\begin{tabular}{|r lllll l|}
\hline
& data set & Wos 1985 & WoS 1985 & WoS 1985 & WoS 1995 & WoS 2005 \\ 
\hline
1 & Input publications & 391,860 & 391,860 & 391,860 & 537,160 & 886,648 \\ 
2 & Input journals & 8,075 & 8,075 & 8,075 & 10,983 & 15,203 \\ 
3 & Observed input journal pairs & 1,277,349 & 1,277,349 & 1,277,349 & 2,373,226 & 5,847,432 \\ 
4 & Simulated journal pairs & 961,487 & 959765 & 1,200,403 & 2,288,225 & 5,835,794 \\
5 & Journal pair coverage & 75.27\% & 75.14\% & 93.97\% & 96.41\% & 99.80\% \\ 
6 & Min z-score & -132.71 & -148.14 & -104.50 & -215.96 & -273.708 \\ 
7 & Q1 z-score & -2.131 & -2.151 & -1.43 & -1.49 & -1.56 \\ 
8 & Median z-score & -0.536 & -0.54 & -0.24 & -0.25 & 0.555 \\ 
9 & Q3 z-score & 3.333 & 3.365 & 4.29 & 4.15 & 2.423 \\ 
10 & Max z-score & 16598.534 & 22015.891 & 12,028.55 & 12,662.15 & 6,152.57 \\ 
11 & Environment & CentOS 7.4 & Spark 2.3 & Spark 2.3 & Spark 2.3 & Spark 2.3 \\
12 & Number of simulations & 10 & 10 & 1000 & 1000 & 1000 \\ 
13 & Run time & 2186h (22 hr /sim) & $<$ 1 hr & $<$ 50h & 50h & 60h \\ 
14 & Algorithm & umsj &  repcs &   repcs &   repcs &   repcs \\ 
\hline
\end{tabular}}
\end{centering}
\end{adjustwidth}
\end{table}

\begin{table}
\begin{adjustwidth}{-2cm}{}
\begin{centering}
\caption{Profile of Disciplinary Networks. Data shown represent the results of 1000 simulations for the applied physics (ap), immunology (imm), 
and metabolism (metab) disciplinary networks. Summary statistics for z-scores are provided as 
well as the number of publications in each data set that were the input to the simulation process.}
\vspace{3mm}
\scalebox{0.9}{
\begin{tabular}{|r l ll ll ll l|}
\hline
 & data set & Input Publications & Journal Pairs & Min & Q1 & Median & Q3 & Max \\ 
\hline
1 & ap1985 & 10298 & 34,267 & -23.05 & -0.94 & -0.21 & 3.03 & 1490.42 \\ 
  2 & ap1995 & 21012 & 60,340 & -45.36 & -0.97 & -0.24 & 2.86 & 646.03 \\ 
  3 & ap2005 & 35600 & 199,928 & -47.76 & -0.80 & -0.20 & 3.53 & 2158.47 \\ 
  4 & imm85 & 17942 & 159,107 & -48.33 & -1.09 & -0.27 & 2.49 & 934.63 \\ 
  5 & imm95 & 22759 & 319,855 & -59.56 & -1.10 & -0.28 & 2.37 & 1507.61 \\ 
  6 & imm2005 & 28539 & 751,950 & -74.54 & -0.99 & -0.30 & 1.84 & 2560.51 \\ 
  7 & metab1985 & 67342 & 431,993 & -97.00 & -1.46 & -0.34 & 2.34 & 4193.49 \\ 
  8 & metab1995 & 100350 & 865,406 & -132.85 & -1.56 & -0.37 & 2.16 & 3998.44 \\ 
  9 & metab2005 & 159910 & 2,349,005 & -127.81 & -1.60 & -0.41 & 1.83 & 3472.77 \\
\hline
\end{tabular}}
\end{centering}
\end{adjustwidth}
\end{table}

\begin{table}
\begin{adjustwidth}{-1cm}{}
\begin{centering}
\caption{Comparison of top 5\% cited publications vs all publications in applied physics (ap) immunology (imm), metabolism (metab), and WoS data sets.
Numbers shown are percent of publications in each group. Data are shown for reference years 1985, 1995, and 2005 }
\vspace{3mm}
\scalebox{0.8}{
\begin{tabular}{|r rlrrrrrrr r|}
  \hline
 & year & category & ap\_5 & ap\_all & imm\_5 & imm\_all & metab\_5 & metab\_all & wos\_5 & wos\_all \\ 
  \hline
1 & 1985 & HCHN &  34 &  25 &  29 &  33 &  24 &  29 &   6 &   6 \\ 
  2 & 1985 & HCLN &  15 &  25 &  21 &  17 &  26 &  21 &  44 &  44 \\ 
  3 & 1985 & LCHN &  50 &  47 &  48 &  49 &  48 &  48 &  32 &  29 \\ 
  4 & 1985 & LCLN &   1 &   3 &   2 &   1 &   2 &   2 &  18 &  21 \\ 
  5 & 1995 & HCHN &  35 &  27 &  29 &  34 &  26 &  31 &   6 &   7 \\ 
  6 & 1995 & HCLN &  15 &  23 &  21 &  16 &  24 &  19 &  44 &  43 \\ 
  7 & 1995 & LCHN &  50 &  48 &  48 &  49 &  48 &  48 &  33 &  29 \\ 
  8 & 1995 & LCLN &   0 &   2 &   2 &   1 &   2 &   2 &  17 &  21 \\ 
  9 & 2005 & HCHN &  31 &  29 &  36 &  36 &  30 &  30 &   8 &   7 \\ 
  10 & 2005 & HCLN &  19 &  20 &  14 &  14 &  20 &  20 &  42 &  43 \\ 
  11 & 2005 & LCHN &  48 &  49 &  50 &  49 &  49 &  49 &  30 &  27 \\ 
  12 & 2005 & LCLN &   2 &   2 &   0 &   1 &   1 &   1 &  20 &  23 \\ 
   \hline
\end{tabular}}
\end{centering}
\end{adjustwidth}
\end{table}

\begin{table}
\begin{centering}
\caption{Statistical Significance of Deviation from a Random Distribution of Hits. These are hypothesis test data for the null hypothesis that hits are distributed among the categories randomly in proportion to the 
number of articles in each category using a Chi Square Goodness of Fit Test for novel articles defined as those with the 10th percentile $z$-score being negative and the 1st percentile $z$-score being negative. 
Rejecting the null hypothesis supports the alternate hypothesis that hit rates vary among the categories. The $p$ values indicate the significance of the difference between the observed number of hits and the 
expected number of hits given by the random null model. $\dagger$ denotes that the Chi Square Goodness of Fit Test is not valid because the expected number of hits in at least one category was less than 
the required five hits. This was caused by the combination of a small number of articles in a category due to a low overall hit rate ($1\%$ or $2\%$) and a definition of novelty ($1\%$) that resulted in few articles
 being defined as being of low novelty.  Results that are significant at the 0.05 level are shown in bold font and those significant at the 0.10 level are shown in italics.}
\vspace{3mm}
\scalebox{0.7}{
\begin{tabular}{|l crr r|}
 \hline
Data  && \multicolumn{1}{c}{Highly Cited} & \multicolumn{2}{c}{$p$ value} \\
Set & Year & \multicolumn{1}{c}{Min. Percentile} & Novelty Def.: $1\%$ & Novelty Def.: $10\%$ \\ 
\hline
Immunology & 1985 & 1\% & $\dagger$ 0.000  & $\dagger$ 0.000  \\ 
Immunology & 1985 & 2\% & $\dagger$ 0.000  & $\dagger$ 0.000  \\ 
Immunology & 1985 & 5\% & $\dagger$ 0.000  & \textbf{0.000} \\ 
Immunology & 1985 & 10\% & \textbf{0.000} & \textbf{0.000} \\ 
Immunology & 1995 & 1\% & $\dagger$ 0.000  & $\dagger$ 0.000  \\ 
Immunology & 1995 & 2\% & $\dagger$ 0.000  & $\dagger$ 0.000  \\ 
Immunology & 1995 & 5\% & $\dagger$ 0.000  & \textbf{0.000} \\ 
Immunology & 1995 & 10\% & \textbf{0.000} & \textbf{0.000} \\ 
Immunology & 2005 & 1\% & $\dagger$ 0.000  & $\dagger$ 0.000  \\ 
Immunology & 2005 & 2\% & $\dagger$ 0.000  & $\dagger$ 0.000  \\ 
Immunology & 2005 & 5\% & $\dagger$ 0.000  & \textbf{0.000} \\ 
Immunology & 2005 & 10\% & \textbf{0.000} & \textbf{0.000} \\
Metabolism & 1985 & 1\% & \textbf{0.000} & \textbf{0.000} \\ 
Metabolism & 1985 & 2\% & \textbf{0.000} & \textbf{0.000} \\ 
Metabolism & 1985 & 5\% & \textbf{0.000} & \textbf{0.000} \\ 
Metabolism & 1985 & 10\% & \textbf{0.000} & \textbf{0.000} \\ 
Metabolism & 1995 & 1\% & \textbf{0.000} & \textbf{0.000} \\ 
Metabolism & 1995 & 2\% & \textbf{0.000} & \textbf{0.000} \\ 
Metabolism & 1995 & 5\% & \textbf{0.000} & \textbf{0.000} \\ 
Metabolism & 1995 & 10\% & \textbf{0.000} & \textbf{0.000} \\ 
Metabolism & 2005 & 1\% & $\dagger$ 0.000  & \textbf{0.000} \\ 
Metabolism & 2005 & 2\% & \textbf{0.000} & \textbf{0.000} \\ 
Metabolism & 2005 & 5\% & \textbf{0.000} & \textbf{0.000} \\ 
Metabolism & 2005 & 10\% & \textbf{0.000} & \textbf{0.000} \\
Applied Physics & 1985 & 1\% & $\dagger$ 0.027  & $\dagger$ 0.025  \\ 
Applied Physics & 1985 & 2\% & $\dagger$ 0.000  & $\dagger$ 0.000  \\ 
Applied Physics & 1985 & 5\% & \textbf{0.000} & \textbf{0.000} \\ 
Applied Physics & 1985 & 10\% & \textbf{0.000} & \textbf{0.000} \\ 
Applied Physics & 1995 & 1\% & $\dagger$ 0.010  & $\dagger$ 0.013  \\ 
Applied Physics & 1995 & 2\% & \textbf{0.000} & \textbf{0.000} \\ 
Applied Physics & 1995 & 5\% & \textbf{0.000} & \textbf{0.000} \\ 
Applied Physics & 1995 & 10\% & \textbf{0.000} & \textbf{0.000} \\ 
Applied Physics & 2005 & 1\% & $\dagger$ 0.000  & \textbf{0.000} \\ 
Applied Physics & 2005 & 2\% & \textbf{0.000} & \textbf{0.000} \\ 
Applied Physics & 2005 & 5\% & \textbf{0.000} & \textbf{0.000} \\ 
Applied Physics & 2005 & 10\% & \textbf{0.000} & \textbf{0.000} \\ 
Web of Science & 1985 & 1\% & \textbf{0.000} & \textbf{0.000} \\ 
Web of Science & 1985 & 2\% & \textbf{0.000} & \textbf{0.000} \\ 
Web of Science & 1985 & 5\% & \textbf{0.000} & \textbf{0.000} \\ 
Web of Science & 1985 & 10\% & \textbf{0.000} & \textbf{0.000} \\
Web of Science & 1995 & 1\% & \textbf{0.000} & \textbf{0.000} \\ 
Web of Science & 1995 & 2\% & \textbf{0.000} & \textbf{0.000} \\ 
Web of Science & 1995 & 5\% & \textbf{0.000} & \textbf{0.000} \\ 
Web of Science & 1995 & 10\% & \textbf{0.000} & \textbf{0.000} \\ 
Web of Science & 2005 & 1\% & \textbf{0.000} & \textbf{0.000} \\ 
Web of Science & 2005 & 2\% & \textbf{0.000} & \textbf{0.000} \\ 
Web of Science & 2005 & 5\% & \textbf{0.000} & \textbf{0.000} \\ 
Web of Science & 2005 & 10\% & \textbf{0.000} & \textbf{0.000} \\ 
\hline
\end{tabular}}
\end{centering}
\end{table}

\pagenumbering{gobble}
\begin{table}
\begin{centering}
\caption{Hit Rates By Category. The hit rate is the percentage of publications in the referenced category that are in the top $1\%$, $2\%$, $5\%$, or $10\%$ of papers according to citation count  (see column 3) for novel articles defined as those with the 10th percentile z-score being negative. The z-scores are computed using the local network. The category with the highest percentile is boldfaced (the second highest is also boldfaced if within 0.3\% and greater than the overall percentage of articles considered to be hits). We also evaluated novelty defined as the 1st percentile of z-scores being negative. We report here on novelty defined at the most stringent parameter setting.}
\scalebox{0.7}{
\begin{tabular}{ccrrrrr}
 \hline
 Data  && \multicolumn{1}{c}{Highly Cited}    \\
 Set & Year  & \multicolumn{1}{c}{Min. Percentile} & LNLC & LNHC & HNLC & HNHC \\ 
  \hline
Immunology & 1985&1\%& 0.0& \bf{1.5}& 0.6& \bf{1.4} \\ 
Immunology & 1985&2\%& 0.0& \bf{3.0}& 1.2& \bf{2.8} \\ 
Immunology & 1985&5\%& 1.5& 6.5& 3.2& \bf{7.1} \\ 
Immunology & 1985&10\%& 3.0& 12.0& 7.1& \bf{14.0} \\ 
Immunology & 1995&1\%& 0.0& \bf{1.9}& 0.5& 1.4 \\ 
Immunology & 1995&2\%& 0.0& \bf{3.4}& 1.1& 2.8 \\ 
Immunology & 1995&5\%& 0.6& \bf{7.2}& 3.2& 6.8 \\ 
Immunology & 1995&10\%& 1.7& \bf{12.8}& 7.6& \bf{12.9} \\ 
Immunology & 2005&1\%& 0.0& \bf{1.5}& 0.6& \bf{1.3} \\ 
Immunology & 2005&2\%& 0.0& \bf{2.7}& 1.3& \bf{2.7} \\ 
Immunology & 2005&5\%& 0.0& 6.0& 3.6& \bf{6.7} \\ 
Immunology & 2005&10\%& 2.0& 10.8& 8.1& \bf{12.9} \\ 
Metabolism & 1985&1\%& 0.1& \bf{1.5}& 0.5& \bf{1.5} \\ 
Metabolism & 1985&2\%& 0.3& \bf{2.7}& 1.3& \bf{2.9} \\ 
Metabolism & 1985&5\%& 0.7& 6.6& 3.4& \bf{7.0} \\ 
Metabolism & 1985&10\%& 2.3& 12.3& 7.2& \bf{13.8} \\ 
Metabolism & 1995&1\%& 0.1& \bf{1.7}& 0.6& \bf{1.4} \\ 
Metabolism & 1995&2\%& 0.3& \bf{3.1}& 1.2& \bf{2.8} \\ 
Metabolism & 1995&5\%& 0.7& \bf{7.}0& 3.4& \bf{6.7} \\ 
Metabolism & 1995&10\%& 1.9& \bf{13.0}& 7.4& \bf{13.3} \\ 
Metabolism & 2005&1\%& 0.6& \bf{1.3}& 0.7& \bf{1.3} \\ 
Metabolism & 2005&2\%& 1.0& \bf{2.5}& 1.5& \bf{2.6} \\ 
Metabolism & 2005&5\%& 2.3& 6.0& 3.9& \bf{6.6} \\ 
Metabolism & 2005&10\%& 4.1& 11.4& 8.1& \bf{12.6} \\ 
Applied Physics & 1985&1\%& 0.0& 0.5& \bf{1.2}& \bf{1.2} \\ 
Applied Physics & 1985&2\%& 0.9& 0.9& \bf{2.5}& \bf{2.4} \\ 
Applied Physics & 1985&5\%& 2.8& 3.0& 5.5& \bf{6.5} \\ 
Applied Physics & 1985&10\%& 5.2& 6.7& 10.6& \bf{13.2} \\ 
Applied Physics & 1995&1\%& 0.2& 0.7& \bf{1.2}& \bf{1.0} \\ 
Applied Physics & 1995&2\%& 0.2& 1.3& \bf{2.5}& 2.1 \\ 
Applied Physics & 1995&5\%& 0.9& 3.4& \bf{6.0}& 5.2 \\ 
Applied Physics & 1995&10\%& 4.7& 7.9& \bf{12.3}& 10.9 \\ 
Applied Physics & 2005&1\%& 0.8& 0.6& \bf{1.1}& \bf{1.3} \\ 
Applied Physics & 2005&2\%& 1.1& 1.3& \bf{2.1}& \bf{2.3}\\ 
Applied Physics & 2005&5\%& 1.6& 3.3& 5.4& \bf{5.9} \\ 
Applied Physics & 2005&10\%& 3.9& 7.5& 10.7& \bf{11.4} \\ 
Web of Science & 1985&1\%& 0.4& 1.2& 1.0& \bf{1.6} \\ 
Web of Science & 1985&2\%& 0.9& 2.4& 2.0& \bf{3.3} \\ 
Web of Science & 1985&5\%& 2.6& 5.9& 5.1& \bf{8.4} \\ 
Web of Science & 1985&10\%& 5.8& 11.4& 10.4& \bf{15.8} \\ 
Web of Science & 1995&1\%& 0.4& 1.3& 0.9& \bf{1.7} \\ 
Web of Science & 1995&2\%& 0.9& 2.4& 1.9& \bf{3.3} \\ 
Web of Science & 1995&5\%& 2.5& 6.0& 5.0& \bf{8.0} \\ 
Web of Science & 1995&10\%& 5.6& 11.5& 10.4& \bf{15.6} \\ 
Web of Science & 2005&1\%& 0.4& 1.2& 1.0& \bf{1.7} \\ 
Web of Science & 2005&2\%& 0.9& 2.3& 2.0& \bf{3.4} \\ 
Web of Science & 2005&5\%& 2.5& 5.7& 5.3& \bf{8.1} \\ 
Web of Science & 2005&10\%& 5.6& 11.2& 10.8& \bf{15.0} \\
\hline
\end{tabular}}
\end{centering}
\end{table}

\begin{table}
\begin{centering}
\caption{Explanatory Power of Novelty and Conventionality. This table lists $p$-values in the form of cumulative right-hand tail probabilities for the observed number of hits in the Low Novelty, High Novelty, Low Conventionality, and High Conventionality categories under the sampling distribution generated by the null hypothesis of a random distribution of hit articles in proportion to the number of articles in each of the categories. A small $p$-value, therefore, indicates a number of hits that exceeds the expected number. Results that indicate statistically significant numbers of hits in excess of the expected number at the 0.05 level using a two-tailed test are highlighted in bold font, and those significant at the 0.10 level are italicized.   These data are for the circumstances where novel citation patterns are defined by whether an article's 10th percentile $z$-score is negative. The $z$-scores are computed using the local network. We report these data because this is the most stringent definition of novelty}
\vspace{2mm}
\scalebox{0.7}{
\begin{tabular}{|c rrrrr r|}
 \hline
  & & & \multicolumn{4}{c}{Cumulative Probabilities} \\
   Data &  & \multicolumn{1}{c}{Highly Cited}    & \multicolumn{2}{c}{Conventionality} & \multicolumn{2}{c}{Novelty}      \\  % inserts table
 Set & Year&  \multicolumn{1}{c}{Min. Percentile}  &  \multicolumn{1}{c}{Low} &  \multicolumn{1}{c}{High} &  \multicolumn{1}{c}{Low} &  \multicolumn{1}{c}{High} \\ 
\hline
Immunology & 1985 & 1\% & 1.000 & \textbf{0.000} & \textbf{0.020} & 0.866 \\ 
Immunology & 1985 & 2\% & 1.000 & \textbf{0.000} & \textbf{0.002} & 0.940 \\ 
Immunology & 1985 & 5\% & 1.000 & \textbf{0.000} & \textbf{0.002} & 0.924 \\ 
Immunology & 1985 & 10\% & 1.000 & \textbf{0.000} & \textbf{0.017} & 0.853 \\ 
Immunology & 1995 & 1\% & 1.000 & \textbf{0.000} & \textbf{0.000} & 0.985 \\ 
Immunology & 1995 & 2\% & 1.000 & \textbf{0.000} & \textbf{0.000} & 0.991 \\ 
Immunology & 1995 & 5\% & 1.000 & \textbf{0.000} & \textbf{0.000} & 0.988 \\ 
Immunology & 1995 & 10\% & 1.000 & \textbf{0.000} & \textbf{0.000} & 0.972 \\ 
Immunology & 2005 & 1\% & 1.000 & \textbf{0.000} & \textbf{0.005} & 0.882 \\ 
Immunology & 2005 & 2\% & 1.000 & \textbf{0.000} & \textbf{0.007} & 0.862 \\ 
Immunology & 2005 & 5\% & 1.000 & \textbf{0.000} & \textbf{0.012} & 0.837 \\ 
Immunology & 2005 & 10\% & 1.000 & \textbf{0.000} & 0.265 & 0.609 \\ 
Metabolism & 1985 & 1\% & 1.000 & \textbf{0.000} & \textbf{0.000} & 0.991 \\ 
Metabolism & 1985 & 2\% & 1.000 & \textbf{0.000} & \textbf{0.000} & 0.986 \\ 
Metabolism & 1985 & 5\% & 1.000 & \textbf{0.000} & \textbf{0.000} & 0.999 \\ 
Metabolism & 1985 & 10\% & 1.000 & \textbf{0.000} & \textbf{0.000} & 0.997 \\ 
Metabolism & 1995 & 1\% & 1.000 & \textbf{0.000} & \textbf{0.000} & 1.000 \\ 
Metabolism & 1995 & 2\% & 1.000 & \textbf{0.000} & \textbf{0.000} & 1.000 \\ 
Metabolism & 1995 & 5\% & 1.000 & \textbf{0.000} & \textbf{0.000} & 1.000 \\ 
Metabolism & 1995 & 10\% & 1.000 & \textbf{0.000} & \textbf{0.000} & 1.000 \\ 
Metabolism & 2005 & 1\% & 1.000 & \textbf{0.000} & \textbf{0.000} & 0.997 \\ 
Metabolism & 2005 & 2\% & 1.000 & \textbf{0.000} & \textbf{0.000} & 0.998 \\ 
Metabolism & 2005 & 5\% & 1.000 & \textbf{0.000} & \textbf{0.000} & 0.998 \\ 
Metabolism & 2005 & 10\% & 1.000 & \textbf{0.000} & \textbf{0.000} & 0.996 \\ 
Applied Physics & 1985 & 1\% & 0.177 & 0.860 & 0.998 & 0.071 \\ 
Applied Physics & 1985 & 2\% & 0.066 & 0.952 & 1.000 & \textbf{0.013} \\ 
Applied Physics & 1985 & 5\% & 0.200 & 0.818 & 1.000 & \textbf{0.003} \\ 
Applied Physics & 1985 & 10\% & 0.390 & 0.625 & 1.000 & \textbf{0.000} \\ 
Applied Physics & 1995 & 1\% & 0.062 & 0.955 & 0.996 & 0.090 \\ 
Applied Physics & 1995 & 2\% & \textbf{0.018} & 0.988 & 1.000 & \textbf{0.011} \\ 
Applied Physics & 1995 & 5\% & \textbf{0.002} & 0.999 & 1.000 & \textbf{0.001} \\ 
Applied Physics & 1995 & 10\% & \textbf{0.000} & 1.000 & 1.000 & \textbf{0.000} \\ 
Applied Physics & 2005 & 1\% & 0.319 & 0.706 & 1.000 & \textit{0.028} \\ 
Applied Physics & 2005 & 2\% & 0.272 & 0.748 & 1.000 & \textbf{0.015} \\ 
Applied Physics & 2005 & 5\% & 0.117 & 0.897 & 1.000 & \textbf{0.000} \\ 
Applied Physics & 2005 & 10\% & 0.102 & 0.909 & 1.000 & \textbf{0.000} \\ 
Web of Science & 1985 & 1\% & 1.000 & \textbf{0.000} & 0.986 & \textbf{0.002} \\ 
Web of Science & 1985 & 2\% & 1.000 & \textbf{0.000} & 1.000 & \textbf{0.000} \\ 
Web of Science & 1985 & 5\% & 1.000 & \textbf{0.000} & 1.000 & \textbf{0.000} \\ 
Web of Science & 1985 & 10\% & 1.000 & \textbf{0.000} & 1.000 & \textbf{0.000} \\ 
Web of Science & 1995 & 1\% & 1.000 & \textbf{0.000} & 0.969 & \textbf{0.007} \\ 
Web of Science & 1995 & 2\% & 1.000 & \textbf{0.000} & 1.000 & \textbf{0.000} \\ 
Web of Science & 1995 & 5\% & 1.000 & \textbf{0.000} & 1.000 & \textbf{0.000} \\ 
Web of Science & 1995 & 10\% & 1.000 & \textbf{0.000} & 1.000 & \textbf{0.000} \\ 
Web of Science & 2005 & 1\% & 1.000 & \textbf{0.000} & 1.000 & \textbf{0.000} \\ 
Web of Science & 2005 & 2\% & 1.000 & \textbf{0.000} & 1.000 & \textbf{0.000} \\ 
Web of Science & 2005 & 5\% & 1.000 & \textbf{0.000} & 1.000 & \textbf{0.000} \\ 
Web of Science & 2005 & 10\% & 1.000 & \textbf{0.000} & 1.000 & \textbf{0.000} \\ 
\hline
\end{tabular}} 
\end{centering}
\end{table}

%%%%%
\end{document}
%%%%%%
\end{document}
